---
title: "Advanced Text Analysis - Woman's Exponent vs. Relief Society Magazine"
author: "Birch"
date: "`r Sys.Date()`"
output:
  html_notebook:
    toc: true
    toc_float: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.width = 10, fig.height = 7)
```

# Advanced Text Analysis - Cross-Corpus Contrast

This notebook is the **R reporting layer** of the *cross-corpus* comparison
pipeline. It sits alongside the two single-corpus advanced projects
(`Claudepythonexperimentadvtext` = Woman's Exponent, `..._RSM` = Relief Society
Magazine) and answers a different question than either: **not "what is happening
inside one periodical," but "how do the two periodicals differ in meaning-space?"**

As in the single-corpus pipelines, the heavy machine-learning work runs *outside*
this knit in checkpointed Python scripts; this notebook only **loads the finished
artifacts** and turns them into figures. **If a section's artifact is missing, it
prints a "run script X first" note and skips rather than erroring.**

The contrast rests on a joint STM fit over **both** corpora
(`regression_compare_2_corpora.Rmd`), whose handoff tags every document with its
`corpus`. The Python layer then embeds the combined corpus and the new
`contrast.py` measures, specifically, how the two publications relate:

1. **Combined document atlas** — every article from both periodicals embedded in
   one sentence-transformer space and laid out in 2D, coloured by publication.
   *Do the two corpora occupy the same region, or pull apart?* *(Reads
   `embed_documents.py`.)*
2. **Embedding-space geometry** — three hard numbers for that picture: centroid
   distance, an overlap **AUC** (how separable the two are), and **kNN mixing**
   (how interleaved individual articles are). *(Reads `contrast.py` Part A.)*
3. **Topic prevalence by publication** — which joint-STM topics each periodical
   leans on. *(Pure R from the joint `theta`.)*
4. **Contrastive semantic change of shared terms** — for words both periodicals
   use ("relief", "woman", "suffrage", "welfare"…), does the *meaning* differ
   between them? Measured three ways (PRT / APD / JSD) with MacBERTh, grouping by
   **publication** instead of by time period. *(Reads `contrast.py` Part B.)*
5. **Framing-drift map** — each shared term's MacBERTh prototype in each corpus,
   projected to 2D, with a WE→RSM arrow per word. *(Reads `contrast.py` Part B.)*
6. **BERTopic over both corpora** — a neural topic model clustered on the same
   embeddings, cross-tabulated against publication. *(Reads `run_bertopic.py`.)*

Three **comparative figures** are layered onto this spine: **keyness** (§5b — the
words that most distinguish the two periodicals, via weighted log-odds) with a
**rate-vs-rate scatter** (§5c); a **topic-emphasis difference with confidence
intervals** (§6c) and a **topic co-occurrence contrast** (§6d, which topics travel
together differently); and the **sense-mix bars** (§7b) that turn the abstract
PRT/APD/JSD numbers into "what each shared word *means* in each periodical."

> **The contrastive contextual-embedding approach (sections 4–5) is the frontier
> piece.** Each occurrence of a shared word is embedded *in its sentence context*
> in one pretrained historical space (MacBERTh), so the two periodicals' usages
> are directly comparable with no alignment step. We recover genuine **sense-level**
> difference — whether "relief" leans charitable-aid vs. organizational in one
> periodical vs. the other — not just neighbour reshuffling.

---

## How to produce the inputs (read this first)

This notebook reads two families of files:

**A. Handoff from the joint STM model** (`output_linked/<scenario>/`, suffixed by
K): `advanced_input_K{K}.rds`, `advanced_docs_K{K}.csv` (carries the `corpus` +
`author` tags), `advanced_theta_K{K}.csv`, `advanced_topics_K{K}.csv`. Produced
directly by **§27b of `regression_compare_2_corpora.Rmd`** when you knit the joint
model for the matching `comparison_scenario`. (If you fit on the Linux server, copy
`comparison_session_K{K}.RData` into `output_linked/<scenario>/` and run
`scripts/generate_handoff.R {K} {scenario}` instead.)

**B. Python compute artifacts** (`output_advanced_compare/<scenario>/`). From a
terminal, using the dedicated Python 3.11 venv (NOT system Python). The scripts
read the scenario from `$env:ADV_SCENARIO` (default `compare_full`):

```text
$env:ADV_SCENARIO = "compare_full"   # or compare_WE1892-1912_RSM1914-1934
C:\Users\birch\dh-env\Scripts\python.exe scripts\embed_documents.py 35
C:\Users\birch\dh-env\Scripts\python.exe scripts\contrast.py        35
C:\Users\birch\dh-env\Scripts\python.exe scripts\run_bertopic.py    35
```

The trailing number pins K (use whatever `chosen_K` you fit in the joint model;
`35` is only an example — set it from the Combined searchK). The `ADV_SCENARIO`
env var MUST match the report's `comparison_scenario`. `embed_documents.py` is the
long, checkpointed one;
`contrast.py` reads its embeddings (Part A) and then runs MacBERTh on shared
terms (Part B). See `compareadvancedtextanalysis_handover.md` for the full primer.

---

## 1. Packages

```{r install, eval=FALSE}
install.packages(c(
  "arrow", "ggrepel", "patchwork", "scales", "uwot", "jsonlite", "DT"
))
```

```{r load-packages}
library(stm)
library(tidyverse)
library(scales)
library(ggrepel)
library(patchwork)
library(arrow)
library(uwot)
library(jsonlite)
library(DT)

set.seed(12345)
cat("Packages loaded.\n")
```

---

## 2. Paths & K-agnostic model selection

We do **not** hardcode K. The loader discovers the handoff files in
`output_linked/` and picks the requested K (or the newest). Set `pin_K` to force
a specific model; leave it `NULL` to auto-pick.

```{r paths}
base_path    <- "C:/Users/birch/Rachel/GMU/Dissertation/textanalysis/Claudepythonexperimentadvtext_compare"

# Which comparison to report on. MUST match the joint linker's comparison_scenario
# and the Python ADV_SCENARIO. One joint model (and one K) per scenario.
comparison_scenario <- "compare_full"   # or "compare_WE1892-1912_RSM1914-1934"

linked_path  <- file.path(base_path, "output_linked",          comparison_scenario)  # joint-STM handoff
adv_path     <- file.path(base_path, "output_advanced_compare", comparison_scenario)  # Python artifacts
emb_dir      <- file.path(adv_path, "embeddings")
bertopic_dir <- file.path(adv_path, "bertopic")
contrast_dir <- file.path(adv_path, "contrast")
output_path  <- file.path(adv_path, "report_figures")
if (!dir.exists(output_path)) dir.create(output_path, recursive = TRUE)

pin_K <- 20   # set to an integer (e.g. 30L) to force a model; NULL auto-picks newest

input_candidates <- list.files(linked_path, pattern = "^advanced_input_K\\d+\\.rds$",
                               full.names = TRUE)
if (length(input_candidates) == 0) {
  stop("No advanced_input_K*.rds in ", linked_path,
       "\nKnit regression_compare_2_corpora.Rmd through §27b (or run ",
       "scripts/generate_handoff.R) first.")
}
avail_K <- as.integer(str_match(basename(input_candidates), "_K(\\d+)\\.rds$")[, 2])

if (!is.null(pin_K)) {
  if (!pin_K %in% avail_K) {
    stop("Requested K=", pin_K, " not found. Available: ",
         paste(sort(avail_K), collapse = ", "))
  }
  K <- pin_K
} else {
  # Prefer the newest handoff that ALSO has Python artifacts (doc embeddings), so a
  # topic-only handoff at a new K (no Python compute yet) can't hijack the
  # embedding/word/sense sections. Fall back to newest overall.
  has_emb <- file.exists(file.path(emb_dir, sprintf("doc_emb_K%d.parquet", avail_K)))
  idx <- if (any(has_emb)) which(has_emb) else seq_along(avail_K)
  K <- avail_K[idx][which.max(file.mtime(input_candidates[idx]))]
}
cat("Using K =", K, "  (artifact K; available:", paste(sort(avail_K), collapse = ", "), ")\n")

# Optional: render ONLY the topic charts (§6/§6b/§6c/§6d) from a DIFFERENT joint-K
# than the embedding/word/sense artifacts (those are K-independent and only built
# at the artifact K above). Set once that handoff exists; NULL = use the artifact K.
topic_K <- NULL   # e.g. 20L to view a coarser topic model in §6–§6d

have <- function(path) {
  ok <- file.exists(path)
  if (!ok) cat("  [skip] missing artifact:", basename(path), "\n")
  ok
}
```

---

## 3. Load the joint-STM handoff

The comparison notebook's §27b saved the fitted joint model, the row-aligned
metadata (`meta`, with each document's `corpus`), the topic labels, and the
article text. We never re-derive the corpus or guess at row order.

```{r load-handoff}
adv_in <- readRDS(file.path(linked_path, sprintf("advanced_input_K%d.rds", K)))
model        <- adv_in$stm_model
meta         <- adv_in$meta
topic_labels_manual <- adv_in$topic_labels
modeled_raw  <- adv_in$modeled_raw

stopifnot(model$settings$dim$K == K,
          nrow(meta) == nrow(model$theta),
          length(modeled_raw) == nrow(meta))

vocab <- model$vocab
theta <- model$theta
top_words <- labelTopics(model, n = 3)$prob |> apply(1, paste, collapse = " ")

# The manual labels often already read "Topic 7: Genealogy"; strip any leading
# "Topic <n>:" so we don't end up with "T7: Topic 7: Genealogy" (double topic).
strip_topic_prefix <- function(x) {
  str_squish(str_remove(x, "^\\s*Topic\\s*\\d+\\s*[:.\\-]?\\s*"))
}
topic_labels <- if (!is.null(topic_labels_manual) &&
                    length(topic_labels_manual) == K) {
  paste0("T", seq_len(K), ": ", strip_topic_prefix(topic_labels_manual))
} else {
  paste0("T", seq_len(K), ": ", top_words)
}

docs <- readr::read_csv(file.path(linked_path, sprintf("advanced_docs_K%d.csv", K)),
                        show_col_types = FALSE)
stopifnot(nrow(docs) == nrow(theta))

# The publication tag is the spine of every contrast below.
if (!"corpus" %in% names(docs)) stop("advanced_docs has no 'corpus' column.")
docs$corpus <- as.character(docs$corpus)
corpus_levels <- sort(unique(docs$corpus[!is.na(docs$corpus)]))
pretty_map <- c(Womans_Exponent = "Woman's Exponent",
                Relief_Society_Magazine = "Relief Society Magazine")
pretty <- function(x) ifelse(x %in% names(pretty_map), pretty_map[x], x)
docs$corpus_pretty <- pretty(docs$corpus)

cat("K =", K, " | Documents =", nrow(theta), "\n")
cat("Corpora:", paste(sprintf("%s (%d)", pretty(corpus_levels),
                              tabulate(factor(docs$corpus, corpus_levels))),
                      collapse = "  |  "), "\n")
cat("Year range:", paste(range(docs$year, na.rm = TRUE), collapse = "-"), "\n")
```

---

## 4. Combined document atlas (coloured by publication)

Every article from both periodicals, embedded by `all-MiniLM-L6-v2` and laid out
with UMAP. Where the two colours interleave, the periodicals share vocabulary and
framing; where they separate, each occupies its own region of meaning-space.

```{r atlas}
emb_path <- file.path(emb_dir, sprintf("doc_emb_K%d.parquet", K))
if (have(emb_path)) {
  emb <- arrow::read_parquet(emb_path) |> arrange(row_index)
  dims <- grep("^dim_", names(emb), value = TRUE)
  E <- as.matrix(emb[, dims])
  E <- E / pmax(sqrt(rowSums(E^2)), 1e-9)

  # uwot's Annoy NN index is written to the R session temp dir; if that dir was
  # cleaned mid-session it fails with "Unable to open ... (2)" then an fsize-NA error.
  # Ensure the temp dir exists, and keep the index in-memory (n_threads = 1) to avoid
  # the disk-mmap path entirely.
  if (!dir.exists(tempdir())) dir.create(tempdir(), recursive = TRUE)
  set.seed(12345)
  um <- uwot::umap(E, n_neighbors = 15, min_dist = 0.1, metric = "cosine", n_threads = 1)
  atlas <- docs |>
    filter(row_index %in% emb$row_index) |>
    arrange(row_index) |>
    mutate(x = um[, 1], y = um[, 2])

  p_atlas <- ggplot(atlas, aes(x, y, colour = corpus_pretty)) +
    geom_point(alpha = 0.45, size = 0.9) +
    scale_colour_manual(values = c("Woman's Exponent" = "#1b9e77",
                                   "Relief Society Magazine" = "#d95f02"),
                        na.value = "grey70") +
    labs(title = "Document atlas — both periodicals in one embedding space  (each dot = one article)",
         subtitle = "Each point is one article, coloured by periodical; nearby points = semantically similar (all-MiniLM-L6-v2 + UMAP)",
         colour = "Publication", x = "UMAP 1", y = "UMAP 2") +
    theme_minimal() +
    guides(colour = guide_legend(override.aes = list(alpha = 1, size = 2)))

  ggsave(file.path(output_path, "01_atlas_by_publication.png"),
         p_atlas, width = 11, height = 8, dpi = 120)
  print(p_atlas)
  cat("Saved 01_atlas_by_publication.png\n")
} else {
  cat("Run: python scripts\\embed_documents.py", K, "\n")
}
```

---

## 5. Embedding-space geometry (centroid distance, overlap AUC, kNN mixing)

`contrast.py` Part A reduces the atlas to three numbers:

- **Centroid distance** `1 - cos(mean_WE, mean_RSM)` — how far apart the two
  corpora sit on average.
- **Overlap AUC** — a logistic classifier's cross-validated ability to tell the
  publications apart from a document's embedding. **0.5 = indistinguishable**
  (total overlap); **1.0 = perfectly separable** (no overlap).
- **kNN mixing** — for each article, the fraction of its nearest neighbours in the
  *other* corpus. ~0.5 = fully interleaved; ~0 = each corpus keeps to itself.

```{r geometry}
ov_path  <- file.path(contrast_dir, sprintf("embedding_overlap_K%d.csv", K))
knn_path <- file.path(contrast_dir, sprintf("knn_mixing_K%d.csv", K))
if (have(ov_path)) {
  ov <- readr::read_csv(ov_path, show_col_types = FALSE)
  cat("Centroid distance:", round(ov$centroid_dist, 4), "\n")
  cat("Overlap AUC:      ", round(ov$overlap_auc, 3),
      " (0.5 = identical, 1.0 = fully separable)\n")
  cat(sprintf("kNN mixing:        %s = %.2f | %s = %.2f  (share of neighbours in other corpus)\n",
              pretty(ov$corpus_a), ov$knn_mixing_a,
              pretty(ov$corpus_b), ov$knn_mixing_b))
  knitr::kable(ov |> mutate(corpus_a = pretty(corpus_a), corpus_b = pretty(corpus_b)),
               digits = 3)
}
# The per-article kNN histogram was hard to read; show the three Part-A numbers as
# a three-row panel, each on its own scale with plain-language endpoints. The rows
# read from different ends: high AUC, low centroid, low mixing all mean "separated".
if (exists("ov")) {
  knn_mean <- mean(c(ov$knn_mixing_a, ov$knn_mixing_b))
  gauge_df <- tibble(
    metric = factor(c("Overlap AUC  (classifier)",
                      "Centroid distance  (average meaning)",
                      "Neighbour mixing  (article-level)"),
                    levels = c("Overlap AUC  (classifier)",
                               "Centroid distance  (average meaning)",
                               "Neighbour mixing  (article-level)")),
    value     = c(ov$overlap_auc, ov$centroid_dist, knn_mean),
    lo        = c(0.5, 0, 0),
    hi        = c(1, 0.5, 0.5),
    left_lab  = c("can't tell apart", "same average meaning", "each keeps to its own"),
    right_lab = c("tells apart every time", "very different average", "fully mixed together"))

  p_sep <- ggplot(gauge_df, aes(value, 1)) +
    geom_segment(aes(x = lo, xend = value, yend = 1),
                 linewidth = 7, colour = "#7570b3", lineend = "round") +
    geom_point(size = 5, colour = "grey20") +
    geom_text(aes(x = lo, label = left_lab),  y = 1.75, hjust = 0, size = 3, colour = "grey35") +
    geom_text(aes(x = hi, label = right_lab), y = 1.75, hjust = 1, size = 3, colour = "grey35") +
    geom_text(aes(x = value, label = sprintf("%.2f", value)), y = 0.35, size = 3.3, colour = "grey20") +
    facet_wrap(~ metric, ncol = 1, scales = "free_x") +
    scale_y_continuous(limits = c(0, 2.2)) +
    labs(title = "How separable are the two periodicals in embedding space?",
         subtitle = sprintf("Three views of the atlas; neighbour mixing is the mean of %s %.0f%% / %s %.0f%%.",
                            pretty(ov$corpus_a), 100 * ov$knn_mixing_a,
                            pretty(ov$corpus_b), 100 * ov$knn_mixing_b),
         x = NULL, y = NULL) +
    theme_minimal() +
    theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(),
          panel.grid.major.y = element_blank(), panel.grid.minor = element_blank(),
          strip.text = element_text(face = "bold", hjust = 0))
  ggsave(file.path(output_path, "02_separability_gauge.png"), p_sep,
         width = 10, height = 5, dpi = 120)
  print(p_sep)
  cat("Saved 02_separability_gauge.png\n") } else {  cat("Run: python scripts\\contrast.py", K, "  (writes embedding_overlap)\n")
}
```

---

## 5b. Distinctive vocabulary — keyness ("fightin' words")

Which *words* most distinguish the two periodicals. We score every modelled term
with the **weighted log-odds-ratio with an informative Dirichlet prior** (Monroe,
Colaresi & Quinn 2008): the z-score grows with how lopsided a word's usage is
**and** how much evidence backs it, so rare-word noise is shrunk automatically.
Words with `|z| > 1.96` are reliably distinctive of one publication. This reads
far more directly than the neighbourhood-mixing histogram it replaces — it names
the vocabulary that separates the corpora. Pure R from the article text.

```{r keyness, fig.height=8}
if (length(corpus_levels) != 2) {
  cat("Keyness needs exactly two corpora; found:", paste(corpus_levels, collapse=", "), "\n")
} else {  A <- corpus_levels[1]; B <- corpus_levels[2]   # alphabetical; oriented by pretty()

  # Function-word stoplist (content nouns like "relief"/"suffrage" stay — they ARE
  # the contrast). The +1 prior and a min-count floor further tame OCR noise.
  stop_fn <- c("the","of","and","to","a","in","that","is","was","for","it","with",
    "as","his","on","be","at","by","this","had","not","are","but","from","or",
    "have","an","they","which","one","you","were","her","all","she","there",
    "would","we","him","been","has","when","who","will","more","no","if","out",
    "so","said","what","up","its","into","than","them","can","only","some",
    "could","two","may","then","do","any","my","now","such","like","our","over",
    "me","even","most","made","after","also","did","before","must","through",
    "back","where","much","your","way","well","down","should","because","each",
    "just","those","how","too","very","see","being","here","between","both",
    "under","never","same","another","know","while","last","might","us","off",
    "come","since","against","go","came","right","used","take","few","during",
    "without","again","place","around","however","say","part","once","every",
    "does","got","left","though","less","almost","far","took","yet","set","end",
    "why","find","look","later","point","next","ever","least","given","upon",
    "shall","unto","thee","thy","thou","let","per","their","ing","con")

  # Light lemmatiser: collapse morphological variants to one display root and
  # mark collapsed roots with "*" (woman*, sister*) so sister/sisters etc. don't
  # both occupy a slot. Mirrors `_norm()` in scripts/contrast.py.
  irregular <- c(women = "woman", men = "man", children = "child", wives = "wife",
                 lives = "life", leaves = "leaf", feet = "foot", teeth = "tooth",
                 people = "person", brethren = "brother")
  normalize_token <- function(w) {
    ir <- unname(irregular[w])
    dplyr::case_when(
      !is.na(ir)                                              ~ ir,
      str_length(w) > 4 & str_detect(w, "ies$")              ~ str_replace(w, "ies$", "y"),
      str_detect(w, "(ss|ch|sh|x|z|s)es$")                   ~ str_replace(w, "es$", ""),
      str_length(w) > 3 & str_detect(w, "s$") & !str_detect(w, "ss$") ~ str_replace(w, "s$", ""),
      TRUE                                                    ~ w)
  }

  # Tokenise once; keep the FULL list (toks_all) so §5e can score the function
  # words we drop here. Content keyness works on the non-stop subset.
  toks_all <- tibble(corpus = docs$corpus,
                     text   = str_to_lower(tidyr::replace_na(modeled_raw, ""))) |>
    mutate(w = str_extract_all(text, "[a-z]{3,}")) |>
    select(corpus, w) |>
    tidyr::unnest(w)
  toks <- toks_all |> filter(!w %in% stop_fn)

  # Restrict to STM vocab (drops OCR junk) BEFORE normalising, then fold variants.
  inv <- toks$w %in% vocab
  if (mean(inv) > 0.25) toks <- toks[inv, ]
  toks <- toks |> mutate(key = normalize_token(w))

  # Star a root when it aggregates >1 surface form (or is a plural-only form).
  disp_map <- toks |> distinct(key, w) |>
    group_by(key) |>
    summarise(label = paste0(key[1],
              ifelse(n_distinct(w) > 1 || !(key[1] %in% w), "*", "")), .groups = "drop")

  wide <- toks |>
    count(corpus, key, name = "n") |>
    pivot_wider(names_from = corpus, values_from = n, values_fill = 0) |>
    filter(.data[[A]] + .data[[B]] >= 10) |>
    left_join(disp_map, by = "key")

  yA <- wide[[A]]; yB <- wide[[B]]
  nA <- sum(yA); nB <- sum(yB); V <- nrow(wide)
  fA <- yA + 1; fB <- yB + 1
  log_odds <- log(fA / (nA + V - fA)) - log(fB / (nB + V - fB))
  key <- wide |>
    mutate(log_odds = log_odds, z = log_odds / sqrt(1 / fA + 1 / fB))

  top_key <- bind_rows(
    key |> slice_max(z, n = 20) |> mutate(side = pretty(A)),
    key |> slice_min(z, n = 20) |> mutate(side = pretty(B))
  ) |> mutate(label = fct_reorder(label, z))

  p_key <- ggplot(top_key, aes(z, label, fill = side)) +
    geom_col() +
    scale_fill_manual(values = c("Woman's Exponent" = "#1b9e77",
                                 "Relief Society Magazine" = "#d95f02")) +
    labs(title = "Most distinctive words by publication (weighted log-odds)",
         subtitle = "Monroe et al. (2008) z-scored log-odds with a Dirichlet prior; |z| > 1.96 = reliably distinctive",
         x = sprintf("← %s        z-score        %s →", pretty(B), pretty(A)),
         y = NULL, fill = "Distinctive of") +
    theme_minimal()
  ggsave(file.path(output_path, "07_keyness.png"), p_key,
         width = 11, height = 8, dpi = 120)
  print(p_key)
  cat("Saved 07_keyness.png\n")
}
```

---

## 5c. Vocabulary scatter (rate vs. rate)

The same counts as a scatter: each word's relative frequency in one periodical
against the other (log–log). Words on the dashed diagonal are used equally; words
far off it are characteristic of whichever periodical they lean toward. **Each
point is a single word** (not a topic). The most distinctive terms (coloured, by
the §5b z-score) and a few frequent balanced words (grey italic) are labelled, so
both the contrast and the shared diagonal are anchored.

```{r vocab-scatter, fig.height=8}
if (exists("key")) {
  total_A <- sum(key[[A]]); total_B <- sum(key[[B]])
  scat <- key |>
    mutate(rate_A = (.data[[A]] + 0.5) / total_A,
           rate_B = (.data[[B]] + 0.5) / total_B,
           total  = .data[[A]] + .data[[B]],
           lean   = log2(rate_A / rate_B))
  lab <- bind_rows(slice_max(key, z, n = 18), slice_min(key, z, n = 18)) |>
    distinct(label) |>
    left_join(scat, by = "label")
  # a few frequent, balanced words to anchor the "used equally" diagonal
  lab_shared <- scat |> filter(abs(lean) < 0.15) |> slice_max(total, n = 6)

  p_scat <- ggplot(scat, aes(rate_A, rate_B)) +
    geom_point(aes(colour = z), alpha = 0.4, size = 0.9) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed", colour = "grey55") +
    ggrepel::geom_text_repel(data = lab, aes(label = label, colour = z),
                             size = 3, max.overlaps = 30, show.legend = FALSE) +
    ggrepel::geom_text_repel(data = lab_shared, aes(label = label),
                             colour = "grey25", fontface = "italic",
                             size = 3, max.overlaps = 30) +
    scale_x_log10(labels = scales::label_number()) +
    scale_y_log10(labels = scales::label_number()) +
    scale_colour_gradient2(low = "#1b9e77", mid = "grey75", high = "#d95f02",
                           midpoint = 0,
                           name = sprintf("z  (+ = %s,\n− = %s)", pretty(A), pretty(B))) +
    labs(title = "Which words each periodical uses more  (each dot = one word)",
         subtitle = "Each point is a word; on the dashed line = used at the same rate in both, off-diagonal = favoured by one periodical (grey italic = balanced anchors)",
         x = sprintf("How often %s uses the word  (per-word rate, log scale)", pretty(A)),
         y = sprintf("How often %s uses the word  (per-word rate, log scale)", pretty(B))) +
    theme_minimal()
  ggsave(file.path(output_path, "08_vocab_scatter.png"), p_scat,
         width = 10, height = 8, dpi = 120)
  print(p_scat)
  cat("Saved 08_vocab_scatter.png\n") } else {  cat("Keyness table not built (see §5b) — scatter skipped.\n")
}
```

---

## 5d. Shared register & the frequency–specificity map

§5b finds what *separates* the periodicals; this finds what they **share** — and,
more importantly, gives a principled way to spot "words like woman/man" without a
hand list. Every content word has two coordinates: **frequency** (how common) and
**specificity** — how lopsidedly it splits between the corpora, as a `|log2
rate-ratio|` (an **effect size**; we deliberately avoid the §5b z-score, which at
37k documents is inflated by sample size and flags almost everything). The
high-frequency, low-specificity corner is the **shared register** — the common
ground both periodicals lean on (the "floater" class at corpus scale). Words are
never *excluded* for being frequent; the only removal is the function-word
stoplist (the, of, and…), and the table below shows the frequent **content** words
are all retained and measured. Pure R from the §5b keyness table.

```{r shared-register, fig.height=8}
if (exists("key")) {
  reg <- key |>
    mutate(total  = .data[[A]] + .data[[B]],
           rate_A = (.data[[A]] + 0.5) / sum(.data[[A]]),
           rate_B = (.data[[B]] + 0.5) / sum(.data[[B]]),
           lean   = log2(rate_A / rate_B),     # + leans A, − leans B
           specificity = abs(lean))            # |log2 fold-change| — sample-size-free

  # focus the map on reasonably common words (drop the long rare tail)
  reg_map <- reg |> filter(total >= quantile(total, 0.5))
  # label the frequent, balanced words (the shared register / floater class)
  lab_reg <- reg_map |> slice_max(total, n = 60) |> slice_min(specificity, n = 20)

  p_reg <- ggplot(reg_map, aes(total, specificity)) +
    geom_point(aes(colour = lean), alpha = 0.4, size = 0.8) +
    geom_hline(yintercept = log2(1.5), linetype = "dotted", colour = "grey55") +
    ggrepel::geom_text_repel(data = lab_reg, aes(label = label), size = 3, max.overlaps = 25) +
    scale_x_log10(labels = label_number()) +
    scale_colour_gradient2(low = "#1b9e77", mid = "grey70", high = "#d95f02", midpoint = 0,
                           name = sprintf("leans\n(+%s / −%s)", pretty(A), pretty(B))) +
    labs(title = "Frequency × specificity map",
         subtitle = "Low on y = shared register (similar rates in both); above the dotted line (>1.5×) = leans to one periodical",
         x = "Total occurrences (log scale)", y = "Specificity  |log2 rate ratio|") +
    theme_minimal()
  ggsave(file.path(output_path, "12_shared_register.png"), p_reg,
         width = 11, height = 8, dpi = 120)
  print(p_reg)

  cat("\nMost frequent words used at SIMILAR rates in both — the shared register",
      "(the woman/man 'floater' class at corpus scale). Nothing is excluded for",
      "being frequent; only function words are stoplisted, by design:\n")
  knitr::kable(reg_map |> slice_max(total, n = 60) |> slice_min(specificity, n = 18) |>
                 arrange(desc(total)) |>
                 transmute(Word = label, Total = total,
                           `|log2 ratio|` = round(specificity, 2),
                           `Slightly leans` = ifelse(lean > 0, pretty(A), pretty(B))))
  cat("Saved 12_shared_register.png\n")
} else {
  cat("Keyness table not built (see §5b) — shared register skipped.\n")
}
```

---

## 5e. Register & era contrast (function words)

§5b drops function words to isolate *content*; this section does the opposite, on
purpose — but only for the **register-bearing** ones: personal/possessive
**pronouns**, **modals**, **stance & discourse connectives**, and
**archaic/devotional forms**. Their differential use is a **style-and-era
fingerprint**: the Exponent leans formal, collective, impersonal (`upon`, `our`,
`their`, `those`, `unto`), the Magazine personal and conversational (`you`,
`your`, `she`, `him`, `because`) — 19th-century periodical prose vs a later, more
intimate magazine voice. **Pure glue** (`the`, `and`, `of`, `to`, `for`…) is
*excluded* here: a tiny rate gap on an ultra-common word is noise, not voice. This
is the stylistic mirror of §5b — words that separate the periodicals by *voice*
rather than *subject*.

```{r register-era, fig.height=8}
if (exists("toks_all") && length(corpus_levels) == 2) {
  A <- corpus_levels[1]; B <- corpus_levels[2]

  # Register-bearing function words only — pronouns, modals, stance/discourse
  # connectives, archaic/devotional forms. Pure glue (the/and/of/to/for…) excluded:
  # a tiny rate gap on an ultra-common word is noise, not voice.
  register_words <- c(
    # personal & possessive pronouns (2-letter forms aren't tokenised by [a-z]{3,})
    "you","your","yours","our","ours","her","hers","his","him","she","they",
    "them","their","theirs","its","mine","myself","ourselves","yourself",
    "himself","herself","themselves",
    # demonstratives
    "this","that","these","those","such",
    # modals / auxiliaries
    "shall","should","will","would","can","could","may","might","must","ought","cannot",
    # stance & discourse connectives
    "because","though","although","yet","however","indeed","therefore","thus",
    "hence","whereas","while","whilst","nevertheless","moreover","perhaps",
    "surely","truly","verily","otherwise","besides","meanwhile","else",
    # negation / stance adverbs
    "not","never","very","rather","quite","merely","almost",
    # archaic / formal / devotional register
    "thee","thou","thy","thine","unto","upon","hath","doth","shalt","wert",
    "amongst","betwixt","hither","thither","whence","thence",
    "henceforth","herein","hereby","thereof","therein","wherein","whereof")

  fw <- toks_all |>
    filter(w %in% register_words) |>
    count(corpus, w, name = "n") |>
    pivot_wider(names_from = corpus, values_from = n, values_fill = 0) |>
    filter(.data[[A]] + .data[[B]] >= 20)

  yA <- fw[[A]]; yB <- fw[[B]]
  nA <- sum(yA); nB <- sum(yB); V <- nrow(fw)
  fA <- yA + 1; fB <- yB + 1
  fw <- fw |>
    mutate(log_odds = log(fA / (nA + V - fA)) - log(fB / (nB + V - fB)),
           z = log_odds / sqrt(1 / fA + 1 / fB))

  top_fw <- bind_rows(slice_max(fw, z, n = 16), slice_min(fw, z, n = 16)) |>
    distinct(w, .keep_all = TRUE) |>
    mutate(side = ifelse(z > 0, pretty(A), pretty(B)),
           w = fct_reorder(w, z))

  p_fw <- ggplot(top_fw, aes(z, w, fill = side)) +
    geom_col() +
    scale_fill_manual(values = c("Woman's Exponent" = "#1b9e77",
                                 "Relief Society Magazine" = "#d95f02")) +
    labs(title = "Register & era contrast — voice words",
         subtitle = "Register-bearing function words (pronouns, modals, stance & archaic forms) by keyness; voice/era, not topic",
         x = sprintf("← %s        z-score        %s →", pretty(B), pretty(A)),
         y = NULL, fill = "Favoured by") +
    theme_minimal()
  ggsave(file.path(output_path, "13_register_era_contrast.png"), p_fw,
         width = 11, height = 8, dpi = 120)
  print(p_fw)
  cat("Saved 13_register_era_contrast.png\n")
} else {
  cat("Token list not built (see §5b) — register/era contrast skipped.\n")
}
```

---

## 5f. Optional: topic charts at a different K

The four topic charts below (§6–§6d) are the **only** sections that depend on the
joint-STM K — the atlas, separability, keyness, scatter, register, sense-mix, and
drift are all K-independent. So if you've fit the joint model at a second K (e.g.
`chosen_K <- 20L` in the linker, which writes `advanced_input_K20.rds` **alongside**
the K35 files), set `topic_K <- 20L` in §2 to render §6–§6d from that coarser model
**without re-running any Python** — the embedding/word sections keep using the
artifact-K compute. This chunk swaps the topic model in; §6e swaps it back out.

```{r topic-k-override}
topic_override_active <- FALSE
if (!is.null(topic_K) && topic_K != K) {
  tk_path <- file.path(linked_path, sprintf("advanced_input_K%d.rds", topic_K))
  if (file.exists(tk_path)) {
    .art <- list(K = K, theta = theta, topic_labels = topic_labels,
                 docs = docs, modeled_raw = modeled_raw)   # stash artifact-K objects
    ti  <- readRDS(tk_path)
    mdl <- ti$stm_model
    dt  <- readr::read_csv(file.path(linked_path, sprintf("advanced_docs_K%d.csv", topic_K)),
                           show_col_types = FALSE)
    dt$corpus <- as.character(dt$corpus)
    dt$corpus_pretty <- pretty(dt$corpus)
    stopifnot(nrow(dt) == nrow(mdl$theta), length(ti$modeled_raw) == nrow(mdl$theta))
    tw  <- labelTopics(mdl, n = 3)$prob |> apply(1, paste, collapse = " ")
    tlm <- ti$topic_labels
    # Override the names the topic chunks use; §6e restores them afterwards.
    K            <- topic_K
    theta        <- mdl$theta
    topic_labels <- if (!is.null(tlm) && length(tlm) == topic_K)
                      paste0("T", seq_len(topic_K), ": ", strip_topic_prefix(tlm)) else
                      paste0("T", seq_len(topic_K), ": ", tw)
    docs         <- dt
    modeled_raw  <- ti$modeled_raw
    topic_override_active <- TRUE
    cat(sprintf("Topic charts (§6–§6d) use joint K = %d; embedding/word/sense sections stay at artifact K = %d.\n",
                topic_K, .art$K))
  } else {
    cat(sprintf("topic_K = %d requested but %s not found — topic charts use K = %d.\n",
                topic_K, basename(tk_path), K))
  }
}
```

---

## 6. Topic prevalence by publication

Which joint-STM topics each periodical leans on. Pure R from `theta` and the
`corpus` tag — always available once the handoff loads.

```{r topic-prevalence, fig.height=9}
theta_df <- as_tibble(theta)
names(theta_df) <- paste0("Topic", seq_len(K))
theta_df$corpus <- docs$corpus

prev <- theta_df |>
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "p") |>
  mutate(topic_num = as.integer(str_remove(topic, "Topic"))) |>
  group_by(corpus, topic_num) |>
  summarise(mean_p = mean(p), .groups = "drop") |>
  mutate(corpus_pretty = pretty(corpus),
         label = topic_labels[topic_num])

# order topics by the WE-RSM difference for readability
diff_order <- prev |>
  select(topic_num, corpus_pretty, mean_p) |>
  pivot_wider(names_from = corpus_pretty, values_from = mean_p)
diff_col <- setdiff(names(diff_order), "topic_num")
if (length(diff_col) == 2) {
  diff_order <- diff_order |>
    mutate(d = .data[[diff_col[1]]] - .data[[diff_col[2]]]) |>
    arrange(d)
  prev$label <- factor(prev$label, levels = topic_labels[diff_order$topic_num])
}

p_prev <- ggplot(prev, aes(mean_p, label, colour = corpus_pretty)) +
  geom_line(aes(group = label), colour = "grey75") +
  geom_point(size = 2.4) +
  scale_x_continuous(labels = percent) +
  scale_colour_manual(values = c("Woman's Exponent" = "#1b9e77",
                                 "Relief Society Magazine" = "#d95f02")) +
  labs(title = "Topic prevalence by publication",
       subtitle = "Mean document-topic proportion; line links the two periodicals per topic",
       x = "Mean prevalence", y = NULL, colour = "Publication") +
  theme_minimal()
ggsave(file.path(output_path, "03_topic_prevalence_by_publication.png"),
       p_prev, width = 11, height = 10, dpi = 120)
print(p_prev)
cat("Saved 03_topic_prevalence_by_publication.png\n")
```

---

## 6b. Author topic profiles by publication (faceted "Chart 5")

For each periodical's most prolific **named** authors (>= 10 substantial
articles), the mean joint-STM topic mix of their articles. Because both corpora
share the **same** joint topic space, the stacked bars use one common legend, so
the two facets are directly comparable — *what each author writes about, and how
the typical Exponent author's mix differs from the typical Magazine author's.*
This is the cross-corpus, faceted counterpart to the per-corpus author profiles
in each single-corpus report (RSM §12). Pure R from `theta`, `docs$author`, and
the `corpus` tag — available as soon as the joint handoff loads.

```{r author-profiles-compare, fig.height=11}
# Author column may be lower- or upper-case depending on the handoff writer.
.author <- if ("author" %in% names(docs)) docs$author else if ("Author" %in% names(docs)) docs$Author else NA_character_

# Exclude non-author bylines (same rule as the single-corpus reports).
author_blocklist <- c("unknown", "editor", "the editor", "selected", "anonymous")
org_keywords <- paste0("exponent|magazine|publisher|office|ticket|company|\\bco\\b|",
                       "union|depot|emporium|store|bureau|society|association|department|board")
is_real_author <- function(a) {
  s  <- str_squish(a)
  al <- str_replace_all(str_to_lower(s), "[’‘']", "'")
  has_surname <- str_detect(s, "[A-Za-z]{3,}")
  !is.na(a) & s != "" & !str_starts(s, "\\[") & !str_ends(s, ",") &
    !(al %in% author_blocklist) & !str_detect(al, org_keywords) & has_surname
}

if (all(is.na(.author))) {
  cat("No author column in the joint handoff — re-run the joint linker so",
      "advanced_docs carries 'author', then this chart fills in.\n")
} else {
  # pos = the theta row index (docs is row-aligned to theta positionally, as in §6).
  prof_tbl <- docs |>
    mutate(pos = row_number(),
           text = modeled_raw,
           n_words = str_count(text, "\\S+"),
           author_clean = str_squish(.author)) |>
    filter(is_real_author(author_clean), n_words >= 150)

  # Most prolific named authors PER publication (top 8 each, for legible facets).
  top_by_corpus <- prof_tbl |>
    count(corpus_pretty, author_clean, name = "n_articles") |>
    filter(n_articles >= 10) |>
    group_by(corpus_pretty) |>
    slice_max(n_articles, n = 8, with_ties = FALSE) |>
    ungroup()

  if (nrow(top_by_corpus) == 0) {
    cat("No author with >= 10 substantial articles in either corpus after filtering.\n")
  } else {
    prof <- purrr::pmap_dfr(top_by_corpus, function(corpus_pretty, author_clean, n_articles) {
      rows <- prof_tbl$pos[prof_tbl$author_clean == author_clean &
                           prof_tbl$corpus_pretty == corpus_pretty]
      tibble(corpus_pretty = corpus_pretty, author = author_clean,
             n_articles = n_articles,
             topic = factor(topic_labels, levels = topic_labels),
             prop  = colMeans(theta[rows, , drop = FALSE]))
    })

    # Order authors within each facet by article count (free_y shows each its own).
    lev <- prof |> distinct(corpus_pretty, author, n_articles) |>
      arrange(corpus_pretty, n_articles) |> distinct(author, .keep_all = TRUE) |>
      pull(author)
    prof$author <- factor(prof$author, levels = lev)

    p_authcmp <- ggplot(prof, aes(prop, author, fill = topic)) +
      geom_col(width = 0.85) +
      facet_wrap(~ corpus_pretty, scales = "free_y", ncol = 1) +
      scale_x_continuous(labels = percent, expand = expansion(mult = c(0, 0.02))) +
      scale_fill_viridis_d(option = "turbo") +
      labs(title = "Author topic profiles by publication",
           subtitle = paste0("Mean joint-STM topic mix per prolific named author ",
                             "(>= 10 articles); shared topic space, one legend"),
           x = "Mean topic proportion", y = NULL, fill = "Joint topic") +
      theme_minimal(base_size = 11) +
      theme(plot.title = element_text(face = "bold"),
            strip.text = element_text(face = "bold"),
            legend.text = element_text(size = 7),
            legend.key.size = unit(0.4, "cm"))
    ggsave(file.path(output_path, "03b_author_topic_profiles_by_publication.png"),
           p_authcmp, width = 13, height = 11, dpi = 120)
    print(p_authcmp)

    # Each author's single dominant joint topic.
    prof |> group_by(corpus_pretty, author, n_articles) |>
      slice_max(prop, n = 1, with_ties = FALSE) |> ungroup() |>
      transmute(Publication = corpus_pretty, Author = author, Articles = n_articles,
                `Top joint topic` = as.character(topic),
                Share = percent(prop, 0.1)) |>
      arrange(Publication, desc(Articles)) |> print(n = Inf)
    cat("Saved 03b_author_topic_profiles_by_publication.png\n")
  }
}
```

---

## 6c. Topic emphasis — difference with confidence intervals

The §6 dumbbell shows *where* each periodical sits but carries no uncertainty. Here
we test it: for every joint topic, the difference in **mean document-topic
proportion** between the two publications, with a 95% CI (Welch test over the
per-article proportions) and a Benjamini-Hochberg significance flag. Now you can
say which gaps are *real*, not just rank them. Pure R from `theta` + `corpus`.

```{r topic-diff-ci, fig.height=9}
if (length(corpus_levels) != 2) {
  cat("Topic-difference test needs exactly two corpora.\n")
} else {
  A <- corpus_levels[1]; B <- corpus_levels[2]
  iA <- which(docs$corpus == A); iB <- which(docs$corpus == B)

  diffs <- purrr::map_dfr(seq_len(K), function(k) {
    tt <- t.test(theta[iA, k], theta[iB, k])
    tibble(topic_num = k,
           diff = unname(tt$estimate[1] - tt$estimate[2]),  # mean_A − mean_B
           lo = tt$conf.int[1], hi = tt$conf.int[2], p = tt$p.value)
  }) |>
    mutate(p_adj  = p.adjust(p, "BH"),
           sig    = p_adj < 0.05,
           higher = ifelse(diff > 0, pretty(A), pretty(B)),
           label  = topic_labels[topic_num]) |>
    arrange(diff) |>
    mutate(label = factor(label, levels = label))

  p_diff <- ggplot(diffs, aes(diff, label, colour = higher)) +
    geom_vline(xintercept = 0, colour = "grey50") +
    geom_errorbarh(aes(xmin = lo, xmax = hi), height = 0, linewidth = 0.6, alpha = 0.8) +
    geom_point(aes(alpha = sig), size = 2.6) +
    scale_alpha_manual(values = c(`TRUE` = 1, `FALSE` = 0.3), guide = "none") +
    scale_colour_manual(values = c("Woman's Exponent" = "#1b9e77",
                                   "Relief Society Magazine" = "#d95f02")) +
    scale_x_continuous(labels = percent) +
    labs(title = "Which topics each periodical emphasises",
         subtitle = sprintf("Difference in mean prevalence (%s − %s) with 95%% CIs; faded = not significant (BH-adjusted)",
                            pretty(A), pretty(B)),
         x = sprintf("Mean prevalence difference  (%s − %s)", pretty(A), pretty(B)),
         y = NULL, colour = "Higher in") +
    theme_minimal()
  ggsave(file.path(output_path, "09_topic_diff_ci.png"), p_diff,
         width = 11, height = 10, dpi = 120)
  print(p_diff)
  cat("Saved 09_topic_diff_ci.png\n")
}
```

---

## 6d. Topic co-occurrence contrast

Prevalence asks *how much* each topic appears; this asks how topics **travel
together** — and whether that structure differs by periodical. Within each corpus
we correlate the topic proportions across articles, then surface the topic *pairs*
whose co-occurrence differs most between the two. A pair that bonds in one
periodical but not the other signals a different editorial logic (e.g. "Genealogy"
riding with "Relief Society organisation" in one but not the other). Pure R.

```{r topic-cooc, fig.height=8}
if (length(corpus_levels) != 2) {
  cat("Co-occurrence contrast needs exactly two corpora.\n")
} else {
  A <- corpus_levels[1]; B <- corpus_levels[2]
  cA <- cor(theta[docs$corpus == A, , drop = FALSE])
  cB <- cor(theta[docs$corpus == B, , drop = FALSE])
  ut <- upper.tri(cA)
  pr <- which(ut, arr.ind = TRUE)
  cooc <- tibble(i = pr[, 1], j = pr[, 2],
                 cor_A = cA[ut], cor_B = cB[ut]) |>
    mutate(d = cor_A - cor_B,
           pair = paste(topic_labels[i], "×", topic_labels[j])) |>
    filter(!is.na(d)) |>
    slice_max(abs(d), n = 18) |>
    mutate(pair = fct_reorder(pair, d))

  cooc_long <- cooc |>
    select(pair, cor_A, cor_B) |>
    pivot_longer(c(cor_A, cor_B), names_to = "which", values_to = "cor") |>
    mutate(corpus_pretty = ifelse(which == "cor_A", pretty(A), pretty(B)))

  p_cooc <- ggplot(cooc_long, aes(cor, pair)) +
    geom_line(aes(group = pair), colour = "grey75") +
    geom_point(aes(colour = corpus_pretty), size = 2.6) +
    geom_vline(xintercept = 0, linetype = "dotted", colour = "grey55") +
    scale_colour_manual(values = c("Woman's Exponent" = "#1b9e77",
                                   "Relief Society Magazine" = "#d95f02")) +
    labs(title = "Topic pairs that co-occur differently across the periodicals",
         subtitle = "Within-corpus correlation of topic proportions; the 18 pairs with the largest gap",
         x = "Correlation between the two topics' prevalence", y = NULL,
         colour = "Publication") +
    theme_minimal() +
    theme(axis.text.y = element_text(size = 8))
  ggsave(file.path(output_path, "10_topic_cooccurrence.png"), p_cooc,
         width = 12, height = 8, dpi = 120)
  print(p_cooc)
  cat("Saved 10_topic_cooccurrence.png\n")
}
```

---

## 6e. Restore the artifact-K model

Swaps the artifact-K objects back in (no-op unless §5f overrode them), so the
embedding/word/sense sections below use the K whose Python compute exists.

```{r topic-k-restore}
if (exists("topic_override_active") && isTRUE(topic_override_active)) {
  K            <- .art$K
  theta        <- .art$theta
  topic_labels <- .art$topic_labels
  docs         <- .art$docs
  modeled_raw  <- .art$modeled_raw
  cat(sprintf("Restored artifact K = %d for the embedding/word/sense sections.\n", K))
}
```

---

## 7. Contrastive semantic change of shared terms

For each shared target word, `contrast.py` Part B embeds every occurrence in
context with MacBERTh, separately in each periodical, and compares them:

- **PRT** — distance between the two corpora's prototype (mean) vectors: coarse
  framing drift.
- **APD** — average cross-corpus pairwise distance: spread-sensitive.
- **JSD** — Jensen-Shannon divergence between the two corpora's *sense mixes*
  (induced by clustering all occurrences): does the **mix of senses** differ?

Bigger = the word is used more differently across the two periodicals.

```{r term-contrast}
tc_path <- file.path(contrast_dir, sprintf("term_contrast_K%d.csv", K))
if (have(tc_path)) {
  tc <- readr::read_csv(tc_path, show_col_types = FALSE)
  if (nrow(tc)) {
    tc_long <- tc |>
      select(word, PRT = prt, APD = apd, JSD = jsd) |>
      pivot_longer(c(PRT, APD, JSD), names_to = "measure", values_to = "value") |>
      group_by(measure) |>
      mutate(word = fct_reorder(word, value)) |>
      ungroup()

    p_tc <- ggplot(tc_long, aes(value, word, fill = measure)) +
      geom_col(show.legend = FALSE) +
      facet_wrap(~ measure, scales = "free_x") +
      labs(title = "Contrastive semantic change of shared terms (WE vs. RSM)",
           subtitle = "Higher = the word is framed more differently across the two periodicals",
           x = "Divergence", y = NULL) +
      theme_minimal()
    ggsave(file.path(output_path, "04_term_contrast.png"), p_tc,
           width = 12, height = 7, dpi = 120)
    print(p_tc)

    cat("\nMost divergently-used shared terms (by JSD):\n")
    knitr::kable(tc |> arrange(desc(jsd)) |>
                   transmute(word, PRT = round(prt, 3), APD = round(apd, 3),
                             JSD = round(jsd, 3), n_WE = n_a, n_RSM = n_b) |>
                   head(15))
    cat("Saved 04_term_contrast.png\n")
  } else {
    cat("term_contrast is empty — no shared term had >=5 usable occurrences in both corpora.\n")
  }
} else {
  cat("Run: python scripts\\contrast.py", K, "\n")
}
```

---

## 7b. Sense mix of shared terms (the payoff figure)

§7 reports *how much* a shared word's usage differs as three numbers (PRT/APD/JSD).
This shows *what* differs. For each shared term, `contrast.py` clusters all its
in-context MacBERTh occurrences into **senses** and records how each periodical's
uses split across them. So instead of "JSD = 0.4", you see directly that — say —
"relief" is mostly charitable-aid in one periodical and mostly organisational in
the other. Each sense is glossed by the words that **most distinguish** it from
the term's other senses (a within-word log-odds, not raw frequency), so the labels
actually differ; the term's **overall dominant words** (the high-frequency
"floaters" like `woman*`, `man*`) are shown alongside for context. Morphological
variants are collapsed and marked with `*` (e.g. `sister*` = sister/sisters).
Crucially, frequency is **not** a filter: a floater like `woman*` is admitted to a
sense's gloss (marked `^`) wherever its **lift** — observed-vs-expected
concentration — clears ~1.3, and a separate table reports each floater's per-sense
lift, so you can see whether `woman*`/`man*` are genuinely sense-bearing or just
background. We show the terms whose sense mix differs most between the corpora.
*(Reads `contrast.py` `term_sense_mix` + `term_floater_lift` — re-run
`contrast.py {K}` after this update.)*

```{r sense-mix, fig.height=9}
sm_path <- file.path(contrast_dir, sprintf("term_sense_mix_K%d.csv", K))
if (have(sm_path)) {
  sm <- readr::read_csv(sm_path, show_col_types = FALSE)
  if (nrow(sm) && length(unique(sm$corpus)) == 2) {
    A <- corpus_levels[1]; B <- corpus_levels[2]

    # rank terms by total-variation distance between the two corpora's sense mixes
    div <- sm |>
      select(word, corpus, sense, proportion) |>
      pivot_wider(names_from = corpus, values_from = proportion, values_fill = 0) |>
      group_by(word) |>
      summarise(tv = 0.5 * sum(abs(.data[[A]] - .data[[B]])), .groups = "drop") |>
      arrange(desc(tv))
    keepw <- head(div$word, 9)

    # per-word "floater" words (same for every row of a word); guard if older
    # CSV lacks the column (pre-distinctiveness re-run).
    if (!"term_dominant" %in% names(sm)) sm$term_dominant <- ""
    dom <- sm |> filter(word %in% keepw) |> distinct(word, term_dominant)
    dom_lvl <- dom$term_dominant[match(keepw, dom$word)]

    smk <- sm |>
      filter(word %in% keepw) |>
      mutate(corpus_pretty = pretty(corpus),
             sense_f  = factor(sense),
             word_lab = factor(paste0(word, "  ·  overall: ", term_dominant),
                               levels = paste0(keepw, "  ·  overall: ", dom_lvl)))

    # per-word sense glosses for the reader (sense ids are word-specific)
    gloss <- sm |>
      filter(word %in% keepw) |>
      distinct(word, sense, sense_label) |>
      arrange(factor(word, levels = keepw), sense)

    p_sense <- ggplot(smk, aes(proportion, corpus_pretty, fill = sense_f)) +
      geom_col(width = 0.7) +
      facet_wrap(~ word_lab, ncol = 3) +
      scale_x_continuous(labels = percent, expand = expansion(mult = c(0, 0.02))) +
      scale_fill_viridis_d(option = "turbo", name = "Induced sense (per word)") +
      labs(title = "Sense mix of shared terms by publication",
           subtitle = "Bars split by induced sense (compare the two rows); strip shows the term's overall dominant words",
           x = "Share of occurrences", y = NULL) +
      theme_minimal() +
      theme(legend.position = "bottom", strip.text = element_text(face = "bold", size = 8))
    ggsave(file.path(output_path, "11_sense_mix.png"), p_sense,
           width = 12, height = 9, dpi = 120)
    print(p_sense)

    cat("\nTerm-level dominant ('floater') words:\n")
    knitr::kable(dom |> transmute(Word = word, `Dominant words` = term_dominant))
    cat("\nDistinctive words per induced sense (peaks vs the term's other senses;",
        "'^' marks a high-frequency floater that is concentrated in that sense):\n")
    knitr::kable(gloss |> transmute(Word = word, Sense = sense,
                                    `Distinctive words` = sense_label))

    # Floater distinctiveness: each big word's per-sense lift (observed/expected).
    # This is how woman*/man* are "let through but measured" — peak lift > ~1.2
    # means the floater leans to a sense; ~1 means it is genuine background.
    fl_path <- file.path(contrast_dir, sprintf("term_floater_lift_K%d.csv", K))
    if (have(fl_path)) {
      fl <- readr::read_csv(fl_path, show_col_types = FALSE) |> filter(word %in% keepw)
      # Specificity = 1 − normalised entropy of the floater's distribution across
      # senses. 0 = perfectly even (genuine background); →1 = concentrated. This
      # generalises the lift bar: woman*/man* are kept AND measured, not excluded.
      fl_summ <- fl |>
        group_by(word, floater) |>
        summarise(peak_sense = sense[which.max(lift)],
                  peak_lift   = max(lift),
                  ent = { p <- n_in_sense / sum(n_in_sense); p <- p[p > 0]; -sum(p * log(p)) },
                  ksenses = n(), .groups = "drop") |>
        mutate(specificity = round(1 - ent / log(pmax(ksenses, 2)), 2),
               reading = ifelse(peak_lift >= 1.2 | specificity >= 0.15,
                                "sense-bearing", "background (≈uniform)")) |>
        arrange(factor(word, levels = keepw), desc(specificity))
      cat("\nFloater distinctiveness — every dominant word kept and MEASURED",
          "(specificity 0 = background, →1 = concentrated; peak lift = its strongest sense):\n")
      knitr::kable(fl_summ |> transmute(Word = word, Floater = floater,
                                        Specificity = specificity,
                                        `Peak sense` = peak_sense,
                                        `Peak lift` = round(peak_lift, 2),
                                        Reading = reading))
    }
    cat("Saved 11_sense_mix.png\n")
  } else {
    cat("term_sense_mix is empty or lacks two corpora — no sense-mix figure.\n")
  }
} else {
  cat("Run: python scripts\\contrast.py", K, "  (now also writes term_sense_mix)\n")
}
```

---

## 8. Framing-drift map (WE → RSM per term)

Each shared term has one MacBERTh prototype vector per periodical. Projecting all
prototypes to 2D (PCA) and drawing an arrow from each word's WE prototype to its
RSM prototype shows *direction* and *magnitude* of framing drift at a glance.

```{r drift-map}
proto_path <- file.path(contrast_dir, sprintf("term_prototypes_K%d.parquet", K))
if (have(proto_path)) {
  pr <- arrow::read_parquet(proto_path)
  pdims <- grep("^dim_", names(pr), value = TRUE)
  if (nrow(pr) >= 4 && length(unique(pr$corpus)) == 2) {
    M <- as.matrix(pr[, pdims])
    pc <- prcomp(M, center = TRUE, scale. = FALSE)$x[, 1:2]
    pr2 <- pr |> mutate(PC1 = pc[, 1], PC2 = pc[, 2], corpus_pretty = pretty(corpus))

    wide <- pr2 |>
      select(word, corpus, PC1, PC2) |>
      pivot_wider(names_from = corpus, values_from = c(PC1, PC2))
    cl <- corpus_levels
    p_drift <- ggplot(pr2, aes(PC1, PC2)) +
      geom_segment(data = wide,
                   aes(x = .data[[paste0("PC1_", cl[1])]],
                       y = .data[[paste0("PC2_", cl[1])]],
                       xend = .data[[paste0("PC1_", cl[2])]],
                       yend = .data[[paste0("PC2_", cl[2])]]),
                   arrow = arrow(length = unit(0.18, "cm")),
                   colour = "grey55") +
      geom_point(aes(colour = corpus_pretty), size = 2.6) +
      ggrepel::geom_text_repel(data = pr2 |> filter(corpus == cl[2]),
                               aes(label = word), size = 3, max.overlaps = 20) +
      scale_colour_manual(values = c("Woman's Exponent" = "#1b9e77",
                                     "Relief Society Magazine" = "#d95f02")) +
      labs(title = "Framing-drift map for shared terms",
           subtitle = sprintf("MacBERTh prototypes, PCA to 2D; arrow runs %s → %s",
                              pretty(cl[1]), pretty(cl[2])),
           colour = "Publication", x = "PC1", y = "PC2") +
      theme_minimal()
    ggsave(file.path(output_path, "05_framing_drift_map.png"), p_drift,
           width = 11, height = 8, dpi = 120)
    print(p_drift)
    cat("Saved 05_framing_drift_map.png\n")
  } else {
    cat("Not enough prototypes for a drift map.\n")
  }
} else {
  cat("Run: python scripts\\contrast.py", K, "\n")
}
```

---

## 9. BERTopic over both corpora (cross-tabbed by publication)

A neural topic model clustered on the same embeddings, then cross-tabulated
against publication — which neural themes are WE-dominant, RSM-dominant, or shared.

```{r bertopic}
bt_docs_path <- file.path(bertopic_dir, sprintf("bertopic_docs_K%d.csv", K))
bt_top_path  <- file.path(bertopic_dir, sprintf("bertopic_topics_K%d.csv", K))
if (have(bt_docs_path) && have(bt_top_path)) {
  bt_docs <- readr::read_csv(bt_docs_path, show_col_types = FALSE)
  bt_top  <- readr::read_csv(bt_top_path,  show_col_types = FALSE)
  bt <- bt_docs |>
    left_join(docs |> select(row_index, corpus), by = "row_index") |>
    filter(bertopic_topic >= 0) |>                  # drop outlier cluster -1
    mutate(corpus_pretty = pretty(corpus))

  share <- bt |>
    count(bertopic_topic, corpus_pretty) |>
    group_by(bertopic_topic) |>
    mutate(frac = n / sum(n)) |>
    ungroup() |>
    left_join(bt_top |> select(Topic, Name), by = c("bertopic_topic" = "Topic"))

  # keep the most populous neural clusters for legibility
  keep_topics <- bt |> count(bertopic_topic, sort = TRUE) |> head(20) |> pull(bertopic_topic)
  share_k <- share |> filter(bertopic_topic %in% keep_topics) |>
    mutate(Name = ifelse(is.na(Name), paste0("Topic ", bertopic_topic), Name),
           Name = fct_reorder(Name, frac * (corpus_pretty == "Relief Society Magazine"), sum))

  p_bt <- ggplot(share_k, aes(frac, Name, fill = corpus_pretty)) +
    geom_col() +
    scale_x_continuous(labels = percent) +
    scale_fill_manual(values = c("Woman's Exponent" = "#1b9e77",
                                 "Relief Society Magazine" = "#d95f02")) +
    labs(title = "BERTopic clusters by publication",
         subtitle = "Composition of each neural topic (top 20 by size); fully one colour = corpus-specific theme",
         x = "Share of cluster's documents", y = NULL, fill = "Publication") +
    theme_minimal()
  ggsave(file.path(output_path, "06_bertopic_by_publication.png"), p_bt,
         width = 11, height = 9, dpi = 120)
  print(p_bt)
  cat("Saved 06_bertopic_by_publication.png\n")
} else {
  cat("Run: python scripts\\run_bertopic.py", K, "\n")
}
```

---

## 9b. Authorship — coverage & the master author directory

This is the complement to §6b (which profiles only the 8 most prolific authors): the
**full authorship picture** for both corpora, built by `scripts/author_attribution.py`
(K-independent — a pure function of text + `corpus`, like the embeddings/contrast).
Everything the old §9b–§9f showed is now consolidated into **one master directory**
(below), with a companion **article index** (§9d) that links each attributed article to
its source text. It works in tiers:

- **Tier 1 — byline (named).** Raw OCR/typeset bylines are canonicalised via the
  editable `scripts/author_crosswalk.csv`: initials and OCR variants are merged and
  documented **pseudonyms** resolved (*Blanche Beechwood / Aunt Em / E. B. W. →
  Emmeline B. Wells*; *Prince of Ur / Home Spun → Susa Young Gates*). Commercial ad
  bylines go to an **Advertisement** bucket, masthead/organisational filler to a
  **Masthead / organization** bucket. Every other distinct byline — recurring
  **initials** (`E. T.`) and single-word **pen names** (`Clio`) — is kept as its own
  identity (never dumped); only true blanks / `Unknown` stay anonymous.
- **Tier 2 — probable (stylometric).** For authors with enough confident bylines, a
  fingerprint (function-word rates + character n-grams + structural stats — *not*
  topic words) assigns a **probable** author to anonymous articles, at two thresholds:
  **conservative** (strong, well-separated evidence) and **balanced** (more coverage).
  A machine guess never enters the byline counts — separate columns. **Small-pool
  guard:** a corpus with fewer than `ATTR_MIN_CANDIDATES` (40) trainable authors is
  closed-world-unreliable, so its anonymous articles are left **Unattributed** rather
  than forced onto the few candidates. **Woman's Exponent** (~16 authors) is therefore
  unattributed-by-design; **Relief Society Magazine** (~164) is attributed.
- **Tier 3 — unknown hands.** Anonymous articles no probable author claims are
  clustered stylometrically into distinct "unknown hands" (shown in the directory with
  `Type = Unknown hand`) — anonymous fingerprints a scholar might later name.

In the master directory, unresolved **initials** and **pen names** carry a *Resembles /
notes* column — the full-name author their style is closest to, with a **certainty %**.

> **Scholarly caution.** A "probable" author or a "resembles" match is a *statistical
> inference*, not an attribution of record. Sentiment is descriptive of register only —
> never used to identify anyone.

```{r author-roster}
author_dir <- file.path(adv_path, "author")
roster_path <- file.path(author_dir, sprintf("author_roster_K%d.csv", K))
meta_path   <- file.path(author_dir, sprintf("author_attribution_meta_K%d.json", K))
adoc_path   <- file.path(author_dir, sprintf("author_doc_K%d.csv", K))

if (have(roster_path) && have(meta_path)) {
  roster <- readr::read_csv(roster_path, show_col_types = FALSE)
  ameta  <- jsonlite::fromJSON(meta_path, simplifyVector = FALSE)

  # ---- coverage summary from meta (per corpus, both schemes) ----
  cat("Attribution coverage (share of ALL articles with a name, byline OR probable):\n\n")
  cov_tbl <- purrr::imap_dfr(ameta$corpora, function(cc, corp) {
    tibble(
      Publication = pretty(corp),
      `Substantial docs` = cc$n_substantial %||% NA_integer_,
      `Named bylines`     = cc$n_named_byline %||% NA_integer_,
      `Org / ads`         = cc$n_org %||% NA_integer_,
      `Anon. pool`        = cc$n_unknown_pool %||% NA_integer_,
      `Candidate authors` = cc$n_candidates %||% NA_integer_,
      `CV accuracy`       = if (is.null(cc$cv_accuracy)) NA_real_ else round(as.numeric(cc$cv_accuracy), 2),
      `Named+prob % (cons)` = cc$coverage_cons$pct %||% NA_real_,
      `Named+prob % (bal)`  = cc$coverage_bal$pct  %||% NA_real_)
  })
  print(knitr::kable(cov_tbl))

  # ---- attribution composition: how each scheme carves up the corpus ----
  if (have(adoc_path)) {
    adoc <- readr::read_csv(adoc_path, show_col_types = FALSE)
    comp <- purrr::map_dfr(c("cons", "bal"), function(sch) {
      fa <- adoc[[paste0("final_author_", sch)]]
      cls <- dplyr::case_when(
        adoc$byline_class == "named" ~ "Byline (named)",
        fa == "Advertisement" ~ "Advertisement",
        fa == "Masthead / organization" ~ "Masthead / org",
        fa == "Unattributed" ~ "Unattributed",
        TRUE ~ "Probable (stylometric)")
      tibble(corpus = adoc$corpus, scheme = sch, class = cls)
    }) |>
      count(corpus, scheme, class) |>
      group_by(corpus, scheme) |> mutate(frac = n / sum(n)) |> ungroup() |>
      mutate(Publication = pretty(corpus),
             scheme = factor(ifelse(scheme == "cons", "Conservative", "Balanced"),
                             levels = c("Conservative", "Balanced")),
             class = factor(class, levels = c("Byline (named)", "Probable (stylometric)",
                                              "Advertisement", "Masthead / org",
                                              "Unattributed")))

    p_comp <- ggplot(comp, aes(scheme, frac, fill = class)) +
      geom_col(width = 0.7) +
      facet_wrap(~ Publication) +
      scale_y_continuous(labels = percent, expand = expansion(mult = c(0, 0.02))) +
      scale_fill_manual(values = c("Byline (named)" = "#1b9e77",
                                   "Probable (stylometric)" = "#7570b3",
                                   "Advertisement" = "#e6ab02",
                                   "Masthead / org" = "#a6761d",
                                   "Unattributed" = "grey70")) +
      labs(title = "Who wrote the corpus? Attribution composition by scheme",
           subtitle = "Conservative vs. balanced stylometric thresholds; byline counts are unchanged between them",
           x = NULL, y = "Share of articles", fill = NULL) +
      theme_minimal(base_size = 11) +
      theme(plot.title = element_text(face = "bold"), legend.position = "bottom")
    ggsave(file.path(output_path, "14_attribution_composition.png"),
           p_comp, width = 11, height = 6, dpi = 120)
    print(p_comp)
    cat("Saved 14_attribution_composition.png\n")
  }

  # ================= MASTER AUTHOR DIRECTORY (one table for §9b/d/e/f) =================
  # author-like identities from the roster: full names, unresolved initials, pen names
  dir_auth <- roster |>
    filter(kind %in% c("named", "initials_unresolved", "pen_name_unresolved")) |>
    transmute(Publication = pretty(corpus), corpus, Identity = canonical_author,
              Type = dplyr::case_when(kind == "initials_unresolved" ~ "Initials",
                                      kind == "pen_name_unresolved" ~ "Pen name",
                                      TRUE ~ "Full name"),
              Byline = n_byline + n_byline_initials,
              `Probable (cons)` = n_probable_cons, `Probable (bal)` = n_probable_bal,
              `Mean sentiment` = round(mean_sentiment_afinn, 3),
              Years = ifelse(is.na(year_min), "", paste0(year_min, "–", year_max)))

  # resemblance + certainty for the unresolved aliases (initials / pen names)
  alias_path <- file.path(author_dir, sprintf("alias_attribution_K%d.csv", K))
  if (file.exists(alias_path)) {
    ares <- readr::read_csv(alias_path, show_col_types = FALSE) |>
      transmute(corpus, Identity = alias,
                `Resembles / notes` = probable_author,
                Certainty = scales::percent(mean_confidence, 1))
    dir_auth <- dplyr::left_join(dir_auth, ares, by = c("corpus", "Identity"))
  } else {
    dir_auth$`Resembles / notes` <- NA_character_; dir_auth$Certainty <- NA_character_
  }

  # unknown-hand clusters as their own rows (Type = Unknown hand)
  hands_path <- file.path(author_dir, sprintf("unknown_hands_K%d.csv", K))
  dir_hands <- NULL
  if (file.exists(hands_path)) {
    dir_hands <- readr::read_csv(hands_path, show_col_types = FALSE) |>
      transmute(Publication = pretty(corpus), corpus, Identity = hand, Type = "Unknown hand",
                Byline = 0L, `Probable (cons)` = 0L, `Probable (bal)` = n_docs,
                `Mean sentiment` = NA_real_,
                Years = ifelse(is.na(year_min), "", paste0(year_min, "–", year_max)),
                `Resembles / notes` = paste0("style: ", top_function_words),
                Certainty = NA_character_)
  }

  master <- dplyr::bind_rows(dir_auth, dir_hands) |>
    dplyr::mutate(Type = factor(Type, levels = c("Full name", "Initials", "Pen name", "Unknown hand"))) |>
    dplyr::arrange(Publication, Type, dplyr::desc(Byline), dplyr::desc(`Probable (bal)`)) |>
    dplyr::select(Publication, Identity, Type, Byline, `Probable (cons)`, `Probable (bal)`,
                  `Resembles / notes`, Certainty, `Mean sentiment`, Years)
  cat("\nMaster author directory:", nrow(master), "identities",
      "(full names, initials, pen names, and unknown hands) across both periodicals.\n")
  readr::write_csv(master, file.path(output_path, sprintf("author_directory_K%d.csv", K)))
  DT::datatable(master, rownames = FALSE, filter = "top",
                options = list(pageLength = 25, order = list(list(3, "desc"))),
                caption = paste0("Master author directory (", nrow(master),
                  " identities). Filter by Type; 'Resembles / notes' + Certainty apply to ",
                  "initials/pen names (who they write like) and unknown hands (marker words)."))
} else {
  cat("Run: $env:ADV_SCENARIO=\"", comparison_scenario, "\"; python scripts\\author_attribution.py ", K,
      "\n(then re-knit — this section fills the directory in).\n", sep = "")
}
```

---

## 9c. Attribution confidence & the probable-author gains

The stylometric classifier reports a probability for every anonymous article. This
section shows that confidence distribution against the two thresholds, and which
candidate authors *gain* the most anonymous articles under each scheme — the places
to spend manual-verification effort first.

```{r author-confidence}
if (exists("adoc")) {
  pool <- adoc |> filter(!is.na(attr_bal_prob))
  if (nrow(pool) > 0) {
    cons_p <- ameta$cons_prob %||% 0.80
    bal_p  <- ameta$bal_prob  %||% 0.55
    p_conf <- ggplot(pool, aes(attr_bal_prob, fill = pretty(corpus))) +
      geom_histogram(bins = 40, alpha = 0.7, position = "identity") +
      geom_vline(xintercept = bal_p,  linetype = "dashed", colour = "#7570b3") +
      geom_vline(xintercept = cons_p, linetype = "dotted", colour = "#d95f02") +
      annotate("text", x = bal_p,  y = Inf, label = " balanced", hjust = 0, vjust = 1.5, size = 3, colour = "#7570b3") +
      annotate("text", x = cons_p, y = Inf, label = " conservative", hjust = 0, vjust = 3, size = 3, colour = "#d95f02") +
      scale_fill_manual(values = c("Woman's Exponent" = "#1b9e77",
                                   "Relief Society Magazine" = "#d95f02")) +
      labs(title = "Stylometric attribution confidence (anonymous articles)",
           subtitle = "Top-class probability per anonymous article; a doc is named only above the threshold line",
           x = "Top-class probability", y = "Articles", fill = "Publication") +
      theme_minimal(base_size = 11) + theme(plot.title = element_text(face = "bold"))
    ggsave(file.path(output_path, "15_attribution_confidence.png"), p_conf,
           width = 10, height = 6, dpi = 120)
    print(p_conf)

    gains <- roster |>
      filter(kind == "named", (n_probable_cons + n_probable_bal) > 0) |>
      transmute(Publication = pretty(corpus), Author = canonical_author,
                `Byline` = n_byline, `Probable (cons)` = n_probable_cons,
                `Probable (bal)` = n_probable_bal) |>
      arrange(desc(`Probable (bal)`)) |> head(30)
    cat("\nCandidate authors gaining the most probable (anonymous) articles:\n")
    print(knitr::kable(gains))
    cat("Saved 15_attribution_confidence.png\n")
  } else {
    cat("No probable attributions were made (too few candidate authors). See §9b coverage.\n")
  }
}
```

---

## 9d. Article index — every attributed article, linked to its source

The drill-down for the directory: one row per **attributed** article (byline or
probable), with the author it's filed under and a **Source** link to the local text
file. Filter by `Author` to see *all articles listed under that author*. Unattributed /
advertisement / masthead articles are excluded (no author to list them under).

> **Source links & the web.** There are no source URLs in the corpus, so the link opens
> the local `.txt` (via `file://`). The link is built by the single `make_link()` helper
> below — to publish this to a website search engine, repoint that one function at your
> URL pattern. The structured `article_index_K*.csv` this writes **is** the search
> corpus a web engine would ingest (one record per article, keyed by `doc_id`).

```{r article-index}
if (exists("adoc") && exists("docs")) {
  # map each source filename -> full path by globbing the WE (input) & RSM (input2) folders
  src_root <- dirname(base_path)                       # .../textanalysis
  we_dir  <- file.path(src_root, "Topicmodel", "input")
  rsm_dir <- file.path(src_root, "Topicmodel", "input2")
  src_files <- c(if (dir.exists(we_dir))  list.files(we_dir,  "\\.txt$", recursive = TRUE, full.names = TRUE),
                 if (dir.exists(rsm_dir)) list.files(rsm_dir, "\\.txt$", recursive = TRUE, full.names = TRUE))
  path_map <- if (length(src_files)) setNames(src_files, basename(src_files)) else character(0)

  # link builder — SWAP the file:/// target for your website URL pattern when publishing
  make_link <- function(fname) {
    p <- unname(path_map[fname])
    ifelse(is.na(p), as.character(fname),
           sprintf('<a href="file:///%s" target="_blank">source</a>',
                   gsub(" ", "%20", gsub("\\\\", "/", p))))
  }

  art <- adoc |>
    dplyr::left_join(dplyr::select(docs, row_index, filename), by = "row_index") |>
    dplyr::mutate(
      Author = final_author_bal,
      Attribution = dplyr::case_when(
        byline_source %in% c("byline", "pseudonym", "signature", "title") ~ "Byline",
        byline_source %in% c("initials", "initials_raw")                   ~ "Byline (initials)",
        attr_bal_author != ""                                              ~ "Probable (stylometric)",
        TRUE ~ NA_character_),
      # which scheme: a real byline is certain; a stylometric guess is Conservative
      # (also clears the strict bar) or Balanced-only.
      Scheme = dplyr::case_when(
        byline_source %in% c("byline", "pseudonym", "signature", "title",
                             "initials", "initials_raw")                   ~ "Byline (certain)",
        attr_cons_author != ""                                             ~ "Conservative",
        attr_bal_author != ""                                              ~ "Balanced",
        TRUE ~ NA_character_),
      Confidence = attr_bal_prob) |>                       # NA for real bylines
    dplyr::filter(!Author %in% c("Unattributed", "Advertisement", "Masthead / organization"),
                  !is.na(Attribution)) |>
    dplyr::transmute(Publication = pretty(corpus), Author, Attribution, Scheme, Confidence,
                     Title = title, Year = year, filename)

  # web-portable structured index (no HTML) keyed by filename/doc_id
  art_csv <- art |>
    dplyr::mutate(path = unname(path_map[filename]))
  readr::write_csv(art_csv, file.path(output_path, sprintf("article_index_K%d.csv", K)))

  art_disp <- art |>
    dplyr::mutate(
      Confidence = ifelse(Attribution == "Probable (stylometric)" & !is.na(Confidence),
                          scales::percent(Confidence, 1), "—"),
      Source = vapply(filename, make_link, character(1))) |>
    dplyr::select(Publication, Author, Attribution, Scheme, Confidence, Title, Year, Source) |>
    dplyr::arrange(Author, Year)
  cat(sprintf("Article index: %d attributed articles (%d source files located for linking).\n",
              nrow(art_disp), length(path_map)))
  DT::datatable(art_disp, rownames = FALSE, filter = "top", escape = FALSE,
                options = list(pageLength = 25, deferRender = TRUE,
                               order = list(list(1, "asc"))),
                caption = paste0("Every attributed article. Attribution = how it was assigned; ",
                  "Scheme = Byline / Conservative / Balanced; Confidence = stylometric certainty ",
                  "(— for real bylines). Filter by Author; 'source' opens the local text file."))
}
```

---

*(The former §9d unknown-hands, §9e author index, and §9f alias-resemblance tables are
now unified in the **master author directory** in §9b — filter its `Type` column for
Full name / Initials / Pen name / Unknown hand, and read the `Resembles / notes` +
`Certainty` columns for the stylometric likeness of each initials/pen-name alias.)*

---

## 10. Save report objects

```{r save-objects}
report_objects <- list(
  K = K,                                       # artifact K (embedding/word sections)
  topic_K_used = if (exists("topic_override_active") && isTRUE(topic_override_active))
                   topic_K else K,             # K behind §6–§6d
  corpus_levels = corpus_levels,
  topic_labels = topic_labels,
  overlap = if (exists("ov")) ov else NULL,
  term_contrast = if (exists("tc")) tc else NULL,
  topic_prevalence_by_corpus = if (exists("prev")) prev else NULL,
  author_profiles_by_corpus  = if (exists("prof")) prof else NULL,
  keyness = if (exists("key")) key else NULL,
  shared_register = if (exists("reg")) reg else NULL,
  register_era = if (exists("fw")) fw else NULL,
  floater_specificity = if (exists("fl_summ")) fl_summ else NULL,
  topic_diff = if (exists("diffs")) diffs else NULL,
  topic_cooccurrence = if (exists("cooc")) cooc else NULL,
  sense_mix = if (exists("sm")) sm else NULL,
  author_roster = if (exists("roster")) roster else NULL,          # raw per-author roster
  author_coverage = if (exists("cov_tbl")) cov_tbl else NULL,      # §9b named+probable %
  author_directory = if (exists("master")) master else NULL,       # §9b consolidated master table
  article_index = if (exists("art_csv")) art_csv else NULL,        # §9d article->author->source
  saved_at = Sys.time()
)
saveRDS(report_objects,
        file.path(output_path, sprintf("compare_report_objects_K%d.rds", K)))
cat("Saved compare_report_objects_K", K, ".rds\n", sep = "")
```
