---
title: "Topic-to-Article Linker - Woman's Exponent"
author: "Birch"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: united
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Topic-to-Article Linker

This notebook runs STM topic modeling on whatever Woman's Exponent volumes are
placed in the input folder, then links each topic back to specific articles from
the inventory so you can identify concrete evidentiary examples for each topic
bucket. Just drop WEVol## folders into the input directory and run.

## 1. Load Packages

```{r load-packages}
library(tm)
library(stm)
library(tidyverse)
library(readxl)
library(stopwords)
library(DT)
library(textstem)    # For lemmatization
library(pheatmap)    # For heatmaps
library(scales)      # For percent formatting
library(wordcloud)
library(ggridges)    # For ridgeline plots
library(patchwork)   # For plot composition (|, /)
library(ggrepel)     # For labeled scatter points


set.seed(12345)
cat("Packages loaded.\n")
```

---

## 2. Set Paths

```{r set-paths}
input_path <- "C:/Users/birch/Rachel/GMU/Dissertation/textanalysis/Topicmodel/input"

# Write into the advanced project's WEfull scenario folder, so the saved session
# and generate_handoff.R land where the advanced text-analysis pipeline reads them.
# (For an era scenario, point this at output_linked/<scenario> and set chosen_K to match.)
output_path <- "C:/Users/birch/Rachel/GMU/Dissertation/textanalysis/Claudepythonexperimentadvtext/output_linked/WEfull"

inventory_path <- "C:/Users/birch/Rachel/GMU/Dissertation/textanalysis/exponentorder/output/WE_article_inventory_vols1-41.xlsx"

if (!dir.exists(output_path)) {
  dir.create(output_path, recursive = TRUE)
}

cat("Input:    ", input_path, "\n")
cat("Output:   ", output_path, "\n")
cat("Inventory:", inventory_path, "\n")

```

---

## 3. Load Article Inventory

```{r load-inventory}
inventory <- read_excel(inventory_path, sheet = "Article Inventory")

cat("Inventory loaded:", nrow(inventory), "articles\n")
cat("Columns:", paste(names(inventory), collapse = ", "), "\n\n")

# Detect which volumes are in the input folder
input_vol_dirs <- list.dirs(input_path, recursive = FALSE, full.names = FALSE)
input_vol_nums <- as.integer(str_extract(input_vol_dirs, "\\d+"))
input_vol_nums <- sort(input_vol_nums[!is.na(input_vol_nums)])

cat("Volumes detected in input:", paste(input_vol_nums, collapse = ", "), "\n")

# Filter inventory to only the volumes present in input
inventory_subset <- inventory %>%
  filter(Volume %in% input_vol_nums)

cat("Matching inventory articles:", nrow(inventory_subset), "\n")

```

---

## 4. Import Article Files

```{r import-files}
all_files <- list.files(path = input_path, full.names = TRUE, recursive = TRUE)
file_paths <- all_files[grepl("\\.txt$", all_files, ignore.case = TRUE)]

cat("Total .txt files found:", length(file_paths), "\n\n")

# ---- Header-stripping helper ----
# Many article .txt files start with metadata headers that, if left in,
# pollute the corpus -- "TITLE: X\nAUTHOR: Y\nDATE: Z" lines bleed in as
# regular words and the author's name ends up repeated 2-3x per file.
# Strip both formats: bracket-style `[Title: X]` and key:value lines.
strip_metadata_header <- function(raw) {
  # Strip BOM if present
  raw <- stringr::str_remove(raw, "^\\uFEFF")

  metadata_keywords <- c("title", "author", "date", "filename",
                         "year", "volume", "issue", "page", "type")
  keyword_alt <- paste(metadata_keywords, collapse = "|")

  prev <- ""
  while (raw != prev) {
    prev <- raw
    # Bracket-style header  e.g. "[Title: X]"
    raw <- stringr::str_remove(raw, "^\\[[^\\]]*\\]\\s*\\n?")
    # "Vol 26 Issue 23b" / "Issue 23" identifier on its own line
    raw <- stringr::str_remove(raw,
      "(?im)^(?:vol(?:ume)?\\s*\\d+[a-z]?\\b\\s*)?(?:issue\\s*\\d+[a-z]?\\b\\s*)?\\n")
    # Bare issue identifier like "23b" alone on the first line
    raw <- stringr::str_remove(raw, "(?i)^\\d+[a-z]?\\s*\\n")
    # "Keyword: value\n" line (the colon form)
    raw <- stringr::str_remove(raw,
      paste0("(?im)^(", keyword_alt, ")\\s*:[^\\n]*\\n"))
    # "Keyword\nValue\n" (label on its own line, value on next line)
    raw <- stringr::str_remove(raw,
      paste0("(?im)^(", keyword_alt, ")\\s*\\n[^\\n]+\\n"))
    # Leading blank lines
    raw <- stringr::str_remove(raw, "^\\s*\\n+")
  }
  raw
}

# Read all files, stripping metadata headers as we go
raw_texts <- tibble(
  filepath = file_paths,
  filename = basename(file_paths),
  text = map_chr(file_paths, ~strip_metadata_header(read_file(.x)))
)

cat("Read", nrow(raw_texts), "files.\n")
```

---

## 5. Extract Metadata & Join to Inventory

```{r extract-metadata}
# Extract metadata from file path structure
raw_texts <- raw_texts %>%
  mutate(
    # Parse volume from WEVol## directory
    volume_dir = str_extract(filepath, "WEVol\\d+"),
    volume_num = as.integer(str_extract(volume_dir, "\\d+")),
    # Parse from filename: WE_Vol32_1903_Issue1_002_TITLE.txt
    year = as.integer(str_extract(filename, "(?<=Vol\\d{1,2}_)\\d{4}")),
    issue = str_extract(filename, "(?<=Issue)\\d+"),
    article_number = as.integer(str_extract(filename, "(?<=Issue\\d{1,2}_)\\d{3}")),
    doc_id = row_number(),
    word_count = str_count(text, "\\S+")
  )

# Join to inventory by filename
raw_texts <- raw_texts %>%
  left_join(
    inventory_subset %>% select(Filename, Title, Author, Article_Type, Volume, Month),
    by = c("filename" = "Filename")
  )

match_count <- sum(!is.na(raw_texts$Title))
cat("Matched to inventory:", match_count, "of", nrow(raw_texts), "files\n")
cat("Unmatched:", sum(is.na(raw_texts$Title)), "\n\n")

# Filter the corpus: keep all substantive content INCLUDING ads (so STM can
# form a dedicated ad/commerce topic), but exclude the genuinely non-content
# documents -- TOC-style Front Matter pages and the subscription-rates Masthead.
modeled_types <- c("Article", "Editorial", "Obituary", "Correspondence",
                   "Relief Society Report", "Board/Meeting", "Resolution",
                   "Poetry", "Advertisement")
raw_texts <- raw_texts %>%
  filter(is.na(Article_Type) | Article_Type %in% modeled_types)

cat("Modeled corpus:", nrow(raw_texts), "documents\n")
cat("  including ads:", sum(raw_texts$Article_Type == "Advertisement", na.rm = TRUE), "\n")
cat("Excluded as non-content (Front Matter / Masthead): see above\n\n")

# Show sample
raw_texts %>%
  filter(!is.na(Title)) %>%
  select(filename, Title, Author, Article_Type, Volume, year) %>%
  head(10) %>%
  print()

```

---

## 6. Text Cleaning

```{r clean-text}
standard_stopwords <- stopwords::stopwords("en", source = "snowball")

custom_stopwords <- c(
  "the", "of", "and", "in", "to", "a", "is", "that", "it", "for",
  "as", "on", "with", "be", "was", "by", "are", "from", "or", "an",
  "at", "this", "which", "have", "has", "had", "but", "not", "can",
  "will", "been", "were", "their", "they", "we", "our", "would",
  "there", "what", "so", "if", "who", "than", "may", "also",
  "mrs", "mr", "miss", "dr", "ms",
  "january", "february", "march", "april", "may", "june",
  "july", "august", "september", "october", "november", "december",
  "vol", "page", "number", "volume", "board", "officer", "general",
  "thee", "thou", "whom", "no", "num", "pp", "pg",
  "issue", "nth", "th", "st", "nd", "rd",
  "womansexponent", "exponent",
    # Metadata-header words (belt-and-suspenders against header-stripping misses)
  "title", "author", "authors", "byline", "date", "filename",
  "year", "vol", "volumes", "page", "pages", "issn", "doi",
  # Author-placeholder words -- bare "Unknown" / "Anonymous" tokens that
  # the extraction pipeline writes when the original byline is missing.
  "unknown", "anonymous", "none",
  # Masthead / publication boilerplate
  "editor", "publisher", "publishe", "published", "publish",
  "assistant", "monthly", "salt", "lake", "city", "utah",
  "term", "copy", "year", "month", "cts", "cent",
  "subscription", "subscribe", "postage", "mail", "deliver",
  "advertise", "advertiser", "advertisement", "advertising",

  # Table of contents vocabulary
  "content", "contents", "frontmatter", "front", "matter",
  # Common structural words in programs and listings
  "program", "report", "reports", "committee", "meeting",
  "secretary", "sec", "secy", "asst", "pres", "treas",
  "treasurer", "president", "vice"
)

years_as_words <- as.character(unique(na.omit(raw_texts$year)))

# OCR fragment / junk word blacklist -- common broken words from digitized text
ocr_junk_stopwords <- c(
  # Suffix-only fragments
  "ing", "tion", "ment", "ness", "ings", "tive", "ance", "ence",
  "ered", "ters", "bers", "dren", "howe", "ould", "ight", "ther",
  "ated", "ting", "ally", "ible", "able", "ious", "eous", "ical",
  "onal", "ship", "ward", "wise", "less",
  # Truncated word fragments from OCR
  "deliv", "presi", "inter", "encour", "terest", "testi",
  "soci", "coun", "chil", "pariel", "organiza", "ganized",
  "ference", "musser", "selion",
  # Structural boilerplate remnants
  "column", "columns", "chapter", "section", "article",
  "continued", "copyright", "printed"
)

all_stopwords <- unique(c(standard_stopwords, custom_stopwords,
                          ocr_junk_stopwords, years_as_words))

# Regex patterns to catch OCR fragments not in the explicit list
is_ocr_fragment <- function(w) {
  grepl("^[a-z]{1,3}(tion|ment|ence|ness|ings|tive|ance)$", w) |
  grepl("^(pre|suf|dis|un|re)[a-z]{0,2}$", w) |
  grepl("^[^a-z]+$", w)
}

# ============================================================
# OCR VARIANT REMEDIATION
# Folds known OCR misreads into canonical forms BEFORE lemmatization,
# since lemmatize_words() only normalizes recognized English words.
# Build/edit this list from the `ocr-variant-audit` chunk output.
# ============================================================
ocr_fixes <- c(
  # Suffrage family
  "\\bsuffage\\b"       = "suffrage",
  "\\bsuffeage\\b"      = "suffrage",
  "\\bsufferage\\b"     = "suffrage",
  "\\bsuffiage\\b"      = "suffrage",
  "\\bsuffra\\b"        = "suffrage",
  "\\bsffrage\\b"       = "suffrage",
  "\\bsnffrage\\b"      = "suffrage",
  "\\bsuffrag\\b"       = "suffrage",   # OCR fragment (missing 'e')
  "\\bsuffragea\\b"     = "suffrage",   # OCR variant
  "\\bsuffragean\\b"    = "suffrage",   # OCR variant
  "\\bsuffraged\\b"     = "suffrage",   # OCR (no English verb form)
  "\\bsuffagist\\b"     = "suffragist",
  # Retrenchment family
  "\\brefrenchment\\b"  = "retrenchment",
  "\\bretrechment\\b"   = "retrenchment",
  "\\bretrenchmeet\\b"  = "retrenchment",
  "\\bretrenchmet\\b"   = "retrenchment",
  "\\bretrnchment\\b"   = "retrenchment",
  # Kimball -- OCR misreads only
  "\\bkimbal\\b"        = "kimball",
  "\\bkilmball\\b"      = "kimball",
  "\\bkimbalt\\b"       = "kimball",
  "\\bkinball\\b"       = "kimball",
  "\\bkmball\\b"        = "kimball",
  # Edmunds (Senator George F. Edmunds / Edmunds Act 1882)
  "\\bedends\\b"        = "edmunds",
  "\\bcoedmons\\b"      = "edmunds",
  "\\bedmnnds\\b"       = "edmunds",
  "\\bedmuuds\\b"       = "edmunds",
  "\\bedmundses\\b"     = "edmunds",
  "\\bedmundss\\b"      = "edmunds",
  "\\bedmond\\b"        = "edmunds",    # OCR variant per author judgment
  "\\bedmonds\\b"       = "edmunds",    # OCR variant per author judgment
  "\\bedmund\\b"        = "edmunds",    # OCR variant per author judgment
  # Legislature / constitution
  "\\blegilature\\b"    = "legislature",
  "\\blegislatnre\\b"   = "legislature",
  "\\bconititutional\\b" = "constitutional",
  "\\bconsititution\\b"  = "constitution",
  "\\bconsitution\\b"    = "constitution",
  "\\bconstitntion\\b"   = "constitution",
  "\\bconstittuion\\b"   = "constitution",
  "\\bconstituion\\b"    = "constitution",
  # Prosecute / prosecution -- federal legal action against polygamists.
  # CRITICAL: persecute/persecution are NOT folded.
  "\\bpresecution\\b"   = "prosecution",
  "\\bproecution\\b"    = "prosecution",
  "\\bprosecu\\b"       = "prosecute",
  "\\bprosecut\\b"      = "prosecute",
  # Reynolds (Reynolds v. United States 1879)
  "\\brynolds\\b"       = "reynolds",
  # Polygamy family -- collapse OCR errors AND grammatical variants.
  "\\blygamist\\b"      = "polygamy",   # OCR fragment of polygamist
  "\\blygamists\\b"     = "polygamy",   # OCR fragment of polygamists
  "\\bpolygamista\\b"   = "polygamy",   # OCR misread
  "\\bpolygamic\\b"     = "polygamy",   # adjective form
  "\\bpolygamical\\b"   = "polygamy",   # adjective form
  "\\bpolygamist\\b"    = "polygamy",   # noun, person
  "\\bpolygamists\\b"   = "polygamy"    # plural of polygamist
)

# ============================================================
# SURNAME PROTECTION
# Maps surnames to opaque tokens so lemmatization doesn't collapse them
# into common nouns (e.g., "wells" -> "well", losing Emmeline B. Wells).
# Context-anchored: requires a known first name or title to precede the surname.
# ============================================================
name_protect <- c(
  # Wells -- Emmeline B. Wells (editor 1877-1914)
  "\\b(emmeline|mrs|sister|elder)(\\s+[b-hj-z]\\b){0,3}\\s+wells\\b" = "wellssurname",
  # Young -- Brigham, Zina D. H., titles. Negative lookahead excludes the
  # YLMIA-style organizational compounds.
  "\\b(brigham|zina|mrs|sister|brother|president|elder)(\\s+[b-hj-z]\\b){0,3}\\s+young\\b(?!\\s+(ladies|lady|men|man|women|woman|people|folks|children|girls|boys))" = "youngsurname",
  # Snow -- Eliza R. Snow, Lorenzo Snow
  "\\b(eliza|lorenzo|mrs|sister|brother|president|elder)(\\s+[b-hj-z]\\b){0,3}\\s+snow\\b" = "snowsurname",
  # Smith -- Joseph F./Joseph III/Bathsheba W./Hyrum/Emma/Mary
  "\\b(joseph|bathsheba|emma|mary|hyrum|mrs|sister|brother|president|elder)(\\s+[b-hj-z]\\b){0,3}\\s+smith\\b" = "smithsurname"
)

processed_texts <- raw_texts %>%
  mutate(
    text_clean = str_to_lower(text),
    text_clean = str_remove_all(text_clean, "http\\S+"),
    text_clean = str_remove_all(text_clean, "\\S+@\\S+"),
    text_clean = str_remove_all(text_clean, "\\bvol\\.?\\s*\\d+\\b"),
    text_clean = str_remove_all(text_clean, "\\bno\\.?\\s*\\d+\\b"),
    text_clean = str_remove_all(text_clean, "\\bp\\.?\\s*\\d+\\b"),
    text_clean = str_remove_all(text_clean, "\\b\\d+\\b"),
    text_clean = str_remove_all(text_clean, "[[:punct:][:symbol:]]"),
    text_clean = str_replace_all(text_clean, ocr_fixes),
    text_clean = str_replace_all(text_clean, name_protect),
    text_clean = str_squish(text_clean),
    words = str_split(text_clean, "\\s+"),
    words_filtered = map(words, ~.x[!.x %in% all_stopwords]),
    words_filtered = map(words_filtered, ~.x[!grepl("^\\d+$", .x)]),
    words_filtered = map(words_filtered, ~.x[nchar(.x) >= 3 & !is_ocr_fragment(.x)]),
    # Lemmatize: women->woman, churches->church, etc.
    words_lemma = map(words_filtered, ~lemmatize_words(.x)),
    # Re-filter stopwords after lemmatization (some lemmas become stopwords)
    words_final = map(words_lemma, ~.x[!.x %in% all_stopwords & nchar(.x) >= 3 & !is_ocr_fragment(.x)]),
    text_final = map_chr(words_final, ~paste(.x, collapse = " ")),
    final_word_count = str_count(text_final, "\\S+")
  )

cat("Avg words before:", round(mean(raw_texts$word_count)), "\n")
cat("Avg words after:", round(mean(processed_texts$final_word_count)), "\n")

processed_texts <- processed_texts %>%
  filter(final_word_count >= 5)    # preserve short poems / brief notices

processed_texts <- processed_texts %>%
  mutate(
    unique_token_ratio = purrr::map_dbl(words_final, function(w) {
      if (length(w) < 3) return(1)
      length(unique(w)) / length(w)
    }),
    n_unique_tokens = purrr::map_int(words_final, ~length(unique(.x)))
  )

n_low_density <- processed_texts %>%
  filter(unique_token_ratio < 0.45,
         !Article_Type %in% c("Poetry", "Poem")) %>%
  nrow()

processed_texts <- processed_texts %>%
  filter(unique_token_ratio >= 0.45 |
         Article_Type %in% c("Poetry", "Poem"))

cat("Dropped", n_low_density, "low-density docs (poems exempt)\n")

# ---- Minimum-unique-tokens filter ----
n_too_thin <- processed_texts %>%
  filter(n_unique_tokens < 7,
         !Article_Type %in% c("Poetry", "Poem")) %>%
  nrow()

processed_texts <- processed_texts %>%
  filter(n_unique_tokens >= 7 |
         Article_Type %in% c("Poetry", "Poem"))

cat("Dropped", n_too_thin, "thin-content docs (< 7 unique tokens, poems exempt)\n")
cat("Documents after filtering:", nrow(processed_texts), "\n\n")

# --- Deduplicate near-identical documents (token-bag Jaccard clustering) ---
cat("Deduplicating near-identical documents (Jaccard clustering)...\n")
n_before_dedup <- nrow(processed_texts)

jaccard_threshold <- 0.80   # collapse docs sharing 80%+ of unique vocab
fingerprint_min_len <- 5    # skip ultra-short docs to avoid spurious matches

token_sets <- lapply(processed_texts$words_final, function(w) sort(unique(w)))
set_sizes  <- vapply(token_sets, length, integer(1))

n_docs <- length(token_sets)
edges <- vector("list", 0)
ord <- order(set_sizes)  # process short-to-long so we can early-exit inner loop

for (a in seq_len(n_docs - 1)) {
  i <- ord[a]
  si <- set_sizes[i]
  if (si < fingerprint_min_len) next
  for (b in (a + 1):n_docs) {
    j <- ord[b]
    sj <- set_sizes[j]
    if (sj < fingerprint_min_len) next
    if (si / sj < jaccard_threshold) break   # sorted by size, so all later j fail too
    inter <- length(intersect(token_sets[[i]], token_sets[[j]]))
    union <- si + sj - inter
    if (union == 0) next
    if (inter / union >= jaccard_threshold) {
      edges[[length(edges) + 1]] <- c(i, j)
    }
  }
}

# Connected components via Union-Find (no external graph library needed).
if (length(edges) > 0) {
  uf <- new.env(parent = emptyenv())
  uf$parent <- seq_len(n_docs)

  uf_find <- function(x) {
    root <- x
    while (uf$parent[root] != root) root <- uf$parent[root]
    while (uf$parent[x] != root) {
      nxt <- uf$parent[x]
      uf$parent[x] <- root
      x <- nxt
    }
    root
  }

  uf_union <- function(a, b) {
    ra <- uf_find(a); rb <- uf_find(b)
    if (ra != rb) uf$parent[ra] <- rb
  }

  for (e in edges) uf_union(e[1], e[2])

  cluster_id <- vapply(seq_len(n_docs), uf_find, integer(1))
} else {
  cluster_id <- seq_len(n_docs)   # every doc its own cluster
}

processed_texts <- processed_texts %>%
  mutate(.dup_cluster = cluster_id) %>%
  group_by(.dup_cluster) %>%
  slice_max(final_word_count, n = 1, with_ties = FALSE) %>%  # keep most complete copy
  ungroup() %>%
  select(-.dup_cluster) %>%
  mutate(doc_id = row_number())

cat("  Near-duplicate pairs found:", length(edges), "\n")
cat("  Removed", n_before_dedup - nrow(processed_texts), "near-duplicate documents\n")
cat("  Corpus after dedup:", nrow(processed_texts), "documents\n")
```
##NOT EVERY TIME
```{r remediation-accounting, eval=TRUE}
# ============================================================
# REMEDIATION ACCOUNTING (for dissertation methodology appendix)
# ============================================================

count_token_occurrences <- function(term, texts) {
  pattern <- paste0("\\b", tolower(term), "\\b")
  sum(stringr::str_count(tolower(texts), pattern))
}

# ---- OCR variant folding ----
ocr_lookup <- tibble::tibble(
  pattern   = names(ocr_fixes),
  canonical = unname(ocr_fixes)
) %>%
  mutate(variant = stringr::str_remove_all(pattern, "\\\\b")) %>%
  group_by(canonical) %>%
  summarise(variants = list(variant), .groups = "drop")

remediation_table <- ocr_lookup %>%
  mutate(
    canonical_count_raw  = purrr::map_dbl(canonical, count_token_occurrences,
                                          texts = raw_texts$text),
    variant_count_folded = purrr::map_dbl(variants, function(vs) {
      sum(purrr::map_dbl(vs, count_token_occurrences, texts = raw_texts$text))
    }),
    post_fold_count      = canonical_count_raw + variant_count_folded,
    pct_recovered        = round(100 * variant_count_folded /
                                 pmax(canonical_count_raw, 1), 1),
    n_variants_folded    = lengths(variants),
    variants_list        = purrr::map_chr(variants, ~paste(.x, collapse = ", "))
  ) %>%
  arrange(desc(variant_count_folded)) %>%
  select(canonical, canonical_count_raw, variant_count_folded,
         post_fold_count, pct_recovered, n_variants_folded, variants_list)

cat("=== OCR Remediation Accounting ===\n")
cat("Variant folding (raw text -> canonical form):\n\n")
print(remediation_table %>% select(-variants_list), n = Inf, width = Inf)

cat("\nTotals across all canonical terms:\n")
cat("  Canonical occurrences (pre-fold):  ", sum(remediation_table$canonical_count_raw), "\n")
cat("  Variant tokens folded in:          ", sum(remediation_table$variant_count_folded), "\n")
cat("  Canonical occurrences (post-fold): ", sum(remediation_table$post_fold_count), "\n")
cat("  Net recovery rate:                 ",
    round(100 * sum(remediation_table$variant_count_folded) /
          pmax(sum(remediation_table$canonical_count_raw), 1), 1), "%\n")

# ---- Surname protection (context-anchored counting) ----
name_table <- tibble::tibble(
  pattern = names(name_protect),
  opaque  = unname(name_protect)
) %>%
  mutate(
    surname        = stringr::str_remove(opaque, "surname$"),
    tokens_tagged  = purrr::map_dbl(pattern, function(p) {
      sum(stringr::str_count(tolower(raw_texts$text), p))
    }),
    bare_count_raw   = purrr::map_dbl(surname, count_token_occurrences,
                                      texts = raw_texts$text),
    bare_unprotected = bare_count_raw - tokens_tagged,
    pct_protected    = round(100 * tokens_tagged /
                             pmax(bare_count_raw, 1), 1)
  ) %>%
  select(surname, opaque_token = opaque,
         tokens_tagged, bare_count_raw, bare_unprotected, pct_protected) %>%
  arrange(desc(tokens_tagged))

cat("\n=== Surname Protection Accounting ===\n")
cat("Context-anchored tagging -- only first-name/title + surname patterns are protected.\n")
cat("'bare_unprotected' is the count of common-word uses that fall back to lemmatization.\n\n")
print(name_table, n = Inf, width = Inf)

# ---- Diagnostic: show sample tagged contexts ----
cat("\n=== Tagged Context Samples (sanity check the regex) ===\n")
set.seed(2026)  # reproducible samples
all_text <- tolower(paste(raw_texts$text, collapse = " | "))
for (i in seq_along(name_protect)) {
  pattern <- names(name_protect)[i]
  opaque  <- unname(name_protect)[i]

  ctx_pattern <- paste0("(?:\\S+\\s+){0,2}", pattern, "(?:\\s+\\S+){0,2}")
  matches <- stringr::str_extract_all(all_text, ctx_pattern)[[1]]

  cat("\n--- ", opaque, " (", length(matches), " matches; showing up to 8) ---\n", sep = "")
  if (length(matches) > 0) {
    samples <- sample(matches, min(8, length(matches)))
    cat(paste0("  ", samples, collapse = "\n"), "\n", sep = "")
  } else {
    cat("  (no matches)\n")
  }
}

# ---- Save for methodology appendix ----
write_csv(remediation_table,
          file.path(output_path, "remediation_accounting_ocr.csv"))
write_csv(name_table,
          file.path(output_path, "remediation_accounting_names.csv"))
cat("\nSaved to:\n")
cat("  ", file.path(output_path, "remediation_accounting_ocr.csv"), "\n")
cat("  ", file.path(output_path, "remediation_accounting_names.csv"), "\n")

```

---
```{r}
# --- Diagnose the prevalence covariates in `meta` (the object stm actually sees) ---
cat("meta rows:", nrow(meta), " | docs:", length(docs), "\n")
cat("NA in year:        ", sum(is.na(meta$year)), "\n")
cat("NA in Article_Type:", sum(is.na(meta$Article_Type)), "\n")
cat("Article_Type levels:", length(unique(meta$Article_Type)), "\n")
print(table(meta$Article_Type, useNA = "ifany"))
cat("year range:", paste(range(meta$year, na.rm = TRUE), collapse = " - "),
    "| unique years:", length(unique(na.omit(meta$year))), "\n")
``
`
```{r}
# What the corpus filenames look like
cat("--- Corpus filenames (raw_texts$filename) ---\n")
print(head(raw_texts$filename, 5))

# What the inventory keys look like
cat("\n--- Inventory Filename column ---\n")
print(head(inventory_subset$Filename, 5))

# Do ANY match exactly?
cat("\nExact matches:", sum(raw_texts$filename %in% inventory_subset$Filename),
    "of", nrow(raw_texts), "\n")

# Common culprits:
cat("\nCorpus has .txt extension? ", all(grepl("\\.txt$", head(raw_texts$filename))), "\n")
cat("Inventory has .txt extension?", all(grepl("\\.txt$", head(inventory_subset$Filename))), "\n")
cat("Trailing/leading whitespace in inventory keys? ",
    any(inventory_subset$Filename != trimws(inventory_subset$Filename)), "\n")
```

## 7. Prepare & Fit STM

```{r prepare-stm}
# Fill NA Article_Type so prevalence covariates don't create row mismatches
processed_texts <- processed_texts %>%
  mutate(Article_Type = ifelse(is.na(Article_Type), "Unknown", Article_Type))

processed <- textProcessor(
  documents = processed_texts$text_final,
  metadata = processed_texts %>%
    select(doc_id, filename, volume_num, year, issue, Title, Author, Article_Type),
  lowercase = FALSE,
  removestopwords = FALSE,
  removenumbers = TRUE,
  removepunctuation = FALSE,
  stem = FALSE,
  wordLengths = c(3, Inf),
  sparselevel = 1,
  language = "en",
  verbose = TRUE
)

out <- prepDocuments(
  documents = processed$documents,
  vocab = processed$vocab,
  meta = processed$meta,
  lower.thresh = 3,   # keep singletons (rare legal terms like Edmunds-Tucker)
  upper.thresh = Inf
)

docs <- out$documents
vocab <- out$vocab
meta <- out$meta

# Store the texts that actually made it into the model (for findThoughts later)
modeled_texts <- processed_texts$text_final[match(meta$doc_id, processed_texts$doc_id)]

cat("\nCorpus ready:", length(docs), "documents,", length(vocab), "vocab terms\n")
cat("  (dropped", nrow(processed_texts) - length(docs), "documents during preprocessing)\n")
```

```{r ocr-variant-audit, eval=TRUE}
# ============================================================
# OCR VARIANT AUDIT
# Scans final vocab for likely OCR misreads (Levenshtein distance <= 2).
# ============================================================
audit_terms <- c(
  # Suffrage discourse
  "suffrage", "enfranchise", "franchise", "ballot", "legislature",
  "constitution", "amendment",
  # Polygamy / federal prosecution discourse
  "polygamy", "polygamist", "plural", "marriage", "cohabitation",
  "edmunds", "tucker", "reynolds", "prosecute", "prosecution",
  "raid", "indictment", "convict", "underground",
  # Mormon women's organizing
  "relief", "society", "primary", "retrenchment", "kimball", "wells",
  # Protected surname tokens -- confirm name_protect worked.
  "wellssurname", "youngsurname", "snowsurname", "smithsurname"
)

cat("=== OCR Variant Audit ===\n")
cat("Scanning vocab (n =", length(vocab), ") for variants within edit distance 2\n\n")

audit_results <- purrr::map_dfr(audit_terms, function(term) {
  max_dist <- min(2L, ceiling(0.25 * nchar(term)))
  near <- agrep(term, vocab, max.distance = list(all = max_dist), value = TRUE)
  near <- near[abs(nchar(near) - nchar(term)) <= 2]
  variants <- setdiff(near, term)
  tibble::tibble(
    canonical  = term,
    in_vocab   = term %in% vocab,
    n_variants = length(variants),
    variants   = if (length(variants) > 0) paste(variants, collapse = ", ") else "(none)"
  )
})

audit_results %>%
  filter(!in_vocab | n_variants > 0) %>%
  arrange(desc(n_variants), canonical) %>%
  print(n = Inf, width = Inf)

missing_terms <- audit_results %>% filter(!in_vocab)        %>% pull(canonical)
high_variant  <- audit_results %>% filter(n_variants >= 2) %>% pull(canonical)

cat("\n--- Summary ---\n")
if (length(missing_terms) > 0) {
  cat("Missing from vocab entirely (check OCR or preprocessing):\n  ",
      paste(missing_terms, collapse = ", "), "\n")
} else {
  cat("All audited terms present in vocab.\n")
}
if (length(high_variant) > 0) {
  cat("\nTerms with >=2 variants (highest payoff to fold):\n  ",
      paste(high_variant, collapse = ", "), "\n")
}
```

```{r searchK, cache=TRUE}
# ============================================================
# DIAGNOSTIC: searchK - tests multiple K values
# ============================================================
cat("Running searchK diagnostic (this may take 10-30 minutes)...\n")

K_candidates <- c(35)

searchK_results <- searchK(
  documents = docs,
  vocab = vocab,
  K = K_candidates,
  data = meta,
  prevalence = ~ s(year),
  init.type = "Spectral",
  seed = 12345,
  verbose = FALSE
)

plot(searchK_results)

saveRDS(searchK_results, file.path(output_path, "searchK_results.rds"))
cat("searchK results saved. Use the plots to pick K.\n")
```

```{r searchK-detail-panels, eval=TRUE, fig.width=12, fig.height=10}
# ============================================================
# Detailed 5-panel diagnostic
# ============================================================
if (exists("searchK_results")) {

  sk_plot <- data.frame(
    K        = unlist(searchK_results$results$K),
    heldout  = unlist(searchK_results$results$heldout),
    residual = unlist(searchK_results$results$residual),
    semcoh   = unlist(searchK_results$results$semcoh),
    exclus   = unlist(searchK_results$results$exclus)
  )

  corpus_col <- "#CD661D"

  shared_scales <- list(
    scale_x_continuous(breaks = K_candidates),
    theme_minimal(base_size = 11),
    theme(legend.position = "none", panel.grid.minor = element_blank())
  )

  p1 <- ggplot(sk_plot, aes(x = K, y = heldout)) +
    geom_line(linewidth = 1.2, color = corpus_col) +
    geom_point(size = 3, color = corpus_col) +
    labs(title = "Held-Out Likelihood", subtitle = "Higher is better",
         x = "K", y = "Held-Out Likelihood") + shared_scales

  p2 <- ggplot(sk_plot, aes(x = K, y = residual)) +
    geom_line(linewidth = 1.2, color = corpus_col) +
    geom_point(size = 3, color = corpus_col) +
    labs(title = "Residuals", subtitle = "Lower is better",
         x = "K", y = "Residuals") + shared_scales

  p3 <- ggplot(sk_plot, aes(x = K, y = semcoh)) +
    geom_line(linewidth = 1.2, color = corpus_col) +
    geom_point(size = 3, color = corpus_col) +
    labs(title = "Semantic Coherence",
         subtitle = "Higher is better (trades off with exclusivity)",
         x = "K", y = "Semantic Coherence") + shared_scales

  p4 <- ggplot(sk_plot, aes(x = K, y = exclus)) +
    geom_line(linewidth = 1.2, color = corpus_col) +
    geom_point(size = 3, color = corpus_col) +
    labs(title = "Exclusivity",
         subtitle = "Higher is better (trades off with coherence)",
         x = "K", y = "Exclusivity") + shared_scales

  p5 <- ggplot(sk_plot, aes(x = semcoh, y = exclus)) +
    geom_point(size = 4, alpha = 0.8, color = corpus_col) +
    geom_text(aes(label = K), size = 3.5, vjust = -1) +
    labs(title = "Coherence vs Exclusivity Tradeoff",
         subtitle = "Numbers = K value; upper-right = best quality",
         x = "Semantic Coherence", y = "Exclusivity") +
    theme_minimal(base_size = 11) +
    theme(panel.grid.minor = element_blank())

  combined_diagnostic <- (p1 | p2) / (p3 | p4) / p5 +
    plot_annotation(
      title = "searchK Diagnostic: Woman's Exponent",
      subtitle = "Each panel shows one quality metric across candidate K values",
      theme = theme(plot.title = element_text(face = "bold", size = 16))
    )

  print(combined_diagnostic)
}
```

```{r pareto-frontier}
# ============================================================
# PARETO FRONTIER + HELD-OUT PLATEAU
# Range-independent K selection.
# ============================================================
if (exists("searchK_results")) {
  sk_data <- data.frame(
    K       = unlist(searchK_results$results$K),
    semcoh  = unlist(searchK_results$results$semcoh),
    exclus  = unlist(searchK_results$results$exclus),
    heldout = unlist(searchK_results$results$heldout)
  )
  is_pareto <- function(coh, exc) {
    vapply(seq_along(coh), function(i) {
      !any( (coh >  coh[i] & exc >= exc[i]) |
            (coh >= coh[i] & exc >  exc[i]) )
    }, logical(1))
  }
  sk_data$pareto <- is_pareto(sk_data$semcoh, sk_data$exclus)
  frontier <- sk_data %>%
    filter(pareto) %>%
    arrange(semcoh)
  cat("=== K Selection Diagnostic ===\n")
  cat("Pareto-optimal K values:", paste(sort(frontier$K), collapse = ", "), "\n")
  cat("Dominated K values:    ",
      paste(sort(sk_data$K[!sk_data$pareto]), collapse = ", "),
      ifelse(all(sk_data$pareto), "(none)", ""), "\n\n")
  corpus_col <- "#CD661D"

  p_pareto <- ggplot(sk_data, aes(x = semcoh, y = exclus)) +
    geom_line(data = frontier,
              color = corpus_col, linewidth = 1.2, alpha = 0.6) +
    geom_point(aes(color = pareto, shape = pareto, size = pareto),
               alpha = 0.9) +
    geom_text_repel(aes(label = paste0("K=", K), color = pareto),
                    size = 4, fontface = "bold", show.legend = FALSE,
                    box.padding = 0.6, point.padding = 0.4,
                    seed = 12345) +
    scale_color_manual(values = c("TRUE" = corpus_col, "FALSE" = "grey60"),
                       labels = c("TRUE" = "Pareto-optimal",
                                  "FALSE" = "Dominated")) +
    scale_shape_manual(values = c("TRUE" = 19, "FALSE" = 1),
                       labels = c("TRUE" = "Pareto-optimal",
                                  "FALSE" = "Dominated")) +
    scale_size_manual(values = c("TRUE" = 5, "FALSE" = 3),
                      labels = c("TRUE" = "Pareto-optimal",
                                 "FALSE" = "Dominated")) +
    labs(title = "Pareto Frontier -- Coherence vs Exclusivity",
         subtitle = paste0("Filled = Pareto-optimal. Hollow = dominated ",
                           "(some other K beats it on both metrics)."),
         x = "Semantic Coherence (higher = better)",
         y = "Exclusivity (higher = better)",
         color = NULL, shape = NULL, size = NULL) +
    theme_minimal(base_size = 12) +
    theme(legend.position = "bottom",
          panel.grid.minor = element_blank(),
          plot.title = element_text(face = "bold", size = 14))

  p_heldout <- ggplot(sk_data, aes(x = K, y = heldout)) +
    geom_line(linewidth = 1.0, color = "grey50") +
    geom_point(aes(color = pareto, size = pareto), alpha = 0.9) +
    geom_text_repel(aes(label = paste0("K=", K), color = pareto),
                    size = 3.8, fontface = "bold", show.legend = FALSE,
                    box.padding = 0.5, seed = 12345) +
    scale_color_manual(values = c("TRUE" = corpus_col, "FALSE" = "grey60")) +
    scale_size_manual(values = c("TRUE" = 5, "FALSE" = 3)) +
    scale_x_continuous(breaks = K_candidates) +
    labs(title = "Held-Out Likelihood -- Find the Plateau",
         subtitle = paste0("Orange = Pareto-optimal K. The 'knee' (slope ",
                           "flattens) is where adding K stops paying off."),
         x = "Number of Topics (K)",
         y = "Held-Out Likelihood (higher = better)") +
    theme_minimal(base_size = 12) +
    theme(legend.position = "none",
          panel.grid.minor = element_blank(),
          plot.title = element_text(face = "bold", size = 14))

  combined_k <- (p_pareto / p_heldout) +
    plot_annotation(
      title    = "K Selection: Pareto Frontier + Held-Out Plateau",
      subtitle = paste0("Pick the smallest Pareto-optimal K that sits on ",
                        "the held-out plateau. Then INSPECT the topics."),
      theme = theme(plot.title = element_text(face = "bold", size = 16))
    )

  print(combined_k)
}
```

```{r set-k}
# ============================================================
# SET NUMBER OF TOPICS HERE
# ============================================================
chosen_K <- 35
cat("K =", chosen_K, "\n")
```

```{r fit-model, cache=TRUE}
# Prevalence covariates: the model learns how topic prevalence varies by
# year and article type during fitting.
stm_model <- stm(
  documents = docs,
  vocab = vocab,
  K = chosen_K,
  prevalence = ~ s(year) + Article_Type,
  data = meta,
  max.em.its = 75,
  init.type = "Spectral",
  seed = 12345,
  verbose = FALSE
)

saveRDS(stm_model, file.path(output_path, paste0("stm_model_K", chosen_K, ".rds")))
cat("Model saved.\n")
```

---

## 8. Examine Topics

```{r examine-topics}
all_top_words <- labelTopics(stm_model, n = 15)

# ---- Reverse-map protected surname tokens for display ----
surname_display <- c(
  "wellssurname" = "Wells",
  "youngsurname" = "Young",
  "snowsurname"  = "Snow",
  "smithsurname" = "Smith"
)
for (slot in intersect(names(all_top_words), c("prob", "frex", "lift", "score"))) {
  all_top_words[[slot]][] <- str_replace_all(all_top_words[[slot]], surname_display)
}

cat("Top words per topic:\n\n")
for (i in 1:chosen_K) {
  cat("Topic", i, "\n")
  cat("  FREX:", paste(all_top_words$frex[i, 1:10], collapse = ", "), "\n")
  cat("  PROB:", paste(all_top_words$prob[i, 1:10], collapse = ", "), "\n\n")
}
```

---

## 8b. Auto-Generate Topic Labels

```{r auto-labels}
cat(rep("=", 70), "\n", sep = "")
cat("AUTO-GENERATING LABELS\n")
cat(rep("=", 70), "\n\n", sep = "")

create_specific_label <- function(topic_num, frex_words, prob_words) {
  frex_text <- tolower(paste(frex_words, collapse = " "))
  prob_text <- tolower(paste(prob_words, collapse = " "))
  all_words <- paste(frex_text, prob_text)

  # ---- RELIGION & DOCTRINE ----
  if (grepl("kingdom.*gospel|baptism.*eternal|salvation|atonement", frex_text)) {
    label <- "Gospel Doctrine & Spiritual Kingdom"
  } else if (grepl("passover|paschal|feast|tabernacle", frex_text)) {
    label <- "Biblical Symbolism & Ancient Rituals"
  } else if (grepl("abraham.*sarai|biblical|moses|israel", frex_text)) {
    label <- "Biblical Narratives"
  } else if (grepl("prayer|faith.*hope|testimony|spirit.*holy", frex_text)) {
    label <- "Faith & Spiritual Life"
  } else if (grepl("lesson|scripture|doctrine|commandment", frex_text)) {
    label <- "Religious Lessons & Scripture Study"
  } else if (grepl("temple|ordinance|endowment|sealing", frex_text)) {
    label <- "Temple & Sacred Ordinances"
  } else if (grepl("missionary|mission.*field|convert|preach", frex_text)) {
    label <- "Missionary Work & Conversion"

  # ---- RELIEF SOCIETY & CHURCH ORG ----
  } else if (grepl("sisters.*presidency|organization.*grain|relief.*society.*leader", frex_text)) {
    label <- "Relief Society Leadership & Organization"
  } else if (grepl("stake.*ward|attendance.*conference|quarterly", frex_text)) {
    label <- "Stake & Ward Relief Society Reports"
  } else if (grepl("empey|mclelland|board.*member|general.*board", frex_text)) {
    label <- "Board Member Directory"
  } else if (grepl("conference|general.*conference|session|sustain", all_words)) {
    label <- "Church Conference Proceedings"

  # ---- WOMEN'S RIGHTS & POLITICS ----
  } else if (grepl("suffrage.*vote|legislature|franchise|ballot", frex_text)) {
    label <- "Women's Suffrage & Political Rights"
  } else if (grepl("council.*international|convention|delegate", frex_text)) {
    label <- "International Women's Councils"
  } else if (grepl("equal.*right|petition|protest|reform", frex_text)) {
    label <- "Women's Reform & Activism"

  # ---- DOMESTICITY & HOME ----
  } else if (grepl("recipe|tbsp|boiling|oven|flour|bake", frex_text)) {
    label <- "Recipes & Cooking Instructions"
  } else if (grepl("housework|housekeeping|budget|thrift", frex_text)) {
    label <- "Household Management & Budgeting"
  } else if (grepl("child|mother.*rear|parent|infant|nurture", frex_text)) {
    label <- "Motherhood & Child-Rearing"
  } else if (grepl("garden|plant.*seed|flower|cultivation", frex_text)) {
    label <- "Home Gardening & Agriculture"
  } else if (grepl("sew|pattern|dress|fabric|garment|fashion", frex_text)) {
    label <- "Sewing, Fashion & Handwork"

  # ---- EDUCATION & PROFESSIONALIZATION ----
  } else if (grepl("nurse.*hospital|nursing.*training|medical", frex_text)) {
    label <- "Nursing Training & Hospital Work"
  } else if (grepl("school|teacher|student|education|university|class", frex_text)) {
    label <- "Education & Schools"
  } else if (grepl("diet.*protein|nutrition|malnutrition|vitamin", frex_text)) {
    label <- "Nutrition & Dietary Science"
  } else if (grepl("radium.*curie|pasteur.*science|scientist|discovery", frex_text)) {
    label <- "Scientific Biography & Discovery"

  # ---- HISTORY & PIONEER ----
  } else if (grepl("emigration.*journey|wagon.*pioneer|handcart|plains", frex_text)) {
    label <- "Pioneer Emigration & Journey Stories"
  } else if (grepl("pioneer|settlement|early.*days|frontier", all_words)) {
    label <- "Pioneer Heritage & Settlement"

  # ---- LITERATURE & ARTS ----
  } else if (grepl("irving|tale|novel|literary|author", frex_text)) {
    label <- "Literature & Book Reviews"
  } else if (grepl("jerry|walter|jimmy|agnes|margaret", frex_text) && grepl("said|little|came", prob_text)) {
    label <- "Serialized Fiction & Stories"
  } else if (grepl("poem|verse|stanza|rhyme|lyric", all_words)) {
    label <- "Poetry & Verse"
  } else if (grepl("tableau.*song|music.*hymn|choir|sing", frex_text)) {
    label <- "Musical Programs & Performances"

  # ---- WAR & CURRENT EVENTS ----
  } else if (grepl("entente.*allies|war.*troops|soldier|military|battle", frex_text)) {
    label <- "War Commentary & News"
  } else if (grepl("europe|nation|government|political|congress", frex_text)) {
    label <- "National & International Affairs"

  # ---- COMMERCE & ADS ----
  } else if (grepl("merino.*cotton|bleached.*gauze|advertis|price|store", frex_text)) {
    label <- "Advertisements & Commerce"
  } else if (grepl("^\\d+.*\\d+.*\\d+", frex_text)) {
    label <- "Magazine Index & Page Numbers"

  # ---- HEALTH ----
  } else if (grepl("health|disease|sanit|hygiene|cure|sick", all_words)) {
    label <- "Health & Sanitation"

  # ---- OBITUARY & BIOGRAPHY ----
  } else if (grepl("death|funeral|deceased|mourn|tribute", frex_text)) {
    label <- "Obituaries & Tributes"
  } else if (grepl("life.*born|biography|memoir|career|accomplish", frex_text)) {
    label <- "Biographical Sketches"

  # ---- CORRESPONDENCE ----
  } else if (grepl("letter|editor|dear|correspond|write", frex_text)) {
    label <- "Correspondence & Letters"

  # ---- FALLBACK: use top 3 FREX words ----
  } else {
    keywords <- paste(tools::toTitleCase(frex_words[1:3]), collapse = " / ")
    label <- keywords
  }

  return(label)
}

topic_labels <- sapply(1:chosen_K, function(i) {
  frex_words <- all_top_words$frex[i, 1:10]
  prob_words <- all_top_words$prob[i, 1:10]
  create_specific_label(i, frex_words, prob_words)
})

cat("Auto-generated labels:\n")
cat(rep("=", 70), "\n\n", sep = "")

for (i in 1:chosen_K) {
  cat("Topic", i, ":", topic_labels[i], "\n")
  cat("  FREX:", paste(all_top_words$frex[i, 1:7], collapse = ", "), "\n")
  cat("  PROB:", paste(all_top_words$prob[i, 1:7], collapse = ", "), "\n\n")
}

# Export auto-labels for reference
frex_for_export <- apply(all_top_words$frex, 1, function(x) paste(x, collapse = ", "))
prob_for_export <- apply(all_top_words$prob, 1, function(x) paste(x, collapse = ", "))

label_export <- tibble(
  topic_num = 1:chosen_K,
  auto_label = topic_labels,
  frex_words = frex_for_export,
  prob_words = prob_for_export,
  manual_label = ""
)

labels_file <- file.path(output_path, paste0("topic_labels_K", chosen_K, ".csv"))
write_csv(label_export, labels_file)
cat("Labels saved to:", labels_file, "\n")
```

---

## 8c. Manual Label Overrides (Optional)

```{r manual-overrides}
# ============================================================
# MANUAL OVERRIDES - edit as needed
# ============================================================
topic_labels[1] <- "Historical People and Places"
topic_labels[2] <- "National and International Women's Councils"
topic_labels[3] <- "Fictional Stories"
#topic_labels[4] <- "Fictional Stories"
topic_labels[5] <- "Relief Society and Conference Reports"
topic_labels[6] <- "Poetic Prose and Literature"
topic_labels[7] <- "Poems"
topic_labels[8] <- "Relief Society Board Meeting Reports"
topic_labels[9] <- "Resolutions of Respect"
topic_labels[10] <- "Primary Association Reports"
topic_labels[11] <- "Railroad Advertisements"
#topic_labels[12] <- "Sericulture"
topic_labels[13] <- "Birthday Announcements"
topic_labels[14] <- "International News and Histories"
topic_labels[15] <- "Motherhood"
topic_labels[16] <- "Political Party News and Events"
topic_labels[17] <- "Moral Stories"
topic_labels[18] <- "Community Celebrations"
topic_labels[19] <- "Obituaries"
topic_labels[20] <- "Pioneer Legacy"
topic_labels[21] <- "Editorial Advice"
topic_labels[22] <- "Sericulture"
topic_labels[23] <- "Advertisements"
topic_labels[24] <- "Women's Education and Refinement"
topic_labels[25] <- "Gospel Doctrine & Scripture"   # else auto-labeler gives "Gospel Doctrine & Spiritual Kingdom" (collides with T34); T25 = doctrine/scripture/ordinances
topic_labels[26] <- "Mourning and Memoriam"
topic_labels[27] <- "Household Hints and Recipes"
topic_labels[28] <- "Textile Advertisements"
topic_labels[29] <- "Current Events and News"
topic_labels[31] <- "L.D.S. Women of the Past"
topic_labels[32] <- "Polygamy and Political News"
topic_labels[33] <- "Serialized Fiction"
topic_labels[34] <- "Gospel Doctrine and Spiritual Kingdom"
topic_labels[35] <- "Education and Technical Training"


cat("FINAL TOPIC LABELS\n")
cat(rep("=", 70), "\n\n", sep = "")
for (i in 1:chosen_K) {
  cat("  Topic", i, ":", topic_labels[i], "\n")
}
```

---

## 8d. Find Examples for a Specific Topic

```{r find-examples-custom}
# ============================================================
# CHANGE THIS to examine any topic
# ============================================================
topic_to_examine <- 8

n_examples <- 15

cat(rep("=", 70), "\n", sep = "")
cat("TOPIC", topic_to_examine, ":", topic_labels[topic_to_examine], "\n")
cat(rep("=", 70), "\n", sep = "")
cat("FREX:", paste(all_top_words$frex[topic_to_examine, 1:10], collapse = ", "), "\n")
cat("PROB:", paste(all_top_words$prob[topic_to_examine, 1:10], collapse = ", "), "\n")
cat(rep("-", 70), "\n\n", sep = "")

thoughts <- findThoughts(stm_model,
                         texts = modeled_texts,
                         topics = topic_to_examine,
                         n = n_examples)

thought_indices <- thoughts$index[[1]]

for (i in seq_along(thought_indices)) {
  idx <- thought_indices[i]
  row <- processed_texts[idx, ]

  cat(sprintf("Example %d of %d:\n", i, length(thought_indices)))
  cat(sprintf("  File:   %s\n", row$filename))
  cat(sprintf("  Title:  %s\n", ifelse(is.na(row$Title), "(unknown)", row$Title)))
  cat(sprintf("  Author: %s\n", ifelse(is.na(row$Author) | row$Author == "Unknown", "-", row$Author)))
  cat(sprintf("  Type:   %s\n", ifelse(is.na(row$Article_Type), "-", row$Article_Type)))
  cat(sprintf("  Vol %s, %s, Issue %s\n\n", row$volume_num, row$year, row$issue))
  cat(substr(thoughts$docs[[1]][i], 1, 400), "\n\n")
  cat(rep("-", 50), "\n\n", sep = "")
}
```

---

## 9. Link Topics to Articles

```{r link-topics-to-articles}
# Get document-topic proportions (make.dt merges meta columns automatically)
doc_topics <- make.dt(stm_model, meta = meta)

cat("Columns in doc_topics:\n")
cat(paste(names(doc_topics), collapse = ", "), "\n\n")

topic_article_link <- doc_topics %>%
  pivot_longer(
    cols = starts_with("Topic"),
    names_to = "topic",
    values_to = "proportion"
  ) %>%
  mutate(
    topic_num = as.integer(str_remove(topic, "Topic")),
    topic_label = topic_labels[topic_num]
  ) %>%
  select(topic_num, topic_label, proportion,
         any_of(c("filename", "Title", "Author", "Article_Type",
                  "volume_num", "year", "issue"))) %>%
  arrange(topic_num, desc(proportion))

cat("Linked table:", nrow(topic_article_link), "rows\n")
cat("(", nrow(doc_topics), "documents x", chosen_K, "topics )\n")
```

---

## 9b. Dominant Topic Assignment

```{r dominant-topic}
# ============================================================
# THRESHOLD: articles above this % are "strong" exemplars
# ============================================================
exemplar_threshold <- 0.40  # 40%

dominant_topics <- doc_topics %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "proportion") %>%
  mutate(topic_num = as.integer(str_remove(topic, "Topic"))) %>%
  group_by(doc_id) %>%
  slice_max(proportion, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  mutate(
    topic_label = topic_labels[topic_num],
    strong_exemplar = proportion >= exemplar_threshold,
    proportion_pct = round(proportion * 100, 1)
  ) %>%
  select(doc_id, any_of(c("filename", "Title", "Author", "Article_Type",
         "volume_num", "year", "issue")),
         dominant_topic = topic_num, topic_label, proportion_pct, strong_exemplar) %>%
  arrange(dominant_topic, desc(proportion_pct))

cat("Dominant topic assigned to", nrow(dominant_topics), "documents\n")
cat("Strong exemplars (>", exemplar_threshold * 100, "%):", sum(dominant_topics$strong_exemplar), "\n\n")

dominant_topics %>%
  group_by(dominant_topic, topic_label) %>%
  summarise(
    n_articles = n(),
    n_strong = sum(strong_exemplar),
    avg_proportion = round(mean(proportion_pct), 1),
    .groups = "drop"
  ) %>%
  print(n = chosen_K)
```

```{r strong-exemplars}
cat("\nSTRONG EXEMPLARS (>", exemplar_threshold * 100, "% topic proportion):\n")

for (t in 1:chosen_K) {
  strong <- dominant_topics %>%
    filter(dominant_topic == t, strong_exemplar)

  cat("\n", rep("-", 60), "\n", sep = "")
  cat("Topic", t, ":", topic_labels[t], " (", nrow(strong), " strong exemplars)\n")

  if (nrow(strong) > 0) {
    for (i in 1:min(10, nrow(strong))) {
      row <- strong[i, ]
      cat(sprintf("  [%s%%] %s | %s | Vol %s %s\n",
                  row$proportion_pct,
                  ifelse(is.na(row$Title), row$filename, row$Title),
                  ifelse(is.na(row$Author) | row$Author == "Unknown", "-", row$Author),
                  row$volume_num, row$year))
    }
  } else {
    cat("  (none above threshold - try lowering exemplar_threshold)\n")
  }
}
```

---

## 10. Top Articles per Topic

```{r top-articles-per-topic}
top_n_per_topic <- 3

for (t in 1:chosen_K) {
  cat("\n", rep("=", 70), "\n", sep = "")
  cat("TOPIC", t, ":", topic_labels[t], "\n")
  cat(rep("=", 70), "\n")
  cat("FREX:", paste(all_top_words$frex[t, 1:10], collapse = ", "), "\n\n")

  top_arts <- topic_article_link %>%
    filter(topic_num == t) %>%
    head(top_n_per_topic)

  for (i in 1:nrow(top_arts)) {
    row <- top_arts[i, ]
    cat(sprintf("  %2d. [%.1f%%] Vol %s, %s, Issue %s | %s | %s | %s\n",
                i,
                row$proportion * 100,
                row$volume_num,
                row$year,
                row$issue,
                ifelse(is.na(row$Title), row$filename, row$Title),
                ifelse(is.na(row$Author) | row$Author == "Unknown", "-", row$Author),
                ifelse(is.na(row$Article_Type), "-", row$Article_Type)))
  }
}
```

---

## 11. Interactive Article Browser

```{r interactive-browser}
browse_data <- topic_article_link %>%
  group_by(topic_num) %>%
  slice_max(proportion, n = 25) %>%
  ungroup() %>%
  mutate(
    proportion_pct = round(proportion * 100, 1)
  ) %>%
  select(
    Topic = topic_num,
    Label = topic_label,
    `%` = proportion_pct,
    Title,
    Author,
    Type = Article_Type,
    Vol = volume_num,
    Year = year,
    Issue = issue,
    Filename = filename
  )

datatable(
  browse_data,
  filter = "top",
  options = list(pageLength = 20, scrollX = TRUE),
  caption = "Top 25 articles per topic - filter by topic, type, author, etc."
)
```

---

## 12. Topic Prevalence Summary

```{r topic-prevalence, fig.height = 14, fig.width = 14}
topic_props <- colMeans(doc_topics %>% select(starts_with("Topic")))

prevalence_df <- tibble(
  topic_num = 1:chosen_K,
  label = topic_labels,
  prevalence = topic_props,
  pct = round(topic_props * 100, 1)
) %>%
  arrange(desc(prevalence))

par(mar = c(5, 22, 4, 2))
bar_y <- barplot(
  height    = prevalence_df$prevalence,
  names.arg = prevalence_df$label,
  horiz     = TRUE,
  las       = 1,
  col       = "#CD661D",
  border    = "#8B4513",
  main      = paste0("Topic Prevalence - Woman's Exponent (Vols ",
                     min(input_vol_nums), "-", max(input_vol_nums), ")"),
  xlab      = "Expected Topic Proportion",
  cex.names = 0.8,
  xlim      = c(0, max(prevalence_df$prevalence) * 1.3)
)
text(
  x      = prevalence_df$prevalence + 0.005,
  y      = bar_y,
  labels = paste0(prevalence_df$pct, "%"),
  cex    = 0.7, col = "#8B4513", font = 2
)
par(mar = c(5, 4, 4, 2))

print(prevalence_df %>% select(topic_num, label, pct), n = Inf)
write_csv(
  prevalence_df %>% select(topic_num, label, prevalence, pct),
  file.path(output_path, paste0("topic_prevalence_K", chosen_K, ".csv"))
)
```

---

## 13. STM Summary Plot

```{r stm-summary, fig.width=10, fig.height=6}
plot(stm_model,
     type = "summary",
     n = min(10, chosen_K),
     main = paste("Topic Prevalence (K =", chosen_K, ")"),
     xlim = c(0, 0.3))
```

---

## 14. Lollipop Prevalence with Top Words

```{r lollipop-prevalence, fig.width=10, fig.height=6}
top_words_display <- labelTopics(stm_model, n = 10)

labels_df <- tibble(
  topic = 1:chosen_K,
  name = topic_labels,
  words = sapply(1:chosen_K, function(i) paste(top_words_display$prob[i, 1:10], collapse = ", ")),
  full_label = paste0(name, ": ", words),
  prevalence = topic_props
)

ggplot(labels_df, aes(x = prevalence, y = reorder(full_label, prevalence))) +
  geom_segment(aes(x = 0, xend = prevalence, y = full_label, yend = full_label),
               linewidth = 1.2, color = "black") +
  geom_point(aes(x = prevalence, y = full_label), size = 0.5) +
  labs(
    title = paste("Topic Prevalence (K =", chosen_K, ")"),
    x = "Expected Topic Proportions",
    y = NULL
  ) +
  theme_minimal(base_size = 10) +
  theme(
    axis.text.y = element_text(size = 8, hjust = 1),
    plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_x_continuous(limits = c(0, 0.35), breaks = seq(0, 0.35, 0.05))
```

---

## 15. Topic Prevalence Over Time

```{r prevalence-over-time, fig.width=10, fig.height=6}
cat("Estimating time effects...\n")

prep_time <- estimateEffect(
  formula = 1:chosen_K ~ s(year),
  stmobj = stm_model,
  metadata = meta,
  uncertainty = "Global"
)

cat("Estimation complete.\n\n")

top_6_topics <- order(topic_props, decreasing = TRUE)[1:min(6, chosen_K)]

par(mfrow = c(2, 3), mar = c(4, 4, 3, 1))
for (topic_num in top_6_topics) {
  plot(
    prep_time,
    covariate = "year",
    model = stm_model,
    topics = topic_num,
    method = "continuous",
    xlim = range(meta$year, na.rm = TRUE),
    main = str_wrap(topic_labels[topic_num], 30),
    xlab = "Year",
    ylab = "Topic Proportion",
    linecol = "#3b82f6",
    printlegend = TRUE,
    ci.level = 0.95,
    lwd = 2
  )
}
par(mfrow = c(1, 1))
```

---

## 16. Scatter Plot - Top 6 Topics Over Time

```{r scatter-top6, fig.width=10, fig.height=6}
topic_time_data <- make.dt(stm_model, meta = meta) %>%
  select(starts_with("Topic"), year) %>%
  filter(!is.na(year)) %>%
  group_by(year) %>%
  summarize(across(starts_with("Topic"), mean, na.rm = TRUE), .groups = "drop") %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "prevalence") %>%
  mutate(
    topic_num = as.numeric(str_remove(topic, "Topic")),
    topic_label = str_wrap(topic_labels[topic_num], 30)
  )

topic_time_top6 <- topic_time_data %>%
  filter(topic_num %in% top_6_topics)

ggplot(topic_time_top6, aes(x = year, y = prevalence)) +
  geom_line(color = "#E0EEEE", size = 1.5) +
  geom_point(color = "#E0EEEE", size = 3, alpha = 0.6) +
  geom_smooth(method = "loess", color = "#CD661D", linetype = "dashed",
              se = TRUE, alpha = 0.2) +
  facet_wrap(~topic_label, ncol = 3, scales = "free_y") +
  labs(
    title = "Topic Prevalence Over Time: Top 6 Most Prevalent Topics",
    subtitle = "Points = actual data | Dashed line = trend",
    x = "Year",
    y = "Mean Topic Proportion"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(size = 10, face = "bold"),
    panel.grid.minor = element_blank(),
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(size = 11, color = "grey40")
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1))
```

---

## 17. All Topics Over Time

```{r all-topics-time, fig.width=10, fig.height=8}
ggplot(topic_time_data, aes(x = year, y = prevalence)) +
  geom_line(color = "#CD661d", size = 0.8) +
  geom_point(color = "#CD661d", size = 1.5, alpha = 0.5) +
  facet_wrap(~topic_label, ncol = 4, scales = "free_y") +
  labs(
    title = paste0("Complete Topic Evolution Over Time (Woman's Exponent)"),
    subtitle = paste0("All ", chosen_K, " topics across years"),
    x = "Year",
    y = "Topic Proportion"
  ) +
  theme_minimal(base_size = 10) +
  theme(
    strip.text = element_text(size = 7, face = "bold"),
    panel.grid.minor = element_blank()
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1))
```

---

## 18. Single Topic Detail

```{r single-topic-detail, fig.width=10, fig.height=6}
# CHANGE THIS to examine any topic in detail
topic_to_examine <- 1

topic_detail <- topic_time_data %>%
  filter(topic_num == topic_to_examine)

ggplot(topic_detail, aes(x = year, y = prevalence)) +
  geom_line(color = "#3b82f6", size = 1.5) +
  geom_point(color = "#3b82f6", size = 4, alpha = 0.7) +
  geom_smooth(method = "loess", color = "#ef4444",
              fill = "#fecaca", alpha = 0.3, size = 1) +
  labs(
    title = topic_labels[topic_to_examine],
    subtitle = "Points = annual averages | Red band = smoothed trend with confidence interval",
    x = "Year",
    y = "Topic Proportion"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(size = 11, color = "#64748b"),
    panel.grid.minor = element_blank()
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1)) +
  scale_x_continuous(breaks = seq(min(topic_detail$year),
                                   max(topic_detail$year), by = 2))
```

---

## 19. Topic Correlation Network

```{r correlation-network, fig.width=10, fig.height=8}
mod.out.corr <- topicCorr(stm_model)
plot(mod.out.corr, main = "Topic Correlation Network")
```

---

## 20. Word Clouds

```{r wordcloud-topic1, fig.width=8, fig.height=6}
cloud(stm_model,
      topic = 1,
      scale = c(3, 0.5),
      main = topic_labels[1])
```

```{r wordcloud-all, fig.width=8, fig.height=6, eval=FALSE}
# Set eval=TRUE to generate word clouds for all topics
for (i in 1:chosen_K) {
  cloud(stm_model,
        topic = i,
        scale = c(3, 0.5),
        main = topic_labels[i])
}
```

---

## 21. Topic Quality

```{r topic-quality, fig.width=8, fig.height=6}
topicQuality(stm_model, documents = docs)
```

---

## 22. Compare Two Topics

```{r compare-topics, fig.width=10, fig.height=6}
plot(stm_model,
     type = "perspectives",
     topics = c(1, 2),
     main = paste("Comparing", topic_labels[1], "vs", topic_labels[2]))
```

---

## 23. Trend Summary Statistics

```{r trend-summary}
topic_trends <- topic_time_data %>%
  group_by(topic_num, topic_label) %>%
  summarise(
    start_prev = first(prevalence),
    end_prev   = last(prevalence),
    change     = end_prev - start_prev,
    pct_change = round((change / start_prev) * 100, 1),
    trend      = case_when(
      change >  0.005 ~ "Increasing",
      change < -0.005 ~ "Decreasing",
      TRUE            ~ "Stable"
    ),
    .groups = "drop"
  ) %>%
  arrange(desc(abs(pct_change)))

cat("TOPIC CHANGE SUMMARY\n")
cat(rep("=", 50), "\n\n", sep = "")

for (i in 1:nrow(topic_trends)) {
  direction <- ifelse(topic_trends$pct_change[i] > 0, "increased", "decreased")
  cat(sprintf("Topic %d (%s): %s by %.1f%% over the study period\n",
              topic_trends$topic_num[i],
              topic_trends$topic_label[i],
              direction,
              abs(topic_trends$pct_change[i])))
}

cat("\n\nSUMMARY TABLE\n")
print(topic_trends %>% select(topic_num, topic_label, pct_change, trend))
```

---

## 23b. Detailed Topic Change Over Time

```{r topic-change-detailed}
cat(rep("=", 70), "\n", sep = "")
cat("DETAILED TOPIC PERCENTAGE CHANGE OVER TIME\n")
cat(rep("=", 70), "\n\n", sep = "")

# Part 1: Overall percentage change (first year -> last year)
overall_change <- topic_time_data %>%
  group_by(topic_num, topic_label) %>%
  arrange(year) %>%
  summarise(
    first_year       = first(year),
    last_year        = last(year),
    first_prevalence = first(prevalence),
    last_prevalence  = last(prevalence),
    abs_change_pp    = (last_prevalence - first_prevalence) * 100,
    pct_change       = ifelse(first_prevalence > 0.001,
                              (last_prevalence - first_prevalence) / first_prevalence * 100,
                              NA_real_),
    mean_prevalence  = mean(prevalence),
    max_prevalence   = max(prevalence),
    min_prevalence   = min(prevalence),
    peak_year        = year[which.max(prevalence)],
    trough_year      = year[which.min(prevalence)],
    .groups = "drop"
  ) %>%
  mutate(
    direction = case_when(
      pct_change >  10 ~ "Growing",
      pct_change < -10 ~ "Declining",
      TRUE             ~ "Stable"
    )
  ) %>%
  arrange(desc(pct_change))

cat(sprintf("OVERALL CHANGE (%d -> %d):\n\n",
            min(topic_time_data$year), max(topic_time_data$year)))
cat(sprintf("%-40s  %8s  %8s  %10s  %9s  %10s\n",
            "Topic", "First %", "Last %", "Change pp", "% Change", "Direction"))
cat(rep("-", 95), "\n", sep = "")
for (i in 1:nrow(overall_change)) {
  r <- overall_change[i, ]
  pct_str <- ifelse(is.na(r$pct_change), "N/A", sprintf("%+.1f%%", r$pct_change))
  cat(sprintf("%-40s  %7.2f%%  %7.2f%%  %+8.2fpp  %9s  %10s\n",
              str_trunc(paste0("T", r$topic_num, ": ", r$topic_label), 40),
              r$first_prevalence * 100, r$last_prevalence * 100,
              r$abs_change_pp, pct_str, r$direction))
}

cat("\n\nPEAK / TROUGH YEARS:\n\n")
cat(sprintf("%-40s  %10s  %10s  %10s\n",
            "Topic", "Peak Year", "Peak %", "Trough Year"))
cat(rep("-", 80), "\n", sep = "")
for (i in 1:nrow(overall_change)) {
  r <- overall_change[i, ]
  cat(sprintf("%-40s  %10d  %9.2f%%  %10d\n",
              str_trunc(paste0("T", r$topic_num, ": ", r$topic_label), 40),
              r$peak_year, r$max_prevalence * 100, r$trough_year))
}

# Part 2: Year-over-year percentage changes (wide table)
cat("\n\nYEAR-OVER-YEAR PERCENTAGE CHANGE (%):\n")
cat("(positive = prevalence grew that year; negative = prevalence dropped)\n\n")

yoy_change <- topic_time_data %>%
  arrange(topic_num, year) %>%
  group_by(topic_num) %>%
  mutate(
    prev_prevalence = lag(prevalence),
    yoy_pct = ifelse(!is.na(prev_prevalence) & prev_prevalence > 0.001,
                     (prevalence - prev_prevalence) / prev_prevalence * 100,
                     NA_real_)
  ) %>%
  ungroup() %>%
  select(topic_num, topic_label, year, yoy_pct)

yoy_wide <- yoy_change %>%
  select(topic_num, topic_label, year, yoy_pct) %>%
  pivot_wider(names_from = year, values_from = yoy_pct) %>%
  arrange(topic_num) %>%
  mutate(topic = paste0("T", topic_num, ": ", str_trunc(topic_label, 30))) %>%
  select(topic, everything(), -topic_num, -topic_label)

print(yoy_wide, n = chosen_K, width = Inf)

# Part 3: Export detailed change table to CSV
overall_change_export <- overall_change %>%
  mutate(
    first_prevalence_pct = round(first_prevalence * 100, 2),
    last_prevalence_pct  = round(last_prevalence * 100, 2),
    mean_prevalence_pct  = round(mean_prevalence * 100, 2),
    max_prevalence_pct   = round(max_prevalence * 100, 2),
    min_prevalence_pct   = round(min_prevalence * 100, 2),
    abs_change_pp        = round(abs_change_pp, 2),
    pct_change           = round(pct_change, 1)
  ) %>%
  select(topic_num, topic_label, first_year, last_year,
         first_prevalence_pct, last_prevalence_pct,
         abs_change_pp, pct_change, direction,
         mean_prevalence_pct, max_prevalence_pct, peak_year,
         min_prevalence_pct, trough_year)

change_file <- file.path(output_path, paste0("topic_change_over_time_K", chosen_K, ".csv"))
write_csv(overall_change_export, change_file)
cat("\n\nDetailed change table saved to:", change_file, "\n")

yoy_file <- file.path(output_path, paste0("topic_year_over_year_change_K", chosen_K, ".csv"))
write_csv(yoy_change %>% mutate(yoy_pct = round(yoy_pct, 2)), yoy_file)
cat("Year-over-year change saved to:", yoy_file, "\n")
```

---

## 24. Topic Prevalence Stats Table

```{r prevalence-stats}
prevalence_summary <- doc_topics %>%
  select(starts_with("Topic")) %>%
  summarise(across(everything(), mean, na.rm = TRUE)) %>%
  pivot_longer(everything(), names_to = "topic", values_to = "mean_proportion") %>%
  mutate(
    topic_num   = as.numeric(str_remove(topic, "Topic")),
    label       = topic_labels[topic_num],
    percentage  = round(mean_proportion * 100, 2),
    rank        = rank(-mean_proportion)
  ) %>%
  arrange(rank) %>%
  select(rank, label, percentage)

print(prevalence_summary)
```

---

## 25. Article Type Distribution per Topic

```{r type-by-topic}
type_topic <- topic_article_link %>%
  filter(!is.na(Article_Type)) %>%
  group_by(topic_num, topic_label, Article_Type) %>%
  summarise(
    mean_proportion = mean(proportion),
    n_articles = n_distinct(filename),
    .groups = "drop"
  ) %>%
  arrange(topic_num, desc(mean_proportion))

type_topic %>%
  group_by(topic_num, topic_label) %>%
  slice_max(mean_proportion, n = 3) %>%
  print(n = chosen_K * 3)
```

---

## 26. Topic-Article Type Heatmap

```{r type-heatmap, fig.width=10, fig.height=7}
heatmap_data <- topic_article_link %>%
  filter(!is.na(Article_Type), Article_Type != "Front Matter") %>%
  group_by(topic_num, Article_Type) %>%
  summarise(mean_prop = mean(proportion), .groups = "drop") %>%
  pivot_wider(names_from = Article_Type, values_from = mean_prop, values_fill = 0)

heatmap_matrix <- as.matrix(heatmap_data %>% select(-topic_num))
rownames(heatmap_matrix) <- paste0("T", heatmap_data$topic_num, ": ",
                                    str_trunc(topic_labels[heatmap_data$topic_num], 25))

pheatmap(
  heatmap_matrix,
  main = "Topic Affinity by Article Type",
  color = colorRampPalette(c("white", "#FDDBC7", "#CD661D", "#8B4513"))(50),
  cluster_rows = TRUE,
  cluster_cols = TRUE,
  display_numbers = TRUE,
  number_format = "%.2f",
  fontsize_number = 7,
  fontsize_row = 9,
  fontsize_col = 9,
  angle_col = 45
)
```

---

## 27. Stacked Area Chart - Topic Composition Over Time

```{r stacked-area, fig.width=12, fig.height=6}
stacked_data <- make.dt(stm_model, meta = meta) %>%
  select(starts_with("Topic"), year) %>%
  filter(!is.na(year)) %>%
  group_by(year) %>%
  summarize(across(starts_with("Topic"), mean, na.rm = TRUE), .groups = "drop") %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "prevalence") %>%
  mutate(
    topic_num = as.numeric(str_remove(topic, "Topic")),
    label = topic_labels[topic_num]
  )

ggplot(stacked_data, aes(x = year, y = prevalence, fill = reorder(label, -topic_num))) +
  geom_area(alpha = 0.8, color = "white", linewidth = 0.3) +
  labs(
    title = "Topic Composition Over Time",
    subtitle = "How the discourse mix shifts across years",
    x = "Year",
    y = "Topic Proportion",
    fill = "Topic"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    legend.position = "right",
    legend.text = element_text(size = 7),
    legend.key.size = unit(0.4, "cm")
  ) +
  scale_y_continuous(labels = percent_format()) +
  scale_fill_brewer(palette = "Set3", direction = -1)
```

---

## 28. Topic Co-occurrence Within Articles

```{r topic-cooccurrence, fig.width=9, fig.height=8}
topic_prop_matrix <- doc_topics %>%
  select(starts_with("Topic"))

topic_cor <- cor(topic_prop_matrix)
rownames(topic_cor) <- paste0("T", 1:chosen_K, ": ", str_trunc(topic_labels, 20))
colnames(topic_cor) <- paste0("T", 1:chosen_K)

pheatmap(
  topic_cor,
  main = "Topic Co-occurrence (Correlation Matrix)",
  color = colorRampPalette(c("#2166AC", "white", "#B2182B"))(50),
  display_numbers = TRUE,
  number_format = "%.2f",
  fontsize_number = 8,
  fontsize_row = 9,
  fontsize_col = 9,
  breaks = seq(-1, 1, length.out = 51)
)
```

---

## 29. Exclusivity vs Semantic Coherence

```{r exclusivity-coherence, fig.width=9, fig.height=7}
topic_qual <- data.frame(
  topic = 1:chosen_K,
  label = topic_labels,
  coherence = semanticCoherence(stm_model, docs),
  exclusivity = exclusivity(stm_model)
)

ggplot(topic_qual, aes(x = coherence, y = exclusivity)) +
  geom_point(size = 4, color = "#CD661D") +
  geom_text(aes(label = paste0("T", topic)), vjust = -1, size = 3.5) +
  geom_text(aes(label = str_trunc(label, 25)), vjust = 2, size = 2.5,
            color = "grey40") +
  labs(
    title = "Topic Quality: Exclusivity vs Semantic Coherence",
    subtitle = "Upper-right = best topics (coherent + distinctive)",
    x = "Semantic Coherence",
    y = "Exclusivity"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(face = "bold", size = 14)
  )
```

---

## 30. Dominant Topic Distribution

```{r dominant-distribution, fig.width=10, fig.height=6}
dom_summary <- dominant_topics %>%
  count(dominant_topic, topic_label) %>%
  mutate(pct = n / sum(n) * 100)

ggplot(dom_summary, aes(x = reorder(topic_label, n), y = n, fill = pct)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, " (", round(pct, 1), "%)")),
            hjust = -0.1, size = 3) +
  coord_flip() +
  labs(
    title = "Articles per Dominant Topic",
    subtitle = "Each article assigned to its strongest topic",
    x = NULL, y = "Number of Articles"
  ) +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold")) +
  scale_fill_gradient(low = "#FDDBC7", high = "#8B4513") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.15)))
```

---

## 31. Topic-by-Volume Heatmap

```{r topic-volume-heatmap, fig.width=14, fig.height=7}
vol_topic_data <- make.dt(stm_model, meta = meta) %>%
  select(starts_with("Topic"), volume_num) %>%
  filter(!is.na(volume_num)) %>%
  group_by(volume_num) %>%
  summarize(across(starts_with("Topic"), mean, na.rm = TRUE), .groups = "drop")

vol_matrix <- as.matrix(vol_topic_data %>% select(-volume_num))
rownames(vol_matrix) <- paste0("Vol ", vol_topic_data$volume_num)
colnames(vol_matrix) <- paste0("T", 1:chosen_K, ": ", str_trunc(topic_labels, 20))

pheatmap(
  t(vol_matrix),
  main = "Topic Prevalence by Volume",
  color = colorRampPalette(c("white", "#FDDBC7", "#CD661D", "#8B4513"))(100),
  cluster_rows = TRUE,
  cluster_cols = FALSE,
  display_numbers = FALSE,
  fontsize_row = 8,
  fontsize_col = 9,
  angle_col = 45,
  border_color = "grey90"
)
```

---

## 32. Author-Topic Analysis

```{r author-topic, fig.width=12, fig.height=8}
author_counts <- dominant_topics %>%
  filter(!is.na(Author), Author != "Unknown") %>%
  count(Author, sort = TRUE)

top_authors <- author_counts %>%
  head(20) %>%
  pull(Author)

author_topic_data <- topic_article_link %>%
  filter(Author %in% top_authors) %>%
  group_by(Author, topic_num) %>%
  summarise(mean_prop = mean(proportion), .groups = "drop") %>%
  pivot_wider(names_from = topic_num, values_from = mean_prop, values_fill = 0)

for (k in 1:chosen_K) {
  if (!as.character(k) %in% names(author_topic_data)) {
    author_topic_data[[as.character(k)]] <- 0
  }
}
author_topic_data <- author_topic_data %>%
  select(Author, all_of(as.character(1:chosen_K)))

author_matrix <- as.matrix(author_topic_data %>% select(-Author))
rownames(author_matrix) <- author_topic_data$Author
colnames(author_matrix) <- paste0("T", 1:chosen_K, ": ", str_trunc(topic_labels, 18))

pheatmap(
  author_matrix,
  main = paste0("Author-Topic Affinity (Top ", length(top_authors), " Authors)"),
  color = colorRampPalette(c("white", "#FDDBC7", "#CD661D", "#8B4513"))(100),
  cluster_rows = TRUE,
  cluster_cols = TRUE,
  fontsize_row = 8,
  fontsize_col = 8,
  angle_col = 45,
  border_color = "grey90"
)
```

```{r author-topic-table}
author_dominant <- dominant_topics %>%
  filter(Author %in% top_authors) %>%
  count(Author, dominant_topic, topic_label, sort = TRUE) %>%
  group_by(Author) %>%
  slice_max(n, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  arrange(dominant_topic, desc(n))

cat("Most prolific authors and their primary topic:\n\n")
print(author_dominant, n = 20)
```

---

## 33. Topic Diversity per Volume

```{r topic-diversity, fig.width=10, fig.height=6}
vol_diversity <- make.dt(stm_model, meta = meta) %>%
  select(starts_with("Topic"), volume_num, year) %>%
  filter(!is.na(volume_num)) %>%
  group_by(volume_num) %>%
  summarize(
    across(starts_with("Topic"), mean, na.rm = TRUE),
    year = first(year),
    n_articles = n(),
    .groups = "drop"
  ) %>%
  rowwise() %>%
  mutate(
    entropy = {
      props <- c_across(starts_with("Topic"))
      props <- props[props > 0]
      -sum(props * log(props))
    },
    diversity = entropy / log(chosen_K)
  ) %>%
  ungroup()

ggplot(vol_diversity, aes(x = volume_num, y = diversity)) +
  geom_col(aes(fill = diversity), show.legend = FALSE) +
  geom_text(aes(label = round(diversity, 2)), vjust = -0.3, size = 2.5) +
  labs(
    title = "Topic Diversity per Volume",
    subtitle = "Higher = more thematically diverse (Shannon entropy, normalized)",
    x = "Volume",
    y = "Diversity (0 = one topic dominates, 1 = perfectly even)"
  ) +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold")) +
  scale_fill_gradient(low = "#FDDBC7", high = "#8B4513") +
  scale_y_continuous(limits = c(0, 1.1))
```

---

## 34. Ridgeline Plot - Topic Proportion Distributions

```{r ridgeline, fig.width=10, fig.height=8}
ridge_data <- topic_article_link %>%
  mutate(topic_label_full = paste0("T", topic_num, ": ", topic_label))

ggplot(ridge_data, aes(x = proportion, y = reorder(topic_label_full, topic_num),
                        fill = after_stat(x))) +
  geom_density_ridges_gradient(scale = 2.5, rel_min_height = 0.01,
                                gradient_lwd = 0.3) +
  scale_fill_gradient(low = "#FDDBC7", high = "#8B4513", guide = "none") +
  labs(
    title = "Distribution of Topic Proportions Across Articles",
    subtitle = "Long right tails = some articles are strongly about that topic",
    x = "Topic Proportion",
    y = NULL
  ) +
  theme_minimal(base_size = 11) +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    axis.text.y = element_text(size = 8)
  ) +
  scale_x_continuous(labels = percent_format(), limits = c(0, NA))
```

---

## 35. Topic Dendrogram

```{r dendrogram, fig.width=10, fig.height=6}
topic_word_matrix <- exp(stm_model$beta$logbeta[[1]])

topic_dist <- dist(topic_word_matrix, method = "euclidean")
topic_clust <- hclust(topic_dist, method = "ward.D2")

topic_clust$labels <- paste0("T", 1:chosen_K, ": ", topic_labels)

par(mar = c(2, 4, 3, 12))
plot(as.dendrogram(topic_clust),
     horiz = TRUE,
     main = "Topic Similarity Dendrogram",
     xlab = "Distance",
     cex = 0.8)
par(mar = c(5, 4, 4, 2))
```

---

## 36. Within-Topic Vocabulary Comparison (Early vs Late Period)

```{r vocab-comparison-era, fig.width=16, fig.height=20}
cat(rep("=", 70), "\n", sep = "")
cat("WITHIN-TOPIC VOCABULARY COMPARISON (EARLY vs LATE)\n")
cat(rep("=", 70), "\n\n", sep = "")

median_year <- median(meta$year, na.rm = TRUE)
doc_topics_era <- doc_topics %>%
  mutate(era = ifelse(year <= median_year, "Early", "Late"))

cat("Era split at year", median_year, "\n")
cat("  Early:", sum(doc_topics_era$era == "Early"), "documents\n")
cat("  Late: ", sum(doc_topics_era$era == "Late"), "documents\n\n")

get_topic_words_by_era <- function(topic_num, era_name) {
  topic_col <- paste0("Topic", topic_num)
  era_docs <- doc_topics_era %>% filter(era == era_name)
  threshold <- quantile(era_docs[[topic_col]], 0.75, na.rm = TRUE)

  doc_ids <- era_docs %>%
    filter(.data[[topic_col]] >= threshold) %>%
    pull(doc_id)

  words <- processed_texts %>%
    filter(doc_id %in% doc_ids) %>%
    pull(text_final) %>%
    paste(collapse = " ") %>%
    str_split("\\s+") %>%
    `[[`(1)

  freq <- sort(table(words), decreasing = TRUE)
  tibble(word = names(freq), count = as.integer(freq)) %>%
    mutate(proportion = count / sum(count)) %>%
    filter(
      nchar(word) >= 4,
      !word %in% all_stopwords,
      !is_ocr_fragment(word)
    )
}

top_6_for_vocab <- order(topic_props, decreasing = TRUE)[1:min(6, chosen_K)]

cat("Comparing vocabulary for top", length(top_6_for_vocab), "topics:\n")
for (t in top_6_for_vocab) {
  cat(sprintf("  T%d: %s\n", t, topic_labels[t]))
}
cat("\n")

vocab_plots <- list()
for (idx in seq_along(top_6_for_vocab)) {
  t <- top_6_for_vocab[idx]

  words_early <- get_topic_words_by_era(t, "Early")
  words_late  <- get_topic_words_by_era(t, "Late")

  word_compare <- full_join(
    words_early %>% select(word, early_prop = proportion),
    words_late  %>% select(word, late_prop = proportion),
    by = "word"
  ) %>%
    replace_na(list(early_prop = 0.0001, late_prop = 0.0001)) %>%
    mutate(
      log_ratio = log2(early_prop / late_prop),
      avg_prop = (early_prop + late_prop) / 2
    ) %>%
    filter(avg_prop > 0.001) %>%
    arrange(desc(abs(log_ratio)))

  top_early <- word_compare %>% filter(log_ratio > 0) %>% head(20)
  top_late  <- word_compare %>% filter(log_ratio < 0) %>% head(20)

  early_label <- paste0("More in Early (≤", median_year, ")")
  late_label  <- paste0("More in Late (>", median_year, ")")

  plot_words <- bind_rows(top_early, top_late) %>%
    mutate(
      direction = ifelse(log_ratio > 0, early_label, late_label),
      word = reorder(word, log_ratio)
    )

  p <- ggplot(plot_words, aes(x = log_ratio, y = word, fill = direction)) +
    geom_col(alpha = 0.8) +
    geom_vline(xintercept = 0, linewidth = 0.8) +
    scale_fill_manual(values = setNames(c("#CD661D", "#8B4513"),
                                        c(early_label, late_label))) +
    labs(title = paste0("T", t, ": ", str_trunc(topic_labels[t], 35)),
         x = "Word emphasis by period (right = earlier, left = later)",
         y = NULL, fill = NULL) +
    theme_minimal(base_size = 8) +
    theme(legend.position = "none",
          plot.title = element_text(size = 10, face = "bold"))

  vocab_plots[[idx]] <- p
}

if (length(vocab_plots) >= 6) {
  (vocab_plots[[1]] | vocab_plots[[2]] | vocab_plots[[3]]) /
  (vocab_plots[[4]] | vocab_plots[[5]] | vocab_plots[[6]]) +
    plot_annotation(
      title = "Within-Topic Vocabulary Shifts: Early vs Late Period",
      subtitle = paste0("Top 20 words each era emphasizes differently (split at ",
                        median_year, ")"),
      theme = theme(plot.title = element_text(size = 16, face = "bold"))
    )
} else if (length(vocab_plots) >= 1) {
  wrap_plots(vocab_plots, ncol = min(3, length(vocab_plots))) +
    plot_annotation(title = "Within-Topic Vocabulary Shifts: Early vs Late Period")
}
```

### All topics, paginated

```{r vocab-comparison-all, fig.width=16, fig.height=10}
cat(rep("=", 70), "\n", sep = "")
cat("WITHIN-TOPIC VOCABULARY COMPARISON (EARLY vs LATE) -- paginated\n")
cat(rep("=", 70), "\n\n", sep = "")

cat("Building plots for all", length(order(topic_props, decreasing = TRUE)), "topics...\n")

all_topics_ordered <- order(topic_props, decreasing = TRUE)

vocab_plots <- list()
for (idx in seq_along(all_topics_ordered)) {
  t <- all_topics_ordered[idx]

  words_early <- get_topic_words_by_era(t, "Early")
  words_late  <- get_topic_words_by_era(t, "Late")

  word_compare <- full_join(
    words_early %>% select(word, early_prop = proportion),
    words_late  %>% select(word, late_prop  = proportion),
    by = "word"
  ) %>%
    replace_na(list(early_prop = 0.0001, late_prop = 0.0001)) %>%
    mutate(
      log_ratio = log2(early_prop / late_prop),
      avg_prop  = (early_prop + late_prop) / 2
    ) %>%
    filter(avg_prop > 0.001) %>%
    arrange(desc(abs(log_ratio)))

  top_early <- word_compare %>% filter(log_ratio > 0) %>% head(20)
  top_late  <- word_compare %>% filter(log_ratio < 0) %>% head(20)

  early_label <- paste0("More in Early (≤", median_year, ")")
  late_label  <- paste0("More in Late (>",    median_year, ")")

  plot_words <- bind_rows(top_early, top_late) %>%
    mutate(
      direction = ifelse(log_ratio > 0, early_label, late_label),
      word      = reorder(word, log_ratio)
    )

  p <- ggplot(plot_words, aes(x = log_ratio, y = word, fill = direction)) +
    geom_col(alpha = 0.85) +
    geom_vline(xintercept = 0, linewidth = 0.8) +
    scale_fill_manual(values = setNames(c("#CD661D", "#8B4513"),
                                        c(early_label, late_label))) +
    labs(
      title = paste0("T", t, ": ", str_trunc(topic_labels[t], 45)),
      x     = paste0("← More after ", median_year,
                     "   |   More before ", median_year, " →"),
      y     = NULL,
      fill  = NULL
    ) +
    theme_minimal(base_size = 10) +
    theme(
      legend.position = "none",
      plot.title      = element_text(size = 12, face = "bold"),
      axis.text.y     = element_text(size = 9),
      axis.title.x    = element_text(size = 9),
      plot.margin     = margin(8, 12, 8, 12)
    )

  vocab_plots[[idx]] <- p
}

# Paginate: 4 plots per page, 2 columns wide (2x2 per page)
plots_per_page <- 4
n_pages <- ceiling(length(vocab_plots) / plots_per_page)

for (page in seq_len(n_pages)) {
  start_i <- (page - 1) * plots_per_page + 1
  end_i   <- min(start_i + plots_per_page - 1, length(vocab_plots))
  batch   <- vocab_plots[start_i:end_i]

  # FIX: the '+ plot_annotation(...)' must actually be appended to the
  # wrap_plots() result (previously the '+' was swallowed by a comment).
  combined <- wrap_plots(batch, ncol = 2) +
    plot_annotation(
      title    = paste0("Within-Topic Vocabulary Shifts -- Page ",
                        page, " of ", n_pages),
      subtitle = paste0("Topics ", start_i, "–", end_i,
                        " by prevalence rank. Era split at ", median_year,
                        ". Orange = more before; brown = more after."),
      theme    = theme(plot.title    = element_text(size = 18, face = "bold"),
                       plot.subtitle = element_text(size = 12))
    )

  print(combined)

  # Save each page as a standalone PNG (so dissertation renders at full size,
  # not the notebook's compressed display width).
  ggsave(
    file.path(output_path,
              paste0("vocab_shifts_K", chosen_K, "_page", page, ".png")),
    combined, width = 14, height = 24, dpi = 200, limitsize = FALSE
  )
}

cat("\nSaved", n_pages, "PNG pages to:", output_path, "\n")
```

### Vocabulary changepoints (Jensen-Shannon divergence)

Uses JSD to find each topic's own change-year, rather than a shared median split.

```{r vocab-comparison-changepoint, fig.width=14, fig.height=22}
cat(rep("=", 70), "\n", sep = "")
cat("WITHIN-TOPIC VOCABULARY CHANGEPOINT DETECTION -- paginated\n")
cat(rep("=", 70), "\n\n", sep = "")

# ---- Helpers ----
.topic_words <- function(doc_ids) {
  words <- processed_texts %>%
    filter(doc_id %in% doc_ids) %>%
    pull(text_final) %>%
    paste(collapse = " ") %>%
    str_split("\\s+") %>%
    `[[`(1)
  words[nchar(words) >= 4 &
        !words %in% all_stopwords &
        !is_ocr_fragment(words)]
}

.js_divergence <- function(words_a, words_b) {
  if (length(words_a) < 50 || length(words_b) < 50) return(0)
  vocab_union <- union(unique(words_a), unique(words_b))
  p_a <- as.numeric(table(factor(words_a, levels = vocab_union))) / length(words_a)
  p_b <- as.numeric(table(factor(words_b, levels = vocab_union))) / length(words_b)
  m   <- (p_a + p_b) / 2
  eps <- 1e-12
  kl  <- function(p, q) sum(p * log2((p + eps) / (q + eps)), na.rm = TRUE)
  (kl(p_a, m) + kl(p_b, m)) / 2
}

find_topic_changepoint <- function(topic_num, min_docs_per_side = 15) {
  topic_col <- paste0("Topic", topic_num)
  threshold <- quantile(doc_topics[[topic_col]], 0.75, na.rm = TRUE)

  topic_docs <- doc_topics %>%
    filter(.data[[topic_col]] >= threshold, !is.na(year)) %>%
    select(doc_id, year) %>%
    arrange(year)

  if (nrow(topic_docs) < 2 * min_docs_per_side) {
    return(list(year = NA_integer_, max_div = NA_real_, curve = NULL))
  }

  candidates <- sort(unique(topic_docs$year))
  candidates <- candidates[
    vapply(candidates, function(y) {
      sum(topic_docs$year <= y) >= min_docs_per_side &
      sum(topic_docs$year >  y) >= min_docs_per_side
    }, logical(1))
  ]
  if (length(candidates) == 0) {
    return(list(year = NA_integer_, max_div = NA_real_, curve = NULL))
  }

  divergences <- vapply(candidates, function(yr) {
    early_ids <- topic_docs$doc_id[topic_docs$year <= yr]
    late_ids  <- topic_docs$doc_id[topic_docs$year >  yr]
    .js_divergence(.topic_words(early_ids), .topic_words(late_ids))
  }, numeric(1))

  list(
    year    = candidates[which.max(divergences)],
    max_div = max(divergences),
    curve   = tibble(year = candidates, divergence = divergences)
  )
}

cat("Detecting changepoints for all", chosen_K, "topics...\n")
changepoints <- list()
for (t in 1:chosen_K) {
  cat(sprintf("  T%d: %s ... ", t, str_trunc(topic_labels[t], 35)))
  cp <- find_topic_changepoint(t)
  changepoints[[t]] <- cp
  if (is.na(cp$year)) {
    cat("(too few docs)\n")
  } else {
    cat(sprintf("split at %d (JS = %.3f)\n", cp$year, cp$max_div))
  }
}

saveRDS(changepoints,
        file.path(output_path, paste0("changepoints_K", chosen_K, ".rds")))

changepoint_df <- tibble(
  topic_num   = 1:chosen_K,
  label       = topic_labels,
  prevalence  = topic_props,
  split_year  = vapply(changepoints, `[[`, integer(1),  "year"),
  max_jsd     = vapply(changepoints, `[[`, numeric(1), "max_div")
) %>%
  arrange(desc(prevalence))

cat("\nChangepoint summary (sorted by prevalence):\n")
print(changepoint_df, n = Inf)

write_csv(changepoint_df,
          file.path(output_path, paste0("topic_changepoints_K", chosen_K, ".csv")))

get_topic_words_at_split <- function(topic_num, split_year, side = c("early","late")) {
  side <- match.arg(side)
  topic_col <- paste0("Topic", topic_num)
  threshold <- quantile(doc_topics[[topic_col]], 0.75, na.rm = TRUE)

  era_filter <- if (side == "early") rlang::expr(year <= !!split_year)
                else                  rlang::expr(year >  !!split_year)

  doc_ids <- doc_topics %>%
    filter(.data[[topic_col]] >= threshold, !is.na(year)) %>%
    filter(!!era_filter) %>%
    pull(doc_id)

  words <- .topic_words(doc_ids)
  freq  <- sort(table(words), decreasing = TRUE)
  tibble(word = names(freq), count = as.integer(freq)) %>%
    mutate(proportion = count / sum(count))
}

all_topics_ordered <- order(topic_props, decreasing = TRUE)

vocab_plots <- list()
for (idx in seq_along(all_topics_ordered)) {
  t  <- all_topics_ordered[idx]
  cp <- changepoints[[t]]

  if (is.na(cp$year)) {
    vocab_plots[[idx]] <- ggplot() +
      ggplot2::annotate("text", x = 0, y = 0,
               label = paste0("T", t, ": insufficient data"),
               size = 6) +
      theme_void()
    next
  }

  split_yr <- cp$year
  words_early <- get_topic_words_at_split(t, split_yr, "early")
  words_late  <- get_topic_words_at_split(t, split_yr, "late")

  word_compare <- full_join(
    words_early %>% select(word, early_prop = proportion),
    words_late  %>% select(word, late_prop  = proportion),
    by = "word"
  ) %>%
    replace_na(list(early_prop = 0.0001, late_prop = 0.0001)) %>%
    mutate(
      log_ratio = log2(early_prop / late_prop),
      avg_prop  = (early_prop + late_prop) / 2
    ) %>%
    filter(avg_prop > 0.001) %>%
    arrange(desc(abs(log_ratio)))

  top_early <- word_compare %>% filter(log_ratio > 0) %>% head(15)
  top_late  <- word_compare %>% filter(log_ratio < 0) %>% head(15)

  early_label <- paste0("More ≤", split_yr)
  late_label  <- paste0("More >",     split_yr)

  plot_words <- bind_rows(top_early, top_late) %>%
    mutate(
      direction = ifelse(log_ratio > 0, early_label, late_label),
      word      = reorder(word, log_ratio)
    )

  p <- ggplot(plot_words, aes(x = log_ratio, y = word, fill = direction)) +
    geom_col(alpha = 0.85) +
    geom_vline(xintercept = 0, linewidth = 0.8) +
    scale_fill_manual(values = setNames(c("#CD661D", "#8B4513"),
                                        c(early_label, late_label))) +
    labs(
      title    = paste0("T", t, ": ", str_trunc(topic_labels[t], 45)),
      subtitle = paste0("Changepoint: ", split_yr,
                        "   |   JSD = ", sprintf("%.2f", cp$max_div),
                        "   |   Prevalence: ",
                        sprintf("%.1f%%", topic_props[t] * 100)),
      x        = paste0("← after ", split_yr,
                        "   |   before ", split_yr, " →"),
      y        = NULL, fill = NULL
    ) +
    theme_minimal(base_size = 10) +
    theme(
      legend.position = "none",
      plot.title      = element_text(size = 12, face = "bold"),
      plot.subtitle   = element_text(size = 10, color = "grey35"),
      axis.text.y     = element_text(size = 10),
      axis.title.x    = element_text(size = 9),
      plot.margin     = margin(8, 12, 8, 12)
    )

  vocab_plots[[idx]] <- p
}

plots_per_page <- 4
n_pages <- ceiling(length(vocab_plots) / plots_per_page)

for (page in seq_len(n_pages)) {
  start_i <- (page - 1) * plots_per_page + 1
  end_i   <- min(start_i + plots_per_page - 1, length(vocab_plots))
  batch   <- vocab_plots[start_i:end_i]

  combined <- wrap_plots(batch, ncol = 2) +
    plot_annotation(
      title    = paste0("Topic-Specific Vocabulary Changepoints -- Page ",
                        page, " of ", n_pages),
      subtitle = paste0("Topics ", start_i, "–", end_i,
                        " by prevalence rank. Each split at its own ",
                        "JSD-maximizing year."),
      theme    = theme(plot.title    = element_text(size = 18, face = "bold"),
                       plot.subtitle = element_text(size = 12))
    )

  print(combined)

  ggsave(
    file.path(output_path,
              paste0("changepoint_shifts_K", chosen_K, "_page", page, ".png")),
    combined, width = 14, height = 22, dpi = 200, limitsize = FALSE
  )
}

cat("\nSaved", n_pages, "PNG pages to:", output_path, "\n")
```

### Per-topic word trajectories over time

```{r word-trajectories, fig.width=14, fig.height=20}
cat(rep("=", 70), "\n", sep = "")
cat("PER-TOPIC WORD TRAJECTORIES OVER TIME\n")
cat(rep("=", 70), "\n\n", sep = "")

if (!exists("changepoints")) {
  changepoints <- readRDS(
    file.path(output_path, paste0("changepoints_K", chosen_K, ".rds"))
  )
}

get_word_trajectories <- function(topic_num, n_words = 8, min_years_present = 4) {
  topic_col <- paste0("Topic", topic_num)
  threshold <- quantile(doc_topics[[topic_col]], 0.75, na.rm = TRUE)

  topic_doc_info <- doc_topics %>%
    filter(.data[[topic_col]] >= threshold, !is.na(year)) %>%
    select(doc_id, year)

  if (nrow(topic_doc_info) < 30) return(NULL)

  word_year_df <- processed_texts %>%
    filter(doc_id %in% topic_doc_info$doc_id) %>%
    select(doc_id, text_final) %>%
    inner_join(topic_doc_info, by = "doc_id") %>%
    mutate(words = str_split(text_final, "\\s+")) %>%
    select(year, words) %>%
    unnest(words) %>%
    filter(nchar(words) >= 4,
           !words %in% all_stopwords,
           !is_ocr_fragment(words))

  word_year_counts <- word_year_df %>%
    count(year, words) %>%
    group_by(words) %>%
    mutate(years_present = n_distinct(year),
           total = sum(n)) %>%
    ungroup()

  top_words <- word_year_counts %>%
    filter(years_present >= min_years_present) %>%
    distinct(words, total) %>%
    arrange(desc(total)) %>%
    head(n_words) %>%
    pull(words)

  if (length(top_words) == 0) return(NULL)

  per_year_totals <- word_year_df %>%
    filter(words %in% top_words) %>%
    count(year, name = "year_total")

  trajectory <- word_year_counts %>%
    filter(words %in% top_words) %>%
    inner_join(per_year_totals, by = "year") %>%
    mutate(prop = n / year_total) %>%
    select(year, word = words, prop)

  all_years <- seq(min(trajectory$year), max(trajectory$year))
  trajectory <- trajectory %>%
    complete(year = all_years, word = top_words, fill = list(prop = 0))

  trajectory
}

all_topics_ordered <- order(topic_props, decreasing = TRUE)

traj_palette <- c("#CD661D", "#1F77B4", "#2CA02C", "#9467BD",
                  "#8B4513", "#17BECF", "#E377C2", "#7F7F7F")

trajectory_plots <- list()
for (idx in seq_along(all_topics_ordered)) {
  t  <- all_topics_ordered[idx]
  cp <- changepoints[[t]]

  cat(sprintf("  T%d (%s): computing trajectories...\n",
              t, str_trunc(topic_labels[t], 35)))
  traj <- get_word_trajectories(t, n_words = 8, min_years_present = 4)

  if (is.null(traj) || nrow(traj) == 0) {
    trajectory_plots[[idx]] <- ggplot() +
      ggplot2::annotate("text", x = 0, y = 0,
               label = paste0("T", t, ": insufficient data"),
               size = 6) +
      theme_void()
    next
  }

  p <- ggplot(traj, aes(x = year, y = prop, color = word)) +
    geom_point(alpha = 0.25, size = 1.2) +
    geom_smooth(method = "loess", se = FALSE, span = 0.55, linewidth = 1.1) +
    scale_color_manual(values = traj_palette[seq_len(n_distinct(traj$word))]) +
    scale_x_continuous(breaks = scales::pretty_breaks(n = 6)) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    labs(
      title    = paste0("T", t, ": ", str_trunc(topic_labels[t], 45)),
      subtitle = if (!is.na(cp$year))
                   paste0("Changepoint: ", cp$year,
                          "   |   JSD = ", sprintf("%.2f", cp$max_div))
                 else "Changepoint: (insufficient data)",
      x = NULL,
      y = "Share of topic vocab",
      color = NULL
    ) +
    theme_minimal(base_size = 10) +
    theme(
      legend.position = "right",
      legend.text     = element_text(size = 9),
      legend.key.size = unit(0.8, "lines"),
      plot.title      = element_text(size = 12, face = "bold"),
      plot.subtitle   = element_text(size = 10, color = "grey35"),
      axis.title.y    = element_text(size = 9),
      panel.grid.minor = element_blank(),
      plot.margin     = margin(8, 12, 8, 12)
    )

  if (!is.na(cp$year)) {
    p <- p +
      geom_vline(xintercept = cp$year,
                 linetype = "dashed", color = "grey25", linewidth = 0.6) +
      ggplot2::annotate("text", x = cp$year, y = Inf,
               label = paste0(" CP: ", cp$year),
               hjust = 0, vjust = 1.5, size = 3.2, color = "grey25",
               fontface = "italic")
  }

  trajectory_plots[[idx]] <- p
}

plots_per_page <- 4
n_pages <- ceiling(length(trajectory_plots) / plots_per_page)

for (page in seq_len(n_pages)) {
  start_i <- (page - 1) * plots_per_page + 1
  end_i   <- min(start_i + plots_per_page - 1, length(trajectory_plots))
  batch   <- trajectory_plots[start_i:end_i]

  combined <- wrap_plots(batch, ncol = 2) +
    plot_annotation(
      title    = paste0("Top-Word Trajectories Within Topics -- Page ",
                        page, " of ", n_pages),
      subtitle = paste0("Topics ", start_i, "–", end_i,
                        " by prevalence rank. Lines = LOESS-smoothed share ",
                        "of topic vocab per year. Dashed line = JSD changepoint."),
      theme    = theme(plot.title    = element_text(size = 18, face = "bold"),
                       plot.subtitle = element_text(size = 12))
    )

  print(combined)

  ggsave(
    file.path(output_path,
              paste0("word_trajectories_K", chosen_K, "_page", page, ".png")),
    combined, width = 14, height = 20, dpi = 200, limitsize = FALSE
  )
}

cat("\nSaved", n_pages, "PNG pages to:", output_path, "\n")
```

---

## 37. Topic Diversity & Concentration (Document-Level)

```{r doc-level-diversity, fig.width=12, fig.height=10}
cat(rep("=", 70), "\n", sep = "")
cat("DOCUMENT-LEVEL TOPIC DIVERSITY\n")
cat(rep("=", 70), "\n\n", sep = "")

doc_entropy <- doc_topics %>%
  select(doc_id, starts_with("Topic")) %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "p") %>%
  filter(p > 0) %>%
  group_by(doc_id) %>%
  summarize(entropy = -sum(p * log2(p)), .groups = "drop")

doc_gini <- doc_topics %>%
  select(doc_id, starts_with("Topic")) %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "p") %>%
  group_by(doc_id) %>%
  summarize(
    max_topic_prop = max(p),
    gini = 1 - sum(p^2),
    .groups = "drop"
  )

diversity_summary <- doc_entropy %>%
  left_join(doc_gini, by = "doc_id") %>%
  summarize(
    mean_entropy = mean(entropy),
    sd_entropy = sd(entropy),
    mean_gini = mean(gini),
    mean_max_prop = mean(max_topic_prop),
    pct_strong_exemplar = mean(max_topic_prop >= 0.4) * 100
  )

cat("Diversity Metrics (Woman's Exponent):\n\n")
cat(sprintf("  Mean Shannon Entropy:     %.2f bits\n", diversity_summary$mean_entropy))
cat(sprintf("  SD Entropy:               %.2f\n", diversity_summary$sd_entropy))
cat(sprintf("  Mean Gini (inv-Herf):     %.3f\n", diversity_summary$mean_gini))
cat(sprintf("  Mean Dominant Topic %%:    %.1f%%\n", diversity_summary$mean_max_prop * 100))
cat(sprintf("  Strong Exemplars (>40%%):  %.1f%% of documents\n\n", diversity_summary$pct_strong_exemplar))

p1 <- ggplot(doc_entropy, aes(x = entropy)) +
  geom_density(fill = "#CD661D", alpha = 0.5, linewidth = 0.8, color = "#8B4513") +
  labs(title = "Topic Diversity per Document",
       subtitle = "Higher entropy = article discusses more topics evenly",
       x = "Shannon Entropy (bits)", y = "Density") +
  theme_minimal(base_size = 12)

p2 <- ggplot(doc_gini, aes(x = max_topic_prop)) +
  geom_density(fill = "#CD661D", alpha = 0.5, linewidth = 0.8, color = "#8B4513") +
  geom_vline(xintercept = 0.4, linetype = "dashed", color = "grey40") +
  ggplot2::annotate("text", x = 0.42, y = 0, label = "Exemplar\nthreshold", size = 3, hjust = 0) +
  labs(title = "Topic Concentration per Document",
       subtitle = "Higher = article dominated by single topic; dashed line = 40% exemplar threshold",
       x = "Dominant Topic Proportion", y = "Density") +
  theme_minimal(base_size = 12) +
  scale_x_continuous(labels = percent_format())

p1 / p2
```

### Effective Number of Topics

```{r effective-topics-we, fig.width=10, fig.height=5}
pub_topic_dist <- doc_topics %>%
  summarize(across(starts_with("Topic"), mean)) %>%
  pivot_longer(everything(), names_to = "topic", values_to = "prevalence") %>%
  mutate(
    topic_num = as.integer(str_remove(topic, "Topic")),
    label = str_trunc(topic_labels[topic_num], 25)
  )

eff_topics <- pub_topic_dist %>%
  filter(prevalence > 0) %>%
  summarize(eff = exp(-sum(prevalence * log(prevalence)))) %>%
  pull(eff)

cat(sprintf("Effective number of topics: %.1f (of %d)\n\n", eff_topics, chosen_K))

ggplot(pub_topic_dist, aes(x = reorder(label, -prevalence), y = prevalence)) +
  geom_col(fill = "#CD661D", alpha = 0.8) +
  labs(title = "Topic Weight Distribution — Woman's Exponent",
       subtitle = paste0("Effective topics: ", round(eff_topics, 1), " of ", chosen_K),
       x = NULL, y = "Mean Proportion") +
  theme_minimal(base_size = 10) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8)) +
  scale_y_continuous(labels = percent_format())
```

---

## 38. Topic Prevalence Heatmap Over Time

```{r topic-heatmap-time, fig.width=12, fig.height=7}
yearly_topics_we <- doc_topics %>%
  filter(!is.na(year)) %>%
  select(year, starts_with("Topic")) %>%
  group_by(year) %>%
  summarize(across(starts_with("Topic"), mean), .groups = "drop") %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "prevalence") %>%
  mutate(
    topic_num = as.integer(str_remove(topic, "Topic")),
    short_label = paste0("T", topic_num, ": ", str_trunc(topic_labels[topic_num], 20))
  )

ggplot(yearly_topics_we, aes(x = year, y = short_label, fill = prevalence)) +
  geom_tile(color = "white", linewidth = 0.3) +
  scale_fill_gradient(low = "white", high = "#8B4513",
                      labels = percent_format()) +
  labs(title = "Topic Prevalence Over Time — Woman's Exponent",
       subtitle = "Darker = higher prevalence in that year",
       x = "Year", y = NULL, fill = "Prevalence") +
  theme_minimal(base_size = 11) +
  theme(panel.grid = element_blank(),
        plot.title = element_text(face = "bold", size = 14)) +
  scale_y_discrete(limits = rev) +
  scale_x_continuous(breaks = sort(unique(yearly_topics_we$year)))
```

---

## 39. Topic Percentage Change (Early vs Late Era)

```{r topic-era-change, fig.width=12, fig.height=8}
cat(rep("=", 70), "\n", sep = "")
cat("PERCENTAGE CHANGE IN TOPICS: EARLY vs LATE ERA\n")
cat(rep("=", 70), "\n\n", sep = "")

era_means <- doc_topics_era %>%
  group_by(era) %>%
  summarize(across(starts_with("Topic"), mean), .groups = "drop") %>%
  pivot_longer(-era, names_to = "topic", values_to = "prevalence") %>%
  mutate(topic_num = as.integer(str_remove(topic, "Topic"))) %>%
  pivot_wider(names_from = era, values_from = prevalence)

era_change <- era_means %>%
  mutate(
    label = topic_labels[topic_num],
    early_pct = Early * 100,
    late_pct = Late * 100,
    abs_change = late_pct - early_pct,
    pct_change = ifelse(Early > 0.001,
                        (Late - Early) / Early * 100,
                        NA_real_),
    direction = case_when(
      abs_change > 0.5  ~ "Grew in Late Period",
      abs_change < -0.5 ~ "Declined in Late Period",
      TRUE ~ "Stable"
    )
  ) %>%
  arrange(desc(abs_change))

cat(sprintf("Era split: Early (≤%d) vs Late (>%d)\n\n", median_year, median_year))
cat(sprintf("%-35s  %7s  %7s  %8s  %9s\n",
            "Topic", "Early%", "Late%", "Change", "% Change"))
cat(rep("-", 80), "\n", sep = "")
for (i in 1:nrow(era_change)) {
  r <- era_change[i, ]
  pct_str <- ifelse(is.na(r$pct_change), "N/A", sprintf("%+.0f%%", r$pct_change))
  cat(sprintf("%-35s  %5.1f%%  %5.1f%%  %+6.1fpp  %9s\n",
              str_trunc(r$label, 35), r$early_pct, r$late_pct, r$abs_change, pct_str))
}

p_abs <- era_change %>%
  mutate(display = paste0("T", topic_num, ": ", str_trunc(label, 28)),
         display = reorder(display, abs_change)) %>%
  ggplot(aes(x = abs_change, y = display, fill = direction)) +
  geom_col(alpha = 0.85) +
  geom_vline(xintercept = 0, linewidth = 1) +
  scale_fill_manual(values = c("Grew in Late Period" = "#458B74",
                                "Declined in Late Period" = "#CD661D",
                                "Stable" = "#94a3b8")) +
  labs(title = paste0("Topic Change: Early (≤", median_year,
                      ") vs Late (>", median_year, ") Period"),
       subtitle = "Absolute change in percentage points of topic prevalence",
       x = "Change (percentage points)", y = NULL, fill = NULL) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom", panel.grid.major.y = element_blank())

print(p_abs)
```

```{r topic-era-change-relative, fig.width=12, fig.height=8}
era_change_filtered <- era_change %>%
  filter(!is.na(pct_change), abs(pct_change) < 500) %>%
  mutate(display = paste0("T", topic_num, ": ", str_trunc(label, 28)),
         display = reorder(display, pct_change))

if (nrow(era_change_filtered) > 0) {
  ggplot(era_change_filtered, aes(x = pct_change, y = display, fill = direction)) +
    geom_col(alpha = 0.85) +
    geom_vline(xintercept = 0, linewidth = 1) +
    scale_fill_manual(values = c("Grew in Late Period" = "#458B74",
                                  "Declined in Late Period" = "#CD661D",
                                  "Stable" = "#94a3b8")) +
    labs(title = "Relative Percentage Change in Topic Prevalence",
         subtitle = paste0("How much did each topic grow or shrink relative to its early-period (≤",
                           median_year, ") baseline?"),
         x = "Relative Change (%)", y = NULL, fill = NULL) +
    theme_minimal(base_size = 11) +
    theme(legend.position = "bottom", panel.grid.major.y = element_blank())
}
```

---

## 40. Topic Evolution Summary

```{r evolution-summary, fig.width=10, fig.height=10}
cat(rep("=", 70), "\n", sep = "")
cat("TOPIC EVOLUTION SUMMARY\n")
cat(rep("=", 70), "\n\n", sep = "")

topic_evolution <- era_change %>%
  mutate(
    evolution_type = case_when(
      abs(abs_change) <= 0.5 ~ "Stable",
      abs_change > 0.5  ~ "Growing",
      abs_change < -0.5 ~ "Declining"
    ),
    evolution_type = factor(evolution_type,
                            levels = c("Stable", "Growing", "Declining"))
  )

cat("TOPIC EVOLUTION CLASSIFICATION:\n\n")
for (etype in c("Stable", "Growing", "Declining")) {
  cat(toupper(etype), ":\n")
  subset_ev <- topic_evolution %>% filter(evolution_type == etype)
  if (nrow(subset_ev) > 0) {
    for (i in 1:nrow(subset_ev)) {
      r <- subset_ev[i, ]
      cat(sprintf("  T%d: %s (Early: %.1f%%, Late: %.1f%%, %+.1fpp)\n",
                  r$topic_num, r$label, r$early_pct, r$late_pct, r$abs_change))
    }
  } else {
    cat("  (none)\n")
  }
  cat("\n")
}

ggplot(topic_evolution, aes(x = early_pct, y = late_pct, color = evolution_type)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed",
              color = "grey70", linewidth = 1) +
  geom_point(size = 5, alpha = 0.8) +
  geom_text_repel(aes(label = paste0("T", topic_num, ": ", str_trunc(label, 25))),
                  size = 3, max.overlaps = 20, show.legend = FALSE) +
  scale_color_manual(values = c(
    "Stable" = "#6495ED",
    "Growing" = "#458B74",
    "Declining" = "#CD661D"
  )) +
  labs(title = "Topic Evolution: Early vs Late Period",
       subtitle = paste0("Diagonal = no change | Above = grew in late period (",
                         median_year + 1, "-", max(meta$year, na.rm = TRUE),
                         ") | Below = declined"),
       x = paste0("Early Period Mean % (≤", median_year, ")"),
       y = paste0("Late Period Mean % (>", median_year, ")"),
       color = "Evolution Type") +
  theme_minimal(base_size = 13) +
  theme(legend.position = "bottom",
        plot.title = element_text(face = "bold", size = 16)) +
  coord_fixed()
```

---

## 41. Representative Passages

```{r representative-passages}
cat("REPRESENTATIVE PASSAGES PER TOPIC\n")
cat(rep("=", 70), "\n\n", sep = "")

for (t in 1:chosen_K) {
  cat("TOPIC", t, ":", topic_labels[t], "\n")
  cat(rep("-", 60), "\n", sep = "")

  top_docs <- topic_article_link %>%
    filter(topic_num == t) %>%
    head(3)

  topic_words <- tolower(all_top_words$frex[t, 1:15])

  for (j in 1:nrow(top_docs)) {
    fname <- top_docs$filename[j]
    title_str <- ifelse(is.na(top_docs$Title[j]), fname, top_docs$Title[j])

    match_file <- list.files(input_path, pattern = fixed(fname),
                             recursive = TRUE, full.names = TRUE)
    if (length(match_file) == 0) next

    full_text <- read_file(match_file[1])

    sentences <- str_split(full_text, "(?<=[.!?])\\s+")[[1]]
    sentences <- sentences[nchar(sentences) > 40 & nchar(sentences) < 500]

    if (length(sentences) == 0) next

    scores <- sapply(sentences, function(s) {
      words <- tolower(str_split(s, "\\s+")[[1]])
      sum(words %in% topic_words) / max(length(words), 1)
    })

    best_idx <- order(scores, decreasing = TRUE)[1]
    best_sentence <- str_squish(sentences[best_idx])

    cat(sprintf("\n  [%s] (%.1f%% Topic %d)\n",
                title_str, top_docs$proportion[j] * 100, t))
    cat("  \"", str_trunc(best_sentence, 300), "\"\n", sep = "")
  }
  cat("\n\n")
}
```

---

## 42. Export Results

```{r export-results}
full_export <- topic_article_link %>%
  mutate(proportion_pct = round(proportion * 100, 2))

write_csv(full_export,
          file.path(output_path, "topic_article_full_link.csv"))

exemplars <- topic_article_link %>%
  group_by(topic_num, topic_label) %>%
  slice_max(proportion, n = 25) %>%
  ungroup() %>%
  mutate(proportion_pct = round(proportion * 100, 2))

write_csv(exemplars,
          file.path(output_path, "topic_exemplar_articles.csv"))

topic_summary <- tibble(
  topic_num = 1:chosen_K,
  label = topic_labels,
  prevalence_pct = round(topic_props * 100, 2),
  frex_words = apply(all_top_words$frex, 1, function(x) paste(x, collapse = ", ")),
  prob_words = apply(all_top_words$prob, 1, function(x) paste(x, collapse = ", "))
)

write_csv(topic_summary,
          file.path(output_path, "topic_summary.csv"))

write_csv(dominant_topics,
          file.path(output_path, "dominant_topic_per_article.csv"))

strong_only <- dominant_topics %>% filter(strong_exemplar)
write_csv(strong_only,
          file.path(output_path, "strong_exemplars.csv"))

cat("Exported to:", output_path, "\n")
cat("  - topic_article_full_link.csv (all doc-topic proportions)\n")
cat("  - topic_exemplar_articles.csv (top 25 articles per topic)\n")
cat("  - topic_summary.csv (labels + words)\n")
cat("  - dominant_topic_per_article.csv (each article tagged with its strongest topic)\n")
cat("  - strong_exemplars.csv (articles >", exemplar_threshold * 100, "% in their dominant topic)\n")
```

---

## 43. Read a Specific Article

```{r read-article-function}
read_article <- function(fname, input_dir = input_path) {
  match <- list.files(input_dir, pattern = fixed(fname), recursive = TRUE, full.names = TRUE)
  if (length(match) == 0) {
    cat("File not found:", fname, "\n")
    return(invisible(NULL))
  }
  txt <- read_file(match[1])
  cat(rep("=", 70), "\n", sep = "")
  cat("File:", fname, "\n")
  cat(rep("=", 70), "\n\n", sep = "")
  cat(substr(txt, 1, 2000), "\n\n...")
  return(invisible(txt))
}

# Example: read the top article from Topic 1
top1 <- topic_article_link %>% filter(topic_num == 1) %>% head(1)
read_article(top1$filename)
```

---

## 44. Save Session

```{r save-session}
save(stm_model, docs, vocab, meta, raw_texts, processed_texts,
     all_stopwords, topic_labels, topic_article_link,
     dominant_topics, inventory_subset,
     file = file.path(output_path, paste0("topic_linker_session_K", chosen_K, ".RData")))

cat("Session saved. Reload with:\n")
cat('  load("', file.path(output_path, paste0("topic_linker_session_K", chosen_K, ".RData")), '")\n', sep = "")
```

---

## Quick Reference

After running this notebook, use the exported CSVs:

- **`topic_exemplar_articles.csv`** - Top 25 articles for each topic (your best evidentiary examples).
- **`topic_article_full_link.csv`** - Full matrix of any article's topic distribution.
- **`topic_summary.csv`** - Quick reference for topic labels and key words.

To read a specific article in R:

```r
read_article("WE_Vol32_1903_Issue1_002_WOMANHOOD.txt")
```

```{r session-info}
sessionInfo()
```








