---
title: "Advanced Text Analysis - Woman's Exponent"
author: "Birch"
date: "`r Sys.Date()`"
output:
  html_notebook:
    toc: true
    toc_float: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.width = 10, fig.height = 7)
```

# Advanced Text Analysis - Woman's Exponent

This notebook is the **R reporting layer** of a two-part pipeline. The heavy
machine-learning work (transformer embeddings, a neural topic model, and
contextual diachronic semantic-change measurement) runs *outside* this knit, in
checkpointed Python scripts you launch from a terminal. This notebook does no
model training of its own: it **loads the finished artifacts** those scripts
wrote and turns them into figures and tables.

That split is deliberate. The previous version of this notebook re-derived the
corpus, trained word2vec models, and ran Procrustes alignment all inside the
knit — which is exactly what kept timing out. Now the slow work is decoupled,
resumable, and runs on its own schedule; the knit just reads Parquet/CSV files
and plots. **If a section's artifact is missing, that section prints a friendly
"run script X first" note and skips, rather than erroring.**

The five layers of analysis:

1. **Topic geometry** — Jensen-Shannon distances between STM topics as a
   prevalence-and-cluster bar chart, two MDS "four-quadrant" scatters (one labeled
   by topic, one by FREX words), and a `ggraph` co-occurrence network. *(Computed
   here in R from the STM model — fast, no Python needed.)*
2. **Document atlas + semantic search** — every article embedded with a
   sentence-transformer, laid out in 2D, and made searchable by meaning. §9c adds
   an **interactive article browser**: a full-text keyword search over every
   modeled article, labeled by dominant topic. *(Reads `embed_documents.py`
   output.)*
3. **BERTopic cross-check** — a neural topic model clustered over the same
   embeddings, cross-tabulated against STM to show where the two methods agree.
   *(Reads `run_bertopic.py` output.)*
4. **Diachronic semantic change** — for target words, how meaning moves across
   historical periods, measured three ways (PRT / APD / JSD) with MacBERTh, a
   BERT trained on historical English. *(Reads `semantic_change.py` output.)*
5. **Author topic profiles** — each prolific named author's mean STM topic mix as
   a stacked bar (vertical and horizontal layouts). *(Computed here in R.)*

> **The contextual-embedding approach (layer 4) is the frontier piece.** Instead
> of training a separate word2vec per period and rotating the spaces together
> (the old approach — fragile, and rotation-dependent), every occurrence of a
> word is embedded *in its sentence context* in a single pretrained historical
> space. No alignment is needed, and we recover genuine **sense-level** change,
> not just neighbor reshuffling. This is the SemEval-2020 Task 1 methodology.

---

## How to produce the inputs (read this first)

This notebook reads two families of files:

**A. Handoff from the STM linker** (`output_linked/`, suffixed by K):
`advanced_input_K{K}.rds`, `advanced_docs_K{K}.csv`, `advanced_theta_K{K}.csv`,
`advanced_topics_K{K}.csv`. Produced by `scripts/generate_handoff.R`, which reads
the linker's `topic_linker_session_K{K}.RData` and re-aligns each document to its
source text:

```text
"C:\Program Files\R\R-4.5.3\bin\Rscript.exe" scripts\generate_handoff.R 35
```

**B. Python compute artifacts** (`output_advanced_WE/`). From a terminal, using
the dedicated Python 3.11 venv (NOT system Python):

```text
C:\Users\birch\dh-env\Scripts\python.exe scripts\embed_documents.py   35
C:\Users\birch\dh-env\Scripts\python.exe scripts\run_bertopic.py      35
C:\Users\birch\dh-env\Scripts\python.exe scripts\semantic_change.py   35
C:\Users\birch\dh-env\Scripts\python.exe scripts\hybrid_search.py women right to vote   # on-demand, any query
```

The trailing `35` pins K=35 (the canonical model). Omit it and the scripts use
the newest `advanced_docs_K*.csv` they find. The first three are checkpointed and
resumable — if one stops, just run it again and it picks up where it left off.
Keyword + meaning search now lives **in the report**: §9c is a full-text article
browser (no script needed), and §9 finds meaning-neighbors of any article.
See `WEadvancedtextanalysis_handover.md` for a full setup + Python primer.

---

## 1. Packages

```{r install, eval=FALSE}
# Run once. arrow reads the Parquet files the Python layer writes; stylo is the
# modern stylometry toolkit (Burrows' Delta, bootstrap consensus trees).
install.packages(c(
  "arrow",         # read Parquet embedding files
  "philentropy",   # JSD distance
  "ggdendro",      # dendrogram in ggplot
  "dendextend",    # colored dendrogram branches
  "ggraph",        # network plots in ggplot
  "tidygraph",     # graph objects for ggraph
  "uwot",          # UMAP layout
  "stylo",         # Burrows' Delta + bootstrap consensus tree
  "jsonlite",      # read the periods sidecar
  "DT"             # interactive searchable result tables
))
```

```{r load-packages}
library(stm)
library(tidyverse)
library(scales)
library(ggrepel)
library(patchwork)
library(arrow)
library(philentropy)
library(ggdendro)
library(dendextend)
library(ggraph)
library(tidygraph)
library(igraph)
library(uwot)
library(jsonlite)
library(DT)

set.seed(12345)
cat("Packages loaded.\n")
```

---

## 2. Paths & K-agnostic model selection

We do **not** hardcode K. The loader discovers the available handoff files in
`output_linked/` and picks the requested K (or the newest one). Set
`pin_K <- 35L` to force the canonical model; leave it `NULL` to auto-pick.

```{r paths}
base_path   <- "C:/Users/birch/Rachel/GMU/Dissertation/textanalysis/Claudepythonexperimentadvtext"

# scenario: which corpus slice to report on. Must match the linker's "Scenario
# tag" and the Python ADV_SCENARIO. One of "WEfull" | "WE1872-1891" |
# "WE1892-1912", or a data-derived auto tag the linker printed.
scenario <- "WEfull"

linked_path <- file.path(base_path, "output_linked",      scenario)  # STM handoff
adv_path    <- file.path(base_path, "output_advanced_WE", scenario)  # Python artifacts
emb_dir     <- file.path(adv_path, "embeddings")
bertopic_dir<- file.path(adv_path, "bertopic")
diachr_dir  <- file.path(adv_path, "diachronic")
output_path <- file.path(adv_path, "report_figures")      # this notebook's PNG/CSV outputs
if (!dir.exists(output_path)) dir.create(output_path, recursive = TRUE)

pin_K <- NULL  # auto-picks the K in the selected scenario folder (each holds one K)

# Discover handoff files: advanced_input_K{K}.rds
input_candidates <- list.files(linked_path, pattern = "^advanced_input_K\\d+\\.rds$",
                               full.names = TRUE)
if (length(input_candidates) == 0) {
  stop("No advanced_input_K*.rds in ", linked_path,
       "\nRun the 'Checkpoint - Save Inputs for Advanced Analysis' chunk in ",
       "Topic_to_Article_Linker_WE.Rmd first.")
}
avail_K <- as.integer(str_match(basename(input_candidates), "_K(\\d+)\\.rds$")[, 2])

if (!is.null(pin_K)) {
  if (!pin_K %in% avail_K) {
    stop("Requested K=", pin_K, " not found. Available: ",
         paste(sort(avail_K), collapse = ", "),
         "\nProduce it by running the linker checkpoint chunk with chosen_K = ", pin_K, ".")
  }
  K <- pin_K
} else {
  # newest by mtime
  K <- avail_K[which.max(file.mtime(input_candidates))]
}
cat("Using K =", K, "  (available:", paste(sort(avail_K), collapse = ", "), ")\n")

# Helper: does an artifact exist? Used to gracefully skip sections.
have <- function(path) {
  ok <- file.exists(path)
  if (!ok) cat("  [skip] missing artifact:", basename(path), "\n")
  ok
}
```

---

## 3. Load the STM handoff

The linker's checkpoint chunk saved everything we need in one `.rds`: the fitted
STM model, the document metadata (`meta`, already row-aligned to `theta`), the
manual topic labels, and both the natural-language text (`modeled_raw`, for
stylometry and reading) and the cleaned bag-of-words (`modeled_clean`). Because
the linker aligned these at save time, **we never re-derive the corpus or guess
at row order** — the alignment problem that haunted the old notebook is gone.

```{r load-handoff}
adv_in <- readRDS(file.path(linked_path, sprintf("advanced_input_K%d.rds", K)))
model        <- adv_in$stm_model
meta         <- adv_in$meta            # row-aligned to model$theta
topic_labels_manual <- adv_in$topic_labels
modeled_raw  <- adv_in$modeled_raw     # natural-language article text
modeled_clean<- adv_in$modeled_clean   # cleaned bag-of-words

stopifnot(model$settings$dim$K == K,
          nrow(meta) == nrow(model$theta),
          length(modeled_raw) == nrow(meta))

vocab <- model$vocab
beta  <- exp(model$beta$logbeta[[1]])    # K x V topic-word probabilities
colnames(beta) <- vocab
theta <- model$theta                     # D x K document-topic probabilities

# Plot labels: prefer the manual labels from the linker, fall back to top words.
top_words <- labelTopics(model, n = 3)$prob |> apply(1, paste, collapse = " ")
topic_labels <- if (!is.null(topic_labels_manual) &&
                    length(topic_labels_manual) == K) {
  paste0("T", seq_len(K), ": ", topic_labels_manual)
} else {
  paste0("T", seq_len(K), ": ", top_words)
}
topic_prevalence <- colMeans(theta)

# Also load the flat docs CSV (row_index keyed) so we can join Python artifacts,
# which reference documents by the same row_index.
docs <- readr::read_csv(file.path(linked_path, sprintf("advanced_docs_K%d.csv", K)),
                        show_col_types = FALSE)
stopifnot(nrow(docs) == nrow(theta))

cat("K =", K, " | Vocab =", length(vocab), " | Documents =", nrow(theta), "\n")
cat("Year range:", paste(range(docs$year, na.rm = TRUE), collapse = "-"), "\n")
```

---

## 4. Topic Geometry I — Jensen-Shannon Distance Matrix

JSD between topic word-distributions is a proper, bounded distance — suitable
for both clustering and MDS. Computed in R directly from `beta`; no Python.

```{r jsd}
jsd <- function(p, q) {
  m <- 0.5 * (p + q)
  kl_pm <- sum(p * log((p + 1e-12) / (m + 1e-12)))
  kl_qm <- sum(q * log((q + 1e-12) / (m + 1e-12)))
  sqrt(0.5 * (kl_pm + kl_qm))
}

D_jsd <- matrix(0, K, K)
for (i in 1:K) for (j in 1:K) D_jsd[i, j] <- jsd(beta[i, ], beta[j, ])
rownames(D_jsd) <- colnames(D_jsd) <- paste0("T", 1:K)
cat("JSD matrix range:", round(range(D_jsd[D_jsd > 0]), 3), "\n")

# Number of topic clusters scales gently with K (cut height is taste, not law).
n_clusters <- max(4L, round(K / 7))
hc       <- hclust(as.dist(D_jsd), method = "ward.D2")
clusters <- cutree(hc, k = n_clusters)
cat("Topic clusters:", n_clusters, "\n")
```

---

## 5. Topic Geometry II — Topic Prevalence & Clusters

```{r dendrogram, fig.height=9}
# Bar chart (replaces the dendrogram): each topic's share of the corpus, with the
# topics ORDERED by the Ward/JSD clustering so similar topics sit next to each
# other, and COLORED by cluster. Bar length = prevalence; adjacency + color carry
# the grouping the dendrogram used to show, in a far more readable form.
ord <- order.dendrogram(as.dendrogram(hc))
hier_df <- tibble(
  label      = topic_labels,
  prevalence = topic_prevalence,
  cluster    = factor(clusters)
) |>
  mutate(label = factor(label, levels = topic_labels[ord]))

p_hier <- ggplot(hier_df, aes(prevalence, label, fill = cluster)) +
  geom_col(width = 0.8) +
  scale_fill_brewer(palette = "Set2") +
  scale_x_continuous(labels = scales::percent_format(accuracy = 0.1),
                     expand = expansion(mult = c(0, 0.05))) +
  labs(title = "Topic Prevalence & Clusters (Ward / Jensen-Shannon)",
       subtitle = "Bars ordered by JSD topic-similarity clustering; color = cluster; length = share of corpus",
       x = "Share of corpus", y = NULL, fill = "Cluster") +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold"),
        panel.grid.major.y = element_blank())

print(p_hier)
ggsave(file.path(output_path, "01_topic_prevalence_clusters.png"), p_hier,
       width = 12, height = 9, dpi = 150)
cat("Saved 01_topic_prevalence_clusters.png\n")
```

---

## 6. Topic Geometry III — MDS Four-Quadrant Plot

Classical MDS on the JSD matrix gives each topic a 2D coordinate. Axes are
derived dimensions; interpret them post-hoc from the anchoring topics printed
below.

```{r mds-quadrant, fig.height=9}
mds <- cmdscale(as.dist(D_jsd), k = 2)
mds_df <- tibble(
  topic = seq_len(K), Dim1 = mds[, 1], Dim2 = mds[, 2],
  prevalence = topic_prevalence, cluster = factor(clusters), label = topic_labels
)

p_mds <- ggplot(mds_df, aes(Dim1, Dim2)) +
  geom_hline(yintercept = 0, color = "gray60", linetype = "dashed") +
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
  geom_point(aes(size = prevalence, color = cluster), alpha = 0.85) +
  geom_text_repel(aes(label = label, color = cluster), size = 2.8,
                  max.overlaps = 40, box.padding = 0.4, show.legend = FALSE) +
  scale_size_continuous(range = c(3, 14), labels = percent_format(0.1)) +
  scale_color_brewer(palette = "Set2") +
  labs(title = "Topic Geometry - MDS on Jensen-Shannon Distance",
       subtitle = "Quadrant axes are derived dimensions; interpret post-hoc",
       x = "Dimension 1", y = "Dimension 2", size = "Prevalence", color = "Cluster") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold"))

print(p_mds)
ggsave(file.path(output_path, "02_mds_quadrant.png"), p_mds, width = 12, height = 9, dpi = 150)

# ---- Second view: SAME MDS layout, each topic labeled by its top FREX words ----
# (the words most distinctive to that topic) instead of the manual label — so the
# axes/quadrants can be read straight off vocabulary.
frex_words  <- apply(labelTopics(model, n = 3)$frex, 1, paste, collapse = ", ")
mds_df$frex <- frex_words

p_mds_frex <- ggplot(mds_df, aes(Dim1, Dim2)) +
  geom_hline(yintercept = 0, color = "gray60", linetype = "dashed") +
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
  geom_point(aes(size = prevalence, color = cluster), alpha = 0.85) +
  geom_text_repel(aes(label = frex, color = cluster), size = 2.5,
                  max.overlaps = 40, box.padding = 0.4, show.legend = FALSE) +
  scale_size_continuous(range = c(3, 14), labels = percent_format(0.1)) +
  scale_color_brewer(palette = "Set2") +
  labs(title = "Topic Geometry - MDS, labeled by FREX words",
       subtitle = "Same layout as above; each topic labeled by its most distinctive (FREX) words",
       x = "Dimension 1", y = "Dimension 2", size = "Prevalence", color = "Cluster") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold"))

print(p_mds_frex)
ggsave(file.path(output_path, "02b_mds_frex_words.png"), p_mds_frex, width = 12, height = 9, dpi = 150)
```

```{r mds-interpret}
ne <- 3
cat("=== INTERPRETING THE AXES (topic label + FREX words) ===\n")
for (ax in c("Dim1", "Dim2")) {
  hi <- mds_df |> slice_max(.data[[ax]], n = ne)
  lo <- mds_df |> slice_min(.data[[ax]], n = ne)
  cat("\n", ax, " - positive extreme:\n", sep = "")
  cat(paste0("  ", hi$label, "   [", hi$frex, "]"), sep = "\n")
  cat("\n", ax, " - negative extreme:\n", sep = "")
  cat(paste0("  ", lo$label, "   [", lo$frex, "]"), sep = "\n")
}
```

---

## 7. Topic Geometry IV — Co-occurrence Network

`stm::topicCorr()` measures whether topics *co-occur in the same articles* —
distinct from the JSD vocabulary similarity above.

```{r topic-network, fig.height=8}
tcorr <- topicCorr(model, method = "simple", cutoff = 0.05)
adj <- tcorr$cor; adj[abs(adj) < 0.05] <- 0; diag(adj) <- 0

g <- graph_from_adjacency_matrix(abs(adj), mode = "undirected", weighted = TRUE, diag = FALSE)
V(g)$prevalence <- topic_prevalence
V(g)$label <- topic_labels
V(g)$cluster <- factor(clusters)

p_net <- ggraph(as_tbl_graph(g), layout = "fr") +
  geom_edge_link(aes(width = weight, alpha = weight), color = "gray40") +
  geom_node_point(aes(size = prevalence, color = cluster), alpha = 0.9) +
  geom_node_text(aes(label = label), size = 2.6, repel = TRUE,
                 max.overlaps = 40, segment.alpha = 0.4) +
  scale_edge_width(range = c(0.2, 2)) + scale_edge_alpha(range = c(0.2, 0.8)) +
  scale_size_continuous(range = c(3, 12)) + scale_color_brewer(palette = "Set2") +
  labs(title = "Topic Co-occurrence Network",
       subtitle = "Edges = partial correlations of topic prevalence across documents (|r| > 0.05)",
       color = "Cluster", size = "Prevalence") +
  theme_void() + theme(plot.title = element_text(face = "bold"))

print(p_net)
ggsave(file.path(output_path, "03_topic_network.png"), p_net, width = 12, height = 9, dpi = 150)
```

---

## 8. Document Atlas (transformer embeddings)

Each article was embedded by `embed_documents.py` with a sentence-transformer
(`all-MiniLM-L6-v2`, 384-dim): long articles were split into word-windows,
each window embedded, then length-weighted mean-pooled back to one vector per
document. Here we lay those vectors out in 2D with UMAP and color by decade and
by dominant STM topic. Unlike the old topic-space UMAP, this places articles by
their *full semantic content*, independent of the STM model.

```{r doc-atlas, fig.height=8}
emb_path <- file.path(emb_dir, sprintf("doc_emb_K%d.parquet", K))
if (have(emb_path)) {
  emb_tbl <- read_parquet(emb_path) |> arrange(row_index)
  dim_cols <- grep("^dim_", names(emb_tbl), value = TRUE)
  X <- as.matrix(emb_tbl[, dim_cols])

  # Align doc metadata to the embedded rows (embeddings may be a dev subset).
  atlas_meta <- docs |> filter(row_index %in% emb_tbl$row_index) |> arrange(row_index)
  stopifnot(nrow(atlas_meta) == nrow(X))
  atlas_meta <- atlas_meta |>
    mutate(decade = floor(year / 10) * 10,
           dominant_topic = max.col(theta[match(row_index, docs$row_index), , drop = FALSE]))

  set.seed(12345)
  uu <- umap(X, n_neighbors = 15, min_dist = 0.1, metric = "cosine")
  atlas_meta$umap1 <- uu[, 1]; atlas_meta$umap2 <- uu[, 2]

  # ---- OPTION (a): de-blob the map by faceting into decade small-multiples ----
  # Same UMAP layout, split per decade so points don't pile up; color = dominant
  # STM topic. Reading: where each decade's articles sit, and how that shifts.
  p_atlas_a <- ggplot(atlas_meta, aes(umap1, umap2, color = factor(dominant_topic))) +
    geom_point(alpha = 0.6, size = 0.7) +
    facet_wrap(~ decade, ncol = 3) +
    scale_color_viridis_d(option = "turbo", guide = "none") +
    labs(title = "Article Atlas (a) — semantic map, faceted by decade",
         subtitle = "Each panel = one decade's articles in the SAME embedding layout; color = dominant STM topic",
         x = "UMAP 1", y = "UMAP 2") +
    theme_minimal(base_size = 11) + theme(plot.title = element_text(face = "bold"))
  print(p_atlas_a)
  ggsave(file.path(output_path, "04a_atlas_by_decade.png"), p_atlas_a,
         width = 12, height = 9, dpi = 150)

  # ---- OPTION (b): topic prevalence over time (theme-evolution view) ----
  # Doesn't use the embeddings at all — each STM topic's mean share of the
  # articles each year, as a stacked area. The most direct "how did themes shift".
  topic_year <- as.data.frame(theta) |>
    setNames(paste0("T", seq_len(ncol(theta)))) |>
    mutate(year = docs$year) |>
    filter(!is.na(year)) |>
    tidyr::pivot_longer(-year, names_to = "topic", values_to = "share") |>
    group_by(year, topic) |>
    summarise(share = mean(share), .groups = "drop") |>
    mutate(topic = factor(topic, levels = paste0("T", seq_len(ncol(theta)))))

  p_atlas_b <- ggplot(topic_year, aes(year, share, fill = topic)) +
    geom_area(position = "fill", color = "white", linewidth = 0.1) +
    scale_y_continuous(labels = percent_format()) +
    scale_fill_viridis_d(option = "turbo") +
    labs(title = "Article Atlas (b) — topic prevalence over time",
         subtitle = "Each band = an STM topic's share of that year's articles (themes rising/falling)",
         x = "Year", y = "Share of articles", fill = "Topic") +
    theme_minimal(base_size = 11) + theme(plot.title = element_text(face = "bold"))
  print(p_atlas_b)
  ggsave(file.path(output_path, "04b_topic_over_time.png"), p_atlas_b,
         width = 12, height = 8, dpi = 150)
} else {
  cat("Run:  python scripts\\embed_documents.py", K, "\n")
}
```

---

## 9. Semantic Search

The same embeddings make the corpus searchable *by meaning* rather than keyword.
Pick a query article (by `row_index`) and find its nearest neighbors by cosine
similarity — articles "about the same thing" even when they share no vocabulary.

```{r semantic-search}
if (exists("X")) {
  Xn <- X / sqrt(rowSums(X^2))          # L2-normalize rows -> cosine via dot product
  rownames(Xn) <- emb_tbl$row_index

  nearest_docs <- function(query_row_index, n = 8) {
    qi <- match(as.character(query_row_index), rownames(Xn))
    if (is.na(qi)) { cat("row_index", query_row_index, "not embedded\n"); return(invisible(NULL)) }
    sims <- as.vector(Xn %*% Xn[qi, ])
    ord  <- order(sims, decreasing = TRUE)
    ord  <- ord[ord != qi][1:n]
    atlas_meta |>
      slice(match(rownames(Xn)[ord], as.character(atlas_meta$row_index))) |>
      transmute(row_index, year, author, title,
                similarity = round(sims[ord], 3))
  }

  # Example: nearest neighbors of the first article that mentions "suffrage".
  seed_row <- docs |>
    filter(str_detect(str_to_lower(text), "\\bsuffrage\\b")) |>
    slice(1) |> pull(row_index)
  if (length(seed_row) == 1) {
    cat("Query article row_index =", seed_row, " | ",
        docs$title[match(seed_row, docs$row_index)], "\n\n")
    print(nearest_docs(seed_row, 8))
  }
} else {
  cat("Embeddings not loaded - run embed_documents.py first.\n")
}
```

---

## 9c. Interactive Article Browser (full-text keyword search)

The **Search** box (and the per-column filters) match the **full article text**
via the *Content* column — so you can keyword-search the body, not just the
title/metadata. Cells show the first 200 characters, but the search scans the
whole article. This is the in-report replacement for ad-hoc `hybrid_search.py`
queries. *(For meaning-based rather than literal-word search, use §9
`nearest_docs()` above.)*

```{r interactive-browser}
# ALL modeled articles (one row each), labeled with their dominant STM topic and
# that topic's share. Fully keyword-searchable on the Content (full body) column.
# Sort/filter by the Topic column to browse a single topic; search Content for
# keywords across the whole corpus. Built from the row-aligned theta (doc x topic)
# and docs (one row per modeled article) that §3 loaded.
.dom       <- max.col(theta)                                  # dominant topic per doc
.dom_share <- theta[cbind(seq_len(nrow(theta)), .dom)]        # that topic's share

browse_data <- tibble::tibble(
  Topic   = .dom,
  Label   = topic_labels[.dom],
  `%`     = round(.dom_share * 100, 1),
  Title   = docs$title,
  Author  = docs$author,
  Type    = docs$article_type,
  Volume  = docs$volume_num,
  Year    = docs$year,
  Content = stringr::str_squish(dplyr::coalesce(docs$text, "")),  # full body, searchable
  File    = docs$filename
)

# DataTables 0-based index of the Content column for the JS truncation renderer.
content_col <- which(names(browse_data) == "Content") - 1L

datatable(
  browse_data, filter = "top", rownames = FALSE,
  caption = paste0("ALL ", nrow(browse_data), " modeled articles, labeled by dominant topic. ",
                   "Search box matches the FULL article text (Content); sort/filter the Topic column to browse one topic."),
  options = list(
    pageLength = 20, scrollX = TRUE,
    # Show only the first 200 chars in the cell, but DataTables still SEARCHES the
    # full untruncated text (the 'filter' type receives the whole value).
    columnDefs = list(list(
      targets = content_col,
      render = DT::JS(
        "function(data, type, row) {",
        "  if (type === 'display' && data != null && data.length > 200) {",
        "    return data.substr(0, 200) + '…';",
        "  }",
        "  return data;",
        "}"
      )
    ))
  )
)
```

---

## 10. BERTopic Cross-Check vs STM

`run_bertopic.py` clustered the *same* document embeddings with BERTopic (UMAP +
HDBSCAN). BERTopic discovers its own number of topics bottom-up and labels some
documents as outliers (topic `-1`). We cross-tabulate BERTopic clusters against
each article's dominant STM topic: bright cells off the diagonal show where the
neural model splits or merges an STM topic — **triangulation, not replacement.**

```{r bertopic-crosstab, fig.height=9}
bt_docs_path   <- file.path(bertopic_dir, sprintf("bertopic_docs_K%d.csv", K))
bt_topics_path <- file.path(bertopic_dir, sprintf("bertopic_topics_K%d.csv", K))
if (have(bt_docs_path)) {
  bt_docs <- readr::read_csv(bt_docs_path, show_col_types = FALSE)

  stm_dom <- tibble(row_index = docs$row_index, stm_topic = max.col(theta))
  cmp <- bt_docs |> left_join(stm_dom, by = "row_index") |> filter(!is.na(stm_topic))

  n_out <- sum(cmp$bertopic_topic == -1)
  cat("BERTopic: ", dplyr::n_distinct(cmp$bertopic_topic[cmp$bertopic_topic >= 0]),
      "clusters | outliers:", n_out, "/", nrow(cmp), "\n")

  ct <- cmp |> filter(bertopic_topic >= 0) |>
    count(stm_topic, bertopic_topic) |>
    group_by(bertopic_topic) |> mutate(frac = n / sum(n)) |> ungroup()

  # Line chart (replaces the heatmap/bars): an AGREEMENT CURVE. Each BERTopic
  # cluster's "purity" = the share of its docs in its single most-common STM
  # topic. Sort clusters by purity and connect them: a curve that stays high =
  # the two methods mostly agree; a curve that drops steeply = many neural
  # clusters split across STM topics. Dashed line = 50% (a clean 1:1 match).
  purity <- ct |>
    group_by(bertopic_topic) |>
    slice_max(frac, n = 1, with_ties = FALSE) |>
    ungroup() |>
    arrange(desc(frac)) |>
    mutate(rank = row_number())

  p_ct <- ggplot(purity, aes(rank, frac)) +
    geom_hline(yintercept = 0.5, linetype = "dashed", color = "grey55") +
    geom_line(color = "#2C7FB8", linewidth = 1) +
    geom_point(aes(color = factor(stm_topic)), size = 2.6) +
    scale_y_continuous(labels = percent_format(), limits = c(0, 1)) +
    scale_color_viridis_d(option = "turbo", guide = "none") +
    labs(title = "BERTopic–STM agreement curve",
         subtitle = "Each point = a BERTopic cluster (sorted by purity); y = % of its docs in its top STM topic. Above the dashed 50% line = clean 1:1 mapping with an STM topic.",
         x = "BERTopic clusters, sorted by agreement", y = "Purity (share in top STM topic)") +
    theme_minimal(base_size = 11) +
    theme(plot.title = element_text(face = "bold"))
  print(p_ct)
  ggsave(file.path(output_path, "05_bertopic_vs_stm.png"), p_ct, width = 12, height = 8, dpi = 150)

  if (have(bt_topics_path)) {
    bt_topics <- readr::read_csv(bt_topics_path, show_col_types = FALSE)
    lab_col <- intersect(c("Name", "Representation"), names(bt_topics))[1]
    cat("\nTop BERTopic clusters:\n")
    bt_topics |> filter(Topic >= 0) |> arrange(desc(Count)) |> head(15) |>
      transmute(Topic, Count, label = .data[[lab_col]]) |> print()
  }
} else {
  cat("Run:  python scripts\\run_bertopic.py", K, "\n")
}
```

---

## 11. Diachronic Semantic Change (MacBERTh)

`semantic_change.py` measured, for each target word, how its meaning moves
across the historical periods, three complementary ways:

- **PRT** — prototype distance: `1 - cos` between period mean vectors. Coarse drift.
- **APD** — average pairwise distance: mean `1 - cos` over cross-period pairs.
  Sensitive to changes in *spread*, not just the centroid.
- **JSD** — Jensen-Shannon over induced word senses (KMeans on pooled
  occurrences). Captures change in the *mix of senses* a word is used in.

All three come from embedding each occurrence **in context** with MacBERTh
(historical-English BERT). Higher = more change between the two periods.

```{r diachronic-load}
change_path <- file.path(diachr_dir, sprintf("diachronic_change_K%d.csv", K))
proto_path  <- file.path(diachr_dir, sprintf("diachronic_prototypes_K%d.parquet", K))
periods_path<- file.path(diachr_dir, "diachronic_periods.json")
have_diachr <- have(change_path)
if (have_diachr) {
  change <- readr::read_csv(change_path, show_col_types = FALSE)
  if (file.exists(periods_path)) {
    pj <- fromJSON(periods_path)
    cat("Periods used:", paste(pj$periods$name, collapse = ", "), "\n")
  }
  cat("Comparisons:", nrow(change), "over",
      dplyr::n_distinct(change$word), "words\n")
} else {
  cat("Run:  python scripts\\semantic_change.py", K, "\n")
}
```

```{r diachronic-heatmap, eval=have_diachr, fig.height=8}
# Internal guard so "Run All Chunks" (which ignores eval=have_diachr) can't error.
if (!have_diachr) {
  cat("[skip] diachronic artifacts not computed for this scenario yet.\n")
} else {
# ONE line per change measure (names spelled out), instead of three bar panels.
# For each word we take its PEAK change across any period pair, then scale each
# measure 0-1 so the three sit comparably on one axis. Words sorted by APD.
#   PRT = Prototype distance | APD = Average Pairwise Distance | JSD = Jensen-Shannon Divergence
word_order <- change |> group_by(word) |> summarise(m = max(apd, na.rm = TRUE)) |>
  arrange(desc(m)) |> pull(word)   # most-changed first (also used by the drift plot)

measure_names <- c(prt = "Prototype distance (PRT)",
                   apd = "Average pairwise distance (APD)",
                   jsd = "Jensen-Shannon divergence (JSD)")

peak <- change |>
  group_by(word) |>
  summarise(prt = max(prt, na.rm = TRUE),
            apd = max(apd, na.rm = TRUE),
            jsd = max(jsd, na.rm = TRUE), .groups = "drop") |>
  pivot_longer(c(prt, apd, jsd), names_to = "measure", values_to = "peak") |>
  group_by(measure) |>
  mutate(scaled = (peak - min(peak)) / (max(peak) - min(peak) + 1e-12)) |>
  ungroup() |>
  mutate(word    = factor(word, levels = word_order),
         measure = factor(measure_names[measure], levels = measure_names))

# NOTE: x is WORDS, not time. Each value is a word's PEAK change across the period
# pairs, summarised to one number. (For the genuine temporal view see the
# "drift over time" chart below.) Words sorted by APD, most-changed first.

# (a) GROUPED BAR — magnitude per word, the three measures side by side.
p_bar <- ggplot(peak, aes(word, scaled, fill = measure)) +
  geom_col(position = position_dodge(width = 0.8), width = 0.72) +
  scale_fill_brewer(palette = "Dark2") +
  labs(title = "Diachronic change by word — ranked (bar)",
       subtitle = "Peak shift per word, each measure scaled 0-1. Sorted by APD; taller = more change.  PRT=centroid drift, APD=spread of usage, JSD=sense-mix.",
       x = NULL, y = "Relative change (0-1 within measure)", fill = "Measure") +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "top")
print(p_bar)
ggsave(file.path(output_path, "06_diachronic_change.png"), p_bar, width = 14, height = 8, dpi = 150)

# (b) DOT / LOLLIPOP — same numbers as dots, with a grey guide spanning each word's
# three measures. A WIDE gap between a word's dots = the measures DISAGREE (e.g.
# JSD high but PRT low = its sense-mix shifted more than its average meaning moved).
peak_range <- peak |> group_by(word) |>
  summarise(lo = min(scaled), hi = max(scaled), .groups = "drop")
p_dot <- ggplot(peak, aes(scaled, fct_rev(word))) +
  geom_segment(data = peak_range,
               aes(x = lo, xend = hi, y = fct_rev(word), yend = fct_rev(word)),
               inherit.aes = FALSE, color = "grey80", linewidth = 1.1) +
  geom_point(aes(color = measure), size = 3) +
  scale_color_brewer(palette = "Dark2") +
  labs(title = "Diachronic change by word — dot plot",
       subtitle = "Three measures per word; a wide spread between a word's dots = the measures disagree about HOW it changed.",
       x = "Relative change (0-1 within measure)", y = NULL, color = "Measure") +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold"))
print(p_dot)
ggsave(file.path(output_path, "06b_diachronic_change_dots.png"), p_dot, width = 12, height = 8, dpi = 150)
}
```

```{r diachronic-drift, eval=have_diachr, fig.height=8}
# Drift trajectories: project each word's per-period prototype vector through a
# shared PCA (fit on all prototypes), then connect periods in order.
if (have(proto_path)) {
  proto <- read_parquet(proto_path)
  pdim <- grep("^dim_", names(proto), value = TRUE)
  Pm <- as.matrix(proto[, pdim])
  pca <- prcomp(Pm, center = TRUE, scale. = FALSE)
  proto$PC1 <- pca$x[, 1]; proto$PC2 <- pca$x[, 2]

  # period order from the JSON sidecar if present, else alphabetical
  per_levels <- if (exists("pj")) pj$periods$name else sort(unique(proto$period))
  proto <- proto |> mutate(period = factor(period, levels = per_levels)) |>
    arrange(word, period)

  # Show the most-changed words for legibility.
  show_words <- head(word_order, 9)
  dd <- proto |> filter(word %in% show_words)

  p_drift <- ggplot(dd, aes(PC1, PC2, group = word, color = word)) +
    geom_path(arrow = arrow(length = unit(0.18, "cm"), type = "closed"),
              alpha = 0.8, linewidth = 0.7) +
    geom_point(aes(shape = period), size = 3) +
    geom_text_repel(aes(label = ifelse(period == per_levels[length(per_levels)] |
                                        period == per_levels[1], word, "")),
                    size = 3, max.overlaps = 30, show.legend = FALSE) +
    scale_color_brewer(palette = "Set1") +
    labs(title = "Diachronic Word Drift (MacBERTh prototypes)",
         subtitle = "Each path = one word's meaning trajectory across periods, in a shared PCA",
         x = "PC1", y = "PC2", color = "Word", shape = "Period") +
    theme_minimal(base_size = 12) + theme(plot.title = element_text(face = "bold"))
  print(p_drift)
  ggsave(file.path(output_path, "07_diachronic_drift.png"), p_drift, width = 12, height = 9, dpi = 150)
}
```

### Semantic drift over time

The genuine **temporal** view (the one the ranked charts above can't give): for the
most-changed words, each line is its **cosine distance from its earliest-period
meaning**, plotted across the periods. A line that **rises is drifting away** from
where it started; a **flat** line is stable; the steeper the climb, the faster the
change. Same MacBERTh prototypes as the 2-D drift map, read as "how far from the
start, over time."

```{r diachronic-over-time, eval=have_diachr, fig.height=7}
if (!have_diachr || !have(proto_path)) {
  cat("[skip] need diachronic prototypes for the over-time chart.\n")
} else {
  proto_ot   <- read_parquet(proto_path)
  pdim_ot    <- grep("^dim_", names(proto_ot), value = TRUE)
  per_levels <- if (exists("pj")) pj$periods$name else sort(unique(proto_ot$period))
  show_words <- head(word_order, 9)             # word_order from the chunk above

  drift_ot <- proto_ot |>
    filter(word %in% show_words) |>
    mutate(period = factor(period, levels = per_levels)) |>
    filter(!is.na(period)) |>
    arrange(word, period) |>
    group_by(word) |>
    group_modify(~{
      M  <- as.matrix(.x[, pdim_ot])
      Mn <- M / sqrt(rowSums(M^2))              # L2-normalize -> cosine via dot product
      tibble(period = .x$period, dist = 1 - as.vector(Mn %*% Mn[1, ]))
    }) |>
    ungroup()

  # Label each line directly at its last period (and drop the color legend) so you
  # don't have to match colors to names.
  ends <- drift_ot |> group_by(word) |>
    slice_max(as.integer(period), n = 1, with_ties = FALSE) |> ungroup()
  p_ot <- ggplot(drift_ot, aes(period, dist, group = word, color = word)) +
    geom_line(linewidth = 0.9) +
    geom_point(size = 2.6) +
    ggrepel::geom_text_repel(data = ends, aes(label = word),
                             hjust = 0, direction = "y", nudge_x = 0.18, size = 3.2,
                             segment.alpha = 0.3, max.overlaps = 20, show.legend = FALSE) +
    scale_color_brewer(palette = "Paired", guide = "none") +
    scale_x_discrete(expand = expansion(mult = c(0.04, 0.22))) +
    labs(title = "Semantic drift over time (MacBERTh)",
         subtitle = paste0("Cosine distance from each word's earliest-period meaning (",
                           per_levels[1], "). Rising = drifting away; flat = stable."),
         x = "Period", y = "Distance from earliest period") +
    theme_minimal(base_size = 12) +
    theme(plot.title = element_text(face = "bold"))
  print(p_ot)
  ggsave(file.path(output_path, "07b_diachronic_over_time.png"), p_ot,
         width = 12, height = 7, dpi = 150)
}
```

---

## 11b. Within-Topic Vocabulary Changepoints

For each STM topic, find the year that most sharply splits its **vocabulary**
(maximizing Jensen-Shannon divergence between the pooled word distributions
before vs. after), then show which words rose or fell across that split — the
topic-level companion to §11's word-level diachrony. Built from the row-aligned
`theta` + `docs$year` + `modeled_clean` (the already-cleaned bag-of-words), so it
works for whatever scenario is loaded. Detection is **cached** to an `.rds`, so
the first knit takes a few minutes and re-knits are instant.

```{r vocab-changepoint, fig.width=14, fig.height=22}
# ---- helpers --------------------------------------------------------------
.row_words <- function(rows) {                       # cleaned words for doc rows
  w <- unlist(strsplit(paste(modeled_clean[rows], collapse = " "), "\\s+"))
  w[nchar(w) >= 4]                                   # already stopworded/lemmatized
}
.js_divergence <- function(wa, wb) {
  if (length(wa) < 50 || length(wb) < 50) return(0)
  vu <- union(unique(wa), unique(wb))
  pa <- as.numeric(table(factor(wa, levels = vu))) / length(wa)
  pb <- as.numeric(table(factor(wb, levels = vu))) / length(wb)
  m  <- (pa + pb) / 2; eps <- 1e-12
  kl <- function(p, q) sum(p * log2((p + eps) / (q + eps)), na.rm = TRUE)
  (kl(pa, m) + kl(pb, m)) / 2
}
.yr <- docs$year
find_cp <- function(t, min_side = 15) {
  thr  <- stats::quantile(theta[, t], 0.75, na.rm = TRUE)
  rows <- which(theta[, t] >= thr & !is.na(.yr))
  if (length(rows) < 2 * min_side) return(list(year = NA_integer_, max_div = NA_real_))
  ry   <- .yr[rows]
  cand <- sort(unique(ry))
  cand <- cand[vapply(cand, function(y)
    sum(ry <= y) >= min_side && sum(ry > y) >= min_side, logical(1))]
  if (!length(cand)) return(list(year = NA_integer_, max_div = NA_real_))
  divs <- vapply(cand, function(y)
    .js_divergence(.row_words(rows[ry <= y]), .row_words(rows[ry > y])), numeric(1))
  list(year = as.integer(cand[which.max(divs)]), max_div = max(divs))
}
side_words <- function(t, split, side) {
  thr  <- stats::quantile(theta[, t], 0.75, na.rm = TRUE)
  rows <- which(theta[, t] >= thr & !is.na(.yr))
  rows <- if (side == "early") rows[.yr[rows] <= split] else rows[.yr[rows] > split]
  f <- sort(table(.row_words(rows)), decreasing = TRUE)
  tibble(word = names(f), proportion = as.integer(f) / sum(f))
}

# ---- detect (cached) ------------------------------------------------------
cp_rds <- file.path(output_path, sprintf("topic_changepoints_K%d.rds", K))
if (file.exists(cp_rds)) {
  changepoints <- readRDS(cp_rds); cat("Loaded cached changepoints.\n")
} else {
  cat("Detecting vocabulary changepoints for", ncol(theta), "topics (one-time)...\n")
  changepoints <- lapply(seq_len(ncol(theta)), function(t) {
    cp <- find_cp(t)
    cat(sprintf("  T%-2d %-36s %s\n", t, str_trunc(topic_labels[t], 34),
                if (is.na(cp$year)) "(too few docs)" else sprintf("split %d (JS %.3f)", cp$year, cp$max_div)))
    cp
  })
  saveRDS(changepoints, cp_rds)
}

# ---- summary table --------------------------------------------------------
cp_df <- tibble(topic = seq_len(ncol(theta)), label = topic_labels,
                prevalence = topic_prevalence,
                split_year = vapply(changepoints, function(x) x$year, integer(1)),
                max_jsd    = vapply(changepoints, function(x) x$max_div, numeric(1))) |>
  arrange(desc(prevalence))
print(cp_df, n = Inf)
write_csv(cp_df, file.path(output_path, sprintf("topic_changepoints_K%d.csv", K)))

# ---- per-topic before/after word-shift plots, 4 per page ------------------
ord <- order(topic_prevalence, decreasing = TRUE)
vocab_plots <- lapply(ord, function(t) {
  cp <- changepoints[[t]]
  if (is.na(cp$year))
    return(ggplot() + annotate("text", x = 0, y = 0, size = 6,
                               label = paste0("T", t, ": insufficient data")) + theme_void())
  sy <- cp$year
  cmpw <- full_join(
    side_words(t, sy, "early") |> rename(early = proportion),
    side_words(t, sy, "late")  |> rename(late  = proportion), by = "word") |>
    replace_na(list(early = 1e-4, late = 1e-4)) |>
    mutate(lr = log2(early / late), avg = (early + late) / 2) |>
    filter(avg > 0.001) |> arrange(desc(abs(lr)))
  el <- paste0("More ≤", sy); ll <- paste0("More >", sy)
  pw <- bind_rows(head(filter(cmpw, lr > 0), 15), head(filter(cmpw, lr < 0), 15)) |>
    mutate(direction = ifelse(lr > 0, el, ll), word = reorder(word, lr))
  ggplot(pw, aes(lr, word, fill = direction)) +
    geom_col(alpha = 0.85) + geom_vline(xintercept = 0, linewidth = 0.8) +
    scale_fill_manual(values = setNames(c("#6E8B3D", "#556B2F"), c(el, ll))) +
    labs(title = paste0("T", t, ": ", str_trunc(topic_labels[t], 45)),
         subtitle = sprintf("Changepoint %d  |  JSD %.2f  |  prevalence %.1f%%",
                            sy, cp$max_div, topic_prevalence[t] * 100),
         x = paste0("← after ", sy, "     before ", sy, " →"), y = NULL, fill = NULL) +
    theme_minimal(base_size = 10) +
    theme(legend.position = "none", plot.title = element_text(size = 12, face = "bold"))
})

per_page <- 4L; n_pages <- ceiling(length(vocab_plots) / per_page)
for (pg in seq_len(n_pages)) {
  s <- (pg - 1) * per_page + 1; e <- min(s + per_page - 1, length(vocab_plots))
  comb <- wrap_plots(vocab_plots[s:e], ncol = 2) +
    plot_annotation(title = sprintf("Within-Topic Vocabulary Changepoints — page %d of %d", pg, n_pages))
  print(comb)
  ggsave(file.path(output_path, sprintf("08_vocab_changepoint_K%d_page%d.png", K, pg)),
         comb, width = 14, height = 22, dpi = 150, limitsize = FALSE)
}
cat("\nSaved", n_pages, "changepoint page(s).\n")
```

---

## 12. Author Topic Profiles

For each prolific *named* author, what do they tend to write *about*? This shows
each author's **mean topic mix** — the average STM topic proportions across all
their articles — as a stacked bar (each bar sums to 100%), in both a vertical
(author-comparison) and horizontal (label-reading) layout.

*(This replaced a Burrows' Delta stylometry section. Stylometric authorship
attribution needs far more text per author than these era slices provide, whereas
topic profiles are robust at any size and answer the more useful "who wrote about
what" question. A cross-corpus version like Chart 5 — WE next to RSM — lives in the
joint comparison report, §6b.)*

We restrict to the most prolific named authors (>= 10 substantial articles each)
so the profiles are stable.

```{r stylo-prep}
# Build a per-author sample from the natural-language text (modeled_raw).
# Exclude non-author bylines: "Unknown", the periodical name, OCR/column junk
# (anything bracketed), and initials-only signatures (no real surname), since
# those would pollute the authorship clustering.
author_blocklist <- c("unknown", "editor", "the editor", "selected", "anonymous")
# Organizational / advertisement / masthead bylines that aren't personal authors.
org_keywords <- "exponent|publisher|office|ticket|company|\\bco\\b|union|depot|emporium|store|bureau|society|association|department"
is_real_author <- function(a) {
  s  <- str_squish(a)
  al <- str_replace_all(str_to_lower(s), "[’‘']", "'")  # normalize curly quotes
  has_surname <- str_detect(s, "[A-Za-z]{3,}")        # at least one 3+ letter word
  !is.na(a) & s != "" & !str_starts(s, "\\[") & !str_ends(s, ",") &
    !(al %in% author_blocklist) & !str_detect(al, org_keywords) & has_surname
}

sty_tbl <- docs |>
  mutate(text = modeled_raw,
         n_words = str_count(text, "\\S+"),
         author_clean = str_squish(author)) |>
  filter(is_real_author(author_clean), n_words >= 150)

top_authors <- sty_tbl |> count(author_clean, sort = TRUE) |>
  filter(n >= 10) |> slice_head(n = 12) |> pull(author_clean)
cat("Most prolific named authors used for stylometry:\n")
print(top_authors)

# Concatenate each author's articles into a few labeled samples for stylo.
# stylo wants a named list of long character strings (one "text" per sample).
make_samples_per_author <- function(df, max_words = 5000) {
  out <- list()
  for (a in top_authors) {
    txt <- df |> filter(author_clean == a) |> pull(text) |> paste(collapse = " ")
    words <- str_split(txt, "\\s+")[[1]]
    words <- words[words != ""]
    # split into ~max_words chunks so each author yields 2-4 comparable samples
    n_chunk <- max(1, floor(length(words) / max_words))
    n_chunk <- min(n_chunk, 4)
    if (n_chunk < 1) next
    sizes <- rep(floor(length(words) / n_chunk), n_chunk)
    idx <- c(0, cumsum(sizes))
    for (i in seq_len(n_chunk)) {
      seg <- words[(idx[i] + 1):idx[i + 1]]
      key <- sprintf("%s_%d", str_replace_all(a, "[^A-Za-z]", ""), i)
      out[[key]] <- paste(seg, collapse = " ")
    }
  }
  out
}
sty_samples <- make_samples_per_author(sty_tbl)
cat("\nStylometry samples:", length(sty_samples),
    "from", length(top_authors), "authors\n")
```

```{r stylo-delta, fig.height=10}
if (length(top_authors) >= 1) {
  # For each prolific named author, the MEAN topic mix across their articles, from
  # the row-aligned theta (doc x topic). Stacked bar per author -> sums to 100%.
  prof <- purrr::map_dfr(top_authors, function(a) {
    rows <- sty_tbl$row_index[sty_tbl$author_clean == a]
    tibble(author     = a,
           n_articles = length(rows),
           topic      = factor(topic_labels, levels = topic_labels),
           prop       = colMeans(theta[rows, , drop = FALSE]))
  })
  # Most prolific first.
  auth_order <- prof |> distinct(author, n_articles) |> arrange(desc(n_articles)) |> pull(author)
  prof <- prof |> mutate(author = factor(author, levels = auth_order))

  prof_sub <- paste0("Mean topic mix per prolific named author  (",
                     length(top_authors), " authors, >= 10 articles each)")

  # (a) VERTICAL — authors as columns, topics stacked to 100% (the "Chart 5" view).
  p_prof_v <- ggplot(prof, aes(author, prop, fill = topic)) +
    geom_col(width = 0.85, position = "stack") +
    scale_y_continuous(labels = percent_format(), expand = expansion(mult = c(0, 0.02))) +
    scale_fill_viridis_d(option = "turbo") +
    labs(title = "Author topic profiles (vertical)", subtitle = prof_sub,
         x = NULL, y = "Mean topic proportion", fill = "Topic") +
    theme_minimal(base_size = 11) +
    theme(plot.title = element_text(face = "bold"),
          axis.text.x = element_text(angle = 45, hjust = 1),
          legend.text = element_text(size = 7), legend.key.size = unit(0.4, "cm"))
  print(p_prof_v)
  ggsave(file.path(output_path, "09_author_topic_profiles_vertical.png"), p_prof_v,
         width = 13, height = 8, dpi = 150)

  # (b) HORIZONTAL — authors as rows (easier label-reading with many authors/topics).
  p_prof_h <- ggplot(prof, aes(prop, factor(author, levels = rev(auth_order)), fill = topic)) +
    geom_col(width = 0.85, position = "stack") +
    scale_x_continuous(labels = percent_format(), expand = expansion(mult = c(0, 0.02))) +
    scale_fill_viridis_d(option = "turbo") +
    labs(title = "Author topic profiles (horizontal)", subtitle = prof_sub,
         x = "Mean topic proportion", y = NULL, fill = "Topic") +
    theme_minimal(base_size = 11) +
    theme(plot.title = element_text(face = "bold"),
          legend.text = element_text(size = 7), legend.key.size = unit(0.4, "cm"))
  print(p_prof_h)
  ggsave(file.path(output_path, "09_author_topic_profiles_horizontal.png"), p_prof_h,
         width = 13, height = 8, dpi = 150)

  # Each author's single dominant topic, as a table.
  prof |> group_by(author, n_articles) |>
    slice_max(prop, n = 1, with_ties = FALSE) |> ungroup() |>
    transmute(Author = author, Articles = n_articles,
              `Top topic` = as.character(topic), Share = scales::percent(prop, 0.1)) |>
    arrange(desc(Articles)) |> print(n = Inf)
} else {
  cat("No prolific named authors (>= 10 substantial articles) in this scenario --",
      "this slice is mostly institutional/unknown bylines. The full run has more.\n")
}
```

---

## 13. Save Session

```{r save-session}
saveRDS(list(
  K            = K,
  D_jsd        = D_jsd,
  hc           = hc,
  clusters     = clusters,
  mds_coords   = mds,
  topic_labels = topic_labels,
  fit_date     = Sys.time()
), file.path(output_path, sprintf("advanced_report_objects_K%d.rds", K)))
cat("Saved report objects for K =", K, "\n")
```

---

## Notes & Tuning Hints

- **K is not hardcoded.** Set `pin_K` in §2 to choose the model (35 is
  canonical). Every artifact path is suffixed by K, so K=20 dev runs and K=35
  production runs never collide. To switch K you (a) run the linker checkpoint
  chunk with the new `chosen_K`, then (b) re-run the three Python scripts with
  that K, then (c) re-knit with `pin_K` updated.
- **Graceful skipping.** Sections 8–11 check for their Python artifact and print
  a "run script X" note if it's missing, so the notebook always knits even
  before the compute layer has finished.
- **Why contextual embeddings for diachrony (§11).** Training one word2vec per
  period and Procrustes-rotating them (the old approach) is fragile: the
  rotation is fit on shared vocabulary and small periods give noisy spaces.
  MacBERTh embeds each occurrence in its sentence in a single pretrained space —
  no rotation, and we get sense-level change. Edit `DIACHRONIC_TARGETS` and
  `DEFAULT_PERIOD_BOUNDS` in `scripts/config.py` to change words/periods.
- **Author topic profiles (§12)** show each prolific named author's mean STM topic
  mix as a stacked bar — robust at any corpus size, unlike Burrows' Delta
  stylometry, which needs far more text per author than an era slice provides.
- **Compute layer is resumable.** Each Python script checkpoints; re-running
  after an interruption resumes. The knit itself never trains anything, so it
  won't time out.
```