---
title: "Advanced Text Analysis - Woman's Exponent"
author: "Birch"
date: "`r Sys.Date()`"
output:
  html_notebook:
    toc: true
    toc_float: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.width = 10, fig.height = 7)
```

# Advanced Text Analysis - Woman's Exponent

This notebook is the **R reporting layer** of a two-part pipeline. The heavy
machine-learning work (transformer embeddings, a neural topic model, and
contextual diachronic semantic-change measurement) runs *outside* this knit, in
checkpointed Python scripts you launch from a terminal. This notebook does no
model training of its own: it **loads the finished artifacts** those scripts
wrote and turns them into figures and tables.

That split is deliberate. The previous version of this notebook re-derived the
corpus, trained word2vec models, and ran Procrustes alignment all inside the
knit — which is exactly what kept timing out. Now the slow work is decoupled,
resumable, and runs on its own schedule; the knit just reads Parquet/CSV files
and plots. **If a section's artifact is missing, that section prints a friendly
"run script X first" note and skips, rather than erroring.**

The five layers of analysis:

1. **Topic geometry** — Jensen-Shannon distances between STM topics as a
   dendrogram, an MDS "four-quadrant" scatter, and a `ggraph` co-occurrence
   network. *(Computed here in R from the STM model — fast, no Python needed.)*
2. **Document atlas + semantic search** — every article embedded with a
   sentence-transformer, laid out in 2D, and made searchable by meaning. §9b adds
   **hybrid search**: a free-text query fuses literal keyword (BM25) and semantic
   ranking via Reciprocal Rank Fusion. *(Reads `embed_documents.py` /
   `hybrid_search.py` output.)*
3. **BERTopic cross-check** — a neural topic model clustered over the same
   embeddings, cross-tabulated against STM to show where the two methods agree.
   *(Reads `run_bertopic.py` output.)*
4. **Diachronic semantic change** — for target words, how meaning moves across
   historical periods, measured three ways (PRT / APD / JSD) with MacBERTh, a
   BERT trained on historical English. *(Reads `semantic_change.py` output.)*
5. **Stylometry** — Burrows' Delta and a bootstrap consensus tree over the most
   prolific authors, via the `stylo` package. *(Computed here in R.)*

> **The contextual-embedding approach (layer 4) is the frontier piece.** Instead
> of training a separate word2vec per period and rotating the spaces together
> (the old approach — fragile, and rotation-dependent), every occurrence of a
> word is embedded *in its sentence context* in a single pretrained historical
> space. No alignment is needed, and we recover genuine **sense-level** change,
> not just neighbor reshuffling. This is the SemEval-2020 Task 1 methodology.

---

## How to produce the inputs (read this first)

This notebook reads two families of files:

**A. Handoff from the STM linker** (`output_linked/`, suffixed by K):
`advanced_input_K{K}.rds`, `advanced_docs_K{K}.csv`, `advanced_theta_K{K}.csv`,
`advanced_topics_K{K}.csv`. Produced by `scripts/generate_handoff.R`, which reads
the linker's `topic_linker_session_K{K}.RData` and re-aligns each document to its
source text:

```text
"C:\Program Files\R\R-4.5.3\bin\Rscript.exe" scripts\generate_handoff.R 35
```

**B. Python compute artifacts** (`output_advanced_WE/`). From a terminal, using
the dedicated Python 3.11 venv (NOT system Python). Set the scenario first so each
run writes to its own subfolder:

```text
set ADV_SCENARIO=WEfull
C:\Users\birch\dh-env\Scripts\python.exe scripts\embed_documents.py        35
C:\Users\birch\dh-env\Scripts\python.exe scripts\run_bertopic.py           35
C:\Users\birch\dh-env\Scripts\python.exe scripts\semantic_change.py        35
C:\Users\birch\dh-env\Scripts\python.exe scripts\word_geometry_embeddings.py 35   # §6 word meaning-geometry (MacBERTh per-word)
```

The trailing number pins K (WEfull is K=35; the era scenarios WE1872-1891 and
WE1892-1912 use their own K). `ADV_SCENARIO` selects the subfolder under
`output_linked/` and `output_advanced_WE/`, so runs never overwrite each other.
Each script is checkpointed and resumable — if one stops, just run it again and it
picks up where it left off.
See `WEadvancedtextanalysis_handover.md` for a full setup + Python primer.

---

## 1. Packages

```{r install, eval=FALSE}
# Run once. arrow reads the Parquet files the Python layer writes; stylo is the
# modern stylometry toolkit (Burrows' Delta, bootstrap consensus trees).
install.packages(c(
  "arrow",         # read Parquet embedding files
  "philentropy",   # JSD distance
  "ggdendro",      # dendrogram in ggplot
  "dendextend",    # colored dendrogram branches
  "ggraph",        # network plots in ggplot
  "ggalluvial",    # alluvial / Sankey flow diagrams (STM <-> BERTopic)
  "tidygraph",     # graph objects for ggraph
  "uwot",          # UMAP layout
  "stylo",         # Burrows' Delta + bootstrap consensus tree
  "jsonlite",      # read the periods sidecar
  "DT",             # interactive searchable result tables
  "shiny",
  "plotly"
))
```

```{r load-packages}
library(stm)
library(tidyverse)
library(scales)
library(ggrepel)
library(patchwork)
library(arrow)
library(philentropy)
library(ggdendro)
library(dendextend)
library(ggraph)
library(ggalluvial)
library(tidygraph)
library(igraph)
library(uwot)
library(jsonlite)
library(DT)
library(shiny)
library(plotly)

set.seed(12345)
cat("Packages loaded.\n")
```

---

## 2. Paths & K-agnostic model selection

We do **not** hardcode K. The loader discovers the available handoff files in
`output_linked/<scenario>/` and picks the requested K (or the newest one). Set
`pin_K <- 35L` to force the canonical WEfull model; leave it `NULL` to auto-pick.

```{r paths}
base_path   <- "C:/Users/birch/Rachel/GMU/Dissertation/textanalysis/Claudepythonexperimentadvtext"

# scenario: which corpus slice to report on. Must match the linker's "Scenario
# tag" and the Python ADV_SCENARIO. One of "WEfull" | "WE1872-1891" | "WE1892-1912".
scenario <- "WE1892-1912"

linked_path <- file.path(base_path, "output_linked",      scenario)  # STM handoff
adv_path    <- file.path(base_path, "output_advanced_WE", scenario)  # Python artifacts
emb_dir     <- file.path(adv_path, "embeddings")
bertopic_dir<- file.path(adv_path, "bertopic")
diachr_dir  <- file.path(adv_path, "diachronic")
output_path <- file.path(adv_path, "report_figures")      # this notebook's PNG/CSV outputs
if (!dir.exists(output_path)) dir.create(output_path, recursive = TRUE)

pin_K <- 25L   # WEfull canonical; for an era scenario use its K (WE1892-1912=25, WE1872-1891=20). NULL auto-picks.

# Discover handoff files: advanced_input_K{K}.rds
input_candidates <- list.files(linked_path, pattern = "^advanced_input_K\\d+\\.rds$",
                               full.names = TRUE)
if (length(input_candidates) == 0) {
  stop("No advanced_input_K*.rds in ", linked_path,
       "\nRun the linker checkpoint in Topic_to_Article_Linker_WE.Rmd, ",
       "then scripts/generate_handoff.R first.")
}
avail_K <- as.integer(str_match(basename(input_candidates), "_K(\\d+)\\.rds$")[, 2])

if (!is.null(pin_K)) {
  if (!pin_K %in% avail_K) {
    stop("Requested K=", pin_K, " not found. Available: ",
         paste(sort(avail_K), collapse = ", "),
         "\nProduce it by saving the WE linker session at that chosen_K, then running generate_handoff.R ", pin_K, ".")
  }
  K <- pin_K
} else {
  # newest by mtime
  K <- avail_K[which.max(file.mtime(input_candidates))]
}
cat("Using K =", K, "  (available:", paste(sort(avail_K), collapse = ", "), ")\n")

# Helper: does an artifact exist? Used to gracefully skip sections.
have <- function(path) {
  ok <- file.exists(path)
  if (!ok) cat("  [skip] missing artifact:", basename(path), "\n")
  ok
}
```

---

## 3. Load the STM handoff

The linker's checkpoint chunk saved everything we need in one `.rds`: the fitted
STM model, the document metadata (`meta`, already row-aligned to `theta`), the
manual topic labels, and both the natural-language text (`modeled_raw`, for
stylometry and reading) and the cleaned bag-of-words (`modeled_clean`). Because
the linker aligned these at save time, **we never re-derive the corpus or guess
at row order** — the alignment problem that haunted the old notebook is gone.

```{r load-handoff}
adv_in <- readRDS(file.path(linked_path, sprintf("advanced_input_K%d.rds", K)))
model        <- adv_in$stm_model
meta         <- adv_in$meta            # row-aligned to model$theta
topic_labels_manual <- adv_in$topic_labels
modeled_raw  <- adv_in$modeled_raw     # natural-language article text
modeled_clean<- adv_in$modeled_clean   # cleaned bag-of-words

stopifnot(model$settings$dim$K == K,
          nrow(meta) == nrow(model$theta),
          length(modeled_raw) == nrow(meta))

vocab <- model$vocab
beta  <- exp(model$beta$logbeta[[1]])    # K x V topic-word probabilities
colnames(beta) <- vocab
theta <- model$theta                     # D x K document-topic probabilities

# Plot labels: prefer the manual labels from the linker, fall back to top words.
top_words <- labelTopics(model, n = 3)$prob |> apply(1, paste, collapse = " ")
topic_labels <- if (!is.null(topic_labels_manual) &&
                    length(topic_labels_manual) == K) {
  paste0("T", seq_len(K), ": ", topic_labels_manual)
} else {
  paste0("T", seq_len(K), ": ", top_words)
}
topic_prevalence <- colMeans(theta)

# Also load the flat docs CSV (row_index keyed) so we can join Python artifacts,
# which reference documents by the same row_index.
docs <- readr::read_csv(file.path(linked_path, sprintf("advanced_docs_K%d.csv", K)),
                        show_col_types = FALSE)
stopifnot(nrow(docs) == nrow(theta))

cat("K =", K, " | Vocab =", length(vocab), " | Documents =", nrow(theta), "\n")
cat("Year range:", paste(range(docs$year, na.rm = TRUE), collapse = "-"), "\n")
```

---

## 4. Topic Geometry I — Topic-Distance Matrix (theme or vocabulary)

Topic-to-topic distance, used for **both** the families and the MDS topic map.
Pick the basis with `family_basis` in the chunk:

- **`"theme"`** (semantic) — each topic is the mean *meaning* of its articles
  (their sentence-transformer doc embeddings, prevalence-weighted), so families
  group topics that are **about the same thing**, even with different words.
- **`"vocabulary"`** — Jensen-Shannon distance between topics' word distributions,
  so families group topics that **share words** (the original behaviour).

`"theme"` needs `doc_emb` present (from `embed_documents.py`); it auto-falls-back
to `"vocabulary"` if missing.

```{r jsd}
family_basis <- "theme"      # "theme" (semantic) or "vocabulary" (JSD on words)

# --- vocabulary distance: Jensen-Shannon between topic word distributions ------
jsd <- function(p, q) {
  m <- 0.5 * (p + q)
  kl_pm <- sum(p * log((p + 1e-12) / (m + 1e-12)))
  kl_qm <- sum(q * log((q + 1e-12) / (m + 1e-12)))
  sqrt(0.5 * (kl_pm + kl_qm))
}
D_vocab <- matrix(0, K, K)
for (i in 1:K) for (j in 1:K) D_vocab[i, j] <- jsd(beta[i, ], beta[j, ])

# --- theme distance: each topic = mean MEANING of its articles (doc embeddings) -
# Always computed (when doc_emb exists) so the theme-vs-vocabulary comparison below
# has both; the family_basis toggle just decides which one drives the families/map.
.emb_path  <- file.path(emb_dir, sprintf("doc_emb_K%d.parquet", K))
have_theme <- file.exists(.emb_path)
D_theme <- NULL
if (have_theme) {
  .e   <- arrow::read_parquet(.emb_path)
  .dc  <- grep("^dim_", names(.e), value = TRUE)
  .X   <- as.matrix(.e[, .dc]); .X <- .X / sqrt(rowSums(.X^2))      # L2-normalize doc vectors
  er   <- match(docs$row_index, .e$row_index)                      # theta row -> embedding row
  keep <- !is.na(er)
  Wt   <- theta[keep, , drop = FALSE]                              # docs x K (prevalence weights)
  Xe   <- .X[er[keep], , drop = FALSE]                             # docs x dim
  Tmean <- crossprod(Wt, Xe) / colSums(Wt)                         # K x dim: theta-weighted mean meaning
  Tn   <- Tmean / sqrt(rowSums(Tmean^2))
  D_theme <- 1 - (Tn %*% t(Tn)); diag(D_theme) <- 0                # cosine distance between topic THEMES
}
# Active distance for the families + MDS map, per the family_basis toggle.
if (family_basis == "theme" && have_theme) {
  D_jsd <- D_theme; basis_used <- "THEME (semantic — mean doc embedding per topic)"
} else {
  D_jsd <- D_vocab
  basis_used <- if (family_basis == "theme")
    "VOCABULARY (theme requested but doc_emb missing — run embed_documents.py; fell back)"
  else "VOCABULARY (Jensen-Shannon on words)"
}
rownames(D_jsd) <- colnames(D_jsd) <- paste0("T", 1:K)
cat("Family / geometry basis:", basis_used, "\n")
cat("Distance range:", round(range(D_jsd[row(D_jsd) != col(D_jsd)]), 3), "\n")

# Number of topic clusters scales gently with K (cut height is taste, not law).
n_clusters <- max(8L, round(K / 5))
hc       <- hclust(as.dist(D_jsd), method = "ward.D2")
clusters <- cutree(hc, k = n_clusters)

# >>> Manual family overrides (optional editorial fixes). After reading the
# silhouette diagnostic + family-examples, reassign any topic to a different
# family by its number — these flow through names, colors, and every plot.
clusters[12]  <- 6    # move topic 7 into family 3 (e.g. its nearest family)
clusters[21] <- 8
clusters[24] <- 7
clusters[7] <- 2
clusters[9] <- 2
clusters[2] <- 4
clusters[23] <- 2
clusters[2] <- 2
clusters[14] <- 1
clusters[8] <- 1



cat("Topic clusters:", n_clusters, "\n")
```

### Cluster membership & naming

Ward clustering grouped these topics **automatically** by vocabulary similarity;
the numbers are arbitrary IDs. Below, each cluster's member topics are printed so
you can give it a human name. Edit the `cluster_names` vector — any entry left
`""` falls back to an auto-name (the top words of that cluster's most prevalent
topic). The names you set here flow into the §5 bar chart's legend.

```{r cluster-naming}
# Which topics landed in each cluster (use this to decide a name).
for (cl in sort(unique(clusters))) {
  tt <- which(clusters == cl)
  cat(sprintf("\nCluster %d  (%d topics):\n", cl, length(tt)))
  cat(paste0("  ", topic_labels[tt]), sep = "\n")
}

# Auto-default: each cluster named by the top words of its MOST PREVALENT topic.
auto_cluster_names <- vapply(seq_len(n_clusters), function(cl) {
  tt   <- which(clusters == cl)
  lead <- tt[which.max(topic_prevalence[tt])]
  top_words[lead]
}, character(1))

# >>> EDIT ME: name each cluster. Index = cluster number; "" keeps the auto-name.
cluster_names <- setNames(rep("", n_clusters), seq_len(n_clusters))
# e.g.:
cluster_names["1"] <- "Famous Women"
cluster_names["2"] <- "Public Events"
cluster_names["3"] <- "Advertisements"
cluster_names["4"] <- "Print Culture"
cluster_names["5"] <- "Memoriam Resolutions"
cluster_names["6"] <- "Relief Society Projects"
cluster_names["7"] <- "Women's Rights"
cluster_names["8"] <- "Current Events"


# (re-derive for THIS corpus from the family-examples table below — WE K=35 has its
#  own cluster count/order, so don't reuse the RSM numbering)




# Final per-cluster label (named entry, else auto), prefixed Cn for reference.
cluster_label <- ifelse(nzchar(cluster_names), cluster_names, auto_cluster_names)
cluster_label <- paste0("C", seq_len(n_clusters), ": ", cluster_label)

# Factor mapping each TOPIC -> its (named) cluster label, reusable in any plot
# that currently uses `factor(clusters)` (e.g. §5, and optionally §6/§7).
cluster_named <- factor(cluster_label[clusters], levels = cluster_label)

# Per-topic family name (short, no "Cn:" prefix) for in-plot text tags, plus a
# combined "topic — family" label so every chart can show BOTH on its points.
family_short        <- sub("^C\\d+: ", "", cluster_label)   # length n_clusters
topic_family_short  <- family_short[clusters]               # length K
topic_with_family   <- paste0(topic_labels, "  ·  ", topic_family_short)

# ---- Canonical color palettes (so a topic/family keeps ONE color everywhere) --
# Per-topic palette: a fixed turbo color per topic, keyed three ways to match how
# different charts reference a topic (integer index, "T#", and full label). Using
# scale_*_manual(values = ...) with these guarantees topic i is the same color in
# §8, §10 and §12 even when a chart only shows a subset of topics.
.topic_cols   <- scales::viridis_pal(option = "turbo")(K)
topic_col_int <- setNames(.topic_cols, as.character(seq_len(K)))  # factor(dominant_topic) / stm_topic
topic_col_T   <- setNames(.topic_cols, paste0("T", seq_len(K)))   # "T1".."TK"
topic_col_lab <- setNames(.topic_cols, topic_labels)             # full topic labels
# Per-family palette: a fixed Set2 (ramped to n_clusters) color per family label.
family_cols   <- setNames(
  grDevices::colorRampPalette(RColorBrewer::brewer.pal(8, "Set2"))(n_clusters),
  cluster_label)

cat("\nCluster names in use:\n"); cat(paste0("  ", cluster_label), sep = "\n")
```

### Family coherence (silhouette diagnostic)

How well do the families actually hold together? Each topic gets a **silhouette
width**: roughly **+1** = it sits firmly inside its family, **~0** = it's on the
border between two families, **negative** = it's actually closer to a *different*
family (likely misgrouped). The per-family and overall averages tell you whether
the grouping is coherent; the flagged topics are the ones to eyeball. This reflects
whatever `family_basis` you chose — switching to `"theme"` usually lifts these.

```{r family-silhouette, fig.height=9}
.sil <- function(D, cl) {
  groups <- sort(unique(cl)); n <- length(cl)
  sw <- numeric(n); near <- integer(n)
  for (i in seq_len(n)) {
    same <- which(cl == cl[i]); same <- same[same != i]
    a  <- if (length(same)) mean(D[i, same]) else 0
    others <- setdiff(groups, cl[i])
    bv <- vapply(others, function(g) mean(D[i, cl == g]), numeric(1))
    sw[i]   <- if (length(bv) && max(a, min(bv)) > 0) (min(bv) - a) / max(a, min(bv)) else 0
    near[i] <- if (length(bv)) others[which.min(bv)] else cl[i]   # nearest OTHER family
  }
  list(sil = sw, near = near)
}
.s     <- .sil(D_jsd, clusters)
sil_df <- tibble(topic = seq_along(clusters), label = topic_labels, family = cluster_named,
                 `nearest other family` = cluster_label[.s$near], sil = round(.s$sil, 2)) |>
  arrange(family, sil)

cat(sprintf("Overall mean silhouette: %.2f   (>0.5 strong | 0.25-0.5 reasonable | <0.25 weak/overlapping)\n",
            mean(.s$sil)))
cat("\nPer-family coherence (lowest first):\n")
print(sil_df |> group_by(family) |>
        summarise(topics = dplyr::n(), mean_sil = round(mean(sil), 2), .groups = "drop") |>
        arrange(mean_sil))

poor <- sil_df |> filter(sil < 0.1)
if (nrow(poor)) {
  cat("\nPoorly-fit topics — and the family each is CLOSEST to (a candidate move):\n")
  print(poor |> select(topic, label, family, `nearest other family`, sil), n = Inf)
}

ggplot(sil_df, aes(stats::reorder(label, sil), sil, fill = family)) +
  geom_col(width = 0.8) + coord_flip() +
  geom_hline(yintercept = 0, linewidth = 0.3) +
  scale_fill_manual(values = family_cols) +
  labs(title = "Family coherence — silhouette per topic",
       subtitle = "High = fits its family well; near 0 = borderline; negative = closer to another family",
       x = NULL, y = "Silhouette width", fill = "Topic family") +
  theme_minimal(base_size = 9) +
  theme(plot.title = element_text(face = "bold"), legend.text = element_text(size = 7))
```

### Theme vs. vocabulary families — tanglegram

How grouping by **meaning** (doc embeddings) differs from grouping by **shared
words** (JSD), read off the `D_theme` and `D_vocab` matrices the `jsd` chunk already
computed — no re-running anything. Vocabulary tree on the left, theme tree on the
right, every topic linked across. **Straight** links = the topic clusters similarly
either way; **crossing** links = it regroups. Shared sub-branches are colored together.

```{r family-tanglegram, fig.width=13, fig.height=15}
if (exists("D_theme") && !is.null(D_theme) && requireNamespace("dendextend", quietly = TRUE)) {
  .lab <- paste0("T", seq_len(K), " ", stringr::str_trunc(sub("^T[0-9]+: ", "", topic_labels), 22))
  .Dv <- D_vocab; .Dt <- D_theme
  rownames(.Dv) <- colnames(.Dv) <- .lab; rownames(.Dt) <- colnames(.Dt) <- .lab
  .dv <- as.dendrogram(hclust(as.dist(.Dv), "ward.D2"))
  .dt <- as.dendrogram(hclust(as.dist(.Dt), "ward.D2"))
  .dl <- dendextend::untangle(dendextend::dendlist(.dv, .dt), method = "step2side")
  dendextend::tanglegram(.dl,
    main_left = "Vocabulary (shared words)", main_right = "Theme (meaning)",
    common_subtrees_color_branches = TRUE, highlight_distinct_edges = FALSE,
    margin_inner = 15, lab.cex = 0.65, cex_main = 1)
} else cat("[skip] needs D_theme + the dendextend package.\n")
```

### Read example articles per family

Use this to decide what to **name** each family. For every family (cluster) it
lists the articles that belong to it most strongly — ranked by their total topic
mass across the family's topics — with a searchable full-text snippet. Read a few,
then set the names in `cluster_names` above and re-knit.

```{r family-examples}
family_topics   <- function(cl) which(clusters == cl)
family_examples <- function(cl, n = 10) {
  tt   <- family_topics(cl)
  mass <- rowSums(theta[, tt, drop = FALSE])          # each doc's membership in the family
  ord  <- order(mass, decreasing = TRUE)[seq_len(min(n, sum(mass > 0)))]
  tibble(
    Family  = cluster_label[cl],
    Topics  = paste0("T", paste(tt, collapse = ", T")),
    Share   = round(mass[ord] * 100, 1),
    Year    = docs$year[ord],
    Author  = docs$author[ord],
    Title   = docs$title[ord],
    Content = stringr::str_squish(dplyr::coalesce(docs$text[ord], ""))
  )
}
fam_tbl <- purrr::map_dfr(seq_len(n_clusters), family_examples, n = 10)

content_col2 <- which(names(fam_tbl) == "Content") - 1L
datatable(
  fam_tbl, filter = "top", rownames = FALSE,
  caption = paste0("Representative articles per topic family (top 10 each, by family membership). ",
                   "Sort/filter the Family column to read one family; the Search box scans the full article text."),
  options = list(
    pageLength = 10, scrollX = TRUE,
    columnDefs = list(list(
      targets = content_col2,
      render = DT::JS(
        "function(data, type, row) {",
        "  if (type === 'display' && data != null && data.length > 200) {",
        "    return data.substr(0, 200) + '…';",
        "  }",
        "  return data;",
        "}"
      )
    ))
  )
)
```

---

## 5. Topic Geometry II — Topic Prevalence & Clusters

```{r dendrogram, fig.height=9}
# Bar chart (replaces the dendrogram): each topic's share of the corpus, with the
# topics ORDERED by the Ward/JSD clustering so similar topics sit next to each
# other, and COLORED by cluster. Bar length = prevalence; adjacency + color carry
# the grouping the dendrogram used to show, in a far more readable form.
ord <- order.dendrogram(as.dendrogram(hc))
hier_df <- tibble(
  label      = topic_labels,
  prevalence = topic_prevalence,
  cluster    = cluster_named           # named clusters from §4 (edit names there)
) |>
  mutate(label = factor(label, levels = topic_labels[ord]))

p_hier <- ggplot(hier_df, aes(prevalence, label, fill = cluster)) +
  geom_col(width = 0.8) +
  scale_fill_manual(values = family_cols) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 0.1),
                     expand = expansion(mult = c(0, 0.05))) +
  labs(title = "Topic Prevalence & Clusters (Ward / Jensen-Shannon)",
       subtitle = "Bars ordered by JSD topic-similarity clustering; color = named topic family; length = share of corpus",
       x = "Share of corpus", y = NULL, fill = "Topic family") +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold"),
        panel.grid.major.y = element_blank())

print(p_hier)
ggsave(file.path(output_path, "01_topic_prevalence_clusters.png"), p_hier,
       width = 12, height = 9, dpi = 150)
cat("Saved 01_topic_prevalence_clusters.png\n")
```

---

## 6. Topic Geometry III — MDS Four-Quadrant Plot

Classical MDS on the JSD matrix gives each topic a 2D coordinate. Axes are
derived dimensions; interpret them post-hoc from the anchoring topics printed
below.

```{r mds-quadrant, fig.height=9}
mds <- cmdscale(as.dist(D_jsd), k = 2)
mds_df <- tibble(
  topic = seq_len(K), Dim1 = mds[, 1], Dim2 = mds[, 2],
  prevalence = topic_prevalence, cluster = cluster_named, label = topic_labels
)

p_mds <- ggplot(mds_df, aes(Dim1, Dim2)) +
  geom_hline(yintercept = 0, color = "gray60", linetype = "dashed") +
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
  geom_point(aes(size = prevalence, color = cluster), alpha = 0.85) +
  geom_text_repel(aes(label = paste0(label, "\n", topic_family_short), color = cluster),
                  size = 2.6, lineheight = 0.85,
                  max.overlaps = 40, box.padding = 0.4, show.legend = FALSE) +
  scale_size_continuous(range = c(3, 14), labels = percent_format(0.1)) +
  scale_color_manual(values = family_cols) +
  labs(title = "Topic Geometry - MDS on Jensen-Shannon Distance",
       subtitle = "Quadrant axes are derived dimensions; interpret post-hoc. Each point labeled by topic and its family.",
       x = "Dimension 1", y = "Dimension 2", size = "Prevalence", color = "Topic family") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold"))

print(p_mds)
ggsave(file.path(output_path, "02_mds_quadrant.png"), p_mds, width = 12, height = 9, dpi = 150)

# ---- Second view: SAME MDS layout, each topic labeled by its top FREX words ----
# (the words most distinctive to that topic) instead of the manual label — so the
# axes/quadrants can be read straight off vocabulary.
frex_words  <- apply(labelTopics(model, n = 3)$frex, 1, paste, collapse = ", ")
mds_df$frex <- frex_words

p_mds_frex <- ggplot(mds_df, aes(Dim1, Dim2)) +
  geom_hline(yintercept = 0, color = "gray60", linetype = "dashed") +
  geom_vline(xintercept = 0, color = "gray60", linetype = "dashed") +
  geom_point(aes(size = prevalence, color = cluster), alpha = 0.85) +
  geom_text_repel(aes(label = paste0(frex, "\n[", topic_family_short, "]"), color = cluster),
                  size = 2.4, lineheight = 0.85,
                  max.overlaps = 40, box.padding = 0.4, show.legend = FALSE) +
  scale_size_continuous(range = c(3, 14), labels = percent_format(0.1)) +
  scale_color_manual(values = family_cols) +
  labs(title = "Topic Geometry - MDS, labeled by FREX words",
       subtitle = "Same layout as above; each topic labeled by its most distinctive (FREX) words and its family",
       x = "Dimension 1", y = "Dimension 2", size = "Prevalence", color = "Topic family") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold"))

print(p_mds_frex)
ggsave(file.path(output_path, "02b_mds_frex_words.png"), p_mds_frex, width = 12, height = 9, dpi = 150)
```

### MDS axis anchors (how to read the dimensions)

The MDS dimensions have no built-in meaning — you name each one from the topics
sitting at its extremes. The **anchor topics** are the `ne` topics with the
highest and lowest coordinate on each axis; the contrast between a dimension's
positive- and negative-end anchors is what that dimension *means*. The table
lists them with their FREX (most distinctive) words; the plot below circles the
same anchors on the layout so you can see where they sit.

```{r mds-interpret}
ne <- 3   # number of anchor topics per axis-end (raise to 4-5 if the contrast is unclear)

# Tidy anchor table: one row per (axis, end, topic), with FREX words.
anchors <- purrr::map_dfr(c("Dim1", "Dim2"), function(ax) {
  hi <- mds_df |> slice_max(.data[[ax]], n = ne) |> mutate(end = "positive (+)")
  lo <- mds_df |> slice_min(.data[[ax]], n = ne) |> mutate(end = "negative (-)")
  bind_rows(hi, lo) |>
    transmute(Axis = ax, End = end, Topic = label, `FREX words` = frex,
              coord = .data[[ax]])
}) |>
  arrange(Axis, desc(End == "positive (+)"), desc(abs(coord))) |>
  select(-coord)

knitr::kable(anchors, caption = paste0(
  "MDS axis anchors: the ", ne, " topics at each end of each dimension. ",
  "Read a dimension by contrasting its (+) and (-) anchor words."))

# Role tag (e.g. 'D1+', 'D2-') for each anchor topic, for the highlighted plot.
anchor_roles <- purrr::map_dfr(c("Dim1", "Dim2"), function(ax) {
  tag <- paste0("D", substr(ax, 4, 4))
  hi <- mds_df |> slice_max(.data[[ax]], n = ne) |> transmute(topic, role = paste0(tag, "+"))
  lo <- mds_df |> slice_min(.data[[ax]], n = ne) |> transmute(topic, role = paste0(tag, "-"))
  bind_rows(hi, lo)
}) |>
  group_by(topic) |>
  summarise(role = paste(role, collapse = " "), .groups = "drop")

mds_anchor <- mds_df |>
  left_join(anchor_roles, by = "topic") |>
  mutate(is_anchor = !is.na(role))
```

```{r mds-anchor-plot, fig.height=9}
# Same MDS layout as §6, but the axis-anchor topics are circled and tagged with
# which axis-end they define (D1+/D1-/D2+/D2-). Non-anchors are faded back so the
# anchors — the topics that GIVE the axes their meaning — stand out.
p_mds_anchor <- ggplot(mds_anchor, aes(Dim1, Dim2)) +
  geom_hline(yintercept = 0, color = "gray70", linetype = "dashed") +
  geom_vline(xintercept = 0, color = "gray70", linetype = "dashed") +
  geom_point(data = ~filter(.x, !is_anchor),
             aes(size = prevalence), color = "grey75", alpha = 0.55) +
  geom_text(data = ~filter(.x, !is_anchor),                     # number the context dots
            aes(label = paste0("T", topic)), size = 1.9, color = "grey35") +
  geom_point(data = ~filter(.x, is_anchor),
             aes(size = prevalence, color = cluster), alpha = 0.95,
             shape = 21, stroke = 1.4, fill = "white") +
  geom_point(data = ~filter(.x, is_anchor),
             aes(size = prevalence, color = cluster), alpha = 0.35) +
  ggrepel::geom_text_repel(
    data = ~filter(.x, is_anchor),
    aes(label = paste0("[", role, "] ", label, "\n", sub("^C\\d+: ", "", as.character(cluster))),
        color = cluster),
    size = 2.8, fontface = "bold", lineheight = 0.85,
    box.padding = 0.5, max.overlaps = 40, show.legend = FALSE) +
  scale_size_continuous(range = c(3, 14), labels = percent_format(0.1)) +
  scale_color_manual(values = family_cols) +
  labs(title = "Topic Geometry - MDS with axis anchors highlighted",
       subtitle = "Circled, bold = the anchor topics defining each axis-end (D1 = Dimension 1, D2 = Dimension 2; +/- = which end). Tag shows topic, axis role, and family. Faded grey dots, labeled T#, = non-anchor topics.",
       x = "Dimension 1", y = "Dimension 2", size = "Prevalence", color = "Topic family") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold"))

print(p_mds_anchor)
ggsave(file.path(output_path, "02d_mds_anchors.png"), p_mds_anchor,
       width = 12, height = 9, dpi = 150)
```

### How many dimensions does the 2-D plot actually capture? (scree) + 3-D view

MDS can return more than two dimensions; they're ordered by how much of the
JSD topic-distance structure each one preserves. The **scree** bar chart shows
that share per dimension — if dimension 3 is small, the 2-D plot already tells
the story; if it's substantial, the 3-D scatter below reveals separation the
flat plot hides. Colors = the same Ward/JSD clusters as the 2-D plot; dot size =
prevalence. The 3-D plot is interactive in the HTML notebook (drag to rotate,
scroll to zoom, hover for the topic label).

```{r mds-3d-scree, fig.height=6}
# ---- Scree: variance (distance structure) captured per MDS dimension ---------
mds_full <- cmdscale(as.dist(D_jsd), k = 5, eig = TRUE)
eig   <- pmax(mds_full$eig, 0)                 # negative eigenvalues -> 0
scree <- tibble(dim = seq_along(eig), pct = eig / sum(eig)) |> filter(dim <= 6)

p_scree <- ggplot(scree, aes(dim, pct)) +
  geom_col(fill = "#2C7FB8", width = 0.7) +
  geom_text(aes(label = percent(pct, 0.1)), vjust = -0.4, size = 3) +
  scale_y_continuous(labels = percent_format(), expand = expansion(mult = c(0, 0.12))) +
  scale_x_continuous(breaks = 1:6) +
  labs(title = "MDS scree — distance structure captured per dimension",
       subtitle = "Each dimension's share of the JSD topic-distance structure. A small dim 3 means the 2-D plot is enough; a large one justifies the 3-D view.",
       x = "MDS dimension", y = "Share of distance structure") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold"),
        panel.grid.minor = element_blank())
print(p_scree)
ggsave(file.path(output_path, "02c_mds_scree.png"), p_scree, width = 9, height = 6, dpi = 150)
cat(sprintf("2-D MDS captures %.1f%% of the topic-distance structure; 3-D captures %.1f%%.\n",
            100 * sum(scree$pct[1:2]), 100 * sum(scree$pct[1:3])))

# ---- 3-D MDS scatter (interactive in the HTML notebook) ----------------------
mds3    <- cmdscale(as.dist(D_jsd), k = 3)
mds3_df <- tibble(Dim1 = mds3[, 1], Dim2 = mds3[, 2], Dim3 = mds3[, 3],
                  label = topic_labels, family = topic_family_short,
                  prevalence = topic_prevalence, cluster = cluster_named)
# Reuse the canonical family palette so cluster colors match every other chart.
clus_pal <- unname(family_cols[levels(mds3_df$cluster)])

plotly::plot_ly(
  mds3_df, x = ~Dim1, y = ~Dim2, z = ~Dim3,
  color = ~cluster, colors = clus_pal,
  size = ~prevalence, sizes = c(6, 26),     # pixel-diameter range (was far too large)
  text = ~paste0(label, "<br>Family: ", family), hoverinfo = "text",
  type = "scatter3d", mode = "markers",
  marker = list(sizemode = "diameter", opacity = 0.85,
                line = list(width = 0.5, color = "grey30"))
) |>
  plotly::layout(title = "Topic Geometry — 3-D MDS on Jensen-Shannon distance",
                 legend = list(title = list(text = "Topic family")),
                 scene = list(xaxis = list(title = "Dim 1"),
                              yaxis = list(title = "Dim 2"),
                              zaxis = list(title = "Dim 3")))
```

### Inside one topic — 3-D word geometry by meaning (interactive)

The plots above place whole *topics*. This one zooms *inside* a single topic: the
dots are that topic's **top words**, positioned by **meaning**. It uses the best
source available, in this order:

1. **MacBERTh contextual** (`word_geometry_embeddings.py`) — every occurrence of
   each word is embedded *in its sentence*, within the topic's own articles, and
   mean-pooled. This is true sense-level meaning (the §11 method, applied per word)
   and the most rigorous option.
2. **Doc-embedding meaning** (`embed_documents.py`) — a word = the mean
   sentence-transformer embedding of the topic's articles that use it.
3. **Co-occurrence** — pure fallback so the chunk always runs.

Words used in similar meanings sit close. **Use the dropdown to switch topics**;
the plot is drag-to-rotate / scroll-to-zoom, dot size = the word's probability in
the topic, and **hovering a word shows the articles it appears in.**

```{r topic-word-geometry, fig.height=7}
# Tier 1 source: MacBERTh per-(topic,word) contextual vectors, if built.
mac_path_wg <- file.path(emb_dir, sprintf("topic_word_vectors_K%d.parquet", K))
have_mac_wg <- file.exists(mac_path_wg)
if (have_mac_wg) wg_mac <- arrow::read_parquet(mac_path_wg)

# Tier 2 source: per-document sentence-transformer embeddings.
emb_path_wg <- file.path(emb_dir, sprintf("doc_emb_K%d.parquet", K))
have_emb_wg <- file.exists(emb_path_wg)
if (have_emb_wg) {
  .emb_wg <- arrow::read_parquet(emb_path_wg)
  .edim   <- grep("^dim_", names(.emb_wg), value = TRUE)
  .Xemb   <- as.matrix(.emb_wg[, .edim]); rownames(.Xemb) <- as.character(.emb_wg$row_index)
}

word_geometry <- function(t, n_words = 20, min_docs = 5) {
  thr  <- stats::quantile(theta[, t], 0.75, na.rm = TRUE)
  rows <- which(theta[, t] >= thr)
  if (length(rows) < min_docs) return(NULL)

  use_mac <- have_mac_wg && any(wg_mac$topic == t)
  if (use_mac) {
    sub   <- dplyr::filter(wg_mac, topic == t, word %in% colnames(beta))
    words <- sub$word
  } else {
    words <- names(sort(beta[t, ], decreasing = TRUE))[seq_len(n_words)]
  }
  if (length(words) < 4) return(NULL)

  toks <- strsplit(modeled_clean[rows], "\\s+")
  contains <- lapply(words, function(w) which(vapply(toks, function(d) w %in% d, logical(1))))
  names(contains) <- words
  n_in <- vapply(contains, length, integer(1))

  if (use_mac) {
    dcols <- grep("^dim_", names(sub), value = TRUE)             # MacBERTh contextual vectors
    Wmat  <- as.matrix(sub[, dcols]); rownames(Wmat) <- words
  } else if (have_emb_wg) {
    emb_row <- match(as.character(docs$row_index[rows]), rownames(.Xemb))   # topic row -> embedding row
    vecs <- lapply(words, function(w) {
      er <- emb_row[contains[[w]]]; er <- er[!is.na(er)]
      if (length(er) < 1) return(NULL)
      colMeans(.Xemb[er, , drop = FALSE])                # word = mean meaning of its articles
    })
    keep <- !vapply(vecs, is.null, logical(1))
    if (sum(keep) < 4) return(NULL)
    Wmat <- do.call(rbind, vecs[keep]); rownames(Wmat) <- words[keep]
  } else {
    M <- vapply(toks, function(d) as.integer(table(factor(d, levels = words))),
                integer(length(words))); rownames(M) <- words
    M <- M[rowSums(M) > 0, , drop = FALSE]
    if (nrow(M) < 4) return(NULL)
    Wmat <- M
  }
  Wn <- Wmat / sqrt(rowSums(Wmat^2))
  D  <- 1 - (Wn %*% t(Wn)); diag(D) <- 0                 # cosine distance between words
  co <- cmdscale(as.dist(D), k = 3)
  kw <- rownames(co)
  hover <- vapply(kw, function(w) {
    r  <- rows[contains[[w]]]; r <- r[order(theta[r, t], decreasing = TRUE)]
    ex <- if (length(r)) paste(sprintf("%s (%s)",
            stringr::str_trunc(dplyr::coalesce(docs$title[r[seq_len(min(3, length(r)))]], "untitled"), 42),
            docs$year[r[seq_len(min(3, length(r)))]]), collapse = "<br>") else "(no article text)"
    paste0("<b>", w, "</b>  ·  prob ", signif(beta[t, w], 3),
           "<br>in ", n_in[[w]], " of the topic's articles<br><i>e.g.</i><br>", ex)
  }, character(1))
  tibble(word = kw, D1 = co[, 1], D2 = co[, 2], D3 = co[, 3],
         prob = beta[t, kw], n_docs = n_in[kw], hover = hover)
}

geoms <- lapply(seq_len(K), word_geometry)
valid <- which(!vapply(geoms, is.null, logical(1)))
wg_method <- if (have_mac_wg) "MacBERTh contextual (per-word, in context)" else
             if (have_emb_wg) "doc-embedding meaning (MiniLM)" else "co-occurrence (fallback)"
cat("Word geometry positioned by:", wg_method, "\n")

if (length(valid) == 0) {
  cat("No topic had enough documents/words for a word-geometry layout.\n")
} else {
  fig_wg <- plotly::plot_ly()
  for (i in seq_along(valid)) {
    t <- valid[i]; g <- geoms[[t]]
    fig_wg <- plotly::add_trace(
      fig_wg, data = g, x = ~D1, y = ~D2, z = ~D3,
      type = "scatter3d", mode = "markers+text",
      text = ~word, textposition = "top center",
      hovertext = ~hover, hoverinfo = "text",
      marker = list(size = scales::rescale(g$prob, to = c(6, 22)),
                    color = unname(family_cols[clusters[t]]),
                    opacity = 0.85, line = list(width = 0.5, color = "grey30")),
      name = topic_labels[t], visible = (i == 1)
    )
  }
  buttons <- lapply(seq_along(valid), function(i) {
    vis <- rep(FALSE, length(valid)); vis[i] <- TRUE
    list(method = "update",
         args  = list(list(visible = vis),
                      list(title = paste0("Word meaning-geometry inside ", topic_labels[valid[i]]))),
         label = topic_labels[valid[i]])
  })
  fig_wg |>
    plotly::layout(
      title = paste0("Word meaning-geometry inside ", topic_labels[valid[1]]),
      showlegend = FALSE,
      updatemenus = list(list(active = 0, buttons = buttons,
                              direction = "down", x = 1.02, y = 0.9, xanchor = "left")),
      scene = list(xaxis = list(title = "M1"),
                   yaxis = list(title = "M2"),
                   zaxis = list(title = "M3")))
}
```

### Topic cards — top words & representative articles

A compact reference for *what each topic is*: its family, top probability words,
prevalence, and a few representative articles (the highest-`theta` documents).
Searchable and sortable — filter the Family column to browse one family.

```{r topic-cards}
rep_docs <- function(t, n = 3) {
  r <- order(theta[, t], decreasing = TRUE)[seq_len(n)]
  paste(sprintf("%s (%s%s)", dplyr::coalesce(docs$title[r], "untitled"), docs$year[r],
                ifelse(is.na(docs$author[r]) | docs$author[r] == "", "",
                       paste0(", ", docs$author[r]))),
        collapse = "  |  ")
}
topic_cards <- tibble(
  Topic        = paste0("T", seq_len(K)),
  Family       = topic_family_short,
  Label        = topic_labels,
  Prevalence   = round(topic_prevalence * 100, 1),
  `Top words`  = apply(labelTopics(model, n = 10)$prob, 1, paste, collapse = ", "),
  `Representative articles` = vapply(seq_len(K), rep_docs, character(1))
) |> arrange(desc(Prevalence))

datatable(topic_cards, filter = "top", rownames = FALSE,
          caption = "Topic cards: family, top words, prevalence, and representative articles per topic.",
          options = list(pageLength = 10, scrollX = TRUE))
```

### Word meaning in context — collocates, usage & period flags

What did each topic word *mean in the Woman's Exponent*? Rather than a modern
dictionary, this reads meaning straight from the corpus: each word's **collocates**
(the distinctive words it keeps company with — "you shall know a word by the company
it keeps") plus a real **keyword-in-context** example. It also **flags period /
Latter-day Saint terms** whose 1870s–1910s sense differs from general modern English
(e.g. *calling*, *principle*, *relief*), from an editable lexicon you can extend.
Fully self-contained (no external lookups, works offline); the collocates/usage table
is cached so re-knits are instant. `collocates()` / `corpus_usage()` work on any word.

```{r word-context-helpers}
# Tokenized corpus (unique cleaned tokens per doc) + doc frequencies, built once.
.gl_tok <- lapply(strsplit(modeled_clean, "[[:space:]]+"), function(x) unique(x[nchar(x) >= 3L]))
.gl_df  <- table(unlist(.gl_tok)); .gl_N <- length(.gl_tok)

# collocates(): words that most DISTINCTIVELY co-occur with a word (lift-ranked) —
# its contextual meaning. min_co avoids rare flukes.
collocates <- function(word, n = 8, min_co = 5) {
  w <- tolower(gsub("[^a-z]", "", word))
  has <- which(vapply(.gl_tok, function(d) w %in% d, logical(1)))
  if (length(has) < min_co) return(NA_character_)
  co <- table(unlist(.gl_tok[has])); co <- co[names(co) != w & as.integer(co) >= min_co]
  if (!length(co)) return(NA_character_)
  lift <- (as.numeric(co) / length(has)) / (as.numeric(.gl_df[names(co)]) / .gl_N)
  paste(names(co)[order(lift, decreasing = TRUE)][seq_len(min(n, length(co)))], collapse = ", ")
}

# corpus_usage(): a real keyword-in-context snippet. Restrict rows to a topic's docs.
corpus_usage <- function(word, rows = seq_along(modeled_raw), half = 7) {
  w <- tolower(gsub("[^a-z]", "", word))
  for (r in rows) {
    toks  <- strsplit(modeled_raw[r], "\\s+")[[1]]; clean <- tolower(gsub("[^a-z]", "", toks))
    i <- which(clean == w | startsWith(clean, w))[1]
    if (!is.na(i)) { lo <- max(1, i - half); hi <- min(length(toks), i + half)
      return(paste(toks[lo:hi], collapse = " ")) }
  }
  NA_character_
}

# --- Period lexicon: terms whose 1870s-1910s / Latter-day Saint sense differs from
# general modern English. >>> EDIT FREELY: add any you notice; flagged in the glossary.
period_terms <- c(
  calling     = "a church assignment/role (not a phone call)",
  testimony   = "a declaration of religious conviction",
  saint       = "a Latter-day Saint church member",
  relief      = "often the Relief Society (the women's organization)",
  principle   = "frequently plural marriage ('the principle')",
  ordinance   = "a sacred religious rite (not a municipal law)",
  endowment   = "a temple ceremony (not a financial fund)",
  sealing     = "a temple marriage / family-binding rite",
  gathering   = "migration of converts to Zion / Utah",
  ward        = "a local congregation (not a hospital ward)",
  stake       = "a regional cluster of congregations",
  elder       = "a male missionary / priesthood holder",
  sister      = "a fellow churchwoman (term of address)",
  gay         = "cheerful / lighthearted (period sense)",
  intercourse = "social interaction / conversation (period sense)",
  presiding   = "leading a meeting or organization"
)
period_note <- function(word) {
  w <- tolower(gsub("[^a-z]", "", word))
  if (w %in% names(period_terms)) unname(period_terms[w]) else ""
}
cat('Helpers ready:  collocates("relief")   corpus_usage("relief")   period_note("calling")\n')
```

```{r word-context-glossary}
n_gloss_words <- 8                       # top words to gloss per topic
.gl_cache <- file.path(output_path, sprintf("word_context_K%d.rds", K))
if (file.exists(.gl_cache)) {
  glossary <- readRDS(.gl_cache); cat("Loaded cached collocates/usage table.\n")
} else {
  cat("Building collocates/usage table (one-time; cached after)...\n")
  glossary <- purrr::map_dfr(seq_len(K), function(t) {
    thr   <- stats::quantile(theta[, t], 0.75, na.rm = TRUE); rows <- which(theta[, t] >= thr)
    words <- names(sort(beta[t, ], decreasing = TRUE))[seq_len(n_gloss_words)]
    tibble::tibble(
      Topic = paste0("T", t), Family = topic_family_short[t], Word = words,
      Prob  = round(beta[t, words], 4),
      `Context (collocates)`      = vapply(words, collocates, character(1)),
      `Usage in Woman's Exponent` = vapply(words, function(w) corpus_usage(w, rows), character(1)))
  })
  saveRDS(glossary, .gl_cache)
}
# Period flag recomputed fresh from the (editable) lexicon, not cached.
glossary$`Period note` <- vapply(glossary$Word, period_note, character(1))
glossary <- dplyr::relocate(glossary, `Period note`, .after = Prob)

datatable(glossary, filter = "top", rownames = FALSE,
          caption = paste0("Word meaning in context: collocates (distinctive co-occurring words) + an in-corpus ",
                           "usage snippet. 'Period note' flags terms whose 1870s-1910s / LDS sense differs from ",
                           "modern English. Filter the Topic or Period note column."),
          options = list(pageLength = 15, scrollX = TRUE))
```

**Semi-automatic nudge — candidate period terms.** Words whose distinctive collocates
lean on the LDS/period *anchor* vocabulary (`lord`, `gospel`, `priesthood`, `relief`, …)
are likely used in a period/religious sense. This surfaces them as candidates to
review — add the real ones to `period_terms` in the helpers chunk above. It reuses the
cached collocates, so it costs nothing, and skips terms you've already flagged.

```{r word-context-nudge}
period_anchors <- c("lord","gospel","zion","priesthood","temple","conference",
                    "presidency","saint","sister","relief","society","testimony",
                    "ordinance","prophet","ward","stake","elder","sacrament","faith","spirit")
.nudge <- glossary |>
  dplyr::distinct(Word, `Context (collocates)`) |>
  dplyr::filter(!Word %in% names(period_terms), !Word %in% period_anchors,
                !is.na(`Context (collocates)`)) |>
  dplyr::mutate(.coll = strsplit(`Context (collocates)`, ",\\s*"),
                `anchor overlap` = vapply(.coll, function(cs) sum(trimws(cs) %in% period_anchors),
                                          integer(1))) |>
  dplyr::filter(`anchor overlap` >= 2) |>
  dplyr::arrange(dplyr::desc(`anchor overlap`)) |>
  dplyr::select(Word, `anchor overlap`, `Context (collocates)`)

cat("Candidate period terms to review (then add to period_terms):", nrow(.nudge), "found\n")
if (nrow(.nudge)) {
  datatable(.nudge, rownames = FALSE,
            caption = "Semi-automatic nudge: words whose distinctive collocates overlap the LDS/period anchor set — review as period-sense candidates.",
            options = list(pageLength = 12, scrollX = TRUE))
} else cat("(no strong candidates beyond what's already flagged)\n")
```

> **Standalone Shiny app (for website integration).** The interactive word
> meaning-geometry above also exists as a self-contained Shiny app at
> `topic_explorer_app/app.R`. It reads the same artifacts (it trains nothing),
> lets a visitor pick any topic and see its 3-D word-meaning layout plus the
> topic's top words and representative articles. Set `base_path`, `scenario`, and
> `pin_K` at the top of `app.R` to match your knit. **Run locally** (the chunk
> below is `eval=FALSE` so it never blocks the knit):
>
> - Local: `shiny::runApp("topic_explorer_app", launch.browser = TRUE)`
> - **Deploy to the web (one command):** `source("topic_explorer_app/bundle_for_deploy.R")`
>   bundles the needed artifacts into `topic_explorer_app/data/`; set `DEPLOY <- TRUE`
>   in it (after a one-time `rsconnect::setAccountInfo(...)`) to also publish to
>   shinyapps.io. The app auto-reads `./data` when the live project isn't reachable.

```{r run-shiny-app, eval=FALSE}
# Local interactive run (not executed during knit).
shiny::runApp("topic_explorer_app", launch.browser = TRUE)
```

> **Companion app — Topic Map (`topic_map_app/app.R`).** A second self-contained
> Shiny app, topic-level rather than word-level: the whole corpus as an
> interactive 3-D topic map (MDS on JSD, colored by family, sized by prevalence).
> A visitor rotates the map and clicks any topic to see its top words, its share
> of the magazine over time, its representative articles, and its closest topics.
> `bundle_for_deploy.R` now bundles **both** apps (set `DEPLOY <- TRUE` to publish
> both). Run locally:

```{r run-topic-map-app, eval=FALSE}
# Local interactive run (not executed during knit).
shiny::runApp("topic_map_app", launch.browser = TRUE)
```

### 4-D MDS — all pairwise views (scatterplot matrix)

You can't draw four axes at once, so a 4-D MDS is shown as its **six pairwise
projections**. Each panel plots two of the four dimensions; `T#` = topic, color =
family. Read it this way: two topics close together in **every** panel are truly
close; topics that look close in one panel but separate in another are pulled
apart by a higher dimension — separation the 2-D plot can't show. Check the scree
above first: if dimensions 3–4 are tiny, the extra panels add little.

```{r mds-4d, fig.width=14, fig.height=9}
mds4 <- cmdscale(as.dist(D_jsd), k = 4)
colnames(mds4) <- paste0("D", 1:4)
mds4_df <- as_tibble(mds4) |>
  mutate(topic = seq_len(K), tnum = paste0("T", topic),
         prevalence = topic_prevalence, family = cluster_named)

dim_pairs  <- combn(paste0("D", 1:4), 2, simplify = FALSE)   # 6 pairs
pair_plots <- lapply(dim_pairs, function(p) {
  ggplot(mds4_df, aes(.data[[p[1]]], .data[[p[2]]], color = family)) +
    geom_hline(yintercept = 0, color = "gray85") +
    geom_vline(xintercept = 0, color = "gray85") +
    geom_point(aes(size = prevalence), alpha = 0.85) +
    geom_text(aes(label = tnum), size = 2, vjust = -0.9, show.legend = FALSE) +
    scale_color_manual(values = family_cols, guide = "none") +
    scale_size_continuous(range = c(2, 8), guide = "none") +
    labs(x = p[1], y = p[2]) +
    theme_minimal(base_size = 10)
})
p_mds4 <- wrap_plots(pair_plots, ncol = 3) +
  plot_annotation(
    title = "Topic Geometry — 4-D MDS, all pairwise views",
    subtitle = "Six projections of the four MDS dimensions; T# = topic, color = family. Close in ALL panels = truly close; close in some but not others = a higher dimension separates them.",
    theme = theme(plot.title = element_text(face = "bold")))
print(p_mds4)
ggsave(file.path(output_path, "02e_mds_4d_pairs.png"), p_mds4, width = 14, height = 9, dpi = 150)
```

### 5-D MDS — what the 5th dimension adds

Rather than redraw all ten pairwise panels, this isolates the **new** axis: D5
plotted against each lower dimension. Topics that separate **vertically** in these
panels are pulled apart *only* by the 5th dimension — a distinction none of the
first four axes captured. Check the scree first: if D5's bar is tiny, expect these
points to look vertically flat (the dimension carries little structure).

```{r mds-5d, fig.width=16, fig.height=5}
# Reusable single panel (one dimension vs another), used by every matrix below.
mds_panel <- function(df, xd, yd) {
  ggplot(df, aes(.data[[xd]], .data[[yd]], color = family)) +
    geom_hline(yintercept = 0, color = "gray85") +
    geom_vline(xintercept = 0, color = "gray85") +
    geom_point(aes(size = prevalence), alpha = 0.85) +
    geom_text(aes(label = tnum), size = 2, vjust = -0.9, show.legend = FALSE) +
    scale_color_manual(values = family_cols, guide = "none") +
    scale_size_continuous(range = c(2, 8), guide = "none") +
    labs(x = xd, y = yd) +
    theme_minimal(base_size = 9)
}

mds5 <- cmdscale(as.dist(D_jsd), k = 5)
colnames(mds5) <- paste0("D", 1:5)
mds5_df <- as_tibble(mds5) |>
  mutate(topic = seq_len(K), tnum = paste0("T", topic),
         prevalence = topic_prevalence, family = cluster_named)

plots5 <- lapply(paste0("D", 1:4), function(d) mds_panel(mds5_df, d, "D5"))
p_mds5 <- wrap_plots(plots5, ncol = 4) +
  plot_annotation(
    title = "5-D MDS — the 5th dimension vs. each lower dimension",
    subtitle = "D5 (y-axis) against D1-D4; T# = topic, color = family. Vertical separation here = a distinction unique to the 5th dimension.",
    theme = theme(plot.title = element_text(face = "bold")))
print(p_mds5)
ggsave(file.path(output_path, "02f_mds_5d.png"), p_mds5, width = 16, height = 5, dpi = 150)
```

### 5-D MDS — full scatterplot matrix (all 10 pairs)

The complete 5-D view: every pair of the five dimensions (D1–D5 → 10 panels).
Same reading as the 4-D matrix — topics close in **every** panel are truly close.

```{r mds-5d-full, fig.width=14, fig.height=12}
pairs5  <- combn(paste0("D", 1:5), 2, simplify = FALSE)          # 10 pairs
plots5f <- lapply(pairs5, function(p) mds_panel(mds5_df, p[1], p[2]))
p_mds5f <- wrap_plots(plots5f, ncol = 4) +
  plot_annotation(
    title = "5-D MDS — full scatterplot matrix (10 pairwise views)",
    subtitle = "Every pair of the five MDS dimensions; T# = topic, color = family.",
    theme = theme(plot.title = element_text(face = "bold")))
print(p_mds5f)
ggsave(file.path(output_path, "02f2_mds_5d_full.png"), p_mds5f, width = 14, height = 12, dpi = 150)
```

### 6-D MDS — what the 6th dimension adds

Same idea, one axis higher: D6 against each of D1-D5. By this depth the captured
structure is usually very small (again, read it off the scree) — these panels are
mostly for completeness, to confirm nothing surprising hides in the 6th dimension.

```{r mds-6d, fig.width=16, fig.height=5}
mds6 <- cmdscale(as.dist(D_jsd), k = 6)
colnames(mds6) <- paste0("D", 1:6)
mds6_df <- as_tibble(mds6) |>
  mutate(topic = seq_len(K), tnum = paste0("T", topic),
         prevalence = topic_prevalence, family = cluster_named)

plots6 <- lapply(paste0("D", 1:5), function(d) mds_panel(mds6_df, d, "D6"))
p_mds6 <- wrap_plots(plots6, ncol = 5) +
  plot_annotation(
    title = "6-D MDS — the 6th dimension vs. each lower dimension",
    subtitle = "D6 (y-axis) against D1-D5; T# = topic, color = family. Usually near-flat by this depth — confirm via the scree how little it carries.",
    theme = theme(plot.title = element_text(face = "bold")))
print(p_mds6)
ggsave(file.path(output_path, "02g_mds_6d.png"), p_mds6, width = 16, height = 5, dpi = 150)
```

### 6-D MDS — full scatterplot matrix (all 15 pairs)

The complete 6-D view: every pair of the six dimensions (D1–D6 → 15 panels). The
densest of the set — most useful for confirming the higher dimensions carry no
hidden structure rather than for reading individual topics.

```{r mds-6d-full, fig.width=15, fig.height=15}
pairs6  <- combn(paste0("D", 1:6), 2, simplify = FALSE)          # 15 pairs
plots6f <- lapply(pairs6, function(p) mds_panel(mds6_df, p[1], p[2]))
p_mds6f <- wrap_plots(plots6f, ncol = 4) +
  plot_annotation(
    title = "6-D MDS — full scatterplot matrix (15 pairwise views)",
    subtitle = "Every pair of the six MDS dimensions; T# = topic, color = family.",
    theme = theme(plot.title = element_text(face = "bold")))
print(p_mds6f)
ggsave(file.path(output_path, "02g2_mds_6d_full.png"), p_mds6f, width = 15, height = 15, dpi = 150)
```

### Measuring the distance between two topics (exactly)

Distances *on the plots* only approximate the truth (the scree % is how much you
lose flattening to 2-D/3-D). The **exact** relative closeness of any two topics is
their Jensen-Shannon distance in `D_jsd` — `0` = identical vocabulary, larger =
more different (this corpus's range is printed back in §4). These helpers read it
directly, so they're exact no matter how many dimensions you plot.

```{r topic-distances}
topic_dist <- function(a, b) D_jsd[a, b]    # exact JSD between topic a and topic b

# Closest (or farthest) topics to a given topic, by exact JSD.
nearest_topics <- function(t, n = 5, farthest = FALSE) {
  d <- D_jsd[t, ]; d[t] <- NA
  ord <- order(d, decreasing = farthest, na.last = NA)[seq_len(n)]
  tibble(reference   = topic_labels[t],
         other       = topic_labels[ord],
         family      = topic_family_short[ord],
         same_family = clusters[ord] == clusters[t],
         JSD         = round(d[ord], 3))
}

# Compact overview: every topic's single nearest neighbor (most similar vocabulary).
closest_tbl <- purrr::map_dfr(seq_len(K), ~nearest_topics(.x, n = 1)) |>
  mutate(JSD_rank = rank(JSD)) |> arrange(JSD)
knitr::kable(closest_tbl, caption = paste0(
  "Each topic's single nearest topic by exact Jensen-Shannon distance ",
  "(smaller = more similar; topics at the top are the most alike pair in the corpus). ",
  "Use nearest_topics(t, n) for more neighbors, or nearest_topics(t, n, farthest = TRUE) for the most DIFFERENT topics."))
```

---

## 7. Topic Geometry IV — Co-occurrence Network

`stm::topicCorr()` measures whether topics *co-occur in the same articles* —
distinct from the JSD vocabulary similarity above.

```{r topic-network, fig.height=8}
tcorr <- topicCorr(model, method = "simple", cutoff = 0.05)
adj <- tcorr$cor; adj[abs(adj) < 0.05] <- 0; diag(adj) <- 0

g <- graph_from_adjacency_matrix(abs(adj), mode = "undirected", weighted = TRUE, diag = FALSE)
V(g)$prevalence <- topic_prevalence
V(g)$label <- paste0(topic_labels, "\n", topic_family_short)   # topic + family
V(g)$cluster <- as.character(cluster_named)   # char (not factor) survives igraph attrs

p_net <- ggraph(as_tbl_graph(g), layout = "fr") +
  geom_edge_link(aes(width = weight, alpha = weight), color = "gray40") +
  geom_node_point(aes(size = prevalence, color = cluster), alpha = 0.9) +
  geom_node_text(aes(label = label), size = 2.4, lineheight = 0.85, repel = TRUE,
                 max.overlaps = 40, segment.alpha = 0.4) +
  scale_edge_width(range = c(0.2, 2)) + scale_edge_alpha(range = c(0.2, 0.8)) +
  scale_size_continuous(range = c(3, 12)) + scale_color_manual(values = family_cols) +
  labs(title = "Topic Co-occurrence Network",
       subtitle = "Edges = partial correlations of topic prevalence across documents (|r| > 0.05); node label = topic + family",
       color = "Topic family", size = "Prevalence") +
  theme_void() + theme(plot.title = element_text(face = "bold"))

print(p_net)
ggsave(file.path(output_path, "03_topic_network.png"), p_net, width = 12, height = 9, dpi = 150)
```

---

## 8. Document Atlas (transformer embeddings)

Each article was embedded by `embed_documents.py` with a sentence-transformer
(`all-MiniLM-L6-v2`, 384-dim): long articles were split into word-windows,
each window embedded, then length-weighted mean-pooled back to one vector per
document. Here we lay those vectors out in 2D with UMAP and color by decade and
by dominant STM topic. Unlike the old topic-space UMAP, this places articles by
their *full semantic content*, independent of the STM model.

```{r doc-atlas, fig.height=8}
emb_path <- file.path(emb_dir, sprintf("doc_emb_K%d.parquet", K))
if (have(emb_path)) {
  emb_tbl <- read_parquet(emb_path) |> arrange(row_index)
  dim_cols <- grep("^dim_", names(emb_tbl), value = TRUE)
  X <- as.matrix(emb_tbl[, dim_cols])

  # Align doc metadata to the embedded rows (embeddings may be a dev subset).
  atlas_meta <- docs |> filter(row_index %in% emb_tbl$row_index) |> arrange(row_index)
  stopifnot(nrow(atlas_meta) == nrow(X))
  atlas_meta <- atlas_meta |>
    mutate(decade = floor(year / 10) * 10,
           dominant_topic = max.col(theta[match(row_index, docs$row_index), , drop = FALSE]))

  set.seed(12345)
  uu <- umap(X, n_neighbors = 15, min_dist = 0.1, metric = "cosine")
  atlas_meta$umap1 <- uu[, 1]; atlas_meta$umap2 <- uu[, 2]

  # ---- OPTION (a): de-blob the map by faceting into decade small-multiples ----
  # Same UMAP layout, split per decade so points don't pile up; color = dominant
  # STM topic. Reading: where each decade's articles sit, and how that shifts.
  p_atlas_a <- ggplot(atlas_meta, aes(umap1, umap2, color = factor(dominant_topic))) +
    geom_point(alpha = 0.6, size = 0.7) +
    facet_wrap(~ decade, ncol = 3) +
    scale_color_manual(values = topic_col_int, guide = "none") +
    labs(title = "Article Atlas (a) — semantic map, faceted by decade",
         subtitle = "Each panel = one decade's articles in the SAME embedding layout; color = dominant STM topic",
         x = "UMAP 1", y = "UMAP 2") +
    theme_minimal(base_size = 11) + theme(plot.title = element_text(face = "bold"))
  print(p_atlas_a)
  ggsave(file.path(output_path, "04a_atlas_by_decade.png"), p_atlas_a,
         width = 12, height = 9, dpi = 150)

  # ---- OPTION (b): topic prevalence over time (theme-evolution view) ----
  # Doesn't use the embeddings at all — each STM topic's mean share of the
  # articles each year, as a stacked area. The most direct "how did themes shift".
  topic_year <- as.data.frame(theta) |>
    setNames(paste0("T", seq_len(ncol(theta)))) |>
    mutate(year = docs$year) |>
    filter(!is.na(year)) |>
    tidyr::pivot_longer(-year, names_to = "topic", values_to = "share") |>
    group_by(year, topic) |>
    summarise(share = mean(share), .groups = "drop") |>
    mutate(topic = factor(topic, levels = paste0("T", seq_len(ncol(theta)))))

  p_atlas_b <- ggplot(topic_year, aes(year, share, fill = topic)) +
    geom_area(position = "fill", color = "white", linewidth = 0.1) +
    scale_y_continuous(labels = percent_format()) +
    scale_fill_manual(values = topic_col_T) +
    labs(title = "Article Atlas (b) — topic prevalence over time",
         subtitle = "Each band = an STM topic's share of that year's articles (themes rising/falling)",
         x = "Year", y = "Share of articles", fill = "Topic") +
    theme_minimal(base_size = 11) + theme(plot.title = element_text(face = "bold"))
  print(p_atlas_b)
  ggsave(file.path(output_path, "04b_topic_over_time.png"), p_atlas_b,
         width = 12, height = 8, dpi = 150)
} else {
  cat("Run:  python scripts\\embed_documents.py", K, "\n")
}
```

---

## 9. Search the corpus — keyword + meaning

The doc embeddings make the corpus searchable two complementary ways, combined in
one live app:

- **Keyword** — articles whose full text literally contains your term(s).
- **By meaning** — the app builds a query vector from the embeddings of the
  articles that match your term, then ranks *every* article by cosine similarity.
  That surfaces articles about the same thing **even when they never use the word**
  (search *welfare*, also get "the poor," "charity," "the needy"). You can also pin
  it to one article by `row_index` to find that article's nearest neighbours.

> **Combined app — Corpus Search (`search_app/app.R`).** One search box, two result
> tabs (keyword / by meaning). It recomputes everything live from
> `advanced_docs_K{K}.csv` + `doc_emb_K{K}.parquet`, so if articles are added or
> edited and re-embedded the app just reflects the new files — nothing is
> precomputed to go stale. Run locally (the chunk below is `eval=FALSE` so it never
> blocks the knit):

```{r run-search-app, eval=FALSE}
shiny::runApp("search_app", launch.browser = TRUE)
```

The static report below keeps a plain **keyword** browser so the knitted document
stays searchable offline; the app above adds the live **meaning** search on top.

---

## 9c. Interactive Article Browser (full-text keyword search)

The **Search** box (and the per-column filters) match the **full article text**
via the *Content* column — so you can keyword-search the body, not just the
title/metadata. Cells show the first 200 characters, but the search scans the
whole article. This is the in-report replacement for ad-hoc `hybrid_search.py`
queries. *(For meaning-based search — related articles that don't share the word —
run the combined **Corpus Search** app from §9.)*

```{r interactive-browser}
# Top articles per topic, WITH the full (header-stripped) article body so the
# DataTables Search box can keyword-search the BODY, not just metadata. Built from
# the row-aligned theta (doc x topic) and docs (one row per modeled article) that
# §3 loaded -- works for whatever scenario is selected.
# ALL modeled articles (one row each), labeled with their dominant STM topic and
# that topic's share. Fully keyword-searchable on the Content (full body) column.
# Sort/filter by the Topic column to browse a single topic; search Content for
# keywords across the whole corpus.
.dom       <- max.col(theta)                                  # dominant topic per doc
.dom_share <- theta[cbind(seq_len(nrow(theta)), .dom)]        # that topic's share

browse_data <- tibble::tibble(
  Topic   = .dom,
  Label   = topic_labels[.dom],
  `%`     = round(.dom_share * 100, 1),
  Title   = docs$title,
  Author  = docs$author,
  Type    = docs$article_type,
  Volume  = docs$volume_num,
  Year    = docs$year,
  Content = stringr::str_squish(dplyr::coalesce(docs$text, "")),  # full body, searchable
  File    = docs$filename
)

# DataTables 0-based index of the Content column for the JS truncation renderer.
content_col <- which(names(browse_data) == "Content") - 1L

datatable(
  browse_data, filter = "top", rownames = FALSE,
  caption = paste0("ALL ", nrow(browse_data), " modeled articles, labeled by dominant topic. ",
                   "Search box matches the FULL article text (Content); sort/filter the Topic column to browse one topic."),
  options = list(
    pageLength = 20, scrollX = TRUE,
    # Show only the first 200 chars in the cell, but DataTables still SEARCHES the
    # full untruncated text (the 'filter' type receives the whole value).
    columnDefs = list(list(
      targets = content_col,
      render = DT::JS(
        "function(data, type, row) {",
        "  if (type === 'display' && data != null && data.length > 200) {",
        "    return data.substr(0, 200) + '…';",
        "  }",
        "  return data;",
        "}"
      )
    ))
  )
)
```

---

## 10. BERTopic Cross-Check vs STM

`run_bertopic.py` clustered the *same* document embeddings with BERTopic (UMAP +
HDBSCAN). BERTopic discovers its own number of topics bottom-up and labels some
documents as outliers (topic `-1`). We cross-tabulate BERTopic clusters against
each article's dominant STM topic: bright cells off the diagonal show where the
neural model splits or merges an STM topic — **triangulation, not replacement.**

```{r bertopic-crosstab, fig.height=9}
bt_docs_path   <- file.path(bertopic_dir, sprintf("bertopic_docs_K%d.csv", K))
bt_topics_path <- file.path(bertopic_dir, sprintf("bertopic_topics_K%d.csv", K))
if (have(bt_docs_path)) {
  bt_docs <- readr::read_csv(bt_docs_path, show_col_types = FALSE)

  stm_dom <- tibble(row_index = docs$row_index, stm_topic = max.col(theta))
  cmp <- bt_docs |> left_join(stm_dom, by = "row_index") |> filter(!is.na(stm_topic))

  n_out <- sum(cmp$bertopic_topic == -1)
  cat("BERTopic: ", dplyr::n_distinct(cmp$bertopic_topic[cmp$bertopic_topic >= 0]),
      "clusters | outliers:", n_out, "/", nrow(cmp), "\n")

  ct <- cmp |> filter(bertopic_topic >= 0) |>
    count(stm_topic, bertopic_topic) |>
    group_by(bertopic_topic) |> mutate(frac = n / sum(n)) |> ungroup()

  # Line chart (replaces the heatmap/bars): an AGREEMENT CURVE. Each BERTopic
  # cluster's "purity" = the share of its docs in its single most-common STM
  # topic. Sort clusters by purity and connect them: a curve that stays high =
  # the two methods mostly agree; a curve that drops steeply = many neural
  # clusters split across STM topics. Dashed line = 50% (a clean 1:1 match).
  purity <- ct |>
    group_by(bertopic_topic) |>
    slice_max(frac, n = 1, with_ties = FALSE) |>
    ungroup() |>
    arrange(desc(frac)) |>
    mutate(rank = row_number(),
           # Each point's label: which BERTopic cluster, and the STM topic it maps to.
           point_label = paste0("BT", bertopic_topic, " → ", topic_labels[stm_topic]))

  p_ct <- ggplot(purity, aes(rank, frac)) +
    geom_hline(yintercept = 0.5, linetype = "dashed", color = "grey55") +
    geom_line(color = "#2C7FB8", linewidth = 1) +
    geom_point(aes(color = factor(stm_topic)), size = 2.6) +
    ggrepel::geom_text_repel(aes(label = point_label, color = factor(stm_topic)),
                             size = 2.3, box.padding = 0.35, max.overlaps = 40,
                             segment.alpha = 0.4, show.legend = FALSE) +
    scale_y_continuous(labels = percent_format(), limits = c(0, 1)) +
    scale_color_manual(values = topic_col_int, guide = "none") +
    labs(title = "BERTopic–STM agreement curve",
         subtitle = "Each point = a BERTopic cluster (sorted by purity), labeled 'BTn → the STM topic it maps to'; y = % of its docs in that topic. Above the dashed 50% line = clean 1:1 mapping.",
         x = "BERTopic clusters, sorted by agreement", y = "Purity (share in top STM topic)") +
    theme_minimal(base_size = 11) +
    theme(plot.title = element_text(face = "bold"))
  print(p_ct)
  ggsave(file.path(output_path, "05_bertopic_vs_stm.png"), p_ct, width = 12, height = 8, dpi = 150)

  if (have(bt_topics_path)) {
    bt_topics <- readr::read_csv(bt_topics_path, show_col_types = FALSE)
    lab_col <- intersect(c("Name", "Representation"), names(bt_topics))[1]
    cat("\nTop BERTopic clusters:\n")
    bt_topics |> filter(Topic >= 0) |> arrange(desc(Count)) |> head(15) |>
      transmute(Topic, Count, label = .data[[lab_col]]) |> print()
  }
} else {
  cat("Run:  python scripts\\run_bertopic.py", K, "\n")
}
```

### STM ↔ BERTopic article flows (alluvial)

The agreement curve compresses each neural cluster to one purity number. This
**alluvial diagram** shows the actual *flows*: every ribbon connects an STM topic
(left) to a BERTopic cluster (right), and ribbon **width = how many articles** the
two share. Read it as a routing map:

- **One STM topic fanning out into several clusters** → the neural model *split*
  that STM topic into finer sub-themes.
- **Several STM topics converging on one cluster** → the neural model *merged*
  them (it sees them as one thing).
- **A clean 1-in-1-out ribbon** → the two methods agree on that theme.

Only flows carrying ≥10% of a cluster's articles are drawn, so the diagram stays
legible (raise/lower `flow_min` to show more or fewer ribbons).

```{r bertopic-alluvial, fig.height=11}
if (exists("ct")) {
  flow_min <- 0.10                                   # min share of a cluster to draw a ribbon

  # Right-side labels: use BERTopic's own names if we loaded them, else "BT<n>".
  bt_label <- if (exists("bt_topics")) {
    lc <- intersect(c("Name", "Representation"), names(bt_topics))[1]
    setNames(stringr::str_trunc(as.character(bt_topics[[lc]]), 28),
             as.character(bt_topics$Topic))
  } else NULL

  flows <- ct |>
    filter(frac >= flow_min) |>
    mutate(STM      = topic_labels[stm_topic],
           BERTopic = if (!is.null(bt_label))
                        dplyr::coalesce(bt_label[as.character(bertopic_topic)],
                                        paste0("BT", bertopic_topic))
                      else paste0("BT", bertopic_topic))

  # Order STM strata by prevalence so the busiest topics read top-down.
  flows <- flows |>
    mutate(STM = factor(STM, levels = topic_labels[order(topic_prevalence)]))

  p_sankey <- ggplot(flows, aes(axis1 = STM, axis2 = BERTopic, y = n)) +
    geom_alluvium(aes(fill = STM), alpha = 0.7, width = 1/10, decreasing = FALSE) +
    geom_stratum(width = 1/10, fill = "grey92", color = "grey40") +
    geom_text(stat = "stratum", aes(label = after_stat(stratum)),
              size = 2.3, lineheight = 0.85) +
    scale_x_discrete(limits = c("STM topic", "BERTopic cluster"),
                     expand = c(0.15, 0.05)) +
    scale_fill_manual(values = topic_col_lab, guide = "none") +
    labs(title = "STM ↔ BERTopic article flows (alluvial)",
         subtitle = paste0("Ribbon width = shared articles. One STM topic fanning into many clusters = the neural model split it; ",
                           "many topics merging into one cluster = it lumped them. Flows ≥", scales::percent(flow_min), " of a cluster shown."),
         x = NULL, y = "Articles") +
    theme_minimal(base_size = 10) +
    theme(plot.title = element_text(face = "bold"),
          axis.text.y = element_blank(),
          panel.grid = element_blank())
  print(p_sankey)
  ggsave(file.path(output_path, "05c_bertopic_stm_alluvial.png"), p_sankey,
         width = 13, height = 11, dpi = 150)
  cat("Saved 05c_bertopic_stm_alluvial.png\n")
} else {
  cat("[skip] BERTopic crosstab (ct) not built - run run_bertopic.py first.\n")
}
```

---

## 11. Diachronic Semantic Change (MacBERTh)

`semantic_change.py` measured, for each target word, how its meaning moves
across the historical periods, three complementary ways:

- **PRT** — prototype distance: `1 - cos` between period mean vectors. Coarse drift.
- **APD** — average pairwise distance: mean `1 - cos` over cross-period pairs.
  Sensitive to changes in *spread*, not just the centroid.
- **JSD** — Jensen-Shannon over induced word senses (KMeans on pooled
  occurrences). Captures change in the *mix of senses* a word is used in.

All three come from embedding each occurrence **in context** with MacBERTh
(historical-English BERT). Higher = more change between the two periods.

```{r diachronic-load}
change_path <- file.path(diachr_dir, sprintf("diachronic_change_K%d.csv", K))
proto_path  <- file.path(diachr_dir, sprintf("diachronic_prototypes_K%d.parquet", K))
periods_path<- file.path(diachr_dir, "diachronic_periods.json")
have_diachr <- have(change_path)
if (have_diachr) {
  change <- readr::read_csv(change_path, show_col_types = FALSE)
  if (file.exists(periods_path)) {
    pj <- fromJSON(periods_path)
    cat("Periods used:", paste(pj$periods$name, collapse = ", "), "\n")
  }
  cat("Comparisons:", nrow(change), "over",
      dplyr::n_distinct(change$word), "words\n")
} else {
  cat("Run:  python scripts\\semantic_change.py", K, "\n")
}
```

```{r diachronic-heatmap, eval=have_diachr, fig.height=8}
# Internal guard so "Run All Chunks" (which ignores eval=have_diachr) can't error.
if (!have_diachr) {
  cat("[skip] diachronic artifacts not computed for this scenario yet.\n")
} else {
# ONE line per change measure (names spelled out), instead of three bar panels.
# For each word we take its PEAK change across any period pair, then scale each
# measure 0-1 so the three sit comparably on one axis. Words sorted by APD.
#   PRT = Prototype distance | APD = Average Pairwise Distance | JSD = Jensen-Shannon Divergence
word_order <- change |> group_by(word) |> summarise(m = max(apd, na.rm = TRUE)) |>
  arrange(desc(m)) |> pull(word)   # most-changed first (also used by the drift plot)

measure_names <- c(prt = "Prototype distance (PRT)",
                   apd = "Average pairwise distance (APD)",
                   jsd = "Jensen-Shannon divergence (JSD)")

peak <- change |>
  group_by(word) |>
  summarise(prt = max(prt, na.rm = TRUE),
            apd = max(apd, na.rm = TRUE),
            jsd = max(jsd, na.rm = TRUE), .groups = "drop") |>
  pivot_longer(c(prt, apd, jsd), names_to = "measure", values_to = "peak") |>
  group_by(measure) |>
  mutate(scaled = (peak - min(peak)) / (max(peak) - min(peak) + 1e-12)) |>
  ungroup() |>
  mutate(word    = factor(word, levels = word_order),
         measure = factor(measure_names[measure], levels = measure_names))

# NOTE: x is WORDS, not time. Each value is a word's PEAK change across the period
# pairs, summarised to one number. (For the genuine temporal view see the
# "drift over time" chart below.) Words sorted by APD, most-changed first.

# (a) GROUPED BAR — magnitude per word, the three measures side by side.
p_bar <- ggplot(peak, aes(word, scaled, fill = measure)) +
  geom_col(position = position_dodge(width = 0.8), width = 0.72) +
  scale_fill_brewer(palette = "Dark2") +
  labs(title = "Diachronic change by word — ranked (bar)",
       subtitle = "Peak shift per word, each measure scaled 0-1. Sorted by APD; taller = more change.  PRT=centroid drift, APD=spread of usage, JSD=sense-mix.",
       x = NULL, y = "Relative change (0-1 within measure)", fill = "Measure") +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold"),
        axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "top")
print(p_bar)
ggsave(file.path(output_path, "06_diachronic_change.png"), p_bar, width = 14, height = 8, dpi = 150)

# (b) DOT / LOLLIPOP — same numbers as dots, with a grey guide spanning each word's
# three measures. A WIDE gap between a word's dots = the measures DISAGREE (e.g.
# JSD high but PRT low = its sense-mix shifted more than its average meaning moved).
peak_range <- peak |> group_by(word) |>
  summarise(lo = min(scaled), hi = max(scaled), .groups = "drop")
p_dot <- ggplot(peak, aes(scaled, fct_rev(word))) +
  geom_segment(data = peak_range,
               aes(x = lo, xend = hi, y = fct_rev(word), yend = fct_rev(word)),
               inherit.aes = FALSE, color = "grey80", linewidth = 1.1) +
  geom_point(aes(color = measure), size = 3) +
  scale_color_brewer(palette = "Dark2") +
  labs(title = "Diachronic change by word — dot plot",
       subtitle = "Three measures per word; a wide spread between a word's dots = the measures disagree about HOW it changed.",
       x = "Relative change (0-1 within measure)", y = NULL, color = "Measure") +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold"))
print(p_dot)
ggsave(file.path(output_path, "06b_diachronic_change_dots.png"), p_dot, width = 12, height = 8, dpi = 150)
}
```

```{r diachronic-drift, eval=have_diachr, fig.height=8}
# Drift trajectories: project each word's per-period prototype vector through a
# shared PCA (fit on all prototypes), then connect periods in order.
if (have(proto_path)) {
  proto <- read_parquet(proto_path)
  pdim <- grep("^dim_", names(proto), value = TRUE)
  Pm <- as.matrix(proto[, pdim])
  pca <- prcomp(Pm, center = TRUE, scale. = FALSE)
  proto$PC1 <- pca$x[, 1]; proto$PC2 <- pca$x[, 2]

  # period order from the JSON sidecar if present, else alphabetical
  per_levels <- if (exists("pj")) pj$periods$name else sort(unique(proto$period))
  proto <- proto |> mutate(period = factor(period, levels = per_levels)) |>
    arrange(word, period)

  # Show the most-changed words for legibility.
  show_words <- head(word_order, 9)
  dd <- proto |> filter(word %in% show_words)

  p_drift <- ggplot(dd, aes(PC1, PC2, group = word, color = word)) +
    geom_path(arrow = arrow(length = unit(0.18, "cm"), type = "closed"),
              alpha = 0.8, linewidth = 0.7) +
    geom_point(aes(shape = period), size = 3) +
    geom_text_repel(aes(label = ifelse(period == per_levels[length(per_levels)] |
                                        period == per_levels[1], word, "")),
                    size = 3, max.overlaps = 30, show.legend = FALSE) +
    scale_color_brewer(palette = "Set1") +
    labs(title = "Diachronic Word Drift (MacBERTh prototypes)",
         subtitle = "Each path = one word's meaning trajectory across periods, in a shared PCA",
         x = "PC1", y = "PC2", color = "Word", shape = "Period") +
    theme_minimal(base_size = 12) + theme(plot.title = element_text(face = "bold"))
  print(p_drift)
  ggsave(file.path(output_path, "07_diachronic_drift.png"), p_drift, width = 12, height = 9, dpi = 150)
}
```

### Semantic drift over time

The genuine **temporal** view (the one the ranked charts above can't give): for the
most-changed words, each line is its **cosine distance from its earliest-period
meaning**, plotted across the periods. A line that **rises is drifting away** from
where it started; a **flat** line is stable; the steeper the climb, the faster the
change. Same MacBERTh prototypes as the 2-D drift map, read as "how far from the
start, over time."

```{r diachronic-over-time, eval=have_diachr, fig.height=7}
if (!have_diachr || !have(proto_path)) {
  cat("[skip] need diachronic prototypes for the over-time chart.\n")
} else {
  proto_ot   <- read_parquet(proto_path)
  pdim_ot    <- grep("^dim_", names(proto_ot), value = TRUE)
  per_levels <- if (exists("pj")) pj$periods$name else sort(unique(proto_ot$period))
  show_words <- head(word_order, 9)             # word_order from the chunk above

  drift_ot <- proto_ot |>
    filter(word %in% show_words) |>
    mutate(period = factor(period, levels = per_levels)) |>
    filter(!is.na(period)) |>
    arrange(word, period) |>
    group_by(word) |>
    group_modify(~{
      M  <- as.matrix(.x[, pdim_ot])
      Mn <- M / sqrt(rowSums(M^2))              # L2-normalize -> cosine via dot product
      tibble(period = .x$period, dist = 1 - as.vector(Mn %*% Mn[1, ]))
    }) |>
    ungroup()

  # Label each line directly at its last period (and drop the color legend) so you
  # don't have to match colors to names.
  ends <- drift_ot |> group_by(word) |>
    slice_max(as.integer(period), n = 1, with_ties = FALSE) |> ungroup()
  p_ot <- ggplot(drift_ot, aes(period, dist, group = word, color = word)) +
    geom_line(linewidth = 0.9) +
    geom_point(size = 2.6) +
    ggrepel::geom_text_repel(data = ends, aes(label = word),
                             hjust = 0, direction = "y", nudge_x = 0.18, size = 3.2,
                             segment.alpha = 0.3, max.overlaps = 20, show.legend = FALSE) +
    scale_color_brewer(palette = "Paired", guide = "none") +
    scale_x_discrete(expand = expansion(mult = c(0.04, 0.22))) +
    labs(title = "Semantic drift over time (MacBERTh)",
         subtitle = paste0("Cosine distance from each word's earliest-period meaning (",
                           per_levels[1], "). Rising = drifting away; flat = stable."),
         x = "Period", y = "Distance from earliest period") +
    theme_minimal(base_size = 12) +
    theme(plot.title = element_text(face = "bold"))
  print(p_ot)
  ggsave(file.path(output_path, "07b_diachronic_over_time.png"), p_ot,
         width = 12, height = 7, dpi = 150)
}
```

### What a word meant, then vs. later (diachronic explorer)

The drift plot above shows a word's meaning *moved*; this fills in *to what*. For each
diachronic target word and each period it gives the word's **distinctive collocates in
that period** plus a **real usage quote from that period** — so you can read "what
*sister* meant in the first period" vs. "what it meant in the last." Three views: an
**interactive drift** (hover a point for that period's meaning), a **filterable
period-by-period table**, and a **standalone Shiny app**. Uses the §11 diachronic
targets, the MacBERTh prototypes, and the §6 word-context helpers.

```{r diachronic-meaning-setup, eval=have_diachr}
dwm_ok <- have_diachr && have(proto_path) && exists(".gl_tok")
if (!dwm_ok) {
  cat("[skip] need diachronic artifacts + the §6 word-context helpers (.gl_tok).\n")
} else {
  if (exists("pj")) {
    per_lv <- pj$periods$name; per_lo <- pj$periods$start; per_hi <- pj$periods$end
  } else {
    per_lv <- sort(unique(c(change$period_a, change$period_b)))
    per_lo <- as.integer(sub("-.*", "", per_lv)); per_hi <- as.integer(sub(".*-", "", per_lv))
  }
  doc_period <- vapply(docs$year, function(y) {
    if (is.na(y)) return(NA_character_)
    h <- which(per_lo <= y & y <= per_hi); if (length(h)) per_lv[h[1]] else NA_character_
  }, character(1))
  targets <- sort(unique(change$word))

  # Period-specific distinctive collocates (lift within a period's documents).
  period_collocates <- function(word, rows, n = 8, min_co = 3) {
    w <- tolower(gsub("[^a-z]", "", word)); tok <- .gl_tok[rows]
    has <- which(vapply(tok, function(d) w %in% d, logical(1)))
    if (length(has) < min_co) return(NA_character_)
    co <- table(unlist(tok[has])); co <- co[names(co) != w & as.integer(co) >= min_co]
    if (!length(co)) return(NA_character_)
    base <- table(unlist(tok))
    lift <- (as.numeric(co) / length(has)) / (as.numeric(base[names(co)]) / length(tok))
    paste(names(co)[order(lift, decreasing = TRUE)][seq_len(min(n, length(co)))], collapse = ", ")
  }

  .dwm_cache <- file.path(output_path, sprintf("diachronic_word_meaning_K%d.rds", K))
  if (file.exists(.dwm_cache)) {
    dwm <- readRDS(.dwm_cache); cat("Loaded cached diachronic word-meaning table.\n")
  } else {
    cat("Building diachronic word-meaning table (one-time; cached)...\n")
    dwm <- purrr::map_dfr(targets, function(w) purrr::map_dfr(per_lv, function(p) {
      rows <- which(doc_period == p)
      tibble::tibble(word = w, period = p, n_docs = length(rows),
                     collocates = period_collocates(w, rows),
                     usage = corpus_usage(w, rows))
    }))
    saveRDS(dwm, .dwm_cache)   # the Shiny app reads this
  }
}
```

```{r diachronic-meaning-table, eval=have_diachr}
if (exists("dwm_ok") && dwm_ok) {
  datatable(
    dwm |> dplyr::transmute(Word = word, Period = period, Docs = n_docs,
                            `Collocates (this period)` = collocates,
                            `Usage (this period)` = usage),
    filter = "top", rownames = FALSE,
    caption = paste0("What each word meant, period by period: distinctive collocates + a real usage quote ",
                     "from that period's articles. Filter the Word column to read one word's trajectory."),
    options = list(pageLength = 12, scrollX = TRUE))
}
```

```{r diachronic-meaning-drift, eval=have_diachr, fig.height=7}
if (exists("dwm_ok") && dwm_ok) {
  proto_e <- arrow::read_parquet(proto_path)
  pdim <- grep("^dim_", names(proto_e), value = TRUE)
  .pc  <- prcomp(as.matrix(proto_e[, pdim]), center = TRUE)
  proto_e$PC1 <- .pc$x[, 1]; proto_e$PC2 <- .pc$x[, 2]
  show_w <- head(if (exists("word_order")) word_order else
                   (change |> dplyr::group_by(word) |> dplyr::summarise(m = max(apd, na.rm = TRUE)) |>
                      dplyr::arrange(dplyr::desc(m)) |> dplyr::pull(word)), 10)
  pe <- proto_e |> dplyr::filter(word %in% show_w) |> dplyr::arrange(word, period) |>
    dplyr::left_join(dwm, by = c("word", "period"))
  pe$hover <- paste0("<b>", pe$word, " — ", pe$period, "</b><br>collocates: ",
                     ifelse(is.na(pe$collocates), "—", pe$collocates),
                     "<br><i>", ifelse(is.na(pe$usage), "", substr(pe$usage, 1, 90)), "</i>")
  plotly::plot_ly(pe, x = ~PC1, y = ~PC2, color = ~word, text = ~hover, hoverinfo = "text",
                  type = "scatter", mode = "lines+markers",
                  marker = list(size = 9), line = list(width = 1.5)) |>
    plotly::layout(title = "Diachronic word meaning — hover a point for that period's collocates + usage",
                   xaxis = list(title = "PC1"), yaxis = list(title = "PC2"))
}
```

> **Standalone app — Diachronic Word Explorer (`diachronic_word_app/app.R`).** Pick a
> word from a dropdown and see its meaning **period-by-period** (collocates + a usage
> quote) next to its drift path. Reads the cached `diachronic_word_meaning_K{K}.rds` +
> the MacBERTh prototypes. Run locally (chunk below is `eval=FALSE`):

```{r run-diachronic-app, eval=FALSE}
shiny::runApp("diachronic_word_app", launch.browser = TRUE)
```

---

## 11b. Within-Topic Vocabulary Changepoints

For each STM topic, find the year that most sharply splits its **vocabulary**
(maximizing Jensen-Shannon divergence between the pooled word distributions
before vs. after), then show which words rose or fell across that split — the
topic-level companion to §11's word-level diachrony. Built from the row-aligned
`theta` + `docs$year` + `modeled_clean` (the already-cleaned bag-of-words), so it
works for whatever scenario is loaded. Detection is **cached** to an `.rds`, so
the first knit takes a few minutes and re-knits are instant.

```{r vocab-changepoint, fig.width=14, fig.height=22}
# ---- helpers --------------------------------------------------------------
.row_words <- function(rows) {                       # cleaned words for doc rows
  w <- unlist(strsplit(paste(modeled_clean[rows], collapse = " "), "\\s+"))
  w[nchar(w) >= 4]                                   # already stopworded/lemmatized
}
.js_divergence <- function(wa, wb) {
  if (length(wa) < 50 || length(wb) < 50) return(0)
  vu <- union(unique(wa), unique(wb))
  pa <- as.numeric(table(factor(wa, levels = vu))) / length(wa)
  pb <- as.numeric(table(factor(wb, levels = vu))) / length(wb)
  m  <- (pa + pb) / 2; eps <- 1e-12
  kl <- function(p, q) sum(p * log2((p + eps) / (q + eps)), na.rm = TRUE)
  (kl(pa, m) + kl(pb, m)) / 2
}
.yr <- docs$year
find_cp <- function(t, min_side = 15) {
  thr  <- stats::quantile(theta[, t], 0.75, na.rm = TRUE)
  rows <- which(theta[, t] >= thr & !is.na(.yr))
  if (length(rows) < 2 * min_side) return(list(year = NA_integer_, max_div = NA_real_))
  ry   <- .yr[rows]
  cand <- sort(unique(ry))
  cand <- cand[vapply(cand, function(y)
    sum(ry <= y) >= min_side && sum(ry > y) >= min_side, logical(1))]
  if (!length(cand)) return(list(year = NA_integer_, max_div = NA_real_))
  divs <- vapply(cand, function(y)
    .js_divergence(.row_words(rows[ry <= y]), .row_words(rows[ry > y])), numeric(1))
  list(year = as.integer(cand[which.max(divs)]), max_div = max(divs))
}
side_words <- function(t, split, side) {
  thr  <- stats::quantile(theta[, t], 0.75, na.rm = TRUE)
  rows <- which(theta[, t] >= thr & !is.na(.yr))
  rows <- if (side == "early") rows[.yr[rows] <= split] else rows[.yr[rows] > split]
  f <- sort(table(.row_words(rows)), decreasing = TRUE)
  tibble(word = names(f), proportion = as.integer(f) / sum(f))
}

# ---- detect (cached) ------------------------------------------------------
cp_rds <- file.path(output_path, sprintf("topic_changepoints_K%d.rds", K))
if (file.exists(cp_rds)) {
  changepoints <- readRDS(cp_rds); cat("Loaded cached changepoints.\n")
} else {
  cat("Detecting vocabulary changepoints for", ncol(theta), "topics (one-time)...\n")
  changepoints <- lapply(seq_len(ncol(theta)), function(t) {
    cp <- find_cp(t)
    cat(sprintf("  T%-2d %-36s %s\n", t, str_trunc(topic_labels[t], 34),
                if (is.na(cp$year)) "(too few docs)" else sprintf("split %d (JS %.3f)", cp$year, cp$max_div)))
    cp
  })
  saveRDS(changepoints, cp_rds)
}

# ---- summary table --------------------------------------------------------
cp_df <- tibble(topic = seq_len(ncol(theta)), label = topic_labels,
                prevalence = topic_prevalence,
                split_year = vapply(changepoints, function(x) x$year, integer(1)),
                max_jsd    = vapply(changepoints, function(x) x$max_div, numeric(1))) |>
  arrange(desc(prevalence))
print(cp_df, n = Inf)
write_csv(cp_df, file.path(output_path, sprintf("topic_changepoints_K%d.csv", K)))

# ---- per-topic before/after word-shift plots, 4 per page ------------------
ord <- order(topic_prevalence, decreasing = TRUE)
vocab_plots <- lapply(ord, function(t) {
  cp <- changepoints[[t]]
  if (is.na(cp$year))
    return(ggplot() + annotate("text", x = 0, y = 0, size = 6,
                               label = paste0("T", t, ": insufficient data")) + theme_void())
  sy <- cp$year
  cmpw <- full_join(
    side_words(t, sy, "early") |> rename(early = proportion),
    side_words(t, sy, "late")  |> rename(late  = proportion), by = "word") |>
    replace_na(list(early = 1e-4, late = 1e-4)) |>
    mutate(lr = log2(early / late), avg = (early + late) / 2) |>
    filter(avg > 0.001) |> arrange(desc(abs(lr)))
  el <- paste0("More ≤", sy); ll <- paste0("More >", sy)
  pw <- bind_rows(head(filter(cmpw, lr > 0), 15), head(filter(cmpw, lr < 0), 15)) |>
    mutate(direction = ifelse(lr > 0, el, ll), word = reorder(word, lr))
  ggplot(pw, aes(lr, word, fill = direction)) +
    geom_col(alpha = 0.85) + geom_vline(xintercept = 0, linewidth = 0.8) +
    scale_fill_manual(values = setNames(c("#6E8B3D", "#556B2F"), c(el, ll))) +
    labs(title = paste0("T", t, ": ", str_trunc(topic_labels[t], 45)),
         subtitle = sprintf("Changepoint %d  |  JSD %.2f  |  prevalence %.1f%%",
                            sy, cp$max_div, topic_prevalence[t] * 100),
         x = paste0("← after ", sy, "     before ", sy, " →"), y = NULL, fill = NULL) +
    theme_minimal(base_size = 10) +
    theme(legend.position = "none", plot.title = element_text(size = 12, face = "bold"))
})

per_page <- 4L; n_pages <- ceiling(length(vocab_plots) / per_page)
for (pg in seq_len(n_pages)) {
  s <- (pg - 1) * per_page + 1; e <- min(s + per_page - 1, length(vocab_plots))
  comb <- wrap_plots(vocab_plots[s:e], ncol = 2) +
    plot_annotation(title = sprintf("Within-Topic Vocabulary Changepoints — page %d of %d", pg, n_pages))
  print(comb)
  ggsave(file.path(output_path, sprintf("08_vocab_changepoint_K%d_page%d.png", K, pg)),
         comb, width = 14, height = 22, dpi = 150, limitsize = FALSE)
}
cat("\nSaved", n_pages, "changepoint page(s).\n")
```

---

## 12. Author Topic Profiles

For each prolific *named* author, what do they tend to write *about*? This shows
each author's **mean topic mix** — the average STM topic proportions across all
their articles — as a stacked bar (each bar sums to 100%).

*(This replaced a Burrows' Delta stylometry section. Stylometric authorship
attribution needs far more text per author than these era slices provide, whereas
topic profiles are robust at any size and answer the more useful "who wrote about
what" question. A cross-corpus version like your Chart 5 — WE next to RSM — belongs
in the joint comparison.)*

We restrict to the most prolific named authors (>= 10 substantial articles each)
so the profiles are stable.

```{r stylo-prep}
# Build a per-author sample from the natural-language text (modeled_raw).
# Exclude non-author bylines: "Unknown", the periodical name, OCR/column junk
# (anything bracketed), and initials-only signatures (no real surname), since
# those would pollute the authorship clustering.
author_blocklist <- c("unknown", "editor", "the editor", "selected", "anonymous")
# Organizational / advertisement / masthead bylines that aren't personal authors.
org_keywords <- "exponent|publisher|office|ticket|company|\\bco\\b|union|depot|emporium|store|bureau|society|association|department"
is_real_author <- function(a) {
  s  <- str_squish(a)
  al <- str_replace_all(str_to_lower(s), "[’‘']", "'")  # normalize curly quotes
  has_surname <- str_detect(s, "[A-Za-z]{3,}")        # at least one 3+ letter word
  !is.na(a) & s != "" & !str_starts(s, "\\[") & !str_ends(s, ",") &
    !(al %in% author_blocklist) & !str_detect(al, org_keywords) & has_surname
}

sty_tbl <- docs |>
  mutate(text = modeled_raw,
         n_words = str_count(text, "\\S+"),
         author_clean = str_squish(author)) |>
  filter(is_real_author(author_clean), n_words >= 150)

top_authors <- sty_tbl |> count(author_clean, sort = TRUE) |>
  filter(n >= 10) |> slice_head(n = 12) |> pull(author_clean)
cat("Most prolific named authors used for stylometry:\n")
print(top_authors)

# Concatenate each author's articles into a few labeled samples for stylo.
# stylo wants a named list of long character strings (one "text" per sample).
make_samples_per_author <- function(df, max_words = 5000) {
  out <- list()
  for (a in top_authors) {
    txt <- df |> filter(author_clean == a) |> pull(text) |> paste(collapse = " ")
    words <- str_split(txt, "\\s+")[[1]]
    words <- words[words != ""]
    # split into ~max_words chunks so each author yields 2-4 comparable samples
    n_chunk <- max(1, floor(length(words) / max_words))
    n_chunk <- min(n_chunk, 4)
    if (n_chunk < 1) next
    sizes <- rep(floor(length(words) / n_chunk), n_chunk)
    idx <- c(0, cumsum(sizes))
    for (i in seq_len(n_chunk)) {
      seg <- words[(idx[i] + 1):idx[i + 1]]
      key <- sprintf("%s_%d", str_replace_all(a, "[^A-Za-z]", ""), i)
      out[[key]] <- paste(seg, collapse = " ")
    }
  }
  out
}
sty_samples <- make_samples_per_author(sty_tbl)
cat("\nStylometry samples:", length(sty_samples),
    "from", length(top_authors), "authors\n")
```

```{r stylo-delta, fig.height=10}
if (length(top_authors) >= 1) {
  # For each prolific named author, the MEAN topic mix across their articles, from
  # the row-aligned theta (doc x topic). Stacked bar per author -> sums to 100%.
  prof <- purrr::map_dfr(top_authors, function(a) {
    rows <- sty_tbl$row_index[sty_tbl$author_clean == a]
    tibble(author     = a,
           n_articles = length(rows),
           topic      = factor(topic_labels, levels = topic_labels),
           prop       = colMeans(theta[rows, , drop = FALSE]))
  })
  # Most prolific first.
  auth_order <- prof |> distinct(author, n_articles) |> arrange(desc(n_articles)) |> pull(author)
  prof <- prof |> mutate(author = factor(author, levels = auth_order))

  prof_sub <- paste0("Mean topic mix per prolific named author  (",
                     length(top_authors), " authors, >= 10 articles each)")

  # (a) VERTICAL — authors as columns, topics stacked to 100% (matches the pasted "Chart 5").
  p_prof_v <- ggplot(prof, aes(author, prop, fill = topic)) +
    geom_col(width = 0.85, position = "stack") +
    scale_y_continuous(labels = percent_format(), expand = expansion(mult = c(0, 0.02))) +
    scale_fill_manual(values = topic_col_lab) +
    labs(title = "Author topic profiles (vertical)", subtitle = prof_sub,
         x = NULL, y = "Mean topic proportion", fill = "Topic") +
    theme_minimal(base_size = 11) +
    theme(plot.title = element_text(face = "bold"),
          axis.text.x = element_text(angle = 45, hjust = 1),
          legend.text = element_text(size = 7), legend.key.size = unit(0.4, "cm"))
  print(p_prof_v)
  ggsave(file.path(output_path, "09_author_topic_profiles_vertical.png"), p_prof_v,
         width = 13, height = 8, dpi = 150)

  # (b) HORIZONTAL — authors as rows (easier label-reading with many authors/topics).
  p_prof_h <- ggplot(prof, aes(prop, factor(author, levels = rev(auth_order)), fill = topic)) +
    geom_col(width = 0.85, position = "stack") +
    scale_x_continuous(labels = percent_format(), expand = expansion(mult = c(0, 0.02))) +
    scale_fill_manual(values = topic_col_lab) +
    labs(title = "Author topic profiles (horizontal)", subtitle = prof_sub,
         x = "Mean topic proportion", y = NULL, fill = "Topic") +
    theme_minimal(base_size = 11) +
    theme(plot.title = element_text(face = "bold"),
          legend.text = element_text(size = 7), legend.key.size = unit(0.4, "cm"))
  print(p_prof_h)
  ggsave(file.path(output_path, "09_author_topic_profiles_horizontal.png"), p_prof_h,
         width = 13, height = 8, dpi = 150)

  # Each author's single dominant topic, as a table.
  prof |> group_by(author, n_articles) |>
    slice_max(prop, n = 1, with_ties = FALSE) |> ungroup() |>
    transmute(Author = author, Articles = n_articles,
              `Top topic` = as.character(topic), Share = scales::percent(prop, 0.1)) |>
    arrange(desc(Articles)) |> print(n = Inf)
} else {
  cat("No prolific named authors (>= 10 substantial articles) in this scenario --",
      "this slice is mostly institutional/unknown bylines. The full run has more.\n")
}
```

---

## 13. Save Session

```{r save-session}
saveRDS(list(
  K            = K,
  D_jsd        = D_jsd,
  hc           = hc,
  clusters     = clusters,
  mds_coords   = mds,
  topic_labels = topic_labels,
  fit_date     = Sys.time()
), file.path(output_path, sprintf("advanced_report_objects_K%d.rds", K)))
cat("Saved report objects for K =", K, "\n")
```

---

## Notes & Tuning Hints

- **K is not hardcoded.** Set `pin_K` in §2 to choose the model (35 is
  canonical). Every artifact path is suffixed by K, so K=20 dev runs and K=35
  production runs never collide. To switch K you (a) run the linker checkpoint
  chunk with the new `chosen_K`, then (b) re-run the three Python scripts with
  that K, then (c) re-knit with `pin_K` updated.
- **Graceful skipping.** Sections 8–11 check for their Python artifact and print
  a "run script X" note if it's missing, so the notebook always knits even
  before the compute layer has finished.
- **Why contextual embeddings for diachrony (§11).** Training one word2vec per
  period and Procrustes-rotating them (the old approach) is fragile: the
  rotation is fit on shared vocabulary and small periods give noisy spaces.
  MacBERTh embeds each occurrence in its sentence in a single pretrained space —
  no rotation, and we get sense-level change. Edit `DIACHRONIC_TARGETS` and
  `DEFAULT_PERIOD_BOUNDS` in `scripts/config.py` to change words/periods.
- **Stylometry (§12)** uses `stylo`'s bootstrap consensus tree, which aggregates
  groupings across MFW band sizes (100–300 here) so the result doesn't depend on
  one arbitrary feature count — more defensible than a single Delta dendrogram.
- **Compute layer is resumable.** Each Python script checkpoints; re-running
  after an interruption resumes. The knit itself never trains anything, so it
  won't time out.
```