
---
title: "Topic-to-Article Linker - Relief Society Magazine"
author: "Birch"
date: "`r Sys.Date()`"
output:
  html_notebook:
    toc: true
    toc_float: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Topic-to-Article Linker - Relief Society Magazine

This notebook runs STM topic modeling on whatever RSM volumes are placed in the
input folder, then links each topic back to specific articles from the inventory
so you can identify concrete evidentiary examples for each topic bucket.
Drop Vol##_#### folders into the input directory and run.

---

## 1. Load Packages

```{r load-packages}
library(tm)
library(stm)
library(tidyverse)
library(readxl)
library(stopwords)
library(igraph)
library(DT)
library(textstem)    # For lemmatization
library(pheatmap)    # For heatmaps
library(scales)      # For percent formatting
library(wordcloud)
library(ggridges)    # For ridgeline plots
library(patchwork)   # For plot composition (|, /)
library(ggrepel)     # For labeled scatter points
library(hunspell)
library(stringdist)

set.seed(12345)
cat("Packages loaded.\n")
```

---

## 2. Set Paths

```{r set-paths}
cat(Sys.getenv("HOME"), "\n")

# ---- Scenario (corpus slice) ----------------------------------------------
# Pick which slice of the RSM corpus to model. Each scenario writes to its own
# subfolder output_linked/<tag>/ so runs never collide.
#   "RSMfull"      -> entire corpus (no year filter)
#   "RSM1913-1934" -> years 1913-1934
#   "RSM1935-1950" -> years 1935-1950
#   "RSM1951-1970" -> years 1951-1970
#   "auto"         -> run on WHATEVER volumes are physically in input2 and derive
#                     the tag from the observed year span. Drop volumes in, run.
scenario <- "RSM1935-1950"
.scenario_ranges <- list(
  "RSMfull"      = c(-Inf, Inf),
  "RSM1914-1934" = c(1914, 1934),
  "RSM1935-1950" = c(1935, 1950),
  "RSM1951-1970" = c(1951, 1970)
)
scenario_years <- if (scenario %in% names(.scenario_ranges)) {
  .scenario_ranges[[scenario]]
} else {
  c(-Inf, Inf)   # "auto"/unknown: no year filter; corpus = whatever's in input2
}

# Environment-aware roots. On Windows EVERYTHING lives on the local Rachel hard
# drive -- corpus, inventory, output -- so OneDrive sync never touches the heavy
# I/O. The Rachel input2 holds the full 57-volume canon (1914-1970). The scenario
# subfolder is appended to output_root in section 5, once observed years are known.
if (.Platform$OS.type == "windows") {
  input_path     <- "C:/Users/birch/Rachel/GMU/Dissertation/textanalysis/Topicmodel/input2"
  output_root    <- "C:/Users/birch/Rachel/GMU/Dissertation/textanalysis/Claudepythonexperimentadvtext_RSM/output_linked"
  inventory_path <- "C:/Users/birch/Rachel/GMU/Dissertation/textanalysis/Articleextractionrfiles/Administrationorganization/RSM_article_inventory_vols1-57.xlsx"
} else {
  input_path     <- "/home/rbirch/rbirch/Topicmodel/input2"
  output_root    <- "/home/rbirch/rbirch/Topicmodel/output_linked_RSM"
  inventory_path <- "/home/rbirch/rbirch/Articleextractionrfiles/Administrationorganization/RSM_article_inventory_vols1-57.xlsx"
}

# output_path is finalized in section 5 (the "auto" tag needs observed years);
# point it at the root for now so any earlier write still lands somewhere sane.
output_path <- output_root
if (!dir.exists(output_root)) dir.create(output_root, recursive = TRUE)

cat("OS:       ", .Platform$OS.type, "\n")
cat("Scenario: ", scenario, " | year filter: ",
    if (all(is.finite(scenario_years))) paste(scenario_years, collapse = "-") else "none",
    "\n", sep = "")
cat("Input:      ", input_path, "\n")
cat("Output root:", output_root, "\n")
cat("Inventory:  ", inventory_path, "\n")
```

---
```{r}
# Check if anything exists at that path
file.exists("C:/Users/birch/Rachel/GMU/Dissertation/textanalysis/Topicmodel/input2")
dir.exists("C:/Users/birch/Rachel/GMU/Dissertation/textanalysis/Topicmodel/input2")

# Search from home for any .txt files
head(list.files(Sys.getenv("HOME"), pattern = "\\.txt$", recursive = TRUE), 20)
list.files("~/Topicmodel/input2", recursive = FALSE)

# Confirm the full path
list.dirs("~/Topicmodel/input2", recursive = FALSE, full.names = FALSE)

```


## 3. Load Article Inventory

```{r load-inventory}
# See what's actually in the folder
inventory <- read_excel(inventory_path, sheet = "Article Inventory")

cat("Inventory loaded:", nrow(inventory), "articles\n")
cat("Columns:", paste(names(inventory), collapse = ", "), "\n\n")

# Detect which volumes are in the input folder
input_vol_dirs <- list.dirs(input_path, recursive = FALSE, full.names = FALSE)
input_vol_nums <- as.integer(str_extract(input_vol_dirs, "^\\d+|(?<=Vol)\\d+"))
input_vol_nums <- sort(input_vol_nums[!is.na(input_vol_nums)])

cat("Volumes detected in input:", paste(input_vol_nums, collapse = ", "), "\n")

# Filter inventory to only the volumes present in input
inventory_subset <- inventory %>%
  filter(Volume %in% input_vol_nums)

cat("Matching inventory articles:", nrow(inventory_subset), "\n")
```

---

## 4. Import Article Files

```{r import-files}
all_files <- list.files(path = input_path, full.names = TRUE, recursive = TRUE)
file_paths <- all_files[grepl("\\.txt$", all_files, ignore.case = TRUE)]

# Exclude backup folders, QC reports, cleanup files.
# Case-insensitive: machine-generated QC files are named "_qc_report_volNN.txt"
# (lowercase), which a case-sensitive "QC_Report" pattern would let slip through.
file_paths <- file_paths[!grepl("_backups|qc_report|cleanup", file_paths, ignore.case = TRUE)]

cat("Total .txt files found:", length(file_paths), "\n\n")

# ---- Header-stripping helper ----
# Many article .txt files start with metadata headers that, if left in,
# pollute the corpus — "TITLE: X\nAUTHOR: Y\nDATE: Z" lines bleed in as
# regular words. Some files use colons, some don't, some prefix with a
# volume/issue identifier like "23b" or "Vol 26 Issue 23b". This handles
# all those forms by iterating until no metadata pattern matches.
strip_metadata_header <- function(raw) {
  # Strip BOM if present
  raw <- stringr::str_remove(raw, "^\\uFEFF")

  metadata_keywords <- c("title", "author", "date", "filename",
                         "year", "volume", "issue", "page", "type")
  keyword_alt <- paste(metadata_keywords, collapse = "|")

  prev <- ""
  while (raw != prev) {
    prev <- raw
    # Bracket-style header  e.g. "[Title: X]"
    raw <- stringr::str_remove(raw, "^\\[[^\\]]*\\]\\s*\\n?")
    # "Vol 26 Issue 23b" / "Issue 23" identifier on its own line
    raw <- stringr::str_remove(raw,
      "(?im)^(?:vol(?:ume)?\\s*\\d+[a-z]?\\b\\s*)?(?:issue\\s*\\d+[a-z]?\\b\\s*)?\\n")
    # Bare issue identifier like "23b" alone on the first line
    raw <- stringr::str_remove(raw, "(?i)^\\d+[a-z]?\\s*\\n")
    # "Keyword: value\n" line (the colon form)
    raw <- stringr::str_remove(raw,
      paste0("(?im)^(", keyword_alt, ")\\s*:[^\\n]*\\n"))
    # "Keyword\nValue\n" (label on its own line, value on next line)
    raw <- stringr::str_remove(raw,
      paste0("(?im)^(", keyword_alt, ")\\s*\\n[^\\n]+\\n"))
    # Leading blank lines
    raw <- stringr::str_remove(raw, "^\\s*\\n+")
  }
  raw
}

# Read all files, stripping metadata headers as we go
raw_texts <- tibble(
  filepath = file_paths,
  filename = basename(file_paths),
  text = map_chr(file_paths, ~strip_metadata_header(read_file(.x)))
)

cat("Read", nrow(raw_texts), "files.\n")
```

---

## 5. Extract Metadata & Join to Inventory

```{r extract-metadata}
# Extract metadata from directory structure: Vol{num}_{year}/{Month}/filename
raw_texts <- raw_texts %>%
  mutate(
    # Parse from directory path
    volume_folder = str_extract(filepath, "Vol\\d+_\\d{4}"),
    volume_num = as.integer(str_extract(volume_folder, "(?<=Vol)\\d+")),
    year = as.integer(str_extract(volume_folder, "\\d{4}$")),
    # Month from directory
    month = str_extract(filepath,
      "(?<=/)(January|February|March|April|May|June|July|August|September|October|November|December)(?=/)"),
    doc_id = row_number(),
    word_count = str_count(text, "\\S+")
  )

# ---- Scenario year filter + output folder (see section 2 set-paths) ----
# Named scenarios slice the full corpus by year; "auto" keeps whatever volumes
# are physically in input2. Once observed years are known we finalize the output
# subfolder (and, for "auto", its tag), so ALL output_path writes below land in
# output_linked/<tag>/.
if (all(is.finite(scenario_years))) {
  .before <- nrow(raw_texts)
  raw_texts <- raw_texts %>%
    filter(!is.na(year), year >= scenario_years[1], year <= scenario_years[2]) %>%
    mutate(doc_id = row_number())
  cat("Scenario '", scenario, "': kept ", nrow(raw_texts), " of ", .before,
      " docs in years [", scenario_years[1], "-", scenario_years[2], "]\n", sep = "")
}
scenario_tag <- if (scenario %in% names(.scenario_ranges)) {
  scenario
} else {
  sprintf("RSM%d-%d", min(raw_texts$year, na.rm = TRUE), max(raw_texts$year, na.rm = TRUE))
}
output_path <- file.path(output_root, scenario_tag)
if (!dir.exists(output_path)) dir.create(output_path, recursive = TRUE)
cat("Scenario tag: ", scenario_tag, "  ->  ", output_path, "\n", sep = "")
cat("  (use this tag for the report's `scenario` and Python ADV_SCENARIO)\n")

# Join to inventory by filename
raw_texts <- raw_texts %>%
  left_join(
    inventory_subset %>% select(Filename, Title, Author, Article_Type, Volume, Month, Issue),
    by = c("filename" = "Filename")
  )

# ---- De-duplicate Author == Title at the metadata source ----
# Some inventory rows copy the SAME string into both Title and Author (mostly
# advertisements and bare signature lines, e.g. a business or person's name set
# in the byline slot). That isn't a real authorship attribution -- it's an
# artifact of the inventory builder. When Author merely echoes Title
# (case/whitespace-insensitive), blank it so the browser and the author-topic
# analysis don't treat the title as an author. NOTE: this runs AFTER the join
# but the surname-protection auto-build (§6) parses inventory_subset$Author
# directly, so real bylines used for name protection are unaffected.
.norm <- function(x) stringr::str_squish(stringr::str_to_lower(tidyr::replace_na(as.character(x), "")))
dup_author_n <- sum(.norm(raw_texts$Author) != "" &
                    .norm(raw_texts$Author) == .norm(raw_texts$Title), na.rm = TRUE)
raw_texts <- raw_texts %>%
  mutate(Author = if_else(.norm(Author) != "" & .norm(Author) == .norm(Title),
                          NA_character_, Author))
cat("Author == Title duplicates blanked:", dup_author_n, "\n")

match_count <- sum(!is.na(raw_texts$Title))
cat("Matched to inventory:", match_count, "of", nrow(raw_texts), "files\n")
cat("Unmatched:", sum(is.na(raw_texts$Title)), "\n\n")

raw_texts %>%
  filter(!is.na(Title)) %>%
  select(filename, Title, Author, Article_Type, Volume, year) %>%
  head(10) %>%
  print()
```

---

## 5b. Filter Out Non-Content Articles (Optional)

All article types are included by default. Uncomment lines to exclude any.

```{r filter-content}
cat("Article types before filtering:\n")
raw_texts %>%
  count(Article_Type, sort = TRUE) %>%
  print(n = 20)

cat("\n")

# ============================================================
# EXCLUDE THESE ARTICLE TYPES FROM MODELING
# Add types here ONLY if you want to remove them.
# All types are included by default.
# ============================================================
exclude_types <- c(
  "Board",         # Board member roster lists (pure name rosters, not content)
  "Contents"       # Tables of contents (title/page-number lists)
  # "Misc"         # KEPT IN — ads are part of the print culture record
)

exclude_patterns <- c(
  "BOARD",          # Catches board files not matched by Article_Type
  "CONTENTS",       # Catches contents files not matched by Article_Type
  # Volume index pages (typed as "Article" in the inventory but functionally
  # tables of contents — pure title/page-number listings, not editorial content).
  # Matches "Index-Vol", "Index_Vol", "IndexVol" variants.
  "Index[-_]?Vol"
)

before_count <- nrow(raw_texts)

raw_texts <- raw_texts %>%
  filter(
    !(Article_Type %in% exclude_types) | is.na(Article_Type)
  ) %>%
  filter(
    !str_detect(filename, paste(c(exclude_patterns, "^$"), collapse = "|"))
  )

cat("Filtered:", before_count - nrow(raw_texts), "documents removed\n")
cat("Remaining:", nrow(raw_texts), "articles for modeling\n\n")

raw_texts <- raw_texts %>%
  mutate(doc_id = row_number())
```

---

## 6. Text Cleaning

```{r clean-text}
standard_stopwords <- stopwords::stopwords("en", source = "snowball")

custom_stopwords <- c(
  "the", "of", "and", "in", "to", "a", "is", "that", "it", "for",
  "as", "on", "with", "be", "was", "by", "are", "from", "or", "an",
  "at", "this", "which", "have", "has", "had", "but", "not", "can",
  "will", "been", "were", "their", "they", "we", "our", "would",
  "there", "what", "so", "if", "who", "than", "may", "also",
  "mrs", "mr", "miss", "dr", "ms",
  "january", "february", "march", "april", "may", "june",
  "july", "august", "september", "october", "november", "december",
  "vol", "page", "number", "volume", "board", "officer", "general",
  "thee", "thou", "whom", "no", "num", "pp", "pg",
  "issue", "nth", "th", "st", "nd", "rd",
  # Metadata-header words (belt-and-suspenders against header-stripping misses)
  "title", "author", "authors", "byline", "date", "filename",
  "year", "volumes", "pages", "issn", "doi",
  # Author-placeholder words — bare "Unknown" / "Anonymous" tokens that
  # the extraction pipeline writes when the original byline is missing.
  # Without this, every author-less document carries a token "unknown"
  # which the model then clusters around.
  "unknown", "anonymous", "none",
  # RSM-specific boilerplate
  "relief", "society", "magazine", "bulletin",
  "latter", "day",
  # Masthead / publication boilerplate
  "editor", "publisher", "publishe", "published", "publish",
  "assistant", "monthly", "salt", "lake", "city", "utah",
  "term", "copy", "year", "month", "cts", "cent",
  "subscription", "subscribe", "postage", "mail", "deliver",
  "advertise", "advertiser", "advertisement", "advertising",
  "rate", "discount", "liberal", "regular", "space", "line",
  "nonpanel", "square", "extra",
  # Table of contents vocabulary
  "content", "contents", "frontmatter", "front", "matter",
  # Common structural words
  "program", "report", "reports", "committee", "meeting",
  "secretary", "sec", "secy", "asst", "pres", "treas",
  "treasurer", "president", "vice"
)

years_as_words <- as.character(unique(na.omit(raw_texts$year)))

# OCR fragment / junk word blacklist — common broken words from digitized text
ocr_junk_stopwords <- c(
  # Suffix-only fragments
  "ing", "tion", "ment", "ness", "ings", "tive", "ance", "ence",
  "ered", "ters", "bers", "dren", "howe", "ould", "ight", "ther",
  "ated", "ting", "ally", "ible", "able", "ious", "eous", "ical",
  "onal", "ship", "ward", "wise", "less",
  # Truncated word fragments from OCR
  "deliv", "presi", "inter", "encour", "terest", "testi",
  "soci", "coun", "chil", "pariel", "organiza", "ganized",
  "ference", "musser", "selion",
  # Structural boilerplate remnants
  "column", "columns", "chapter", "section", "article",
  "continued", "copyright", "printed"
)

all_stopwords <- unique(c(standard_stopwords, custom_stopwords,
                          ocr_junk_stopwords, years_as_words))

# Regex patterns to catch OCR fragments not in the explicit list
is_ocr_fragment <- function(w) {
  grepl("^[a-z]{1,3}(tion|ment|ence|ness|ings|tive|ance)$", w) |
  grepl("^(pre|suf|dis|un|re)[a-z]{0,2}$", w) |
  grepl("^[^a-z]+$", w)
}

# ============================================================
# OCR VARIANT REMEDIATION
# Folds known OCR misreads into canonical forms BEFORE lemmatization,
# since lemmatize_words() only normalizes recognized English words.
# Build/edit this list from the `ocr-variant-audit` chunk output.
# ============================================================
ocr_fixes <- c(
  # Relief Society institutional vocabulary
  "\\brelef\\b"          = "relief",
  "\\brelelief\\b"       = "relief",
  "\\brellef\\b"         = "relief",
  "\\bsocety\\b"         = "society",
  "\\bsoclety\\b"        = "society",
  # Welfare / Depression-era discourse
  "\\bweifare\\b"        = "welfare",
  "\\bwelfaee\\b"        = "welfare",
  # Missionary / temple
  "\\bmissonary\\b"      = "missionary",
  "\\bmissioary\\b"      = "missionary",
  "\\bmissonaries\\b"    = "missionaries",
  "\\btempie\\b"         = "temple",
  # Suffrage / Progressive era civic discourse
  "\\bsuffage\\b"        = "suffrage",
  "\\bsuffeage\\b"       = "suffrage",
  "\\bsufferage\\b"      = "suffrage",
  "\\bsffrage\\b"        = "suffrage",
  "\\bsuffrag\\b"        = "suffrage",   # OCR fragment (missing 'e')
  "\\bsuffragea\\b"      = "suffrage",
  "\\bsuffagist\\b"      = "suffragist",
  # Kimball — OCR misreads only
  "\\bkimbal\\b"         = "kimball",
  "\\bkilmball\\b"       = "kimball",
  "\\bkimbalt\\b"        = "kimball",
  "\\bkinball\\b"        = "kimball",
  "\\bkmball\\b"         = "kimball",
  # Note: "brimhall" is a distinct Mormon surname — NOT folded.
  # Spafford (Belle S. Spafford, RS President 1945–1974) — OCR variants
  "\\bspaford\\b"        = "spafford",
  "\\bspafiord\\b"       = "spafford",
  # Legislature / constitution (carried over from earlier period coverage)
  "\\blegilature\\b"     = "legislature",
  "\\blegislatnre\\b"    = "legislature",
  "\\bconititutional\\b" = "constitutional",
  "\\bconsititution\\b"  = "constitution"
)

# ============================================================
# SURNAME PROTECTION — AUTO-BUILT FROM INVENTORY
#
# Maps surnames to opaque tokens so lemmatization doesn't collapse them
# into common nouns (e.g., "wells" → "well", losing Emmeline B. Wells).
#
# Strategy (two-tier):
#   (a) AUTO: parse every (first_name, surname) pair from inventory_subset$Author,
#       group by surname, build one context-anchored regex per surname.
#       Common-word surnames (Young, Snow, Wells, Smith, …) require a first
#       name or title to precede them — low false positives.
#       Unique surnames (Spafford, Lyman, …) can match with title only.
#   (b) OVERRIDES: hand-tuned regex for tricky cases (e.g., "Young" needs a
#       negative lookahead to exclude "Young Ladies"/"Young Men" YLMIA refs).
#       Overrides REPLACE the auto-built pattern for that surname.
#
# After topic fitting, surname_display (in §8) maps these back to readable names.
# ============================================================

# Common-word surnames — these are also ordinary English words, so we MUST
# require a preceding first name or title to avoid mistagging adjective/noun uses.
common_word_surnames <- c(
  "young", "snow", "wells", "smith", "white", "brown", "black", "green",
  "hall", "brooks", "stone", "bell", "bishop", "marsh", "park", "reed",
  "rice", "fields", "woods", "wood", "wright", "moore", "hill", "lake",
  "lee", "long", "rose", "field", "cook", "carpenter", "miller", "fisher",
  "shepherd", "page", "winter", "summer", "spring", "may", "love",
  # Words present in our custom_stopwords / boilerplate filtering — those will
  # be stripped anyway, but listed for transparency.
  "young", "wells"
)
common_word_surnames <- unique(common_word_surnames)

# Standard titles that may precede any surname
title_alt <- "mrs|sister|brother|president|elder|mother|bishop"

# ---- Non-name words ----
# Words that show up in the `Author` column because the source magazine
# pages used the byline slot for department headers, article-type markers,
# or editorial labels. Any author string CONTAINING one of these as a token
# is rejected outright — and any parsed first/last that lands on one of
# these is also dropped.
non_name_words <- c(
  # Editorial / department labels
  "anonymous", "various", "editorial", "frontispiece", "department",
  "presidency", "auxiliary", "hygiene", "magazine", "society",
  "primary", "ward", "stake", "office", "committee", "board",
  "general", "headquarters", "home", "relationships",
  # Article-type / structural markers
  "annual", "monthly", "review", "summary", "report", "reports",
  "minutes", "notice", "notes", "advertisement", "obituary",
  "biography", "tribute", "address", "lesson", "lessons",
  "guide", "outline", "leaflet", "bulletin",
  # Numbers / measurements that landed in author fields
  "million", "thousand", "hundred", "number", "page", "pages",
  # Placeholders / unknowns / staff titles
  "unknown", "none", "staff", "editor", "editors", "publisher",
  # OCR concatenation artifacts seen in the inventory
  "porterrissanen"
)
non_name_words <- unique(tolower(non_name_words))

# ---- non_surname_words ----
# These reject an entry only when they appear as the SURNAME (not the first
# name). Lets us keep "Joseph Smith" (Joseph is a legitimate first name) but
# drop "Mary Christ" (Christ as a surname is almost always a parse error /
# religious-figure reference, not an LDS author).
non_surname_words <- c(
  # Religious figures
  "christ", "jesus", "lord", "god",
  # Biblical figures whose names are also common first names in this corpus —
  # rejected ONLY as surnames; still usable as first names
  "luke", "john", "matthew", "mark", "paul", "peter",
  "moses", "abraham", "joseph", "isaac", "jacob", "samuel"
)
non_surname_words <- unique(tolower(non_surname_words))

# ---- Parse the inventory Author column → tibble(first_name, surname) ----
parse_authors <- function(author_strings) {
  author_strings <- author_strings[!is.na(author_strings)]
  author_strings <- author_strings[!author_strings %in% c("Unknown", "", "-")]
  author_strings <- unique(author_strings)

  parsed <- purrr::map_dfr(author_strings, function(a) {
    # Handle "Last, First M." → "First M. Last"
    if (stringr::str_detect(a, ",")) {
      parts <- stringr::str_split(a, ",", n = 2)[[1]]
      a <- paste(stringr::str_trim(parts[2]), stringr::str_trim(parts[1]))
    }
    a <- stringr::str_remove_all(a, "\\b(Jr\\.?|Sr\\.?|III?|IV)\\b")
    a <- stringr::str_squish(a)
    # Tokenize, strip initials / 1-letter tokens / titles
    tokens <- stringr::str_split(tolower(a), "\\s+")[[1]]
    titles_only <- c("mr", "mrs", "miss", "ms", "dr", "sister", "brother",
                     "elder", "president", "bishop", "mother")
    tokens <- tokens[nchar(tokens) > 1 & !tokens %in% titles_only]
    tokens <- stringr::str_remove_all(tokens, "[[:punct:]]")
    tokens <- tokens[nchar(tokens) > 1]
    if (length(tokens) < 2) return(NULL)
    # Reject entire string if ANY token is a non-name word —
    # catches "Hygiene Department", "Home Editor", "General Board", etc.
    if (any(tokens %in% non_name_words)) return(NULL)
    tibble::tibble(
      first_name = tokens[1],
      surname    = tail(tokens, 1)
    )
  })

  if (nrow(parsed) == 0) return(parsed)

  # ---- Post-parse cleanup: drop pairs that fail surname sanity checks ----
  parsed %>%
    dplyr::filter(
      # Length sanity: surnames between 3 and 15 chars
      # (drops concatenated OCR mashups like "porterrissanen")
      nchar(surname) >= 3,
      nchar(surname) <= 15,
      nchar(first_name) >= 2,
      # Alphabetic only
      !stringr::str_detect(surname, "[^a-z]"),
      # No 4+ char repeats (catches OCR garbage like "aaaaaa")
      !stringr::str_detect(surname, "(.)\\1{3,}"),
      # Either-position rejects: department/structural words
      !surname %in% non_name_words,
      !first_name %in% non_name_words,
      # Surname-only rejects: religious figures whose names are also common
      # first names (keeps "Joseph Smith" while dropping "Mary Christ")
      !surname %in% non_surname_words,
      # Reject plural-shaped "surnames" that are actually noun phrases
      !surname %in% c("relationships", "auxiliaries", "presidencies",
                      "departments", "magazines", "societies", "reports",
                      "lessons", "members", "saints", "officers", "leaders",
                      "teachers", "workers", "writers")
    )
}

inventory_authors <- if (exists("inventory_subset") && "Author" %in% names(inventory_subset)) {
  parse_authors(inventory_subset$Author)
} else {
  tibble::tibble(first_name = character(), surname = character())
}

# Report what was kept vs. rejected so you can audit the filter
n_raw_authors <- if (exists("inventory_subset") && "Author" %in% names(inventory_subset)) {
  length(unique(na.omit(inventory_subset$Author)))
} else 0
cat("Author column unique entries: ", n_raw_authors, "\n", sep = "")
cat("Retained after filtering:     ", nrow(inventory_authors),
    " (first, last) pairs\n", sep = "")

# ---- Group by surname; collect every first name observed with it ----
surname_groups <- inventory_authors %>%
  dplyr::group_by(surname) %>%
  dplyr::summarise(first_names = list(unique(first_name)), .groups = "drop") %>%
  dplyr::filter(nchar(surname) >= 3) %>%
  # Drop surnames that are exclusively stopword/junk strings
  dplyr::filter(!surname %in% c("the", "and", "for", "with"))

# ---- Build one regex pattern per surname ----
# ALL auto-built patterns require a preceding title or first name. This is
# critical for religious-magazine text: surnames that look like common words
# (christ, luke, done, child, chapel, plant, rich, porter, ...) would otherwise
# match every occurrence and strip them from the religious vocabulary the
# topic model needs to see. Bare-surname references (e.g., "Smith wrote …")
# fall back to ordinary lemmatization — that's the precision/recall trade.
# Generic title catch-all (Pass 2) still picks up titled refs to authors not
# in the inventory, so most "Sister Smith" type mentions are still covered.
# `common_words` is kept as a documentation hook but no longer branches logic.
build_name_pattern <- function(surname, first_names, common_words) {
  first_names <- first_names[nchar(first_names) >= 2]
  preceding   <- unique(c(first_names, stringr::str_split(title_alt, "\\|")[[1]]))
  preceding_alt <- paste(preceding, collapse = "|")
  paste0("\\b(", preceding_alt, ")(\\s+[b-hj-z]\\b){0,3}\\s+", surname, "\\b")
}

name_protect_auto <- if (nrow(surname_groups) > 0) {
  patterns <- purrr::map2_chr(
    surname_groups$surname,
    surname_groups$first_names,
    build_name_pattern,
    common_words = common_word_surnames
  )
  setNames(paste0(surname_groups$surname, "surname"), patterns)
} else {
  character(0)
}

# ---- HAND-CURATED OVERRIDES ----
# These REPLACE the auto-built pattern for surnames that need special handling.
# Add an override when the inventory-derived pattern misfires (false positives
# from common-word collisions, or recall problems from missing first names).
name_protect_overrides <- c(
  # Young — negative lookahead excludes YLMIA-style compounds
  # ("Young Ladies' Mutual Improvement Assoc.", "Young Men's Society")
  "\\b(brigham|zina|mrs|sister|brother|president|elder)(\\s+[b-hj-z]\\b){0,3}\\s+young\\b(?!\\s+(ladies|lady|men|man|women|woman|people|folks|children|girls|boys))" = "youngsurname",
  # Wells — Emmeline B. Wells (RS general president 1910–1921) plus titles
  "\\b(emmeline|mrs|sister|elder)(\\s+[b-hj-z]\\b){0,3}\\s+wells\\b" = "wellssurname",
  # Snow — Eliza R. Snow, Lorenzo Snow
  "\\b(eliza|lorenzo|mrs|sister|brother|president|elder)(\\s+[b-hj-z]\\b){0,3}\\s+snow\\b" = "snowsurname",
  # Smith — many family members + titles
  "\\b(joseph|bathsheba|emma|mary|hyrum|mrs|sister|brother|president|elder)(\\s+[b-hj-z]\\b){0,3}\\s+smith\\b" = "smithsurname",
  # Kimball — Sarah M., J. Golden, Spencer W., Heber C.
  "\\b(sarah|spencer|golden|heber|mrs|sister|brother|president|elder)(\\s+[b-hj-z]\\b){0,3}\\s+kimball\\b" = "kimballsurname"
)

# Strip auto-built patterns for any surname that has a manual override
override_surnames <- stringr::str_remove(unname(name_protect_overrides), "surname$")
name_protect_auto <- name_protect_auto[
  !stringr::str_detect(unname(name_protect_auto),
                       paste0("^(", paste(override_surnames, collapse = "|"), ")surname$"))
]

# Merge: overrides first (applied first), then auto-built
name_protect <- c(name_protect_overrides, name_protect_auto)

cat("name_protect entries: ",
    length(name_protect_overrides), " overrides + ",
    length(name_protect_auto), " auto-built = ",
    length(name_protect), " total\n", sep = "")
cat("  Auto-built surnames: ",
    paste(stringr::str_remove(unname(name_protect_auto), "surname$"),
          collapse = ", "), "\n", sep = "")

# ============================================================
# GENERIC TITLE-ANCHORED CATCH-ALL
# After the inventory-driven `name_protect` patterns run, a generic pass
# catches anyone who appears with a recognized title — even if they're
# not in the inventory. Pattern: (title)[ middle words ] last_word →
# tag last_word as a surname.
#
# Examples this catches (that inventory-driven patterns miss):
#   "sister beecher said"     → "sister beechersurname said"
#   "elder taylor wrote"      → "elder taylorsurname wrote"
#   "president clark visited" → "president clarksurname visited"
#
# `generic_title_excludes` blocks common nouns that incidentally follow
# titles. The lookbehind `(?<!surname)` makes the pass idempotent — words
# already tagged by inventory patterns are not re-tagged.
# ============================================================
generic_title_excludes <- c(
  # Organizational vocabulary commonly following titles
  "magazine", "society", "ladies", "lady", "men", "man", "women", "woman",
  "people", "folks", "children", "girls", "boys", "members", "saints",
  "auxiliary", "primary", "missionary", "missionaries", "department",
  "presidency", "council", "councilors", "committee", "board", "office",
  # Common abstract / concept nouns
  "love", "charity", "faith", "hope", "work", "lesson", "report",
  "meeting", "conference", "spirit", "kingdom", "church", "gospel",
  "message", "letter", "address", "talk", "remarks", "introduction",
  # Filler / formal openers / common adjectives
  "anonymous", "various", "editorial", "respectfully", "esteemed",
  "dear", "beloved", "honored", "honorable",
  # Things that look like surnames but aren't
  "general", "local", "young"   # 'young' handled in name_protect_overrides
)

# Merge with stopwords — anything that gets dropped later shouldn't be tagged
# anyway. Use unique() to dedupe.
generic_title_excludes <- unique(c(generic_title_excludes, all_stopwords))
generic_title_excludes_pattern <- paste(generic_title_excludes, collapse = "|")

# Build the regex.
#   group 1 = title
#   group 2 = optional middle block (0-3 intermediate words, often first name + initials)
#   group 3 = last word (the surname)
# Negative lookahead blocks common nouns; lookbehind prevents re-tagging.
generic_name_pattern <- paste0(
  "\\b(", title_alt, ")",
  "((?:\\s+[a-z]+){0,3})",                                       # middle block
  "\\s+(?!(?:", generic_title_excludes_pattern, ")\\b)",         # exclude common nouns
  "([a-z]{3,})(?<!surname)\\b"                                   # surname (not already tagged)
)

processed_texts <- raw_texts %>%
  mutate(
    text_clean = str_to_lower(text),
    text_clean = str_remove_all(text_clean, "http\\S+"),
    text_clean = str_remove_all(text_clean, "\\S+@\\S+"),
    text_clean = str_remove_all(text_clean, "\\bvol\\.?\\s*\\d+\\b"),
    text_clean = str_remove_all(text_clean, "\\bno\\.?\\s*\\d+\\b"),
    text_clean = str_remove_all(text_clean, "\\bp\\.?\\s*\\d+\\b"),
    text_clean = str_remove_all(text_clean, "\\b\\d+\\b"),
    # ICU regex note: [[:punct:]] alone misses math/other symbols (= < > + etc.)
    # that 19th/20th-century OCR routinely produces as soft-hyphen / line-break
    # artifacts. The [:symbol:] class catches those.
    text_clean = str_remove_all(text_clean, "[[:punct:][:symbol:]]"),
    text_clean = str_replace_all(text_clean, ocr_fixes),
    # Pass 1: inventory-driven + override patterns (full name + initials + surname)
    text_clean = str_replace_all(text_clean, name_protect),
    # Pass 2: generic title-anchored catch-all — tags the LAST word after any
    # recognized title as a surname. Keeps title + middle words intact so they
    # can be filtered downstream by the stopword pass.
    text_clean = str_replace_all(text_clean, generic_name_pattern, "\\1\\2 \\3surname"),
    text_clean = str_squish(text_clean),
    words = str_split(text_clean, "\\s+"),
    words_filtered = map(words, ~.x[!.x %in% all_stopwords]),
    words_filtered = map(words_filtered, ~.x[!grepl("^\\d+$", .x)]),
    words_filtered = map(words_filtered, ~.x[nchar(.x) >= 3 & !is_ocr_fragment(.x)]),
    # Lemmatize: women->woman, churches->church, etc.
    words_lemma = map(words_filtered, ~lemmatize_words(.x)),
    # Re-filter stopwords after lemmatization (some lemmas become stopwords)
    words_final = map(words_lemma, ~.x[!.x %in% all_stopwords & nchar(.x) >= 3 & !is_ocr_fragment(.x)]),
    text_final = map_chr(words_final, ~paste(.x, collapse = " ")),
    final_word_count = str_count(text_final, "\\S+")
  )

cat("Avg words before:", round(mean(raw_texts$word_count)), "\n")
cat("Avg words after:", round(mean(processed_texts$final_word_count)), "\n")

processed_texts <- processed_texts %>%
  filter(final_word_count >= 5)    # was 10 — lowered to preserve short poems
                                   # and brief notices that have substantive content

# ---- Content-density filter ----
# Drops articles that survive the word-count threshold but are mostly the same
# name/word repeated (biographical byline stubs). Real prose hits 70-90% unique-
# token ratio; byline stubs hit 30-50%. Threshold 0.45.
#
# POEMS ARE EXEMPT — refrains, anaphora, and short-line repetition can pull
# real poetry below 0.45. The inventory's Article_Type column flags poems
# reliably, so we let those through regardless of density.
processed_texts <- processed_texts %>%
  mutate(
    unique_token_ratio = purrr::map_dbl(words_final, function(w) {
      if (length(w) < 3) return(1)
      length(unique(w)) / length(w)
    }),
    # Count of distinct post-stopword, post-lemmatization tokens.
    # This is what really matters for topic modeling: the number of
    # distinct "ideas" in a document, not the raw token count.
    n_unique_tokens = purrr::map_int(words_final, ~length(unique(.x)))
  )

n_low_density <- processed_texts %>%
  filter(unique_token_ratio < 0.45,
         !Article_Type %in% c("Poetry", "Poem")) %>%
  nrow()

processed_texts <- processed_texts %>%
  filter(unique_token_ratio >= 0.45 |
         Article_Type %in% c("Poetry", "Poem"))

cat("Dropped", n_low_density, "low-density docs (poems exempt)\n")

# ---- Minimum-unique-tokens filter ----
# Density catches WIDE-but-shallow repetition; this catches NARROW-and-shallow
# documents — correspondence stubs, header-only orphans, OCR fragments where
# only the title/date words survived. A real article (even a brief death
# notice) has 8-10+ distinct content tokens. A correspondence stub like
# "letter arizona zenos nov 24th" has 4-5.
#
# Threshold of 7 unique tokens lands in the gap between these.
# POEMS ARE EXEMPT — same logic as the density filter.
n_too_thin <- processed_texts %>%
  filter(n_unique_tokens < 7,
         !Article_Type %in% c("Poetry", "Poem")) %>%
  nrow()

processed_texts <- processed_texts %>%
  filter(n_unique_tokens >= 7 |
         Article_Type %in% c("Poetry", "Poem"))

cat("Dropped", n_too_thin, "thin-content docs (< 7 unique tokens, poems exempt)\n")
cat("Documents after filtering:", nrow(processed_texts), "\n\n")

# --- Deduplicate near-identical documents (token-bag Jaccard clustering) ---
# Some articles were split into multiple sub-files with identical text
# (e.g., Guide Lessons _b_a_a, _b_a_b, _b_b, _b_c). Recurring articles
# also appear in many issues as near-identical copies with OCR drift.
# A literal substring fingerprint can't catch these — every copy's first
# 200 characters differ by a few letters. Instead, compare the SET of
# unique post-lemma tokens per document with Jaccard similarity, then
# collapse high-similarity clusters (igraph connected components) down
# to one representative each.
cat("Deduplicating near-identical documents (Jaccard clustering)...\n")
n_before_dedup <- nrow(processed_texts)

jaccard_threshold <- 0.80   # 0.8 = collapse docs sharing 80%+ of unique vocab
fingerprint_min_len <- 5    # skip ultra-short docs to avoid spurious matches

token_sets <- lapply(processed_texts$words_final, function(w) sort(unique(w)))
set_sizes  <- vapply(token_sets, length, integer(1))

# Build sparse edge list with a length-ratio prefilter so we don't do a full
# n^2 sweep on the full corpus. Two docs can only clear `jaccard_threshold`
# if their size ratio also does — that lets us skip most pairs in O(1).
n_docs <- length(token_sets)
edges <- vector("list", 0)
ord <- order(set_sizes)  # process short-to-long so we can early-exit inner loop

for (a in seq_len(n_docs - 1)) {
  i <- ord[a]
  si <- set_sizes[i]
  if (si < fingerprint_min_len) next
  # Inner loop only needs to consider docs whose size is within the ratio band.
  for (b in (a + 1):n_docs) {
    j <- ord[b]
    sj <- set_sizes[j]
    if (sj < fingerprint_min_len) next
    if (si / sj < jaccard_threshold) break   # sorted by size, so all later j fail too
    inter <- length(intersect(token_sets[[i]], token_sets[[j]]))
    union <- si + sj - inter
    if (union == 0) next
    if (inter / union >= jaccard_threshold) {
      edges[[length(edges) + 1]] <- c(i, j)
    }
  }
}

if (length(edges) > 0) {
  edge_mat <- do.call(rbind, edges)
  g <- igraph::graph_from_edgelist(edge_mat, directed = FALSE)
  # graph_from_edgelist only knows about vertices in edges; add isolates.
  n_isolates <- max(0L, n_docs - igraph::vcount(g))
  if (n_isolates > 0) g <- igraph::add_vertices(g, n_isolates)
  cluster_id <- igraph::components(g)$membership[seq_len(n_docs)]
} else {
  cluster_id <- seq_len(n_docs)   # every doc its own cluster
}

processed_texts <- processed_texts %>%
  mutate(.dup_cluster = cluster_id) %>%
  group_by(.dup_cluster) %>%
  slice_max(final_word_count, n = 1, with_ties = FALSE) %>%  # keep most complete copy
  ungroup() %>%
  select(-.dup_cluster) %>%
  mutate(doc_id = row_number())

cat("  Near-duplicate pairs found:", length(edges), "\n")
cat("  Removed", n_before_dedup - nrow(processed_texts), "near-duplicate documents\n")
cat("  Corpus after dedup:", nrow(processed_texts), "documents\n")
```
## Remediation accounting — METHODS-APPENDIX ONLY, not used by the model
# Counts what the §6 ocr_fixes / name_protect steps did and writes two CSVs for
# the dissertation methods chapter. Nothing downstream reads its output, so it is
# kept eval=FALSE for normal runs. The body is OPTIMIZED (corpus lowercased once;
# context-sample diagnostic runs on a 400-doc sample), so a one-off run for the
# appendix takes ~1-2 min rather than all day. Flip to eval=TRUE to regenerate.
```{r remediation-accounting, eval=FALSE}
# ============================================================
# REMEDIATION ACCOUNTING (for dissertation methodology appendix)
# Documents how many raw-text tokens were folded by ocr_fixes and
# how many surnames were tagged by name_protect. Produces a paper
# trail of the preprocessing decisions that altered vocabulary.
# Saves a CSV for inclusion in the methods chapter.
# ============================================================

# Lowercase the raw corpus ONCE; every count below reuses this vector instead
# of re-lowercasing the whole corpus per term and per surname (the original
# cost that made this chunk run for hours on the full canon).
corpus_lower <- stringr::str_to_lower(raw_texts$text)

count_token_occurrences <- function(term, texts_lower) {
  # Case-insensitive word-boundary count over the (pre-lowercased) raw corpus
  pattern <- paste0("\\b", tolower(term), "\\b")
  sum(stringr::str_count(texts_lower, pattern))
}

# ---- OCR variant folding ----
ocr_lookup <- tibble::tibble(
  pattern   = names(ocr_fixes),
  canonical = unname(ocr_fixes)
) %>%
  mutate(variant = stringr::str_remove_all(pattern, "\\\\b")) %>%
  group_by(canonical) %>%
  summarise(variants = list(variant), .groups = "drop")

remediation_table <- ocr_lookup %>%
  mutate(
    canonical_count_raw  = purrr::map_dbl(canonical, count_token_occurrences,
                                          texts_lower = corpus_lower),
    variant_count_folded = purrr::map_dbl(variants, function(vs) {
      sum(purrr::map_dbl(vs, count_token_occurrences, texts_lower = corpus_lower))
    }),
    post_fold_count      = canonical_count_raw + variant_count_folded,
    pct_recovered        = round(100 * variant_count_folded /
                                 pmax(canonical_count_raw, 1), 1),
    n_variants_folded    = lengths(variants),
    variants_list        = purrr::map_chr(variants, ~paste(.x, collapse = ", "))
  ) %>%
  arrange(desc(variant_count_folded)) %>%
  select(canonical, canonical_count_raw, variant_count_folded,
         post_fold_count, pct_recovered, n_variants_folded, variants_list)

cat("=== OCR Remediation Accounting ===\n")
cat("Variant folding (raw text → canonical form):\n\n")
print(remediation_table %>% select(-variants_list), n = Inf, width = Inf)

cat("\nTotals across all canonical terms:\n")
cat("  Canonical occurrences (pre-fold):  ", sum(remediation_table$canonical_count_raw), "\n")
cat("  Variant tokens folded in:          ", sum(remediation_table$variant_count_folded), "\n")
cat("  Canonical occurrences (post-fold): ", sum(remediation_table$post_fold_count), "\n")
cat("  Net recovery rate:                 ",
    round(100 * sum(remediation_table$variant_count_folded) /
          pmax(sum(remediation_table$canonical_count_raw), 1), 1), "%\n")

# ---- Surname protection (context-anchored counting) ----
# Counts both:
#   (a) tokens_tagged    — bare-surname occurrences captured by the
#                          context-anchored pattern (real name references)
#   (b) bare_count_raw   — all bare-surname occurrences in raw text
#                          (includes adjective/noun uses like "young woman")
#   (c) bare_unprotected — bare_count_raw - tokens_tagged
#                          (uses that fall back to ordinary lemmatization,
#                           mostly common-word meanings)
name_table <- tibble::tibble(
  pattern = names(name_protect),
  opaque  = unname(name_protect)
) %>%
  mutate(
    surname        = stringr::str_remove(opaque, "surname$"),
    tokens_tagged  = purrr::map_dbl(pattern, function(p) {
      sum(stringr::str_count(corpus_lower, p))
    }),
    bare_count_raw   = purrr::map_dbl(surname, count_token_occurrences,
                                      texts_lower = corpus_lower),
    bare_unprotected = bare_count_raw - tokens_tagged,
    pct_protected    = round(100 * tokens_tagged /
                             pmax(bare_count_raw, 1), 1)
  ) %>%
  select(surname, opaque_token = opaque,
         tokens_tagged, bare_count_raw, bare_unprotected, pct_protected) %>%
  arrange(desc(tokens_tagged))

cat("\n=== Surname Protection Accounting ===\n")
cat("Context-anchored tagging — only first-name/title + surname patterns are protected.\n")
cat("'bare_unprotected' is the count of common-word uses that fall back to lemmatization.\n\n")
print(name_table, n = Inf, width = Inf)

# ---- Diagnostic: show sample tagged contexts ----
# Use this to spot false positives in the regex.
cat("\n=== Tagged Context Samples (sanity check the regex; doc sample) ===\n")
set.seed(2026)  # reproducible samples
# Illustrative only (NOT used by the CSVs), so scan a RANDOM SAMPLE of documents
# rather than the whole corpus pasted into one multi-MB string — that paste plus
# the backtracking context regex was the original all-day bottleneck. Bump
# ctx_sample_n for broader coverage.
ctx_sample_n <- min(400L, length(corpus_lower))
ctx_text <- paste(sample(corpus_lower, ctx_sample_n), collapse = " | ")
for (i in seq_along(name_protect)) {
  pattern <- names(name_protect)[i]
  opaque  <- unname(name_protect)[i]

  # Capture pattern + 2 surrounding words on each side for context
  ctx_pattern <- paste0("(?:\\S+\\s+){0,2}", pattern, "(?:\\s+\\S+){0,2}")
  matches <- stringr::str_extract_all(ctx_text, ctx_pattern)[[1]]

  cat("\n--- ", opaque, " (", length(matches), " matches in sample; showing up to 8) ---\n", sep = "")
  if (length(matches) > 0) {
    samples <- sample(matches, min(8, length(matches)))
    cat(paste0("  ", samples, collapse = "\n"), "\n", sep = "")
  } else {
    cat("  (no matches in sample)\n")
  }
}

# ---- Save for methodology appendix ----
write_csv(remediation_table,
          file.path(output_path, "remediation_accounting_ocr.csv"))
write_csv(name_table,
          file.path(output_path, "remediation_accounting_names.csv"))
cat("\nSaved to:\n")
cat("  ", file.path(output_path, "remediation_accounting_ocr.csv"), "\n")
cat("  ", file.path(output_path, "remediation_accounting_names.csv"), "\n")
```

---

## 7. Prepare & Fit STM

```{r prepare-stm}
# Fill NAs in covariates so STM row counts stay consistent
# Use .data$ to avoid conflicts with R's built-in month() function
processed_texts <- processed_texts %>%
  mutate(
    Article_Type = ifelse(is.na(.data$Article_Type), "Unknown", .data$Article_Type),
    year = ifelse(is.na(.data$year), median(.data$year, na.rm = TRUE), .data$year)
  )

# month column may not exist if metadata extraction missed it
if ("month" %in% names(processed_texts)) {
  processed_texts <- processed_texts %>%
    mutate(month = ifelse(is.na(.data$month), "Unknown", .data$month))
} else {
  processed_texts$month <- "Unknown"
}

processed <- textProcessor(
  documents = processed_texts$text_final,
  metadata = processed_texts %>%
    select(doc_id, filename, volume_num, year, month, Title, Author, Article_Type),
  lowercase = FALSE,
  removestopwords = FALSE,
  removenumbers = TRUE,
  removepunctuation = FALSE,
  stem = FALSE,
  wordLengths = c(3, Inf),
  sparselevel = 1,
  language = "en",
  verbose = TRUE
)

out <- prepDocuments(
  documents = processed$documents,
  vocab = processed$vocab,
  meta = processed$meta,
  lower.thresh = 3,   # keep singletons (rare named-leader references, specific RS programs)
  upper.thresh = Inf
)

docs <- out$documents
vocab <- out$vocab
meta <- out$meta

# Store the texts that actually made it into the model (for findThoughts later)
modeled_texts <- processed_texts$text_final[match(meta$doc_id, processed_texts$doc_id)]
cat("\nCorpus ready:", length(docs), "documents,", length(vocab), "vocab terms\n")
cat("  (dropped", nrow(processed_texts) - length(docs), "documents during preprocessing)\n")

# Ensure meta is exactly aligned with docs (no NAs in covariates)
meta$year <- as.numeric(meta$year)
meta$year[is.na(meta$year)] <- median(meta$year, na.rm = TRUE)
if (is.null(meta$month)) meta$month <- "Unknown"
meta$month[is.na(meta$month)] <- "Unknown"

cat("\nCorpus ready:", length(docs), "documents,", length(vocab), "vocab terms\n")
cat("Meta rows:", nrow(meta), "(should match docs)\n")
```

```{r ocr-variant-audit, eval=TRUE}
# ============================================================
# OCR VARIANT AUDIT
# Scans final vocab for likely OCR misreads of historically important
# terms using approximate string matching (Levenshtein distance ≤ 2).
#
# Use results to build a str_replace_all() remediation table that runs
# BEFORE lemmatization. Lemmatization can't help — it only normalizes
# morphological variants of real words, not OCR errors.
# ============================================================

# Terms central to Relief Society Magazine's 20th-century discourse
# (Progressive era, suffrage, world wars, welfare program, missionary work).
# Edit this list to match what matters for your analysis.
audit_terms <- c(
  # Suffrage / Progressive era civic discourse
  "suffrage", "enfranchise", "franchise", "ballot", "legislature",
  "constitution", "amendment", "citizenship",
  # Relief Society institutional vocabulary
  "relief", "society", "ward", "stake", "auxiliary", "presidency",
  "magazine", "lesson", "department",
  # World wars / Red Cross era
  "wartime", "soldier", "soldiers", "armistice", "conservation",
  "rationing",
  # Welfare / Depression era
  "welfare", "depression", "unemployment", "storehouse",
  # Missionary / temple discourse
  "missionary", "missionaries", "temple", "ordinance", "covenant",
  # Mormon women leadership
  "smith", "wells", "kimball", "spafford", "lyman",
  # Protected surname tokens — confirm name_protect worked.
  # These should show in_vocab = TRUE with 0 variants.
  "wellssurname", "youngsurname", "snowsurname", "smithsurname",
  "kimballsurname", "spaffordsurname", "lymansurname"
)

cat("=== OCR Variant Audit ===\n")
cat("Scanning vocab (n =", length(vocab), ") for variants within edit distance 2\n\n")

audit_results <- purrr::map_dfr(audit_terms, function(term) {
  # Length-proportional distance, capped at 2:
  # 4 chars → 1 edit | 5-8 chars → 2 | 9+ chars → 2 (capped)
  max_dist <- min(2L, ceiling(0.25 * nchar(term)))
  near <- agrep(term, vocab, max.distance = list(all = max_dist), value = TRUE)
  # Drop concatenation false positives — variant must be within ±2 chars of canonical
  near <- near[abs(nchar(near) - nchar(term)) <= 2]
  variants <- setdiff(near, term)
  tibble::tibble(
    canonical  = term,
    in_vocab   = term %in% vocab,
    n_variants = length(variants),
    variants   = if (length(variants) > 0) paste(variants, collapse = ", ") else "(none)"
  )
})

# Show terms that are missing OR have OCR variants worth folding
audit_results %>%
  filter(!in_vocab | n_variants > 0) %>%
  arrange(desc(n_variants), canonical) %>%
  print(n = Inf, width = Inf)

missing_terms <- audit_results %>% filter(!in_vocab)        %>% pull(canonical)
high_variant  <- audit_results %>% filter(n_variants >= 2) %>% pull(canonical)

cat("\n--- Summary ---\n")
if (length(missing_terms) > 0) {
  cat("Missing from vocab entirely (check OCR or preprocessing):\n  ",
      paste(missing_terms, collapse = ", "), "\n")
} else {
  cat("All audited terms present in vocab.\n")
}
if (length(high_variant) > 0) {
  cat("\nTerms with >=2 variants (highest payoff to fold):\n  ",
      paste(high_variant, collapse = ", "), "\n")
}

cat("\n--- Remediation pattern ---\n")
cat("Build a named vector and apply BEFORE lemmatization in the preprocessing chunk:\n")
cat('  ocr_fixes <- c(\n')
cat('    "\\\\bweifare\\\\b"   = "welfare",\n')
cat('    "\\\\bsuffrace\\\\b"  = "suffrage",\n')
cat('    "\\\\bspaford\\\\b"   = "spafford"\n')
cat('  )\n')
cat('  text_clean <- str_replace_all(text_clean, ocr_fixes)\n')
```

```{r hunspell-ocr-check, eval=TRUE}
# ============================================================
# HUNSPELL OCR DETECTION
# A real spell-checker pass over the final vocab. Flags every term
# not in the English dictionary (and not in our custom Mormon/RS lexicon,
# and not a protected surname token) as a potential OCR error.
#
# For each flagged term, suggests:
#   (a) hunspell_suggestion — the spell-checker's top correction
#   (b) closest_vocab_term  — the highest-frequency in-vocab word within
#                              Levenshtein distance 2 of the flagged term
#
# Closest_vocab_term is usually what you want for OCR remediation, because
# it preserves period-appropriate spelling rather than modernizing it.
#
# Output: a copy-paste-ready block of `ocr_fixes` lines, plus a CSV of
# every flagged candidate. Run this AFTER `prepDocuments` so `vocab`
# is the actual modeled vocabulary, not the raw token soup.
# ============================================================
if (!requireNamespace("hunspell", quietly = TRUE)) install.packages("hunspell")
if (!requireNamespace("stringdist", quietly = TRUE)) install.packages("stringdist")
suppressPackageStartupMessages({
  library(hunspell)
  library(stringdist)
})

# ---- Custom Mormon / Relief Society / period-appropriate lexicon ----
# Anything here is treated as a valid word (not an OCR error). Extend as
# needed when the report below flags real terms as misspellings.
mormon_lexicon <- c(
  # Mormon doctrinal / scriptural
  "saints", "stake", "ward", "wards", "endowment", "patriarchal",
  "patriarch", "patriarchs", "elohim", "jehovah", "jesus",
  "nephi", "nephite", "nephites", "lamanite", "lamanites",
  "moroni", "lehi", "ammon", "alma", "helaman", "mosiah",
  "abinadi", "enos", "jarom", "mormonism", "deseret", "zion",
  "millennial", "millennium", "celestial", "telestial", "terrestrial",
  "preexistence", "godhead", "priesthood", "melchizedek", "aaronic",
  # Relief Society / women's organizing
  "retrenchment", "ylmia", "auxiliary", "auxiliaries", "primary",
  "presidency", "counselor", "counselors", "magna", "ensign",
  "exponent", "homemaker", "homemakers", "homemaking",
  # Officers / common LDS first names that may appear in text
  "emmeline", "eliza", "zina", "bathsheba", "amasa", "lorenzo",
  "hyrum", "brigham", "heber", "belle", "spencer", "spafford",
  "kimball", "snow", "wells", "smith", "young", "lyman",
  # Place names
  "nauvoo", "kirtland", "moroni", "snowflake", "logan", "ogden",
  "provo", "tooele", "manti",
  # 19th-c. / scriptural English forms hunspell tends to flag
  "thee", "thou", "thine", "thy", "shalt", "doth", "hath", "ye",
  "whence", "wherefore", "verily"
)
mormon_lexicon <- unique(tolower(mormon_lexicon))

# ---- Frequency threshold ----
# Don't bother flagging extremely rare terms; corrections are noisy
# and the volume is too small to matter for the topic model.
min_term_freq <- 5

# ---- Term-frequency over the FINAL processed corpus ----
vocab_freq <- table(unlist(stringr::str_split(processed_texts$text_final, "\\s+")))
vocab_freq <- vocab_freq[nchar(names(vocab_freq)) >= 3 & vocab_freq >= min_term_freq]

# ---- Build "known good" set ----
# Hunspell checks against multiple English dictionaries (en_US, en_GB).
# A term is OK if it passes hunspell OR is in our custom lexicon
# OR is a protected surname token.
protected_tokens <- unname(name_protect)
protected_tokens <- protected_tokens[protected_tokens %in% names(vocab_freq)]

# hunspell_check is vectorized — much faster than per-term checks
is_english <- hunspell::hunspell_check(names(vocab_freq))
known_good <- unique(c(
  names(vocab_freq)[is_english],
  mormon_lexicon,
  protected_tokens
))

flagged_terms <- setdiff(names(vocab_freq), known_good)
flagged_terms <- flagged_terms[!stringr::str_ends(flagged_terms, "surname")]

cat("=== Hunspell OCR Check ===\n")
cat("  Vocab terms checked (freq >=", min_term_freq, "):", length(vocab_freq), "\n")
cat("  Recognized English:    ", sum(is_english), "\n")
cat("  In custom lexicon:     ", length(mormon_lexicon), " entries (subset present in vocab)\n")
cat("  Protected surnames:    ", length(protected_tokens), "\n")
cat("  Flagged as potential OCR errors:", length(flagged_terms), "\n\n")

# ---- For each flagged term, find best correction ----
# hunspell_suggest gives traditional spell-checker corrections.
# stringdist finds the closest IN-VOCAB term (usually better for OCR —
# preserves period-appropriate forms like "honour" instead of "honor").
suggest_correction <- function(term, in_vocab_terms, freq_table) {
  hs <- hunspell::hunspell_suggest(term)[[1]]
  hs_top <- if (length(hs) > 0) tolower(hs[1]) else NA_character_

  # Closest in-vocab match within edit distance 2 (and ≥ 2× more frequent
  # than the flagged term — otherwise we're folding into a noisier variant)
  dists <- stringdist::stringdist(term, in_vocab_terms, method = "lv")
  close_idx <- which(dists > 0 & dists <= 2)
  if (length(close_idx) > 0) {
    close_terms <- in_vocab_terms[close_idx]
    close_freqs <- as.integer(freq_table[close_terms])
    # Filter to terms with at least 2× the flagged term's frequency
    threshold <- as.integer(freq_table[[term]]) * 2
    keep <- close_freqs >= threshold
    if (any(keep)) {
      close_terms <- close_terms[keep]
      close_freqs <- close_freqs[keep]
      vocab_top  <- close_terms[which.max(close_freqs)]
      vocab_freq_top <- close_freqs[which.max(close_freqs)]
    } else {
      vocab_top <- NA_character_
      vocab_freq_top <- NA_integer_
    }
  } else {
    vocab_top <- NA_character_
    vocab_freq_top <- NA_integer_
  }

  list(hunspell = hs_top, vocab = vocab_top, vocab_freq = vocab_freq_top)
}

cat("Computing corrections for", length(flagged_terms), "flagged terms ...\n")
# Use known_good (in-vocab + lexicon) as the candidate pool for in-vocab matches
candidate_pool <- intersect(known_good, names(vocab_freq))

suggestions <- purrr::map_dfr(flagged_terms, function(term) {
  s <- suggest_correction(term, candidate_pool, vocab_freq)
  tibble::tibble(
    flagged              = term,
    count                = as.integer(vocab_freq[[term]]),
    hunspell_suggestion  = s$hunspell,
    closest_vocab_term   = s$vocab,
    closest_vocab_count  = s$vocab_freq
  )
}) %>% dplyr::arrange(dplyr::desc(count))

# ---- Print top candidates ----
cat("\n=== Top 50 OCR error candidates (sorted by frequency) ===\n")
print(head(suggestions, 50), n = 50, width = Inf)

# ---- Generate copy-paste-ready ocr_fixes lines ----
# Prefer closest_vocab_term over hunspell_suggestion when available.
# Only emit lines where we have *some* candidate correction.
cat("\n=== Copy-paste-ready ocr_fixes lines (top 30 highest-confidence) ===\n")
cat("# Add these to the ocr_fixes named vector in the cleaning chunk.\n")
cat("# REVIEW each suggestion — accept only the ones that look right.\n\n")
top_fixes <- suggestions %>%
  dplyr::filter(!is.na(closest_vocab_term) | !is.na(hunspell_suggestion)) %>%
  head(30)

for (i in seq_len(nrow(top_fixes))) {
  r <- top_fixes[i, ]
  canonical <- if (!is.na(r$closest_vocab_term)) r$closest_vocab_term else r$hunspell_suggestion
  source    <- if (!is.na(r$closest_vocab_term)) "vocab"             else "hunspell"
  cat(sprintf('  "\\\\b%s\\\\b" = "%s",   # n=%d via %s\n',
              r$flagged, canonical, r$count, source))
}

# ---- Save full table to CSV for manual review ----
write_csv(suggestions, file.path(output_path, "hunspell_ocr_candidates.csv"))
cat("\nFull candidate table saved to:\n  ",
    file.path(output_path, "hunspell_ocr_candidates.csv"), "\n")
cat("\nWorkflow:\n")
cat("  1. Open hunspell_ocr_candidates.csv\n")
cat("  2. Sort by count, scan top ~100 rows\n")
cat("  3. For each row where closest_vocab_term looks correct, copy the\n")
cat("     ocr_fixes line above into the cleaning chunk\n")
cat("  4. Re-run from the cleaning chunk onward\n")
cat("  5. Re-run this chunk to confirm the flagged term is gone\n")
```

```{r searchK, eval=FALSE, cache=FALSE}
# ============================================================
# DIAGNOSTIC: searchK - tests multiple K values
# Shows held-out likelihood, residuals, semantic coherence,
# and lower bound to help justify your choice of K.
# Set eval=FALSE after running once to skip on re-runs.
# ============================================================
cat("Running searchK diagnostic...\n")

K_candidates <- c(10, 12, 15, 20)

searchK_results <- searchK(
  documents = docs,
  vocab = vocab,
  K = K_candidates,
  data = meta,
  prevalence = ~ s(year),
  init.type = "Spectral",
  seed = 12345,
  verbose = FALSE
)

plot(searchK_results)
saveRDS(searchK_results, file.path(output_path, "searchK_results.rds"))
cat("searchK results saved.\n")
```

```{r searchK-detail-panels, eval=FALSE, fig.width=12, fig.height=10}
# ============================================================
# Detailed 5-panel diagnostic: 4 metric line plots +
# coherence/exclusivity scatter labeled by K (upper-right = best).
# Set eval=TRUE to render alongside the faceted view.
# ============================================================
if (exists("searchK_results")) {

  sk_plot <- data.frame(
    K        = unlist(searchK_results$results$K),
    heldout  = unlist(searchK_results$results$heldout),
    residual = unlist(searchK_results$results$residual),
    semcoh   = unlist(searchK_results$results$semcoh),
    exclus   = unlist(searchK_results$results$exclus)
  )

  corpus_col <- "#6E8B3D"

  shared_scales <- list(
    scale_x_continuous(breaks = K_candidates),
    theme_minimal(base_size = 11),
    theme(legend.position = "none", panel.grid.minor = element_blank())
  )

  p1 <- ggplot(sk_plot, aes(x = K, y = heldout)) +
    geom_line(linewidth = 1.2, color = corpus_col) +
    geom_point(size = 3, color = corpus_col) +
    labs(title = "Held-Out Likelihood", subtitle = "Higher is better",
         x = "K", y = "Held-Out Likelihood") + shared_scales

  p2 <- ggplot(sk_plot, aes(x = K, y = residual)) +
    geom_line(linewidth = 1.2, color = corpus_col) +
    geom_point(size = 3, color = corpus_col) +
    labs(title = "Residuals", subtitle = "Lower is better",
         x = "K", y = "Residuals") + shared_scales

  p3 <- ggplot(sk_plot, aes(x = K, y = semcoh)) +
    geom_line(linewidth = 1.2, color = corpus_col) +
    geom_point(size = 3, color = corpus_col) +
    labs(title = "Semantic Coherence",
         subtitle = "Higher is better (trades off with exclusivity)",
         x = "K", y = "Semantic Coherence") + shared_scales

  p4 <- ggplot(sk_plot, aes(x = K, y = exclus)) +
    geom_line(linewidth = 1.2, color = corpus_col) +
    geom_point(size = 3, color = corpus_col) +
    labs(title = "Exclusivity",
         subtitle = "Higher is better (trades off with coherence)",
         x = "K", y = "Exclusivity") + shared_scales

  p5 <- ggplot(sk_plot, aes(x = semcoh, y = exclus)) +
    geom_point(size = 4, alpha = 0.8, color = corpus_col) +
    geom_text(aes(label = K), size = 3.5, vjust = -1) +
    labs(title = "Coherence vs Exclusivity Tradeoff",
         subtitle = "Numbers = K value; upper-right = best quality",
         x = "Semantic Coherence", y = "Exclusivity") +
    theme_minimal(base_size = 11) +
    theme(panel.grid.minor = element_blank())

  (p1 | p2) / (p3 | p4) / p5 +
    plot_annotation(
      title = "searchK Diagnostic: Relief Society Magazine",
      subtitle = "Each panel shows one quality metric across candidate K values",
      theme = theme(plot.title = element_text(face = "bold", size = 16))
    )
}
```



```{r pareto-heldout, eval=FALSE, fig.width=10, fig.height=10}
# ============================================================
# PARETO FRONTIER + HELD-OUT PLATEAU
# Range-independent K selection. Replaces the gap-minimization
# "sweet spot" which depends on the searchK range you chose.
#
# A K is Pareto-optimal if no other tested K has BOTH higher
# semantic coherence AND higher-or-equal exclusivity (or v.v.).
# Dominated K's are drawn faded — you'd never pick one over a
# frontier K. The held-out likelihood panel shows the plateau:
# smallest Pareto-optimal K on the plateau = parsimonious pick.
# ============================================================
if (exists("searchK_results")) {
  sk_data <- data.frame(
    K       = unlist(searchK_results$results$K),
    semcoh  = unlist(searchK_results$results$semcoh),
    exclus  = unlist(searchK_results$results$exclus),
    heldout = unlist(searchK_results$results$heldout)
  )
  # ----- Pareto status -----
  # Higher is better for both metrics. A point is dominated if some
  # other point beats it on one metric and ties-or-beats on the other.
  is_pareto <- function(coh, exc) {
    vapply(seq_along(coh), function(i) {
      !any( (coh >  coh[i] & exc >= exc[i]) |
            (coh >= coh[i] & exc >  exc[i]) )
    }, logical(1))
  }
  sk_data$pareto <- is_pareto(sk_data$semcoh, sk_data$exclus)
  frontier <- sk_data %>%
    filter(pareto) %>%
    arrange(semcoh)   # sort along the frontier curve
  cat("=== K Selection Diagnostic ===\n")
  cat("Pareto-optimal K values:", paste(sort(frontier$K), collapse = ", "), "\n")
  cat("Dominated K values:    ",
      paste(sort(sk_data$K[!sk_data$pareto]), collapse = ", "),
      ifelse(all(sk_data$pareto), "(none)", ""), "\n\n")
  corpus_col <- "#6E8B3D"
  # ----- Plot 1: Pareto frontier scatter -----
  p_pareto <- ggplot(sk_data, aes(x = semcoh, y = exclus)) +
    geom_line(data = frontier,
              color = corpus_col, linewidth = 1.2, alpha = 0.6) +
    geom_point(aes(color = pareto, shape = pareto, size = pareto),
               alpha = 0.9) +
    geom_text_repel(aes(label = paste0("K=", K), color = pareto),
                    size = 4, fontface = "bold", show.legend = FALSE,
                    box.padding = 0.6, point.padding = 0.4,
                    seed = 12345) +
    scale_color_manual(values = c("TRUE" = corpus_col, "FALSE" = "grey60"),
                       labels = c("TRUE" = "Pareto-optimal",
                                  "FALSE" = "Dominated")) +
    scale_shape_manual(values = c("TRUE" = 19, "FALSE" = 1),
                       labels = c("TRUE" = "Pareto-optimal",
                                  "FALSE" = "Dominated")) +
    scale_size_manual(values = c("TRUE" = 5, "FALSE" = 3),
                      labels = c("TRUE" = "Pareto-optimal",
                                 "FALSE" = "Dominated")) +
    labs(title = "Pareto Frontier — Coherence vs Exclusivity",
         subtitle = paste0("Filled = Pareto-optimal. Hollow = dominated ",
                           "(some other K beats it on both metrics)."),
         x = "Semantic Coherence (higher = better)",
         y = "Exclusivity (higher = better)",
         color = NULL, shape = NULL, size = NULL) +
    theme_minimal(base_size = 12) +
    theme(legend.position = "bottom",
          panel.grid.minor = element_blank(),
          plot.title = element_text(face = "bold", size = 14))
  # ----- Plot 2: Held-out likelihood with Pareto K's highlighted -----
  # The 'knee' is where the line transitions from rising to flat.
  # Smallest Pareto-optimal K past the knee = parsimonious choice.
  p_heldout <- ggplot(sk_data, aes(x = K, y = heldout)) +
    geom_line(linewidth = 1.0, color = "grey50") +
    geom_point(aes(color = pareto, size = pareto), alpha = 0.9) +
    geom_text_repel(aes(label = paste0("K=", K), color = pareto),
                    size = 3.8, fontface = "bold", show.legend = FALSE,
                    box.padding = 0.5, seed = 12345) +
    scale_color_manual(values = c("TRUE" = corpus_col, "FALSE" = "grey60")) +
    scale_size_manual(values = c("TRUE" = 5, "FALSE" = 3)) +
    scale_x_continuous(breaks = K_candidates) +
    labs(title = "Held-Out Likelihood — Find the Plateau",
         subtitle = paste0("Green = Pareto-optimal K. The 'knee' (slope ",
                           "flattens) is where adding K stops paying off."),
         x = "Number of Topics (K)",
         y = "Held-Out Likelihood (higher = better)") +
    theme_minimal(base_size = 12) +
    theme(legend.position = "none",
          panel.grid.minor = element_blank(),
          plot.title = element_text(face = "bold", size = 14))
  # ----- Combined output -----
  (p_pareto / p_heldout) +
    plot_annotation(
      title    = "K Selection: Pareto Frontier + Held-Out Plateau",
      subtitle = paste0("Pick the smallest Pareto-optimal K that sits on ",
                        "the held-out plateau. Then INSPECT the topics."),
      theme = theme(plot.title = element_text(face = "bold", size = 16))
    )
}
```

```{r set-k}
# ============================================================
# SET NUMBER OF TOPICS HERE
# ============================================================
# chosen_K accepts either an integer (pins K) or "auto" (picks the balanced
# coherence/exclusivity point from the searchK run above). "auto" needs the
# searchK chunk to have produced searchK_results this session, or a saved
# searchK_results.rds in this scenario's output folder.
chosen_K <- 15   # or "auto"

if (identical(chosen_K, "auto")) {
  if (!exists("searchK_results")) {
    .skf <- file.path(output_path, "searchK_results.rds")
    if (file.exists(.skf)) searchK_results <- readRDS(.skf)
  }
  if (!exists("searchK_results")) {
    stop("chosen_K = 'auto' needs searchK results. Run the searchK chunk first ",
         "(or set chosen_K to an integer).")
  }
  .sk <- data.frame(
    K      = unlist(searchK_results$results$K),
    semcoh = unlist(searchK_results$results$semcoh),
    exclus = unlist(searchK_results$results$exclus)
  )
  # Rescale each metric to 0-1 and pick K maximizing their average — the
  # upper-right of the coherence/exclusivity frontier.
  .rescale <- function(x) if (diff(range(x)) == 0) rep(1, length(x)) else (x - min(x)) / diff(range(x))
  .sk$score <- (.rescale(.sk$semcoh) + .rescale(.sk$exclus)) / 2
  chosen_K <- .sk$K[which.max(.sk$score)]
  cat("Auto-selected K =", chosen_K, "(balanced coherence/exclusivity)\n")
} else {
  cat("K =", chosen_K, "\n")
}
chosen_K <- as.integer(chosen_K)
```

```{r fit-model, cache=TRUE}
# Using prevalence covariates: the model learns how topic prevalence
# varies by year and article type during fitting, not just post-hoc.
stm_model <- stm(
  documents = docs,
  vocab = vocab,
  K = chosen_K,
  prevalence = ~ s(year) + Article_Type,
  data = meta,
  max.em.its = 75,
  init.type = "Spectral",
  seed = 12345,
  verbose = FALSE
)

saveRDS(stm_model, file.path(output_path, paste0("stm_model_K", chosen_K, ".rds")))
cat("Model saved.\n")
```

---

## 8. Examine Topics

```{r examine-topics}
all_top_words <- labelTopics(stm_model, n = 15)

# ---- Reverse-map ALL protected surname tokens for display ----
# Catches both:
#   (a) inventory-driven tokens from `name_protect`   (e.g., wellssurname)
#   (b) generic catch-all tokens from the title-anchored pass (e.g., taylorsurname)
# Each token has the shape <surname>surname — strip the suffix and title-case.
fix_surname_token <- function(word) {
  ifelse(grepl("surname$", word),
         tools::toTitleCase(sub("surname$", "", word)),
         word)
}
for (slot in intersect(names(all_top_words), c("prob", "frex", "lift", "score"))) {
  all_top_words[[slot]][] <- vapply(all_top_words[[slot]], fix_surname_token, character(1))
}

cat("Top words per topic:\n\n")
for (i in 1:chosen_K) {
  cat("Topic", i, "\n")
  cat("  FREX:", paste(all_top_words$frex[i, 1:10], collapse = ", "), "\n")
  cat("  PROB:", paste(all_top_words$prob[i, 1:10], collapse = ", "), "\n\n")
}
```

---

## 8b. Auto-Generate Topic Labels

```{r auto-labels}
cat(rep("=", 70), "\n", sep = "")
cat("AUTO-GENERATING LABELS\n")
cat(rep("=", 70), "\n\n", sep = "")

create_specific_label <- function(topic_num, frex_words, prob_words) {
  frex_text <- tolower(paste(frex_words, collapse = " "))
  prob_text <- tolower(paste(prob_words, collapse = " "))
  all_words <- paste(frex_text, prob_text)

  # ---- RELIGION & DOCTRINE ----
  if (grepl("kingdom.*gospel|baptism.*eternal|salvation|atonement", frex_text)) {
    label <- "Gospel Doctrine & Spiritual Kingdom"
  } else if (grepl("passover|paschal|feast|tabernacle", frex_text)) {
    label <- "Biblical Symbolism & Ancient Rituals"
  } else if (grepl("abraham.*sarai|biblical|moses|israel", frex_text)) {
    label <- "Biblical Narratives"
  } else if (grepl("prayer|faith.*hope|testimony|spirit.*holy", frex_text)) {
    label <- "Faith & Spiritual Life"
  } else if (grepl("lesson|scripture|doctrine|commandment", frex_text)) {
    label <- "Religious Lessons & Scripture Study"
  } else if (grepl("temple|ordinance|endowment|sealing", frex_text)) {
    label <- "Temple & Sacred Ordinances"
  } else if (grepl("missionary|mission.*field|convert|preach", frex_text)) {
    label <- "Missionary Work & Conversion"

  # ---- RELIEF SOCIETY & CHURCH ORG ----
  } else if (grepl("sisters.*presidency|organization.*grain|relief.*leader", frex_text)) {
    label <- "Relief Society Leadership & Organization"
  } else if (grepl("stake.*ward|attendance.*conference|quarterly", frex_text)) {
    label <- "Stake & Ward Relief Society Reports"
  } else if (grepl("conference|general.*conference|session|sustain", all_words)) {
    label <- "Church Conference Proceedings"

  # ---- WOMEN'S RIGHTS & POLITICS ----
  } else if (grepl("suffrage.*vote|legislature|franchise|ballot", frex_text)) {
    label <- "Women's Suffrage & Political Rights"
  } else if (grepl("council.*international|convention|delegate", frex_text)) {
    label <- "International Women's Councils"
  } else if (grepl("equal.*right|petition|protest|reform", frex_text)) {
    label <- "Women's Reform & Activism"

  # ---- DOMESTICITY & HOME ----
  } else if (grepl("recipe|tbsp|boiling|oven|flour|bake", frex_text)) {
    label <- "Recipes & Cooking Instructions"
  } else if (grepl("housework|housekeeping|budget|thrift", frex_text)) {
    label <- "Household Management & Budgeting"
  } else if (grepl("child|mother.*rear|parent|infant|nurture", frex_text)) {
    label <- "Motherhood & Child-Rearing"
  } else if (grepl("garden|plant.*seed|flower|cultivation", frex_text)) {
    label <- "Home Gardening & Agriculture"
  } else if (grepl("sew|pattern|dress|fabric|garment|fashion", frex_text)) {
    label <- "Sewing, Fashion & Handwork"

  # ---- EDUCATION & PROFESSIONALIZATION ----
  } else if (grepl("nurse.*hospital|nursing.*training|medical", frex_text)) {
    label <- "Nursing Training & Hospital Work"
  } else if (grepl("school|teacher|student|education|university|class", frex_text)) {
    label <- "Education & Schools"
  } else if (grepl("diet.*protein|nutrition|malnutrition|vitamin", frex_text)) {
    label <- "Nutrition & Dietary Science"
  } else if (grepl("radium.*curie|pasteur.*science|scientist|discovery", frex_text)) {
    label <- "Scientific Biography & Discovery"

  # ---- HISTORY & PIONEER ----
  } else if (grepl("emigration.*journey|wagon.*pioneer|handcart|plains", frex_text)) {
    label <- "Pioneer Emigration & Journey Stories"
  } else if (grepl("pioneer|settlement|early.*days|frontier", all_words)) {
    label <- "Pioneer Heritage & Settlement"

  # ---- LITERATURE & ARTS ----
  } else if (grepl("irving|tale|novel|literary|author", frex_text)) {
    label <- "Literature & Book Reviews"
  } else if (grepl("jerry|walter|jimmy|agnes|margaret", frex_text) && grepl("said|little|came", prob_text)) {
    label <- "Serialized Fiction & Stories"
  } else if (grepl("poem|verse|stanza|rhyme|lyric", all_words)) {
    label <- "Poetry & Verse"
  } else if (grepl("tableau.*song|music.*hymn|choir|sing", frex_text)) {
    label <- "Musical Programs & Performances"

  # ---- WAR & CURRENT EVENTS ----
  } else if (grepl("entente.*allies|war.*troops|soldier|military|battle", frex_text)) {
    label <- "War Commentary & News"
  } else if (grepl("europe|nation|government|political|congress", frex_text)) {
    label <- "National & International Affairs"

  # ---- HEALTH ----
  } else if (grepl("health|disease|sanit|hygiene|cure|sick", all_words)) {
    label <- "Health & Sanitation"

  # ---- OBITUARY & BIOGRAPHY ----
  } else if (grepl("death|funeral|deceased|mourn|tribute", frex_text)) {
    label <- "Obituaries & Tributes"
  } else if (grepl("life.*born|biography|memoir|career|accomplish", frex_text)) {
    label <- "Biographical Sketches"

  # ---- GENEALOGY ----
  } else if (grepl("genealog|ancestor|pedigree|lineage|family.*history", frex_text)) {
    label <- "Genealogy & Family History"

  # ---- SOCIAL WELFARE ----
  } else if (grepl("welfare|charity|poor|needy|donate|service", frex_text)) {
    label <- "Social Welfare & Charitable Work"

  # ---- FALLBACK ----
  } else {
    keywords <- paste(tools::toTitleCase(frex_words[1:3]), collapse = " / ")
    label <- keywords
  }

  return(label)
}

topic_labels <- sapply(1:chosen_K, function(i) {
  frex_words <- all_top_words$frex[i, 1:10]
  prob_words <- all_top_words$prob[i, 1:10]
  create_specific_label(i, frex_words, prob_words)
})

cat("Auto-generated labels:\n\n")
for (i in 1:chosen_K) {
  cat("Topic", i, ":", topic_labels[i], "\n")
  cat("  FREX:", paste(all_top_words$frex[i, 1:7], collapse = ", "), "\n")
  cat("  PROB:", paste(all_top_words$prob[i, 1:7], collapse = ", "), "\n\n")
}

# Export auto-labels
label_export <- tibble(
  topic_num = 1:chosen_K,
  auto_label = topic_labels,
  frex_words = apply(all_top_words$frex, 1, function(x) paste(x, collapse = ", ")),
  prob_words = apply(all_top_words$prob, 1, function(x) paste(x, collapse = ", ")),
  manual_label = ""
)
write_csv(label_export, file.path(output_path, paste0("topic_labels_K", chosen_K, ".csv")))
```

---

## 8c. Manual Label Overrides (Optional)

```{r manual-overrides}
# ============================================================
# MANUAL OVERRIDES - uncomment and edit as needed
# ============================================================
topic_labels[1] <- "Gardening and Flower Displays"
topic_labels[2] <- "Church Organizational Announcements"
topic_labels[3] <- "National & International Affairs"
topic_labels[4] <- "Relief Society Conference Reports"
topic_labels[5] <- "Motherhood and Marriage Advice"
topic_labels[6] <- "Recipes"
topic_labels[7] <- "Poetry"
topic_labels[8] <- "Religious Lessons & Scripture Study"
topic_labels[9] <- "Women's Religious Responsibility"
topic_labels[10] <- "Pioneer Emigration & Journey Stories"
topic_labels[11] <- "Relief Society Magazine Subscription and Correspondence Announcements"
topic_labels[12] <- "Fictional Stories"
topic_labels[13] <- "Advertisements"
topic_labels[14] <- "Literature and Poetry"
topic_labels[15] <- "Relief Society Initiatives and Programs"

cat("FINAL TOPIC LABELS\n")
cat(rep("=", 70), "\n\n", sep = "")
for (i in 1:chosen_K) {
  cat("  Topic", i, ":", topic_labels[i], "\n")
}
```

---

## 8d. Find Examples for a Specific Topic

```{r find-examples-custom}
# ============================================================
# CHANGE THIS to examine any topic
# ===========================================================
topic_to_examine <- 4
n_examples <- 15

cat(rep("=", 70), "\n", sep = "")
cat("TOPIC", topic_to_examine, ":", topic_labels[topic_to_examine], "\n")
cat(rep("=", 70), "\n", sep = "")
cat("FREX:", paste(all_top_words$frex[topic_to_examine, 1:10], collapse = ", "), "\n")
cat("PROB:", paste(all_top_words$prob[topic_to_examine, 1:10], collapse = ", "), "\n")
cat(rep("-", 70), "\n\n", sep = "")

# modeled_texts was stored after prepDocuments — guaranteed to match model docs
thoughts <- findThoughts(stm_model,
                         texts = modeled_texts,
                         topics = topic_to_examine,
                         n = n_examples)

thought_indices <- thoughts$index[[1]]

for (i in seq_along(thought_indices)) {
  idx <- thought_indices[i]
  row <- processed_texts[idx, ]

  cat(sprintf("Example %d of %d:\n", i, length(thought_indices)))
  cat(sprintf("  File:   %s\n", row$filename))
  cat(sprintf("  Title:  %s\n", ifelse(is.na(row$Title), "(unknown)", row$Title)))
  cat(sprintf("  Author: %s\n", ifelse(is.na(row$Author) | row$Author == "Unknown", "-", row$Author)))
  cat(sprintf("  Type:   %s\n", ifelse(is.na(row$Article_Type), "-", row$Article_Type)))
  cat(sprintf("  Vol %s, %s\n\n", row$volume_num, row$year))
  cat(substr(thoughts$docs[[1]][i], 1, 400), "\n\n")
  cat(rep("-", 50), "\n\n", sep = "")
}
```

---

## 9. Link Topics to Articles

```{r link-topics-to-articles}
doc_topics <- make.dt(stm_model, meta = meta)

cat("Columns in doc_topics:\n")
cat(paste(names(doc_topics), collapse = ", "), "\n\n")

topic_article_link <- doc_topics %>%
  pivot_longer(
    cols = starts_with("Topic"),
    names_to = "topic",
    values_to = "proportion"
  ) %>%
  mutate(
    topic_num = as.integer(str_remove(topic, "Topic")),
    topic_label = topic_labels[topic_num]
  ) %>%
  select(topic_num, topic_label, proportion,
         any_of(c("doc_id", "filename", "Title", "Author", "Article_Type",
                  "volume_num", "year", "month"))) %>%
  arrange(topic_num, desc(proportion))

cat("Linked table:", nrow(topic_article_link), "rows\n")
```

---

## 9b. Dominant Topic Assignment

```{r dominant-topic}
exemplar_threshold <- 0.40

dominant_topics <- doc_topics %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "proportion") %>%
  mutate(topic_num = as.integer(str_remove(topic, "Topic"))) %>%
  group_by(doc_id) %>%
  slice_max(proportion, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  mutate(
    topic_label = topic_labels[topic_num],
    strong_exemplar = proportion >= exemplar_threshold,
    proportion_pct = round(proportion * 100, 1)
  ) %>%
  select(doc_id, any_of(c("filename", "Title", "Author", "Article_Type",
         "volume_num", "year", "month")),
         dominant_topic = topic_num, topic_label, proportion_pct, strong_exemplar) %>%
  arrange(dominant_topic, desc(proportion_pct))

cat("Dominant topic assigned to", nrow(dominant_topics), "documents\n")
cat("Strong exemplars (>", exemplar_threshold * 100, "%):", sum(dominant_topics$strong_exemplar), "\n\n")

dominant_topics %>%
  group_by(dominant_topic, topic_label) %>%
  summarise(n_articles = n(), n_strong = sum(strong_exemplar),
            avg_proportion = round(mean(proportion_pct), 1), .groups = "drop") %>%
  print(n = chosen_K)
```

```{r strong-exemplars}
cat("\nSTRONG EXEMPLARS (>", exemplar_threshold * 100, "%):\n")

for (t in 1:chosen_K) {
  strong <- dominant_topics %>% filter(dominant_topic == t, strong_exemplar)
  cat("\n", rep("-", 60), "\n", sep = "")
  cat("Topic", t, ":", topic_labels[t], " (", nrow(strong), " strong)\n")
  if (nrow(strong) > 0) {
    for (i in 1:min(10, nrow(strong))) {
      row <- strong[i, ]
      cat(sprintf("  [%s%%] %s | %s | Vol %s %s\n",
                  row$proportion_pct,
                  ifelse(is.na(row$Title), row$filename, row$Title),
                  ifelse(is.na(row$Author) | row$Author == "Unknown", "-", row$Author),
                  row$volume_num, row$year))
    }
  } else {
    cat("  (none above threshold)\n")
  }
}
```

---

## 10. Top Articles per Topic

```{r top-articles-per-topic}
top_n_per_topic <- 15

for (t in 1:chosen_K) {
  cat("\n", rep("=", 70), "\n", sep = "")
  cat("TOPIC", t, ":", topic_labels[t], "\n")
  cat(rep("=", 70), "\n")
  cat("FREX:", paste(all_top_words$frex[t, 1:10], collapse = ", "), "\n\n")

  top_arts <- topic_article_link %>% filter(topic_num == t) %>% head(top_n_per_topic)

  for (i in 1:nrow(top_arts)) {
    row <- top_arts[i, ]
    cat(sprintf("  %2d. [%.1f%%] Vol %s, %s | %s | %s | %s\n",
                i, row$proportion * 100, row$volume_num, row$year,
                ifelse(is.na(row$Title), row$filename, row$Title),
                ifelse(is.na(row$Author) | row$Author == "Unknown", "-", row$Author),
                ifelse(is.na(row$Article_Type), "-", row$Article_Type)))
  }
}
```

---

## 11. Interactive Article Browser

The **Search** box (and the per-column filters) now also match the **full
article text** via the *Content* column — so you can keyword-search the body,
not just the title. Cells show the first 200 characters, but the search scans
the whole article. (For *meaning*-based search rather than literal words, use
§9 `nearest_docs()` in the RSM advanced-text-analysis notebook.)

```{r interactive-browser}
# Raw article body (header already stripped) for full-text search.
# processed_texts$text is the header-stripped raw body; its doc_id is the
# post-dedup id that also flows into meta -> doc_topics -> topic_article_link.
article_text <- processed_texts %>% select(doc_id, .body = text)

browse_data <- topic_article_link %>%
  group_by(topic_num) %>%
  slice_max(proportion, n = 25) %>%
  ungroup() %>%
  left_join(article_text, by = "doc_id") %>%
  mutate(
    proportion_pct = round(proportion * 100, 1),
    Content = str_squish(replace_na(.body, ""))   # collapse whitespace/newlines
  ) %>%
  select(Topic = topic_num, Label = topic_label, `%` = proportion_pct,
         any_of(c("Title", "Author", "Article_Type", "volume_num",
                  "year", "month")),
         Content,                # <-- full body text, now searchable
         any_of("filename"))

# DataTables column index (0-based) of the Content column, for the JS renderer
content_col <- which(names(browse_data) == "Content") - 1L

datatable(
  browse_data,
  filter = "top",
  options = list(
    pageLength = 20,
    scrollX = TRUE,
    # Show only the first 200 characters in the cell, but DataTables still
    # SEARCHES the full text (the 'filter' type receives the untruncated value).
    columnDefs = list(list(
      targets = content_col,
      render = DT::JS(
        "function(data, type, row) {",
        "  if (type === 'display' && data != null && data.length > 200) {",
        "    return data.substr(0, 200) + '…';",
        "  }",
        "  return data;",
        "}"
      )
    ))
  ),
  caption = paste("Top 25 articles per topic - the Search box now also matches",
                  "the FULL article text (Content column), not just metadata.")
)
```

---

## 12. Topic Prevalence Summary

```{r topic-prevalence, fig.height = 14, fig.width = 14}
topic_props_mean <- colMeans(doc_topics %>% select(starts_with("Topic")))

prevalence_df <- tibble(
  topic_num = 1:chosen_K, label = topic_labels,
  prevalence = topic_props_mean, pct = round(topic_props_mean * 100, 1)
) %>% arrange(desc(prevalence))

# Bar plot
par(mar = c(5, 22, 4, 2))
bar_y <- barplot(
  height    = prevalence_df$prevalence,
  names.arg = prevalence_df$label,
  horiz     = TRUE,
  las       = 1,
  col       = "#C1CDC1",
  border    = "#556B2F",
  main      = paste0("Topic Prevalence - RSM (Vols ",
                     min(input_vol_nums), "-", max(input_vol_nums), ")"),
  xlab      = "Expected Topic Proportion",
  cex.names = 0.8,
  xlim      = c(0, max(prevalence_df$prevalence) * 1.3)
)
text(
  x      = prevalence_df$prevalence + 0.005,
  y      = bar_y,                              # ← was seq(0.7, by = 1.2, ...)
  labels = paste0(prevalence_df$pct, "%"),
  cex    = 0.7, col = "#556B2F", font = 2
)
par(mar = c(5, 4, 4, 2))

print(prevalence_df %>% select(topic_num, label, pct), n = Inf)
write_csv(
  prevalence_df %>% select(topic_num, label, prevalence, pct),
  file.path(output_path, paste0("topic_prevalence_K", chosen_K, ".csv"))
)
```

---

## 13. STM Summary Plot

```{r stm-summary, fig.width=10, fig.height=6}
plot(stm_model, type = "summary", n = min(10, chosen_K),
     main = paste("Topic Prevalence (K =", chosen_K, ")"), xlim = c(0, 0.3))
```

---

## 14. Lollipop Prevalence with Top Words

```{r lollipop-prevalence, fig.width=10, fig.height=6}
labels_df <- tibble(
  topic = 1:chosen_K, name = topic_labels,
  words = sapply(1:chosen_K, function(i) paste(all_top_words$prob[i, 1:10], collapse = ", ")),
  full_label = paste0(name, ": ", words), prevalence = topic_props_mean)

ggplot(labels_df, aes(x = prevalence, y = reorder(full_label, prevalence))) +
  geom_segment(aes(x = 0, xend = prevalence, y = full_label, yend = full_label),
               linewidth = 1.2, color = "black") +
  geom_point(size = 0.5) +
  labs(title = paste("Topic Prevalence (K =", chosen_K, ")"),
       x = "Expected Topic Proportions", y = NULL) +
  theme_minimal(base_size = 10) +
  theme(axis.text.y = element_text(size = 8, hjust = 1),
        plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
        panel.grid.major.y = element_blank(), panel.grid.minor = element_blank()) +
  scale_x_continuous(limits = c(0, 0.35), breaks = seq(0, 0.35, 0.05))
```

---

## 15. Topic Prevalence Over Time

```{r prevalence-over-time, fig.width=10, fig.height=6}
cat("Docs:", length(docs), "| Meta rows:", nrow(meta), "\n")
cat("NA years:", sum(is.na(meta$year)), "| NA Article_Type:", sum(is.na(meta$Article_Type)), "\n")

# Use the same covariates as the model fit, or just year
prep_time <- estimateEffect(1:chosen_K ~ s(year) + Article_Type,
                            stmobj = stm_model,
                            metadata = meta,
                            uncertainty = "Global")

top_6_topics <- order(topic_props_mean, decreasing = TRUE)[1:min(6, chosen_K)]

par(mfrow = c(2, 3), mar = c(4, 4, 3, 1))
for (tn in top_6_topics) {
  plot(prep_time, covariate = "year", model = stm_model, topics = tn,
       method = "continuous", xlim = range(meta$year, na.rm = TRUE),
       main = str_wrap(topic_labels[tn], 30), xlab = "Year",
       ylab = "Topic Proportion", linecol = "#53868B",
       printlegend = TRUE, ci.level = 0.95, lwd = 2)
}
par(mfrow = c(1, 1))
```

---

## 16. Scatter Plot - Top 6 Topics Over Time

```{r scatter-top6, fig.width=10, fig.height=6}
topic_time_data <- doc_topics %>%
  select(starts_with("Topic"), year) %>%
  filter(!is.na(year)) %>%
  group_by(year) %>%
  summarize(across(starts_with("Topic"), mean, na.rm = TRUE), .groups = "drop") %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "prevalence") %>%
  mutate(topic_num = as.numeric(str_remove(topic, "Topic")),
         topic_label = str_wrap(topic_labels[topic_num], 30))

ggplot(topic_time_data %>% filter(topic_num %in% top_6_topics),
       aes(x = year, y = prevalence)) +
  geom_line(color = "#8B1A1A", size = 1.5) +
  geom_point(color = "#CD2626", size = 3, alpha = 0.7) +
  geom_smooth(method = "loess", color = "#8B0000", linetype = "dashed",
              se = TRUE, fill = "#FFB6C1", alpha = 0.3) +
  facet_wrap(~topic_label, ncol = 3, scales = "free_y") +
  labs(title = "Top 6 Topics Over Time - Relief Society Magazine",
       x = "Year", y = "Mean Topic Proportion") +
  theme_minimal(base_size = 12) +
  theme(strip.text = element_text(size = 10, face = "bold"),
        panel.grid.minor = element_blank(),
        plot.title = element_text(face = "bold", size = 14)) +
  scale_y_continuous(labels = percent_format(accuracy = 0.1))
```

---

## 17. All Topics Over Time

```{r all-topics-time, fig.width=10, fig.height=8}
ggplot(topic_time_data, aes(x = year, y = prevalence)) +
  geom_line(color = "#53868B", size = 0.8) +
  geom_point(color = "#53868B", size = 1.5, alpha = 0.5) +
  facet_wrap(~topic_label, ncol = 4, scales = "free_y") +
  labs(title = "Complete Topic Evolution - Relief Society Magazine",
       x = "Year", y = "Topic Proportion") +
  theme_minimal(base_size = 10) +
  theme(strip.text = element_text(size = 7, face = "bold"),
        panel.grid.minor = element_blank()) +
  scale_y_continuous(labels = percent_format(accuracy = 0.1))
```

---

## 18. Single Topic Detail

```{r single-topic-detail, fig.width=10, fig.height=6}
topic_to_examine <- 1
topic_detail <- topic_time_data %>% filter(topic_num == topic_to_examine)

ggplot(topic_detail, aes(x = year, y = prevalence)) +
  geom_line(color = "#53868B", size = 1.5) +
  geom_point(color = "#53868B", size = 4, alpha = 0.7) +
  geom_smooth(method = "loess", color = "#CD2626", fill = "#FFB6C1", alpha = 0.3, size = 1) +
  labs(title = topic_labels[topic_to_examine],
       subtitle = "Points = annual averages | Red band = smoothed trend",
       x = "Year", y = "Topic Proportion") +
  theme_minimal(base_size = 14) +
  theme(plot.title = element_text(face = "bold", size = 16),
        panel.grid.minor = element_blank()) +
  scale_y_continuous(labels = percent_format(accuracy = 0.1))
```

---

## 19. Topic Correlation Network

```{r correlation-network, fig.width=10, fig.height=8}
mod.out.corr <- topicCorr(stm_model)
plot(mod.out.corr, main = "Topic Correlation Network - RSM",
     vertex.color = "#C1CDC1", vertex.label.color = "#556B2F")
```

---

## 20. Word Clouds

```{r wordcloud-topic1, fig.width=8, fig.height=6}
rs_colors <- c("#6E8B3D", "#A2CD5A", "#BCEE68", "#556B2F")
cloud(stm_model, topic = 1, scale = c(3, 0.5), colors = rs_colors,
      main = topic_labels[1])
```

```{r wordcloud-all, fig.width=8, fig.height=6, eval=FALSE}
for (i in 1:chosen_K) {
  cloud(stm_model, topic = i, scale = c(3, 0.5), colors = rs_colors,
        main = topic_labels[i])
}
```

---

## 21. Topic Quality

```{r topic-quality, fig.width=8, fig.height=6}
topicQuality(stm_model, documents = docs)
```

---

## 22. Compare Two Topics

```{r compare-topics, fig.width=10, fig.height=6}
plot(stm_model, type = "perspectives", topics = c(1, 2),
     main = paste("Comparing", topic_labels[1], "vs", topic_labels[2]))
```

---

## 23. Trend Summary Statistics

```{r trend-summary}
topic_trends <- topic_time_data %>%
  group_by(topic_num, topic_label) %>%
  summarise(start_prev = first(prevalence), end_prev = last(prevalence),
            change = end_prev - start_prev,
            pct_change = round((change / start_prev) * 100, 1),
            trend = case_when(change > 0.005 ~ "Increasing",
                              change < -0.005 ~ "Decreasing", TRUE ~ "Stable"),
            .groups = "drop") %>%
  arrange(desc(abs(pct_change)))

cat("TOPIC CHANGE SUMMARY\n", rep("=", 50), "\n\n", sep = "")
for (i in 1:nrow(topic_trends)) {
  cat(sprintf("Topic %d (%s): %s by %.1f%%\n",
              topic_trends$topic_num[i], topic_trends$topic_label[i],
              ifelse(topic_trends$pct_change[i] > 0, "increased", "decreased"),
              abs(topic_trends$pct_change[i])))
}

cat("\n\nSUMMARY TABLE\n")
print(topic_trends %>% select(topic_num, topic_label, pct_change, trend))
```

---

## 23b. Detailed Topic Change Over Time

Comprehensive table showing each topic's percentage change from the
earliest year to the latest year, plus year-over-year percentage changes
to see when each topic rose or fell.

```{r topic-change-detailed}
cat(rep("=", 70), "\n", sep = "")
cat("DETAILED TOPIC PERCENTAGE CHANGE OVER TIME\n")
cat(rep("=", 70), "\n\n", sep = "")

# ============================================================
# Part 1: Overall percentage change (first year -> last year)
# ============================================================
overall_change <- topic_time_data %>%
  group_by(topic_num, topic_label) %>%
  arrange(year) %>%
  summarise(
    first_year       = first(year),
    last_year        = last(year),
    first_prevalence = first(prevalence),
    last_prevalence  = last(prevalence),
    abs_change_pp    = (last_prevalence - first_prevalence) * 100,   # pp
    pct_change       = ifelse(first_prevalence > 0.001,
                              (last_prevalence - first_prevalence) / first_prevalence * 100,
                              NA_real_),
    mean_prevalence  = mean(prevalence),
    max_prevalence   = max(prevalence),
    min_prevalence   = min(prevalence),
    peak_year        = year[which.max(prevalence)],
    trough_year      = year[which.min(prevalence)],
    .groups = "drop"
  ) %>%
  mutate(
    direction = case_when(
      pct_change >  10 ~ "Growing",
      pct_change < -10 ~ "Declining",
      TRUE             ~ "Stable"
    )
  ) %>%
  arrange(desc(pct_change))

cat(sprintf("OVERALL CHANGE (%d -> %d):\n\n",
            min(topic_time_data$year), max(topic_time_data$year)))
cat(sprintf("%-40s  %8s  %8s  %10s  %9s  %10s\n",
            "Topic", "First %", "Last %", "Change pp", "% Change", "Direction"))
cat(rep("-", 95), "\n", sep = "")
for (i in 1:nrow(overall_change)) {
  r <- overall_change[i, ]
  pct_str <- ifelse(is.na(r$pct_change), "N/A", sprintf("%+.1f%%", r$pct_change))
  cat(sprintf("%-40s  %7.2f%%  %7.2f%%  %+8.2fpp  %9s  %10s\n",
              str_trunc(paste0("T", r$topic_num, ": ", r$topic_label), 40),
              r$first_prevalence * 100, r$last_prevalence * 100,
              r$abs_change_pp, pct_str, r$direction))
}

cat("\n\nPEAK / TROUGH YEARS:\n\n")
cat(sprintf("%-40s  %10s  %10s  %10s\n",
            "Topic", "Peak Year", "Peak %", "Trough Year"))
cat(rep("-", 80), "\n", sep = "")
for (i in 1:nrow(overall_change)) {
  r <- overall_change[i, ]
  cat(sprintf("%-40s  %10d  %9.2f%%  %10d\n",
              str_trunc(paste0("T", r$topic_num, ": ", r$topic_label), 40),
              r$peak_year, r$max_prevalence * 100, r$trough_year))
}

# ============================================================
# Part 2: Year-over-year percentage changes (wide table)
# ============================================================
cat("\n\nYEAR-OVER-YEAR PERCENTAGE CHANGE (%):\n")
cat("(positive = prevalence grew that year; negative = prevalence dropped)\n\n")

yoy_change <- topic_time_data %>%
  arrange(topic_num, year) %>%
  group_by(topic_num) %>%
  mutate(
    prev_prevalence = lag(prevalence),
    yoy_pct = ifelse(!is.na(prev_prevalence) & prev_prevalence > 0.001,
                     (prevalence - prev_prevalence) / prev_prevalence * 100,
                     NA_real_)
  ) %>%
  ungroup() %>%
  select(topic_num, topic_label, year, yoy_pct)

yoy_wide <- yoy_change %>%
  select(topic_num, topic_label, year, yoy_pct) %>%
  pivot_wider(names_from = year, values_from = yoy_pct) %>%
  arrange(topic_num) %>%
  mutate(topic = paste0("T", topic_num, ": ", str_trunc(topic_label, 30))) %>%
  select(topic, everything(), -topic_num, -topic_label)

print(yoy_wide, n = chosen_K, width = Inf)

# ============================================================
# Part 3: Export detailed change table to CSV
# ============================================================
overall_change_export <- overall_change %>%
  mutate(
    first_prevalence_pct = round(first_prevalence * 100, 2),
    last_prevalence_pct  = round(last_prevalence * 100, 2),
    mean_prevalence_pct  = round(mean_prevalence * 100, 2),
    max_prevalence_pct   = round(max_prevalence * 100, 2),
    min_prevalence_pct   = round(min_prevalence * 100, 2),
    abs_change_pp        = round(abs_change_pp, 2),
    pct_change           = round(pct_change, 1)
  ) %>%
  select(topic_num, topic_label, first_year, last_year,
         first_prevalence_pct, last_prevalence_pct,
         abs_change_pp, pct_change, direction,
         mean_prevalence_pct, max_prevalence_pct, peak_year,
         min_prevalence_pct, trough_year)

change_file <- file.path(output_path, paste0("topic_change_over_time_K", chosen_K, ".csv"))
write_csv(overall_change_export, change_file)
cat("\n\nDetailed change table saved to:", change_file, "\n")

yoy_file <- file.path(output_path, paste0("topic_year_over_year_change_K", chosen_K, ".csv"))
write_csv(yoy_change %>%
            mutate(yoy_pct = round(yoy_pct, 2)),
          yoy_file)
cat("Year-over-year change saved to:", yoy_file, "\n")
```

---

## 24. Topic Prevalence Stats Table

```{r prevalence-stats}
doc_topics %>%
  select(starts_with("Topic")) %>%
  summarise(across(everything(), mean, na.rm = TRUE)) %>%
  pivot_longer(everything(), names_to = "topic", values_to = "mean_proportion") %>%
  mutate(topic_num = as.numeric(str_remove(topic, "Topic")),
         label = topic_labels[topic_num],
         percentage = round(mean_proportion * 100, 2),
         rank = rank(-mean_proportion)) %>%
  arrange(rank) %>%
  select(rank, label, percentage) %>%
  print()
```

---

## 25. Article Type Distribution per Topic

```{r type-by-topic}
type_topic <- topic_article_link %>%
  filter(!is.na(Article_Type)) %>%
  group_by(topic_num, topic_label, Article_Type) %>%
  summarise(mean_proportion = mean(proportion), n_articles = n_distinct(filename),
            .groups = "drop") %>%
  arrange(topic_num, desc(mean_proportion))

type_topic %>%
  group_by(topic_num, topic_label) %>%
  slice_max(mean_proportion, n = 3) %>%
  print(n = chosen_K * 3)
```

---

## 26. Topic-Article Type Heatmap

```{r type-heatmap, fig.width=10, fig.height=7}
heatmap_data <- topic_article_link %>%
  filter(!is.na(Article_Type)) %>%
  group_by(topic_num, Article_Type) %>%
  summarise(mean_prop = mean(proportion), .groups = "drop") %>%
  pivot_wider(names_from = Article_Type, values_from = mean_prop, values_fill = 0)

heatmap_matrix <- as.matrix(heatmap_data %>% select(-topic_num))
rownames(heatmap_matrix) <- paste0("T", heatmap_data$topic_num, ": ",
                                    str_trunc(topic_labels[heatmap_data$topic_num], 25))

pheatmap(heatmap_matrix, main = "Topic Affinity by Article Type - RSM",
  color = colorRampPalette(c("white", "#C1CDC1", "#6E8B3D", "#556B2F"))(50),
  cluster_rows = TRUE, cluster_cols = TRUE, display_numbers = TRUE,
  number_format = "%.2f", fontsize_number = 7, fontsize_row = 9,
  fontsize_col = 9, angle_col = 45)
```

---
```{r}
library(RColorBrewer)
display.brewer.all()
```

## 27. Stacked Area Chart - Topic Composition Over Time

```{r stacked-area, fig.width=12, fig.height=6}
stacked_data <- topic_time_data %>%
  mutate(label = topic_labels[topic_num])

ggplot(stacked_data, aes(x = year, y = prevalence, fill = reorder(label, -topic_num))) +
  geom_area(alpha = 0.8, color = "white", linewidth = 0.3) +
  labs(title = "Topic Composition Over Time - RSM",
       x = "Year", y = "Topic Proportion", fill = "Topic") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold", size = 14),
        legend.text = element_text(size = 7), legend.key.size = unit(0.4, "cm")) +
  scale_y_continuous(labels = percent_format()) +
  scale_fill_brewer(palette = "Set2", direction = -1)
```

---

## 28. Topic Co-occurrence Within Articles

```{r topic-cooccurrence, fig.width=9, fig.height=8}
topic_cor <- cor(doc_topics %>% select(starts_with("Topic")))
rownames(topic_cor) <- paste0("T", 1:chosen_K, ": ", str_trunc(topic_labels, 20))
colnames(topic_cor) <- paste0("T", 1:chosen_K)

pheatmap(topic_cor, main = "Topic Co-occurrence - RSM",
  color = colorRampPalette(c("#2166AC", "white", "#B2182B"))(50),
  display_numbers = TRUE, number_format = "%.2f", fontsize_number = 8,
  breaks = seq(-1, 1, length.out = 51))
```

---

## 29. Exclusivity vs Semantic Coherence

```{r exclusivity-coherence, fig.width=9, fig.height=7}
topic_qual <- data.frame(
  topic = 1:chosen_K, label = topic_labels,
  coherence = semanticCoherence(stm_model, docs),
  exclusivity = exclusivity(stm_model))

ggplot(topic_qual, aes(x = coherence, y = exclusivity)) +
  geom_point(size = 4, color = "#6E8B3D") +
  geom_text(aes(label = paste0("T", topic)), vjust = -1, size = 3.5) +
  geom_text(aes(label = str_trunc(label, 25)), vjust = 2, size = 2.5, color = "grey40") +
  labs(title = "Topic Quality: Exclusivity vs Semantic Coherence",
       x = "Semantic Coherence", y = "Exclusivity") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold", size = 14))
```

---

## 30. Dominant Topic Distribution

```{r dominant-distribution, fig.width=10, fig.height=6}
dom_summary <- dominant_topics %>% count(dominant_topic, topic_label) %>%
  mutate(pct = n / sum(n) * 100)

ggplot(dom_summary, aes(x = reorder(topic_label, n), y = n, fill = pct)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, " (", round(pct, 1), "%)")), hjust = -0.1, size = 3) +
  coord_flip() +
  labs(title = "Articles per Dominant Topic - RSM", x = NULL, y = "Number of Articles") +
  theme_minimal(base_size = 11) +
  scale_fill_gradient(low = "#C1CDC1", high = "#556B2F") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.15)))
```

---

## 31. Topic-by-Volume Heatmap

```{r topic-volume-heatmap, fig.width=14, fig.height=7}
vol_topic_data <- doc_topics %>%
  select(starts_with("Topic"), volume_num) %>%
  filter(!is.na(volume_num)) %>%
  group_by(volume_num) %>%
  summarize(across(starts_with("Topic"), mean, na.rm = TRUE), .groups = "drop")

vol_matrix <- as.matrix(vol_topic_data %>% select(-volume_num))
rownames(vol_matrix) <- paste0("Vol ", vol_topic_data$volume_num)
colnames(vol_matrix) <- paste0("T", 1:chosen_K, ": ", str_trunc(topic_labels, 20))

pheatmap(t(vol_matrix), main = "Topic Prevalence by Volume - RSM",
  color = colorRampPalette(c("white", "#C1CDC1", "#6E8B3D", "#556B2F"))(100),
  cluster_rows = TRUE, cluster_cols = FALSE, display_numbers = FALSE,
  fontsize_row = 8, fontsize_col = 9, angle_col = 45, border_color = "grey90")
```

---

## 32. Author-Topic Analysis

```{r author-topic, fig.width=12, fig.height=8}
author_counts <- dominant_topics %>%
  filter(!is.na(Author), Author != "Unknown", nchar(Author) > 1) %>%
  count(Author, sort = TRUE)

cat("Authors with named articles:", nrow(author_counts), "\n")

if (nrow(author_counts) >= 2) {
  top_authors <- author_counts %>% head(min(20, nrow(author_counts))) %>% pull(Author)
  cat("Top authors:", paste(head(top_authors, 5), collapse = ", "), "\n\n")

  author_topic_data <- topic_article_link %>%
    filter(Author %in% top_authors) %>%
    group_by(Author, topic_num) %>%
    summarise(mean_prop = mean(proportion), .groups = "drop") %>%
    pivot_wider(names_from = topic_num, values_from = mean_prop, values_fill = 0)

  for (k in 1:chosen_K) {
    if (!as.character(k) %in% names(author_topic_data)) {
      author_topic_data[[as.character(k)]] <- 0
    }
  }
  author_topic_data <- author_topic_data %>%
    select(Author, all_of(as.character(1:chosen_K)))

  author_matrix <- as.matrix(author_topic_data %>% select(-Author))
  author_matrix[is.na(author_matrix) | is.nan(author_matrix) | is.infinite(author_matrix)] <- 0
  rownames(author_matrix) <- author_topic_data$Author
  colnames(author_matrix) <- paste0("T", 1:chosen_K, ": ", str_trunc(topic_labels, 18))

  pheatmap(author_matrix,
    main = paste0("Author-Topic Affinity (Top ", length(top_authors), " Authors) - RSM"),
    color = colorRampPalette(c("white", "#C1CDC1", "#6E8B3D", "#556B2F"))(100),
    cluster_rows = FALSE, cluster_cols = FALSE,
    fontsize_row = 8, fontsize_col = 8, angle_col = 45, border_color = "grey90")
} else {
  cat("\nSkipping author-topic heatmap: the RSM inventory has no author data for Vols 1-10.\n")
  cat("Authors ARE present in the filenames (e.g., 'Lula_Greene_Richards') but were not\n")
  cat("parsed into the inventory. To enable this visualization, update the RSM inventory\n")
  cat("to populate the Author column for early volumes.\n")
}
```

---

## 33. Topic Diversity per Volume

```{r topic-diversity, fig.width=10, fig.height=6}
vol_diversity <- doc_topics %>%
  select(starts_with("Topic"), volume_num, year) %>%
  filter(!is.na(volume_num)) %>%
  group_by(volume_num) %>%
  summarize(across(starts_with("Topic"), mean, na.rm = TRUE),
            year = first(year), n_articles = n(), .groups = "drop") %>%
  rowwise() %>%
  mutate(entropy = { props <- c_across(starts_with("Topic")); props <- props[props > 0]
    -sum(props * log(props)) },
    diversity = entropy / log(chosen_K)) %>%
  ungroup()

ggplot(vol_diversity, aes(x = volume_num, y = diversity)) +
  geom_col(aes(fill = diversity), show.legend = FALSE) +
  geom_text(aes(label = round(diversity, 2)), vjust = -0.3, size = 2.5) +
  labs(title = "Topic Diversity per Volume - RSM",
       subtitle = "Higher = more thematically diverse (Shannon entropy)",
       x = "Volume", y = "Diversity (0-1)") +
  theme_minimal(base_size = 11) +
  scale_fill_gradient(low = "#C1CDC1", high = "#556B2F") +
  scale_y_continuous(limits = c(0, 1.1))
```

---

## 34. Ridgeline Plot

```{r ridgeline, fig.width=10, fig.height=8}
ridge_data <- topic_article_link %>%
  mutate(topic_label_full = paste0("T", topic_num, ": ", topic_label))

ggplot(ridge_data, aes(x = proportion, y = reorder(topic_label_full, topic_num),
                        fill = after_stat(x))) +
  geom_density_ridges_gradient(scale = 2.5, rel_min_height = 0.01, gradient_lwd = 0.3) +
  scale_fill_gradient(low = "#C1CDC1", high = "#556B2F", guide = "none") +
  labs(title = "Distribution of Topic Proportions - RSM",
       x = "Topic Proportion", y = NULL) +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold", size = 14)) +
  scale_x_continuous(labels = percent_format(), limits = c(0, NA))
```

---

## 35. Topic Dendrogram

```{r dendrogram, fig.width=10, fig.height=6}
topic_word_matrix <- exp(stm_model$beta$logbeta[[1]])
topic_dist <- dist(topic_word_matrix, method = "euclidean")
topic_clust <- hclust(topic_dist, method = "ward.D2")
topic_clust$labels <- paste0("T", 1:chosen_K, ": ", topic_labels)

par(mar = c(2, 4, 3, 12))
plot(as.dendrogram(topic_clust), horiz = TRUE,
     main = "Topic Similarity Dendrogram - RSM", xlab = "Distance", cex = 0.8)
par(mar = c(5, 4, 4, 2))
```

---

## 36. Within-Topic Vocabulary Comparison (Early vs Late Period)

When the same topic appears across both eras of the Magazine, does the
**language** shift? This reveals how the publication's framing of shared
concerns evolved over time.

```{r vocab-comparison-era, fig.width=16, fig.height=20}
cat(rep("=", 70), "\n", sep = "")
cat("WITHIN-TOPIC VOCABULARY COMPARISON (EARLY vs LATE)\n")
cat(rep("=", 70), "\n\n", sep = "")

# Split into early and late eras at median year
median_year <- median(meta$year, na.rm = TRUE)
doc_topics_era <- doc_topics %>%
  mutate(era = ifelse(year <= median_year, "Early", "Late"))

cat("Era split at year", median_year, "\n")
cat("  Early:", sum(doc_topics_era$era == "Early"), "documents\n")
cat("  Late: ", sum(doc_topics_era$era == "Late"), "documents\n\n")

# Function: get word frequencies for top-quartile docs of a topic in an era
# (includes OCR junk filtering as safety net even though stopwords catch most)
get_topic_words_by_era <- function(topic_num, era_name) {
  topic_col <- paste0("Topic", topic_num)
  era_docs <- doc_topics_era %>% filter(era == era_name)
  threshold <- quantile(era_docs[[topic_col]], 0.75, na.rm = TRUE)

  doc_ids <- era_docs %>%
    filter(.data[[topic_col]] >= threshold) %>%
    pull(doc_id)

  words <- processed_texts %>%
    filter(doc_id %in% doc_ids) %>%
    pull(text_final) %>%
    paste(collapse = " ") %>%
    str_split("\\s+") %>%
    `[[`(1)

  freq <- sort(table(words), decreasing = TRUE)
  tibble(word = names(freq), count = as.integer(freq)) %>%
    mutate(proportion = count / sum(count)) %>%
    filter(
      nchar(word) >= 4,
      !word %in% all_stopwords,
      !is_ocr_fragment(word)
    )
}

# Pick the 6 most prevalent topics for comparison
top_6_for_vocab <- order(topic_props_mean, decreasing = TRUE)[1:min(6, chosen_K)]

cat("Comparing vocabulary for top", length(top_6_for_vocab), "topics:\n")
for (t in top_6_for_vocab) {
  cat(sprintf("  T%d: %s\n", t, topic_labels[t]))
}
cat("\n")

# Build log-ratio plots
vocab_plots <- list()
for (idx in seq_along(top_6_for_vocab)) {
  t <- top_6_for_vocab[idx]

  words_early <- get_topic_words_by_era(t, "Early")
  words_late  <- get_topic_words_by_era(t, "Late")

  word_compare <- full_join(
    words_early %>% select(word, early_prop = proportion),
    words_late  %>% select(word, late_prop = proportion),
    by = "word"
  ) %>%
    replace_na(list(early_prop = 0.0001, late_prop = 0.0001)) %>%
    mutate(
      log_ratio = log2(early_prop / late_prop),
      avg_prop = (early_prop + late_prop) / 2
    ) %>%
    filter(avg_prop > 0.001) %>%
    arrange(desc(abs(log_ratio)))

  # Top 20 words each direction
  top_early <- word_compare %>% filter(log_ratio > 0) %>% head(20)
  top_late  <- word_compare %>% filter(log_ratio < 0) %>% head(20)
  plot_words <- bind_rows(top_early, top_late) %>%
    mutate(
      direction = ifelse(log_ratio > 0,
                         paste0("More in Early (\u2264", median_year, ")"),
                         paste0("More in Late (>", median_year, ")")),
      word = reorder(word, log_ratio)
    )

  early_label <- paste0("More in Early (\u2264", median_year, ")")
  late_label  <- paste0("More in Late (>", median_year, ")")

  p <- ggplot(plot_words, aes(x = log_ratio, y = word, fill = direction)) +
    geom_col(alpha = 0.8) +
    geom_vline(xintercept = 0, linewidth = 0.8) +
    scale_fill_manual(values = setNames(c("#6E8B3D", "#556B2F"),
                                        c(early_label, late_label))) +
    labs(title = paste0("T", t, ": ", str_trunc(topic_labels[t], 35)),
         x = paste0("Word emphasis by period: Right= Before ", median_year,
                    " and Left= After ", median_year),
         y = NULL, fill = NULL) +
    theme_minimal(base_size = 8) +
    theme(legend.position = "none",
          plot.title = element_text(size = 10, face = "bold"))

  vocab_plots[[idx]] <- p
}

# Combine plots
if (length(vocab_plots) >= 6) {
  (vocab_plots[[1]] | vocab_plots[[2]] | vocab_plots[[3]]) /
  (vocab_plots[[4]] | vocab_plots[[5]] | vocab_plots[[6]]) +
    plot_annotation(
      title = "Within-Topic Vocabulary Shifts: Early vs Late Period",
      subtitle = paste0("Top 20 words each era emphasizes differently (split at ",
                        median_year, ")"),
      theme = theme(plot.title = element_text(size = 16, face = "bold"))
    )
} else if (length(vocab_plots) >= 1) {
  wrap_plots(vocab_plots, ncol = min(3, length(vocab_plots))) +
    plot_annotation(title = "Within-Topic Vocabulary Shifts: Early vs Late Period")
}
```

---
```{r, fig.width=16, fig.height=10}
cat(rep("=", 70), "\n", sep = "")
cat("WITHIN-TOPIC VOCABULARY COMPARISON (EARLY vs LATE) — paginated\n")
cat(rep("=", 70), "\n\n", sep = "")

# Split into early and late eras at median year
median_year <- median(meta$year, na.rm = TRUE)
doc_topics_era <- doc_topics %>%
  mutate(era = ifelse(year <= median_year, "Early", "Late"))

cat("Era split at year", median_year, "\n")
cat("  Early:", sum(doc_topics_era$era == "Early"), "documents\n")
cat("  Late: ", sum(doc_topics_era$era == "Late"), "documents\n\n")

# Function: get word frequencies for top-quartile docs of a topic in an era
get_topic_words_by_era <- function(topic_num, era_name) {
  topic_col <- paste0("Topic", topic_num)
  era_docs <- doc_topics_era %>% filter(era == era_name)
  threshold <- quantile(era_docs[[topic_col]], 0.75, na.rm = TRUE)

  doc_ids <- era_docs %>%
    filter(.data[[topic_col]] >= threshold) %>%
    pull(doc_id)

  words <- processed_texts %>%
    filter(doc_id %in% doc_ids) %>%
    pull(text_final) %>%
    paste(collapse = " ") %>%
    str_split("\\s+") %>%
    `[[`(1)

  freq <- sort(table(words), decreasing = TRUE)
  tibble(word = names(freq), count = as.integer(freq)) %>%
    mutate(proportion = count / sum(count)) %>%
    filter(
      nchar(word) >= 4,
      !word %in% all_stopwords,
      !is_ocr_fragment(word)
    )
}

# All topics ordered by prevalence (most prevalent first)
all_topics_ordered <- order(topic_props_mean, decreasing = TRUE)

cat("Building plots for all", length(all_topics_ordered), "topics...\n")

# Build a plot for every topic at GENEROUS sizing
vocab_plots <- list()
for (idx in seq_along(all_topics_ordered)) {
  t <- all_topics_ordered[idx]

  words_early <- get_topic_words_by_era(t, "Early")
  words_late  <- get_topic_words_by_era(t, "Late")

  word_compare <- full_join(
    words_early %>% select(word, early_prop = proportion),
    words_late  %>% select(word, late_prop  = proportion),
    by = "word"
  ) %>%
    replace_na(list(early_prop = 0.0001, late_prop = 0.0001)) %>%
    mutate(
      log_ratio = log2(early_prop / late_prop),
      avg_prop  = (early_prop + late_prop) / 2
    ) %>%
    filter(avg_prop > 0.001) %>%
    arrange(desc(abs(log_ratio)))

  top_early <- word_compare %>% filter(log_ratio > 0) %>% head(20)
  top_late  <- word_compare %>% filter(log_ratio < 0) %>% head(20)

  early_label <- paste0("More in Early (≤", median_year, ")")
  late_label  <- paste0("More in Late (>",    median_year, ")")

  plot_words <- bind_rows(top_early, top_late) %>%
    mutate(
      direction = ifelse(log_ratio > 0, early_label, late_label),
      word      = reorder(word, log_ratio)
    )

  p <- ggplot(plot_words, aes(x = log_ratio, y = word, fill = direction)) +
    geom_col(alpha = 0.85) +
    geom_vline(xintercept = 0, linewidth = 0.8) +
    scale_fill_manual(values = setNames(c("#6E8B3D", "#556B2F"),
                                        c(early_label, late_label))) +
    labs(
      title = paste0("T", t, ": ", str_trunc(topic_labels[t], 45)),
      x     = paste0("← More after ", median_year,
                     "   |   More before ", median_year, " →"),
      y     = NULL,
      fill  = NULL
    ) +
    theme_minimal(base_size = 10) +
    theme(
      legend.position = "none",
      plot.title      = element_text(size = 12, face = "bold"),
      axis.text.y     = element_text(size = 9),
      axis.title.x    = element_text(size = 9),
      plot.margin     = margin(8, 12, 8, 12)
    )

  vocab_plots[[idx]] <- p
}

# Paginate: 4 plots per page, 2 columns wide (2x2 per page)
plots_per_page <- 4
n_pages <- ceiling(length(vocab_plots) / plots_per_page)

for (page in seq_len(n_pages)) {
  start_i <- (page - 1) * plots_per_page + 1
  end_i   <- min(start_i + plots_per_page - 1, length(vocab_plots))
  batch   <- vocab_plots[start_i:end_i]

  combined <- wrap_plots(batch, ncol = 2) +
    plot_annotation(
      title    = paste0("Within-Topic Vocabulary Shifts — Page ",
                        page, " of ", n_pages),
      subtitle = paste0("Topics ", start_i, "–", end_i,
                        " by prevalence rank. Era split at ", median_year,
                        ". Light green = more before; dark green = more after."),
      theme    = theme(plot.title    = element_text(size = 18, face = "bold"),
                       plot.subtitle = element_text(size = 12))
    )

  print(combined)

  # Save each page as a standalone PNG (so dissertation renders at full size,
  # not the notebook's compressed display width).
  ggsave(
    file.path(output_path,
              paste0("vocab_shifts_K", chosen_K, "_page", page, ".png")),
    combined, width = 14, height = 24, dpi = 200, limitsize = FALSE
  )
}

cat("\nSaved", n_pages, "PNG pages to:", output_path, "\n")
```

##USING JSD TO IDENTIFY THE CHANGE OF YEAR TO A SPECIFIC TOPIC Y AXIS RATHER THAN NORMALIZING AND USING A MEDIAN YEAR FOR THE CHANGE IN WORD USAGE
```{r vocab-comparison-changepoint, fig.width=14, fig.height=22}
cat(rep("=", 70), "\n", sep = "")
cat("WITHIN-TOPIC VOCABULARY CHANGEPOINT DETECTION — paginated\n")
cat(rep("=", 70), "\n\n", sep = "")

# ---- Helpers (reused below for trajectory chunk too) ----
.topic_words <- function(doc_ids) {
  words <- processed_texts %>%
    filter(doc_id %in% doc_ids) %>%
    pull(text_final) %>%
    paste(collapse = " ") %>%
    str_split("\\s+") %>%
    `[[`(1)
  words[nchar(words) >= 4 &
        !words %in% all_stopwords &
        !is_ocr_fragment(words)]
}

.js_divergence <- function(words_a, words_b) {
  if (length(words_a) < 50 || length(words_b) < 50) return(0)
  vocab_union <- union(unique(words_a), unique(words_b))
  p_a <- as.numeric(table(factor(words_a, levels = vocab_union))) / length(words_a)
  p_b <- as.numeric(table(factor(words_b, levels = vocab_union))) / length(words_b)
  m   <- (p_a + p_b) / 2
  eps <- 1e-12
  kl  <- function(p, q) sum(p * log2((p + eps) / (q + eps)), na.rm = TRUE)
  (kl(p_a, m) + kl(p_b, m)) / 2
}

find_topic_changepoint <- function(topic_num, min_docs_per_side = 15) {
  topic_col <- paste0("Topic", topic_num)
  threshold <- quantile(doc_topics[[topic_col]], 0.75, na.rm = TRUE)

  topic_docs <- doc_topics %>%
    filter(.data[[topic_col]] >= threshold, !is.na(year)) %>%
    select(doc_id, year) %>%
    arrange(year)

  if (nrow(topic_docs) < 2 * min_docs_per_side) {
    return(list(year = NA_integer_, max_div = NA_real_, curve = NULL))
  }

  candidates <- sort(unique(topic_docs$year))
  candidates <- candidates[
    vapply(candidates, function(y) {
      sum(topic_docs$year <= y) >= min_docs_per_side &
      sum(topic_docs$year >  y) >= min_docs_per_side
    }, logical(1))
  ]
  if (length(candidates) == 0) {
    return(list(year = NA_integer_, max_div = NA_real_, curve = NULL))
  }

  divergences <- vapply(candidates, function(yr) {
    early_ids <- topic_docs$doc_id[topic_docs$year <= yr]
    late_ids  <- topic_docs$doc_id[topic_docs$year >  yr]
    .js_divergence(.topic_words(early_ids), .topic_words(late_ids))
  }, numeric(1))

  list(
    # as.integer() keeps the type consistent with the NA_integer_ branch above,
    # so the downstream vapply(..., integer(1), "year") doesn't choke on a double.
    year    = as.integer(candidates[which.max(divergences)]),
    max_div = max(divergences),
    curve   = tibble(year = candidates, divergence = divergences)
  )
}

# ---- Detect changepoint for every topic (cache to .rds so trajectory chunk reuses) ----
cat("Detecting changepoints for all", chosen_K, "topics...\n")
changepoints <- list()
for (t in 1:chosen_K) {
  cat(sprintf("  T%d: %s ... ", t, str_trunc(topic_labels[t], 35)))
  cp <- find_topic_changepoint(t)
  changepoints[[t]] <- cp
  if (is.na(cp$year)) {
    cat("(too few docs)\n")
  } else {
    cat(sprintf("split at %d (JS = %.3f)\n", cp$year, cp$max_div))
  }
}

# Save for trajectory chunk
saveRDS(changepoints,
        file.path(output_path, paste0("changepoints_K", chosen_K, ".rds")))

# Summary CSV
changepoint_df <- tibble(
  topic_num   = 1:chosen_K,
  label       = topic_labels,
  prevalence  = topic_props_mean,
  split_year  = vapply(changepoints, `[[`, integer(1),  "year"),
  max_jsd     = vapply(changepoints, `[[`, numeric(1), "max_div")
) %>%
  arrange(desc(prevalence))

cat("\nChangepoint summary (sorted by prevalence):\n")
print(changepoint_df, n = Inf)

write_csv(changepoint_df,
          file.path(output_path, paste0("topic_changepoints_K", chosen_K, ".csv")))

# ---- Word frequencies for a topic on one side of its changepoint ----
get_topic_words_at_split <- function(topic_num, split_year, side = c("early","late")) {
  side <- match.arg(side)
  topic_col <- paste0("Topic", topic_num)
  threshold <- quantile(doc_topics[[topic_col]], 0.75, na.rm = TRUE)

  era_filter <- if (side == "early") rlang::expr(year <= !!split_year)
                else                  rlang::expr(year >  !!split_year)

  doc_ids <- doc_topics %>%
    filter(.data[[topic_col]] >= threshold, !is.na(year)) %>%
    filter(!!era_filter) %>%
    pull(doc_id)

  words <- .topic_words(doc_ids)
  freq  <- sort(table(words), decreasing = TRUE)
  tibble(word = names(freq), count = as.integer(freq)) %>%
    mutate(proportion = count / sum(count))
}

# ---- Build a plot per topic at GENEROUS sizing ----
all_topics_ordered <- order(topic_props_mean, decreasing = TRUE)

vocab_plots <- list()
for (idx in seq_along(all_topics_ordered)) {
  t  <- all_topics_ordered[idx]
  cp <- changepoints[[t]]

  if (is.na(cp$year)) {
    vocab_plots[[idx]] <- ggplot() +
      ggplot::annotate("text", x = 0, y = 0,
               label = paste0("T", t, ": insufficient data"),
               size = 6) +
      theme_void()
    next
  }

  split_yr <- cp$year
  words_early <- get_topic_words_at_split(t, split_yr, "early")
  words_late  <- get_topic_words_at_split(t, split_yr, "late")

  word_compare <- full_join(
    words_early %>% select(word, early_prop = proportion),
    words_late  %>% select(word, late_prop  = proportion),
    by = "word"
  ) %>%
    replace_na(list(early_prop = 0.0001, late_prop = 0.0001)) %>%
    mutate(
      log_ratio = log2(early_prop / late_prop),
      avg_prop  = (early_prop + late_prop) / 2
    ) %>%
    filter(avg_prop > 0.001) %>%
    arrange(desc(abs(log_ratio)))

  top_early <- word_compare %>% filter(log_ratio > 0) %>% head(15)
  top_late  <- word_compare %>% filter(log_ratio < 0) %>% head(15)

  early_label <- paste0("More ≤", split_yr)
  late_label  <- paste0("More >",     split_yr)

  plot_words <- bind_rows(top_early, top_late) %>%
    mutate(
      direction = ifelse(log_ratio > 0, early_label, late_label),
      word      = reorder(word, log_ratio)
    )

  p <- ggplot(plot_words, aes(x = log_ratio, y = word, fill = direction)) +
    geom_col(alpha = 0.85) +
    geom_vline(xintercept = 0, linewidth = 0.8) +
    scale_fill_manual(values = setNames(c("#6E8B3D", "#556B2F"),
                                        c(early_label, late_label))) +
    labs(
      title    = paste0("T", t, ": ", str_trunc(topic_labels[t], 45)),
      subtitle = paste0("Changepoint: ", split_yr,
                        "   |   JSD = ", sprintf("%.2f", cp$max_div),
                        "   |   Prevalence: ",
                        sprintf("%.1f%%", topic_props_mean[t] * 100)),
      x        = paste0("← after ", split_yr,
                        "   |   before ", split_yr, " →"),
      y        = NULL, fill = NULL
    ) +
    theme_minimal(base_size = 10) +
    theme(
      legend.position = "none",
      plot.title      = element_text(size = 12, face = "bold"),
      plot.subtitle   = element_text(size = 10, color = "grey35"),
      axis.text.y     = element_text(size = 10),
      axis.title.x    = element_text(size = 9),
      plot.margin     = margin(8, 12, 8, 12)
    )

  vocab_plots[[idx]] <- p
}

# Paginate: 4 plots per page, 2 columns wide
plots_per_page <- 4
n_pages <- ceiling(length(vocab_plots) / plots_per_page)

for (page in seq_len(n_pages)) {
  start_i <- (page - 1) * plots_per_page + 1
  end_i   <- min(start_i + plots_per_page - 1, length(vocab_plots))
  batch   <- vocab_plots[start_i:end_i]

  combined <- wrap_plots(batch, ncol = 2) +
    plot_annotation(
      title    = paste0("Topic-Specific Vocabulary Changepoints — Page ",
                        page, " of ", n_pages),
      subtitle = paste0("Topics ", start_i, "–", end_i,
                        " by prevalence rank. Each split at its own ",
                        "JSD-maximizing year."),
      theme    = theme(plot.title    = element_text(size = 18, face = "bold"),
                       plot.subtitle = element_text(size = 12))
    )

  print(combined)

  ggsave(
    file.path(output_path,
              paste0("changepoint_shifts_K", chosen_K, "_page", page, ".png")),
    combined, width = 14, height = 22, dpi = 200, limitsize = FALSE
  )
}

cat("\nSaved", n_pages, "PNG pages to:", output_path, "\n")
```

##WORDS CHANGE OVER TIME USING JENSEN-SHANNON DIVERGENCE TO MARK CHANGE OVER TIME RELATIVE TO EACH TOPIC
```{r}
cat(rep("=", 70), "\n", sep = "")
cat("PER-TOPIC WORD TRAJECTORIES OVER TIME\n")
cat(rep("=", 70), "\n\n", sep = "")

# Reload changepoints if not in memory (from previous chunk)
if (!exists("changepoints")) {
  changepoints <- readRDS(
    file.path(output_path, paste0("changepoints_K", chosen_K, ".rds"))
  )
}

# ---- Compute trajectories for one topic ----
# For each of the topic's top N words, the proportion of that word's
# occurrences across all topic-tokens in each year. Smoothed with loess
# to dampen year-to-year noise. Limited to words that have substantive
# presence (avoid plotting words that appear in only 1-2 years).
get_word_trajectories <- function(topic_num, n_words = 8, min_years_present = 4) {
  topic_col <- paste0("Topic", topic_num)
  threshold <- quantile(doc_topics[[topic_col]], 0.75, na.rm = TRUE)

  topic_doc_info <- doc_topics %>%
    filter(.data[[topic_col]] >= threshold, !is.na(year)) %>%
    select(doc_id, year)

  if (nrow(topic_doc_info) < 30) return(NULL)

  # Tokenize all top-quartile docs, tagged with year
  word_year_df <- processed_texts %>%
    filter(doc_id %in% topic_doc_info$doc_id) %>%
    select(doc_id, text_final) %>%
    inner_join(topic_doc_info, by = "doc_id") %>%
    mutate(words = str_split(text_final, "\\s+")) %>%
    select(year, words) %>%
    unnest(words) %>%
    filter(nchar(words) >= 4,
           !words %in% all_stopwords,
           !is_ocr_fragment(words))

  # Top N most frequent words overall in the topic — but require they
  # appear in at least min_years_present distinct years (avoids one-shot OCR fluke)
  word_year_counts <- word_year_df %>%
    count(year, words) %>%
    group_by(words) %>%
    mutate(years_present = n_distinct(year),
           total = sum(n)) %>%
    ungroup()

  top_words <- word_year_counts %>%
    filter(years_present >= min_years_present) %>%
    distinct(words, total) %>%
    arrange(desc(total)) %>%
    head(n_words) %>%
    pull(words)

  if (length(top_words) == 0) return(NULL)

  # Per-year total of any top-word tokens (denominator)
  per_year_totals <- word_year_df %>%
    filter(words %in% top_words) %>%
    count(year, name = "year_total")

  trajectory <- word_year_counts %>%
    filter(words %in% top_words) %>%
    inner_join(per_year_totals, by = "year") %>%
    mutate(prop = n / year_total) %>%
    select(year, word = words, prop)

  # Fill missing year×word combos with zero so lines drop to 0 where word absent
  all_years <- seq(min(trajectory$year), max(trajectory$year))
  trajectory <- trajectory %>%
    complete(year = all_years, word = top_words, fill = list(prop = 0))

  trajectory
}

# ---- Build a trajectory plot per topic ----
all_topics_ordered <- order(topic_props_mean, decreasing = TRUE)

# Distinct color palette that can render 8 lines clearly
traj_palette <- c("#6E8B3D", "#1F77B4", "#2CA02C", "#9467BD",
                  "#556B2F", "#17BECF", "#E377C2", "#7F7F7F")

trajectory_plots <- list()
for (idx in seq_along(all_topics_ordered)) {
  t  <- all_topics_ordered[idx]
  cp <- changepoints[[t]]

  cat(sprintf("  T%d (%s): computing trajectories...\n",
              t, str_trunc(topic_labels[t], 35)))
  traj <- get_word_trajectories(t, n_words = 8, min_years_present = 4)

  if (is.null(traj) || nrow(traj) == 0) {
    trajectory_plots[[idx]] <- ggplot() +
      ggplot::annotate("text", x = 0, y = 0,
               label = paste0("T", t, ": insufficient data"),
               size = 6) +
      theme_void()
    next
  }

  p <- ggplot(traj, aes(x = year, y = prop, color = word)) +
    geom_point(alpha = 0.25, size = 1.2) +
    geom_smooth(method = "loess", se = FALSE, span = 0.55, linewidth = 1.1) +
    scale_color_manual(values = traj_palette[seq_len(n_distinct(traj$word))]) +
    scale_x_continuous(breaks = scales::pretty_breaks(n = 6)) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    labs(
      title    = paste0("T", t, ": ", str_trunc(topic_labels[t], 45)),
      subtitle = if (!is.na(cp$year))
                   paste0("Changepoint: ", cp$year,
                          "   |   JSD = ", sprintf("%.2f", cp$max_div))
                 else "Changepoint: (insufficient data)",
      x = NULL,
      y = "Share of topic vocab",
      color = NULL
    ) +
    theme_minimal(base_size = 10) +
    theme(
      legend.position = "right",
      legend.text     = element_text(size = 9),
      legend.key.size = unit(0.8, "lines"),
      plot.title      = element_text(size = 12, face = "bold"),
      plot.subtitle   = element_text(size = 10, color = "grey35"),
      axis.title.y    = element_text(size = 9),
      panel.grid.minor = element_blank(),
      plot.margin     = margin(8, 12, 8, 12)
    )

  # Overlay the JSD changepoint year as a dashed vertical line
  if (!is.na(cp$year)) {
    p <- p +
      geom_vline(xintercept = cp$year,
                 linetype = "dashed", color = "grey25", linewidth = 0.6) +
      ggplot2::annotate("text", x = cp$year, y = Inf,
               label = paste0(" CP: ", cp$year),
               hjust = 0, vjust = 1.5, size = 3.2, color = "grey25",
               fontface = "italic")
  }

  trajectory_plots[[idx]] <- p
}

# Paginate: 4 plots per page, 2 columns wide
plots_per_page <- 4
n_pages <- ceiling(length(trajectory_plots) / plots_per_page)

for (page in seq_len(n_pages)) {
  start_i <- (page - 1) * plots_per_page + 1
  end_i   <- min(start_i + plots_per_page - 1, length(trajectory_plots))
  batch   <- trajectory_plots[start_i:end_i]

  combined <- wrap_plots(batch, ncol = 2) +
    plot_annotation(
      title    = paste0("Top-Word Trajectories Within Topics — Page ",
                        page, " of ", n_pages),
      subtitle = paste0("Topics ", start_i, "–", end_i,
                        " by prevalence rank. Lines = LOESS-smoothed share ",
                        "of topic vocab per year. Dashed line = JSD changepoint."),
      theme    = theme(plot.title    = element_text(size = 18, face = "bold"),
                       plot.subtitle = element_text(size = 12))
    )

  print(combined)

  ggsave(
    file.path(output_path,
              paste0("word_trajectories_K", chosen_K, "_page", page, ".png")),
    combined, width = 14, height = 20, dpi = 200, limitsize = FALSE
  )
}

cat("\nSaved", n_pages, "PNG pages to:", output_path, "\n")
```



## 37. Topic Diversity & Concentration (Document-Level)

Section 33 measures diversity per *volume*. This section measures it per
*document*: is the typical article about one topic or several?

```{r doc-level-diversity, fig.width=12, fig.height=10}
cat(rep("=", 70), "\n", sep = "")
cat("DOCUMENT-LEVEL TOPIC DIVERSITY\n")
cat(rep("=", 70), "\n\n", sep = "")

# Shannon entropy per document (higher = more diverse)
doc_entropy <- doc_topics %>%
  select(doc_id, starts_with("Topic")) %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "p") %>%
  filter(p > 0) %>%
  group_by(doc_id) %>%
  summarize(entropy = -sum(p * log2(p)), .groups = "drop")

# Gini concentration per document
doc_gini <- doc_topics %>%
  select(doc_id, starts_with("Topic")) %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "p") %>%
  group_by(doc_id) %>%
  summarize(
    max_topic_prop = max(p),
    gini = 1 - sum(p^2),
    .groups = "drop"
  )

# Summary
diversity_summary <- doc_entropy %>%
  left_join(doc_gini, by = "doc_id") %>%
  summarize(
    mean_entropy = mean(entropy),
    sd_entropy = sd(entropy),
    mean_gini = mean(gini),
    mean_max_prop = mean(max_topic_prop),
    pct_strong_exemplar = mean(max_topic_prop >= 0.4) * 100
  )

cat("Diversity Metrics (Relief Society Magazine):\n\n")
cat(sprintf("  Mean Shannon Entropy:     %.2f bits\n", diversity_summary$mean_entropy))
cat(sprintf("  SD Entropy:               %.2f\n", diversity_summary$sd_entropy))
cat(sprintf("  Mean Gini (inv-Herf):     %.3f\n", diversity_summary$mean_gini))
cat(sprintf("  Mean Dominant Topic %%:    %.1f%%\n", diversity_summary$mean_max_prop * 100))
cat(sprintf("  Strong Exemplars (>40%%):  %.1f%% of documents\n\n", diversity_summary$pct_strong_exemplar))

# Entropy distribution
p1 <- ggplot(doc_entropy, aes(x = entropy)) +
  geom_density(fill = "#6E8B3D", alpha = 0.5, linewidth = 0.8, color = "#556B2F") +
  labs(title = "Topic Diversity per Document",
       subtitle = "Higher entropy = article discusses more topics evenly",
       x = "Shannon Entropy (bits)", y = "Density") +
  theme_minimal(base_size = 12)

# Dominant topic concentration
p2 <- ggplot(doc_gini, aes(x = max_topic_prop)) +
  geom_density(fill = "#6E8B3D", alpha = 0.5, linewidth = 0.8, color = "#556B2F") +
  geom_vline(xintercept = 0.4, linetype = "dashed", color = "grey40") +
  ggplot2::annotate("text", x = 0.42, y = 0, label = "Exemplar\nthreshold", size = 3, hjust = 0) +
  labs(title = "Topic Concentration per Document",
       subtitle = "Higher = article dominated by single topic; dashed line = 40% exemplar threshold",
       x = "Dominant Topic Proportion", y = "Density") +
  theme_minimal(base_size = 12) +
  scale_x_continuous(labels = percent_format())

p1 / p2
```

### Effective Number of Topics

```{r effective-topics-rsm, fig.width=10, fig.height=5}
# Publication-level topic distribution
pub_topic_dist <- doc_topics %>%
  summarize(across(starts_with("Topic"), mean)) %>%
  pivot_longer(everything(), names_to = "topic", values_to = "prevalence") %>%
  mutate(
    topic_num = as.integer(str_remove(topic, "Topic")),
    label = str_trunc(topic_labels[topic_num], 25)
  )

# Effective number of topics = exp(entropy of topic distribution)
eff_topics <- pub_topic_dist %>%
  filter(prevalence > 0) %>%
  summarize(eff = exp(-sum(prevalence * log(prevalence)))) %>%
  pull(eff)

cat(sprintf("Effective number of topics: %.1f (of %d)\n\n", eff_topics, chosen_K))

ggplot(pub_topic_dist, aes(x = reorder(label, -prevalence), y = prevalence)) +
  geom_col(fill = "#6E8B3D", alpha = 0.8) +
  labs(title = "Topic Weight Distribution \u2014 Relief Society Magazine",
       subtitle = paste0("Effective topics: ", round(eff_topics, 1), " of ", chosen_K),
       x = NULL, y = "Mean Proportion") +
  theme_minimal(base_size = 10) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8)) +
  scale_y_continuous(labels = percent_format())
```

---

## 38. Topic Prevalence Heatmap Over Time

```{r topic-heatmap-time, fig.width=12, fig.height=7}
# Yearly topic prevalence
yearly_topics_rsm <- doc_topics %>%
  filter(!is.na(year)) %>%
  select(year, starts_with("Topic")) %>%
  group_by(year) %>%
  summarize(across(starts_with("Topic"), mean), .groups = "drop") %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "prevalence") %>%
  mutate(
    topic_num = as.integer(str_remove(topic, "Topic")),
    short_label = paste0("T", topic_num, ": ", str_trunc(topic_labels[topic_num], 20))
  )

ggplot(yearly_topics_rsm, aes(x = year, y = short_label, fill = prevalence)) +
  geom_tile(color = "white", linewidth = 0.3) +
  scale_fill_gradient(low = "white", high = "#556B2F",
                      labels = percent_format()) +
  labs(title = "Topic Prevalence Over Time \u2014 Relief Society Magazine",
       subtitle = "Darker = higher prevalence in that year",
       x = "Year", y = NULL, fill = "Prevalence") +
  theme_minimal(base_size = 11) +
  theme(panel.grid = element_blank(),
        plot.title = element_text(face = "bold", size = 14)) +
  scale_y_discrete(limits = rev) +
  scale_x_continuous(breaks = sort(unique(yearly_topics_rsm$year)))
```

---

## 39. Topic Percentage Change (Early vs Late Era)

How much does each topic's prevalence **shift** from the early period to the
late period?

```{r topic-era-change, fig.width=12, fig.height=8}
cat(rep("=", 70), "\n", sep = "")
cat("PERCENTAGE CHANGE IN TOPICS: EARLY vs LATE ERA\n")
cat(rep("=", 70), "\n\n", sep = "")

# Mean prevalence per topic per era
era_means <- doc_topics_era %>%
  group_by(era) %>%
  summarize(across(starts_with("Topic"), mean), .groups = "drop") %>%
  pivot_longer(-era, names_to = "topic", values_to = "prevalence") %>%
  mutate(topic_num = as.integer(str_remove(topic, "Topic"))) %>%
  pivot_wider(names_from = era, values_from = prevalence)

era_change <- era_means %>%
  mutate(
    label = topic_labels[topic_num],
    early_pct = Early * 100,
    late_pct = Late * 100,
    abs_change = late_pct - early_pct,
    pct_change = ifelse(Early > 0.001,
                        (Late - Early) / Early * 100,
                        NA_real_),
    direction = case_when(
      abs_change > 0.5  ~ "Grew in Late Period",
      abs_change < -0.5 ~ "Declined in Late Period",
      TRUE ~ "Stable"
    )
  ) %>%
  arrange(desc(abs_change))

cat(sprintf("Era split: Early (\u2264%d) vs Late (>%d)\n\n", median_year, median_year))
cat(sprintf("%-35s  %7s  %7s  %8s  %9s\n",
            "Topic", "Early%", "Late%", "Change", "% Change"))
cat(rep("-", 80), "\n", sep = "")
for (i in 1:nrow(era_change)) {
  r <- era_change[i, ]
  pct_str <- ifelse(is.na(r$pct_change), "N/A", sprintf("%+.0f%%", r$pct_change))
  cat(sprintf("%-35s  %5.1f%%  %5.1f%%  %+6.1fpp  %9s\n",
              str_trunc(r$label, 35), r$early_pct, r$late_pct, r$abs_change, pct_str))
}

# Absolute change bar chart
p_abs <- era_change %>%
  mutate(display = paste0("T", topic_num, ": ", str_trunc(label, 28)),
         display = reorder(display, abs_change)) %>%
  ggplot(aes(x = abs_change, y = display, fill = direction)) +
  geom_col(alpha = 0.85) +
  geom_vline(xintercept = 0, linewidth = 1) +
  scale_fill_manual(values = c("Grew in Late Period" = "#6E8B3D",
                                "Declined in Late Period" = "#CD661D",
                                "Stable" = "#94a3b8")) +
  labs(title = paste0("Topic Change: Early (\u2264", median_year,
                      ") vs Late (>", median_year, ") Period"),
       subtitle = "Absolute change in percentage points of topic prevalence",
       x = "Change (percentage points)", y = NULL, fill = NULL) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom", panel.grid.major.y = element_blank())

print(p_abs)
```

```{r topic-era-change-relative, fig.width=12, fig.height=8}
# Relative (%) change bar chart
era_change_filtered <- era_change %>%
  filter(!is.na(pct_change), abs(pct_change) < 500) %>%
  mutate(display = paste0("T", topic_num, ": ", str_trunc(label, 28)),
         display = reorder(display, pct_change))

if (nrow(era_change_filtered) > 0) {
  ggplot(era_change_filtered, aes(x = pct_change, y = display, fill = direction)) +
    geom_col(alpha = 0.85) +
    geom_vline(xintercept = 0, linewidth = 1) +
    scale_fill_manual(values = c("Grew in Late Period" = "#6E8B3D",
                                  "Declined in Late Period" = "#CD661D",
                                  "Stable" = "#94a3b8")) +
    labs(title = "Relative Percentage Change in Topic Prevalence",
         subtitle = paste0("How much did each topic grow or shrink relative to its early-period (\u2264",
                           median_year, ") baseline?"),
         x = "Relative Change (%)", y = NULL, fill = NULL) +
    theme_minimal(base_size = 11) +
    theme(legend.position = "bottom", panel.grid.major.y = element_blank())
}
```

---

## 40. Topic Evolution Summary

```{r evolution-summary, fig.width=10, fig.height=10}
cat(rep("=", 70), "\n", sep = "")
cat("TOPIC EVOLUTION SUMMARY\n")
cat(rep("=", 70), "\n\n", sep = "")

topic_evolution <- era_change %>%
  mutate(
    evolution_type = case_when(
      abs(abs_change) <= 0.5 ~ "Stable",
      abs_change > 0.5  ~ "Growing",
      abs_change < -0.5 ~ "Declining"
    ),
    evolution_type = factor(evolution_type,
                            levels = c("Stable", "Growing", "Declining"))
  )

cat("TOPIC EVOLUTION CLASSIFICATION:\n\n")
for (etype in c("Stable", "Growing", "Declining")) {
  cat(toupper(etype), ":\n")
  subset_ev <- topic_evolution %>% filter(evolution_type == etype)
  if (nrow(subset_ev) > 0) {
    for (i in 1:nrow(subset_ev)) {
      r <- subset_ev[i, ]
      cat(sprintf("  T%d: %s (Early: %.1f%%, Late: %.1f%%, %+.1fpp)\n",
                  r$topic_num, r$label, r$early_pct, r$late_pct, r$abs_change))
    }
  } else {
    cat("  (none)\n")
  }
  cat("\n")
}

# Scatter plot: early vs late prevalence
ggplot(topic_evolution, aes(x = early_pct, y = late_pct, color = evolution_type)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed",
              color = "grey70", linewidth = 1) +
  geom_point(size = 5, alpha = 0.8) +
  geom_text_repel(aes(label = paste0("T", topic_num, ": ", str_trunc(label, 25))),
                  size = 3, max.overlaps = 20, show.legend = FALSE) +
  scale_color_manual(values = c(
    "Stable" = "#6495ED",
    "Growing" = "#6E8B3D",
    "Declining" = "#CD661D"
  )) +
  labs(title = "Topic Evolution: Early vs Late Period",
       subtitle = paste0("Diagonal = no change | Above = grew in late period (",
                         median_year + 1, "-", max(meta$year, na.rm = TRUE),
                         ") | Below = declined"),
       x = paste0("Early Period Mean % (\u2264", median_year, ")"),
       y = paste0("Late Period Mean % (>", median_year, ")"),
       color = "Evolution Type") +
  theme_minimal(base_size = 13) +
  theme(legend.position = "bottom",
        plot.title = element_text(face = "bold", size = 16)) +
  coord_fixed()
```

---

## 41. Representative Passages

```{r representative-passages}
cat("REPRESENTATIVE PASSAGES PER TOPIC\n")
cat(rep("=", 70), "\n\n", sep = "")

for (t in 1:chosen_K) {
  cat("TOPIC", t, ":", topic_labels[t], "\n")
  cat(rep("-", 60), "\n", sep = "")

  top_docs <- topic_article_link %>% filter(topic_num == t) %>% head(3)
  topic_words <- tolower(all_top_words$frex[t, 1:15])

  for (j in 1:nrow(top_docs)) {
    fname <- top_docs$filename[j]
    title_str <- ifelse(is.na(top_docs$Title[j]), fname, top_docs$Title[j])
    match_file <- list.files(input_path, pattern = fixed(fname),
                             recursive = TRUE, full.names = TRUE)
    if (length(match_file) == 0) next
    full_text <- read_file(match_file[1])
    sentences <- str_split(full_text, "(?<=[.!?])\\s+")[[1]]
    sentences <- sentences[nchar(sentences) > 40 & nchar(sentences) < 500]
    if (length(sentences) == 0) next
    scores <- sapply(sentences, function(s) {
      words <- tolower(str_split(s, "\\s+")[[1]])
      sum(words %in% topic_words) / max(length(words), 1)
    })
    best_sentence <- str_squish(sentences[order(scores, decreasing = TRUE)[1]])
    cat(sprintf("\n  [%s] (%.1f%% Topic %d)\n", title_str,
                top_docs$proportion[j] * 100, t))
    cat("  \"", str_trunc(best_sentence, 300), "\"\n", sep = "")
  }
  cat("\n\n")
}
```

---

## 42. Export Results

```{r export-results}
# 1. Full topic-article link
write_csv(topic_article_link %>% mutate(proportion_pct = round(proportion * 100, 2)),
          file.path(output_path, "topic_article_full_link.csv"))

# 2. Top exemplars
write_csv(topic_article_link %>% group_by(topic_num, topic_label) %>%
  slice_max(proportion, n = 25) %>% ungroup() %>%
  mutate(proportion_pct = round(proportion * 100, 2)),
  file.path(output_path, "topic_exemplar_articles.csv"))

# 3. Topic summary
write_csv(tibble(topic_num = 1:chosen_K, label = topic_labels,
  prevalence_pct = round(topic_props_mean * 100, 2),
  frex_words = apply(all_top_words$frex, 1, function(x) paste(x, collapse = ", ")),
  prob_words = apply(all_top_words$prob, 1, function(x) paste(x, collapse = ", "))),
  file.path(output_path, "topic_summary.csv"))

# 4. Dominant topic per article
write_csv(dominant_topics, file.path(output_path, "dominant_topic_per_article.csv"))

# 5. Strong exemplars
write_csv(dominant_topics %>% filter(strong_exemplar),
          file.path(output_path, "strong_exemplars.csv"))

cat("Exported to:", output_path, "\n")
cat("  - topic_article_full_link.csv\n  - topic_exemplar_articles.csv\n")
cat("  - topic_summary.csv\n  - dominant_topic_per_article.csv\n  - strong_exemplars.csv\n")
```

---

## 43. Read a Specific Article

```{r read-article-function}
read_article <- function(fname, input_dir = input_path) {
  match <- list.files(input_dir, pattern = fixed(fname), recursive = TRUE, full.names = TRUE)
  if (length(match) == 0) { cat("File not found:", fname, "\n"); return(invisible(NULL)) }
  txt <- read_file(match[1])
  cat(rep("=", 70), "\n", sep = ""); cat("File:", fname, "\n")
  cat(rep("=", 70), "\n\n", sep = ""); cat(substr(txt, 1, 2000), "\n\n...")
  return(invisible(txt))
}

top1 <- topic_article_link %>% filter(topic_num == 1) %>% head(1)
read_article(top1$filename)
```

---

## 43b. Advanced-Analysis Hand-off (advanced_* files)

Writes the four `advanced_*_K{K}` files the advanced text-analysis pipeline
(Python embed / BERTopic / diachronic + the report) consumes — **directly**, so
no separate `generate_handoff.R` bridge step is needed. Same schema and logic as
that bridge, run inline against the in-memory objects. Lands in
`output_linked/<scenario>/` because `output_path` is scenario-scoped.

```{r advanced-handoff}
# Align each modeled document back to its original + cleaned text.
.modeled_idx   <- match(meta$doc_id, processed_texts$doc_id)
.modeled_raw   <- processed_texts$text[.modeled_idx]
.modeled_clean <- processed_texts$text_final[.modeled_idx]

stopifnot(nrow(meta) == nrow(stm_model$theta),
          length(.modeled_raw) == nrow(meta),
          !anyNA(.modeled_idx))

# Defensive column access (meta schema can vary slightly across runs).
.col <- function(df, nm) if (nm %in% names(df)) df[[nm]] else NA

adv_docs <- tibble::tibble(
  row_index    = seq_len(nrow(meta)),
  doc_id       = meta$doc_id,
  filename     = .col(meta, "filename"),
  title        = .col(meta, "Title"),
  author       = .col(meta, "Author"),
  article_type = .col(meta, "Article_Type"),
  volume_num   = .col(meta, "volume_num"),
  year         = .col(meta, "year"),
  issue        = .col(meta, "issue"),
  n_words      = stringr::str_count(.modeled_raw, "\\S+"),
  text         = .modeled_raw
)

theta_df <- as.data.frame(stm_model$theta)
colnames(theta_df) <- paste0("Topic", seq_len(ncol(theta_df)))
theta_df <- dplyr::bind_cols(row_index = seq_len(nrow(theta_df)), theta_df)

.tw <- labelTopics(stm_model, n = 12)
topics_df <- tibble::tibble(
  topic_num = seq_len(chosen_K),
  label     = if (!is.null(topic_labels) && length(topic_labels) == chosen_K)
                topic_labels else paste0("Topic ", seq_len(chosen_K)),
  frex      = apply(.tw$frex, 1, paste, collapse = ", "),
  prob      = apply(.tw$prob, 1, paste, collapse = ", ")
)

.ksfx <- paste0("_K", chosen_K)
saveRDS(list(stm_model = stm_model, meta = meta, topic_labels = topic_labels,
             modeled_raw = .modeled_raw, modeled_clean = .modeled_clean,
             fit_date = Sys.time()),
        file.path(output_path, paste0("advanced_input", .ksfx, ".rds")))
readr::write_csv(adv_docs,  file.path(output_path, paste0("advanced_docs",   .ksfx, ".csv")))
readr::write_csv(theta_df,  file.path(output_path, paste0("advanced_theta",  .ksfx, ".csv")))
readr::write_csv(topics_df, file.path(output_path, paste0("advanced_topics", .ksfx, ".csv")))

cat("Advanced hand-off written to:", output_path, "\n")
cat("  Docs:", nrow(adv_docs), "| Topics:", chosen_K,
    "| Year range:", paste(range(adv_docs$year, na.rm = TRUE), collapse = "-"), "\n")
```

---

## 44. Save Session

```{r save-session}
save(stm_model, docs, vocab, meta, raw_texts, processed_texts,
     all_stopwords, topic_labels, topic_article_link,
     dominant_topics, inventory_subset,
     file = file.path(output_path, paste0("topic_linker_session_K", chosen_K, ".RData")))

cat("Session saved. Reload with:\n")
cat('  load("', file.path(output_path, paste0("topic_linker_session_K", chosen_K, ".RData")), '")\n', sep = "")
```

---

```{r session-info}
sessionInfo()
```
