---
title: "Relief Society Magazine - Universal Article Extractor"
output:
  html_notebook:
    toc: true
    toc_float: true
---

# Configuration

Set input/output directories and which volumes to process.

```{r setup, message=FALSE}
library(stringr)
library(readr)

INPUT_DIR <- "C:/Users/birch/OneDrive - George Mason University - O365 Production/Dissertation/textanalysis/Articleextractionrfiles/input"
OUTPUT_DIR <- "C:/Users/birch/OneDrive - George Mason University - O365 Production/Dissertation/textanalysis/Articleextractionrfiles/output"

if (!dir.exists(OUTPUT_DIR)) dir.create(OUTPUT_DIR, recursive = TRUE)

# Set to specific volume numbers to process, e.g. c(9, 10), or NULL for all
PROCESS_VOLUMES <- c(9, 10)
```

# Known Article Categories

Recurring section headers that appear across issues. Each has body-text patterns
and a search region hint (where in the issue the section typically appears).

```{r known-categories}
KNOWN_CATEGORIES <- list(
  list(name = "Editorial",
       body_patterns = c("EDITORIAL[S]?\\b", "EDITORIAL THOUGHTS"),
       search_region = "back_half"),
  list(name = "Guide Lessons",
       body_patterns = c("GUIDE LESSONS?\\b", "LESSON OUTLINES?"),
       search_region = "back_third"),
  list(name = "Current Topics",
       body_patterns = c("CURRENT TOPICS\\b", "CURRENT EVENTS\\b"),
       search_region = "any"),
  list(name = "Notes from the Field",
       body_patterns = c("NOTES FROM THE FIELD", "Notes from the Field"),
       search_region = "any"),
  list(name = "Genealogy",
       body_patterns = c("\\bGENEALOGY\\b", "GENEALOGICAL NOTES"),
       search_region = "any"),
  list(name = "Home Science",
       body_patterns = c("HOME SCIENCE DEPARTMENT", "HOME SCIENCE\\b",
                         "HOME GARDENING", "LESSONS? IN HOME GARDENING"),
       search_region = "any"),
  list(name = "Relief Society Reports",
       body_patterns = c("RELIEF SOCIETY REPORTS?\\b"),
       search_region = "any"),
  list(name = "Mothers in Israel",
       body_patterns = c("MOTHERS? IN ISRAEL"),
       search_region = "front_half"),
  list(name = "Miscellaneous Notes",
       body_patterns = c("MISCELLANEOUS NOTES\\b"),
       search_region = "any"),
  list(name = "Plain Gossip",
       body_patterns = c("PLAIN GOSSIP\\b", "Plain Gossip\\b"),
       search_region = "any"),
  list(name = "Home Ethics",
       body_patterns = c("HOME ETHICS\\b"),
       search_region = "any"),
  list(name = "Literature",
       body_patterns = c("\\bLITERATURE\\b"),
       search_region = "any"),
  list(name = "Art and Architecture",
       body_patterns = c("ART AND ARCHITECTURE"),
       search_region = "any"),
  list(name = "Home Economics",
       body_patterns = c("HOME ECONOMICS? DEPARTMENT", "HOME ECONOMICS\\b"),
       search_region = "any"),
  list(name = "Patriotic Department",
       body_patterns = c("PATRIOTIC DEPARTMENT"),
       search_region = "any"),
  list(name = "Home Entertainments",
       body_patterns = c("HOME ENTERTAINMENTS?\\b", "HOME EVENING ENTERTAINMENT"),
       search_region = "any"),
  list(name = "The General Procession",
       body_patterns = c("THE GENERAL PROCESSION"),
       search_region = "any")
)
```

# Helper Functions

## File Metadata Extraction

Parse volume, issue number, month, and year from the filename.

```{r metadata}
get_metadata <- function(filename) {
  vol <- str_extract(filename, "(?<=Vol)\\d+")
  raw_year <- str_extract(filename, "\\d{4}")

  # Correct known year typos based on volume number
  # Vol 1=1914, Vol 2=1915, ..., Vol 9=1922, Vol 10=1923, etc.
  VOLUME_YEAR_MAP <- c(
    "1"="1914", "2"="1915", "3"="1916", "4"="1917", "5"="1918",
    "6"="1919", "7"="1920", "8"="1921", "9"="1922", "10"="1923",
    "11"="1924", "12"="1925", "13"="1926", "14"="1927", "15"="1928",
    "16"="1929", "17"="1930", "18"="1931", "19"="1932", "20"="1933"
  )
  expected_year <- VOLUME_YEAR_MAP[vol]
  year <- raw_year
  if (!is.null(expected_year) && !is.na(expected_year) && raw_year != expected_year) {
    cat(sprintf("  NOTE: Filename year %s corrected to %s (Vol %s)\n",
                raw_year, expected_year, vol))
    year <- expected_year
  }

  list(
    volume = vol,
    issue  = str_extract(filename, "(?<=No)\\d+"),
    month  = str_extract(filename, "(January|February|March|April|May|June|July|August|September|October|November|December)"),
    year   = year
  )
}
```

## Safe File Reading

Handle UTF-8 and Windows-1252 encoded files gracefully.

```{r read-safe}
read_file_safe <- function(filepath) {
  text <- tryCatch(
    read_file(filepath, locale = locale(encoding = "UTF-8")),
    error = function(e) {
      read_file(filepath, locale = locale(encoding = "windows-1252"))
    }
  )
  iconv(text, from = "UTF-8", to = "UTF-8", sub = "")
}
```

## Text Normalization

Some OCR files have very few newlines (text runs together). Insert newlines
at key structural markers to make parsing possible.

```{r normalize}
normalize_text <- function(text) {
  # Remove LLM-artifact lines (from AI-assisted OCR correction)
  text <- str_replace_all(text,
    "Here is the corrected OCR transcription[^\n]*\n?", "")

  # Replace Markdown bold markers **text** with plain text
  text <- str_replace_all(text, "\\*\\*([^*]+)\\*\\*", "\\1")

  newline_count <- str_count(text, "\n")
  chars_per_newline <- nchar(text) / max(1, newline_count)

  if (chars_per_newline > 5000) {
    cat(sprintf("  Low newlines detected (%d in %d chars). Normalizing...\n",
                newline_count, nchar(text)))

    # --- Phase 1: Major structural markers ---
    text <- str_replace(text,
      "(CONTENTS\\s+(?:JANUARY|FEBRUARY|MARCH|APRIL|MAY|JUNE|JULY|AUGUST|SEPTEMBER|OCTOBER|NOVEMBER|DECEMBER))",
      "\n\\1")
    text <- str_replace_all(text, "(ADVERTISERS)", "\n\\1")
    text <- str_replace_all(text,
      "(THE Relief Society Magazine Vol)", "\n\\1")
    text <- str_replace_all(text,
      "(Z\\.\\s*C\\.\\s*M\\.\\s*[IL1])", "\n\\1")

    # --- Phase 2: Section headers (for heavily collapsed files) ---
    # Insert newline before Vol. X MONTH, YEAR No. N header
    text <- str_replace_all(text,
      "(Vol\\.\\s+[IVX0-9]+\\.?\\s+(?:JANUARY|FEBRUARY|MARCH|APRIL|MAY|JUNE|JULY|AUGUST|SEPTEMBER|OCTOBER|NOVEMBER|DECEMBER),?\\s+\\d{4})",
      "\n\\1")

    # Insert newline before PUBLICATION INFORMATION
    text <- str_replace_all(text,
      "(PUBLICATION INFORMATION)", "\n\\1")

    # Insert newline before "Organ of the Relief Society"
    text <- str_replace_all(text,
      "(Organ of the Relief Society)", "\n\\1")

    # Insert newline before "Entered as second-class"
    text <- str_replace_all(text,
      "(Entered as second-class)", "\n\\1")

    # Insert newline before "Mention Relief Society Magazine"
    text <- str_replace_all(text,
      "(Mention Relief Society Magazine)", "\n\\1")

    # --- Phase 3: CONTENTS entry separation ---
    # In collapsed CONTENTS: break after page numbers before next title
    # Pattern: digit(s) + space + uppercase letter (new entry)
    text <- str_replace_all(text,
      "(\\d{1,4})\\s+((?:Frontispiece|[A-Z][a-z]{2,}))", "\\1\n\\2")

    # --- Phase 4: Article body markers ---
    # Insert newline before "By Author Name" patterns (article starts)
    text <- str_replace_all(text,
      "([.!?])\\s+((?:By|BY)\\s+[A-Z][a-z]+\\s+[A-Z])", "\\1\n\\2")

    # Insert newline before known section headers
    text <- str_replace_all(text,
      "([.!?])\\s+((?:EDITORIAL|Editorial|GUIDE LESSONS?|Notes [Ff]rom the Field|IN MEMORIAM|THE GENERAL BOARD))",
      "\\1\n\\2")

    # Insert newline before "Notes From the Field"
    text <- str_replace_all(text,
      "([.!?])\\s+(Notes\\s+[Ff]rom\\s+the\\s+Field)", "\\1\n\\2")

    # Insert newline before running page headers: "TITLE IN CAPS. 123" or "123 TITLE IN CAPS."
    text <- str_replace_all(text,
      "([.!?])\\s+(\\d{2,3}\\s+[A-Z][A-Z\\s]{3,}\\.)", "\\1\n\\2")
    text <- str_replace_all(text,
      "([.!?])\\s+([A-Z][A-Z\\s',]{5,}\\.\\s+\\d{2,3})", "\\1\n\\2")

    # --- Phase 5: Aggressive normalization for truly collapsed files (0 newlines) ---
    post_newlines <- str_count(text, "\n")
    if (post_newlines < 50) {
      cat(sprintf("  Still very few newlines (%d). Applying aggressive normalization...\n",
                  post_newlines))

      # Break before ALL CAPS titles (3+ words, surrounded by lowercase)
      # Pattern: lowercase/punctuation then 3+ ALL CAPS words then lowercase
      text <- str_replace_all(text,
        "([a-z.!?\"'])\\s+((?:[A-Z][A-Z']{2,}\\s+){2,}[A-Z][A-Z']{2,})\\s+([A-Z][a-z])",
        "\\1\n\\2\n\\3")

      # Break before "Title. By Author" patterns even without sentence end
      text <- str_replace_all(text,
        "([a-z.!?\"])\\s+([A-Z][a-z]+(?:\\s+[A-Z][a-z]+){1,5}\\.?\\s+(?:By|BY)\\s+[A-Z][a-z]+)",
        "\\1\n\\2")

      # Break before page number + ALL CAPS running header: "389 RELIEF SOCIETY MAGAZINE"
      text <- str_replace_all(text,
        "([a-z.!?\"])\\s+(\\d{2,3}\\s+[A-Z][A-Z ]{5,})", "\\1\n\\2")

      # Break before ALL CAPS running header + page number: "RELIEF SOCIETY MAGAZINE 389"
      text <- str_replace_all(text,
        "([a-z.!?\"])\\s+([A-Z][A-Z ]{5,}\\s+\\d{2,3})", "\\1\n\\2")

      # Break at transitions from sentence end to new capitalized paragraph
      text <- str_replace_all(text,
        "([.!?])\\s{2,}([A-Z][a-z])", "\\1\n\\2")

      # Break before "Of Interest to Women"
      text <- str_replace_all(text,
        "([.!?\"])\\s+(Of Interest to Women)", "\\1\n\\2")

      # Break before "Items About Women"
      text <- str_replace_all(text,
        "([.!?\"])\\s+(ITEMS ABOUT WOMEN)", "\\1\n\\2")

      # Break before "THE GENERAL B" (General Board)
      text <- str_replace_all(text,
        "([.!?\"])\\s+(THE GENERAL B(?:OARD|UA))", "\\1\n\\2")

      cat(sprintf("  Post-aggressive normalization: %d newlines\n",
                  str_count(text, "\n")))
    }

    cat(sprintf("  Post-normalization: %d newlines\n", str_count(text, "\n")))
  }
  return(text)
}
```

## Filename Sanitization

```{r safe-filename}
safe_filename <- function(title, max_len = 60) {
  clean <- str_replace_all(title, '[<>:"/\\\\|?*]', '')
  clean <- str_replace_all(clean, '\\s+', '_')
  clean <- str_replace_all(clean, '_+', '_')
  clean <- str_replace(clean, '^_|_$', '')
  if (nchar(clean) > max_len) clean <- str_sub(clean, 1, max_len)
  if (nchar(clean) == 0) clean <- "untitled"
  return(clean)
}
```

## Significant Word Extraction

Get meaningful words from a title (filtering out stop words) for fuzzy matching.

```{r significant-words}
get_significant_words <- function(title) {
  stop_words <- c("the", "a", "an", "of", "in", "on", "at", "to", "for",
                  "and", "or", "but", "by", "its", "is", "are", "was",
                  "were", "be", "been", "our", "her", "his", "my", "we",
                  "it", "as", "with", "from", "that", "this", "not", "no",
                  "out", "new", "all", "how", "what", "who", "when",
                  "where", "why", "can", "may", "will", "shall", "has",
                  "had", "have", "does", "did", "do", "about", "into")
  words <- str_split(title, "\\s+")[[1]]
  words <- words[nchar(words) > 2]
  words <- words[!tolower(words) %in% stop_words]
  words <- str_replace(words, "[?.!,;:]+$", "")
  words <- words[nchar(words) > 0]
  return(words)
}
```

## Article Classification

Classify an article title into a category based on keyword patterns.

```{r classify}
classify_article <- function(title) {
  t <- tolower(title)
  if (str_detect(t, "^editorial"))                return("Editorial")
  if (str_detect(t, "guide lesson"))              return("Guide_Lessons")
  if (str_detect(t, "current (topic|event)"))     return("Current_Topics")
  if (str_detect(t, "notes from the field"))      return("Notes_from_Field")
  if (str_detect(t, "genealog"))                  return("Genealogy")
  if (str_detect(t, "home (science|gardening)"))  return("Home_Science")
  if (str_detect(t, "mothers?.in.israel"))        return("Mothers_in_Israel")
  if (str_detect(t, "plain gossip"))              return("Plain_Gossip")
  if (str_detect(t, "home ethics"))               return("Home_Ethics")
  if (str_detect(t, "miscellaneous note"))        return("Misc_Notes")
  if (str_detect(t, "prince of ur"))              return("Prince_of_Ur")
  if (str_detect(t, "literature"))                return("Literature")
  if (str_detect(t, "art and arch"))              return("Art_Architecture")
  if (str_detect(t, "home economics"))            return("Home_Economics")
  if (str_detect(t, "patriotic dep"))             return("Patriotic_Dept")
  if (str_detect(t, "home entertain"))            return("Home_Entertainments")
  if (str_detect(t, "relief society report"))     return("RS_Reports")
  if (str_detect(t, "general procession"))        return("General_Procession")
  if (str_detect(t, "frontispiece"))              return("Frontispiece")
  if (str_detect(t, "instructions"))              return("Instructions")
  if (str_detect(t, "recipes"))                   return("Recipes")
  if (str_detect(t, "poem|verse|stanza"))         return("Poetry")
  if (str_detect(t, "interest to women"))         return("Of_Interest")
  if (str_detect(t, "convention|conference"))      return("Conventions")
  return("Article")
}
```

# Contents Section Parser

The CONTENTS section lists article titles with page numbers. It comes in two
formats: line-based (one entry per line) and inline (all entries on one long line).

## Line-Based Parser

```{r parse-linebased}
parse_contents_linebased <- function(lines) {
  articles <- data.frame(title = character(), page = integer(),
                         stringsAsFactors = FALSE)
  pending_title <- ""

  for (line in lines) {
    line <- str_trim(line)
    if (nchar(line) < 3) next
    if (str_detect(line, "(?i)^CONTENTS?\\b")) next
    if (str_detect(line, "(?i)^ADVERTISERS?\\b")) next
    if (str_detect(line, "(?i)^ADVERTISEMENT\\b")) next
    if (str_detect(line, "(?i)^Page$")) next
    if (str_detect(line, "(?i)^PUBLICATION INFORMATION")) next
    if (str_detect(line, "(?i)corrected|transcription|formatted|vertical list")) next

    # Check for multiple entries on one line: "Editorial 159 Guide Lessons 160"
    multi_matches <- str_match_all(line,
      "([A-Za-z][A-Za-z ,'.:\\-\u2014\u2013]+?)\\s+(\\d{1,4})(?=\\s+[A-Z]|\\s*$)")[[1]]
    if (nrow(multi_matches) >= 2) {
      for (mi in 1:nrow(multi_matches)) {
        title <- str_trim(multi_matches[mi, 2])
        page_num <- as.integer(multi_matches[mi, 3])
        title <- str_replace_all(title, "\\.{2,}", " ")
        title <- str_trim(title)
        if (nchar(title) >= 2 && !is.na(page_num) &&
            page_num >= 1 && page_num <= 2000) {
          if (nchar(pending_title) > 0) {
            title <- paste(pending_title, title)
            pending_title <- ""
          }
          articles <- rbind(articles, data.frame(title = title, page = page_num,
                                                 stringsAsFactors = FALSE))
        }
      }
      pending_title <- ""
      next
    }

    page_match <- str_match(line, "\\s+(\\d{1,4})\\s*$")
    if (is.na(page_match[1, 1])) {
      clean_line <- str_replace_all(line, "\\.{2,}", " ")
      clean_line <- str_trim(clean_line)
      if (nchar(clean_line) < 2 || str_detect(clean_line, "^\\d+$")) next

      if (str_detect(clean_line, "(?i)Frontispiece")) {
        if (nchar(pending_title) > 0) {
          clean_line <- paste(pending_title, clean_line)
          pending_title <- ""
        }
        articles <- rbind(articles, data.frame(title = clean_line, page = 0L,
                                               stringsAsFactors = FALSE))
        next
      }
      pending_title <- clean_line
      next
    }

    page_num <- as.integer(page_match[1, 2])
    if (is.na(page_num) || page_num < 1 || page_num > 2000) next

    title <- str_trim(str_replace(line, "\\s+\\d{1,4}\\s*$", ""))
    title <- str_replace_all(title, "\\.{2,}", " ")

    # OCR garbage cleaner
    title <- str_replace_all(title, "[\u00A9\u00AB\u00BB\u00B0\u00AE]+", " ")
    title <- str_replace_all(title, "[\\d\\.\\-]{3,}", " ")
    title <- str_replace(title, "\\s+(?:[a-z]{1,6}\\s+){2,}[a-z]{1,6}\\s*$", "")
    title <- str_replace(title, "^\\s*(?:[a-z]{1,6}\\s+){2,}[a-z]{1,6}\\s+", "")
    title <- str_replace(title, "\\s+[A-Z]{1,3}\\s*$", "")
    title <- str_replace_all(title, "[a-z]{3,}([A-Z][a-z])", " \\1")
    title <- str_replace_all(title, "\\s{2,}", " ")
    title <- str_trim(title)

    if (nchar(title) < 2) next
    if (str_detect(title, "^\\d+$")) next

    if (nchar(pending_title) > 0) {
      title <- paste(pending_title, title)
      pending_title <- ""
    }

    articles <- rbind(articles, data.frame(title = title, page = page_num,
                                           stringsAsFactors = FALSE))
  }
  return(articles)
}
```

## Inline Parser

For CONTENTS sections where everything is on one or two lines.

```{r parse-inline}
parse_contents_inline <- function(text) {
  articles <- data.frame(title = character(), page = integer(),
                         stringsAsFactors = FALSE)
  text <- str_replace_all(text, "\\s+", " ")

  page_locs <- str_locate_all(text, "[,\\s]\\s*(\\d{1,4})(?:\\s|$)")[[1]]
  if (nrow(page_locs) == 0) return(articles)

  for (i in 1:nrow(page_locs)) {
    page_start <- page_locs[i, 1]
    page_end   <- page_locs[i, 2]
    page_str   <- str_trim(str_sub(text, page_start, page_end))
    page_str   <- str_replace(page_str, "^,\\s*", "")
    page_num   <- as.integer(page_str)

    if (is.na(page_num) || page_num < 1 || page_num > 2000) next

    if (i == 1) {
      entry_start <- 1
    } else {
      entry_start <- page_locs[i - 1, 2] + 1
    }

    entry_text <- str_trim(str_sub(text, entry_start, page_start - 1))
    entry_text <- str_replace_all(entry_text, "\\.{2,}", " ")
    entry_text <- str_replace_all(entry_text, "\\s*[\u2014\u2013]\\s*", " ")
    entry_text <- str_trim(entry_text)

    if (nchar(entry_text) < 2) next
    if (str_detect(entry_text, "(?i)^CONTENTS")) next
    if (str_detect(entry_text, "^\\d{4}$")) next

    if (str_detect(entry_text, "(?i)Frontispiece")) {
      parts <- str_split(entry_text, "(?i)Frontispiece")[[1]]
      if (nchar(str_trim(parts[1])) >= 3) {
        articles <- rbind(articles, data.frame(
          title = paste(str_trim(parts[1]), "Frontispiece"),
          page = page_num, stringsAsFactors = FALSE))
      }
      if (length(parts) > 1 && nchar(str_trim(parts[2])) >= 3) {
        entry_text <- str_trim(parts[2])
      } else {
        next
      }
    }

    articles <- rbind(articles, data.frame(
      title = entry_text, page = page_num, stringsAsFactors = FALSE))
  }
  return(articles)
}
```

## Main Contents Parser

Dispatches to line-based or inline parser as appropriate.

```{r parse-contents}
parse_contents_section <- function(contents_text) {
  contents_text <- str_replace_all(contents_text, "\r\n", "\n")
  contents_text <- str_replace_all(contents_text, "\r", "\n")

  # If CONTENTS has very few newlines, inject them
  if (str_count(contents_text, "\n") < 5) {
    contents_text <- str_replace(contents_text,
      "(CONTENTS\\s+[A-Z]+,?\\s+\\d{4})", "\\1\n")
    contents_text <- str_replace_all(contents_text,
      "(\\d{1,4})\\s+((?:\"|\\u201C)?[A-Z])", "\\1\n\\2")
    contents_text <- str_replace_all(contents_text,
      "\\s+(ADVERTISERS)", "\n\\1")
  }

  articles <- data.frame(title = character(), page = integer(),
                         stringsAsFactors = FALSE)
  lines <- str_split(contents_text, "\n")[[1]]
  lines <- lines[nchar(str_trim(lines)) > 0]
  lines_with_pagenum <- sum(str_detect(lines, "\\d+\\s*$"))

  if (lines_with_pagenum >= 3 && length(lines) > 3) {
    articles <- parse_contents_linebased(lines)
  } else {
    articles <- parse_contents_inline(contents_text)
  }

  if (nrow(articles) > 0) {
    articles <- articles[!duplicated(articles$title), ]
    articles <- articles[order(articles$page), ]
    articles$category <- sapply(articles$title, classify_article)
  }
  return(articles)
}
```

# Title Finding Engine (Multi-Strategy)

Five progressively fuzzier strategies to locate an article title in the body text.

```{r find-title}
find_title_in_text <- function(text, title, search_start, search_end) {
  if (search_start >= search_end) return(NULL)
  search_text <- str_sub(text, search_start, search_end)

  # Strip category prefixes like "Music:" or "Editorial," before searching
  search_title <- title
  if (str_detect(search_title, "^(Music|Art|Poetry|Fiction|Drama|Editorial):\\s+")) {
    search_title <- str_replace(search_title, "^(Music|Art|Poetry|Fiction|Drama|Editorial):\\s+", "")
  }
  if (str_detect(search_title, "^Editorial,\\s+")) {
    search_title <- str_replace(search_title, "^Editorial,\\s+", "")
  }

  # --- Strategy 1: Exact match ---
  escaped_title <- str_replace_all(search_title, "([.?*+^$\\[\\]\\\\(){}|])", "\\\\\\1")
  exact_match <- tryCatch(
    str_locate(search_text, regex(escaped_title, ignore_case = TRUE)),
    error = function(e) matrix(NA, 1, 2))
  if (!is.na(exact_match[1, 1])) return(search_start + exact_match[1, 1] - 1)

  # --- Strategy 1b: Hyphen/punctuation tolerant ---
  hyphen_title <- str_replace_all(escaped_title, "\\\\-|\\-", "[\\\\s\\\\-]?")
  hyphen_match <- tryCatch(
    str_locate(search_text, regex(hyphen_title, ignore_case = TRUE)),
    error = function(e) matrix(NA, 1, 2))
  if (!is.na(hyphen_match[1, 1])) return(search_start + hyphen_match[1, 1] - 1)

  # --- Strategy 2: Whitespace-flexible ---
  collapsed_title <- str_replace_all(escaped_title, "\\\\s\\+|\\s+", "\\\\s+")
  collapsed_match <- tryCatch(
    str_locate(search_text, regex(collapsed_title, ignore_case = TRUE)),
    error = function(e) matrix(NA, 1, 2))
  if (!is.na(collapsed_match[1, 1])) return(search_start + collapsed_match[1, 1] - 1)

  # --- Strategy 3: Shortened title (first N words) with validation ---
  title_words <- str_split(search_title, "\\s+")[[1]]
  if (length(title_words) >= 3) {
    sig_for_validation <- get_significant_words(search_title)
    for (n_words in c(min(length(title_words), 5), 3, 2)) {
      short_title <- paste(title_words[1:n_words], collapse = " ")
      escaped_short <- str_replace_all(short_title,
        "([.?*+^$\\[\\]\\\\(){}|])", "\\\\\\1")
      short_match <- tryCatch(
        str_locate(search_text, regex(escaped_short, ignore_case = TRUE)),
        error = function(e) matrix(NA, 1, 2))
      if (!is.na(short_match[1, 1])) {
        if (length(sig_for_validation) > 0 && n_words < length(title_words)) {
          vicinity_start <- max(1, short_match[1, 1] - 50)
          vicinity_end <- min(nchar(search_text), short_match[1, 2] + 500)
          vicinity <- str_sub(search_text, vicinity_start, vicinity_end)
          sig_found <- any(sapply(sig_for_validation, function(w) {
            ew <- str_replace_all(w, "([.?*+^$\\[\\]\\\\(){}|-])", "\\\\\\1")
            str_detect(vicinity, regex(paste0("\\b", ew, "\\b"), ignore_case = TRUE))
          }))
          if (!sig_found) next
        }
        return(search_start + short_match[1, 1] - 1)
      }
    }
  }

  # --- Strategy 4: Significant word proximity clustering ---
  sig_words <- get_significant_words(search_title)
  if (length(sig_words) == 0) return(NULL)

  if (length(sig_words) == 1) {
    word <- sig_words[1]
    escaped <- str_replace_all(word, "([.?*+^$\\[\\]\\\\(){}|-])", "\\\\\\1")
    pattern <- paste0("\\b", escaped, "\\b")
    matches <- str_locate_all(search_text, regex(pattern, ignore_case = TRUE))[[1]]
    if (nrow(matches) > 0) return(search_start + matches[1, 1] - 1)
    return(NULL)
  }

  word_positions <- list()
  for (word in sig_words) {
    escaped <- str_replace_all(word, "([.?*+^$\\[\\]\\\\(){}|-])", "\\\\\\1")
    pattern <- paste0("\\b", escaped, "\\b")
    matches <- str_locate_all(search_text, regex(pattern, ignore_case = TRUE))[[1]]
    if (nrow(matches) > 0) {
      word_positions[[word]] <- matches[, 1]
    } else if (nchar(word) >= 4) {
      stem <- str_sub(word, 1, max(3, nchar(word) - 2))
      escaped_stem <- str_replace_all(stem, "([.?*+^$\\[\\]\\\\(){}|-])", "\\\\\\1")
      stem_pattern <- paste0("\\b", escaped_stem, "[a-z]{0,4}\\b")
      stem_matches <- tryCatch(
        str_locate_all(search_text, regex(stem_pattern, ignore_case = TRUE))[[1]],
        error = function(e) matrix(nrow = 0, ncol = 2))
      if (nrow(stem_matches) > 0) {
        word_positions[[word]] <- stem_matches[, 1]
      } else {
        clean_word <- str_replace_all(word, "[^A-Za-z]", "")
        if (nchar(clean_word) >= 3) {
          escaped_clean <- str_replace_all(clean_word, "([.?*+^$\\[\\]\\\\(){}|-])", "\\\\\\1")
          clean_matches <- str_locate_all(search_text,
            regex(escaped_clean, ignore_case = TRUE))[[1]]
          if (nrow(clean_matches) > 0) word_positions[[word]] <- clean_matches[, 1]
        }
      }
    } else {
      clean_word <- str_replace_all(word, "[^A-Za-z]", "")
      if (nchar(clean_word) >= 3) {
        escaped_clean <- str_replace_all(clean_word, "([.?*+^$\\[\\]\\\\(){}|-])", "\\\\\\1")
        clean_matches <- str_locate_all(search_text,
          regex(escaped_clean, ignore_case = TRUE))[[1]]
        if (nrow(clean_matches) > 0) word_positions[[word]] <- clean_matches[, 1]
      }
    }
  }

  min_needed <- max(2, ceiling(length(sig_words) * 0.5))
  if (length(word_positions) < min(min_needed, length(sig_words))) {
    if (length(title_words) >= 3) {
      author_candidate <- paste(tail(title_words, 2), collapse = " ")
      if (str_detect(author_candidate, "^[A-Z].*[A-Z]")) {
        escaped_author <- str_replace_all(author_candidate,
          "([.?*+^$\\[\\]\\\\(){}|])", "\\\\\\1")
        author_match <- tryCatch(
          str_locate(search_text, regex(escaped_author, ignore_case = TRUE)),
          error = function(e) matrix(NA, 1, 2))
        if (!is.na(author_match[1, 1])) {
          pos <- search_start + max(1, author_match[1, 1] - 200) - 1
          return(pos)
        }
      }
    }
    return(NULL)
  }

  all_pos <- sort(unique(unlist(word_positions)))
  best_pos <- NULL
  best_count <- 0

  for (pos in all_pos) {
    count <- sum(sapply(word_positions, function(positions) {
      any(abs(positions - pos) <= 200)
    }))
    if (count > best_count) {
      best_count <- count
      best_pos <- pos
    }
  }

  if (best_count >= min(min_needed, length(word_positions))) {
    return(search_start + best_pos - 1)
  }
  return(NULL)
}
```

# Section Boundary Detection

Locate the major structural sections of each issue: CONTENTS, front ads, board
listing, article body, and back ads.

```{r find-sections}
find_sections <- function(text) {
  sections <- list()
  total_len <- nchar(text)

  # --- CONTENTS ---
  contents_patterns <- c(
    "CONTENTS?\\s*[\u2014\u2013-]+\\s*[A-Z]",
    "CONTENTS?[:.;,]?\\s*(?:[A-Z]+,?\\s+\\d{4}\\.?)?\\s*\n",
    "CONTENTS?[:.;,]?\\s+[A-Z]",
    "CONTENTS?[:.;,]\\s",
    "\\nCONTENTS\\s",
    "^CONTENTS\\s",
    "\\*\\*Page\\*\\*",
    "\\nPage\\s*\\n"
  )

  contents_start <- NA
  for (pat in contents_patterns) {
    m <- str_locate(text, regex(pat, ignore_case = FALSE))
    if (!is.na(m[1, 1])) { contents_start <- m[1, 1]; break }
  }
  if (is.na(contents_start)) {
    for (pat in contents_patterns) {
      m <- str_locate(text, regex(pat, ignore_case = TRUE))
      if (!is.na(m[1, 1])) { contents_start <- m[1, 1]; break }
    }
  }

  if (!is.na(contents_start)) {
    search_region <- str_sub(text, contents_start,
                             min(contents_start + 5000, total_len))
    end_markers <- c("ADVERTISERS", "ADVERTISEMENT\\b", "PUBLICATION INFORMATION",
                     "Entered as second-class", "Organ of the Relief Society")
    contents_end <- nchar(search_region) + contents_start - 1

    for (marker in end_markers) {
      m <- str_locate(search_region, regex(marker, ignore_case = TRUE))
      if (!is.na(m[1, 1]) && m[1, 1] > 10) {
        candidate <- contents_start + m[1, 1] - 2
        if (candidate < contents_end) contents_end <- candidate
      }
    }

    # --- Validate: does the found region actually look like a table of contents? ---
    # A real CONTENTS section has short lines ending in page numbers, or
    # contains known section markers like "Frontispiece" / "Guide Lessons".
    # False positives (like "contents" in story text) have long prose lines.
    candidate_text <- str_sub(text, contents_start, contents_end)

    # Check 1: Does it contain known TOC markers?
    has_toc_markers <- str_detect(candidate_text,
      regex("(?:Frontispiece|Guide Lessons|Notes [Ff]rom the Field)", ignore_case = FALSE))

    # Check 2: Does it have lines ending in page numbers? (classic TOC format)
    lines_with_trailing_numbers <- str_count(candidate_text, "\\w\\s+\\d{2,3}\\s*\\n")

    # Check 3: Is the candidate relatively short (real TOCs are usually < 2500 chars)?
    candidate_length <- nchar(candidate_text)

    # Check 4: Was the match from case-sensitive CONTENTS or case-insensitive?
    # Case-sensitive matches are much more reliable
    case_sensitive_match <- str_detect(
      str_sub(text, contents_start, min(contents_start + 20, total_len)),
      "CONTENTS|Page\\s*\\n")

    is_valid <- has_toc_markers ||
                (lines_with_trailing_numbers >= 3) ||
                (case_sensitive_match && candidate_length < 3000)

    if (is_valid) {
      sections$contents_start <- contents_start
      sections$contents_end <- contents_end
      sections$contents_text <- candidate_text
    } else {
      cat("  CONTENTS candidate rejected (false positive in body text)\n")
      contents_start <- NA
    }
  }

  # --- FRONT ADVERTISERS DIRECTORY ---
  front_adv_patterns <- c("ADVERTISERS'?\\s+DIRECTORY", "ADVERTISERS\\s*:",
                          "ADVERTISEMENT\\b", "\\nADVERTISEMENTS?\\n",
                          "\\nADVERTISEMENTS?\\s*\\n")
  sections$front_adv_start <- NA
  sections$front_adv_end <- NA

  front_search_end <- min(as.integer(total_len * 0.35), total_len)
  front_search_text <- str_sub(text, 1, front_search_end)

  for (pat in front_adv_patterns) {
    m <- str_locate(front_search_text, regex(pat, ignore_case = TRUE))
    if (!is.na(m[1, 1])) {
      sections$front_adv_start <- m[1, 1]
      adv_region <- str_sub(text, m[1, 1], min(m[1, 1] + 8000, total_len))
      zcmi_match <- str_locate_all(adv_region,
        regex("Z\\.?\\s*C\\.?\\s*M\\.?\\s*[IL1]\\.?,?\\s*(?:FACTORY|Salt\\s+Lake|Main\\s+Street)",
              ignore_case = TRUE))[[1]]
      if (nrow(zcmi_match) > 0) {
        zcmi_end <- m[1, 1] + zcmi_match[nrow(zcmi_match), 2]
        after_zcmi <- str_sub(text, zcmi_end, min(zcmi_end + 500, total_len))
        body_marker <- str_locate(after_zcmi,
          regex("\\n[A-Z][A-Z ]{3,}\\n|\\n[A-Z][a-z]", ignore_case = FALSE))
        if (!is.na(body_marker[1, 1])) {
          sections$front_adv_end <- zcmi_end + body_marker[1, 1] - 1
        } else {
          newline_pos <- str_locate(after_zcmi, "\n")
          if (!is.na(newline_pos[1, 1])) {
            sections$front_adv_end <- zcmi_end + newline_pos[1, 2]
          } else {
            sections$front_adv_end <- zcmi_end + 50
          }
        }
      } else {
        sections$front_adv_end <- min(m[1, 1] + 3000, total_len)
      }
      break
    }
  }

  # --- BODY START ---
  if (!is.na(sections$front_adv_end)) {
    sections$body_start <- sections$front_adv_end
  } else {
    body_pattern <- "THE\\s+Relief\\s+Society\\s+Magazine\\s+Vol\\.?\\s+[IVX0-9]+"
    body_matches <- str_locate_all(text, regex(body_pattern, ignore_case = FALSE))[[1]]

    if (nrow(body_matches) >= 2) {
      sections$body_start <- body_matches[2, 1]
    } else if (nrow(body_matches) == 1 && body_matches[1, 1] < total_len * 0.5) {
      sections$body_start <- body_matches[1, 1]
    } else {
      vol_header <- str_locate(text,
        regex("Vol\\.?\\s+[IVX0-9]+\\.?\\s+(?:JANUARY|FEBRUARY|MARCH|APRIL|MAY|JUNE|JULY|AUGUST|SEPTEMBER|OCTOBER|NOVEMBER|DECEMBER)",
              ignore_case = FALSE))
      if (!is.na(vol_header[1, 1]) && vol_header[1, 1] > 100) {
        sections$body_start <- vol_header[1, 1]
      } else if (!is.na(contents_start)) {
        sections$body_start <- sections$contents_end + 1
      } else {
        sections$body_start <- 1
      }
    }
  }

  # --- BACK-OF-ISSUE ADS ---
  ads_patterns <- c("ADVERTISERS'?\\s+DIRECTORY", "ADVERTISERS\\s*:",
                    "INDEX TO ADVERTISERS", "PATRONIZE OUR ADVERTISERS")
  search_start_ads <- as.integer(total_len * 0.7)
  search_text_ads <- str_sub(text, search_start_ads, total_len)

  sections$ads_start <- total_len
  for (pat in ads_patterns) {
    m <- str_locate(search_text_ads, regex(pat, ignore_case = TRUE))
    if (!is.na(m[1, 1])) {
      sections$ads_start <- search_start_ads + m[1, 1] - 1
      break
    }
  }

  # Fallback: commercial patterns in last 10%
  if (sections$ads_start >= total_len) {
    back_search_start <- as.integer(total_len * 0.9)
    back_search_text <- str_sub(text, back_search_start, total_len)
    ad_indicators <- c(
      "Salt Lake City,?\\s*Utah",
      "Send for (Samples|Catalog)",
      "FACTORY PR[I1]CE",
      "Phone\\s+[A-Z]",
      "Mail Orders",
      "Kindly mention this magazine",
      "Mention Relief Society Magazine",
      "Wedding Invitations"
    )
    earliest_ad <- total_len
    for (ap in ad_indicators) {
      am <- str_locate(back_search_text, regex(ap, ignore_case = TRUE))
      if (!is.na(am[1, 1])) {
        candidate <- back_search_start + am[1, 1] - 1
        if (candidate < earliest_ad) earliest_ad <- candidate
      }
    }
    if (earliest_ad < total_len) {
      lookback <- str_sub(text, max(1, earliest_ad - 500), earliest_ad - 1)
      breaks <- str_locate_all(lookback, "[\\.\\n]\\s")[[1]]
      if (nrow(breaks) > 0) {
        sections$ads_start <- max(1, earliest_ad - 500) + breaks[nrow(breaks), 2]
      } else {
        sections$ads_start <- earliest_ad
      }
    }
  }

  # --- BOARD LISTING ---
  board_roster_patterns <- c(
    "THE GENERAL BOARD[,.]?\\s+Mrs\\.",
    "THE GENERAL BOARD[,.]?\\s+Miss\\s",
    "GENERAL BOARD\\s+OF\\s+(?:THE\\s+)?RELIEF\\s+SOCIETY[,.]?\\s+(?:Mrs\\.|Reading)",
    "GENERAL BOARD OF RELIEF SOCIETY\\s*\\n"
  )
  board_fallback <- c("THE GENERAL BOARD", "GENERAL BOARD, RELIEF SOCIETY",
                      "GENERAL BOARD OF RELIEF SOCIETY")

  sections$board_start <- NA
  sections$board_end <- NA

  for (pat in board_roster_patterns) {
    m <- str_locate(text, regex(pat, ignore_case = TRUE))
    if (!is.na(m[1, 1])) {
      sections$board_start <- m[1, 1]
      break
    }
  }
  if (is.na(sections$board_start)) {
    for (pat in board_fallback) {
      all_m <- str_locate_all(text, regex(pat, ignore_case = TRUE))[[1]]
      if (nrow(all_m) > 0) {
        for (mi in 1:nrow(all_m)) {
          after_text <- str_sub(text, all_m[mi, 2] + 1,
                                min(all_m[mi, 2] + 30, nchar(text)))
          if (!str_detect(after_text, "^\\s+of\\s+the\\s+Relief") &&
              !str_detect(after_text, "^\\s+of\\s+Relief")) {
            sections$board_start <- all_m[mi, 1]
            break
          }
        }
        if (!is.na(sections$board_start)) break
      }
    }
  }

  if (!is.na(sections$board_start)) {
    board_search <- str_sub(text, sections$board_start,
                            min(sections$board_start + 3000, nchar(text)))
    board_end_markers <- c("Music\\s+Director.*?Organist",
                           "Organist\\b",
                           "Bishop'?s\\s+B[ul]i?lding",
                           "Salt Lake City,?\\s+Utah",
                           "Bishops?\\s+Bldg",
                           "Room\\s+\\d+.*?Utah",
                           "Vol\\.\\s+[IVX0-9]+")
    for (em in board_end_markers) {
      em_match <- str_locate_all(board_search, regex(em, ignore_case = TRUE))[[1]]
      if (nrow(em_match) > 0) {
        sections$board_end <- sections$board_start + em_match[nrow(em_match), 2]
        break
      }
    }
    if (is.na(sections$board_end)) {
      sections$board_end <- min(sections$board_start + 2000, nchar(text))
    }
  }

  sections$front_ads_end <- max(1, sections$body_start - 1)
  return(sections)
}
```

# Page-Number Aware Search

Use the page number from the CONTENTS to estimate where in the body text an
article should appear, then search in a window around that estimate.

```{r page-search}
estimate_char_position <- function(page_num, min_page, max_page,
                                   body_start, body_end) {
  if (max_page <= min_page) return(body_start)
  body_len <- body_end - body_start
  fraction <- (page_num - min_page) / (max_page - min_page)
  estimated <- body_start + as.integer(fraction * body_len)
  return(max(body_start, min(estimated, body_end)))
}

find_article_with_page_hint <- function(text, title, page_num,
                                        min_page, max_page,
                                        body_start, body_end) {
  est_pos <- estimate_char_position(page_num, min_page, max_page,
                                    body_start, body_end)
  body_len <- body_end - body_start
  window_size <- max(5000, as.integer(body_len * 0.25))

  search_start <- max(body_start, est_pos - window_size)
  search_end   <- min(body_end, est_pos + window_size)

  pos <- find_title_in_text(text, title, search_start, search_end)
  if (!is.null(pos)) {
    return(pos)  # Narrow window found it - trust this result
  }
  # Narrow window failed, try full body
  pos <- find_title_in_text(text, title, body_start, body_end)
  return(pos)
}
```

# Diagnostic: Classify Missed Articles

When a CONTENTS title can't be found, determine whether it was a search failure
or truly absent from the OCR text.

```{r classify-miss}
classify_miss <- function(text, title, body_start, body_end) {
  sig_words <- get_significant_words(title)
  if (length(sig_words) == 0) {
    return(list(status = "MISSED_SEARCH",
                notes = "No significant words in title"))
  }
  body_text <- str_sub(text, body_start, body_end)
  words_in_body <- sapply(sig_words, function(w) {
    escaped <- str_replace_all(w, "([.?*+^$\\[\\]\\\\(){}|-])", "\\\\\\1")
    str_detect(body_text, regex(paste0("\\b", escaped, "\\b"), ignore_case = TRUE))
  })
  fraction_found <- sum(words_in_body) / length(sig_words)

  if (fraction_found >= 0.5) {
    return(list(
      status = "MISSED_SEARCH",
      notes = sprintf("%d/%d significant words found in body (%s)",
                      sum(words_in_body), length(sig_words),
                      paste(sig_words[words_in_body], collapse = ", "))
    ))
  } else {
    return(list(
      status = "ABSENT_FROM_SOURCE",
      notes = sprintf("Only %d/%d significant words in body (%s missing)",
                      sum(words_in_body), length(sig_words),
                      paste(sig_words[!words_in_body], collapse = ", "))
    ))
  }
}
```

# Category-Based Boundary Detection

Find known section headers (EDITORIAL, GUIDE LESSONS, etc.) in the body text.

```{r find-cat-headers}
find_category_headers <- function(text, body_start, body_end) {
  found <- data.frame(name = character(), position = integer(),
                      stringsAsFactors = FALSE)
  body_len <- body_end - body_start

  for (cat in KNOWN_CATEGORIES) {
    if (cat$search_region == "back_half") {
      s_start <- body_start + as.integer(body_len * 0.5)
      s_end <- body_end
    } else if (cat$search_region == "back_third") {
      s_start <- body_start + as.integer(body_len * 0.66)
      s_end <- body_end
    } else if (cat$search_region == "front_half") {
      s_start <- body_start
      s_end <- body_start + as.integer(body_len * 0.5)
    } else {
      s_start <- body_start
      s_end <- body_end
    }

    search_text <- str_sub(text, s_start, s_end)

    for (pat in cat$body_patterns) {
      matches <- str_locate_all(search_text,
        regex(pat, ignore_case = FALSE))[[1]]

      if (nrow(matches) > 0) {
        for (mi in 1:nrow(matches)) {
          candidate_pos <- s_start + matches[mi, 1] - 1
          candidate_end <- s_start + matches[mi, 2] - 1

          context_start <- max(1, candidate_pos - 5)
          context_before <- str_sub(text, context_start, candidate_pos - 1)
          context_after <- str_sub(text, candidate_end + 1,
                                   min(candidate_end + 10, nchar(text)))

          is_running_header <- str_detect(context_before, "\\d+\\s*$") ||
                               str_detect(context_after, "^[.:]?\\s*\\d{1,4}\\b")

          # For Editorial, also check if this is a masthead
          is_masthead <- FALSE
          if (cat$name == "Editorial" && !is_running_header) {
            mast_context <- str_sub(text, candidate_pos,
                                    min(nchar(text), candidate_pos + 300))
            is_masthead <- str_detect(mast_context,
              regex("(?:Mott[oe]|Charity Never|RELIEF SOCIETY MAGAZINE|Editor\\s*[-.]|Business Manager|Entered as second[- ]class|Organ of the Relief)",
                    ignore_case = TRUE))
          }

          if (!is_running_header && !is_masthead) {
            found <- rbind(found, data.frame(
              name = cat$name, position = candidate_pos,
              stringsAsFactors = FALSE))
            break
          }
        }
        break
      }
    }
  }
  return(found)
}
```

# Running Header Cleaner

Remove magazine running headers from extracted article text.

```{r clean-headers}
clean_running_headers <- function(article_text) {
  article_text <- str_replace_all(article_text,
    regex("THE\\s+Relief\\s+Society\\s+Magazine\\s+Vol\\..*?No\\.\\s*\\d+\\.?",
          ignore_case = TRUE), "\n")
  article_text <- str_replace_all(article_text,
    regex("\\d+\\s+RELIEF\\s+SOCIETY\\s+MAGAZINE\\.?", ignore_case = FALSE), "\n")
  article_text <- str_replace_all(article_text,
    regex("RELIEF\\s+SOCIETY\\s+MAGAZINE\\.?\\s+\\d+", ignore_case = FALSE), "\n")
  article_text <- str_replace_all(article_text,
    regex("Vol\\.?\\s+[IVX]+\\.?\\s+(?:JANUARY|FEBRUARY|MARCH|APRIL|MAY|JUNE|JULY|AUGUST|SEPTEMBER|OCTOBER|NOVEMBER|DECEMBER),?\\s+\\d{4}\\.?\\s+No\\.\\s*\\d+\\.?",
          ignore_case = FALSE), "\n")
  article_text <- str_replace_all(article_text,
    regex("\\d+\\s+[A-Z][A-Z\\s',-]+\\.", ignore_case = FALSE), "\n")
  article_text <- str_replace(article_text,
    regex("Entered as second-class matter.*?Utah", dotall = TRUE,
          ignore_case = TRUE), "")
  article_text <- str_replace_all(article_text, "\\n{4,}", "\n\n\n")
  article_text <- trimws(article_text)
  return(article_text)
}
```

# Fallback Extraction (No CONTENTS)

When no CONTENTS section is found, detect article boundaries using running header
transitions, known category headers, and "By Author" patterns.

```{r fallback-extraction}
extract_articles_no_contents <- function(text, body_start, body_end) {
  articles <- data.frame(title = character(), page = integer(),
                         position = integer(), category = character(),
                         stringsAsFactors = FALSE)

  body_text <- str_sub(text, body_start, body_end)
  body_len <- nchar(body_text)

  # --- Strategy 1: Running header title transitions ---
  # Pattern A: "TITLE. 429 " (with period)
  # Pattern B: "TITLE 429 " (without period, for collapsed files)
  # Pattern C: "429 TITLE" (page number before title)
  header_patterns <- c(
    "([A-Z][A-Z\\s',\\-]+)\\.\\s+(\\d{2,3})\\s",
    "([A-Z][A-Z\\s',\\-]{5,})\\s+(\\d{2,3})\\s+[A-Za-z]",
    "(\\d{2,3})\\s+([A-Z][A-Z\\s',\\-]{5,})"
  )

  header_titles <- list()
  for (h_pat in header_patterns) {
    odd_headers <- str_locate_all(body_text,
      regex(h_pat, ignore_case = FALSE))[[1]]

    if (nrow(odd_headers) > 0) {
      for (hi in 1:nrow(odd_headers)) {
        h_text <- str_trim(str_sub(body_text, odd_headers[hi, 1], odd_headers[hi, 2]))
        # Remove page number, trailing chars, and period
        h_title <- str_replace(h_text, "\\s+\\d+\\s+[A-Za-z]\\s*$", "")  # "TITLE 429 T" -> "TITLE"
        h_title <- str_replace(h_title, "\\s+\\d+\\s*$", "")              # "TITLE 429" -> "TITLE"
        h_title <- str_replace(h_title, "^\\d+\\s+", "")                  # "429 TITLE" -> "TITLE"
        h_title <- str_trim(str_replace(h_title, "\\.$", ""))
        if (str_detect(h_title, "(?i)RELIEF\\s+SOCIETY\\s+MAGAZINE")) next
        if (nchar(h_title) < 3) next
        h_norm <- toupper(str_replace_all(h_title, "\\s+", " "))
        if (is.null(header_titles[[h_norm]])) {
          header_titles[[h_norm]] <- list(
            title = h_title,
            first_pos = body_start + odd_headers[hi, 1] - 1
          )
        }
      }
    }
  }

  # --- Strategy 2: Known category headers ---
  cat_headers <- find_category_headers(text, body_start, body_end)

  # --- Strategy 3: "Title. By Author." patterns ---
  by_matches <- str_locate_all(body_text,
    regex("[A-Z][A-Za-z'\\-,\\s]{3,60}\\.?\\s+(?:By|by|B\\\\)\\s+[A-Z][a-z]+\\s+[A-Z]",
          ignore_case = FALSE))[[1]]

  by_articles <- list()
  if (nrow(by_matches) > 0) {
    for (bi in 1:nrow(by_matches)) {
      match_text <- str_sub(body_text, by_matches[bi, 1], by_matches[bi, 2])
      title_part <- str_trim(str_replace(match_text,
        "\\s*\\.?\\s*(?:By|by|B\\\\)\\s+[A-Z].*$", ""))
      if (nchar(title_part) < 3) next
      abs_pos <- body_start + by_matches[bi, 1] - 1
      before_ctx <- str_sub(text, max(1, abs_pos - 8), abs_pos - 1)
      if (str_detect(before_ctx, "\\d{2,3}\\s*$")) next
      by_articles[[length(by_articles) + 1]] <- list(
        title = title_part, position = abs_pos
      )
    }
  }

  # --- Merge all detected boundaries ---
  all_boundaries <- data.frame(title = character(), position = integer(),
                               source = character(), stringsAsFactors = FALSE)

  cat(sprintf("  Fallback: %d header titles, %d by-author\n",
              length(header_titles), length(by_articles)))
  for (h_norm in names(header_titles)) {
    entry <- header_titles[[h_norm]]
    all_boundaries <- rbind(all_boundaries, data.frame(
      title = entry$title, position = entry$first_pos,
      source = "header", stringsAsFactors = FALSE))
  }
  if (nrow(cat_headers) > 0) {
    for (ci in 1:nrow(cat_headers)) {
      all_boundaries <- rbind(all_boundaries, data.frame(
        title = cat_headers$name[ci], position = cat_headers$position[ci],
        source = "category", stringsAsFactors = FALSE))
    }
  }
  for (ba in by_articles) {
    all_boundaries <- rbind(all_boundaries, data.frame(
      title = ba$title, position = ba$position,
      source = "by_author", stringsAsFactors = FALSE))
  }

  if (nrow(all_boundaries) == 0) return(NULL)
  all_boundaries <- all_boundaries[order(all_boundaries$position), ]

  # De-duplication
  all_boundaries$norm_title <- toupper(all_boundaries$title)
  all_boundaries$norm_title <- str_replace_all(all_boundaries$norm_title, "[^A-Z\\s]", "")
  all_boundaries$norm_title <- str_replace_all(all_boundaries$norm_title, "\\s+", " ")
  all_boundaries$norm_title <- str_trim(all_boundaries$norm_title)

  source_priority <- c("category" = 1, "by_author" = 2, "header" = 3)
  keep <- rep(TRUE, nrow(all_boundaries))

  if (nrow(all_boundaries) > 1) {
    for (i in 2:nrow(all_boundaries)) {
      if (!keep[i]) next
      for (j in 1:(i-1)) {
        if (!keep[j]) next
        same_title <- FALSE
        ti <- all_boundaries$norm_title[i]
        tj <- all_boundaries$norm_title[j]
        if (ti == tj) same_title <- TRUE
        if (!same_title && nchar(ti) >= 5 && nchar(tj) >= 5) {
          words_i <- str_split(ti, "\\s+")[[1]]
          words_j <- str_split(tj, "\\s+")[[1]]
          exact_overlap <- sum(words_i %in% words_j)
          if (exact_overlap >= max(1, 0.7 * min(length(words_i), length(words_j)))) {
            same_title <- TRUE
          }
          if (!same_title) {
            fuzzy_i <- str_replace_all(words_i, "[AEIOU]", "")
            fuzzy_j <- str_replace_all(words_j, "[AEIOU]", "")
            fuzzy_overlap <- sum(fuzzy_i %in% fuzzy_j)
            if (fuzzy_overlap >= max(1, 0.6 * min(length(words_i), length(words_j)))) {
              same_title <- TRUE
            }
          }
          if (!same_title && abs(nchar(ti) - nchar(tj)) < 5) {
            shorter <- min(nchar(ti), nchar(tj))
            if (shorter > 5) {
              ci_ch <- strsplit(ti, "")[[1]]
              cj_ch <- strsplit(tj, "")[[1]]
              min_len <- min(length(ci_ch), length(cj_ch))
              char_match <- sum(ci_ch[1:min_len] == cj_ch[1:min_len])
              if (char_match / min_len >= 0.8) same_title <- TRUE
            }
          }
          if (!same_title && (str_detect(ti, fixed(tj)) || str_detect(tj, fixed(ti)))) {
            same_title <- TRUE
          }
        }

        if (same_title) {
          p_i <- source_priority[all_boundaries$source[i]]
          p_j <- source_priority[all_boundaries$source[j]]
          if (p_i < p_j && (all_boundaries$position[i] - all_boundaries$position[j] < 1000)) {
            keep[j] <- FALSE
          } else {
            keep[i] <- FALSE
          }
          break
        }
        if (all_boundaries$position[i] - all_boundaries$position[j] < 500) {
          p_i <- source_priority[all_boundaries$source[i]]
          p_j <- source_priority[all_boundaries$source[j]]
          if (p_i < p_j) { keep[j] <- FALSE } else { keep[i] <- FALSE }
          break
        }
      }
    }
  }
  all_boundaries <- all_boundaries[keep, ]
  if (nrow(all_boundaries) == 0) return(NULL)

  # Filter junk entries
  good <- sapply(1:nrow(all_boundaries), function(i) {
    title <- all_boundaries$title[i]
    if (all_boundaries$source[i] == "category") return(TRUE)
    words <- str_split(title, "\\s+")[[1]]
    words <- words[nchar(words) > 1]
    if (length(words) == 0) return(FALSE)
    if (length(words) == 1 && all_boundaries$source[i] == "header") return(FALSE)
    cap_words <- sum(str_detect(words, "^[A-Z]"))
    if (cap_words / length(words) < 0.6) return(FALSE)
    if (str_detect(title, "(?i)^(and |but |or |when |that |which |where )")) return(FALSE)
    if (str_detect(title, "[a-z][A-Z]")) {
      if (!str_detect(title, "^Mc[A-Z]")) return(FALSE)
    }
    if (str_detect(title, ",\\s+[a-z]")) return(FALSE)
    return(TRUE)
  })
  all_boundaries <- all_boundaries[good, ]
  if (nrow(all_boundaries) == 0) return(NULL)

  result <- data.frame(
    title = all_boundaries$title,
    page = NA_integer_,
    stringsAsFactors = FALSE
  )
  result$category <- sapply(result$title, classify_article)
  result$position <- all_boundaries$position

  cat(sprintf("  Fallback extraction: %d article boundaries detected\n", nrow(result)))
  return(result)
}
```

# Core Processing Function

This is the main workhorse. For each monthly issue file it:

1. Reads and normalizes the text
2. Finds structural sections (CONTENTS, Board, ads, body)
3. Saves Board and Contents files
4. Parses the CONTENTS to get article titles and page numbers
5. Locates each article in the body text
6. Extracts articles into individual files
7. Collects leftover text into a Misc folder

```{r process-issue}
process_issue <- function(filepath, output_dir) {
  filename <- basename(filepath)
  metadata <- get_metadata(filename)

  text <- read_file_safe(filepath)
  text <- normalize_text(text)
  total_chars <- nchar(text)

  cat("\n", rep("=", 70), "\n", sep = "")
  cat("Processing:", filename, "\n")
  cat("Chars:", format(total_chars, big.mark = ","), "\n")
  cat(rep("=", 70), "\n", sep = "")

  vol_year_folder <- paste0("Vol", metadata$volume, "_", metadata$year)
  month_folder <- file.path(output_dir, vol_year_folder, metadata$month)
  # Clean previous output for this month to avoid leftover files
  if (dir.exists(month_folder)) {
    old_files <- list.files(month_folder, full.names = TRUE)
    if (length(old_files) > 0) file.remove(old_files)
  }
  dir.create(month_folder, showWarnings = FALSE, recursive = TRUE)
  prefix <- paste0(metadata$month, "_Vol", metadata$volume)

  sections <- find_sections(text)

  # --- Save BOARD file ---
  board_text <- ""
  if (!is.na(sections$board_start)) {
    board_text <- str_trim(str_sub(text, sections$board_start, sections$board_end))
    write_file(board_text,
               file.path(month_folder, paste0(prefix, "_00_BOARD.txt")))
    cat("  Board saved\n")
  }

  # --- Save CONTENTS file ---
  articles <- NULL
  if (!is.null(sections$contents_text)) {
    write_file(str_trim(sections$contents_text),
               file.path(month_folder, paste0(prefix, "_00_CONTENTS.txt")))
    cat("  Contents file saved\n")
    articles <- parse_contents_section(sections$contents_text)
    if (!is.null(articles) && nrow(articles) > 0) {
      cat("  Contents:", nrow(articles), "articles listed\n")
    }
  }

  # --- Determine body boundaries ---
  body_start <- 1
  if (!is.null(sections$body_start)) body_start <- max(body_start, sections$body_start)
  body_end <- sections$ads_start - 1
  if (body_end <= body_start) body_end <- nchar(text)

  use_fallback <- FALSE

  if (is.null(articles) || nrow(articles) == 0) {
    cat("  No CONTENTS found. Trying fallback extraction...\n")
    fallback <- extract_articles_no_contents(text, body_start, body_end)
    if (!is.null(fallback) && nrow(fallback) > 0) {
      articles <- fallback[, c("title", "page", "category")]
      use_fallback <- TRUE
      fallback_positions <- fallback$position
    } else {
      cat("  Fallback found no articles. Full text -> MISC.\n")
      write_file(text, file.path(month_folder, paste0(prefix, "_Misc.txt")))
      return(data.frame(file = filename, articles_found = 0, articles_saved = 0,
                        missed_search = 0, absent_source = 0,
                        total_chars = total_chars, stringsAsFactors = FALSE))
    }
  }

  cat(sprintf("  Body: %d to %d (%dk chars)\n",
              body_start, body_end,
              as.integer((body_end - body_start) / 1000)))

  cat_headers <- find_category_headers(text, body_start, body_end)
  if (nrow(cat_headers) > 0) {
    cat(sprintf("  Category headers: %s\n",
                paste(cat_headers$name, collapse = ", ")))
  }

  # --- Position search ---
  if (use_fallback) {
    positions <- fallback_positions
    for (i in 1:nrow(articles)) {
      cat(sprintf("    [%02d] %-45s @ %6d [%s]\n",
                  i, str_sub(articles$title[i], 1, 45), positions[i],
                  articles$category[i]))
    }
  } else {

    # Exclude page 0 (Frontispiece) from range to avoid skewing position estimates
    real_pages <- articles$page[articles$page > 0]
    min_page <- if (length(real_pages) > 0) min(real_pages, na.rm = TRUE) else 1
    max_page <- if (length(real_pages) > 0) max(real_pages, na.rm = TRUE) else 1
    positions <- rep(NA_integer_, nrow(articles))

    for (i in 1:nrow(articles)) {
      title <- articles$title[i]
      page  <- articles$page[i]
      category <- articles$category[i]
      search_body_end <- body_end

      # Known category header shortcut
      if (category != "Article" && category != "Frontispiece" &&
          category != "Of_Interest" && category != "Conventions") {
        cat_match <- cat_headers[tolower(cat_headers$name) ==
                                 tolower(str_replace_all(category, "_", " ")), ]
        if (nrow(cat_match) > 0) {
          positions[i] <- cat_match$position[1]
          cat(sprintf("    [%02d] %-45s @ %6d [%s]\n",
                      i, str_sub(title, 1, 45), positions[i], category))
          next
        }
      }

      # Editorial special handling
      if (str_detect(title, "(?i)^Editorial")) {
        edit_start <- as.integer(body_start + (body_end - body_start) * 0.5)
        edit_search_end <- min(nchar(text), body_end + 5000)
        search_t <- str_sub(text, edit_start, edit_search_end)
        edit_matches <- str_locate_all(search_t, regex("EDITORIAL", ignore_case = FALSE))[[1]]

        if (nrow(edit_matches) > 0) {
          for (mi in 1:nrow(edit_matches)) {
            candidate <- edit_start + edit_matches[mi, 1] - 1
            context_before <- str_sub(text, max(1, candidate - 5), candidate - 1)
            context_after <- str_sub(text, candidate,
                                     min(nchar(text), candidate + 200))
            # Skip if preceded by running header page number
            if (str_detect(context_before, "\\d+\\s*$")) next
            # Skip if this is a masthead (followed by Motto/Motte, Editor, Magazine, etc.)
            if (str_detect(context_after,
                regex("(?:Mott[oe]|Charity Never|RELIEF SOCIETY MAGAZINE|Editor\\s*[-.]|Business Manager|Entered as second[- ]class)",
                      ignore_case = TRUE))) next
            if (candidate > body_start + 500) {
              positions[i] <- candidate
              break
            }
          }
        }
        if (!is.na(positions[i])) {
          cat(sprintf("    [%02d] %-45s @ %6d [%s]\n",
                      i, str_sub(title, 1, 45), positions[i], category))
          next
        }
        # EDITORIAL special handling failed (all matches were mastheads).
        # Try searching for the subtitle (e.g. "Prayer" from "Editorial: Prayer")
        subtitle <- str_replace(title, "(?i)^Editorial[s]?[,:;—\\-]+\\s*", "")
        subtitle <- str_trim(subtitle)
        if (nchar(subtitle) > 2 && subtitle != title) {
          sub_pos <- NULL
          sub_upper <- toupper(subtitle)
          sub_escaped <- str_replace_all(sub_upper,
            "([.?*+^$\\[\\]\\\\(){}|])", "\\\\\\1")
          search_t_sub <- str_sub(text, edit_start, edit_search_end)

          # Strategy A: ALL CAPS on its own line
          caps_line <- str_locate(search_t_sub,
            regex(paste0("(?:^|\\n)\\s*", sub_escaped, "\\s*(?:\\n|$)"),
                  ignore_case = FALSE))
          if (!is.na(caps_line[1, 1])) {
            raw_pos <- edit_start + caps_line[1, 1] - 1
            actual_text <- str_sub(text, raw_pos, raw_pos + nchar(sub_upper) + 5)
            ws_off <- str_locate(actual_text, "[A-Z]")[1, 1] - 1
            if (!is.na(ws_off)) sub_pos <- raw_pos + ws_off else sub_pos <- raw_pos
          }

          # Strategy B: ALL CAPS preceded by page/issue header pattern or whitespace
          if (is.null(sub_pos)) {
            caps_word <- str_locate(search_t_sub,
              regex(paste0("(?:No\\.\\s*\\d+\\s+|\\d{1,4}\\s+)", sub_escaped, "\\s+[A-Z]"),
                    ignore_case = FALSE))
            if (!is.na(caps_word[1, 1])) {
              # Find the actual start of the ALL CAPS word
              match_text <- str_sub(search_t_sub, caps_word[1, 1],
                                    caps_word[1, 2])
              word_start <- str_locate(match_text,
                regex(sub_escaped, ignore_case = FALSE))[1, 1]
              if (!is.na(word_start)) {
                sub_pos <- edit_start + caps_word[1, 1] + word_start - 2
              }
            }
          }

          # Strategy C: ALL CAPS as standalone word anywhere
          if (is.null(sub_pos)) {
            caps_any <- str_locate(search_t_sub,
              regex(paste0("\\b", sub_escaped, "\\b"), ignore_case = FALSE))
            if (!is.na(caps_any[1, 1])) {
              sub_pos <- edit_start + caps_any[1, 1] - 1
            }
          }

          # Strategy D: fall back to case-insensitive search
          if (is.null(sub_pos)) {
            sub_pos <- find_title_in_text(text, subtitle, edit_start,
                                          edit_search_end)
          }

          if (!is.null(sub_pos) && !is.na(sub_pos)) {
            positions[i] <- sub_pos
            cat(sprintf("    [%02d] %-45s @ %6d [%s] (subtitle)\n",
                        i, str_sub(title, 1, 45), sub_pos, category))
            next
          }
        }
        search_body_end <- edit_search_end
      }

      # Guide Lessons special handling
      if (str_detect(title, "(?i)^Guide\\s+Lesson")) {
        gl_start <- as.integer(body_start + (body_end - body_start) * 0.6)
        gl_search_text <- str_sub(text, gl_start, body_end)
        gl_matches <- str_locate_all(gl_search_text,
          regex("GUIDE\\s+LESSONS?", ignore_case = FALSE))[[1]]
        if (nrow(gl_matches) > 0) {
          pos <- gl_start + gl_matches[nrow(gl_matches), 1] - 1
          after_text <- str_sub(text, pos + 14, min(pos + 25, nchar(text)))
          if (str_detect(after_text, "^[.:]?\\s*\\d{1,4}\\b")) {
            if (nrow(gl_matches) >= 2) {
              pos <- gl_start + gl_matches[nrow(gl_matches) - 1, 1] - 1
            }
          }
        } else {
          pos <- find_title_in_text(text, "Guide Lessons", gl_start, body_end)
        }
        if (!is.null(pos)) positions[i] <- pos
        if (!is.na(positions[i])) {
          cat(sprintf("    [%02d] %-45s @ %6d [%s]\n",
                      i, str_sub(title, 1, 45), positions[i], category))
        }
        next
      }

      # General title search with page hint
      pos <- find_article_with_page_hint(text, title, page,
                                         min_page, max_page,
                                         body_start, search_body_end)

      if (!is.null(pos)) {
        positions[i] <- pos
        cat(sprintf("    [%02d] %-45s @ %6d [%s]\n",
                    i, str_sub(title, 1, 45), positions[i], category))
      } else if (body_start > 100) {
        pre_pos <- NULL
        safe_start <- 1
        if (!is.null(sections$contents_end) && !is.na(sections$contents_end)) {
          safe_start <- sections$contents_end + 1
        }
        if (safe_start < body_start) {
          pre_pos <- find_title_in_text(text, title, safe_start, body_start)
        }
        if (!is.null(pre_pos)) {
          positions[i] <- pre_pos
          cat(sprintf("    [%02d] %-45s @ %6d [%s] (pre-body)\n",
                      i, str_sub(title, 1, 45), positions[i], category))
        } else {
          cat(sprintf("    [%02d] %-45s   MISSED [%s]\n",
                      i, str_sub(title, 1, 45), category))
        }
      } else {
        cat(sprintf("    [%02d] %-45s   MISSED [%s]\n",
                    i, str_sub(title, 1, 45), category))
      }
    }

    # --- Look-back adjustment ---
    for (i in which(!is.na(positions))) {
      pos <- positions[i]
      lookback_start <- max(body_start, pos - 200)
      lookback_text <- str_sub(text, lookback_start, pos - 1)
      boundaries <- str_locate_all(lookback_text, "[\\.!?]\\s+|\\n")[[1]]
      if (nrow(boundaries) > 0) {
        last_boundary <- boundaries[nrow(boundaries), 2]
        adjusted <- lookback_start + last_boundary
        if (pos - adjusted < 150 && pos - adjusted > 0) {
          gap_text <- str_trim(str_sub(text, adjusted, pos - 1))
          if (nchar(gap_text) > 0 && nchar(gap_text) < 100) {
            words <- str_split(gap_text, "\\s+")[[1]]
            cap_words <- sum(str_detect(words, "^[A-Z]"))
            if (cap_words / max(1, length(words)) >= 0.5) {
              positions[i] <- adjusted
            }
          }
        }
      }
    }

    # --- Position validation ---
    for (i in which(!is.na(positions))) {
      title <- articles$title[i]
      pos <- positions[i]
      sig_words <- get_significant_words(title)
      if (length(sig_words) == 0) next

      check_end <- min(nchar(text), pos + 1000)
      check_text <- str_sub(text, pos, check_end)
      found_count <- sum(sapply(sig_words, function(w) {
        ew <- str_replace_all(w, "([.?*+^$\\[\\]\\\\(){}|-])", "\\\\\\1")
        str_detect(check_text, regex(paste0("\\b", ew, "\\b"), ignore_case = TRUE))
      }))

      if (found_count / length(sig_words) < 0.5) {
        alt_pos <- find_title_in_text(text, title, body_start, body_end)
        if (!is.null(alt_pos) && alt_pos != pos) {
          alt_end <- min(nchar(text), alt_pos + 1000)
          alt_text <- str_sub(text, alt_pos, alt_end)
          alt_count <- sum(sapply(sig_words, function(w) {
            ew <- str_replace_all(w, "([.?*+^$\\[\\]\\\\(){}|-])", "\\\\\\1")
            str_detect(alt_text, regex(paste0("\\b", ew, "\\b"), ignore_case = TRUE))
          }))
          if (alt_count > found_count) {
            positions[i] <- alt_pos
            cat(sprintf("    [%02d] Repositioned to %d (was %d, %d/%d -> %d/%d sig words)\n",
                        i, alt_pos, pos, found_count, length(sig_words),
                        alt_count, length(sig_words)))
          } else if (found_count == 0) {
            positions[i] <- NA
            cat(sprintf("    [%02d] %-45s   REJECTED (0 sig words at pos %d)\n",
                        i, str_sub(title, 1, 45), pos))
          }
        } else if (found_count == 0) {
          positions[i] <- NA
          cat(sprintf("    [%02d] %-45s   REJECTED (0/%d sig words at pos %d)\n",
                      i, str_sub(title, 1, 45), length(sig_words), pos))
        }
      }
    }
  } # end else (CONTENTS-based position search)

  # (Page-order consistency check removed — too aggressive for OCR text
  #  where page estimates are imprecise. Position validation above handles
  #  the most important cases via sig-word checking.)

  # --- Diagnostic report ---
  diag <- data.frame(
    title = articles$title,
    page = articles$page,
    category = articles$category,
    position = positions,
    status = ifelse(!is.na(positions), "FOUND", "UNKNOWN"),
    notes = "",
    stringsAsFactors = FALSE
  )
  for (i in which(is.na(positions))) {
    result <- classify_miss(text, articles$title[i], body_start, body_end)
    diag$status[i] <- result$status
    diag$notes[i] <- result$notes
  }

  # --- Build valid article list ---
  valid_idx <- which(!is.na(positions))

  if (length(valid_idx) > 1) {
    keep_v <- rep(TRUE, length(valid_idx))
    for (k in 2:length(valid_idx)) {
      if (abs(positions[valid_idx[k]] - positions[valid_idx[k - 1]]) < 50) {
        keep_v[k] <- FALSE
      }
    }
    valid_idx <- valid_idx[keep_v]
  }

  # --- Compute end boundaries (sentence-aware) ---
  # For each article, find where the next article begins, then snap backward
  # to a clean sentence boundary. Strategy: look back a small window (200 chars)
  # from the next article's start to find the last sentence-ending punctuation.
  # This ensures we capture all content up to a natural stopping point while
  # not losing significant text (max 200 chars of snap).
  all_valid_pos <- sort(positions[valid_idx])
  article_ends <- rep(NA_integer_, length(valid_idx))
  for (k in seq_along(valid_idx)) {
    my_pos <- positions[valid_idx[k]]
    higher <- all_valid_pos[all_valid_pos > my_pos]
    if (length(higher) > 0) {
      raw_end <- higher[1] - 1
    } else {
      raw_end <- max(body_end, my_pos + 10000)
      raw_end <- min(raw_end, nchar(text))
    }

    # Snap backward to the last sentence boundary within 200 chars of raw_end.
    # This is a gentle snap — we lose at most ~200 chars (1-2 sentences) to
    # avoid mid-sentence cutoffs, while keeping virtually all article content.
    lookback_size <- min(200, raw_end - my_pos - 50)
    if (lookback_size > 10) {
      lookback_start <- raw_end - lookback_size
      lookback_text <- str_sub(text, lookback_start, raw_end)

      # Find last sentence boundary: period/!/? followed by space/newline
      sent_boundaries <- str_locate_all(lookback_text,
        "[.!?]\\s+|[.!?]\\n|[.!?]$")[[1]]

      if (nrow(sent_boundaries) > 0) {
        last_sent <- sent_boundaries[nrow(sent_boundaries), 1]
        snapped_end <- lookback_start + last_sent  # include the period
        if (snapped_end > my_pos + 50) {
          article_ends[k] <- snapped_end
        } else {
          article_ends[k] <- raw_end
        }
      } else {
        article_ends[k] <- raw_end
      }
    } else {
      article_ends[k] <- raw_end
    }
  }

  # --- Extract and save articles ---
  saved_count <- 0

  if (length(valid_idx) > 0) {
    for (k in seq_along(valid_idx)) {
      i <- valid_idx[k]
      article_start <- positions[i]
      article_end <- article_ends[k]

      article_text <- str_sub(text, article_start, article_end)

      # Strip board text
      if (nchar(board_text) > 0) {
        article_text <- str_replace(article_text, fixed(board_text), "")
      }
      article_text <- str_replace(article_text,
        regex("THE GENERAL BOARD\\s+Mrs\\..*?(?:Salt Lake City,?\\s+Utah|Bishop'?s\\s+B[ul]i?lding|Room\\s+\\d+.*?Utah)",
              dotall = TRUE, ignore_case = TRUE), "")
      article_text <- str_replace(article_text,
        regex("GENERAL BOARD OF RELIEF SOCIETY.*?(?:Salt Lake City,?\\s+Utah|Bishop'?s\\s+B[ul]i?lding|Room\\s+\\d+.*?Utah|Vol\\.\\s+[IVX0-9]+)",
              dotall = TRUE, ignore_case = TRUE), "")
      article_text <- str_replace(article_text,
        regex("Entered as second[- ]class matter.*?(?:Salt Lake City,?\\s*Utah|Utah\\.)",
              dotall = TRUE, ignore_case = TRUE), "")
      article_text <- str_replace(article_text,
        regex("Motto\\s*[\u2014\u2013-]+\\s*Charity Never Faileth\\.?", ignore_case = TRUE), "")

      article_text <- clean_running_headers(article_text)
      article_text <- str_trim(article_text)

      if (nchar(article_text) < 5) next

      saved_count <- saved_count + 1

      category <- articles$category[i]
      clean_title <- safe_filename(articles$title[i])
      fname <- paste0(prefix, "_", sprintf("%02d", i), "_",
                      category, "_", clean_title, ".txt")
      write_file(article_text, file.path(month_folder, fname))
    }
  }

  cat(sprintf("\n  Saved: %d / %d articles\n", saved_count, nrow(articles)))

  # --- Coverage diagnostic: check for gaps between articles ---
  if (length(valid_idx) > 1) {
    sorted_ranges <- data.frame(
      idx = valid_idx,
      title = articles$title[valid_idx],
      start = positions[valid_idx],
      end = article_ends,
      stringsAsFactors = FALSE
    )
    sorted_ranges <- sorted_ranges[order(sorted_ranges$start), ]

    total_gap_chars <- 0
    for (g in 2:nrow(sorted_ranges)) {
      gap <- sorted_ranges$start[g] - sorted_ranges$end[g - 1] - 1
      if (gap > 200) {
        total_gap_chars <- total_gap_chars + gap
      }
    }
    body_coverage <- sum(sorted_ranges$end - sorted_ranges$start + 1)
    body_total <- body_end - body_start + 1
    pct <- round(100 * body_coverage / body_total, 1)
    if (total_gap_chars > 500) {
      cat(sprintf("  Coverage: %s%% of body (%d chars in gaps > 200)\n",
                  pct, total_gap_chars))
    } else {
      cat(sprintf("  Coverage: %s%% of body text\n", pct))
    }
  }

  # --- Build single MISC file: everything not captured in an article ---
  misc_parts <- c()

  # Front matter (cover, ads, contents, advertisers directory)
  front_ads_end <- if (!is.null(sections$front_ads_end)) sections$front_ads_end else 0
  if (front_ads_end > 10) {
    front_text <- str_trim(str_sub(text, 1, front_ads_end))
    if (nchar(front_text) > 50) {
      misc_parts <- c(misc_parts,
                      "========== FRONT MATTER ==========",
                      front_text)
    }
  }

  # Gaps between articles (uncovered body text)
  if (length(valid_idx) > 0) {
    all_ranges <- data.frame(
      start = positions[valid_idx],
      end   = article_ends,
      stringsAsFactors = FALSE)
    all_ranges <- all_ranges[order(all_ranges$start), ]

    gap_texts <- c()
    prev_end <- body_start - 1
    for (r in 1:nrow(all_ranges)) {
      gap_start <- prev_end + 1
      gap_end   <- all_ranges$start[r] - 1
      if (gap_end > gap_start && (gap_end - gap_start) > 50) {
        gap_text <- str_trim(str_sub(text, gap_start, gap_end))
        if (nchar(board_text) > 0) {
          gap_text <- str_replace(gap_text, fixed(board_text), "")
          gap_text <- str_trim(gap_text)
        }
        if (nchar(gap_text) > 50) {
          gap_texts <- c(gap_texts, gap_text)
        }
      }
      prev_end <- max(prev_end, all_ranges$end[r])
    }

    if (length(gap_texts) > 0) {
      gap_combined <- paste(gap_texts, collapse = "\n\n--- gap ---\n\n")
      misc_parts <- c(misc_parts,
                      "\n========== UNCOVERED TEXT ==========",
                      gap_combined)
    }

    # Back matter (everything after last article to end of file)
    back_start <- prev_end + 1
    if (back_start < nchar(text)) {
      back_text <- str_trim(str_sub(text, back_start, nchar(text)))
      if (nchar(back_text) > 50) {
        misc_parts <- c(misc_parts,
                        "\n========== BACK MATTER ==========",
                        back_text)
      }
    }
  } else {
    if (sections$ads_start < nchar(text)) {
      back_ads <- str_trim(str_sub(text, sections$ads_start, nchar(text)))
      if (nchar(back_ads) > 50) {
        misc_parts <- c(misc_parts,
                        "\n========== BACK MATTER ==========",
                        back_ads)
      }
    }
  }

  # Write single combined Misc file
  if (length(misc_parts) > 0) {
    misc_combined <- paste(misc_parts, collapse = "\n\n")
    write_file(misc_combined,
               file.path(month_folder, paste0(prefix, "_Misc.txt")))
    cat("  Misc file saved\n")
  } else {
    cat("  No misc content found\n")
  }

  # --- Diagnostic summary ---
  n_found <- sum(diag$status == "FOUND")
  n_missed <- sum(diag$status == "MISSED_SEARCH")
  n_absent <- sum(diag$status == "ABSENT_FROM_SOURCE")
  cat(sprintf("  Diagnostic: %d found, %d missed-search, %d absent-from-source\n",
              n_found, n_missed, n_absent))
  if (n_missed > 0) {
    missed <- diag[diag$status == "MISSED_SEARCH", ]
    for (mi in 1:nrow(missed)) {
      cat(sprintf("    MISSED: \"%s\" (p.%s) - %s\n",
                  missed$title[mi], missed$page[mi], missed$notes[mi]))
    }
  }
  if (n_absent > 0) {
    absent <- diag[diag$status == "ABSENT_FROM_SOURCE", ]
    for (ai in 1:nrow(absent)) {
      cat(sprintf("    ABSENT: \"%s\" (p.%s) - %s\n",
                  absent$title[ai], absent$page[ai], absent$notes[ai]))
    }
  }

  return(data.frame(
    file = filename,
    articles_found = nrow(articles),
    articles_saved = saved_count,
    missed_search = n_missed,
    absent_source = n_absent,
    total_chars = total_chars,
    stringsAsFactors = FALSE
  ))
}
```

# Main Execution

Process all issue files matching the configured volume filter.

```{r run, message=FALSE, warning=FALSE}
cat("Relief Society Magazine - Universal Article Extractor\n")
cat(rep("=", 70), "\n\n", sep = "")

# Discover input files (recurse into subdirectories like Vol9split, Vol10split)
input_files <- list.files(INPUT_DIR, pattern = "\\.txt$",
                          full.names = TRUE, recursive = TRUE)
input_files <- sort(input_files)

if (!is.null(PROCESS_VOLUMES)) {
  vol_pattern <- paste0("Vol(", paste(PROCESS_VOLUMES, collapse = "|"), ")[_]")
  input_files <- input_files[str_detect(basename(input_files), vol_pattern)]
}

cat("Found", length(input_files), "issue file(s)\n\n")

results <- list()
for (f in input_files) {
  result <- tryCatch(
    process_issue(f, OUTPUT_DIR),
    error = function(e) {
      cat("ERROR:", basename(f), "-", e$message, "\n")
      data.frame(file = basename(f), articles_found = 0, articles_saved = 0,
                 missed_search = 0, absent_source = 0,
                 total_chars = 0, stringsAsFactors = FALSE)
    }
  )
  results[[length(results) + 1]] <- result
}
```

# Results Summary

```{r summary}
results_df <- do.call(rbind, results)

cat("\n", rep("=", 70), "\n", sep = "")
cat("EXTRACTION COMPLETE\n")
cat(rep("=", 70), "\n\n", sep = "")

if (!is.null(results_df) && nrow(results_df) > 0) {
  print(results_df)

  cat(sprintf("\nFiles processed:      %d\n", nrow(results_df)))
  cat(sprintf("Articles in Contents: %d\n", sum(results_df$articles_found)))
  cat(sprintf("Articles saved:       %d\n", sum(results_df$articles_saved)))
  cat(sprintf("Missed (search fail): %d\n", sum(results_df$missed_search)))
  cat(sprintf("Absent from source:   %d\n", sum(results_df$absent_source)))

  hit_rate <- sum(results_df$articles_saved) /
    max(1, sum(results_df$articles_found)) * 100
  cat(sprintf("Hit rate:             %.1f%%\n", hit_rate))

  low <- results_df[results_df$articles_found > 0 &
                     results_df$articles_saved / results_df$articles_found < 0.7, ]
  if (nrow(low) > 0) {
    cat("\nIssues below 70% extraction:\n")
    print(low[, c("file", "articles_found", "articles_saved",
                   "missed_search", "absent_source")])
  }
}

cat("\nOutput:", OUTPUT_DIR, "\n")
```
