---
title: "Relief Society Magazine — Universal Article Extractor"
date: "`r Sys.Date()`"
output:
  html_notebook:
    toc: true
    toc_float: true
    theme: flatly
    code_folding: hide
---

```{r setup, message=FALSE, warning=FALSE}
for (pkg in c("stringr","readr","knitr","kableExtra")) {
  if (!requireNamespace(pkg, quietly=TRUE)) install.packages(pkg)
}
library(stringr); library(readr); library(knitr); library(kableExtra)

# ============================================================
# CONFIGURATION — update these paths to match your machine
# ============================================================
INPUT_DIRS <- c(
  "C:/Users/birch/OneDrive - George Mason University - O365 Production/Dissertation/textanalysis/Articleextractionrfiles/input/Vol21split"
)
OUTPUT_DIR <- "C:/Users/birch/OneDrive - George Mason University - O365 Production/Dissertation/textanalysis/Articleextractionrfiles/output"

if (!dir.exists(OUTPUT_DIR)) dir.create(OUTPUT_DIR, recursive=TRUE)
```

```{r helpers}
# ============================================================
# HELPERS
# ============================================================

read_file_safe <- function(path) {
  tryCatch(
    read_file(path, locale=locale(encoding="UTF-8")),
    error=function(e) read_file(path, locale=locale(encoding="windows-1252"))
  )
}

safe_filename <- function(title) {
  clean <- str_replace_all(title, "[<>:\"/\\\\|?*,;()\\[\\]\r\n\u2014\u2013'\u2018\u2019\u201c\u201d`]", "")
  clean <- str_replace_all(clean, "\\s+", "_")
  clean <- str_replace_all(clean, "_+", "_")
  clean <- str_trim(str_replace_all(clean, "^_+|_+$", ""))
  if (nchar(clean) == 0) clean <- "untitled"
  # Cap at 75 characters to stay safely within Windows 260-char path limit.
  # Calculation: typical folder path (~145) + separator (1) + file prefix (~31)
  # + title (75) + ".txt" (4) = 256 chars, safely below the 260-char limit.
  if (nchar(clean) > 75) clean <- str_sub(clean, 1, 75)
  clean <- str_replace(clean, "_+$", "")  # remove trailing underscore after truncation
  clean
}

get_significant_words <- function(title) {
  stops <- c("the","a","an","of","in","on","at","to","for","and","or","but","by",
             "its","is","are","was","were","be","been","our","her","his","my","we",
             "it","as","with","from","that","this","not","no","out","new","all",
             "how","what","who","when","where","why","can","may","will","shall",
             "has","had","have","does","did","do","about","into","upon")
  words <- str_split(title, "[\\s\u2014\u2013]+|\\s*-{2,}\\s*")[[1]]
  words <- words[nchar(words) > 2]
  words <- words[!tolower(words) %in% stops]
  words <- str_replace(words, "[?.!,;:]+$", "")
  words[nchar(words) > 0]
}

# Snap a found title position backward to the nearest paragraph break.
# Many article titles appear in the MIDDLE of a line (e.g., "By Author\nTitle\nText...")
# or after running headers.  Walking back to the nearest blank line gives the
# clean article start that includes any pre-title header / byline text.
# Looks back up to max_back chars; returns original pos if no break found.
snap_to_para_start <- function(text, pos, min_pos, max_back=600L) {
  if (pos <= min_pos) return(pos)
  lo  <- max(min_pos, pos - max_back)
  pre <- str_sub(text, lo, pos - 1L)

  # First choice: find the LAST double-newline (paragraph break) in the lookback window
  breaks <- str_locate_all(pre, "(\r?\n){2,}")[[1]]
  if (nrow(breaks) > 0L) {
    snap <- lo + breaks[nrow(breaks), 2]
    if (snap < pos) return(snap)
  }

  # Second choice: single newline (common in OCR where blank lines are missing)
  single_nl <- str_locate_all(pre, "\n")[[1]]
  if (nrow(single_nl) > 0L) {
    snap <- lo + single_nl[nrow(single_nl), 2]
    if (snap < pos) return(snap)
  }

  # Third choice: end of previous sentence within the last 150 chars only.
  # Handles run-together OCR text where articles flow on the same line, e.g.:
  # "...knew., Long years have passed then, dear, Evening By Merling Clyde Tis..."
  # Use a tight 150-char window to avoid snapping far back into the previous article.
  lo_tight <- max(min_pos, pos - 150L)
  pre_tight <- str_sub(text, lo_tight, pos - 1L)
  sent_ends <- str_locate_all(pre_tight, "[.!?][)'\",]?\\s+")[[1]]
  if (nrow(sent_ends) > 0L) {
    snap <- lo_tight + sent_ends[nrow(sent_ends), 2]
    if (snap < pos) return(snap)
  }

  # No good snap point found — return raw match position
  pos
}

classify_article <- function(title) {
  t <- tolower(title)
  if (str_detect(t, "^editorial|editorial[\\s\u2014\u2013-]")) return("Editorial")
  if (str_detect(t, "guide lesson"))                           return("Guide_Lessons")
  if (str_detect(t, "notes (from|to) the field"))             return("Notes_from_Field")
  if (str_detect(t, "home economics"))                        return("Home_Economics")
  if (str_detect(t, "home science"))                          return("Home_Science")
  if (str_detect(t, "current (topic|event)"))                 return("Current_Topics")
  if (str_detect(t, "home entertain"))                        return("Home_Entertainments")
  if (str_detect(t, "frontispiece"))                          return("Frontispiece")
  if (str_detect(t, "book notice"))                           return("Book_Notices")
  if (str_detect(t, "theological studies"))                   return("Lesson_Department")
  if (str_detect(t, "eliza roxey snow|poetry contest"))       return("Poetry_Contest")
  "Article"
}

get_metadata <- function(filename) {
  list(
    volume = str_extract(filename, "(?i)(?<=Vol)\\d+"),
    number = str_extract(filename, "(?i)(?<=No)\\d+"),
    month  = str_extract(filename, paste0(
      "(?i)(January|February|March|April|May|June|July|",
      "August|September|October|November|December)")),
    year   = str_extract(filename, "\\d{4}")
  )
}
```

```{r find-sections}
# ============================================================
# FIND SECTIONS
# Correctly locates:
#   contents_start / contents_text — the TOC listing
#   body_start — character position where article bodies begin
#                (AFTER the publication-info block, never before it)
#   board_start / board_end — the general board roster
#   body_end — last character of article content
#
# The key insight: the publication-info block
# ("Entered as second-class matter ... Phone Wasatch NNNN")
# marks the true boundary between the front matter/CONTENTS
# and the article body. body_start = position after this block
# plus the following VOL marker line.
# This prevents the CONTENTS listing from being searched for
# article titles, which caused fragments and wrong boundaries.
# ============================================================
find_sections <- function(text) {
  s   <- list()
  len <- nchar(text)

  # ---- CONTENTS keyword ----
  cp <- str_locate(text, regex("\\bCONTENTS\\b"))
  s$contents_start <- if (!is.na(cp[1,1])) cp[1,1] else NA_integer_

  # ---- Publication-info block ----
  # "Entered as second-class matter ... Phone Wasatch NNNN"
  # There may be two of these (one before CONTENTS in front ads, one at end of CONTENTS).
  # We want the LAST one that occurs before or near the end of the CONTENTS section.
  pub_pattern <- regex(
    "Entered as second[- ]class matter[\\s\\S]{0,400}(?:Phone\\s+Wasatch\\s+\\d+|Wasatch\\s+\\d+)",
    ignore_case=TRUE, dotall=TRUE)
  all_pub <- str_locate_all(text, pub_pattern)[[1]]

  # Find the pub block that is associated with the CONTENTS section
  # (closest one AT OR AFTER CONTENTS start, never before it)
  s$pub_end <- NA_integer_
  if (nrow(all_pub) > 0 && !is.na(s$contents_start)) {
    # Only accept pub blocks whose START is at or after (contents_start - 200)
    after <- all_pub[all_pub[,1] >= s$contents_start - 200, , drop=FALSE]
    if (nrow(after) > 0) {
      s$pub_end <- after[1, 2]
    }
    # Do NOT fall back to the last match overall: it may be in back-ads
    # far from CONTENTS, which corrupts pub_end and body_start.
  }

  # Safety: pub_end must be at or after contents_start.
  # If it landed before (e.g. front-ad block just before CONTENTS), reset to NA
  # so the fallback loop below can find the correct marker after CONTENTS.
  if (!is.na(s$pub_end) && !is.na(s$contents_start) &&
      s$pub_end < s$contents_start) {
    s$pub_end <- NA_integer_
  }

  # Fallback pub-end markers — always filtered to >= contents_start AND within 6000 chars
  # The 6000-char window prevents back-ads occurrences from being picked up.
  if (is.na(s$pub_end)) {
    for (pat in c("Phone\\s+Wasatch\\s+\\d+", "\\$1\\.00\\s+a\\s+Year[^\\n]{0,60}Single Copy",
                  "Organ\\s+of\\s+the\\s+Relief\\s+Society")) {
      m <- str_locate_all(text, regex(pat, ignore_case=TRUE))[[1]]
      if (nrow(m) > 0 && !is.na(s$contents_start)) {
        after <- m[m[,1] >= s$contents_start &
                   m[,1] <  s$contents_start + 6000L, , drop=FALSE]
        if (nrow(after) > 0) { s$pub_end <- after[1,2]; break }
      }
    }
  }

  # ---- CONTENTS text ----
  # From CONTENTS keyword to pub_end.
  # Clamp to max 5000 chars to prevent runaway if pub_end detection fails.
  s$contents_text <- NULL
  if (!is.na(s$contents_start)) {
    # Hard cap: CONTENTS section should never be more than 5000 chars
    hard_cap <- min(s$contents_start + 5000L, len)
    end_of_contents <- if (!is.na(s$pub_end) && s$pub_end < hard_cap) s$pub_end else hard_cap

    # Additional safety: if we can find "Organ of the Relief Society" before hard_cap, use that
    organ_m <- str_locate(
      str_sub(text, s$contents_start, hard_cap),
      regex("Organ\\s+of\\s+the\\s+Relief\\s+Society", ignore_case=TRUE))
    if (!is.na(organ_m[1,1])) {
      organ_abs <- s$contents_start + organ_m[1,1] - 1L
      if (organ_abs < end_of_contents) end_of_contents <- organ_abs
    }

    s$contents_end  <- end_of_contents
    s$contents_text <- str_sub(text, s$contents_start, s$contents_end)
  } else {
    s$contents_end <- NA_integer_
  }

  # ---- BODY START ----
  # Find the VOL. N MONTH, YEAR No. N masthead line that separates the
  # front-matter (subscription info, pub block) from the first article.
  # body_start = character AFTER the end of that VOL line.
  #
  # Problem solved here: some split files have their CONTENTS section starting
  # late (e.g. at char 2425), so contents_end can be as late as char 7425.
  # If we only search AFTER contents_end, we miss the VOL marker that sits
  # between the CONTENTS text and the first article (e.g. at char 3595).
  # Fix: search the entire first 12,000 chars of the file for ALL occurrences
  # of the VOL pattern, then pick the LAST one that is followed by article text
  # (not by another pub/masthead block).  This reliably finds the final 
  # "VOL. XVI MARCH, 1929 No. 3" line that immediately precedes the first article,
  # even when the same line appears twice (once in the CONTENTS block, once after).
  s$body_start <- NA_integer_

  # Primary VOL pattern: requires "No. N" at the end (standard masthead format)
  # e.g. "VOL. XVI MARCH, 1929 No. 3"
  vol_pat <- regex(
    "VOL\\.?\\s*(?:[IVXL]+|\\d+)\\.?[^\\n]{0,25}(?:JANUARY|FEBRUARY|MARCH|APRIL|MAY|JUNE|JULY|AUGUST|SEPTEMBER|OCTOBER|NOVEMBER|DECEMBER)[^\\n]{0,30}No\\.?\\s*\\d+",
    ignore_case=TRUE)

  # Fallback VOL pattern: handles OCR-corrupted "No." (e.g. "= a" instead of "No. 9")
  # This is looser — just VOL + Roman/Arabic + Month + Year — to find the masthead line
  # even when the issue number is garbled.
  vol_pat_loose <- regex(
    "VOL\\.?\\s*(?:[IVXL]+|\\d+)\\.?[^\\n]{0,25}(?:JANUARY|FEBRUARY|MARCH|APRIL|MAY|JUNE|JULY|AUGUST|SEPTEMBER|OCTOBER|NOVEMBER|DECEMBER)[^\\n]{0,15}(?:19|18)\\d\\d",
    ignore_case=TRUE)

  # Search across the first 30,000 chars (covers all known split-file layouts,
  # including issues where CONTENTS starts late or the VOL marker is far from file start)
  wide_chunk   <- str_sub(text, 1L, min(30000L, len))
  vol_m_strict <- str_locate_all(wide_chunk, vol_pat)[[1]]
  vol_m_loose  <- str_locate_all(wide_chunk, vol_pat_loose)[[1]]
  # Run BOTH patterns and combine.  An early garbled-OCR masthead (e.g. "= a" instead of
  # "No. 9") is caught by the loose pattern even when the strict pattern also matches a
  # later, clean copy of the same line.  Combining and sorting by position then picking
  # the FIRST match after CONTENTS correctly sets body_start to just after the masthead.
  all_vol_m <- rbind(vol_m_strict, vol_m_loose)
  if (nrow(all_vol_m) > 0) {
    all_vol_m <- all_vol_m[!duplicated(all_vol_m[, 1L]), , drop=FALSE]
    all_vol_m <- all_vol_m[order(all_vol_m[, 1L]), , drop=FALSE]
  }

  s$vol_marker_found <- FALSE   # TRUE when body_start set from a reliable VOL marker

  if (nrow(all_vol_m) > 0) {
    # Use the FIRST occurrence AFTER the CONTENTS section start.
    # Rationale: the masthead VOL line appears in the front matter, immediately after
    # the CONTENTS + publication block. In some issues (Sep16, Sep17) the masthead
    # is followed by article content WITH NO NEWLINE — all in one giant text blob.
    # Later in that blob, running-header copies of the VOL line appear (e.g. at pg edges).
    # Using the LAST occurrence would pick a running header mid-article, setting body_start
    # too late and skipping 3–4 early articles. Using the FIRST occurrence after CONTENTS
    # reliably picks the masthead, placing body_start right at the article content start.
    contents_start_for_vol <- if (!is.na(s$contents_start)) s$contents_start else 0L
    # Filter to matches after CONTENTS start; fall back to all matches if none qualify
    after_contents <- all_vol_m[all_vol_m[,1] > contents_start_for_vol, , drop=FALSE]
    target_row  <- if (nrow(after_contents) > 0) 1L else 1L  # first qualifying
    target_m    <- if (nrow(after_contents) > 0) after_contents else all_vol_m
    vol_end_rel <- target_m[target_row, 2]
    # Advance past the rest of that line, but cap at 300 chars.
    # Rationale: in some OCR files the VOL masthead line runs directly into article
    # content with no newline for thousands of characters (e.g. Sep16, Sep17).
    # If we naively seek the next \n we skip over all those articles.
    # Capping at 300 chars ensures body_start lands just after the masthead marker,
    # right at the beginning of article content.
    tail_chunk  <- str_sub(wide_chunk, vol_end_rel + 1L, vol_end_rel + 300L)
    line_end_m  <- str_locate(tail_chunk, "\n")
    extra       <- if (!is.na(line_end_m[1,1])) line_end_m[1,1] else 0L
    s$body_start       <- vol_end_rel + extra
    s$vol_marker_found <- TRUE
  }

  # Fallback: if no VOL marker found anywhere, start right after the CONTENTS block
  if (is.na(s$body_start) || s$body_start < 1L) {
    s$body_start <- if (!is.na(s$contents_end)) s$contents_end + 1L
                    else if (!is.na(s$pub_end))  s$pub_end + 1L
                    else 1L
  }

  # ---- BOARD section ----
  board_pats <- c(
    "PRESIDENCY\\s+AND\\s+GENERAL\\s+BOARD(?:\\s+OF(?:\\s+THE)?)?\\s+RELIEF",
    "GENERAL\\s+BOARD\\s+(?:RELIEF|OF\\s+(?:THE\\s+)?RELIEF|MRS\\.)",
    "THE\\s+GENERAL\\s+BOARD[,.]?\\s+(?:MRS\\.|Mrs\\.)"
  )
  s$board_start <- NA_integer_
  s$board_end   <- NA_integer_
  for (bp in board_pats) {
    m <- str_locate(text, regex(bp, ignore_case=TRUE))
    if (!is.na(m[1,1])) { s$board_start <- m[1,1]; break }
  }
  if (!is.na(s$board_start)) {
    bc <- str_sub(text, s$board_start, min(s$board_start + 3000L, len))
    for (ep in c("Room\\s+\\d+[^\\n]{0,50}(?:Bishop|Building|Utah)",
                 "Bishop'?s?\\s+Buil", "Music\\s+Director",
                 "\\$1\\.00\\s+a\\s+Year")) {
      em <- str_locate_all(bc, regex(ep, ignore_case=TRUE))[[1]]
      if (nrow(em) > 0) { s$board_end <- s$board_start + em[nrow(em),2]; break }
    }
    if (is.na(s$board_end)) s$board_end <- min(s$board_start + 2000L, len)
  }

  # ---- BODY END (start of back ads) ----
  # Search last 30% for back-ad markers
  ads_from   <- as.integer(len * 0.70)
  ads_chunk  <- str_sub(text, ads_from, len)
  s$body_end <- len
  for (ap in c("ADVERTISERS'?\\s+(?:DIRECTORY|INDEX)",
                "INDEX\\s+TO\\s+ADVERTISERS",
                "PATRONIZE\\s+OUR\\s+ADVERTISERS")) {
    m <- str_locate(ads_chunk, regex(ap, ignore_case=TRUE))
    if (!is.na(m[1,1])) { s$body_end <- ads_from + m[1,1] - 1L; break }
  }

  return(s)
}
```

```{r parse-contents}
# ============================================================
# CONTENTS PARSER
# Handles both line-by-line and single-line collapsed CONTENTS.
# Strips dot leaders, page numbers, trailing author attributions.
# Returns data.frame(title, page, category)
# ============================================================
parse_contents_section <- function(contents_text) {
  empty <- data.frame(title=character(), page=integer(), category=character(),
                      stringsAsFactors=FALSE)
  if (is.null(contents_text) || nchar(str_trim(contents_text)) == 0) return(empty)

  ct <- str_replace_all(contents_text, "\r\n|\r", "\n")
  ct <- str_replace_all(ct, regex("Here is the corrected OCR.*?:\\s*",
                                   ignore_case=TRUE), "")
  ct <- str_replace_all(ct, "\\*\\*Page\\*\\*", "")

  # Always apply inline expansion to split embedded "NNN Title" within long lines.
  # This covers single-line CONTENTS and partially-collapsed formats.
  ct_exp <- str_replace_all(ct, "\\.{2,}", " ")
  ct_exp <- str_replace_all(ct_exp, "\\s{2,}", " ")
  # Split on "page_number SPACE Capital" -- matches single-letter words too (A, I)
  ct_exp <- str_replace_all(ct_exp, "(\\d{1,4})\\s{1,3}([A-Z\"])", "\\1\n\\2")
  lines  <- str_split(ct_exp, "\n")[[1]]
  lines  <- lines[nchar(str_trim(lines)) > 0]

  arts <- parse_linebased(lines)

  if (nrow(arts) > 0) {
    arts <- arts[!duplicated(arts$title), ]
    arts <- arts[order(arts$page), ]
    arts$category <- sapply(arts$title, classify_article)
  }
  arts
}

parse_linebased <- function(lines) {
  arts    <- data.frame(title=character(), page=integer(), stringsAsFactors=FALSE)
  pending <- ""
  skip    <- regex(
    "^(CONTENTS?|ADVERTISERS?|Page\\s*$|\\*\\*|(THE\\s+)?RELIEF\\s+SOCIETY|Vol\\.?\\s*[IVXL0-9]|Organ\\s+of\\s+the)",
    ignore_case=TRUE)

  # Strip "By Firstname [Middle] Lastname..." suffix from a CONTENTS title string.
  # Only removes explicit "By Author" attribution — bare trailing names (without "By")
  # are left in place. The S10 author-proximity strategy handles those cases:
  # it extracts the last word of the title as a candidate author last name and
  # searches for "By LastName" proximity in the body text.
  strip_author <- function(t) {
    t <- str_trim(str_replace(t,
      regex("\\s+[Bb]y\\s+[A-Z][a-zA-Z.,'\u2014\u2013 -]{2,}$"), ""))
    str_trim(t)
  }

  for (ln in lines) {
    ln <- str_trim(ln)
    ln <- str_trim(str_replace(ln, "^\\*+\\s*", ""))   # strip leading * OCR artifacts
    if (nchar(ln) < 2 || str_detect(ln, skip)) next

    clean <- str_trim(str_replace_all(ln, "\\s{2,}", " "))

    # Special case: line contains "Frontispiece" in the MIDDLE followed by a page number
    # e.g. "Portrait of Mrs. X Frontispiece Emily Sophia Richards 521"
    # -> two entries: (Portrait... Frontispiece, pg=0) and (Emily Sophia Richards, pg=521)
    front_mid <- str_match(clean,
      "^(.+?)\\s+[Ff]rontispiece\\s+(.+?)\\s+(\\d{1,4})\\s*$")
    if (!is.na(front_mid[1,1])) {
      bef <- str_trim(strip_author(front_mid[1,2]))
      aft <- str_trim(strip_author(front_mid[1,3]))
      pg_val <- suppressWarnings(as.integer(front_mid[1,4]))
      if (nchar(bef) >= 2)
        arts <- rbind(arts, data.frame(title=paste(bef,"Frontispiece"),
                                       page=0L, stringsAsFactors=FALSE))
      if (nchar(aft) >= 2 && !is.na(pg_val) && pg_val >= 1)
        arts <- rbind(arts, data.frame(title=aft, page=pg_val,
                                       stringsAsFactors=FALSE))
      pending <- ""
      next
    }

    pg_m <- str_match(clean, "\\s+(\\d{1,4})\\s*$")

    if (is.na(pg_m[1,1])) {
      if (str_detect(clean, regex("Frontispiece", ignore_case=TRUE))) {
        full <- if (nchar(pending) > 0 && nchar(pending) < 60) paste(pending, clean) else clean
        full <- strip_author(full)
        arts <- rbind(arts, data.frame(title=str_trim(full), page=0L,
                                       stringsAsFactors=FALSE))
        pending <- ""
      } else if (nchar(clean) > 1 && !str_detect(clean, "^\\d+$")) {
        is_continuation <- nchar(pending) > 0 && nchar(pending) < 60 &&
          (str_detect(clean, "^[a-z]") ||
           str_detect(clean, "^(By |by )") ||
           (nchar(clean) < 40 && str_detect(clean, "^[A-Z][a-z]")))
        pending <- if (nchar(pending) == 0) clean
                   else if (is_continuation) paste(pending, clean)
                   else clean
      }
      next
    }

    pg <- suppressWarnings(as.integer(pg_m[1,2]))
    if (is.na(pg) || pg < 1 || pg > 2000) next

    title <- str_trim(str_replace(clean, "\\s+\\d{1,4}\\s*$", ""))
    title <- strip_author(title)
    title <- str_trim(str_replace_all(title, "\\s{2,}", " "))
    if (nchar(title) < 2 || str_detect(title, "^\\d+$")) { pending <- ""; next }

    if (nchar(pending) > 0 && nchar(pending) < 60)
      title <- paste(pending, title)
    pending <- ""
    arts <- rbind(arts, data.frame(title=str_trim(title), page=pg,
                                   stringsAsFactors=FALSE))
  }
  arts
}
```

```{r page-index}
# ============================================================
# PAGE INDEX
# Maps page numbers to character positions within body text.
# Used only to narrow search windows; not required for correctness.
# ============================================================
build_page_index <- function(body_text, body_offset) {
  pages <- data.frame(page=integer(), position=integer(), stringsAsFactors=FALSE)

  even_m <- str_locate_all(body_text,
    regex("(\\d{1,3})\\s+(?:THE\\s+)?RELIEF\\s+SOCIETY\\s+MAGAZINE\\.?",
          ignore_case=FALSE))[[1]]
  if (nrow(even_m) > 0) {
    for (i in seq_len(nrow(even_m))) {
      chunk <- str_sub(body_text, even_m[i,1], even_m[i,2])
      pg    <- suppressWarnings(as.integer(str_extract(chunk, "^\\d+")))
      if (!is.na(pg) && pg >= 1 && pg <= 999)
        pages <- rbind(pages, data.frame(page=pg,
          position=even_m[i,1] + body_offset - 1L, stringsAsFactors=FALSE))
    }
  }

  if (nrow(pages) > 2) {
    keep <- rep(TRUE, nrow(pages))
    for (i in 2:(nrow(pages)-1)) {
      if (pages$page[i] < pages$page[i-1] - 5 ||
          pages$page[i] > pages$page[i+1] + 5) keep[i] <- FALSE
    }
    pages <- pages[keep, ]
  }
  pages[!duplicated(pages$page), ]
}

page_to_pos <- function(pi, pg, lo, hi) {
  if (nrow(pi)==0) return(lo)
  ex <- pi[pi$page==pg, ]
  if (nrow(ex)>0) return(ex$position[1])
  bef <- pi[pi$page < pg, ]
  aft <- pi[pi$page > pg, ]
  CPP <- 2400L
  if (nrow(bef)>0 && nrow(aft)>0) {
    b <- bef[nrow(bef),]; a <- aft[1,]
    frac <- (pg - b$page) / (a$page - b$page)
    return(as.integer(b$position + frac*(a$position - b$position)))
  }
  if (nrow(bef)>0) return(as.integer(bef$position[nrow(bef)] + (pg - bef$page[nrow(bef)]) * CPP))
  if (nrow(aft)>0) return(max(lo, as.integer(aft$position[1]  - (aft$page[1]  - pg) * CPP)))
  lo
}
```

```{r title-finder}
# ============================================================
# TITLE FINDER
# Searches for a title string within a character window.
# Tries six strategies in order, from exact to fuzzy.
# Returns the absolute character position in the full text,
# or NA if not found.
#
# IMPORTANT: callers always pass window = [body_start, body_end]
# so the CONTENTS listing is never searched.
# ============================================================
find_in_window <- function(text, title, w_start, w_end, allow_s10 = TRUE,
                           require_para_start = FALSE) {
  if (w_start >= w_end || nchar(str_trim(title)) == 0) return(NA_integer_)
  chunk <- str_sub(text, w_start, w_end)

  # Normalise em-dashes and en-dashes to plain hyphen for matching
  title <- str_replace_all(title, "\u2014|\u2013|---?", "-")
  # Drop Frontispiece suffix (handled separately)
  title <- str_trim(str_replace(title,
    regex("\\s+Frontispiece\\s*$", ignore_case=TRUE), ""))

  try_pat <- function(pat) {
    m <- tryCatch(str_locate(chunk, regex(pat, ignore_case=TRUE)),
                  error=function(e) matrix(NA_integer_,1,2))
    if (!is.na(m[1,1])) return(w_start + m[1,1] - 1L)
    NA_integer_
  }

  # Variant of try_pat that requires the match to be at a paragraph/line start.
  # Used for Strategy 11 proximity matches when no page_index is available,
  # to prevent matching title/author words inside the body of a previous article.
  try_pat_para <- function(pat) {
    pos <- try_pat(pat)
    if (is.na(pos)) return(NA_integer_)
    # Check that the character immediately before the match is a newline or start-of-body
    if (pos <= w_start) return(pos)   # at start of window = OK
    preceding <- str_sub(text, max(1L, pos - 2L), pos - 1L)
    if (str_detect(preceding, "\n")) return(pos)
    NA_integer_   # match is inside a line, not at paragraph start → reject
  }

  esc <- function(s) str_replace_all(s, "([.?*+^$\\[\\]\\\\(){}|])", "\\\\\\1")

  # 1. Exact match
  pos <- try_pat(esc(title)); if (!is.na(pos)) return(pos)

  # 2. Whitespace flexible
  pos <- try_pat(str_replace_all(esc(title), "\\s+", "\\\\s+"))
  if (!is.na(pos)) return(pos)

  # 3. Dash flexible (plain - or em/en dash)
  df  <- str_replace_all(esc(title), "[-\u2014\u2013]", "[-\u2014\u2013]+")
  df  <- str_replace_all(df, "\\s+", "\\\\s+")
  pos <- try_pat(df); if (!is.na(pos)) return(pos)

  # 4. Drop intra-word hyphens
  nh <- str_replace_all(title, "(?<=[a-zA-Z])-(?=[a-zA-Z])", "")
  if (nh != title) {
    pos <- try_pat(str_replace_all(esc(nh), "\\s+", "\\\\s+"))
    if (!is.na(pos)) return(pos)
  }

  # 5. EDITORIAL special case
  # Body format: "EDITORIAL\nThe Bright New Year"  (two separate lines)
  # CONTENTS produces: "EditorialThe Bright New Year" (merged, dash stripped)
  # Strategy: if title starts with "Editorial", search for EDITORIAL + subtitle words
  if (str_detect(title, regex("^Editorial", ignore_case=TRUE))) {
    subtitle <- str_trim(str_replace(title, regex("^Editorial[-: ]*", ignore_case=TRUE), ""))
    sub_words <- str_split(subtitle, "\\s+")[[1]]
    sub_words <- sub_words[nchar(sub_words) > 2]
    if (length(sub_words) >= 1) {
      # Search for EDITORIAL followed by the first significant word within ~200 chars
      ed_pat <- paste0("EDITORIAL[\\s\\S]{0,200}\\b",
                       esc(sub_words[1]), "\\b")
      pos <- try_pat(ed_pat)
      if (!is.na(pos)) return(pos)
    }
    # Fallback: just find EDITORIAL itself (there's usually only one per issue)
    pos <- try_pat("EDITORIAL\\b")
    if (!is.na(pos)) return(pos)
  }

  # 6. PORTRAIT special case
  # Portrait pages are image-only; body may contain only the person's name as a caption.
  # Search for the name AFTER stripping "Portrait of" / "Mrs." / "Miss" / "Dr."
  if (str_detect(title, regex("^(?:Portrait|Frontispiece Portrait)", ignore_case=TRUE))) {
    name <- str_replace(title, regex("^(?:Frontispiece\\s+)?Portrait\\s+of\\s+", ignore_case=TRUE), "")
    name <- str_replace(name, regex("^(?:Mrs?|Miss|Dr)\\.?\\s+", ignore_case=TRUE), "")
    name <- str_trim(name)
    if (nchar(name) >= 4) {
      pos <- try_pat(str_replace_all(esc(name), "\\s+", "\\\\s+"))
      if (!is.na(pos)) return(pos)
      # Try just the last name
      last <- str_extract(name, "[A-Z][a-z]+$")
      if (!is.na(last) && nchar(last) >= 4) {
        pos <- try_pat(paste0("\\b", esc(last), "\\b"))
        if (!is.na(pos)) return(pos)
      }
    }
  }

  # 7. Title contains em-dash subtitle: search only part BEFORE the dash
  # e.g. "Nature in the Raw-Snake River" -> search "Nature in the Raw"
  if (str_detect(title, "-")) {
    before_dash <- str_trim(str_split(title, "-")[[1]][1])
    if (nchar(before_dash) >= 4 && before_dash != title) {
      pos <- try_pat(str_replace_all(esc(before_dash), "\\s+", "\\\\s+"))
      if (!is.na(pos)) return(pos)
    }
  }

  # 8. Strip leading/trailing honorifics (Pres., Dr., Mrs., Mr.)
  cleaned <- str_trim(str_replace(title,
    regex("^(?:Pres\\.|Dr\\.|Mrs?\\.|Prof\\.)\\s+"), ""))
  if (cleaned != title && nchar(cleaned) >= 4) {
    pos <- try_pat(str_replace_all(esc(cleaned), "\\s+", "\\\\s+"))
    if (!is.na(pos)) return(pos)
  }

  # 9. Significant-word proximity (most permissive, run last)
  sigs <- get_significant_words(title)
  if (length(sigs) >= 2) {
    for (n in c(min(length(sigs),4), min(length(sigs),3), 2)) {
      if (n > length(sigs)) next
      pat <- paste(
        sapply(sigs[seq_len(n)], function(w) paste0("\\b", esc(w), "\\b")),
        collapse=".{0,80}")
      pos <- try_pat(pat)
      if (!is.na(pos)) return(pos)
    }
  }

  # 9b. Plural/singular normalization
  # OCR CONTENTS entries sometimes differ in number from the body heading:
  # e.g. CONTENTS has "Thoroughbreds" but body heading reads "Thoroughbred".
  # Try dropping a trailing 's' from each significant word that ends in 's'.
  if (length(sigs) >= 1) {
    sigs_norm <- sapply(sigs, function(w)
      if (str_detect(w, "s$") && nchar(w) > 4) str_sub(w, 1, nchar(w)-1L) else w)
    if (!identical(sigs, sigs_norm)) {
      for (n in c(min(length(sigs_norm),4), min(length(sigs_norm),3), 2)) {
        if (n > length(sigs_norm)) next
        pat <- paste(
          sapply(sigs_norm[seq_len(n)], function(w) paste0("\\b", esc(w), "\\b")),
          collapse=".{0,80}")
        pos <- try_pat(pat)
        if (!is.na(pos)) return(pos)
      }
    }
  }

  # 10. Author-name search
  # Normally only runs when allow_s10=TRUE (narrow/wide windows), because on full-body
  # fallback it risks false-positive matches far from the article's true position.
  # EXCEPTION: allow S10 on full-body when the title contains an embedded author name
  # (trailing capitalized words that look like a personal name suffix).
  # e.g. "Love's Recompense Grace Jacobson" — body has "Love's Recompense By Mrs. Grace Jacobson"
  # S1-S9 all fail because the title form ≠ body form. S10 finds it by author-name proximity.
  # The plausibility guard in the caller (|pos - pg_est| ≤ tolerance) prevents far-off matches.
  author_m_check <- str_match(title,
    "^(.{3,40}?)\\s+([A-Z][a-zA-Z.]+(?:\\s+[A-Z][a-zA-Z.]*){1,3})$")
  has_embedded_author <- !is.na(author_m_check[1,1])
  if (!allow_s10 && !has_embedded_author) return(NA_integer_)
  #
  # Many CONTENTS entries embed the author after the title:
  #   "One Sunrise Elsie E. Barrett"  -> title "One Sunrise" + author "Elsie E. Barrett"
  #   "A Tribute Annie Wells Cannon"  -> title "A Tribute"   + author "Annie Wells Cannon"
  # In the article body, the author appears on a byline: "By Elsie E. Barrett"
  # This strategy extracts a candidate author from the trailing capitalized-name
  # suffix of the title and searches for it (with and without "By").
  #
  # Guard: Portrait titles already have strategy 6 (name extraction after "Portrait of").
  # Running strategy 10 on them confuses the portrait subject for an author byline,
  # causing false matches when the person's name appears elsewhere in the body.
  if (str_detect(title, regex("^Portrait", ignore_case = TRUE))) return(NA_integer_)
  #
  # Candidate author: 2-3 trailing words that are ALL Title-Case or UPPER (names),
  # preceded by a single-word or short title part.
  author_m <- str_match(title,
    "^(.{3,40}?)\\s+([A-Z][a-zA-Z.]+(?:\\s+[A-Z][a-zA-Z.]*){1,3})$")
  if (!is.na(author_m[1,1])) {
    title_part <- str_trim(author_m[1,2])   # e.g. "One Sunrise"
    author_str <- str_trim(author_m[1,3])   # e.g. "Elsie E. Barrett"
    last_name  <- str_extract(author_str, "[A-Za-z]+$")   # e.g. "Barrett"

    # Safety guard: author_str must look like a real personal name.
    # Require the LAST word (surname) to be >= 4 chars (rules out "Men", "Cox", "Wu").
    # 4-char surnames like Lund, Lind, Done, Reed, Page are common in these texts.
    is_valid_author <- !is.na(last_name) && nchar(last_name) >= 4

    # Guard for 10a/10b: only search by author name when title_part has at least
    # one significant word >= 5 chars. (Lowered from 6 to catch titles like
    # "A Song for New Years" where "Years"=5, "Winter Grass" where "Grass"=5.)
    tp_sigs      <- get_significant_words(title_part)
    tp_long_sigs <- tp_sigs[nchar(tp_sigs) >= 5]
    author_search_safe <- length(tp_long_sigs) >= 1

    if (is_valid_author) {
      # 10a. "By <full author>" in body (e.g. "By Elsie E. Barrett")
      if (author_search_safe) {
        pos <- try_pat(paste0("[Bb]y\\s+[A-Z][a-zA-Z.]+(?:\\s+[A-Z.]+){0,2}\\s+",
                              esc(last_name), "\\b"))
        if (!is.na(pos)) return(pos)
      }

      # 10b. Full author string (handles "Elsie E. Barrett" or "Annie Wells Cannon")
      if (author_search_safe) {
        pos <- try_pat(str_replace_all(esc(author_str), "\\s+", "\\\\s+"))
        if (!is.na(pos)) return(pos)
      }

      # 10c. Just the title part — only when title_part has >= 2 sig words >= 5 chars each,
      # or one sig word >= 8 chars.  Short/common title parts match too many places.
      tp_long5 <- tp_sigs[nchar(tp_sigs) >= 5]
      tp_long8 <- tp_sigs[nchar(tp_sigs) >= 8]
      title_search_safe <- length(tp_long5) >= 2 || length(tp_long8) >= 1
      if (title_search_safe && title_part != title) {
        pos <- try_pat(str_replace_all(esc(title_part), "\\s+", "\\\\s+"))
        if (!is.na(pos)) return(pos)
      }

      # 10d. Title sig word + last-name proximity (first sig word only, forward)
      if (author_search_safe && length(tp_sigs) >= 1) {
        pos <- try_pat(paste0("\\b", esc(tp_sigs[1]), "\\b.{0,200}\\b",
                              esc(last_name), "\\b"))
        if (!is.na(pos)) return(pos)
      }

      # 11. Combined title+author proximity — ALL sig words tried in both directions.
      # This is the "title separated from author by minimal words" strategy.
      # The article heading and byline may appear on adjacent lines:
      #   TITLE WORDS                     ← article heading line
      #   By Author Name                  ← byline line (already caught by 10a)
      # OR they may appear separately in running text.
      # Strategy 11 tries every sig word paired with the last name, forward AND reverse,
      # with a generous gap allowance. Requires sig word >= 4 chars to reduce noise.
      # Reverse direction (last_name before sig_word) catches cases where author
      # attribution appears above the title (e.g. photo captions or section headers).
      # When require_para_start=TRUE (no page_index files), the match must begin at
      # a line/paragraph start to prevent false matches inside article body text.
      tp_fn <- if (require_para_start) try_pat_para else try_pat
      for (sw in tp_sigs[nchar(tp_sigs) >= 4]) {
        # Forward: title word appears first, then author last name
        pos <- tp_fn(paste0("\\b", esc(sw), "\\b.{0,400}\\b", esc(last_name), "\\b"))
        if (!is.na(pos)) return(pos)
        # Reverse: author last name appears first, then title word (within ~2 lines)
        pos <- tp_fn(paste0("\\b", esc(last_name), "\\b.{0,120}\\b", esc(sw), "\\b"))
        if (!is.na(pos)) return(pos)
      }
    }
  }

  NA_integer_
}
# Page-guided search: narrow -> wide -> full body with plausibility guard
# Strategy 10 (author-name search) runs in all windows but full-body results
# are validated against the page estimate to prevent false positives.
find_article_start <- function(text, title, pg, page_index, body_start, body_end) {
  CPP <- 2400L

  # Full-body search if page index too small (no page estimate to validate against)
  if (nrow(page_index) < 3)
    return(find_in_window(text, title, body_start, body_end, allow_s10=TRUE))

  pg_est <- page_to_pos(page_index, pg, body_start, body_end)

  # Narrow (±2 pages) — S10 allowed, bounded window
  s1 <- max(body_start, page_to_pos(page_index, max(1L,pg-2L), body_start, body_end) - CPP)
  e1 <- min(body_end,   page_to_pos(page_index, pg+3L,         body_start, body_end) + CPP)
  pos <- find_in_window(text, title, s1, e1, allow_s10=TRUE)
  if (!is.na(pos)) return(pos)

  # Wide (±5 pages) — S10 allowed, bounded window
  s2 <- max(body_start, page_to_pos(page_index, max(1L,pg-5L), body_start, body_end) - CPP*2L)
  e2 <- min(body_end,   page_to_pos(page_index, pg+6L,         body_start, body_end) + CPP*2L)
  pos <- find_in_window(text, title, s2, e2, allow_s10=TRUE)
  if (!is.na(pos)) return(pos)

  # Full-body — S10 allowed but result validated against page estimate
  pos_fb <- find_in_window(text, title, body_start, body_end, allow_s10=TRUE)
  if (!is.na(pos_fb) && (is.na(pg_est) || abs(pos_fb - pg_est) <= 25000L))
    return(pos_fb)
  NA_integer_
}
```

```{r header-cleaner}
# ============================================================
# RUNNING HEADER CLEANER
# Removes OCR-embedded running headers from extracted article text.
# ============================================================
clean_headers <- function(txt) {
  # "N RELIEF SOCIETY MAGAZINE" even-page headers
  txt <- str_replace_all(txt,
    regex("\\d{1,3}\\s+(?:THE\\s+)?RELIEF\\s+SOCIETY\\s+MAGAZINE\\.?"), " ")
  # "RELIEF SOCIETY MAGAZINE N" reversed
  txt <- str_replace_all(txt,
    regex("(?:THE\\s+)?RELIEF\\s+SOCIETY\\s+MAGAZINE\\.?\\s+\\d{1,3}"), " ")
  # "THE Relief Society Magazine Vol. N No. N" mixed-case body header
  txt <- str_replace_all(txt,
    regex("THE\\s+Relief\\s+Society\\s+Magazine\\s+VOL\\.?\\s+[IVXL0-9]+[^\\n]{0,40}No\\.?\\s+\\d+",
          ignore_case=FALSE), " ")
  # "RELIEF SOCIETY CONFERENCE NNN" running head (conference issue)
  txt <- str_replace_all(txt,
    regex("RELIEF\\s+SOCIETY\\s+CONFERENCE\\s+\\d{1,4}"), " ")
  # Board roster block
  txt <- str_replace_all(txt,
    regex("(?:PRESIDENCY\\s+AND\\s+)?GENERAL\\s+BOARD[^\\n]{0,200}(?:Salt Lake City|Bishop.*?Building|Room\\s+\\d+|Music Director)",
          dotall=TRUE, ignore_case=TRUE), " ")
  # Collapse extra whitespace but preserve paragraph breaks
  txt <- str_replace_all(txt, "[ \\t]{3,}", "  ")
  str_trim(txt)
}
```

```{r process-issue}
# ============================================================
# PROCESS ISSUE
# Core function: reads one split-issue .txt file and extracts
# one text file per article.
#
# ARTICLE BOUNDARY LOGIC:
# 1. Parse CONTENTS -> list of (title, page)
# 2. Search for each title in body_start..body_end ONLY
#    (CONTENTS listing is explicitly excluded from search)
# 3. Sort found positions; each article runs from its start
#    to the next article's start (or body_end for the last)
# 4. ALL text from body_start to body_end is accounted for:
#    - Gaps between articles -> Misc_gap files
#    - Text before first article -> Misc_front
#    - Text after last article -> Misc_back
#    No text is ever discarded.
# 5. Articles not found in OCR text -> placeholder file
#    stating text is absent from source.
# ============================================================
process_issue <- function(filepath, output_dir) {
  filename <- basename(filepath)
  meta     <- get_metadata(filename)
  if (is.na(meta$month))  meta$month  <- "Unknown"
  if (is.na(meta$volume)) meta$volume <- "XX"
  if (is.na(meta$year))   meta$year   <- "????"
  if (is.na(meta$number)) meta$number <- "0"

  text <- read_file_safe(filepath)
  len  <- nchar(text)

  cat("\n", rep("=",70), "\n", sep="")
  cat("FILE:", filename, "\n")
  cat("SIZE:", format(len, big.mark=","), "chars\n")

  # Output folder: output/Vol16_1929/March/
  out_folder <- file.path(output_dir,
                          paste0("Vol", meta$volume, "_", meta$year),
                          meta$month)
  if (dir.exists(out_folder)) unlink(out_folder, recursive=TRUE)
  dir.create(out_folder, showWarnings=FALSE, recursive=TRUE)

  prefix <- paste0(meta$month, "_Vol", meta$volume, "_No", meta$number)

  # ----------------------------------------------------------
  # Step 1: Locate sections
  # ----------------------------------------------------------
  s <- find_sections(text)
  body_start <- s$body_start
  body_end   <- s$body_end

  # Safety: ensure body_start does not overlap with contents region.
  # EXCEPTION: if body_start was set from a reliable VOL marker (e.g. "VOL. XVI MARCH, 1929 No. 3"),
  # trust it even if it falls before contents_end. The VOL marker precisely marks
  # where the masthead ends and article text begins. The contents_end "hard cap" is
  # a rough heuristic that sometimes extends too far (e.g. body_start=3595 but
  # contents_end=7425 due to hard_cap=contents_start+5000), so the clamp would
  # incorrectly push body_start back to 7426, losing several pages of articles.
  if (!is.na(s$contents_end) && !is.na(body_start) && body_start <= s$contents_end) {
    if (isTRUE(s$vol_marker_found)) {
      cat("  NOTE: body_start from VOL marker (", body_start,
          ") is before contents_end (", s$contents_end,
          ") — trusting VOL marker\n", sep="")
      # Keep body_start as-is; the VOL marker is authoritative.
    } else {
      cat("  WARNING: body_start inside CONTENTS region — advancing past contents_end\n")
      body_start <- s$contents_end + 1L
      s$body_start <- body_start
    }
  }

  cat(sprintf("  CONTENTS: %s to %s\n",
              ifelse(is.na(s$contents_start),"?",s$contents_start),
              ifelse(is.na(s$contents_end),  "?",s$contents_end)))
  cat(sprintf("  body_start: %s  body_end: %s\n",
              format(body_start, big.mark=","),
              format(body_end,   big.mark=",")))

  # ----------------------------------------------------------
  # Step 2: Save CONTENTS and BOARD files, plus a _00_Misc.txt
  # containing ALL text from the beginning of the file up to
  # body_start (volume header, issue number, CONTENTS listing,
  # Board roster, etc.).  Every byte before the body is captured.
  # ----------------------------------------------------------
  pre_body_text <- str_trim(str_sub(text, 1L, body_start - 1L))
  if (nchar(pre_body_text) > 0) {
    # Trim any article text that leaked into the pre-body region.
    # Many issues print the first article (often a poem) on the inside front cover,
    # right after the last advertisement.  The reliable cut point is the LAST
    # "Mention Relief Society Magazine" ad footer — article text follows that.
    # Since the first article is already extracted correctly as a body article,
    # trimming here avoids a duplicate in _00_Misc.txt with no data loss.
    last_ad <- str_locate_all(pre_body_text,
      regex("Mention Relief Society Magazine", ignore_case=TRUE))[[1]]
    if (nrow(last_ad) > 0) {
      cut_pos <- last_ad[nrow(last_ad), "end"]
      pre_body_trimmed <- str_trim(str_sub(pre_body_text, 1L, cut_pos))
    } else {
      pre_body_trimmed <- pre_body_text
    }
    write_file(pre_body_trimmed,
               file.path(out_folder, paste0(prefix, "_00_Misc.txt")))
    trimmed_chars <- nchar(pre_body_text) - nchar(pre_body_trimmed)
    if (trimmed_chars > 10) {
      cat(sprintf("  Pre-body (00_Misc): %s chars (trimmed %s chars of article text already captured in body)\n",
                  format(nchar(pre_body_trimmed), big.mark=","),
                  format(trimmed_chars, big.mark=",")))
    } else {
      cat(sprintf("  Pre-body (00_Misc): %s chars\n",
                  format(nchar(pre_body_trimmed), big.mark=",")))
    }
  }

  if (!is.null(s$contents_text))
    write_file(str_trim(s$contents_text),
               file.path(out_folder, paste0(prefix, "_00_CONTENTS.txt")))

  board_text <- ""
  if (!is.na(s$board_start)) {
    board_text <- str_trim(str_sub(text, s$board_start, s$board_end))
    write_file(board_text,
               file.path(out_folder, paste0(prefix, "_00_BOARD.txt")))
    cat(sprintf("  Board: %d chars\n", nchar(board_text)))
  }

  # ----------------------------------------------------------
  # Step 3: Parse CONTENTS
  # ----------------------------------------------------------
  arts <- if (!is.null(s$contents_text))
    parse_contents_section(s$contents_text) else
    data.frame(title=character(), page=integer(), category=character(),
               stringsAsFactors=FALSE)

  cat(sprintf("  Articles in CONTENTS: %d\n", nrow(arts)))

  if (nrow(arts) == 0) {
    # Save full body as one Misc file — no text is lost
    write_file(str_sub(text, body_start, body_end),
               file.path(out_folder, paste0(prefix, "_Misc_fullbody.txt")))
    cat("  No CONTENTS parsed. Full body saved as Misc.\n")
    return(data.frame(file=filename, n_contents=0L, n_saved=0L,
                      n_missed=0L, total_chars=len, stringsAsFactors=FALSE))
  }

  # ----------------------------------------------------------
  # Step 4: Build page index (within body only, positions absolute)
  # ----------------------------------------------------------
  body_text  <- str_sub(text, body_start, body_end)
  page_index <- build_page_index(body_text, body_start)
  cat(sprintf("  Page index: %d markers\n", nrow(page_index)))

  # ----------------------------------------------------------
  # Step 5: TWO-PASS HYBRID SEARCH
  #
  # PASS A — Independent search (no sequential advancement):
  #   Each article searches its own page-windowed region of the full body,
  #   independently of every other article. search_from is NOT advanced.
  #   This means Strategy 10/11 false positives cannot cascade: if article [i]
  #   gets a wrong position, it cannot push article [i+1]'s search forward.
  #
  # PASS B — Order validation:
  #   The CONTENTS table defines the true article order. After all candidates
  #   are found, enforce monotonicity: if candidate[i] <= candidate[i-1]
  #   (i.e., this article appears to start before or at the same place as the
  #   previous one), the candidate is a false match and is discarded.
  #   The article then falls through to the page-estimate fallback in Step 6.
  # ----------------------------------------------------------
  candidates <- rep(NA_integer_, nrow(arts))   # raw finds from Pass A
  positions  <- rep(NA_integer_, nrow(arts))   # validated positions from Pass B
  CPP <- 2400L

  # ---- Pass A: independent per-article search ----
  for (i in seq_len(nrow(arts))) {
    title <- arts$title[i]
    pg    <- arts$page[i]
    cat_i <- arts$category[i]

    # Frontispiece / page-0 articles: always near start of body
    if (cat_i == "Frontispiece" || pg <= 0L) {
      ft <- str_trim(str_replace(title, regex("\\s+Frontispiece\\s*$",
                                              ignore_case=TRUE), ""))
      win_end <- min(body_end, body_start + 6000L)
      pos <- if (nchar(ft) >= 3)
        find_in_window(text, ft, body_start, win_end)
      else NA_integer_
      if (is.na(pos))
        pos <- find_in_window(text, title, body_start, win_end)
      candidates[i] <- if (!is.na(pos))
        max(snap_to_para_start(text, pos, body_start, max_back=300L), body_start)
      else body_start   # fallback: body_start
      next
    }

    # Normal articles: narrow → wide → full-body, each bounded by page estimate.
    # IMPORTANT: search always starts from body_start (not search_from),
    # so articles can be found even if a previous article's position was wrong.
    if (nrow(page_index) >= 3) {
      pg_est <- page_to_pos(page_index, pg, body_start, body_end)
      # Narrow window: pg ± 3–4 pages
      s1 <- max(body_start,
                page_to_pos(page_index, max(1L, pg-3L), body_start, body_end) - CPP)
      e1 <- min(body_end,
                page_to_pos(page_index, pg+4L, body_start, body_end) + CPP)
      pos <- find_in_window(text, title, s1, e1, allow_s10=TRUE)
      # Wide window: pg ± 6–7 pages
      if (is.na(pos)) {
        s2 <- max(body_start,
                  page_to_pos(page_index, max(1L, pg-6L), body_start, body_end) - CPP*2L)
        e2 <- min(body_end,
                  page_to_pos(page_index, pg+7L, body_start, body_end) + CPP*2L)
        pos <- find_in_window(text, title, s2, e2, allow_s10=TRUE)
      }
      # Full-body fallback: plausibility-checked against pg_est.
      # Conference proceedings articles (Work and Business Meeting, General Session,
      # etc.) often appear as subsection headings EARLIER in the body than their
      # page number suggests — use a wider tolerance (50,000 chars) for those.
      # SPECIAL CASE: When pg_est was clamped to body_end (because ALL page markers
      # extrapolate beyond body_end), the pg_est is unreliable — it simply reflects
      # the end of the file, not a real position estimate. For conference session
      # headings in this situation the gap can exceed 100k chars (e.g. Jun16 where
      # "Work and Business Meeting" is at @25816 but pg_est = body_end = 149966).
      # In that case, skip the plausibility check entirely and use the full-body find.
      if (is.na(pos)) {
        pos_fb <- find_in_window(text, title, body_start, body_end, allow_s10=FALSE)
        if (!is.na(pos_fb)) {
          # pg_est is unreliable when:
          #   (a) clamped to body_end  — page number extrapolates beyond the file, OR
          #   (b) extrapolated below body_start — inverted/disordered page markers
          # In either case the estimate is meaningless, so skip the plausibility check.
          # pg_est is unreliable when it falls outside the body:
          #   >= body_end : extrapolation put the estimate past the end of the file
          #                 (covers both clamped-to-body_end AND unclamped overshoots,
          #                  e.g. pg352 in a conference issue where the last page marker
          #                  is pg338 → estimate = 169,222 >> body_end = 149,966)
          #   < body_start: negative/backward extrapolation from inverted page markers
          pg_est_is_clamped  <- !is.na(pg_est) && (pg_est >= body_end)
          pg_est_is_negative <- !is.na(pg_est) && (pg_est < body_start)
          pg_est_unreliable  <- pg_est_is_clamped || pg_est_is_negative
          plausible <- is.na(pg_est) ||
                       pg_est_unreliable  ||
                       abs(pos_fb - pg_est) <= 25000L
          pos <- if (plausible) pos_fb else NA_integer_
        }
      }
      # S10 full-body fallback: uses author-proximity strategies (allow_s10=TRUE).
      if (is.na(pos)) {
        pos_fb2 <- find_in_window(text, title, body_start, body_end, allow_s10=TRUE)
        if (!is.na(pos_fb2)) {
          pg_est_is_clamped2  <- !is.na(pg_est) && (pg_est >= body_end)
          pg_est_is_negative2 <- !is.na(pg_est) && (pg_est < body_start)
          pg_est_unreliable2  <- pg_est_is_clamped2 || pg_est_is_negative2
          plausible2 <- is.na(pg_est) ||
                        pg_est_unreliable2 ||
                        abs(pos_fb2 - pg_est) <= 25000L
          pos <- if (plausible2) pos_fb2 else NA_integer_
        }
      }
    } else {
      # No page index: search full body with S10/S11.
      pos <- find_in_window(text, title, body_start, body_end, allow_s10=TRUE)
    }

    if (!is.na(pos)) {
      candidates[i] <- max(snap_to_para_start(text, pos, body_start), body_start)
    }
  }

  # ---- Pass B: accept all plausible candidates ----
  # Since Pass A found each article independently (no cascade), we can accept
  # any candidate that passed its plausibility check. We do NOT enforce strict
  # monotonicity here because the OCR body text order sometimes differs from
  # the CONTENTS page order (e.g. an article on pg482 may physically appear
  # before one on pg481 in the scan). Strict ordering would reject legitimate
  # finds in those cases.
  # 
  # The art_tbl sort in Step 7 handles the final ordering: it sorts all found
  # positions by character offset and assigns boundaries accordingly. Articles
  # that share the same position (body_start fallback) are deduplicated there.
  for (i in seq_len(nrow(arts))) {
    if (!is.na(candidates[i])) {
      positions[i] <- candidates[i]
    }
  }

  # ---- Report found positions ----
  for (i in seq_len(nrow(arts))) {
    pg <- arts$page[i]
    cat(sprintf("    [%02d] pg%3s %-48s -> %s\n", i,
                ifelse(is.numeric(pg), as.character(as.integer(pg)), pg),
                str_sub(arts$title[i],1,48),
                if (!is.na(positions[i])) paste0("@", positions[i]) else "MISS"))
  }

  # ----------------------------------------------------------
  # Step 6: Page-position fallback for remaining misses
  # ----------------------------------------------------------
  for (i in seq_len(nrow(arts))) {
    if (!is.na(positions[i])) next
    if (arts$page[i] <= 0L || nrow(page_index) < 3) next
    est <- page_to_pos(page_index, arts$page[i], body_start, body_end)
    if (est >= body_start && est <= body_end) {
      # The page estimate may land INSIDE the article (heading appears before the
      # estimated character position).  Search backward up to 2000 chars from est
      # to find the actual title.  If found, use that position; otherwise snap
      # est back to the nearest paragraph break within 1000 chars.
      back_start <- max(body_start, est - 2000L)
      pos_try <- find_in_window(text, arts$title[i], back_start,
                                min(body_end, est + 500L), allow_s10=TRUE)
      if (!is.na(pos_try)) {
        positions[i] <- max(snap_to_para_start(text, pos_try, body_start), body_start)
      } else {
        positions[i] <- max(snap_to_para_start(text, est, body_start, max_back=1000L),
                            body_start)
      }
      cat(sprintf("    [%02d] pg%3d %-48s -> @%d [page-est]\n",
                  i, arts$page[i], str_sub(arts$title[i],1,48), positions[i]))
    }
  }

  # ----------------------------------------------------------
  # Step 7: Assign boundaries
  # Each article: start_pos to (next_start - 1), last to body_end.
  # Missed articles (not found in OCR) get placeholder files.
  # ----------------------------------------------------------

  # Build a sorted table of found articles
  found_idx <- which(!is.na(positions))
  miss_idx  <- which(is.na(positions))

  saved_count <- 0L

  if (length(found_idx) == 0) {
    # Nothing found — save entire body as one Misc file
    write_file(str_sub(text, body_start, body_end),
               file.path(out_folder, paste0(prefix, "_Misc_fullbody.txt")))
    cat("  No article positions found. Full body saved.\n")
    # Placeholder files for all articles
    for (i in seq_len(nrow(arts))) {
      fn <- file.path(out_folder,
        paste0(prefix, "_", sprintf("%02d",i), "_",
               arts$category[i], "_", safe_filename(arts$title[i]),
               "_NOT_IN_SOURCE.txt"))
      write_file(paste0("[TEXT NOT FOUND IN SOURCE OCR]\nTitle: ", arts$title[i],
                        "\nPage: ", arts$page[i]), fn)
    }
    return(data.frame(file=filename, n_contents=nrow(arts), n_saved=0L,
                      n_missed=nrow(arts), total_chars=len, stringsAsFactors=FALSE))
  }

  art_tbl <- data.frame(
    orig_i   = found_idx,
    position = positions[found_idx],
    stringsAsFactors=FALSE)
  art_tbl  <- art_tbl[order(art_tbl$position), ]

  # ----------------------------------------------------------
  # Step 7b: Group near-adjacent articles for merging.
  #
  # Articles listed separately in the CONTENTS sometimes correspond to
  # continuous text in the OCR (e.g. Morning + Afternoon sessions,
  # or three short companion pieces with no gap between them).
  # When consecutive articles are within MERGE_THRESH characters of
  # each other — including the exact-same-position case (both resolve
  # to body_start or to the same section heading) — they are merged
  # into ONE output file.  The file is labelled with the title of the
  # first article in the group; all subsequent titles are appended
  # after a " + " separator so the combined content is traceable.
  #
  # This replaces the old "+1 offset" disambiguation which created
  # 1-character stub files for all but the last article at a shared
  # position.
  # ----------------------------------------------------------
  MERGE_THRESH <- 200L

  groups    <- list()
  cur_grp   <- c(1L)
  for (k in seq_len(nrow(art_tbl))) {
    if (k == 1L) {
      cur_grp <- c(k)
    } else if (art_tbl$position[k] - art_tbl$position[k - 1L] <= MERGE_THRESH) {
      cur_grp <- c(cur_grp, k)
    } else {
      groups[[length(groups) + 1L]] <- cur_grp
      cur_grp <- c(k)
    }
  }
  groups[[length(groups) + 1L]] <- cur_grp
  n_groups <- length(groups)

  # Compute start / end position and list of orig_i for every merged group
  grp_start <- integer(n_groups)
  grp_end   <- integer(n_groups)
  grp_orig  <- vector("list", n_groups)
  for (g in seq_len(n_groups)) {
    rows          <- groups[[g]]
    grp_start[g]  <- art_tbl$position[rows[1L]]
    grp_end[g]    <- if (g < n_groups)
                       art_tbl$position[groups[[g + 1L]][1L]] - 1L
                     else
                       body_end
    grp_orig[[g]] <- art_tbl$orig_i[rows]
  }

  # ----------------------------------------------------------
  # Step 8: FRONT MATTER
  # Everything from body_start up to the first group's start.
  # ----------------------------------------------------------
  if (grp_start[1L] > body_start) {
    front <- clean_headers(str_sub(text, body_start, grp_start[1L] - 1L))
    if (nchar(board_text) > 50) front <- str_replace(front, fixed(board_text), "")
    front <- str_trim(front)
    if (nchar(front) > 0) {
      write_file(front,
                 file.path(out_folder, paste0(prefix, "_Misc_front_matter.txt")))
      cat(sprintf("  Misc: front_matter saved (%s chars)\n",
                  format(nchar(front), big.mark=",")))
    }
  }

  # ----------------------------------------------------------
  # Step 9: SAVE EACH (MERGED) ARTICLE GROUP and GAPS between them
  # ----------------------------------------------------------
  for (g in seq_len(n_groups)) {
    orig_is  <- grp_orig[[g]]
    a_start  <- grp_start[g]
    a_end    <- grp_end[g]

    art_raw  <- str_sub(text, a_start, a_end)
    art_text <- clean_headers(art_raw)
    if (nchar(board_text) > 50)
      art_text <- str_replace(art_text, fixed(board_text), "")
    art_text <- str_trim(art_text)

    # Combined title: first article's title (+ subsequent if merged)
    primary_i     <- orig_is[1L]
    combined_title <- paste(arts$title[orig_is], collapse = " + ")
    display_title  <- str_sub(combined_title, 1, 60)

    saved_count <- saved_count + length(orig_is)   # count articles covered, not files
    fn <- file.path(out_folder,
      paste0(prefix, "_", sprintf("%02d", g), "_",
             arts$category[primary_i], "_",
             safe_filename(arts$title[primary_i]), ".txt"))
    write_file(art_text, fn)

    if (length(orig_is) > 1L) {
      cat(sprintf("    Saved [%02d] %-60s %s chars  [MERGED %d articles]\n",
                  g, display_title, format(nchar(art_text), big.mark=","),
                  length(orig_is)))
    } else {
      cat(sprintf("    Saved [%02d] %-48s %s chars\n",
                  g, str_sub(arts$title[primary_i], 1, 48),
                  format(nchar(art_text), big.mark=",")))
    }

    # Gap to next group — save even small gaps so NO text is ever lost
    if (g < n_groups) {
      g_start <- grp_end[g] + 1L
      g_end   <- grp_start[g + 1L] - 1L
      if (g_end >= g_start) {
        gap <- str_trim(clean_headers(str_sub(text, g_start, g_end)))
        if (nchar(board_text) > 50) gap <- str_replace(gap, fixed(board_text), "")
        gap <- str_trim(gap)
        if (nchar(gap) > 5L) {
          gfn <- file.path(out_folder,
            paste0(prefix, "_Misc_gap_", sprintf("%02d", g), "_",
                   sprintf("%02d", g + 1L), ".txt"))
          write_file(gap, gfn)
          cat(sprintf("    Misc gap [%02d]->[%02d]: %s chars\n",
                      g, g + 1L, format(nchar(gap), big.mark=",")))
        }
      }
    }
  }

  # ----------------------------------------------------------
  # Step 10: BACK MATTER
  # Everything from the last group's end to body_end.
  # ----------------------------------------------------------
  last_end <- grp_end[n_groups]
  if (last_end < body_end) {
    back <- str_trim(clean_headers(str_sub(text, last_end + 1L, body_end)))
    if (nchar(back) > 5L) {
      write_file(back,
                 file.path(out_folder, paste0(prefix, "_Misc_back_matter.txt")))
      cat(sprintf("  Misc: back_matter saved (%s chars)\n",
                  format(nchar(back), big.mark=",")))
    }
  }

  # ----------------------------------------------------------
  # Step 11: Pre-body search for MISS articles, then placeholders
  # Some CONTENTS entries (e.g. "PUBLISHED MONTHLY BY THE GENERAL BOARD...")
  # refer to text that lives in the pre-body region (already captured in
  # _00_Misc.txt). Search there before writing a NOT_IN_SOURCE placeholder.
  # ----------------------------------------------------------
  true_miss_idx <- integer(0)
  if (length(miss_idx) > 0) {
    for (mi in miss_idx) {
      pb_pos <- find_in_window(text, arts$title[mi], 1L, body_start - 1L,
                               allow_s10=TRUE)
      if (!is.na(pb_pos)) {
        # Found in pre-body — already in _00_Misc.txt, count as saved
        saved_count <- saved_count + 1L
        cat(sprintf("    Captured in _00_Misc: '%s' (pre-body @%d)\n",
                    str_sub(arts$title[mi],1,50), pb_pos))
      } else {
        true_miss_idx <- c(true_miss_idx, mi)
      }
    }
  }

  if (length(true_miss_idx) > 0) {
    for (mi in true_miss_idx) {
      short_title <- safe_filename(arts$title[mi])
      fn <- file.path(out_folder,
        paste0(prefix, "_NOT_IN_SOURCE_pg", arts$page[mi], "_",
               str_sub(short_title, 1, 40), ".txt"))
      write_file(paste0("[TEXT NOT FOUND IN OCR SOURCE]\n\n",
                        "Title: ", arts$title[mi], "\n",
                        "Page:  ", arts$page[mi], "\n\n",
                        "This article was listed in the CONTENTS but its text\n",
                        "does not appear in the digitised source file.\n",
                        "The original print pages may not have been scanned."), fn)
      cat(sprintf("    NOT IN SOURCE: '%s' (pg %s)\n",
                  str_sub(arts$title[mi],1,50), arts$page[mi]))
    }
  }

  n_missed <- length(true_miss_idx)
  cat(sprintf("\n  RESULT: %d saved, %d NOT IN SOURCE, %d total in CONTENTS\n",
              saved_count, n_missed, nrow(arts)))

  data.frame(file=filename, n_contents=nrow(arts), n_saved=saved_count,
             n_missed=n_missed, total_chars=len, stringsAsFactors=FALSE)
}
```

```{r run, message=FALSE}
# ============================================================
# MAIN LOOP
# ============================================================
cat("Relief Society Magazine — Universal Article Extractor\n")
cat(rep("=",70), "\n\n", sep="")

all_results <- list()

for (input_dir in INPUT_DIRS) {
  if (!dir.exists(input_dir)) {
    cat("WARNING: not found:", input_dir, "\n"); next
  }
  files <- sort(list.files(input_dir, pattern="\\.txt$",
                           full.names=TRUE, recursive=FALSE))
  cat("\n", rep("#",70), "\n", sep="")
  cat("FOLDER:", basename(input_dir), " — ", length(files), "file(s)\n")
  cat(rep("#",70), "\n", sep="")

  for (f in files) {
    res <- tryCatch(
      process_issue(f, OUTPUT_DIR),
      error=function(e) {
        cat("ERROR:", basename(f), "—", conditionMessage(e), "\n")
        data.frame(file=basename(f), n_contents=0L, n_saved=0L,
                   n_missed=0L, total_chars=0L, stringsAsFactors=FALSE)
      })
    all_results[[length(all_results)+1]] <- res
  }
}

results_df <- if (length(all_results)>0) do.call(rbind, all_results) else NULL
```

## Summary {.tabset}

### Results Table

```{r summary}
if (!is.null(results_df) && nrow(results_df)>0) {
  cat(sprintf("Files processed:       %d\n",   nrow(results_df)))
  cat(sprintf("Articles in CONTENTS:  %d\n",   sum(results_df$n_contents)))
  cat(sprintf("Articles saved:        %d\n",   sum(results_df$n_saved)))
  cat(sprintf("Not in source (OCR):   %d\n",   sum(results_df$n_missed)))
  cat(sprintf("Hit rate:              %.1f%%\n",
              sum(results_df$n_saved) / max(1, sum(results_df$n_contents)) * 100))
  cat("Output folder:", OUTPUT_DIR, "\n\n")

  kable(results_df,
        col.names=c("File","In CONTENTS","Saved","Not in Source","Total Chars"),
        format.args=list(big.mark=",")) %>%
    kable_styling(bootstrap_options=c("striped","hover","condensed"),
                  full_width=FALSE) %>%
    column_spec(4, color=ifelse(results_df$n_missed > 0, "red", "darkgreen"))
}
```

### Notes on "Not In Source" Files

When an article listed in the CONTENTS cannot be found anywhere in the body text, the script saves a `_NOT_IN_SOURCE_` placeholder file. This happens when the original print pages were not included in the digitisation/OCR — the text simply is not in the source file. These are **not extraction errors**; they reflect genuine gaps in the OCR source material.

Gaps between articles are saved as `_Misc_gap_` files so that no text is ever discarded. The entire range from `body_start` to `body_end` is always fully covered.
