---
title: "Vol 2-3 FINAL SPLIT - Working Section Detection"
output: html_notebook
---

```{r setup, include=FALSE}
library(stringr)
library(readr)
```

# FINAL SPLIT VERSION
# - Working split detection
# - Better section break patterns
# - Match validation (not just single words)
# - Comprehensive extraction

```{r config}
INPUT_DIR <- "C:\\Users\\birch\\OneDrive - George Mason University - O365 Production\\Dissertation\\textanalysis\\Articleextractionrfiles\\input"
OUTPUT_DIR <- "C:\\Users\\birch\\OneDrive - George Mason University - O365 Production\\Dissertation\\textanalysis\\Articleextractionrfiles\\output"
```

```{r functions}
get_metadata <- function(filename) {
  list(
    volume = str_extract(filename, "(?<=Vol)\\d+"),
    month = str_extract(filename, "(January|February|March|April|May|June|July|August|September|October|November|December)"),
    year = str_extract(filename, "\\d{4}")
  )
}

parse_contents <- function(text) {
  contents_match <- str_match(text, regex("CONTENTS.*?(?=ADVERTISERS|GENERAL BOARD)", 
                                         dotall = TRUE, ignore_case = TRUE))
  if (is.na(contents_match[1])) return(NULL)
  
  contents_text <- contents_match[1]
  contents_text <- str_replace_all(contents_text, "\\r\\n", " ")
  contents_text <- str_replace_all(contents_text, "\\s+", " ")
  
  page_matches <- str_locate_all(contents_text, "\\s(\\d{1,4})\\s")[[1]]
  if (nrow(page_matches) == 0) return(NULL)
  
  articles <- data.frame(title = character(), page = integer(), stringsAsFactors = FALSE)
  
  for (i in 1:nrow(page_matches)) {
    page_start <- page_matches[i, 1]
    page_end <- page_matches[i, 2]
    page_num <- as.integer(str_trim(str_sub(contents_text, page_start, page_end)))
    
    if (is.na(page_num) || page_num < 1 || page_num > 1000) next
    
    entry_start <- if (i == 1) 1 else page_matches[i - 1, 2] + 1
    entry_text <- str_sub(contents_text, entry_start, page_start - 1)
    entry_text <- str_trim(entry_text)
    
    if (is.na(entry_text) || nchar(entry_text) < 3) next
    if (str_detect(entry_text, "^CONTENTS|^Vol\\.|^No\\.|^\\d{4}")) next
    
    title_only <- str_replace(entry_text, "\\s*[—–-].*$", "")
    
    parts <- str_split(title_only, "\\s+")[[1]]
    if (length(parts) >= 4 && all(str_detect(parts[(length(parts)-1):length(parts)], "^[A-Z]"))) {
      title_only <- paste(parts[1:(length(parts)-2)], collapse = " ")
    }
    
    title_only <- str_replace_all(title_only, '"', '')
    title_only <- trimws(title_only)
    
    if (nchar(title_only) < 3) next
    
    articles <- rbind(articles, data.frame(
      title = title_only,
      page = page_num,
      stringsAsFactors = FALSE
    ))
  }
  
  if (nrow(articles) == 0) return(NULL)
  
  articles <- articles[!duplicated(articles$page), ]
  articles <- articles[!duplicated(articles$title), ]
  articles <- articles[order(articles$page), ]
  
  return(articles)
}

find_article_ultra <- function(text, title, start_pos, end_pos) {
  search_text <- str_sub(text, start_pos, end_pos)
  
  # Special handlers
  if (str_detect(title, "^Editorial")) {
    matches <- str_locate_all(search_text, regex("EDITORIAL", ignore_case = TRUE))[[1]]
    if (nrow(matches) > 0) return(start_pos + matches[1, 1] - 1)
  }
  
  if (str_detect(title, "Current Topics")) {
    matches <- str_locate_all(search_text, regex("Current Topics", ignore_case = TRUE))[[1]]
    if (nrow(matches) > 0) return(start_pos + matches[1, 1] - 1)
  }
  
  words <- str_split(title, "\\s+")[[1]]
  
  # Try full title
  title_escaped <- str_replace_all(title, "([.?*+^$\\[\\]\\\\(){}|\\-])", "\\\\\\1")
  matches <- tryCatch({
    str_locate_all(search_text, regex(title_escaped, ignore_case = TRUE))[[1]]
  }, error = function(e) matrix(ncol=2, nrow=0))
  
  if (nrow(matches) > 0) return(start_pos + matches[1, 1] - 1)
  
  # Try progressively shorter titles
  if (length(words) >= 2) {
    for (n_words in rev(2:min(4, length(words)))) {
      partial <- paste(words[1:n_words], collapse = " ")
      partial_escaped <- str_replace_all(partial, "([.?*+^$\\[\\]\\\\(){}|\\-])", "\\\\\\1")
      
      matches <- tryCatch({
        str_locate_all(search_text, regex(partial_escaped, ignore_case = TRUE))[[1]]
      }, error = function(e) matrix(ncol=2, nrow=0))
      
      if (nrow(matches) > 0) return(start_pos + matches[1, 1] - 1)
    }
  }
  
  # Try ALL CAPS
  title_upper <- toupper(title)
  title_upper_escaped <- str_replace_all(title_upper, "([.?*+^$\\[\\]\\\\(){}|\\-])", "\\\\\\1")
  
  matches <- tryCatch({
    str_locate_all(search_text, regex(title_upper_escaped, ignore_case = FALSE))[[1]]
  }, error = function(e) matrix(ncol=2, nrow=0))
  
  if (nrow(matches) > 0) return(start_pos + matches[1, 1] - 1)
  
  # Try significant words
  sig_words <- words[nchar(words) >= 4]
  common <- c("the", "a", "an", "of", "in", "on", "at", "to", "for", "and", "or", "but", "by", "with", "from")
  sig_words <- sig_words[!tolower(sig_words) %in% common]
  
  if (length(sig_words) == 0) sig_words <- words[nchar(words) >= 3]
  sig_words <- sig_words[!tolower(sig_words) %in% common]
  
  for (word in sig_words) {
    word_safe <- str_replace_all(word, "([.?*+^$\\[\\]\\\\(){}|\\-])", "\\\\\\1")
    matches <- tryCatch({
      str_locate_all(search_text, regex(paste0("\\b", word_safe, "\\b"), ignore_case = TRUE))[[1]]
    }, error = function(e) matrix(ncol=2, nrow=0))
    
    if (nrow(matches) > 0) return(start_pos + matches[1, 1] - 1)
  }
  
  return(NULL)
}

# IMPROVED: Detect multiple section break patterns
detect_section_breaks <- function(text) {
  breaks <- c()
  
  # Split into lines for analysis
  lines <- str_split(text, "\\r?\\n")[[1]]
  cumulative_pos <- 0
  
  for (i in 1:length(lines)) {
    line <- str_trim(lines[i])
    line_len <- nchar(lines[i]) + 1  # +1 for newline
    
    # Pattern 1: ALL CAPS headers (10-80 chars, mostly caps)
    if (nchar(line) >= 10 && nchar(line) <= 80) {
      caps_count <- sum(str_count(line, "[A-Z]"))
      total_letters <- sum(str_count(line, "[A-Za-z]"))
      
      if (total_letters > 5 && caps_count / total_letters > 0.7) {
        # Check it's not in middle of sentence
        prev_line <- if (i > 1) str_trim(lines[i-1]) else ""
        if (!str_detect(prev_line, "[,;:]\\s*$")) {
          breaks <- c(breaks, cumulative_pos)
        }
      }
    }
    
    # Pattern 2: Title Case Headers (Like This One) - 10-60 chars
    if (nchar(line) >= 10 && nchar(line) <= 60) {
      words <- str_split(line, "\\s+")[[1]]
      if (length(words) >= 2 && length(words) <= 10) {
        title_case_count <- sum(str_detect(words, "^[A-Z][a-z]+"))
        if (title_case_count / length(words) > 0.6) {
          prev_line <- if (i > 1) str_trim(lines[i-1]) else ""
          if (nchar(prev_line) == 0 || !str_detect(prev_line, "[,;:]\\s*$")) {
            breaks <- c(breaks, cumulative_pos)
          }
        }
      }
    }
    
    # Pattern 3: Headers followed by "By AuthorName"
    if (i < length(lines) - 1) {
      next_line <- str_trim(lines[i + 1])
      if (str_detect(next_line, "^By\\s+[A-Z]")) {
        breaks <- c(breaks, cumulative_pos)
      }
    }
    
    cumulative_pos <- cumulative_pos + line_len
  }
  
  # Remove duplicates and sort
  breaks <- unique(breaks)
  breaks <- breaks[breaks > 100]  # Ignore breaks in first 100 chars
  breaks <- sort(breaks)
  
  return(breaks)
}

process_file <- function(filepath, output_dir) {
  filename <- basename(filepath)
  metadata <- get_metadata(filename)
  
  text <- tryCatch({
    read_file(filepath, locale = locale(encoding = "UTF-8"))
  }, error = function(e) {
    read_file(filepath, locale = locale(encoding = "windows-1252"))
  })
  
  text <- iconv(text, from = "UTF-8", to = "UTF-8", sub = "")
  total_chars <- nchar(text)
  
  cat("\n", rep("=", 70), "\n", sep = "")
  cat(filename, "\n")
  cat(rep("=", 70), "\n", sep = "")
  
  month_folder <- file.path(output_dir, metadata$year, metadata$month)
  dir.create(month_folder, showWarnings = FALSE, recursive = TRUE)
  
  # Extract Contents
  contents_match <- str_locate(text, regex("CONTENTS.*?(?=ADVERTISERS|GENERAL BOARD)", 
                                           dotall = TRUE, ignore_case = TRUE))
  contents_end <- 2000
  
  if (!is.na(contents_match[1])) {
    contents_text <- str_sub(text, contents_match[1], contents_match[2])
    write_file(paste0("TABLE OF CONTENTS\n", paste(rep("=", 70), collapse = ""), "\n\n", contents_text),
               file.path(month_folder, sprintf("%s_Vol%s_00_CONTENTS.txt", metadata$month, metadata$volume)))
    contents_end <- contents_match[2] + 100
    cat("✓ Contents\n")
  }
  
  # Extract Board
  board_match <- str_locate(text, regex("GENERAL BOARD.*?Relief Society Magazine", 
                                        dotall = TRUE, ignore_case = TRUE))
  
  if (!is.na(board_match[1]) && board_match[1] < contents_end + 3000) {
    board_text <- str_sub(text, board_match[1], board_match[2])
    write_file(paste0("GENERAL BOARD\n", paste(rep("=", 70), collapse = ""), "\n\n", board_text),
               file.path(month_folder, sprintf("%s_Vol%s_00_BOARD.txt", metadata$month, metadata$volume)))
    if (board_match[2] > contents_end) contents_end <- board_match[2] + 100
    cat("✓ Board\n")
  }
  
  # Parse Contents
  articles <- parse_contents(text)
  
  if (is.null(articles) || nrow(articles) == 0) {
    cat("✗ No Contents\n")
    return(data.frame(file = filename, found = 0, saved = 0, coverage_pct = 0))
  }
  
  cat(sprintf("✓ %d articles\n", nrow(articles)))
  
  # Search
  search_start <- contents_end
  search_end <- as.integer(nchar(text) * 0.95)
  
  cat("\nMatching...\n")
  positions <- rep(NA, nrow(articles))
  
  for (i in 1:nrow(articles)) {
    pos <- find_article_ultra(text, articles$title[i], search_start, search_end)
    
    if (!is.null(pos)) {
      positions[i] <- pos
      cat(sprintf("  ✓ %s\n", str_sub(articles$title[i], 1, 45)))
    } else {
      cat(sprintf("  ✗ %s\n", str_sub(articles$title[i], 1, 45)))
    }
  }
  
  valid_idx <- which(!is.na(positions))
  cat(sprintf("\n✓ %d/%d matched (%.0f%%)\n\n", length(valid_idx), nrow(articles), 
              100 * length(valid_idx) / nrow(articles)))
  
  if (length(valid_idx) == 0) {
    return(data.frame(file = filename, found = nrow(articles), saved = 0, coverage_pct = 0))
  }
  
  # Chronological order
  matched_articles <- data.frame(
    original_idx = valid_idx,
    title = articles$title[valid_idx],
    position = positions[valid_idx],
    stringsAsFactors = FALSE
  )
  
  matched_articles <- matched_articles[order(matched_articles$position), ]
  
  ads_start <- as.integer(nchar(text) * 0.98)
  
  # Extract with splitting
  cat("Extracting...\n")
  saved <- 0
  chars_saved <- 0
  file_num <- 1
  
  for (i in 1:nrow(matched_articles)) {
    art_start <- matched_articles$position[i]
    art_end <- if (i < nrow(matched_articles)) {
      matched_articles$position[i + 1] - 1
    } else {
      min(ads_start - 1, art_start + 20000)
    }
    
    art_len <- art_end - art_start + 1
    art_text <- str_sub(text, art_start, art_end)
    
    # SPLIT LOGIC
    if (art_len > 10000) {
      cat(sprintf("  [%02d] LONG: %s (%d chars)\n", file_num, 
                  str_sub(matched_articles$title[i], 1, 35), art_len))
      
      # Detect breaks
      breaks <- detect_section_breaks(art_text)
      
      if (length(breaks) > 0) {
        # Filter breaks that are too close together (< 500 chars)
        filtered_breaks <- c()
        last_break <- 0
        for (brk in breaks) {
          if (brk - last_break > 500) {
            filtered_breaks <- c(filtered_breaks, brk)
            last_break <- brk
          }
        }
        breaks <- filtered_breaks
      }
      
      if (length(breaks) > 0) {
        cat(sprintf("       → Splitting into %d parts\n", length(breaks) + 1))
        
        # Create parts
        parts_starts <- c(1, breaks + 1)
        parts_ends <- c(breaks, nchar(art_text))
        
        for (part_idx in 1:length(parts_starts)) {
          part_text <- str_sub(art_text, parts_starts[part_idx], parts_ends[part_idx])
          part_text <- trimws(part_text)
          
          if (nchar(part_text) < 100) next
          
          clean_title <- matched_articles$title[i] %>%
            str_replace_all('[<>:"/\\\\|?*—]', '') %>%
            str_replace_all('\\s+', '_') %>%
            str_sub(1, 40)
          
          fname <- file.path(month_folder, sprintf("%s_Vol%s_%02d_%s_pt%d.txt",
                                                   metadata$month, metadata$volume, file_num, 
                                                   clean_title, part_idx))
          
          header <- sprintf("%s (Part %d/%d)\n%s\n\n", 
                          matched_articles$title[i], part_idx, length(parts_starts),
                          paste(rep("=", 70), collapse = ""))
          write_file(paste0(header, part_text), fname)
          
          saved <- saved + 1
          chars_saved <- chars_saved + nchar(part_text)
        }
        
        file_num <- file_num + 1
        next
      }
    }
    
    # Normal save
    art_text <- trimws(art_text)
    
    clean_title <- matched_articles$title[i] %>%
      str_replace_all('[<>:"/\\\\|?*—]', '') %>%
      str_replace_all('\\s+', '_') %>%
      str_sub(1, 50)
    
    fname <- file.path(month_folder, sprintf("%s_Vol%s_%02d_%s.txt",
                                             metadata$month, metadata$volume, file_num, clean_title))
    
    header <- sprintf("%s\n%s\n\n", matched_articles$title[i], paste(rep("=", 70), collapse = ""))
    write_file(paste0(header, art_text), fname)
    
    saved <- saved + 1
    chars_saved <- chars_saved + nchar(art_text)
    
    cat(sprintf("  [%02d] ✓ %s (%d)\n", file_num, str_sub(matched_articles$title[i], 1, 35), art_len))
    file_num <- file_num + 1
  }
  
  coverage <- (chars_saved / total_chars) * 100
  cat(sprintf("\n✓ %d files, %.1f%% coverage\n", saved, coverage))
  
  return(data.frame(file = filename, found = nrow(articles), saved = saved,
                   coverage_pct = coverage, stringsAsFactors = FALSE))
}
```

```{r run}
files <- list.files(INPUT_DIR, pattern = "Vol[23]_.*\\.txt$", full.names = TRUE)

results_list <- lapply(files, function(f) {
  tryCatch({
    process_file(f, OUTPUT_DIR)
  }, error = function(e) {
    cat("\nERROR:", basename(f), "-", e$message, "\n")
    data.frame(file = basename(f), found = 0, saved = 0, coverage_pct = 0, stringsAsFactors = FALSE)
  })
})

results <- do.call(rbind, results_list)

cat("\n", rep("=", 70), "\n", sep = "")
cat("FINAL SPLIT RESULTS\n")
cat(rep("=", 70), "\n", sep = "")
print(results, row.names = FALSE)
cat("\nTotal files created:", sum(results$saved), "\n")
cat("Avg coverage:", sprintf("%.1f%%", mean(results$coverage_pct)), "\n")
```

## KEY IMPROVEMENTS:

1. **Working Split Detection** (lines 141-194):
   - ALL CAPS headers (70%+ caps letters)
   - Title Case Headers (60%+ title case words)  
   - "By AuthorName" patterns
   - Filters out mid-sentence breaks
   - Requires 500+ char gaps between splits

2. **Better Break Filtering** (lines 352-361):
   - Only keeps breaks >500 chars apart
   - Prevents over-splitting

3. **Keeps All Matches** - no 30-char minimum

4. **Part Numbering** - `_pt1.txt`, `_pt2.txt`, etc.

This should split those 20KB+ articles and increase file count!
