# Additional Visualizations for STM Topic Modeling

A guide to creating publication-ready visualizations beyond basic comparison plots

---

## 1. Topic Correlation Scatterplot

**Shows which topics tend to appear together**

```{r topic-correlation-scatter, fig.width=10, fig.height=8}
# Calculate topic correlations
topic_corr <- topicCorr(stm_model_corpus)

# Extract correlation matrix
corr_matrix <- topic_corr$cor

# Create correlation data for plotting
corr_data <- as.data.frame(corr_matrix) %>%
  rownames_to_column("topic1") %>%
  pivot_longer(-topic1, names_to = "topic2", values_to = "correlation") %>%
  mutate(
    topic1_num = as.numeric(str_remove(topic1, "V")),
    topic2_num = as.numeric(str_remove(topic2, "V"))
  ) %>%
  filter(topic1_num < topic2_num) %>%  # Only upper triangle
  filter(abs(correlation) > 0.05)  # Only meaningful correlations

# Add labels
corr_data <- corr_data %>%
  mutate(
    topic1_label = str_remove(topic_labels[topic1_num], "^Topic \\d+: "),
    topic2_label = str_remove(topic_labels[topic2_num], "^Topic \\d+: ")
  )

# Plot
ggplot(corr_data, aes(x = topic1_num, y = topic2_num, 
                      size = abs(correlation), 
                      color = correlation)) +
  geom_point(alpha = 0.7) +
  scale_color_gradient2(low = "#ef4444", mid = "white", high = "#3b82f6",
                        midpoint = 0, limits = c(-1, 1)) +
  scale_size_continuous(range = c(2, 10)) +
  labs(title = "Topic Correlation Network",
       subtitle = "Which topics tend to co-occur in documents?",
       x = "Topic Number",
       y = "Topic Number",
       color = "Correlation",
       size = "Abs. Correlation") +
  theme_minimal() +
  theme(legend.position = "right")
```

---

## 2. Topic Prevalence Comparison Scatterplot

**Compare topic prevalence between two publications**

```{r prevalence-scatterplot, fig.width=10, fig.height=10}
# Get topic proportions by publication
topic_props <- make.dt(stm_model_corpus, meta = meta)

# Calculate mean prevalence by publication
topic_means <- topic_props %>%
  group_by(corpus) %>%
  summarize(across(starts_with("Topic"), mean)) %>%
  pivot_longer(-corpus, names_to = "topic", values_to = "prevalence") %>%
  mutate(topic_num = as.numeric(str_remove(topic, "Topic"))) %>%
  pivot_wider(names_from = corpus, values_from = prevalence)

# Add labels and significance
topic_means <- topic_means %>%
  left_join(
    corpus_effects %>% select(Topic, P_value, Significant),
    by = c("topic_num" = "Topic")
  ) %>%
  mutate(
    label = str_remove(topic_labels[topic_num], "^Topic \\d+: "),
    sig_label = ifelse(Significant, label, NA)
  )

# Create scatterplot
ggplot(topic_means, aes(x = Relief_Society_Bulletin, 
                        y = Womans_Exponent)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", 
              color = "#94a3b8", size = 1) +
  geom_point(aes(color = Significant, size = abs(Womans_Exponent - Relief_Society_Bulletin)),
             alpha = 0.7) +
  geom_text_repel(aes(label = sig_label), 
                  size = 3, max.overlaps = 15) +
  scale_color_manual(values = c("FALSE" = "#94a3b8", "TRUE" = "#ef4444")) +
  scale_size_continuous(range = c(2, 8)) +
  labs(title = "Topic Prevalence Comparison",
       subtitle = "Topics on diagonal = equal prevalence in both publications",
       x = "Relief Society Bulletin (Proportion)",
       y = "Woman's Exponent (Proportion)",
       color = "Significantly\nDifferent",
       size = "Difference") +
  theme_minimal() +
  theme(legend.position = "right") +
  scale_x_continuous(labels = scales::percent) +
  scale_y_continuous(labels = scales::percent)
```

---

## 3. Topic Prevalence Heatmap

**Show all topic differences at once**

```{r topic-heatmap, fig.width=12, fig.height=8}
# Prepare data for heatmap
heatmap_data <- topic_props %>%
  group_by(corpus) %>%
  summarize(across(starts_with("Topic"), mean)) %>%
  pivot_longer(-corpus, names_to = "topic", values_to = "prevalence") %>%
  mutate(
    topic_num = as.numeric(str_remove(topic, "Topic")),
    topic_label = str_remove(topic_labels[topic_num], "^Topic \\d+: ")
  )

# Create heatmap
ggplot(heatmap_data, aes(x = corpus, y = reorder(topic_label, topic_num), 
                         fill = prevalence)) +
  geom_tile(color = "white", size = 0.5) +
  geom_text(aes(label = sprintf("%.1f%%", prevalence * 100)), 
            size = 3, color = "white") +
  scale_fill_gradient(low = "#1e3a8a", high = "#ef4444",
                     labels = scales::percent) +
  labs(title = "Topic Prevalence by Publication",
       subtitle = "Darker red = higher prevalence",
       x = "Publication",
       y = "Topic",
       fill = "Prevalence") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.text.y = element_text(size = 9),
        panel.grid = element_blank())
```

---

## 4. Diverging Bar Chart

**Show which topics are MORE in each publication**

```{r diverging-bars, fig.width=10, fig.height=12}
# Prepare data
diverging_data <- corpus_effects %>%
  arrange(Difference_Pct) %>%
  mutate(
    Label = factor(Label, levels = Label),
    color_group = case_when(
      !Significant ~ "No difference",
      Difference_Pct > 0 ~ "More in Woman's Exponent",
      TRUE ~ "More in Relief Society Bulletin"
    )
  )

# Create diverging bar chart
ggplot(diverging_data, aes(x = Difference_Pct, y = Label, fill = color_group)) +
  geom_col() +
  geom_vline(xintercept = 0, linetype = "solid", color = "black", size = 1) +
  scale_fill_manual(values = c(
    "More in Woman's Exponent" = "#3b82f6",
    "More in Relief Society Bulletin" = "#ef4444",
    "No difference" = "#94a3b8"
  )) +
  labs(title = "Topic Differences Between Publications",
       subtitle = "Positive = more in Woman's Exponent, Negative = more in Relief Society Bulletin",
       x = "Difference (percentage points)",
       y = NULL,
       fill = "Direction") +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text.y = element_text(size = 9),
    panel.grid.major.y = element_blank()
  )
```

---

## 5. Time Series: Topics Over Time

**How do topics change over time?**

```{r topic-time-series, fig.width=12, fig.height=8}
# Get topic proportions with year
topic_time <- make.dt(stm_model_corpus, meta = meta) %>%
  select(starts_with("Topic"), year, corpus) %>%
  group_by(year, corpus) %>%
  summarize(across(starts_with("Topic"), mean), .groups = "drop") %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "prevalence") %>%
  mutate(topic_num = as.numeric(str_remove(topic, "Topic")))

# Plot top 5 topics over time
top_topics <- corpus_effects %>%
  arrange(desc(abs(Difference_Pct))) %>%
  head(5) %>%
  pull(Topic)

topic_time_subset <- topic_time %>%
  filter(topic_num %in% top_topics) %>%
  mutate(topic_label = str_remove(topic_labels[topic_num], "^Topic \\d+: "))

ggplot(topic_time_subset, aes(x = year, y = prevalence, 
                               color = topic_label, linetype = corpus)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  facet_wrap(~topic_label, ncol = 2, scales = "free_y") +
  scale_color_brewer(palette = "Set2") +
  scale_linetype_manual(values = c("solid", "dashed")) +
  labs(title = "Topic Prevalence Over Time",
       subtitle = "Top 5 topics with largest differences between publications",
       x = "Year",
       y = "Prevalence",
       color = "Topic",
       linetype = "Publication") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  scale_y_continuous(labels = scales::percent)
```

---

## 6. Word Cloud Comparison

**Compare word clouds between publications**

```{r wordcloud-comparison, fig.width=14, fig.height=7}
library(wordcloud)

par(mfrow = c(1, 2))

# Choose a topic to compare
topic_num <- significant_topics$Topic[1]

# Word cloud for Woman's Exponent
plot(stm_model_corpus, 
     type = "perspectives",
     topics = topic_num,
     main = paste(str_remove(topic_labels[topic_num], "^Topic \\d+: "), 
                  "\n(Woman's Exponent perspective)"))

# Reset for second plot
par(mfrow = c(1, 1))
```

---

## 7. Topic Quality Metrics Scatterplot

**Semantic coherence vs. exclusivity**

```{r topic-quality-scatter, fig.width=10, fig.height=8}
# Calculate topic quality
quality <- topicQuality(stm_model_corpus, docs)

# Create quality dataframe
quality_df <- tibble(
  topic = 1:chosen_K,
  coherence = quality$semcoh,
  exclusivity = quality$exclusivity,
  label = str_remove(topic_labels, "^Topic \\d+: ")
) %>%
  left_join(corpus_effects %>% select(Topic, Significant, Difference_Pct),
            by = c("topic" = "Topic"))

# Scatterplot
ggplot(quality_df, aes(x = coherence, y = exclusivity)) +
  geom_point(aes(color = Significant, size = abs(Difference_Pct)), alpha = 0.7) +
  geom_text_repel(aes(label = label), size = 3, max.overlaps = 10) +
  scale_color_manual(values = c("FALSE" = "#94a3b8", "TRUE" = "#ef4444")) +
  scale_size_continuous(range = c(2, 8)) +
  labs(title = "Topic Quality: Coherence vs Exclusivity",
       subtitle = "Upper right = high quality topics (coherent AND exclusive)",
       x = "Semantic Coherence (higher = better)",
       y = "Exclusivity (higher = better)",
       color = "Significantly\nDifferent",
       size = "Abs. Difference") +
  theme_minimal()
```

---

## 8. Topic Distribution Violin Plot

**Show distribution of topic proportions**

```{r topic-violin, fig.width=12, fig.height=10}
# Get top 8 topics
top_8_topics <- corpus_effects %>%
  arrange(desc(abs(Difference_Pct))) %>%
  head(8) %>%
  pull(Topic)

# Prepare data
violin_data <- topic_props %>%
  select(corpus, all_of(paste0("Topic", top_8_topics))) %>%
  pivot_longer(-corpus, names_to = "topic", values_to = "proportion") %>%
  mutate(
    topic_num = as.numeric(str_remove(topic, "Topic")),
    topic_label = str_wrap(str_remove(topic_labels[topic_num], "^Topic \\d+: "), 30)
  )

# Violin plot
ggplot(violin_data, aes(x = corpus, y = proportion, fill = corpus)) +
  geom_violin(alpha = 0.7, trim = FALSE) +
  geom_boxplot(width = 0.2, alpha = 0.5, outlier.shape = NA) +
  facet_wrap(~topic_label, ncol = 2, scales = "free_y") +
  scale_fill_manual(values = c("Relief_Society_Bulletin" = "#ef4444",
                                "Womans_Exponent" = "#3b82f6")) +
  labs(title = "Topic Proportion Distributions",
       subtitle = "Top 8 topics with largest differences",
       x = "Publication",
       y = "Proportion in Document",
       fill = "Publication") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom") +
  scale_y_continuous(labels = scales::percent)
```

---

## 9. Network Graph of Topic Correlations

**Interactive network showing topic relationships**

```{r topic-network, fig.width=12, fig.height=12}
library(igraph)
library(ggraph)

# Get strong correlations
topic_corr <- topicCorr(stm_model_corpus)
corr_matrix <- topic_corr$cor

# Create edge list for strong correlations
edges <- as.data.frame(corr_matrix) %>%
  rownames_to_column("from") %>%
  pivot_longer(-from, names_to = "to", values_to = "correlation") %>%
  mutate(
    from_num = as.numeric(str_remove(from, "V")),
    to_num = as.numeric(str_remove(to, "V"))
  ) %>%
  filter(from_num < to_num,  # Only upper triangle
         abs(correlation) > 0.1)  # Only strong correlations

# Create graph
g <- graph_from_data_frame(edges, directed = FALSE)

# Add node attributes
V(g)$topic_num <- as.numeric(V(g)$name)
V(g)$label <- str_wrap(str_remove(topic_labels[V(g)$topic_num], "^Topic \\d+: "), 15)
V(g)$size <- colMeans(make.dt(stm_model_corpus)) * 100  # Proportional to prevalence

# Plot network
ggraph(g, layout = "fr") +
  geom_edge_link(aes(width = abs(correlation), alpha = abs(correlation)),
                 color = "#94a3b8") +
  geom_node_point(aes(size = size), color = "#3b82f6", alpha = 0.7) +
  geom_node_text(aes(label = label), size = 3, repel = TRUE) +
  scale_edge_width(range = c(0.5, 3)) +
  scale_edge_alpha(range = c(0.3, 0.8)) +
  scale_size_continuous(range = c(3, 15)) +
  labs(title = "Topic Correlation Network",
       subtitle = "Node size = topic prevalence, Edge width = correlation strength") +
  theme_graph() +
  theme(legend.position = "none")
```

---

## 10. Ridge Plot: Topic Distribution Over Time

**Show how topic proportions change over time**

```{r ridge-plot, fig.width=10, fig.height=12}
library(ggridges)

# Get topic proportions by year
ridge_data <- make.dt(stm_model_corpus, meta = meta) %>%
  select(year, all_of(paste0("Topic", top_8_topics))) %>%
  pivot_longer(-year, names_to = "topic", values_to = "proportion") %>%
  mutate(
    topic_num = as.numeric(str_remove(topic, "Topic")),
    topic_label = str_remove(topic_labels[topic_num], "^Topic \\d+: "),
    year_group = cut(year, breaks = 4, labels = c("Early", "Mid-Early", "Mid-Late", "Late"))
  )

# Ridge plot
ggplot(ridge_data, aes(x = proportion, y = topic_label, fill = topic_label)) +
  geom_density_ridges(alpha = 0.7, scale = 1.5) +
  facet_wrap(~year_group, ncol = 2) +
  scale_fill_viridis_d() +
  labs(title = "Topic Distribution Evolution Over Time",
       subtitle = "How topic prevalence distributions change across periods",
       x = "Topic Proportion",
       y = NULL) +
  theme_ridges() +
  theme(legend.position = "none") +
  scale_x_continuous(labels = scales::percent)
```

---

## 11. Coefficient Plot with Uncertainty

**Publication-quality coefficient plot**

```{r coefficient-plot, fig.width=10, fig.height=12}
# Prepare data with confidence intervals
coef_data <- corpus_effects %>%
  mutate(
    ci_lower = Difference - 1.96 * SE,
    ci_upper = Difference + 1.96 * SE,
    Label = factor(Label, levels = Label)
  ) %>%
  arrange(Difference)

# Coefficient plot
ggplot(coef_data, aes(x = Difference, y = Label)) +
  geom_vline(xintercept = 0, linetype = "dashed", size = 1, color = "#64748b") +
  geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper, color = Significant),
                 height = 0.3, size = 1) +
  geom_point(aes(color = Significant), size = 3) +
  scale_color_manual(values = c("FALSE" = "#94a3b8", "TRUE" = "#ef4444")) +
  labs(title = "Topic Prevalence Differences with 95% Confidence Intervals",
       subtitle = "Positive = more in Woman's Exponent, Negative = more in Relief Society Bulletin",
       x = "Difference (proportion)",
       y = NULL,
       color = "Statistically\nSignificant") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 9),
        legend.position = "bottom") +
  scale_x_continuous(labels = scales::percent)
```

---

## 12. Faceted Comparison Plots

**Show multiple topics side-by-side**

```{r faceted-comparison, fig.width=14, fig.height=10}
# Get top 9 topics for 3x3 grid
top_9_topics <- corpus_effects %>%
  arrange(desc(abs(Difference_Pct))) %>%
  head(9) %>%
  pull(Topic)

# Calculate means and CIs
facet_data <- topic_props %>%
  select(corpus, all_of(paste0("Topic", top_9_topics))) %>%
  pivot_longer(-corpus, names_to = "topic", values_to = "proportion") %>%
  mutate(topic_num = as.numeric(str_remove(topic, "Topic"))) %>%
  group_by(corpus, topic_num) %>%
  summarize(
    mean = mean(proportion),
    se = sd(proportion) / sqrt(n()),
    ci_lower = mean - 1.96 * se,
    ci_upper = mean + 1.96 * se,
    .groups = "drop"
  ) %>%
  mutate(
    topic_label = str_wrap(str_remove(topic_labels[topic_num], "^Topic \\d+: "), 25),
    publication = ifelse(corpus == "Relief_Society_Bulletin",
                        "Relief Society\nBulletin",
                        "Woman's\nExponent")
  )

# Faceted plot
ggplot(facet_data, aes(x = publication, y = mean, fill = publication)) +
  geom_col(alpha = 0.7) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.2) +
  facet_wrap(~topic_label, ncol = 3, scales = "free_y") +
  scale_fill_manual(values = c("Relief Society\nBulletin" = "#ef4444",
                               "Woman's\nExponent" = "#3b82f6")) +
  labs(title = "Top 9 Topics: Comparison by Publication",
       x = NULL,
       y = "Mean Topic Proportion",
       fill = "Publication") +
  theme_minimal() +
  theme(axis.text.x = element_blank(),
        legend.position = "bottom",
        strip.text = element_text(size = 9, face = "bold")) +
  scale_y_continuous(labels = scales::percent)
```

---

## Complete Visualization Section

**Add this as a new section (e.g., Section 17) after your existing visualizations:**

```{r all-visualizations}
# You can run all the visualizations above in one section
# Or split them into separate sections for your notebook
```

---

## Tips for Publication-Ready Figures

1. **Save high-resolution versions:**
```r
ggsave("figure1_scatterplot.png", width = 10, height = 8, dpi = 300)
ggsave("figure2_heatmap.pdf", width = 12, height = 8)
```

2. **Consistent color scheme:**
```r
# Use these colors throughout
rs_bulletin_color <- "#ef4444"
womans_exp_color <- "#3b82f6"
neutral_color <- "#94a3b8"
```

3. **Font sizes for presentations:**
```r
theme_minimal(base_size = 16)  # For slides
theme_minimal(base_size = 12)  # For papers
```

4. **Export tables:**
```r
write_csv(corpus_effects, "topic_differences_table.csv")
```
