---
title: "STM Topic Modeling - Complete Clean Version"
author: "Your Name"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: show
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# STM Topic Modeling - Complete Workflow

All refinements included: metadata extraction from Vol10-1923/June structure, stopword removal, year removal, manual K selection, and thematic auto-labeling.

---

## 1. Load Packages

```{r load-packages}
library(stm)
library(tidyverse)
library(dplyr)
library(stopwords)
library(igraph)
library(wordcloud)
library(tidyr)       # For data tidying
library(stringr)     # For string manipulation
library(purrr)       # For map functions
library(readr)       # For read_file and write_csv
library(tibble)      # For tibble function
library(dplyr)
library(tidyverse)
library(patchwork)
library(scales)
library(ggrepel)


set.seed(12345)
cat("Packages loaded successfully!\n")
```

---

## 2. Set Input and Output Paths

```{r set-paths}
# ============================================================================
# SET INPUT AND OUTPUT PATHS
# ============================================================================

# Input folder (where your .txt files are)
input_path <- "C:/Users/birch/OneDrive - George Mason University - O365 Production/Dissertation/textanalysis/Topicmodel/input"

# Output folder (where results will be saved)
output_path <- "C:/Users/birch/OneDrive - George Mason University - O365 Production/Dissertation/textanalysis/Topicmodel/output"

# Create output directory if it doesn't exist
if (!dir.exists(output_path)) {
  dir.create(output_path, recursive = TRUE)
  cat("✓ Created output directory\n")
}

cat("Paths configured:\n")
cat("  Input: ", input_path, "\n")
cat("  Output:", output_path, "\n\n")
```

---

## 3. Import Files

```{r import-files}
cat("=" , rep("=", 70), "\n", sep = "")
cat("FILE IMPORT\n")
cat("=" , rep("=", 70), "\n\n", sep = "")

# Get all .txt files recursively
all_files <- list.files(path = input_path, full.names = TRUE, recursive = TRUE)
file_paths <- all_files[grepl("\\.txt$", all_files, ignore.case = TRUE)]

cat("Total .txt files found:", length(file_paths), "\n")

if (length(file_paths) == 0) {
  stop("No .txt files found! Check your folder path.")
}

cat("\nFirst 5 files:\n")
for (i in 1:min(5, length(file_paths))) {
  cat(i, ":", basename(file_paths[i]), "\n")
}
```

---

## 4. Sample or Use All Files

```{r read-files}
# ============================================================================
# CHOOSE: SAMPLE OR ALL FILES
# ============================================================================

USE_SAMPLE <- FALSE  # Set to TRUE to sample, FALSE for all files
sample_size <- 300

if (USE_SAMPLE) {
  set.seed(123)
  sampled_paths <- sample(file_paths, size = sample_size)
  cat("\nUsing", sample_size, "of", length(file_paths), "files (sampled)\n")
} else {
  sampled_paths <- file_paths
  cat("\nUsing ALL", length(file_paths), "files\n")
}

cat("\nReading files...\n")

raw_texts <- tibble(
  filepath = sampled_paths,
  filename = basename(sampled_paths),
  text = map_chr(sampled_paths, ~read_file(.x))
)

cat("Successfully read", nrow(raw_texts), "files\n")
```

---

## 5. Extract Metadata

```{r extract-metadata}
cat("\n", rep("=", 70), "\n", sep = "")
cat("EXTRACTING METADATA\n")
cat(rep("=", 70), "\n\n", sep = "")

raw_texts <- raw_texts %>%
  mutate(
    volume_folder = str_extract(filepath, "Vol\\d+[-_]\\d{4}"),
    volume_num = str_extract(volume_folder, "Vol\\d+"),
    year_from_folder = as.numeric(str_extract(volume_folder, "\\d{4}$")),
    month_from_folder = str_extract(filepath, "(?<=/)(January|February|March|April|May|June|July|August|September|October|November|December)(?=/)"),
    month_from_filename = str_extract(filename, "^[A-Za-z]+"),
    volume_from_filename = str_extract(filename, "Vol\\d+"),
    year_from_filename = as.numeric(str_extract(filepath, "(?<![0-9])(1[89]\\d{2})(?![0-9])")),
    month = ifelse(!is.na(month_from_folder), month_from_folder, month_from_filename),
    volume = ifelse(!is.na(volume_num), volume_num, volume_from_filename),
    year = ifelse(!is.na(year_from_folder), year_from_folder, year_from_filename),
    doc_id = row_number(),
    word_count = str_count(text, "\\S+")
  )

cat("Metadata extracted:\n\n")
cat("Volumes:", paste(unique(na.omit(raw_texts$volume)), collapse = ", "), "\n")
cat("Years:", paste(unique(na.omit(raw_texts$year)), collapse = ", "), "\n")
cat("Months:", paste(unique(na.omit(raw_texts$month)), collapse = ", "), "\n\n")

cat("Sample:\n")
print(head(raw_texts %>% select(filename, volume, year, month, word_count), 10))

cat("\n", rep("=", 70), "\n\n", sep = "")
```

---

## 6. Text Cleaning with Stopword Removal

```{r clean-with-stopwords}
cat("\n", rep("=", 70), "\n", sep = "")
cat("TEXT CLEANING\n")
cat(rep("=", 70), "\n\n", sep = "")

# Stopwords
standard_stopwords <- stopwords::stopwords("en", source = "snowball")

custom_stopwords <- c(
  "the", "of", "and", "in", "to", "a", "is", "that", "it", "for",
  "as", "on", "with", "be", "was", "by", "are", "from", "or", "an",
  "at", "this", "which", "have", "has", "had", "but", "not", "can",
  "will", "been", "were", "their", "they", "we", "our", "would",
  "there", "what", "so", "if", "who", "than", "may", "also",
  "mrs", "mr", "miss", "dr", "ms",
  "january", "february", "march", "april", "may", "june",
  "july", "august", "september", "october", "november", "december",
  "vol", "page", "number", "volume", "board", "officer", "general",
  "thee", "thou", "whom", "no", "num", "pp", "pg", "vol", "volume", "page", "number",
  "issue", "nth", "th", "st", "nd", "rd"  # ordinal suffixes
)

# Add years dynamically
years_in_data <- unique(na.omit(raw_texts$year))
years_as_words <- as.character(years_in_data)

cat("Years found:", paste(years_as_words, collapse = ", "), "\n")
cat("Adding as stopwords...\n\n")

# OCR fragment / junk word blacklist
ocr_junk_stopwords <- c(
  "ing", "tion", "ment", "ness", "ings", "tive", "ance", "ence",
  "ered", "ters", "bers", "dren", "howe", "ould", "ight", "ther",
  "ated", "ting", "ally", "ible", "able", "ious", "eous", "ical",
  "onal", "ship", "ward", "wise", "less",
  "deliv", "presi", "inter", "encour", "terest", "testi",
  "soci", "coun", "chil", "pariel", "organiza", "ganized",
  "ference", "musser", "selion",
  "column", "columns", "chapter", "section", "article",
  "continued", "copyright", "printed"
)

all_stopwords <- unique(c(standard_stopwords, custom_stopwords,
                          ocr_junk_stopwords, years_as_words))

cat("Total stopwords:", length(all_stopwords), "\n\n")

# Regex patterns to catch OCR fragments not in the explicit list
is_ocr_fragment <- function(w) {
  grepl("^[a-z]{1,3}(tion|ment|ence|ness|ings|tive|ance)$", w) |
  grepl("^(pre|suf|dis|un|re)[a-z]{0,2}$", w) |
  grepl("^[^a-z]+$", w)
}

# Clean text
processed_texts <- raw_texts %>%
  mutate(
    text_clean = str_to_lower(text),
    
    # Remove URLs and emails
    text_clean = str_remove_all(text_clean, "http\\S+"),
    text_clean = str_remove_all(text_clean, "\\S+@\\S+"),
    
    # ---- NEW: Remove volume/issue/page markers before stripping punctuation ----
    text_clean = str_remove_all(text_clean, "\\bvol\\.?\\s*\\d+\\b"),
    text_clean = str_remove_all(text_clean, "\\bno\\.?\\s*\\d+\\b"),
    text_clean = str_remove_all(text_clean, "\\bp\\.?\\s*\\d+\\b"),
    text_clean = str_remove_all(text_clean, "\\bpp\\.?\\s*\\d+\\b"),
    
    # ---- NEW: Remove all standalone numbers (any length) ----
    text_clean = str_remove_all(text_clean, "\\b\\d+\\b"),
    
    # Remove punctuation AFTER the above (order matters!)
    text_clean = str_remove_all(text_clean, "[[:punct:]]"),
    text_clean = str_squish(text_clean),
    
    words = str_split(text_clean, "\\s+"),
    words_no_stop = map(words, ~.x[!.x %in% all_stopwords]),
    
    # ---- NEW: Also filter out pure number strings that survived ----
    words_no_numbers = map(words_no_stop, ~.x[!grepl("^\\d+$", .x)]),
    words_final = map(words_no_numbers, ~.x[nchar(.x) >= 3 & !is_ocr_fragment(.x)]),
    
    text_final = map_chr(words_final, ~paste(.x, collapse = " ")),
    final_word_count = str_count(text_final, "\\S+")
  )

cat("Cleaning stats:\n")
cat("  Avg before:", round(mean(raw_texts$word_count)), "\n")
cat("  Avg after:", round(mean(processed_texts$final_word_count)), "\n\n")

processed_texts <- processed_texts %>%
  filter(final_word_count >= 10)

cat("Documents after filtering:", nrow(processed_texts), "\n\n")
```

---

## 7. Prepare for STM

```{r prepare-stm}
cat("\n", rep("=", 70), "\n", sep = "")
cat("PREPARING FOR STM\n")
cat(rep("=", 70), "\n\n", sep = "")

processed <- textProcessor(
  documents = processed_texts$text_final,
  metadata = processed_texts %>% select(doc_id, month, volume, year, filename),
  lowercase = FALSE,
  removestopwords = FALSE,
  removenumbers = TRUE,
  removepunctuation = FALSE,
  stem = FALSE,
  wordLengths = c(3, Inf),
  sparselevel = 1,
  language = "en",
  verbose = TRUE
)

cat("\n")

out <- prepDocuments(
  documents = processed$documents,
  vocab = processed$vocab,
  meta = processed$meta,
  lower.thresh = 1,
  upper.thresh = Inf
)

docs <- out$documents
vocab <- out$vocab
meta <- out$meta

# Store the texts that actually made it into the model (for findThoughts later)
modeled_texts <- processed_texts$text_final[match(meta$doc_id, processed_texts$doc_id)]

cat("\n", rep("=", 70), "\n", sep = "")
cat("CORPUS READY\n")
cat(rep("=", 70), "\n\n", sep = "")

cat("Documents:", length(docs), "\n")
cat("Vocabulary:", length(vocab), "\n\n")

if (length(docs) == 0) stop("No documents remaining!")

cat("Sample vocab:\n", paste(vocab[1:50], collapse = ", "), "\n\n")
```

---

## 8. SET K MANUALLY

```{r set-k}
chosen_K <- 10  # CHANGE THIS

cat("Chosen K =", chosen_K, "\n\n")
```

---

## 9. Fit STM Model

```{r fit-model, cache=TRUE}
cat(rep("=", 70), "\n", sep = "")
cat("FITTING MODEL K =", chosen_K, "\n")
cat(rep("=", 70), "\n\n", sep = "")

stm_model <- stm(
  documents = docs,
  vocab = vocab,
  K = chosen_K,
  data = meta,
  max.em.its = 75,
  init.type = "Spectral",
  seed = 12345,
  verbose = TRUE
)

# Save to output folder
model_file <- file.path(output_path, paste0("stm_model_K", chosen_K, ".rds"))
saveRDS(stm_model, model_file)
cat("\n✓ Model saved to:", model_file, "\n")
```

---

## 10. Examine Topics

```{r examine-topics}
cat("\n", rep("=", 70), "\n", sep = "")
cat("TOP WORDS\n")
cat(rep("=", 70), "\n\n", sep = "")

labelTopics(stm_model, n = 15)
```

---

## 11. Auto-Generate Labels (Method 6: Specific)

```{r create-labels-semantic}
cat("\n", rep("=", 70), "\n", sep = "")
cat("AUTO-GENERATING SPECIFIC LABELS\n")
cat(rep("=", 70), "\n\n", sep = "")

create_specific_label <- function(topic_num, frex_words, prob_words) {
  frex_text <- tolower(paste(frex_words, collapse = " "))
  prob_text <- tolower(paste(prob_words, collapse = " "))
  all_words <- paste(frex_text, prob_text)
  
  if (grepl("kingdom.*gospel|baptism.*eternal", frex_text)) {
    label <- "Gospel Doctrine & Spiritual Kingdom"
  } else if (grepl("passover|paschal|feast", frex_text)) {
    label <- "Biblical Symbolism & Ancient Rituals"
  } else if (grepl("nurse.*hospital|nursing.*training", frex_text)) {
    label <- "Nursing Training & Hospital Work"
  } else if (grepl("diet.*protein|nutrition|malnutrition", frex_text)) {
    label <- "Nutrition & Dietary Science"
  } else if (grepl("recipe|tbsp|boiling|oven", frex_text)) {
    label <- "Recipes & Cooking Instructions"
  } else if (grepl("housework|housekeeping|budget", frex_text)) {
    label <- "Household Management & Budgeting"
  } else if (grepl("moral.*parent|obedience.*spiritual", frex_text)) {
    label <- "Moral Education & Character Development"
  } else if (grepl("irving|tale|literature", frex_text)) {
    label <- "American Literature (Washington Irving)"
  } else if (grepl("radium.*curie|pasteur.*science", frex_text)) {
    label <- "Scientific Biography & Discovery"
  } else if (grepl("emigration.*journey|wagon.*pioneer", frex_text)) {
    label <- "Pioneer Emigration & Journey Stories"
  } else if (grepl("sisters.*presidency|organization.*grain", frex_text)) {
    label <- "Relief Society Leadership & Organization"
  } else if (grepl("stake.*ward|attendance.*conference", frex_text)) {
    label <- "Stake & Ward Relief Society Reports"
  } else if (grepl("suffrage.*vote|legislature", frex_text)) {
    label <- "Women's Suffrage & Political Rights"
  } else if (grepl("council.*international|convention", frex_text)) {
    label <- "International Women's Councils"
  } else if (grepl("entente.*allies|war.*troops", frex_text)) {
    label <- "World War I Commentary & News"
  } else if (grepl("tableau.*song|music.*hymn", frex_text)) {
    label <- "Musical Programs & Performances"
  } else if (grepl("^\\d+.*\\d+.*\\d+", frex_text)) {
    label <- "Magazine Index & Page Numbers"
  } else if (grepl("empey.*mclelland|board.*member", frex_text)) {
    label <- "Board Member Directory"
  } else if (grepl("merino.*cotton|bleached.*gauze", frex_text)) {
    label <- "Garment & Product Advertisements"
  } else if (grepl("jerry|walter|jimmy", frex_text) && grepl("said|little", prob_text)) {
    label <- "Serialized Fiction & Stories"
  } else if (grepl("abraham.*sarai|biblical", frex_text)) {
    label <- "Biblical Narratives (Abraham)"
  } else {
    keywords <- paste(tools::toTitleCase(frex_words[1:3]), collapse= " ")
    label <- keywords
  }
  
  return(label)
}

all_top_words <- labelTopics(stm_model, n = 15)

topic_labels <- sapply(1:chosen_K, function(i) {
  frex_words <- all_top_words$frex[i, 1:10]
  prob_words <- all_top_words$prob[i, 1:10]
  specific_label <- create_specific_label(i, frex_words, prob_words)
  paste0("Topic ", i, ": ", specific_label)
})

cat("Specific labels:\n")
cat(rep("=", 70), "\n\n", sep = "")

for (i in 1:chosen_K) {
  cat(topic_labels[i], "\n")
  cat("  FREX: ", paste(all_top_words$frex[i, 1:7], collapse = ", "), "\n")
  cat("  PROB: ", paste(all_top_words$prob[i, 1:7], collapse = ", "), "\n\n")
}

# Export to output folder
frex_for_export <- apply(all_top_words$frex, 1, function(x) paste(x, collapse = ", "))
prob_for_export <- apply(all_top_words$prob, 1, function(x) paste(x, collapse = ", "))

label_export <- tibble(
  topic_num = 1:chosen_K,
  auto_label = str_remove(topic_labels, "^Topic \\d+: "),
  full_label = topic_labels,
  frex_words = frex_for_export,
  prob_words = prob_for_export,
  manual_label = ""
)

labels_file <- file.path(output_path, paste0("topic_labels_K", chosen_K, ".csv"))
write_csv(label_export, labels_file)
cat("✓ Labels saved to:", labels_file, "\n\n")
```


```{r}
# ============================================================================
# MANUAL OVERRIDE (Optional - edit labels after seeing auto-generated ones)
# ============================================================================

# Uncomment and edit any labels you want to change:
topic_labels[1] <- "Topic 1: Pioneer Heritage"
topic_labels[2] <- "Topic 2: Education"
topic_labels[3] <- "Topic 3: Women Professionalization"
topic_labels[4] <- "Topic 4: International Women's Organizations"
topic_labels[5] <- "Topic 5: Relief Society Leadership"
topic_labels[6] <- "Topic 6: Religious Leadership"
topic_labels[7] <- "Topic 7: Religious Lessons"
topic_labels[8] <- "Topic 8: Missionary Reports"
topic_labels[9] <- "Topic 9: Religious Literature"
topic_labels[10] <- "Topic 10: Scientific Advancement"



# Show final labels
cat("\n", rep("=", 70), "\n", sep = "")
cat("FINAL TOPIC LABELS\n")
cat(rep("=", 70), "\n\n", sep = "")

for (i in 1:chosen_K) {
  cat(topic_labels[i], "\n")
}
```
---

## 12. Find Examples

```{r find-examples}
topic_to_examine <- 2


cat("Examples for", topic_labels[topic_to_examine], ":\n")
cat(rep("=", 70), "\n\n", sep = "")

# modeled_texts was stored after prepDocuments — guaranteed to match model docs
thoughts <- findThoughts(stm_model, texts = modeled_texts, topics = topic_to_examine, n = 3)

for (i in 1:3) {
  cat("Example", i, ":\n", substr(thoughts$docs[[1]][i], 1, 250), "...\n\n")
}
```

```{r}
plot(stm_model, 
     type = "summary", 
     n = min(10, chosen_K),
     main = paste("Topic Prevalence (K =", chosen_K, ")"),
     xlim = c(0, 0.3))
```

```{r plot-prevalence-bar, fig.width=10, fig.height=6}
# ============================================================================
# TOPIC PREVALENCE PLOT WITH CUSTOM LABELS - WOMAN'S EXPONENT
# ============================================================================

# Step 1: Define your topic labels (corrected)
topic_labels <- c(
"Pioneer Heritage", 
"Education",
"Women Professionalization", 
"International Women's Organizations",
"Relief Society Leadership",
"Religious Leadership",
"Religious Lessons",
"Missionary Reports",
"Religious Literature",
"Scientific Advancement"

)
 

# Step 2: Get topic prevalences from the model
topic_props <- colMeans(make.dt(stm_model, meta = meta) %>% 
                        select(starts_with("Topic")))

# Step 3: Sort topics by prevalence (highest first)
sorted_order <- order(topic_props, decreasing = TRUE)

# Step 4: Create the plot
par(mar = c(5, 18, 4, 2))  # Wide left margin for labels

barplot(
  height = topic_props[sorted_order],
  names.arg = topic_labels[sorted_order],
  horiz = TRUE,
  las = 1,
  col = "#CD661D",        # Orange/brown for Woman's Exponent
  border = "#8B4513",     # Saddle brown border
  main = "Topic Prevalence - Woman's Exponent",
  xlab = "Expected Topic Proportions",
  cex.names = 0.8,
  xlim = c(0, 0.35)
)

# Step 5: Add percentage labels
text(
  x = topic_props[sorted_order] + 0.015,
  y = (1:10) * 1.2 - 0.5,
  labels = sprintf("%.1f%%", topic_props[sorted_order] * 100),
  cex = 0.8,
  col = "#8B4513",       # Saddle brown text
  font = 2
)

# Step 6: Reset margins
par(mar = c(5, 4, 4, 2))

cat("✓ Plot created successfully\n")
```

```{r}
library(ggplot2)

# Topic names
topic_names <- c(
    "Pioneer Heritage", 
"Education",
"Women Professionalization", 
"International Women's Organizations",
"Relief Society Leadership",
"Religious Leadership",
"Religious Lessons",
"Missionary Reports",
"Religious Literature",
"Scientific Advancement"

)

# Get prevalences and words
topic_props <- colMeans(make.dt(stm_model, meta = meta) %>% 
                        select(starts_with("Topic")))
top_words <- labelTopics(stm_model, n = 10)

# Create labels
labels_df <- tibble(
  topic = 1:10,
  name = topic_names,
  words = sapply(1:10, function(i) paste(top_words$prob[i, 1:10], collapse = ", ")),
  full_label = paste0(name, ": ", words),
  prevalence = topic_props
)

# Plot
ggplot(labels_df, aes(x = prevalence, y = reorder(full_label, prevalence))) +
  geom_segment(aes(x = 0, xend = prevalence, y = full_label, yend = full_label),
               linewidth = 1.2, color = "black") +
  geom_point(aes(x = prevalence, y = full_label), size = 0.5) +  # Small endpoint
  labs(
    title = "Topic Prevalence (K = 10)",
    x = "Expected Topic Proportions",
    y = NULL
  ) +
  theme_minimal(base_size = 10) +
  theme(
    axis.text.y = element_text(size = 8, hjust = 1),
    plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_x_continuous(limits = c(0, 0.35),
                    breaks = seq(0, 0.35, 0.05))
```

---

## 🎯 What This Does:

**Before:**
```
Topic 5: one, mother, little, time, now, said, home, see, just
```

**After:**
```
Serialized Fiction & Stories: one, mother, little, time, now, said, home, see, just
```

---

## 13. Visualizations

### Topic Prevalence

```{r plot-prevalence-time, fig.width=10, fig.height=6}

##Topic Prevalence over time
# ============================================================================
# TOPIC PREVALENCE OVER TIME WITH CORPUS COMPARISON
# ============================================================================
# ============================================================================
# SECTION: TOPIC PREVALENCE OVER TIME
# ============================================================================

cat("=" , rep("=", 70), "\n", sep = "")
cat("TOPIC PREVALENCE OVER TIME\n")
cat("=" , rep("=", 70), "\n\n", sep = "")

# Step 1: Estimate effect of year on topics
cat("Estimating time effects...\n")

prep_time <- estimateEffect(
  formula = 1:chosen_K ~ s(year),  # Smooth function of year
  stmobj = stm_model,
  metadata = meta,
  uncertainty = "Global"
)

cat("✓ Estimation complete\n\n")

# ============================================================================
# OPTION 1: Plot Top 6 Topics by Prevalence
# ============================================================================

# Get topic prevalences
topic_props <- make.dt(stm_model, meta = meta)
topic_prevalences <- colMeans(topic_props %>% select(starts_with("Topic")))

# Get top 6 most prevalent topics
top_6_topics <- order(topic_prevalences, decreasing = TRUE)[1:6]

cat("Plotting top 6 most prevalent topics over time...\n")
cat("Topics:", paste(top_6_topics, collapse = ", "), "\n\n")

# Set up plotting area
par(mfrow = c(2, 3), mar = c(4, 4, 3, 1))

for (topic_num in top_6_topics) {
  plot(
    prep_time,
    covariate = "year",
    model = stm_model,
    topics = topic_num,
    method = "continuous",
    xlim = range(meta$year, na.rm = TRUE),
    main = str_wrap(str_remove(topic_labels[topic_num], "^Topic \\d+: "), 30),
    xlab = "Year",
    ylab = "Topic Proportion",
    linecol = "#3b82f6",
    printlegend = TRUE,
    ci.level = 0.95,
    lwd = 2
  )
}

par(mfrow = c(1, 1))
cat("✓ Plots created\n\n")
```

##Scatter plot
```{r}
# ============================================================================
# CREATE TIME SERIES DATA
# ============================================================================

# Get document-topic proportions with year
topic_time_data <- make.dt(stm_model, meta = meta) %>%
  select(starts_with("Topic"), year) %>%
  filter(!is.na(year)) %>%
  group_by(year) %>%
  summarize(across(starts_with("Topic"), mean, na.rm = TRUE), .groups = "drop") %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "prevalence") %>%
  mutate(
    topic_num = as.numeric(str_remove(topic, "Topic")),
    topic_label = str_wrap(str_remove(topic_labels[topic_num], "^Topic \\d+: "), 30)
  )

# Filter for top 6 topics
topic_time_top6 <- topic_time_data %>%
  filter(topic_num %in% top_6_topics)

# ============================================================================
# CREATE FACETED PLOT
# ============================================================================

ggplot(topic_time_top6, aes(x = year, y = prevalence)) +
  geom_line(color = "#E0EEEE", size = 1.5) +
  geom_point(color = "#E0EEEE", size = 3, alpha = 0.6) +
  geom_smooth(method = "loess", color = "#CD661D", linetype = "dashed", 
              se = TRUE, alpha = 0.2) +
  facet_wrap(~topic_label, ncol = 3, scales = "free_y") +
  labs(
    title = "Topic Prevalence Over Time: Top 6 Most Prevalent Topics",
    subtitle = "Blue line = actual data | Red dashed line = trend",
    x = "Year",
    y = "Mean Topic Proportion"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(size = 10, face = "bold"),
    panel.grid.minor = element_blank(),
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(size = 11, color = "#FFF8DC")
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1))
```
##All topics in one graph
```{r}
# Plot ALL topics
ggplot(topic_time_data, aes(x = year, y = prevalence)) +
  geom_line(color = "#CD661d", size = 0.8) +
  geom_point(color = "#CD661d", size = 1.5, alpha = 0.5) +
  facet_wrap(~topic_label, ncol = 4, scales = "free_y") +
  labs(
    title = "Complete Topic Evolution Over Time (Woman's Exponent)",
    subtitle = "All 20 topics across years",
    x = "Year",
    y = "Topic Proportion"
  ) +
  theme_minimal(base_size = 10) +
  theme(
    strip.text = element_text(size = 7, face = "bold"),
    panel.grid.minor = element_blank()
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1))
```

##Interactive time lapse
```{r}
# Choose one topic to examine in detail
topic_to_examine <- 2  # CHANGE THIS to any topic number

# Filter data
topic_detail <- topic_time_data %>%
  filter(topic_num == topic_to_examine)

# Create detailed plot with trend
ggplot(topic_detail, aes(x = year, y = prevalence)) +
  geom_line(color = "#3b82f6", size = 1.5) +
  geom_point(color = "#3b82f6", size = 4, alpha = 0.7) +
  geom_smooth(method = "loess", color = "#ef4444", 
              fill = "#fecaca", alpha = 0.3, size = 1) +
  labs(
    title = str_remove(topic_labels[topic_to_examine], "^Topic \\d+: "),
    subtitle = "Points = annual averages | Red band = smoothed trend with confidence interval",
    x = "Year",
    y = "Topic Proportion"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(size = 11, color = "#64748b"),
    panel.grid.minor = element_blank()
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1)) +
  scale_x_continuous(breaks = seq(min(topic_detail$year), 
                                   max(topic_detail$year), by = 2))
```

### Topic Correlation Network

```{r plot-correlation, fig.width=10, fig.height=8}
mod.out.corr <- topicCorr(stm_model)
plot(mod.out.corr, main = "Topic Correlation Network")
```

### Word Cloud for Topic 1

```{r wordcloud-1, fig.width=8, fig.height=6}
cloud(stm_model, 
      topic = 9,
      scale = c(3, 0.5),
      main = topic_labels[1])
```

### Create Word Clouds for All Topics

```{r wordcloud-all, fig.width=8, fig.height=6, eval=FALSE}
# Set eval=TRUE to generate word clouds for all topics
for (i in 1:chosen_K) {
  cloud(stm_model, 
        topic = i,
        scale = c(3, 0.5),
        main = topic_labels[i])
}
```

### Topic Quality

```{r topic-quality, fig.width=8, fig.height=6}
topicQuality(stm_model, documents = docs)
```

### Compare Two Topics

```{r compare-topics, fig.width=10, fig.height=6}
# Compare two topics
plot(stm_model, 
     type = "perspectives", 
     topics = c(2, 3),
     main = paste("Comparing", topic_labels[2], "vs", topic_labels[3]))
```

---
```{r topic-prevalence-stats}
# Get average proportion of each topic across all documents
topic_props <- make.dt(stm_model, meta = meta)

prevalence_summary <- topic_props %>%
  select(starts_with("Topic")) %>%
  summarise(across(everything(), mean, na.rm = TRUE)) %>%
  pivot_longer(everything(), names_to = "topic", values_to = "mean_proportion") %>%
  mutate(
    topic_num   = as.numeric(str_remove(topic, "Topic")),
    label       = topic_labels[topic_num],
    percentage  = round(mean_proportion * 100, 2),
    rank        = rank(-mean_proportion)
  ) %>%
  arrange(rank) %>%
  select(rank, label, percentage)

print(prevalence_summary)
```

---
```{r trend-summary}
topic_trends <- topic_time_data %>%
  group_by(topic_num, topic_label) %>%
  summarise(
    start_prev = first(prevalence),
    end_prev   = last(prevalence),
    change     = end_prev - start_prev,
    pct_change = round((change / start_prev) * 100, 1),
    trend      = case_when(
      change >  0.005 ~ "Increasing",
      change < -0.005 ~ "Decreasing",
      TRUE            ~ "Stable"
    ),
    .groups = "drop"
  ) %>%
  arrange(desc(abs(pct_change)))

# Print a readable sentence for each topic
cat("TOPIC CHANGE SUMMARY\n")
cat(rep("=", 50), "\n\n", sep = "")

for (i in 1:nrow(topic_trends)) {
  direction <- ifelse(topic_trends$pct_change[i] > 0, "increased", "decreased")
  cat(sprintf("Topic %d (%s): %s by %.1f%% over the study period\n",
              topic_trends$topic_num[i],
              topic_trends$topic_label[i],
              direction,
              abs(topic_trends$pct_change[i])))
}

# Also print as a clean table
cat("\n\nSUMMARY TABLE\n")
print(topic_trends %>% select(topic_num, topic_label, pct_change, trend))
```

**What was wrong:** The chunk saved results into `topic_trends` but then tried to print `trend_summary` — R couldn't find that name and threw the error.

**What this now outputs**, for example:
```
Topic 1 (Pioneer Heritage): decreased by 14.2% over the study period
Topic 3 (Women Professionalization): increased by 8.7% over the study period
...

## 14. Within-Topic Vocabulary Comparison (Early vs Late Period)

When the same topic appears across both eras of the Exponent, does the **language** shift? This reveals how the publication's framing of shared concerns evolved over time.

```{r vocab-comparison-era, fig.width=16, fig.height=20}
cat(rep("=", 70), "\n", sep = "")
cat("WITHIN-TOPIC VOCABULARY COMPARISON (EARLY vs LATE)\n")
cat(rep("=", 70), "\n\n", sep = "")

# Build document-topic proportions with metadata
topic_props_we <- make.dt(stm_model, meta = meta)

# Split into early and late eras at median year
median_year <- median(meta$year, na.rm = TRUE)
topic_props_we <- topic_props_we %>%
  mutate(era = ifelse(year <= median_year, "Early", "Late"))

cat("Era split at year", median_year, "\n")
cat("  Early:", sum(topic_props_we$era == "Early"), "documents\n")
cat("  Late: ", sum(topic_props_we$era == "Late"), "documents\n\n")

# Function: get word frequencies for top-quartile docs of a topic in an era
# (includes OCR junk filtering as safety net)
get_topic_words_by_era <- function(topic_num, era_name) {
  topic_col <- paste0("Topic", topic_num)
  era_docs <- topic_props_we %>% filter(era == era_name)
  threshold <- quantile(era_docs[[topic_col]], 0.75, na.rm = TRUE)

  doc_ids <- era_docs %>%
    filter(.data[[topic_col]] >= threshold) %>%
    pull(doc_id)

  words <- processed_texts %>%
    filter(doc_id %in% doc_ids) %>%
    pull(text_final) %>%
    paste(collapse = " ") %>%
    str_split("\\s+") %>%
    `[[`(1)

  freq <- sort(table(words), decreasing = TRUE)
  tibble(word = names(freq), count = as.integer(freq)) %>%
    mutate(proportion = count / sum(count)) %>%
    filter(
      nchar(word) >= 4,
      !word %in% all_stopwords,
      !is_ocr_fragment(word)
    )
}

# Pick the 6 most prevalent topics for comparison
top_6_for_vocab <- order(colMeans(topic_props_we %>% select(starts_with("Topic"))),
                         decreasing = TRUE)[1:min(6, chosen_K)]

cat("Comparing vocabulary for top", length(top_6_for_vocab), "topics:\n")
for (t in top_6_for_vocab) {
  cat(sprintf("  T%d: %s\n", t, str_remove(topic_labels[t], "^Topic \\d+: ")))
}
cat("\n")

# Build log-ratio plots
vocab_plots <- list()
for (idx in seq_along(top_6_for_vocab)) {
  t <- top_6_for_vocab[idx]

  words_early <- get_topic_words_by_era(t, "Early")
  words_late  <- get_topic_words_by_era(t, "Late")

  word_compare <- full_join(
    words_early %>% select(word, early_prop = proportion),
    words_late  %>% select(word, late_prop = proportion),
    by = "word"
  ) %>%
    replace_na(list(early_prop = 0.0001, late_prop = 0.0001)) %>%
    mutate(
      log_ratio = log2(early_prop / late_prop),
      avg_prop = (early_prop + late_prop) / 2
    ) %>%
    filter(avg_prop > 0.001) %>%
    arrange(desc(abs(log_ratio)))

  # Top 20 words each direction
  top_early <- word_compare %>% filter(log_ratio > 0) %>% head(20)
  top_late  <- word_compare %>% filter(log_ratio < 0) %>% head(20)
  plot_words <- bind_rows(top_early, top_late) %>%
    mutate(
      direction = ifelse(log_ratio > 0,
                         paste0("More in Early (\u2264", median_year, ")"),
                         paste0("More in Late (>", median_year, ")")),
      word = reorder(word, log_ratio)
    )

  early_label <- paste0("More in Early (\u2264", median_year, ")")
  late_label  <- paste0("More in Late (>", median_year, ")")

  p <- ggplot(plot_words, aes(x = log_ratio, y = word, fill = direction)) +
    geom_col(alpha = 0.8) +
    geom_vline(xintercept = 0, linewidth = 0.8) +
    scale_fill_manual(values = setNames(c("#CD661D", "#8B4513"),
                                        c(early_label, late_label))) +
    labs(title = paste0("T", t, ": ",
                        str_trunc(str_remove(topic_labels[t], "^Topic \\d+: "), 35)),
         x = "Log2 Ratio (Early / Late)", y = NULL, fill = NULL) +
    theme_minimal(base_size = 8) +
    theme(legend.position = "none",
          plot.title = element_text(size = 10, face = "bold"))

  vocab_plots[[idx]] <- p
}

# Combine plots
if (length(vocab_plots) >= 6) {
  (vocab_plots[[1]] | vocab_plots[[2]] | vocab_plots[[3]]) /
  (vocab_plots[[4]] | vocab_plots[[5]] | vocab_plots[[6]]) +
    plot_annotation(
      title = "Within-Topic Vocabulary Shifts: Early vs Late Period",
      subtitle = paste0("Top 20 words each era emphasizes differently (split at ",
                        median_year, ")"),
      theme = theme(plot.title = element_text(size = 16, face = "bold"))
    )
} else if (length(vocab_plots) >= 1) {
  wrap_plots(vocab_plots, ncol = min(3, length(vocab_plots))) +
    plot_annotation(title = "Within-Topic Vocabulary Shifts: Early vs Late Period")
}
```

---

## 15. Topic Diversity & Concentration

Is the Exponent topically diverse across its articles, or do most articles focus narrowly on a single topic?

```{r topic-diversity, fig.width=12, fig.height=10}
cat(rep("=", 70), "\n", sep = "")
cat("TOPIC DIVERSITY ANALYSIS\n")
cat(rep("=", 70), "\n\n", sep = "")

# Shannon entropy per document (higher = more diverse)
doc_entropy <- topic_props_we %>%
  select(doc_id, starts_with("Topic")) %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "p") %>%
  filter(p > 0) %>%
  group_by(doc_id) %>%
  summarize(entropy = -sum(p * log2(p)), .groups = "drop")

# Gini concentration per document
doc_gini <- topic_props_we %>%
  select(doc_id, starts_with("Topic")) %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "p") %>%
  group_by(doc_id) %>%
  summarize(
    max_topic_prop = max(p),
    gini = 1 - sum(p^2),
    .groups = "drop"
  )

# Summary
diversity_summary <- doc_entropy %>%
  left_join(doc_gini, by = "doc_id") %>%
  summarize(
    mean_entropy = mean(entropy),
    sd_entropy = sd(entropy),
    mean_gini = mean(gini),
    mean_max_prop = mean(max_topic_prop),
    pct_strong_exemplar = mean(max_topic_prop >= 0.4) * 100
  )

cat("Diversity Metrics (Woman's Exponent):\n\n")
cat(sprintf("  Mean Shannon Entropy:     %.2f bits\n", diversity_summary$mean_entropy))
cat(sprintf("  SD Entropy:               %.2f\n", diversity_summary$sd_entropy))
cat(sprintf("  Mean Gini (inv-Herf):     %.3f\n", diversity_summary$mean_gini))
cat(sprintf("  Mean Dominant Topic %%:    %.1f%%\n", diversity_summary$mean_max_prop * 100))
cat(sprintf("  Strong Exemplars (>40%%):  %.1f%% of documents\n\n", diversity_summary$pct_strong_exemplar))

# Entropy distribution
p1 <- ggplot(doc_entropy, aes(x = entropy)) +
  geom_density(fill = "#CD661D", alpha = 0.5, linewidth = 0.8, color = "#8B4513") +
  labs(title = "Topic Diversity per Document",
       subtitle = "Higher entropy = article discusses more topics evenly",
       x = "Shannon Entropy (bits)", y = "Density") +
  theme_minimal(base_size = 12)

# Dominant topic concentration
p2 <- ggplot(doc_gini, aes(x = max_topic_prop)) +
  geom_density(fill = "#CD661D", alpha = 0.5, linewidth = 0.8, color = "#8B4513") +
  geom_vline(xintercept = 0.4, linetype = "dashed", color = "grey40") +
  annotate("text", x = 0.42, y = 0, label = "Exemplar\nthreshold", size = 3, hjust = 0) +
  labs(title = "Topic Concentration per Document",
       subtitle = "Higher = article dominated by single topic; dashed line = 40% exemplar threshold",
       x = "Dominant Topic Proportion", y = "Density") +
  theme_minimal(base_size = 12) +
  scale_x_continuous(labels = percent_format())

p1 / p2
```

### Effective Number of Topics

```{r effective-topics, fig.width=10, fig.height=5}
# Publication-level topic distribution
pub_topic_dist <- topic_props_we %>%
  summarize(across(starts_with("Topic"), mean)) %>%
  pivot_longer(everything(), names_to = "topic", values_to = "prevalence") %>%
  mutate(
    topic_num = as.integer(str_remove(topic, "Topic")),
    label = str_trunc(str_remove(topic_labels[topic_num], "^Topic \\d+: "), 25)
  )

# Effective number of topics = exp(entropy of topic distribution)
eff_topics <- pub_topic_dist %>%
  filter(prevalence > 0) %>%
  summarize(eff = exp(-sum(prevalence * log(prevalence)))) %>%
  pull(eff)

cat(sprintf("Effective number of topics: %.1f (of %d)\n\n", eff_topics, chosen_K))

ggplot(pub_topic_dist, aes(x = reorder(label, -prevalence), y = prevalence)) +
  geom_col(fill = "#CD661D", alpha = 0.8) +
  labs(title = "Topic Weight Distribution — Woman's Exponent",
       subtitle = paste0("Effective topics: ", round(eff_topics, 1), " of ", chosen_K),
       x = NULL, y = "Mean Proportion") +
  theme_minimal(base_size = 10) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8)) +
  scale_y_continuous(labels = percent_format())
```

---

## 16. Topic Prevalence Heatmap Over Time

```{r topic-time-heatmap, fig.width=12, fig.height=7}
# Yearly topic prevalence
yearly_topics_we <- topic_props_we %>%
  filter(!is.na(year)) %>%
  select(year, starts_with("Topic")) %>%
  group_by(year) %>%
  summarize(across(starts_with("Topic"), mean), .groups = "drop") %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "prevalence") %>%
  mutate(
    topic_num = as.integer(str_remove(topic, "Topic")),
    label = str_remove(topic_labels[topic_num], "^Topic \\d+: "),
    short_label = paste0("T", topic_num, ": ", str_trunc(label, 20))
  )

ggplot(yearly_topics_we, aes(x = year, y = short_label, fill = prevalence)) +
  geom_tile(color = "white", linewidth = 0.3) +
  scale_fill_gradient(low = "white", high = "#8B4513",
                      labels = percent_format()) +
  labs(title = "Topic Prevalence Over Time — Woman's Exponent",
       subtitle = "Darker = higher prevalence in that year",
       x = "Year", y = NULL, fill = "Prevalence") +
  theme_minimal(base_size = 11) +
  theme(panel.grid = element_blank(),
        plot.title = element_text(face = "bold", size = 14)) +
  scale_y_discrete(limits = rev) +
  scale_x_continuous(breaks = sort(unique(yearly_topics_we$year)))
```

---

## 17. Topic Percentage Change (Early vs Late Era)

How much does each topic's prevalence **shift** from the early period to the late period?

```{r topic-pct-change-era, fig.width=12, fig.height=8}
cat(rep("=", 70), "\n", sep = "")
cat("PERCENTAGE CHANGE IN TOPICS: EARLY vs LATE ERA\n")
cat(rep("=", 70), "\n\n", sep = "")

# Mean prevalence per topic per era
era_means <- topic_props_we %>%
  group_by(era) %>%
  summarize(across(starts_with("Topic"), mean), .groups = "drop") %>%
  pivot_longer(-era, names_to = "topic", values_to = "prevalence") %>%
  mutate(topic_num = as.integer(str_remove(topic, "Topic"))) %>%
  pivot_wider(names_from = era, values_from = prevalence)

era_change <- era_means %>%
  mutate(
    label = str_remove(topic_labels[topic_num], "^Topic \\d+: "),
    early_pct = Early * 100,
    late_pct = Late * 100,
    abs_change = late_pct - early_pct,
    pct_change = ifelse(Early > 0.001,
                        (Late - Early) / Early * 100,
                        NA_real_),
    direction = case_when(
      abs_change > 0.5  ~ "Grew in Late Period",
      abs_change < -0.5 ~ "Declined in Late Period",
      TRUE ~ "Stable"
    )
  ) %>%
  arrange(desc(abs_change))

cat(sprintf("Era split: Early (\u2264%d) vs Late (>%d)\n\n", median_year, median_year))
cat(sprintf("%-35s  %7s  %7s  %8s  %9s\n",
            "Topic", "Early%", "Late%", "Change", "% Change"))
cat(rep("-", 80), "\n", sep = "")
for (i in 1:nrow(era_change)) {
  r <- era_change[i, ]
  pct_str <- ifelse(is.na(r$pct_change), "N/A", sprintf("%+.0f%%", r$pct_change))
  cat(sprintf("%-35s  %5.1f%%  %5.1f%%  %+6.1fpp  %9s\n",
              str_trunc(r$label, 35), r$early_pct, r$late_pct, r$abs_change, pct_str))
}

# Absolute change bar chart
p_abs <- era_change %>%
  mutate(display = paste0("T", topic_num, ": ", str_trunc(label, 28)),
         display = reorder(display, abs_change)) %>%
  ggplot(aes(x = abs_change, y = display, fill = direction)) +
  geom_col(alpha = 0.85) +
  geom_vline(xintercept = 0, linewidth = 1) +
  scale_fill_manual(values = c("Grew in Late Period" = "#458B74",
                                "Declined in Late Period" = "#CD661D",
                                "Stable" = "#94a3b8")) +
  labs(title = paste0("Topic Change: Early (\u2264", median_year,
                      ") vs Late (>", median_year, ") Period"),
       subtitle = "Absolute change in percentage points of topic prevalence",
       x = "Change (percentage points)", y = NULL, fill = NULL) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom", panel.grid.major.y = element_blank())

print(p_abs)
```

```{r topic-pct-change-relative-era, fig.width=12, fig.height=8}
# Relative (%) change bar chart
era_change_filtered <- era_change %>%
  filter(!is.na(pct_change), abs(pct_change) < 500) %>%
  mutate(display = paste0("T", topic_num, ": ", str_trunc(label, 28)),
         display = reorder(display, pct_change))

if (nrow(era_change_filtered) > 0) {
  ggplot(era_change_filtered, aes(x = pct_change, y = display, fill = direction)) +
    geom_col(alpha = 0.85) +
    geom_vline(xintercept = 0, linewidth = 1) +
    scale_fill_manual(values = c("Grew in Late Period" = "#458B74",
                                  "Declined in Late Period" = "#CD661D",
                                  "Stable" = "#94a3b8")) +
    labs(title = "Relative Percentage Change in Topic Prevalence",
         subtitle = paste0("How much did each topic grow or shrink relative to its early-period (\u2264",
                           median_year, ") baseline?"),
         x = "Relative Change (%)", y = NULL, fill = NULL) +
    theme_minimal(base_size = 11) +
    theme(legend.position = "bottom", panel.grid.major.y = element_blank())
}
```

---

## 18. Topic Evolution Summary

```{r evolution-summary-scatter, fig.width=10, fig.height=10}
cat(rep("=", 70), "\n", sep = "")
cat("TOPIC EVOLUTION SUMMARY\n")
cat(rep("=", 70), "\n\n", sep = "")

topic_evolution <- era_change %>%
  mutate(
    evolution_type = case_when(
      abs(abs_change) <= 0.5 ~ "Stable",
      abs_change > 0.5  ~ "Growing",
      abs_change < -0.5 ~ "Declining"
    ),
    evolution_type = factor(evolution_type,
                            levels = c("Stable", "Growing", "Declining"))
  )

cat("TOPIC EVOLUTION CLASSIFICATION:\n\n")
for (etype in c("Stable", "Growing", "Declining")) {
  cat(toupper(etype), ":\n")
  subset <- topic_evolution %>% filter(evolution_type == etype)
  if (nrow(subset) > 0) {
    for (i in 1:nrow(subset)) {
      r <- subset[i, ]
      cat(sprintf("  T%d: %s (Early: %.1f%%, Late: %.1f%%, %+.1fpp)\n",
                  r$topic_num, r$label, r$early_pct, r$late_pct, r$abs_change))
    }
  } else {
    cat("  (none)\n")
  }
  cat("\n")
}

# Scatter plot: early vs late prevalence
ggplot(topic_evolution, aes(x = early_pct, y = late_pct, color = evolution_type)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed",
              color = "grey70", linewidth = 1) +
  geom_point(size = 5, alpha = 0.8) +
  geom_text_repel(aes(label = paste0("T", topic_num, ": ", str_trunc(label, 25))),
                  size = 3, max.overlaps = 20, show.legend = FALSE) +
  scale_color_manual(values = c(
    "Stable" = "#6495ED",
    "Growing" = "#458B74",
    "Declining" = "#CD661D"
  )) +
  labs(title = "Topic Evolution: Early vs Late Period",
       subtitle = paste0("Diagonal = no change | Above = grew in late period (",
                         median_year + 1, "-", max(meta$year, na.rm = TRUE),
                         ") | Below = declined"),
       x = paste0("Early Period Mean % (\u2264", median_year, ")"),
       y = paste0("Late Period Mean % (>", median_year, ")"),
       color = "Evolution Type") +
  theme_minimal(base_size = 13) +
  theme(legend.position = "bottom",
        plot.title = element_text(face = "bold", size = 16)) +
  coord_fixed()
```

---

## 19. Export Results

```{r export-results}
# Document-topic proportions
doc_topics <- make.dt(stm_model, meta = meta)
doc_topics_full <- doc_topics %>%
  left_join(processed_texts %>% select(doc_id, filename, volume, year, month), by = "doc_id")

doc_file <- file.path(output_path, paste0("document_topics_K", chosen_K, ".csv"))
write_csv(doc_topics_full, doc_file)

# Top words
top_words <- labelTopics(stm_model, n = 20)
topic_words_df <- tibble(
  topic = 1:chosen_K,
  label = topic_labels,
  top_prob = apply(top_words$prob, 1, function(x) paste(x, collapse = ", ")),
  top_frex = apply(top_words$frex, 1, function(x) paste(x, collapse = ", "))
)

words_file <- file.path(output_path, paste0("topic_words_K", chosen_K, ".csv"))
write_csv(topic_words_df, words_file)

cat("Results exported!\n")
cat("  -", doc_file, "\n")
cat("  -", words_file, "\n")
```

---

## 20. Save Session

```{r save-session}
session_file <- file.path(output_path, paste0("stm_session_K", chosen_K, ".RData"))
save(stm_model, docs, vocab, meta, raw_texts, processed_texts,
     all_stopwords, topic_labels, file = session_file)

cat("Session saved to:", session_file, "\n")
cat("\nTo reload: load('", session_file, "')\n", sep = "")
```

---

## Session Info

```{r session-info}
sessionInfo()
```
