---
title: "STM Topic Modeling - Relief Society Bulletin"
author: "Your Name"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: show
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# STM Topic Modeling - Complete Workflow

All refinements included: metadata extraction, stopword removal, year removal,
manual K selection, thematic auto-labeling, and article-topic linking.

---

## 1. Load Packages

```{r load-packages}
library(stm)
library(tidyverse)
library(dplyr)
library(stopwords)
library(igraph)
library(wordcloud)
library(tidyr)
library(stringr)
library(purrr)
library(readr)
library(tibble)
library(RColorBrewer)

set.seed(12345)
cat("Packages loaded successfully!\n")
```

---

## 2. Set Input and Output Paths

```{r set-paths}
# ============================================================================
# SET INPUT AND OUTPUT PATHS
# ============================================================================

# Input folder (where your .txt files are)
input_path <- "C:/Users/birch/OneDrive - George Mason University - O365 Production/Dissertation/textanalysis/Topicmodel/input2"

# Output folder (where results will be saved)
output_path <- "C:/Users/birch/OneDrive - George Mason University - O365 Production/Dissertation/textanalysis/Topicmodel/output"

# Create output directory if it doesn't exist
if (!dir.exists(output_path)) {
  dir.create(output_path, recursive = TRUE)
  cat("Created output directory\n")
}

cat("Paths configured:\n")
cat("  Input:  ", input_path, "\n")
cat("  Output: ", output_path, "\n\n")
```

---

## 3. Import Files

```{r import-files}
cat("=", rep("=", 70), "\n", sep = "")
cat("FILE IMPORT\n")
cat("=", rep("=", 70), "\n\n", sep = "")

# Get all .txt files recursively
all_files <- list.files(path = input_path, full.names = TRUE, recursive = TRUE)
file_paths <- all_files[grepl("\\.txt$", all_files, ignore.case = TRUE)]

cat("Total .txt files found:", length(file_paths), "\n")

if (length(file_paths) == 0) {
  stop("No .txt files found! Check your folder path.")
}

cat("\nFirst 5 files:\n")
for (i in 1:min(5, length(file_paths))) {
  cat(i, ":", basename(file_paths[i]), "\n")
}
```

---

## 4. Sample or Use All Files

```{r read-files}
# ============================================================================
# CHOOSE: SAMPLE OR ALL FILES
# ============================================================================
USE_SAMPLE <- FALSE  # Set to TRUE to sample, FALSE for all files
sample_size <- 300

if (USE_SAMPLE) {
  set.seed(123)
  sampled_paths <- sample(file_paths, size = sample_size)
  cat("\nUsing", sample_size, "of", length(file_paths), "files (sampled)\n")
} else {
  sampled_paths <- file_paths
  cat("\nUsing ALL", length(file_paths), "files\n")
}

# Remove any files inside backup folders
sampled_paths <- sampled_paths[!grepl("_backups", sampled_paths)]
cat("After removing backup files:", length(sampled_paths), "files remain\n")

cat("\nReading files...\n")
raw_texts <- tibble(
  filepath = sampled_paths,
  filename = basename(sampled_paths),
  text = map_chr(sampled_paths, ~read_file(.x))
)
cat("Successfully read", nrow(raw_texts), "files\n")
```

---

## 5. Extract Metadata

```{r extract-metadata}
cat("\n", rep("=", 70), "\n", sep = "")
cat("EXTRACTING METADATA\n")
cat(rep("=", 70), "\n\n", sep = "")

raw_texts <- raw_texts %>%
  mutate(
    volume_folder    = str_extract(filepath, "Vol\\d+[-_]\\d{4}"),
    volume_num       = str_extract(volume_folder, "Vol\\d+"),
    year_from_folder = as.numeric(str_extract(volume_folder, "\\d{4}$")),
    month_from_folder   = str_extract(filepath, "(?<=/)(January|February|March|April|May|June|July|August|September|October|November|December)(?=/)"),
    month_from_filename = str_extract(filename, "^[A-Za-z]+"),
    volume_from_filename = str_extract(filename, "Vol\\d+"),
    year_from_filename  = as.numeric(str_extract(filepath, "\\d{4}")),
    month  = ifelse(!is.na(month_from_folder), month_from_folder, month_from_filename),
    volume = ifelse(!is.na(volume_num), volume_num, volume_from_filename),
    year   = ifelse(!is.na(year_from_folder), year_from_folder, year_from_filename),
    doc_id     = row_number(),
    word_count = str_count(text, "\\S+")
  )

cat("Metadata extracted:\n\n")
cat("Volumes:", paste(unique(na.omit(raw_texts$volume)), collapse = ", "), "\n")
cat("Years:",   paste(unique(na.omit(raw_texts$year)),   collapse = ", "), "\n")
cat("Months:",  paste(unique(na.omit(raw_texts$month)),  collapse = ", "), "\n\n")

cat("Sample (first 10 rows):\n")
print(head(raw_texts %>% select(filename, volume, year, month, word_count), 10))

cat("\n", rep("=", 70), "\n\n", sep = "")
```

---

## 6. Text Cleaning with Stopword Removal

```{r clean-text}
cat("\n", rep("=", 70), "\n", sep = "")
cat("TEXT CLEANING\n")
cat(rep("=", 70), "\n\n", sep = "")

# Standard + custom stopwords
standard_stopwords <- stopwords::stopwords("en", source = "snowball")

custom_stopwords <- c(
  "the", "of", "and", "in", "to", "a", "is", "that", "it", "for",
  "as", "on", "with", "be", "was", "by", "are", "from", "or", "an",
  "at", "this", "which", "have", "has", "had", "but", "not", "can",
  "will", "been", "were", "their", "they", "we", "our", "would",
  "there", "what", "so", "if", "who", "than", "may", "also",
  "mrs", "mr", "miss", "dr", "ms",
  "january", "february", "march", "april", "june",
  "july", "august", "september", "october", "november", "december",
  "vol", "page", "number", "volume", "board", "officer", "general"
)

# Add years dynamically from the data
years_in_data <- unique(na.omit(raw_texts$year))
years_as_words <- as.character(years_in_data)

cat("Years found:", paste(years_as_words, collapse = ", "), "\n")
cat("Adding as stopwords...\n\n")

# OCR fragment / junk word blacklist
ocr_junk_stopwords <- c(
  "ing", "tion", "ment", "ness", "ings", "tive", "ance", "ence",
  "ered", "ters", "bers", "dren", "howe", "ould", "ight", "ther",
  "ated", "ting", "ally", "ible", "able", "ious", "eous", "ical",
  "onal", "ship", "ward", "wise", "less",
  "deliv", "presi", "inter", "encour", "terest", "testi",
  "soci", "coun", "chil", "pariel", "organiza", "ganized",
  "ference", "musser", "selion",
  "column", "columns", "chapter", "section", "article",
  "continued", "copyright", "printed"
)

all_stopwords <- unique(c(standard_stopwords, custom_stopwords,
                          ocr_junk_stopwords, years_as_words))
cat("Total stopwords:", length(all_stopwords), "\n\n")

# Regex patterns to catch OCR fragments not in the explicit list
is_ocr_fragment <- function(w) {
  grepl("^[a-z]{1,3}(tion|ment|ence|ness|ings|tive|ance)$", w) |
  grepl("^(pre|suf|dis|un|re)[a-z]{0,2}$", w) |
  grepl("^[^a-z]+$", w)
}

# Clean text
processed_texts <- raw_texts %>%
  mutate(
    text_clean       = str_to_lower(text),
    text_clean       = str_remove_all(text_clean, "http\\S+"),
    text_clean       = str_remove_all(text_clean, "\\S+@\\S+"),
    text_clean       = str_remove_all(text_clean, "[[:punct:]]"),
    text_clean       = str_squish(text_clean),
    words            = str_split(text_clean, "\\s+"),
    words_no_stop    = map(words, ~.x[!.x %in% all_stopwords]),
    words_final      = map(words_no_stop, ~.x[nchar(.x) >= 3 & !is_ocr_fragment(.x)]),
    text_final       = map_chr(words_final, ~paste(.x, collapse = " ")),
    final_word_count = str_count(text_final, "\\S+")
  )

cat("Cleaning stats:\n")
cat("  Avg words before:", round(mean(raw_texts$word_count)), "\n")
cat("  Avg words after: ", round(mean(processed_texts$final_word_count)), "\n\n")

# Remove very short documents
processed_texts <- processed_texts %>%
  filter(final_word_count >= 10)

cat("Documents after filtering (>= 10 words):", nrow(processed_texts), "\n\n")
```

---

## 7. Prepare for STM

```{r prepare-stm}
cat("\n", rep("=", 70), "\n", sep = "")
cat("PREPARING FOR STM\n")
cat(rep("=", 70), "\n\n", sep = "")

processed <- textProcessor(
  documents         = processed_texts$text_final,
  metadata          = processed_texts %>% select(doc_id, month, volume, year, filename),
  lowercase         = FALSE,
  removestopwords   = FALSE,
  removenumbers     = FALSE,
  removepunctuation = FALSE,
  stem              = FALSE,
  wordLengths       = c(3, Inf),
  sparselevel       = 1,
  language          = "en",
  verbose           = TRUE
)

cat("\n")

out <- prepDocuments(
  documents    = processed$documents,
  vocab        = processed$vocab,
  meta         = processed$meta,
  lower.thresh = 1,
  upper.thresh = Inf
)

docs  <- out$documents
vocab <- out$vocab
meta  <- out$meta

# Store the texts that actually made it into the model (for findThoughts later)
modeled_texts <- processed_texts$text_final[match(meta$doc_id, processed_texts$doc_id)]

cat("\n", rep("=", 70), "\n", sep = "")
cat("CORPUS READY\n")
cat(rep("=", 70), "\n\n", sep = "")
cat("Documents:  ", length(docs), "\n")
cat("Vocabulary: ", length(vocab), "\n\n")

if (length(docs) == 0) stop("No documents remaining!")

cat("Sample vocab:\n", paste(vocab[1:50], collapse = ", "), "\n\n")
```

---

## 8. Set K (Number of Topics)

```{r set-k}
# ============================================================================
# CHANGE THIS NUMBER to set how many topics you want
# ============================================================================
chosen_K <- 10

cat("Chosen K =", chosen_K, "\n\n")
```

---

## 9. Fit STM Model

```{r fit-model, cache=TRUE}
cat(rep("=", 70), "\n", sep = "")
cat("FITTING MODEL K =", chosen_K, "\n")
cat(rep("=", 70), "\n\n", sep = "")

stm_model <- stm(
  documents  = docs,
  vocab      = vocab,
  K          = chosen_K,
  data       = meta,
  max.em.its = 75,
  init.type  = "Spectral",
  seed       = 12345,
  verbose    = TRUE
)

model_file <- file.path(output_path, paste0("stm_model_K", chosen_K, ".rds"))
saveRDS(stm_model, model_file)
cat("\nModel saved to:", model_file, "\n")
```

---

## 10. Examine Topics

```{r examine-topics}
cat("\n", rep("=", 70), "\n", sep = "")
cat("TOP WORDS PER TOPIC\n")
cat(rep("=", 70), "\n\n", sep = "")

labelTopics(stm_model, n = 15)
```

---

## 11. Review Words for Labeling

Run this chunk to see FREX, PROB, and LIFT words side by side.
Use these to decide which auto-labels to override in Section 12.

```{r review-words}
cat("=", rep("=", 70), "\n", sep = "")
cat("TOPIC WORD REVIEW\n")
cat("=", rep("=", 70), "\n\n", sep = "")

all_words <- labelTopics(stm_model, n = 20)

for (i in 1:chosen_K) {
  cat(sprintf("--- TOPIC %d ---\n", i))
  cat("  FREX (most distinctive): ", paste(all_words$frex[i, 1:10], collapse = ", "), "\n")
  cat("  PROB (most common):      ", paste(all_words$prob[i, 1:10], collapse = ", "), "\n")
  cat("  LIFT (most exclusive):   ", paste(all_words$lift[i, 1:10], collapse = ", "), "\n\n")
}
```

---

## 12. Auto-Generate Topic Labels

```{r create-labels}
cat("\n", rep("=", 70), "\n", sep = "")
cat("AUTO-GENERATING TOPIC LABELS\n")
cat(rep("=", 70), "\n\n", sep = "")

create_specific_label <- function(topic_num, frex_words, prob_words) {
  frex_text <- tolower(paste(frex_words, collapse = " "))
  prob_text <- tolower(paste(prob_words, collapse = " "))

  if      (grepl("kingdom.*gospel|baptism.*eternal", frex_text))   { label <- "Gospel Doctrine & Spiritual Kingdom"
  } else if (grepl("passover|paschal|feast", frex_text))           { label <- "Biblical Symbolism & Ancient Rituals"
  } else if (grepl("nurse.*hospital|nursing.*training", frex_text)){ label <- "Nursing Training & Hospital Work"
  } else if (grepl("diet.*protein|nutrition|malnutrition", frex_text)) { label <- "Nutrition & Dietary Science"
  } else if (grepl("recipe|tbsp|boiling|oven", frex_text))         { label <- "Recipes & Cooking Instructions"
  } else if (grepl("housework|housekeeping|budget", frex_text))    { label <- "Household Management & Budgeting"
  } else if (grepl("moral.*parent|obedience.*spiritual", frex_text)){ label <- "Moral Education & Character Development"
  } else if (grepl("irving|tale|literature", frex_text))           { label <- "American Literature"
  } else if (grepl("radium.*curie|pasteur.*science", frex_text))   { label <- "Scientific Biography & Discovery"
  } else if (grepl("emigration.*journey|wagon.*pioneer", frex_text)){ label <- "Pioneer Emigration & Journey Stories"
  } else if (grepl("sisters.*presidency|organization.*grain", frex_text)) { label <- "Relief Society Leadership & Organization"
  } else if (grepl("stake.*ward|attendance.*conference", frex_text)){ label <- "Stake & Ward Relief Society Reports"
  } else if (grepl("suffrage.*vote|legislature", frex_text))       { label <- "Women's Suffrage & Political Rights"
  } else if (grepl("council.*international|convention", frex_text)) { label <- "International Women's Councils"
  } else if (grepl("entente.*allies|war.*troops", frex_text))      { label <- "World War I Commentary & News"
  } else if (grepl("tableau.*song|music.*hymn", frex_text))        { label <- "Musical Programs & Performances"
  } else if (grepl("empey.*mclelland|board.*member", frex_text))   { label <- "Board Member Directory"
  } else if (grepl("merino.*cotton|bleached.*gauze", frex_text))   { label <- "Garment & Product Advertisements"
  } else if (grepl("jerry|walter|jimmy", frex_text) && grepl("said|little", prob_text)) { label <- "Serialized Fiction & Stories"
  } else if (grepl("abraham.*sarai|biblical", frex_text))          { label <- "Biblical Narratives"
  } else {
    label <- paste(tools::toTitleCase(frex_words[1:3]), collapse = " ")
  }

  return(label)
}

all_top_words <- labelTopics(stm_model, n = 15)

topic_labels <- sapply(1:chosen_K, function(i) {
  frex_words     <- all_top_words$frex[i, 1:10]
  prob_words     <- all_top_words$prob[i, 1:10]
  specific_label <- create_specific_label(i, frex_words, prob_words)
  paste0("Topic ", i, ": ", specific_label)
})

cat("Auto-generated labels:\n\n")
for (i in 1:chosen_K) {
  cat(topic_labels[i], "\n")
  cat("  FREX: ", paste(all_top_words$frex[i, 1:7], collapse = ", "), "\n\n")
}
```

---

## 13. Manual Label Overrides

After reviewing Section 11 (word review) and Section 12 (auto labels),
uncomment and edit any labels that need changing.

```{r manual-labels}
# ============================================================================
# UNCOMMENT AND EDIT any labels you want to change
# ============================================================================

# topic_labels[1]  <- "Topic 1: Biblical Stories"
# topic_labels[2]  <- "Topic 2: Advertisements"
# topic_labels[3]  <- "Topic 3: World War I News"
# topic_labels[4]  <- "Topic 4: Gospel Doctrine"
# topic_labels[5]  <- "Topic 5: Serialized Fiction"
# topic_labels[6]  <- "Topic 6: Recipes & Cooking"
# topic_labels[7]  <- "Topic 7: Household Management"
# topic_labels[8]  <- "Topic 8: Stake & Ward Reports"
# topic_labels[9]  <- "Topic 9: Relief Society Conferences"
# topic_labels[10] <- "Topic 10: Pioneer Heritage"

# Show final labels
cat("\n", rep("=", 70), "\n", sep = "")
cat("FINAL TOPIC LABELS\n")
cat(rep("=", 70), "\n\n", sep = "")

for (i in 1:chosen_K) {
  cat(topic_labels[i], "\n")
}
```

---

## 14. Find Example Documents per Topic

```{r find-examples}
# ============================================================================
# CHANGE topic_to_examine to any topic number you want to read
# ============================================================================
topic_to_examine <- 1

cat("Examples for", topic_labels[topic_to_examine], ":\n")
cat(rep("=", 70), "\n\n", sep = "")

# modeled_texts was stored after prepDocuments — guaranteed to match model docs
thoughts <- findThoughts(
  model  = stm_model,
  texts  = modeled_texts,
  topics = topic_to_examine,
  n      = 3
)

for (i in 1:3) {
  cat("Example", i, ":\n")
  cat(substr(thoughts$docs[[1]][i], 1, 300), "...\n\n")
}
```

---

## 15. Link Topics to Specific Articles

```{r article-topic-setup}
# ============================================================================
# BUILD THE ARTICLE-TOPIC TABLE
# make.dt() already contains all metadata - no join needed
# ============================================================================

topic_props <- make.dt(stm_model, meta = meta)

# Check what columns are available
cat("Columns available in topic_props:\n")
print(names(topic_props))
cat("\n")
```

```{r top-articles-per-topic}
# ============================================================================
# TOP ARTICLES FOR EACH TOPIC
# ============================================================================

top_articles_for_topic <- function(topic_number, n = 5) {

  topic_col  <- paste0("Topic", topic_number)
  topic_name <- str_remove(topic_labels[topic_number], "^Topic \\d+: ")

  cat(rep("=", 60), "\n", sep = "")
  cat("TOP ARTICLES FOR: ", topic_name, "\n", sep = "")
  cat(rep("=", 60), "\n\n", sep = "")

  result <- topic_props %>%
    arrange(desc(.data[[topic_col]])) %>%
    head(n) %>%
    select(any_of(c("filename", "year", "month", "volume")),
           !!sym(topic_col)) %>%
    rename(topic_proportion = !!sym(topic_col)) %>%
    mutate(topic_proportion = scales::percent(topic_proportion, accuracy = 0.1))

  print(result)
  cat("\n")
}

# Run for every topic
for (i in 1:chosen_K) {
  top_articles_for_topic(i, n = 5)
}
```

---

## 16. Export Master Article-Topic Table

This creates one CSV you can open in Excel and filter by topic label
to see which articles belong to each topic.

```{r export-master-table}
# ============================================================================
# MASTER TABLE: one row per article-topic combination (proportion > 5%)
# ============================================================================

master_table <- topic_props %>%
  pivot_longer(
    cols      = starts_with("Topic"),
    names_to  = "topic",
    values_to = "proportion"
  ) %>%
  mutate(
    topic_num   = as.numeric(str_remove(topic, "Topic")),
    topic_label = str_remove(topic_labels[topic_num], "^Topic \\d+: "),
    # First 300 characters of the article as a readable preview
    text_preview = str_trunc(
      processed_texts$text_final[match(doc_id, processed_texts$doc_id)],
      300
    )
  ) %>%
  filter(proportion > 0.05) %>%   # Only meaningful associations
  arrange(desc(proportion)) %>%
  select(any_of(c("filename", "year", "month", "volume")),
         topic_num, topic_label, proportion, text_preview)

master_file <- file.path(output_path, paste0("articles_by_topic_K", chosen_K, ".csv"))
write_csv(master_table, master_file)

cat("Master table saved to:\n  ", master_file, "\n\n")
cat("Total rows:", nrow(master_table), "\n")
cat("Tip: Open in Excel, then filter the 'topic_label' column to find\n")
cat("     all articles for any topic.\n")
```

---

## 17. Visualizations

### Topic Prevalence Bar Chart

```{r plot-prevalence, fig.width=12, fig.height=7}
# ============================================================================
# TOPIC PREVALENCE PLOT
# ============================================================================

# Get mean prevalence per topic
topic_means <- colMeans(topic_props %>% select(starts_with("Topic")))

# Short labels (without "Topic N: " prefix)
short_labels <- str_remove(topic_labels, "^Topic \\d+: ")

# Sort by prevalence
sorted_order <- order(topic_means, decreasing = TRUE)

par(mar = c(5, 18, 4, 2))

barplot(
  height    = topic_means[sorted_order],
  names.arg = short_labels[sorted_order],
  horiz     = TRUE,
  las       = 1,
  col       = "#C1CDC1",
  border    = "#C1CDC1",
  main      = paste0("Topic Prevalence - Relief Society Bulletin (K = ", chosen_K, ")"),
  xlab      = "Expected Topic Proportions",
  cex.names = 0.85,
  xlim      = c(0, 0.35)
)

# Add percentage labels on bars
text(
  x      = topic_means[sorted_order] + 0.015,
  y      = (1:chosen_K) * 1.2 - 0.5,
  labels = sprintf("%.1f%%", topic_means[sorted_order] * 100),
  cex    = 0.8,
  col    = "#556B2F",
  font   = 2
)

par(mar = c(5, 4, 4, 2))
cat("Prevalence plot created\n")
```

### Topic Correlation Network

```{r plot-correlation, fig.width=10, fig.height=8}
mod.out.corr <- topicCorr(stm_model)
plot(mod.out.corr,
     main         = "Topic Correlation Network (Relief Society Bulletin)",
     vertex.color = "#CD2626",
     vertex.label.color = "#8B0000")
```

---

## 18. Topic Prevalence Over Time

### Estimate Time Effects

```{r estimate-time-effects}
cat("=", rep("=", 70), "\n", sep = "")
cat("TOPIC PREVALENCE OVER TIME\n")
cat("=", rep("=", 70), "\n\n", sep = "")

cat("Estimating time effects...\n")

prep_time <- estimateEffect(
  formula    = 1:chosen_K ~ s(year),
  stmobj     = stm_model,
  metadata   = meta,
  uncertainty = "Global"
)

cat("Estimation complete\n\n")
```

### Identify Top 6 Topics

```{r identify-top-topics}
topic_prevalences <- colMeans(topic_props %>% select(starts_with("Topic")))
top_6_topics      <- order(topic_prevalences, decreasing = TRUE)[1:6]

cat("Top 6 Most Prevalent Topics:\n\n")
for (i in 1:6) {
  topic_num <- top_6_topics[i]
  cat(sprintf("%d. %s (%.1f%%)\n",
              i,
              str_remove(topic_labels[topic_num], "^Topic \\d+: "),
              topic_prevalences[topic_num] * 100))
}
```

### Plot All Topics Over Time

```{r plot-all-topics-time, fig.width=16, fig.height=16}
topic_time_data <- topic_props %>%
  select(starts_with("Topic"), year) %>%
  filter(!is.na(year)) %>%
  group_by(year) %>%
  summarize(across(starts_with("Topic"), mean, na.rm = TRUE), .groups = "drop") %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "prevalence") %>%
  mutate(
    topic_num   = as.numeric(str_remove(topic, "Topic")),
    topic_label = str_wrap(str_remove(topic_labels[topic_num], "^Topic \\d+: "), 30)
  )

ggplot(topic_time_data, aes(x = year, y = prevalence)) +
  geom_line(color = "#53868B", size = 0.8) +
  geom_point(color = "#53868B", size = 1.5, alpha = 0.5) +
  facet_wrap(~topic_label, ncol = 4, scales = "free_y") +
  labs(
    title    = "Complete Topic Evolution Over Time - Relief Society Bulletin",
    subtitle = "All topics across the 1920s",
    x        = "Year",
    y        = "Topic Proportion"
  ) +
  theme_minimal(base_size = 10) +
  theme(
    strip.text       = element_text(size = 9, face = "bold"),
    panel.grid.minor = element_blank()
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1))
```

### Plot Top 6 Topics Over Time

```{r plot-top6-time, fig.width=14, fig.height=10}
topic_time_top6 <- topic_time_data %>%
  filter(topic_num %in% top_6_topics)

ggplot(topic_time_top6, aes(x = year, y = prevalence)) +
  geom_line(color = "#8B1A1A", size = 1.5) +
  geom_point(color = "#CD2626", size = 3, alpha = 0.7) +
  geom_smooth(method = "loess", color = "#8B0000", linetype = "dashed",
              se = TRUE, fill = "#FFB6C1", alpha = 0.3, size = 1) +
  facet_wrap(~topic_label, ncol = 3, scales = "free_y") +
  labs(
    title    = "Top 6 Topics Over Time - Relief Society Bulletin",
    subtitle = "Red line = actual data | Dashed = smoothed trend with confidence band",
    x        = "Year",
    y        = "Mean Topic Proportion"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    strip.text       = element_text(size = 10, face = "bold", color = "#8B0000"),
    panel.grid.minor = element_blank(),
    plot.title       = element_text(face = "bold", size = 14, color = "#8B0000"),
    plot.subtitle    = element_text(size = 11, color = "#A0522D")
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1))
```

### Detailed Single Topic View

```{r single-topic-time, fig.width=12, fig.height=6}
# Change this to any topic number you want to examine in detail
topic_to_examine_time <- top_6_topics[1]

topic_detail <- topic_time_data %>%
  filter(topic_num == topic_to_examine_time)

ggplot(topic_detail, aes(x = year, y = prevalence)) +
  geom_line(color = "#8B1A1A", size = 2) +
  geom_point(color = "#CD2626", size = 5, alpha = 0.7) +
  geom_smooth(method = "loess", color = "#8B0000",
              fill = "#FFB6C1", alpha = 0.3, size = 1.2) +
  labs(
    title    = str_remove(topic_labels[topic_to_examine_time], "^Topic \\d+: "),
    subtitle = "Points = annual averages | Band = smoothed trend with 95% confidence interval",
    x        = "Year",
    y        = "Topic Proportion",
    caption  = "Relief Society Bulletin (1920s)"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title       = element_text(face = "bold", size = 16, color = "#8B0000"),
    plot.subtitle    = element_text(size = 11, color = "#A0522D"),
    panel.grid.minor = element_blank()
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1)) +
  scale_x_continuous(breaks = seq(min(topic_detail$year),
                                   max(topic_detail$year), by = 1))
```

---

## 19. Topic Quality Metrics

```{r topic-quality}
cat("=", rep("=", 70), "\n", sep = "")
cat("TOPIC QUALITY: SEMANTIC COHERENCE VS EXCLUSIVITY\n")
cat("=", rep("=", 70), "\n\n", sep = "")

quality <- topicQuality(stm_model, documents = docs)

quality_df <- tibble(
  topic              = 1:chosen_K,
  semantic_coherence = quality$semcoh,
  exclusivity        = quality$exclusivity,
  label              = str_trunc(str_remove(topic_labels, "^Topic \\d+: "), 30)
)

cat("Semantic Coherence range: [",
    round(min(quality_df$semantic_coherence), 1), ",",
    round(max(quality_df$semantic_coherence), 1), "]\n")
cat("Exclusivity range:        [",
    round(min(quality_df$exclusivity), 1), ",",
    round(max(quality_df$exclusivity), 1), "]\n\n")

print(quality_df %>% arrange(desc(semantic_coherence + exclusivity)))
```

---

## 20. Word Clouds

```{r wordclouds, fig.width=12, fig.height=6}
# ============================================================================
# CHANGE topic_for_cloud to any topic number
# ============================================================================
topic_for_cloud <- 1

rs_colors <- c("#6E8B3D", "#A2CD5A", "#BCEE68", "#556B2F")

cloud(stm_model,
      topic  = topic_for_cloud,
      scale  = c(3, 0.5),
      colors = rs_colors,
      main   = str_remove(topic_labels[topic_for_cloud], "^Topic \\d+: "))
```

---

## 21. Export All Results

```{r export-results}
cat("=", rep("=", 70), "\n", sep = "")
cat("EXPORTING ALL RESULTS\n")
cat("=", rep("=", 70), "\n\n", sep = "")

# 1. Document-topic proportions with metadata
doc_topics_export <- topic_props %>%
  left_join(
    processed_texts %>%
      select(doc_id, filename, volume, year, month) %>%
      mutate(
        volume = ifelse(volume == "", NA_character_, volume),
        month  = ifelse(month  == "", NA_character_, month)
      ),
    by = "doc_id"
  )

doc_file <- file.path(output_path, paste0("document_topics_K", chosen_K, ".csv"))
write_csv(doc_topics_export, doc_file)

# 2. Topic words (FREX + PROB)
top_words <- labelTopics(stm_model, n = 20)

topic_words_df <- tibble(
  topic_num  = 1:chosen_K,
  label      = str_remove(topic_labels, "^Topic \\d+: "),
  frex_words = apply(top_words$frex, 1, paste, collapse = ", "),
  prob_words = apply(top_words$prob, 1, paste, collapse = ", ")
)

words_file <- file.path(output_path, paste0("topic_words_K", chosen_K, ".csv"))
write_csv(topic_words_df, words_file)

# 3. Time trends summary
topic_trends <- topic_time_data %>%
  group_by(topic_num, topic_label) %>%
  summarize(
    mean_prevalence = mean(prevalence, na.rm = TRUE),
    first_year_val  = first(prevalence[order(year)]),
    last_year_val   = last(prevalence[order(year)]),
    change          = last_year_val - first_year_val,
    .groups = "drop"
  ) %>%
  mutate(
    trend = case_when(
      abs(change) < 0.01 ~ "Stable",
      change >  0.01     ~ "Increasing",
      change < -0.01     ~ "Decreasing"
    )
  ) %>%
  arrange(desc(abs(change)))

trends_file <- file.path(output_path, paste0("topic_trends_K", chosen_K, ".csv"))
write_csv(topic_trends, trends_file)

cat("Files saved:\n")
cat("  ", doc_file,    "\n")
cat("  ", words_file,  "\n")
cat("  ", master_file, "\n")
cat("  ", trends_file, "\n\n")
cat("All exports complete!\n")
```

---

## Session Info

```{r session-info}
sessionInfo()
```
