---
title: "STM Topic Modeling - Complete Clean Version"
author: "Your Name"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: show
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# STM Topic Modeling - Complete Workflow

All refinements included: metadata extraction from Vol10-1923/June structure, stopword removal, year removal, manual K selection, and thematic auto-labeling.

---

## 1. Load Packages

```{r load-packages}
library(stm)
library(tidyverse)
library(stopwords)
install.packages("igraph")
library(igraph)
install.packages("wordcloud")
library(wordcloud)

set.seed(12345)
cat("Packages loaded successfully!\n")
```

---

## 2. Import Files

```{r import-files}
# ============================================================================
# SET YOUR FOLDER PATH
# ============================================================================

folder_path <- "C:/Users/birch/OneDrive - George Mason University - O365 Production/Dissertation/textanalysis/Topicmodel/input"

# Get all .txt files recursively
all_files <- list.files(path = folder_path, full.names = TRUE, recursive = TRUE)
file_paths <- all_files[grepl("\\.txt$", all_files, ignore.case = TRUE)]

cat("=" , rep("=", 70), "\n", sep = "")
cat("FILE IMPORT\n")
cat("=" , rep("=", 70), "\n\n", sep = "")

cat("Total .txt files found:", length(file_paths), "\n")

if (length(file_paths) == 0) {
  stop("No .txt files found! Check your folder path.")
}

cat("\nFirst 5 file paths:\n")
for (i in 1:min(5, length(file_paths))) {
  cat(i, ":", basename(file_paths[i]), "\n")
}
```

---

## 3. Sample or Use All Files

```{r read-files}
# ============================================================================
# CHOOSE: SAMPLE OR ALL FILES
# ============================================================================

# Set to FALSE to use ALL files, TRUE to sample
USE_SAMPLE <- FALSE
sample_size <- 300

if (USE_SAMPLE) {
  set.seed(123)
  sampled_paths <- sample(file_paths, size = sample_size)
  cat("\nUsing", sample_size, "of", length(file_paths), "files (sampled)\n")
} else {
  sampled_paths <- file_paths
  cat("\nUsing ALL", length(file_paths), "files\n")
}

# ============================================================================
# READ FILES
# ============================================================================

cat("\nReading files...\n")

raw_texts <- tibble(
  filepath = sampled_paths,
  filename = basename(sampled_paths),
  text = map_chr(sampled_paths, ~read_file(.x))
)

cat("Successfully read", nrow(raw_texts), "files\n")
```

---

## 4. Extract Metadata from Folder Structure

```{r extract-metadata}
cat("\n", rep("=", 70), "\n", sep = "")
cat("EXTRACTING METADATA\n")
cat(rep("=", 70), "\n\n", sep = "")

raw_texts <- raw_texts %>%
  mutate(
    # Extract volume from path (e.g., "Vol10-1923" or "Vol1_1914")
    volume_folder = str_extract(filepath, "Vol\\d+[-_]\\d{4}"),
    volume_num = str_extract(volume_folder, "Vol\\d+"),
    
    # Extract year from volume folder (e.g., 1923 from "Vol10-1923")
    year_from_folder = as.numeric(str_extract(volume_folder, "\\d{4}$")),
    
    # Extract month from path (folder name)
    month_from_folder = str_extract(filepath, "(?<=/)(January|February|March|April|May|June|July|August|September|October|November|December)(?=/)"),
    
    # Extract from filename (fallback)
    month_from_filename = str_extract(filename, "^[A-Za-z]+"),
    volume_from_filename = str_extract(filename, "Vol\\d+"),
    year_from_filename = as.numeric(str_extract(filepath, "\\d{4}")),
    
    # Use folder first, then filename
    month = ifelse(!is.na(month_from_folder), month_from_folder, month_from_filename),
    volume = ifelse(!is.na(volume_num), volume_num, volume_from_filename),
    year = ifelse(!is.na(year_from_folder), year_from_folder, year_from_filename),
    
    # Document ID and word count
    doc_id = row_number(),
    word_count = str_count(text, "\\S+")
  )

cat("Metadata extracted:\n\n")
cat("Volumes found:", paste(unique(na.omit(raw_texts$volume)), collapse = ", "), "\n")
cat("Years found:", paste(unique(na.omit(raw_texts$year)), collapse = ", "), "\n")
cat("Months found:", paste(unique(na.omit(raw_texts$month)), collapse = ", "), "\n\n")

cat("Sample of extracted metadata:\n")
print(head(raw_texts %>% select(filename, volume, year, month, word_count), 10))

cat("\n", rep("=", 70), "\n\n", sep = "")
```

---

## 5. Text Cleaning with Stopword Removal

```{r clean-with-stopwords}
cat("\n", rep("=", 70), "\n", sep = "")
cat("TEXT CLEANING WITH STOPWORD REMOVAL\n")
cat(rep("=", 70), "\n\n", sep = "")

# ============================================================================
# CREATE STOPWORD LIST
# ============================================================================

# Standard English stopwords
standard_stopwords <- stopwords::stopwords("en", source = "snowball")

# Custom stopwords
custom_stopwords <- c(
  # Common words
  "the", "of", "and", "in", "to", "a", "is", "that", "it", "for",
  "as", "on", "with", "be", "was", "by", "are", "from", "or", "an",
  "at", "this", "which", "have", "has", "had", "but", "not", "can",
  "will", "been", "were", "their", "they", "we", "our", "would",
  "there", "what", "so", "if", "who", "than", "may", "also","board",
  "officers", "general", "directors",
  
  # Titles (optional - comment out if you want to keep)
  "mrs", "mr", "miss", "dr", "ms",
  
  # Months (optional - already in metadata)
  "january", "february", "march", "april", "may", "june",
  "july", "august", "september", "october", "november", "december",
  
  # Domain-specific
  "vol", "page", "number", "volume"
)

# ============================================================================
# ADD YEARS DYNAMICALLY
# ============================================================================

# Extract all unique years from data and add as stopwords
years_in_data <- unique(na.omit(raw_texts$year))
years_as_words <- as.character(years_in_data)

cat("Years found in data:", paste(years_as_words, collapse = ", "), "\n")
cat("Adding these as stopwords...\n\n")

# Combine all stopwords
all_stopwords <- unique(c(standard_stopwords, custom_stopwords, years_as_words))

cat("Total stopwords to remove:", length(all_stopwords), "\n")
cat("  (includes", length(years_as_words), "year values)\n\n")

# ============================================================================
# APPLY CLEANING
# ============================================================================

processed_texts <- raw_texts %>%
  mutate(
    # Basic cleaning
    text_clean = str_to_lower(text),
    text_clean = str_remove_all(text_clean, "http\\S+"),
    text_clean = str_remove_all(text_clean, "\\S+@\\S+"),
    text_clean = str_remove_all(text_clean, "[[:punct:]]"),
    text_clean = str_squish(text_clean),
    
    # Remove stopwords
    words = str_split(text_clean, "\\s+"),
    words_no_stop = map(words, ~.x[!.x %in% all_stopwords]),
    
    # Remove short words (< 3 characters)
    words_final = map(words_no_stop, ~.x[nchar(.x) >= 3]),
    
    # Rejoin
    text_final = map_chr(words_final, ~paste(.x, collapse = " ")),
    final_word_count = str_count(text_final, "\\S+")
  )

cat("Cleaning statistics:\n")
cat("  Avg words before:", round(mean(raw_texts$word_count)), "\n")
cat("  Avg words after:", round(mean(processed_texts$final_word_count)), "\n")
cat("  Retention:", round(mean(processed_texts$final_word_count) / mean(raw_texts$word_count) * 100), "%\n\n")

# Filter short documents
cat("Filtering short documents...\n")
cat("Before:", nrow(processed_texts), "documents\n")

processed_texts <- processed_texts %>%
  filter(final_word_count >= 10)

cat("After (>= 10 words):", nrow(processed_texts), "documents\n")
cat("Removed:", nrow(raw_texts) - nrow(processed_texts), "documents\n\n")

if (nrow(processed_texts) == 0) {
  stop("All documents removed! Try less aggressive stopword removal.")
}

# Show example
cat("EXAMPLE - First document:\n")
cat(rep("-", 70), "\n", sep = "")
cat("BEFORE (", raw_texts$word_count[1], " words):\n")
cat(substr(raw_texts$text[1], 1, 250), "...\n\n")
cat("AFTER (", processed_texts$final_word_count[1], " words):\n")
cat(substr(processed_texts$text_final[1], 1, 250), "...\n")
cat(rep("-", 70), "\n\n", sep = "")
```

---

## 6. Prepare for STM

```{r prepare-stm}
cat("\n", rep("=", 70), "\n", sep = "")
cat("PREPARING FOR STM\n")
cat(rep("=", 70), "\n\n", sep = "")

# ============================================================================
# TEXTPROCESSOR
# ============================================================================

cat("Running textProcessor...\n")

processed <- textProcessor(
  documents = processed_texts$text_final,
  metadata = processed_texts %>% select(doc_id, month, volume, year, filename),
  lowercase = FALSE,
  removestopwords = FALSE,
  removenumbers = FALSE,
  removepunctuation = FALSE,
  stem = FALSE,
  wordLengths = c(3, Inf),
  sparselevel = 1,
  language = "en",
  verbose = TRUE
)

cat("\nAfter textProcessor:\n")
cat("  Documents:", length(processed$documents), "\n")
cat("  Vocabulary:", length(processed$vocab), "\n\n")

# ============================================================================
# PREPDOCUMENTS
# ============================================================================

cat("Running prepDocuments...\n\n")

out <- prepDocuments(
  documents = processed$documents,
  vocab = processed$vocab,
  meta = processed$meta,
  lower.thresh = 1,      # Keep words in 1+ documents
  upper.thresh = Inf     # No upper limit
)

docs <- out$documents
vocab <- out$vocab
meta <- out$meta

# ============================================================================
# FINAL CHECK
# ============================================================================

cat("\n", rep("=", 70), "\n", sep = "")
cat("FINAL CORPUS READY\n")
cat(rep("=", 70), "\n\n", sep = "")

cat("Documents:", length(docs), "\n")
cat("Vocabulary:", length(vocab), "\n")
cat("Metadata rows:", nrow(meta), "\n\n")

if (length(docs) == 0 || nrow(meta) == 0) {
  stop("No documents or metadata remaining!")
}

cat("Sample vocabulary (first 50 words):\n")
cat(paste(vocab[1:min(50, length(vocab))], collapse = ", "), "\n")

cat("\n", rep("=", 70), "\n\n", sep = "")
```

---

## 7. SET K MANUALLY

```{r set-k}
# ============================================================================
# MANUALLY SET YOUR K VALUE
# ============================================================================

chosen_K <- 20  # CHANGE THIS to whatever number of topics you want

cat("You have chosen K =", chosen_K, "\n")
cat("This will create", chosen_K, "topics\n\n")
```

---

## 8. Fit STM Model

```{r fit-model, cache=TRUE}
cat(rep("=", 70), "\n", sep = "")
cat("FITTING STM MODEL WITH K =", chosen_K, "\n")
cat(rep("=", 70), "\n\n", sep = "")

stm_model <- stm(
  documents = docs,
  vocab = vocab,
  K = chosen_K,
  data = meta,
  max.em.its = 75,
  init.type = "Spectral",
  seed = 12345,
  verbose = TRUE
)

# Save model
saveRDS(stm_model, paste0("stm_model_K", chosen_K, ".rds"))
cat("\n✓ Model saved to 'stm_model_K", chosen_K, ".rds'\n")
```

---

## 9. Examine Topics

```{r examine-topics}
cat("\n", rep("=", 70), "\n", sep = "")
cat("TOP WORDS FOR EACH TOPIC\n")
cat(rep("=", 70), "\n\n", sep = "")

labelTopics(stm_model, n = 15)
```

---

## 10. Auto-Generate Topic Labels (Method 4: Thematic)

```{r create-labels-semantic}
cat("\n", rep("=", 70), "\n", sep = "")
cat("AUTO-GENERATING TOPIC LABELS - METHOD 6 (SPECIFIC SEMANTIC LABELS)\n")
cat(rep("=", 70), "\n\n", sep = "")

# ============================================================================
# CREATE SPECIFIC SEMANTIC LABELS
# ============================================================================

create_specific_label <- function(topic_num, frex_words, prob_words) {
  # Combine for pattern matching
  frex_text <- tolower(paste(frex_words, collapse = " "))
  prob_text <- tolower(paste(prob_words, collapse = " "))
  all_words <- paste(frex_text, prob_text)
  
  # Create specific, descriptive labels based on word patterns
  
  # Religious topics - be specific
  if (grepl("kingdom.*gospel|baptism.*eternal|spirit.*revelation", frex_text)) {
    label <- "Gospel Doctrine & Spiritual Kingdom"
  } else if (grepl("temple.*work|temple.*dead|genealogy", frex_text)) {
    label <- "Temple Work & Ordinances"
  } else if (grepl("passover|paschal|feast.*symbolic", frex_text)) {
    label <- "Biblical Symbolism & Ancient Rituals"
  } else if (grepl("god|lord|church|prayer|faith", frex_text) && grepl("children|home", prob_text)) {
    label <- "Religious Education in the Home"
    
  # Health & medical - be specific
  } else if (grepl("nurse.*hospital|nursing.*training", frex_text)) {
    label <- "Nursing Training & Hospital Work"
  } else if (grepl("diet.*protein|food.*nutrition|malnutrition", frex_text)) {
    label <- "Nutrition & Dietary Science"
  } else if (grepl("health|medical|disease", frex_text)) {
    label <- "Health & Medical Care"
    
  # Domestic topics - be specific
  } else if (grepl("recipe|cooking|tbsp|boiling|oven", frex_text)) {
    label <- "Recipes & Cooking Instructions"
  } else if (grepl("housework.*housekeeping|budget|homemaking", frex_text)) {
    label <- "Household Management & Budgeting"
  } else if (grepl("architecture.*home|interior|building", frex_text)) {
    label <- "Home Architecture & Design"
    
  # Family & children - be specific
  } else if (grepl("moral.*parent|obedience.*spiritual", frex_text)) {
    label <- "Moral Education & Character Development"
  } else if (grepl("mother.*child|parent.*family", frex_text)) {
    label <- "Motherhood & Child Rearing"
    
  # Literature & education - be specific
  } else if (grepl("franklin|autobiography|biography", frex_text)) {
    label <- "Biography Study (Benjamin Franklin)"
  } else if (grepl("irving|tale|story.*literature", frex_text)) {
    label <- "American Literature (Washington Irving)"
  } else if (grepl("book.*lesson|study.*chapter", frex_text)) {
    label <- "Literature Study Lessons"
  } else if (grepl("radium.*curie|pasteur.*science", frex_text)) {
    label <- "Scientific Biography & Discovery"
    
  # Pioneer history - be specific
  } else if (grepl("emigration.*journey|wagon.*pioneer", frex_text)) {
    label <- "Pioneer Emigration & Journey Stories"
  } else if (grepl("ancestor.*genealogy|surname.*family", frex_text)) {
    label <- "Genealogy & Family History Work"
  } else if (grepl("abraham.*sarai|biblical.*ancient", frex_text)) {
    label <- "Biblical Narratives (Abraham's Story)"
    
  # Relief Society organization - be specific
  } else if (grepl("sisters.*presidency|organization.*grain", frex_text)) {
    label <- "Relief Society Leadership & Organization"
  } else if (grepl("stake.*ward|attendance.*conference", frex_text)) {
    label <- "Stake & Ward Relief Society Reports"
  } else if (grepl("society.*relief.*work", all_words) && grepl("president|organization", frex_text)) {
    label <- "Relief Society Administration"
    
  # Civic engagement - be specific
  } else if (grepl("suffrage.*vote|women.*rights|legislature", frex_text)) {
    label <- "Women's Suffrage & Political Rights"
  } else if (grepl("council.*international|convention.*delegates", frex_text)) {
    label <- "International Women's Councils"
    
  # War & current events - be specific
  } else if (grepl("entente.*allies|war.*troops|german.*battle", frex_text)) {
    label <- "World War I Commentary & News"
    
  # Arts & performance - be specific
  } else if (grepl("tableau.*song|music.*hymn|chorus", frex_text)) {
    label <- "Musical Programs & Performances"
  } else if (grepl("song.*sing|hymn", frex_text)) {
    label <- "Hymns & Sacred Music"
    
  # Administrative/structural - be specific
  } else if (grepl("^\\d+.*\\d+.*\\d+", frex_text)) {
    label <- "Magazine Index & Page Numbers"
  } else if (grepl("empey.*mclelland|names.*board", frex_text)) {
    label <- "Board Member Directory & Leadership"
  } else if (grepl("salt.*lake.*city.*utah", frex_text)) {
    label <- "Local Announcements & Addresses"
    
  # Commercial content - be specific
  } else if (grepl("merino.*cotton|bleached.*gauze|weight.*price", frex_text)) {
    label <- "Garment & Product Advertisements"
    
  # Fiction - be specific
  } else if (grepl("character names|jerry.*walter|dialogue", frex_text) || 
             (grepl("jerry|walter|jimmy|bob", frex_text) && grepl("said|came|little", prob_text))) {
    label <- "Serialized Fiction & Stories"
    
  } else {
    # Default: use top 3 FREX words with category
    keywords <- paste(tools::toTitleCase(frex_words[1:3]), collapse= " ")
    label <- keywords
  }
  
  return(label)
}

# ============================================================================
# GENERATE LABELS FOR ALL TOPICS
# ============================================================================

cat("Generating specific semantic labels for", chosen_K, "topics...\n\n")

# Get top words
all_top_words <- labelTopics(stm_model, n = 15)

# Create labels
topic_labels <- sapply(1:chosen_K, function(i) {
  frex_words <- all_top_words$frex[i, 1:10]
  prob_words <- all_top_words$prob[i, 1:10]
  
  specific_label <- create_specific_label(i, frex_words, prob_words)
  
  paste0("Topic ", i, ": ", specific_label)
})

# ============================================================================
# DISPLAY LABELS IN SEQUENTIAL ORDER (NOT GROUPED)
# ============================================================================

cat("Auto-generated specific labels:\n")
cat(rep("=", 70), "\n\n", sep = "")

for (i in 1:chosen_K) {
  cat(topic_labels[i], "\n")
  
  # Show FREX words for reference
  cat("  FREX: ", paste(all_top_words$frex[i, 1:7], collapse = ", "), "\n")
  
  # Show PROB words for reference
  cat("  PROB: ", paste(all_top_words$prob[i, 1:7], collapse = ", "), "\n\n")
}

cat(rep("=", 70), "\n\n", sep = "")

# ============================================================================
# EXPORT LABELS
# ============================================================================

# Get words for export
frex_for_export <- apply(all_top_words$frex, 1, function(x) paste(x, collapse = ", "))
prob_for_export <- apply(all_top_words$prob, 1, function(x) paste(x, collapse = ", "))

label_export <- tibble(
  topic_num = 1:chosen_K,
  auto_label = str_remove(topic_labels, "^Topic \\d+: "),  # Just the label
  full_label = topic_labels,  # With "Topic N: "
  frex_words = frex_for_export,
  prob_words = prob_for_export,
  manual_label = ""  # Edit this if you want to refine
)

write_csv(label_export, paste0("topic_labels_K", chosen_K, ".csv"))

cat("✓ Labels exported to 'topic_labels_K", chosen_K, ".csv'\n")
cat("  Review and refine 'manual_label' column as needed\n\n")

```

---

### Customizing Categories:

The categories are tailored to Relief Society corpus content. You can:

**Add new categories** (around line 15):
```r
# Add after existing categories:
} else if (grepl("your|keywords|here", all_words)) {
  category <- "Your New Category"
```

**Modify keywords** for existing categories:
```r
# For example, expand Health & Medicine:
} else if (grepl("health|nurse|...|pharmacy|midwife", all_words)) {
```

**Adjust category names**:
```r
category <- "Healthcare & Wellness"  # Instead of "Health & Medicine"
```
## 11. Find Example Documents

```{r find-examples}
# Change this to examine different topics
topic_to_examine <- 1

cat("Example documents for", topic_labels[topic_to_examine], ":\n")
cat(rep("=", 70), "\n\n", sep = "")

thoughts <- findThoughts(
  model = stm_model,
  texts = processed_texts$text_final,
  topics = topic_to_examine,
  n = 3
)

for (i in 1:3) {
  cat("Example", i, ":\n")
  cat(substr(thoughts$docs[[1]][i], 1, 250), "...\n\n")
}
```

---

## 12. Visualizations

### Topic Prevalence

```{r plot-prevalence, fig.width=10, fig.height=6}
plot(stm_model, 
     type = "summary", 
     n = min(10, chosen_K),
     main = paste("Topic Prevalence (K =", chosen_K, ")"),
     xlim = c(0, 0.3))
```

### Topic Correlation Network

```{r plot-correlation, fig.width=10, fig.height=8}
mod.out.corr <- topicCorr(stm_model)
plot(mod.out.corr, main = "Topic Correlation Network")
```

### Word Cloud for Topic 1

```{r wordcloud-1, fig.width=8, fig.height=6}
cloud(stm_model, 
      topic = 1,
      scale = c(3, 0.5),
      main = topic_labels[1])
```

### Create Word Clouds for All Topics

```{r wordcloud-all, fig.width=8, fig.height=6, eval=FALSE}
# Set eval=TRUE to generate word clouds for all topics
for (i in 1:chosen_K) {
  cloud(stm_model, 
        topic = i,
        scale = c(3, 0.5),
        main = topic_labels[i])
}
```

### Topic Quality

```{r topic-quality, fig.width=8, fig.height=6}
topicQuality(stm_model, documents = docs)
```

### Compare Two Topics

```{r compare-topics, fig.width=10, fig.height=6}
# Compare two topics
plot(stm_model, 
     type = "perspectives", 
     topics = c(1, 5),
     main = paste("Comparing", topic_labels[1], "vs", topic_labels[5]))
```

---

## 13. Export Results

```{r export-results}
# ============================================================================
# EXPORT DOCUMENT-TOPIC PROPORTIONS
# ============================================================================

doc_topics <- make.dt(stm_model, meta = meta)

# Add original metadata back
doc_topics_full <- doc_topics %>%
  left_join(
    processed_texts %>% select(doc_id, filename, volume, year, month),
    by = "doc_id"
  )

write_csv(doc_topics_full, paste0("document_topics_K", chosen_K, ".csv"))

# ============================================================================
# EXPORT TOP WORDS PER TOPIC
# ============================================================================

top_words <- labelTopics(stm_model, n = 20)

topic_words_df <- tibble(
  topic = 1:chosen_K,
  label = topic_labels,
  top_prob_words = apply(top_words$prob, 1, function(x) paste(x, collapse = ", ")),
  top_frex_words = apply(top_words$frex, 1, function(x) paste(x, collapse = ", "))
)

write_csv(topic_words_df, paste0("topic_words_K", chosen_K, ".csv"))

cat("Results exported!\n")
cat("  - document_topics_K", chosen_K, ".csv (includes metadata)\n")
cat("  - topic_words_K", chosen_K, ".csv\n")
cat("  - topic_labels_K", chosen_K, ".csv\n")
```

---

## 14. Save Session

```{r save-session}
save(stm_model, docs, vocab, meta, 
     raw_texts, processed_texts, all_stopwords, topic_labels,
     file = paste0("stm_session_K", chosen_K, ".RData"))

cat("Session saved to 'stm_session_K", chosen_K, ".RData'\n")
cat("\nTo reload: load('stm_session_K", chosen_K, ".RData')\n")
```

---

## Quick Reference

### Key Features:
✅ Handles Vol10-1923/June folder structure
✅ Extracts metadata (volume, year, month) automatically
✅ Removes stopwords + years dynamically
✅ Manual K selection (Section 7)
✅ Thematic auto-labeling (Method 4)
✅ Exports include full metadata

### To Change K:
1. Section 7: Change `chosen_K <- 20`
2. Re-run from Section 8 onwards

### To Add Stopwords:
1. Section 5: Add to `custom_stopwords`
2. Re-run from Section 5 onwards

### To Use All Files:
1. Section 3: Set `USE_SAMPLE <- FALSE`

### Files Exported:
- `stm_model_K20.rds` - Fitted model
- `document_topics_K20.csv` - Topic proportions per document
- `topic_words_K20.csv` - Top words per topic
- `topic_labels_K20.csv` - Auto-generated labels
- `stm_session_K20.RData` - Complete session

## Session Info

```{r session-info}
sessionInfo()
```
