---
title: "STM Topic Modeling - Complete Clean Version"
author: "Your Name"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: show
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# STM Topic Modeling - Complete Workflow

All refinements included: metadata extraction from Vol10-1923/June structure, stopword removal, year removal, manual K selection, and thematic auto-labeling.

---

## 1. Load Packages

```{r load-packages}
library(stm)
library(tidyverse)
library(dplyr)
library(stopwords)
library(igraph)
library(wordcloud)
library(tidyr)       # For data tidying
library(stringr)     # For string manipulation
library(purrr)       # For map functions
library(readr)       # For read_file and write_csv
library(tibble)      # For tibble function


set.seed(12345)
cat("Packages loaded successfully!\n")

set.seed(12345)
cat("Packages loaded successfully!\n")
```

---

## 2. Set Input and Output Paths

```{r set-paths}
# ============================================================================
# SET INPUT AND OUTPUT PATHS
# ============================================================================

# Input folder (where your .txt files are)
input_path <- "C:/Users/birch/OneDrive - George Mason University - O365 Production/Dissertation/textanalysis/Topicmodel/input"

# Output folder (where results will be saved)
output_path <- "C:/Users/birch/OneDrive - George Mason University - O365 Production/Dissertation/textanalysis/Topicmodel/output"

# Create output directory if it doesn't exist
if (!dir.exists(output_path)) {
  dir.create(output_path, recursive = TRUE)
  cat("✓ Created output directory\n")
}

cat("Paths configured:\n")
cat("  Input: ", input_path, "\n")
cat("  Output:", output_path, "\n\n")
```

---

## 3. Import Files

```{r import-files}
cat("=" , rep("=", 70), "\n", sep = "")
cat("FILE IMPORT\n")
cat("=" , rep("=", 70), "\n\n", sep = "")

# Get all .txt files recursively
all_files <- list.files(path = input_path, full.names = TRUE, recursive = TRUE)
file_paths <- all_files[grepl("\\.txt$", all_files, ignore.case = TRUE)]

cat("Total .txt files found:", length(file_paths), "\n")

if (length(file_paths) == 0) {
  stop("No .txt files found! Check your folder path.")
}

cat("\nFirst 5 files:\n")
for (i in 1:min(5, length(file_paths))) {
  cat(i, ":", basename(file_paths[i]), "\n")
}
```

---

## 4. Sample or Use All Files

```{r read-files}
# ============================================================================
# CHOOSE: SAMPLE OR ALL FILES
# ============================================================================

USE_SAMPLE <- FALSE  # Set to TRUE to sample, FALSE for all files
sample_size <- 300

if (USE_SAMPLE) {
  set.seed(123)
  sampled_paths <- sample(file_paths, size = sample_size)
  cat("\nUsing", sample_size, "of", length(file_paths), "files (sampled)\n")
} else {
  sampled_paths <- file_paths
  cat("\nUsing ALL", length(file_paths), "files\n")
}

cat("\nReading files...\n")

raw_texts <- tibble(
  filepath = sampled_paths,
  filename = basename(sampled_paths),
  text = map_chr(sampled_paths, ~read_file(.x))
)

cat("Successfully read", nrow(raw_texts), "files\n")
```

---

## 5. Extract Metadata

```{r extract-metadata}
cat("\n", rep("=", 70), "\n", sep = "")
cat("EXTRACTING METADATA\n")
cat(rep("=", 70), "\n\n", sep = "")

raw_texts <- raw_texts %>%
  mutate(
    volume_folder = str_extract(filepath, "Vol\\d+[-_]\\d{4}"),
    volume_num = str_extract(volume_folder, "Vol\\d+"),
    year_from_folder = as.numeric(str_extract(volume_folder, "\\d{4}$")),
    month_from_folder = str_extract(filepath, "(?<=/)(January|February|March|April|May|June|July|August|September|October|November|December)(?=/)"),
    month_from_filename = str_extract(filename, "^[A-Za-z]+"),
    volume_from_filename = str_extract(filename, "Vol\\d+"),
    year_from_filename = as.numeric(str_extract(filepath, "\\d{4}")),
    month = ifelse(!is.na(month_from_folder), month_from_folder, month_from_filename),
    volume = ifelse(!is.na(volume_num), volume_num, volume_from_filename),
    year = ifelse(!is.na(year_from_folder), year_from_folder, year_from_filename),
    doc_id = row_number(),
    word_count = str_count(text, "\\S+")
  )

cat("Metadata extracted:\n\n")
cat("Volumes:", paste(unique(na.omit(raw_texts$volume)), collapse = ", "), "\n")
cat("Years:", paste(unique(na.omit(raw_texts$year)), collapse = ", "), "\n")
cat("Months:", paste(unique(na.omit(raw_texts$month)), collapse = ", "), "\n\n")

cat("Sample:\n")
print(head(raw_texts %>% select(filename, volume, year, month, word_count), 10))

cat("\n", rep("=", 70), "\n\n", sep = "")
```

---

## 6. Text Cleaning with Stopword Removal

```{r clean-with-stopwords}
cat("\n", rep("=", 70), "\n", sep = "")
cat("TEXT CLEANING\n")
cat(rep("=", 70), "\n\n", sep = "")

# Stopwords
standard_stopwords <- stopwords::stopwords("en", source = "snowball")

custom_stopwords <- c(
  "the", "of", "and", "in", "to", "a", "is", "that", "it", "for",
  "as", "on", "with", "be", "was", "by", "are", "from", "or", "an",
  "at", "this", "which", "have", "has", "had", "but", "not", "can",
  "will", "been", "were", "their", "they", "we", "our", "would",
  "there", "what", "so", "if", "who", "than", "may", "also",
  "mrs", "mr", "miss", "dr", "ms",
  "january", "february", "march", "april", "may", "june",
  "july", "august", "september", "october", "november", "december",
  "vol", "page", "number", "volume", "board", "officer", "general"
)

# Add years dynamically
years_in_data <- unique(na.omit(raw_texts$year))
years_as_words <- as.character(years_in_data)

cat("Years found:", paste(years_as_words, collapse = ", "), "\n")
cat("Adding as stopwords...\n\n")

all_stopwords <- unique(c(standard_stopwords, custom_stopwords, years_as_words))

cat("Total stopwords:", length(all_stopwords), "\n\n")

# Clean text
processed_texts <- raw_texts %>%
  mutate(
    text_clean = str_to_lower(text),
    text_clean = str_remove_all(text_clean, "http\\S+"),
    text_clean = str_remove_all(text_clean, "\\S+@\\S+"),
    text_clean = str_remove_all(text_clean, "[[:punct:]]"),
    text_clean = str_squish(text_clean),
    words = str_split(text_clean, "\\s+"),
    words_no_stop = map(words, ~.x[!.x %in% all_stopwords]),
    words_final = map(words_no_stop, ~.x[nchar(.x) >= 3]),
    text_final = map_chr(words_final, ~paste(.x, collapse = " ")),
    final_word_count = str_count(text_final, "\\S+")
  )

cat("Cleaning stats:\n")
cat("  Avg before:", round(mean(raw_texts$word_count)), "\n")
cat("  Avg after:", round(mean(processed_texts$final_word_count)), "\n\n")

processed_texts <- processed_texts %>%
  filter(final_word_count >= 10)

cat("Documents after filtering:", nrow(processed_texts), "\n\n")
```

---

## 7. Prepare for STM

```{r prepare-stm}
cat("\n", rep("=", 70), "\n", sep = "")
cat("PREPARING FOR STM\n")
cat(rep("=", 70), "\n\n", sep = "")

processed <- textProcessor(
  documents = processed_texts$text_final,
  metadata = processed_texts %>% select(doc_id, month, volume, year, filename),
  lowercase = FALSE,
  removestopwords = FALSE,
  removenumbers = FALSE,
  removepunctuation = FALSE,
  stem = FALSE,
  wordLengths = c(3, Inf),
  sparselevel = 1,
  language = "en",
  verbose = TRUE
)

cat("\n")

out <- prepDocuments(
  documents = processed$documents,
  vocab = processed$vocab,
  meta = processed$meta,
  lower.thresh = 1,
  upper.thresh = Inf
)

docs <- out$documents
vocab <- out$vocab
meta <- out$meta

cat("\n", rep("=", 70), "\n", sep = "")
cat("CORPUS READY\n")
cat(rep("=", 70), "\n\n", sep = "")

cat("Documents:", length(docs), "\n")
cat("Vocabulary:", length(vocab), "\n\n")

if (length(docs) == 0) stop("No documents remaining!")

cat("Sample vocab:\n", paste(vocab[1:50], collapse = ", "), "\n\n")
```

---

## 8. SET K MANUALLY

```{r set-k}
chosen_K <- 20  # CHANGE THIS

cat("Chosen K =", chosen_K, "\n\n")
```

---

## 9. Fit STM Model

```{r fit-model, cache=TRUE}
cat(rep("=", 70), "\n", sep = "")
cat("FITTING MODEL K =", chosen_K, "\n")
cat(rep("=", 70), "\n\n", sep = "")

stm_model <- stm(
  documents = docs,
  vocab = vocab,
  K = chosen_K,
  data = meta,
  max.em.its = 75,
  init.type = "Spectral",
  seed = 12345,
  verbose = TRUE
)

# Save to output folder
model_file <- file.path(output_path, paste0("stm_model_K", chosen_K, ".rds"))
saveRDS(stm_model, model_file)
cat("\n✓ Model saved to:", model_file, "\n")
```

---

## 10. Examine Topics

```{r examine-topics}
cat("\n", rep("=", 70), "\n", sep = "")
cat("TOP WORDS\n")
cat(rep("=", 70), "\n\n", sep = "")

labelTopics(stm_model, n = 15)
```

---

## 11. Auto-Generate Labels (Method 6: Specific)

```{r create-labels-semantic}
cat("\n", rep("=", 70), "\n", sep = "")
cat("AUTO-GENERATING SPECIFIC LABELS\n")
cat(rep("=", 70), "\n\n", sep = "")

create_specific_label <- function(topic_num, frex_words, prob_words) {
  frex_text <- tolower(paste(frex_words, collapse = " "))
  prob_text <- tolower(paste(prob_words, collapse = " "))
  all_words <- paste(frex_text, prob_text)
  
  if (grepl("kingdom.*gospel|baptism.*eternal", frex_text)) {
    label <- "Gospel Doctrine & Spiritual Kingdom"
  } else if (grepl("passover|paschal|feast", frex_text)) {
    label <- "Biblical Symbolism & Ancient Rituals"
  } else if (grepl("nurse.*hospital|nursing.*training", frex_text)) {
    label <- "Nursing Training & Hospital Work"
  } else if (grepl("diet.*protein|nutrition|malnutrition", frex_text)) {
    label <- "Nutrition & Dietary Science"
  } else if (grepl("recipe|tbsp|boiling|oven", frex_text)) {
    label <- "Recipes & Cooking Instructions"
  } else if (grepl("housework|housekeeping|budget", frex_text)) {
    label <- "Household Management & Budgeting"
  } else if (grepl("moral.*parent|obedience.*spiritual", frex_text)) {
    label <- "Moral Education & Character Development"
  } else if (grepl("irving|tale|literature", frex_text)) {
    label <- "American Literature (Washington Irving)"
  } else if (grepl("radium.*curie|pasteur.*science", frex_text)) {
    label <- "Scientific Biography & Discovery"
  } else if (grepl("emigration.*journey|wagon.*pioneer", frex_text)) {
    label <- "Pioneer Emigration & Journey Stories"
  } else if (grepl("sisters.*presidency|organization.*grain", frex_text)) {
    label <- "Relief Society Leadership & Organization"
  } else if (grepl("stake.*ward|attendance.*conference", frex_text)) {
    label <- "Stake & Ward Relief Society Reports"
  } else if (grepl("suffrage.*vote|legislature", frex_text)) {
    label <- "Women's Suffrage & Political Rights"
  } else if (grepl("council.*international|convention", frex_text)) {
    label <- "International Women's Councils"
  } else if (grepl("entente.*allies|war.*troops", frex_text)) {
    label <- "World War I Commentary & News"
  } else if (grepl("tableau.*song|music.*hymn", frex_text)) {
    label <- "Musical Programs & Performances"
  } else if (grepl("^\\d+.*\\d+.*\\d+", frex_text)) {
    label <- "Magazine Index & Page Numbers"
  } else if (grepl("empey.*mclelland|board.*member", frex_text)) {
    label <- "Board Member Directory"
  } else if (grepl("merino.*cotton|bleached.*gauze", frex_text)) {
    label <- "Garment & Product Advertisements"
  } else if (grepl("jerry|walter|jimmy", frex_text) && grepl("said|little", prob_text)) {
    label <- "Serialized Fiction & Stories"
  } else if (grepl("abraham.*sarai|biblical", frex_text)) {
    label <- "Biblical Narratives (Abraham)"
  } else {
    keywords <- paste(tools::toTitleCase(frex_words[1:3]), collapse= " ")
    label <- keywords
  }
  
  return(label)
}

all_top_words <- labelTopics(stm_model, n = 15)

topic_labels <- sapply(1:chosen_K, function(i) {
  frex_words <- all_top_words$frex[i, 1:10]
  prob_words <- all_top_words$prob[i, 1:10]
  specific_label <- create_specific_label(i, frex_words, prob_words)
  paste0("Topic ", i, ": ", specific_label)
})

cat("Specific labels:\n")
cat(rep("=", 70), "\n\n", sep = "")

for (i in 1:chosen_K) {
  cat(topic_labels[i], "\n")
  cat("  FREX: ", paste(all_top_words$frex[i, 1:7], collapse = ", "), "\n")
  cat("  PROB: ", paste(all_top_words$prob[i, 1:7], collapse = ", "), "\n\n")
}

# Export to output folder
frex_for_export <- apply(all_top_words$frex, 1, function(x) paste(x, collapse = ", "))
prob_for_export <- apply(all_top_words$prob, 1, function(x) paste(x, collapse = ", "))

label_export <- tibble(
  topic_num = 1:chosen_K,
  auto_label = str_remove(topic_labels, "^Topic \\d+: "),
  full_label = topic_labels,
  frex_words = frex_for_export,
  prob_words = prob_for_export,
  manual_label = ""
)

labels_file <- file.path(output_path, paste0("topic_labels_K", chosen_K, ".csv"))
write_csv(label_export, labels_file)
cat("✓ Labels saved to:", labels_file, "\n\n")
```

---

## 12. Find Examples

```{r find-examples}
topic_to_examine <- 1

cat("Examples for", topic_labels[topic_to_examine], ":\n")
cat(rep("=", 70), "\n\n", sep = "")

thoughts <- findThoughts(stm_model, texts = processed_texts$text_final, topics = topic_to_examine, n = 3)

for (i in 1:3) {
  cat("Example", i, ":\n", substr(thoughts$docs[[1]][i], 1, 250), "...\n\n")
}
```

---

## 13. Visualizations

### Topic Prevalence

```{r plot-prevalence, fig.width=10, fig.height=6}
plot(stm_model, 
     type = "summary", 
     n = min(10, chosen_K),
     main = paste("Topic Prevalence (K =", chosen_K, ")"),
     xlim = c(0, 0.3))
```

### Topic Correlation Network

```{r plot-correlation, fig.width=10, fig.height=8}
mod.out.corr <- topicCorr(stm_model)
plot(mod.out.corr, main = "Topic Correlation Network")
```

### Word Cloud for Topic 1

```{r wordcloud-1, fig.width=8, fig.height=6}
cloud(stm_model, 
      topic = 1,
      scale = c(3, 0.5),
      main = topic_labels[1])
```

### Create Word Clouds for All Topics

```{r wordcloud-all, fig.width=8, fig.height=6, eval=FALSE}
# Set eval=TRUE to generate word clouds for all topics
for (i in 1:chosen_K) {
  cloud(stm_model, 
        topic = i,
        scale = c(3, 0.5),
        main = topic_labels[i])
}
```

### Topic Quality

```{r topic-quality, fig.width=8, fig.height=6}
topicQuality(stm_model, documents = docs)
```

### Compare Two Topics

```{r compare-topics, fig.width=10, fig.height=6}
# Compare two topics
plot(stm_model, 
     type = "perspectives", 
     topics = c(1, 5),
     main = paste("Comparing", topic_labels[1], "vs", topic_labels[5]))
```

---

---

## 14. Export Results

```{r export-results}
# Document-topic proportions
doc_topics <- make.dt(stm_model, meta = meta)
doc_topics_full <- doc_topics %>%
  left_join(processed_texts %>% select(doc_id, filename, volume, year, month), by = "doc_id")

doc_file <- file.path(output_path, paste0("document_topics_K", chosen_K, ".csv"))
write_csv(doc_topics_full, doc_file)

# Top words
top_words <- labelTopics(stm_model, n = 20)
topic_words_df <- tibble(
  topic = 1:chosen_K,
  label = topic_labels,
  top_prob = apply(top_words$prob, 1, function(x) paste(x, collapse = ", ")),
  top_frex = apply(top_words$frex, 1, function(x) paste(x, collapse = ", "))
)

words_file <- file.path(output_path, paste0("topic_words_K", chosen_K, ".csv"))
write_csv(topic_words_df, words_file)

cat("Results exported!\n")
cat("  -", doc_file, "\n")
cat("  -", words_file, "\n")
```

---

## 15. Save Session

```{r save-session}
session_file <- file.path(output_path, paste0("stm_session_K", chosen_K, ".RData"))
save(stm_model, docs, vocab, meta, raw_texts, processed_texts, 
     all_stopwords, topic_labels, file = session_file)

cat("Session saved to:", session_file, "\n")
cat("\nTo reload: load('", session_file, "')\n", sep = "")
```

---

## Files Created

All files are saved to: `C:/Users/birch/.../Topicmodel/output/`

- `stm_model_K20.rds` - Fitted model
- `topic_labels_K20.csv` - Labels with FREX/PROB words
- `document_topics_K20.csv` - Document-topic proportions
- `topic_words_K20.csv` - Top words per topic
- `stm_session_K20.RData` - Complete session

## Session Info

```{r session-info}
sessionInfo()
```
