---
title: "Comparing Two Publications - Woman's Exponent vs Relief Society Magazine"
author: "Birch"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: show
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 6)
```

# Comparing Two Publications with STM

This notebook compares **Woman's Exponent** vs **Relief Society Magazine** using Structural Topic Modeling (STM) with publication as a prevalence covariate.

---

## 1. Load Packages

```{r load-packages}
library(tidyverse)
library(stm)
library(stopwords)
library(kableExtra)
library(textstem)
library(ggrepel)
library(wordcloud)
library(RColorBrewer)
library(igraph)
library(ggraph)
library(patchwork)
library(ggridges)
library(readxl)
library(pheatmap)
library(scales)

set.seed(12345)
cat("Packages loaded!\n")
```

---

## 2. Set Paths (TWO Input Folders)
  
```{r set-paths}
base_path <- "C:/Users/birch/OneDrive - George Mason University - O365 Production/Dissertation/textanalysis"

# Corpus A: Woman's Exponent
corpus_a_path <- file.path(base_path, "Topicmodel/input")

# Corpus B: Relief Society Magazine
corpus_b_path <- file.path(base_path, "Topicmodel/input2")

# Inventories
inventory_a_path <- file.path(base_path, "exponentorder/output/WE_article_inventory_vols1-41.xlsx")
inventory_b_path <- file.path(base_path, "Articleextractionrfiles/Administrationorganization/RSM_article_inventory_vols1-57.xlsx")

# Output folder
output_path <- file.path(base_path, "Topicmodel/output_linked_comparison")

if (!dir.exists(output_path)) {
  dir.create(output_path, recursive = TRUE)
  cat("Created output directory\n")
}

cat("Corpus A (Woman's Exponent):", corpus_a_path, "\n")
cat("Corpus B (Relief Society Magazine):", corpus_b_path, "\n")
cat("Inventory A:", inventory_a_path, "\n")
cat("Inventory B:", inventory_b_path, "\n")
cat("Output:", output_path, "\n\n")
```

---

## 3. Import Both Corpora

```{r import-corpora}
cat("=", rep("=", 70), "\n", sep = "")
cat("IMPORTING BOTH PUBLICATIONS\n")
cat("=", rep("=", 70), "\n\n", sep = "")

# Helper: import a corpus with header stripping and metadata extraction
import_corpus <- function(corpus_path, corpus_name, pub_name) {
  if (!dir.exists(corpus_path)) stop(paste(pub_name, "path does not exist!"))

  file_paths <- list.files(corpus_path, pattern = "\\.txt$",
                           full.names = TRUE, recursive = TRUE, ignore.case = TRUE)
  file_paths <- file_paths[!grepl("_backups", file_paths)]
  cat(pub_name, "files found:", length(file_paths), "\n")

  tibble(
    filepath = file_paths,
    filename = basename(file_paths),
    text = map_chr(file_paths, ~{
      raw <- readr::read_file(.x)
      # Strip bracket metadata header line (RSM and WE both have these)
      str_remove(raw, "^\\[.*?\\]\\s*\\n?")
    })
  ) %>%
    mutate(
      volume_folder    = str_extract(filepath, "(?:WE)?Vol\\d+[-_]\\d{4}"),
      volume_num       = str_extract(volume_folder, "(?:WE)?Vol\\d+"),
      year_from_folder = as.numeric(str_extract(volume_folder, "\\d{4}$")),
      volume_from_file = str_extract(filename, "WEVol\\d+|Vol\\d+"),
      year_from_filename = as.numeric(str_extract(filepath, "(?<![0-9])(1[89]\\d{2})(?![0-9])")),
      month_from_folder = str_extract(filepath,
        "(?<=/)(January|February|March|April|May|June|July|August|September|October|November|December)(?=/)"),
      month_from_filename = str_extract(filename, "^[A-Za-z]+"),
      month  = coalesce(month_from_folder, month_from_filename),
      volume = coalesce(volume_num, volume_from_file),
      year   = coalesce(year_from_folder, year_from_filename),
      corpus      = corpus_name,
      publication = pub_name,
      word_count  = str_count(text, "\\S+")
    )
}

# --- Import both corpora ---
corpus_a <- import_corpus(corpus_a_path, "Womans_Exponent", "Woman's Exponent")
corpus_b <- import_corpus(corpus_b_path, "Relief_Society_Magazine", "Relief Society Magazine")

cat("\nCorpus A:", nrow(corpus_a), "documents |",
    "Years:", paste(range(na.omit(corpus_a$year)), collapse = "-"), "\n")
cat("Corpus B:", nrow(corpus_b), "documents |",
    "Years:", paste(range(na.omit(corpus_b$year)), collapse = "-"), "\n\n")

# --- Load inventories and join metadata ---
cat("Loading inventories...\n")

inv_a <- read_excel(inventory_a_path, sheet = "Article Inventory") %>%
  select(Filename, Title, Author, Article_Type) %>%
  mutate(across(everything(), as.character))

inv_b <- read_excel(inventory_b_path, sheet = "Article Inventory") %>%
  select(Filename, Title, Author, Article_Type) %>%
  mutate(across(everything(), as.character))

cat("  WE inventory:", nrow(inv_a), "rows\n")
cat("  RSM inventory:", nrow(inv_b), "rows\n")

corpus_a <- corpus_a %>%
  left_join(inv_a, by = c("filename" = "Filename"))
corpus_b <- corpus_b %>%
  left_join(inv_b, by = c("filename" = "Filename"))

cat("  WE matched:", sum(!is.na(corpus_a$Title)), "/", nrow(corpus_a), "\n")
cat("  RSM matched:", sum(!is.na(corpus_b$Title)), "/", nrow(corpus_b), "\n")

# --- Filter out Board files (name rosters pollute topic clustering) ---
corpus_a <- corpus_a %>% filter(!str_detect(filename, "BOARD"), !Article_Type %in% "Board" | is.na(Article_Type))
corpus_b <- corpus_b %>% filter(!str_detect(filename, "BOARD"), !Article_Type %in% "Board" | is.na(Article_Type))
cat("  After Board filter: WE =", nrow(corpus_a), "| RSM =", nrow(corpus_b), "\n\n")

# --- Combine ---
combined_corpus <- bind_rows(corpus_a, corpus_b) %>%
  mutate(
    corpus = factor(corpus),
    doc_id = row_number()
  )

cat("Combined corpus:", nrow(combined_corpus), "documents\n")
cat("  Woman's Exponent:", sum(combined_corpus$corpus == "Womans_Exponent"), "\n")
cat("  Relief Society Magazine:", sum(combined_corpus$corpus == "Relief_Society_Magazine"), "\n")
cat("  With author data:", sum(!is.na(combined_corpus$Author) & combined_corpus$Author != ""), "\n\n")
cat(rep("=", 70), "\n\n", sep = "")
```

---

## 4. Text Cleaning

```{r clean-text}
cat("\n", rep("=", 70), "\n", sep = "")
cat("TEXT CLEANING\n")
cat(rep("=", 70), "\n\n", sep = "")

# Combined stopwords from both individual notebooks
base_stopwords <- stopwords::stopwords("en", source = "snowball")

# Publication-specific boilerplate
pub_stopwords <- c(
  # WE-specific
  "womansexponent", "womans", "exponent", "womanexponent",
  # RSM-specific
  "relief", "society", "magazine", "bulletin", "latter", "saint", "saints",
  # Shared LDS/editorial
  "church", "jesus", "christ", "latterday",
  "editor", "publisher", "publishe", "assistant", "monthly",
  "salt", "lake", "city", "utah", "zion",
  # Structural/masthead
  "board", "officer", "general", "secretary", "sec", "secy",
  "asst", "pres", "treas", "president", "vice",
  "vol", "vols", "volume", "num", "page", "pp", "pg", "issue",
  # Advertising
  "advertise", "advertiser", "advertisement", "rate", "discount",
  "subscription", "subscriber", "copy", "copies", "price",
  # Titles/honorifics
  "mrs", "mr", "miss", "dr", "ms", "elder", "sister", "brother", "bishop",
  # Months
  "january", "february", "march", "april", "june",
  "july", "august", "september", "october", "november", "december",
  # Common function words missed by snowball
  "will", "would", "also", "may", "shall", "upon", "unto", "thee", "thou",
  "thy", "hath", "doth", "said", "one", "two", "three"
)

minimal_stopwords <- unique(c(base_stopwords, pub_stopwords))

# Add years from BOTH corpora dynamically
years_in_data  <- unique(na.omit(combined_corpus$year))
years_as_words <- as.character(years_in_data)

cat("Years found:", paste(years_as_words, collapse = ", "), "\n")
cat("Removing as stopwords...\n\n")

# OCR fragment / junk word blacklist — common broken words from digitized text
ocr_junk_stopwords <- c(
  # Suffix-only fragments
  "ing", "tion", "ment", "ness", "ings", "tive", "ance", "ence",
  "ered", "ters", "bers", "dren", "howe", "ould", "ight", "ther",
  "ated", "ting", "ally", "ible", "able", "ious", "eous", "ical",
  "onal", "ship", "ward", "wise", "less",
  # Truncated word fragments from OCR
  "deliv", "presi", "inter", "encour", "terest", "testi",
  "soci", "coun", "chil", "pariel", "organiza", "ganized",
  "ference", "musser", "selion",
  # Structural boilerplate remnants
  "column", "columns", "chapter", "section", "article",
  "continued", "copyright", "printed"
)

all_stopwords <- unique(c(minimal_stopwords, ocr_junk_stopwords, years_as_words))
cat("Total stopwords:", length(all_stopwords), "\n\n")

# --------------------------------------------------------------------------
# FIX 3: Remove Vol/No/page markers and ALL standalone numbers BEFORE
#         removing punctuation, so "Vol. 10" and bare "1897" are caught.
# FIX 4: Apply lemmatization to the actual word-splitting step (was ignored)
# --------------------------------------------------------------------------

# Regex patterns to catch OCR fragments not in the explicit list
is_ocr_fragment <- function(w) {
  grepl("^[a-z]{1,3}(tion|ment|ence|ness|ings|tive|ance)$", w) |
  grepl("^(pre|suf|dis|un|re)[a-z]{0,2}$", w) |
  grepl("^[^a-z]+$", w)
}

processed_texts <- combined_corpus %>%
  mutate(
    text_clean = str_to_lower(text),
    text_clean = str_remove_all(text_clean, "http\\S+"),
    text_clean = str_remove_all(text_clean, "\\S+@\\S+"),

    # FIX 3a: strip Vol/No/page markers before punctuation is removed
    text_clean = str_remove_all(text_clean, "\\bvol\\.?\\s*\\d+\\b"),
    text_clean = str_remove_all(text_clean, "\\bno\\.?\\s*\\d+\\b"),
    text_clean = str_remove_all(text_clean, "\\bpp?\\.?\\s*\\d+\\b"),

    # FIX 3b: remove all standalone numbers
    text_clean = str_remove_all(text_clean, "\\b\\d+\\b"),

    text_clean = str_remove_all(text_clean, "[[:punct:]]"),
    text_clean = str_squish(text_clean),

    # FIX 4: lemmatize, then use that result for word splitting
    text_lemmatized = lemmatize_strings(text_clean),

    words         = str_split(text_lemmatized, "\\s+"),   # <-- was text_clean
    words_no_stop = map(words, ~.x[!.x %in% all_stopwords]),
    # FIX 3c: belt-and-suspenders — drop any token that is purely numeric
    words_no_nums = map(words_no_stop, ~.x[!grepl("^\\d+$", .x)]),
    words_final   = map(words_no_nums, ~.x[nchar(.x) >= 3 & !is_ocr_fragment(.x)]),
    text_final    = map_chr(words_final, ~paste(.x, collapse = " ")),
    final_word_count = str_count(text_final, "\\S+")
  )

cat("Cleaning stats:\n")
cat("  Avg words before:", round(mean(combined_corpus$word_count)), "\n")
cat("  Avg words after:", round(mean(processed_texts$final_word_count)), "\n")
cat("  Retention:", round(mean(processed_texts$final_word_count) /
                          mean(combined_corpus$word_count) * 100), "%\n\n")

processed_texts <- processed_texts %>% filter(final_word_count >= 10)

cat("Documents after filtering (>= 10 words):", nrow(processed_texts), "\n")
cat("  Woman's Exponent:", sum(processed_texts$corpus == "Womans_Exponent"), "\n")
cat("  Relief Society Magazine:", sum(processed_texts$corpus == "Relief_Society_Magazine"), "\n\n")

if (nrow(processed_texts) == 0) stop("All documents removed!")

# --- Deduplicate near-identical documents ---
# Some articles were split into multiple sub-files with identical text
# (e.g., Guide Lessons _b_a_a, _b_a_b, _b_b, _b_c). These duplicates
# give one piece of content outsized weight in the model.
cat("Deduplicating near-identical documents...\n")
n_before_dedup <- nrow(processed_texts)

# Use first 200 characters of cleaned text as a fingerprint
processed_texts <- processed_texts %>%
  mutate(text_fingerprint = substr(text_final, 1, 200)) %>%
  group_by(text_fingerprint, corpus) %>%
  slice(1) %>%    # Keep first occurrence, drop duplicates
  ungroup() %>%
  select(-text_fingerprint) %>%
  mutate(doc_id = row_number())   # Re-number doc_ids after dedup

n_after_dedup <- nrow(processed_texts)
cat("  Removed", n_before_dedup - n_after_dedup, "near-duplicate documents\n")
cat("  Corpus after dedup:", n_after_dedup, "documents\n")
cat("  Woman's Exponent:", sum(processed_texts$corpus == "Womans_Exponent"), "\n")
cat("  Relief Society Magazine:", sum(processed_texts$corpus == "Relief_Society_Magazine"), "\n\n")
```

---

## 5. Prepare for STM

```{r prepare-stm}
cat("\n", rep("=", 70), "\n", sep = "")
cat("PREPARING FOR STM\n")
cat(rep("=", 70), "\n\n", sep = "")

# --- Defensive NA handling BEFORE textProcessor ---
processed_texts <- processed_texts %>%
  mutate(
    year = ifelse(is.na(year), median(year, na.rm = TRUE), year),
    month = ifelse(is.na(month), "Unknown", month),
    Article_Type = ifelse(is.na(Article_Type), "Unknown", Article_Type),
    Author = ifelse(is.na(Author), "", Author)
  )

processed <- textProcessor(
  documents        = processed_texts$text_final,
  metadata         = processed_texts %>% select(doc_id, month, volume, year, corpus,
                                                 publication, filename, Title, Article_Type, Author),
  lowercase        = FALSE,
  removestopwords  = FALSE,  # already done
  removenumbers    = TRUE,
  removepunctuation = FALSE,
  stem             = FALSE,
  wordLengths      = c(3, Inf),
  sparselevel      = 1,
  language         = "en",
  verbose          = TRUE
)

out  <- prepDocuments(processed$documents, processed$vocab, processed$meta, lower.thresh = 1)
docs <- out$documents
vocab <- out$vocab
meta  <- out$meta

# Store the texts that actually made it into the model (for findThoughts later)
modeled_texts <- processed_texts$text_final[match(meta$doc_id, processed_texts$doc_id)]
cat("  (dropped", nrow(processed_texts) - length(docs), "documents during preprocessing)\n")

# --- Defensive NA handling AFTER prepDocuments (rows may have been dropped) ---
meta$year <- as.numeric(meta$year)
meta$year[is.na(meta$year)] <- median(meta$year, na.rm = TRUE)
meta$month[is.na(meta$month)] <- "Unknown"
meta$Article_Type[is.na(meta$Article_Type)] <- "Unknown"

cat("\nDocuments:", length(docs), "\n")
cat("  Woman's Exponent:", sum(meta$corpus == "Womans_Exponent"), "\n")
cat("  Relief Society Magazine:", sum(meta$corpus == "Relief_Society_Magazine"), "\n")
cat("Vocabulary:", length(vocab), "\n\n")

if (length(docs) == 0) stop("No documents remaining!")
```

---

## 6. Diagnostic: searchK
##ONLY WHEN TRYING TO DETERMINE K

```{r searchK-diagnostic, eval=TRUE, cache=TRUE}
# ============================================================
# DIAGNOSTIC: searchK — THREE-WAY COMPARISON
# Runs searchK separately for WE, RSM, and Combined so you can
# compare the optimal K for each corpus and the joint model.
# Set eval=TRUE to run (takes a while), then FALSE after.
# ============================================================
cat(rep("=", 70), "\n", sep = "")
cat("RUNNING searchK: WE alone, RSM alone, and Combined\n")
cat(rep("=", 70), "\n\n", sep = "")

K_candidates <- c(5, 7, 10, 12, 15, 20)

# Helper: run searchK on a subset and return tidy results
run_searchK_for <- function(corpus_filter, label, prev_formula) {
  if (is.null(corpus_filter)) {
    # Combined: use all docs
    sub_docs  <- docs
    sub_vocab <- vocab
    sub_meta  <- meta
  } else {
    # Single corpus: subset and re-prep
    sub_texts <- processed_texts %>% filter(corpus == corpus_filter)
    sub_proc  <- textProcessor(
      documents = sub_texts$text_final,
      metadata  = sub_texts %>% select(doc_id, month, volume, year, corpus,
                                        publication, filename, Article_Type, Author),
      lowercase = FALSE, removestopwords = FALSE, removenumbers = TRUE,
      removepunctuation = FALSE, stem = FALSE, wordLengths = c(3, Inf),
      sparselevel = 1, language = "en", verbose = FALSE
    )
    sub_out   <- prepDocuments(sub_proc$documents, sub_proc$vocab, sub_proc$meta, lower.thresh = 1)
    sub_docs  <- sub_out$documents
    sub_vocab <- sub_out$vocab
    sub_meta  <- sub_out$meta
    sub_meta$year <- as.numeric(sub_meta$year)
    sub_meta$year[is.na(sub_meta$year)] <- median(sub_meta$year, na.rm = TRUE)
  }

  cat("\n--- searchK for", label, "(", length(sub_docs), "docs ) ---\n")

  sk <- searchK(
    documents  = sub_docs,
    vocab      = sub_vocab,
    K          = K_candidates,
    data       = sub_meta,
    prevalence = prev_formula,
    init.type  = "Spectral",
    seed       = 12345,
    verbose    = TRUE
  )

  as.data.frame(sk$results) %>%
    mutate(
      K        = unlist(K),
      heldout  = unlist(heldout),
      residual = unlist(residual),
      semcoh   = unlist(semcoh),
      exclus   = unlist(exclus),
      lbound   = unlist(lbound),
      corpus   = label
    )
}

# Run all three
sk_we       <- run_searchK_for("Womans_Exponent",       "Woman's Exponent",       ~ s(year))
sk_rsm      <- run_searchK_for("Relief_Society_Magazine","Relief Society Magazine", ~ s(year))
sk_combined <- run_searchK_for(NULL,                     "Combined",               ~ corpus + s(year))

searchK_all <- bind_rows(sk_we, sk_rsm, sk_combined)

saveRDS(searchK_all, file.path(output_path, "searchK_three_way_results.rds"))
cat("\nsearchK results saved for all three models.\n")
```

```{r searchK-load-results, eval=TRUE}
# ============================================================
# Load saved searchK results if they exist (avoids re-running)
# Set the searchK-diagnostic chunk above to eval=TRUE to generate
# these results for the first time (takes 30-60 minutes).
# ============================================================
searchK_rds <- file.path(output_path, "searchK_three_way_results.rds")
if (!exists("searchK_all") && file.exists(searchK_rds)) {
  searchK_all <- readRDS(searchK_rds)
  cat("Loaded saved searchK results from:", searchK_rds, "\n")
  cat("Corpora:", paste(unique(searchK_all$corpus), collapse = ", "), "\n")
  cat("K values tested:", paste(sort(unique(searchK_all$K)), collapse = ", "), "\n")
} else if (!exists("searchK_all")) {
  cat("No searchK results found.\n")
  cat("To generate: set the searchK-diagnostic chunk above to eval=TRUE and run it.\n")
  cat("Results will be saved to:", searchK_rds, "\n")
}
```

```{r searchK-comparison-plot, eval=TRUE, fig.width=14, fig.height=12}
# ============================================================
# Three-way searchK comparison: 5 separate panels, 3 lines each
# ============================================================
if (exists("searchK_all")) {

  sk_plot <- searchK_all %>%
    mutate(corpus = factor(corpus, levels = c("Woman's Exponent",
                                               "Relief Society Magazine",
                                               "Combined")))

  shared_scales <- list(
    scale_color_manual(values = c("Woman's Exponent" = "#CD661D",
                                   "Relief Society Magazine" = "#458B74",
                                   "Combined" = "#2563eb")),
    scale_linetype_manual(values = c("solid", "solid", "dashed")),
    scale_x_continuous(breaks = K_candidates),
    theme_minimal(base_size = 11),
    theme(legend.position = "none", panel.grid.minor = element_blank())
  )

  p1 <- ggplot(sk_plot, aes(x = K, y = heldout, color = corpus, linetype = corpus)) +
    geom_line(linewidth = 1.2) + geom_point(size = 3) +
    labs(title = "Held-Out Likelihood", subtitle = "Higher is better",
         x = "K", y = "Held-Out Likelihood") + shared_scales

  p2 <- ggplot(sk_plot, aes(x = K, y = residual, color = corpus, linetype = corpus)) +
    geom_line(linewidth = 1.2) + geom_point(size = 3) +
    labs(title = "Residuals", subtitle = "Lower is better",
         x = "K", y = "Residuals") + shared_scales

  p3 <- ggplot(sk_plot, aes(x = K, y = semcoh, color = corpus, linetype = corpus)) +
    geom_line(linewidth = 1.2) + geom_point(size = 3) +
    labs(title = "Semantic Coherence", subtitle = "Higher is better (trades off with exclusivity)",
         x = "K", y = "Semantic Coherence") + shared_scales

  p4 <- ggplot(sk_plot, aes(x = K, y = exclus, color = corpus, linetype = corpus)) +
    geom_line(linewidth = 1.2) + geom_point(size = 3) +
    labs(title = "Exclusivity", subtitle = "Higher is better (trades off with coherence)",
         x = "K", y = "Exclusivity") + shared_scales

  p5 <- ggplot(sk_plot, aes(x = semcoh, y = exclus, color = corpus, shape = corpus)) +
    geom_point(size = 4, alpha = 0.8) +
    geom_text(aes(label = K), size = 3, vjust = -1, show.legend = FALSE) +
    scale_color_manual(values = c("Woman's Exponent" = "#CD661D",
                                   "Relief Society Magazine" = "#458B74",
                                   "Combined" = "#2563eb")) +
    labs(title = "Coherence vs Exclusivity Tradeoff",
         subtitle = "Numbers = K value; upper-right = best quality",
         x = "Semantic Coherence", y = "Exclusivity",
         color = "Corpus", shape = "Corpus") +
    theme_minimal(base_size = 11) +
    theme(legend.position = "bottom")

  (p1 | p2) / (p3 | p4) / p5 +
    plot_annotation(
      title = "searchK Diagnostic: WE vs RSM vs Combined",
      subtitle = "Orange = Woman's Exponent | Green = Relief Society Magazine | Blue dashed = Combined",
      theme = theme(plot.title = element_text(face = "bold", size = 16))
    )
}
```
##ONLY WHEN TRYING TO DETERMINE K
```{r searchK-faceted-plot, eval=TRUE, fig.width=12, fig.height=9}
# ============================================================
# ALTERNATIVE: Compact 4-panel faceted grid (publication-ready)
# ============================================================
if (exists("searchK_all")) {

  sk_long <- searchK_all %>%
    mutate(corpus = factor(corpus, levels = c("Woman's Exponent",
                                               "Relief Society Magazine",
                                               "Combined"))) %>%
    select(K, corpus, heldout, residual, semcoh, exclus) %>%
    pivot_longer(c(heldout, residual, semcoh, exclus),
                 names_to = "metric", values_to = "value") %>%
    mutate(metric = factor(metric,
      levels = c("heldout", "residual", "semcoh", "exclus"),
      labels = c("Held-Out Likelihood\n(higher is better)",
                  "Residuals\n(lower is better)",
                  "Semantic Coherence\n(higher is better)",
                  "Exclusivity\n(higher is better)")))

  ggplot(sk_long, aes(x = K, y = value, color = corpus, linetype = corpus)) +
    geom_line(linewidth = 1.2) +
    geom_point(size = 3) +
    facet_wrap(~metric, ncol = 2, scales = "free_y") +
    scale_color_manual(values = c("Woman's Exponent" = "#CD661D",
                                   "Relief Society Magazine" = "#458B74",
                                   "Combined" = "#2563eb")) +
    scale_linetype_manual(values = c("solid", "solid", "dashed")) +
    scale_x_continuous(breaks = K_candidates) +
    labs(title = "searchK Diagnostic: WE vs RSM vs Combined",
         subtitle = "Compare optimal K across each corpus and the joint model",
         x = "Number of Topics (K)", y = NULL,
         color = "Corpus", linetype = "Corpus") +
    theme_minimal(base_size = 12) +
    theme(
      legend.position = "bottom",
      strip.text = element_text(face = "bold", size = 11),
      panel.grid.minor = element_blank(),
      plot.title = element_text(face = "bold", size = 16)
    )
}
```
##ONLY WHEN TRYING TO DETERMINE K
```{r searchK-sweet-spot, eval=TRUE, fig.width=14, fig.height=6}
# ============================================================
# COHERENCE vs EXCLUSIVITY OVERLAY — Finding the Sweet Spot
# Both metrics on one plot per corpus, with dual y-axes.
# The crossover/convergence region = optimal K.
# ============================================================
if (exists("searchK_all")) {

  # Normalize both metrics to 0-1 scale for overlay comparison
  sk_norm <- searchK_all %>%
    mutate(corpus = factor(corpus, levels = c("Woman's Exponent",
                                               "Relief Society Magazine",
                                               "Combined"))) %>%
    group_by(corpus) %>%
    mutate(
      coherence_norm = (semcoh - min(semcoh)) / (max(semcoh) - min(semcoh)),
      exclusivity_norm = (exclus - min(exclus)) / (max(exclus) - min(exclus))
    ) %>%
    ungroup() %>%
    select(K, corpus, coherence_norm, exclusivity_norm) %>%
    pivot_longer(c(coherence_norm, exclusivity_norm),
                 names_to = "metric", values_to = "value") %>%
    mutate(metric = ifelse(metric == "coherence_norm",
                           "Semantic Coherence", "Exclusivity"))

  # Find approximate sweet spot per corpus (where lines are closest)
  sweet_spots <- searchK_all %>%
    mutate(corpus = factor(corpus, levels = c("Woman's Exponent",
                                               "Relief Society Magazine",
                                               "Combined"))) %>%
    group_by(corpus) %>%
    mutate(
      coh_n = (semcoh - min(semcoh)) / (max(semcoh) - min(semcoh)),
      exc_n = (exclus - min(exclus)) / (max(exclus) - min(exclus)),
      gap = abs(coh_n - exc_n)
    ) %>%
    slice_min(gap, n = 1) %>%
    ungroup()

  ggplot(sk_norm, aes(x = K, y = value, color = metric, linetype = metric)) +
    geom_line(linewidth = 1.3) +
    geom_point(size = 3) +
    # Mark the sweet spot
    geom_vline(data = sweet_spots,
               aes(xintercept = K),
               linetype = "dotted", color = "grey30", linewidth = 0.8) +
    geom_label(data = sweet_spots,
               aes(x = K, y = 0.5, label = paste0("K=", K)),
               color = "grey30", size = 3.5, fill = "white",
               label.padding = unit(0.2, "lines"),
               inherit.aes = FALSE) +
    facet_wrap(~corpus, ncol = 3) +
    scale_color_manual(values = c("Semantic Coherence" = "#2563eb",
                                   "Exclusivity" = "#dc2626")) +
    scale_linetype_manual(values = c("solid", "dashed")) +
    scale_x_continuous(breaks = K_candidates) +
    labs(title = "Finding the Sweet Spot: Coherence vs Exclusivity",
         subtitle = "Both metrics normalized to 0-1 scale | Dotted line = where the tradeoff is most balanced",
         x = "Number of Topics (K)",
         y = "Normalized Score (0-1)",
         color = "Metric", linetype = "Metric") +
    theme_minimal(base_size = 12) +
    theme(
      legend.position = "bottom",
      strip.text = element_text(face = "bold", size = 12),
      panel.grid.minor = element_blank(),
      plot.title = element_text(face = "bold", size = 16)
    )
}
```

### 6b. Set K

```{r set-k}
chosen_K <- 10  # CHANGE THIS based on searchK results above
cat("Chosen K =", chosen_K, "\n\n")
```

---

## 7. Fit STM with Corpus as Covariate

```{r fit-model, cache=TRUE}
cat(rep("=", 70), "\n", sep = "")
cat("FITTING MODEL WITH CORPUS COVARIATE\n")
cat(rep("=", 70), "\n\n", sep = "")

stm_model_corpus <- stm(
  documents  = docs,
  vocab      = vocab,
  K          = chosen_K,
  prevalence = ~ corpus + s(year),
  data       = meta,
  max.em.its = 75,
  init.type  = "Spectral",
  seed       = 12345,
  verbose    = TRUE
)

model_file <- file.path(output_path, paste0("comparison_model_K", chosen_K, ".rds"))
saveRDS(stm_model_corpus, model_file)
cat("\n✓ Model saved to:", model_file, "\n")
```

---

## 8. Examine Topics

```{r examine-topics}
cat("\n", rep("=", 70), "\n", sep = "")
cat("TOP WORDS FOR EACH TOPIC\n")
cat(rep("=", 70), "\n\n", sep = "")

labelTopics(stm_model_corpus, n = 15)
```

---

## 9. Auto-Generate & Override Topic Labels

```{r create-labels}
cat("\n", rep("=", 70), "\n", sep = "")
cat("AUTO-GENERATING TOPIC LABELS\n")
cat(rep("=", 70), "\n\n", sep = "")

create_specific_label <- function(topic_num, frex_words, prob_words) {
  frex_text <- tolower(paste(frex_words, collapse = " "))
  prob_text <- tolower(paste(prob_words, collapse = " "))

  # --- Religious/Doctrinal ---
  if (grepl("kingdom.*gospel|baptism.*eternal|doctrine|covenant", frex_text)) {
    label <- "Gospel Doctrine & Spiritual Kingdom"
  } else if (grepl("passover|paschal|feast|abraham|sarai|moses|israelite", frex_text)) {
    label <- "Biblical Narratives & Symbolism"
  } else if (grepl("lesson|lecture|teacher|teach.*class|theology", frex_text)) {
    label <- "Gospel Lessons & Religious Instruction"
  } else if (grepl("temple|ordinance|endow|sealing|baptize", frex_text)) {
    label <- "Temple & Sacred Ordinances"
  } else if (grepl("missionary|mission.*convert|preach|investigator", frex_text)) {
    label <- "Missionary Work & Conversion"
  } else if (grepl("faith.*prayer|spiritual.*testimony|believe.*lord", frex_text)) {
    label <- "Faith & Spiritual Life"

  # --- Women's Issues ---
  } else if (grepl("suffrage.*vote|women.*rights|legislature|ballot|franchise", frex_text)) {
    label <- "Women's Suffrage & Political Rights"
  } else if (grepl("council.*international|convention.*delegates|congress.*women", frex_text)) {
    label <- "International Women's Councils"
  } else if (grepl("reform.*activism|temperance|prohibition|civic", frex_text)) {
    label <- "Women's Reform & Activism"

  # --- Organization ---
  } else if (grepl("sisters.*presidency|organization.*grain|auxiliary|general.*board", frex_text)) {
    label <- "Relief Society Leadership & Organization"
  } else if (grepl("stake.*ward|attendance.*conference|branch|reorganize", frex_text)) {
    label <- "Stake & Ward Reports"

  # --- Domestic ---
  } else if (grepl("child|parent|mother.*child|obedience.*parent", frex_text) &&
             grepl("children|child|parent", prob_text)) {
    label <- "Parenting & Child Moral Education"
  } else if (grepl("marriage|husband|wife|family.*home|courtship", frex_text)) {
    label <- "Marriage & Family Life"
  } else if (grepl("recipe|tbsp|boiling|oven|cooking|baking|flour|sugar", frex_text)) {
    label <- "Recipes & Cooking Instructions"
  } else if (grepl("diet.*protein|nutrition|malnutrition|food.*milk|vitamin", frex_text)) {
    label <- "Nutrition & Dietary Science"
  } else if (grepl("housework|housekeeping|budget|homemaking|cleaning", frex_text)) {
    label <- "Household Management & Budgeting"
  } else if (grepl("sew|pattern|crochet|quilt|fabric|needle|stitch|dress", frex_text)) {
    label <- "Sewing, Fashion & Handwork"
  } else if (grepl("garden|plant|seed|flower|shrub|prune|soil", frex_text)) {
    label <- "Home Gardening & Agriculture"

  # --- Health/Science ---
  } else if (grepl("nurse.*hospital|nursing.*training|health.*care|sanit", frex_text)) {
    label <- "Nursing Training & Hospital Work"
  } else if (grepl("radium.*curie|pasteur.*science|scientific|discovery", frex_text)) {
    label <- "Scientific Biography & Discovery"

  # --- History/Pioneer ---
  } else if (grepl("emigration.*journey|wagon.*pioneer|ancestor|handcart", frex_text)) {
    label <- "Pioneer History & Emigration"
  } else if (grepl("genealogy|ancestor.*record|family.*history|pedigree", frex_text)) {
    label <- "Genealogy & Family History"
  } else if (grepl("obituary|funeral|deceased|memorial|tribute.*memory", frex_text)) {
    label <- "Obituaries & Tributes"

  # --- Culture/Arts ---
  } else if (grepl("irving|tale|story.*literature|book.*read|novel|dickens", frex_text)) {
    label <- "Literature & Book Reviews"
  } else if (grepl("jerry|walter|jimmy|bob|chapter.*story", frex_text) &&
             grepl("said|little|story", prob_text)) {
    label <- "Serialized Fiction & Stories"
  } else if (grepl("poem|verse|rhyme|stanza|lyric", frex_text)) {
    label <- "Poetry & Verse"
  } else if (grepl("tableau|music|hymn|chorus|song.*sing|concert", frex_text)) {
    label <- "Musical Programs & Performances"

  # --- Political/World ---
  } else if (grepl("war|entente.*allies|troops|german|battle|soldier", frex_text)) {
    label <- "War News & Commentary"
  } else if (grepl("moral|virtue|character|righteousness", frex_text)) {
    label <- "Moral Education & Character Development"
  } else if (grepl("education|school|university|college|study|student", frex_text)) {
    label <- "Education & Learning"
  } else if (grepl("welfare|charitable|benevolent|poor|needy|donate", frex_text)) {
    label <- "Social Welfare & Charitable Work"

  # --- Structural/Noise ---
  } else if (grepl("^\\d+.*\\d+.*\\d+|page.*number|index", frex_text)) {
    label <- "Magazine Index & Structure"
  } else if (grepl("empey|mclelland|edna|farnsworth|board.*member", frex_text)) {
    label <- "Board Member Directory"
  } else if (grepl("merino|cotton|bleached|gauze|fabric|price|advertisement", frex_text)) {
    label <- "Product Advertisements"
  } else if (grepl("letter.*editor|correspond|reply.*question", frex_text)) {
    label <- "Correspondence & Letters"
  } else {
    keywords <- paste(tools::toTitleCase(frex_words[1:3]), collapse = " ")
    label <- keywords
  }

  return(label)
}

all_top_words <- labelTopics(stm_model_corpus, n = 15)

topic_labels <- sapply(1:chosen_K, function(i) {
  frex_words <- all_top_words$frex[i, 1:10]
  prob_words <- all_top_words$prob[i, 1:10]
  paste0("Topic ", i, ": ", create_specific_label(i, frex_words, prob_words))
})

cat("Auto-generated labels:\n\n")
for (i in 1:chosen_K) {
  cat(topic_labels[i], "\n")
  cat("  FREX:", paste(all_top_words$frex[i, 1:7], collapse = ", "), "\n\n")
}
```

```{r manual-overrides}
# ============================================================================
# MANUAL OVERRIDES — edit after reviewing auto-generated labels above
# Uncomment and modify as needed after running the model
# ============================================================================
topic_labels[1]  <- "Topic 1: Community Celebrations"
#topic_labels[2]  <- "Topic 2: Relief Society Meeting Reports"
topic_labels[3]  <- "Topic 3: Education"
topic_labels[4]  <- "Topic 4: Home-Making and Recipes"
topic_labels[5]  <- "Topic 5: Genealogy"
topic_labels[7]  <- "Topic 7: Relief Society Conference Reports "
topic_labels[8]  <- "Topic 8: World News and Women's Rights Reports"
topic_labels[10]  <- "Topic 10: Poetry"

# Show final labels
cat("\n", rep("=", 70), "\n", sep = "")
cat("FINAL TOPIC LABELS\n")
cat(rep("=", 70), "\n\n", sep = "")
for (i in 1:chosen_K) cat(topic_labels[i], "\n")
```

---

### 9c. Find Article Examples for a Topic

```{r find-examples-custom}
# ============================================================
# CHANGE THIS to examine any topic
# ============================================================
topic_to_examine <- 1
n_examples <- 10

cat(rep("=", 70), "\n", sep = "")
cat("TOPIC", topic_to_examine, ":", topic_labels[topic_to_examine], "\n")
cat(rep("=", 70), "\n", sep = "")
cat("FREX:", paste(all_top_words$frex[topic_to_examine, 1:10], collapse = ", "), "\n")
cat("PROB:", paste(all_top_words$prob[topic_to_examine, 1:10], collapse = ", "), "\n")
cat(rep("-", 70), "\n\n", sep = "")

# modeled_texts was stored after prepDocuments — guaranteed to match model docs
thoughts <- findThoughts(stm_model_corpus,
                         texts = modeled_texts,
                         topics = topic_to_examine,
                         n = n_examples)

thought_indices <- thoughts$index[[1]]

for (i in seq_along(thought_indices)) {
  idx <- thought_indices[i]
  row <- processed_texts[idx, ]

  pub_tag <- ifelse(row$corpus == "Womans_Exponent", "WE", "RSM")

  cat(sprintf("Example %d of %d:\n", i, length(thought_indices)))
  cat(sprintf("  File:        %s\n", row$filename))
  cat(sprintf("  Title:       %s\n", ifelse(is.na(row$Title), "(unknown)", row$Title)))
  cat(sprintf("  Author:      %s\n", ifelse(is.na(row$Author) | row$Author == "", "-", row$Author)))
  cat(sprintf("  Type:        %s\n", ifelse(is.na(row$Article_Type), "-", row$Article_Type)))
  cat(sprintf("  Publication: %s (%s, %s)\n\n", pub_tag, row$volume, row$year))
  cat(substr(thoughts$docs[[1]][i], 1, 400), "\n\n")
  cat(rep("-", 50), "\n\n", sep = "")
}
```

---

## 10. Link Topics to Articles

```{r link-topics-to-articles}
cat(rep("=", 70), "\n", sep = "")
cat("LINKING TOPICS TO ARTICLES\n")
cat(rep("=", 70), "\n\n", sep = "")

doc_topics <- make.dt(stm_model_corpus, meta = meta)

topic_article_link <- doc_topics %>%
  pivot_longer(
    cols = starts_with("Topic"),
    names_to = "topic",
    values_to = "proportion"
  ) %>%
  mutate(
    topic_num = as.integer(str_remove(topic, "Topic")),
    topic_label = topic_labels[topic_num]
  ) %>%
  select(topic_num, topic_label, proportion,
         any_of(c("doc_id", "filename", "Title", "Author", "Article_Type",
                  "volume", "year", "month", "corpus", "publication"))) %>%
  arrange(topic_num, desc(proportion))

cat("Linked table:", nrow(topic_article_link), "rows\n")
cat("  (", nrow(doc_topics), "documents x", chosen_K, "topics )\n\n")
```

### 10b. Dominant Topic Assignment

```{r dominant-topic}
exemplar_threshold <- 0.40

dominant_topics <- doc_topics %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "proportion") %>%
  mutate(topic_num = as.integer(str_remove(topic, "Topic"))) %>%
  group_by(doc_id) %>%
  slice_max(proportion, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  mutate(
    topic_label = topic_labels[topic_num],
    strong_exemplar = proportion >= exemplar_threshold,
    proportion_pct = round(proportion * 100, 1)
  ) %>%
  select(doc_id, any_of(c("filename", "Title", "Author", "Article_Type",
         "volume", "year", "month", "corpus", "publication")),
         dominant_topic = topic_num, topic_label, proportion_pct, strong_exemplar) %>%
  arrange(dominant_topic, desc(proportion_pct))

cat("Dominant topic assigned to", nrow(dominant_topics), "documents\n")
cat("Strong exemplars (>=", exemplar_threshold * 100, "%):",
    sum(dominant_topics$strong_exemplar), "\n\n")

# Summary table
dominant_topics %>%
  group_by(dominant_topic, topic_label) %>%
  summarise(
    n_articles = n(),
    n_strong = sum(strong_exemplar),
    avg_pct = round(mean(proportion_pct), 1),
    .groups = "drop"
  ) %>%
  print(n = chosen_K)
```

### 10c. Strong Exemplar Articles

```{r strong-exemplars}
cat("\nSTRONG EXEMPLARS (>=", exemplar_threshold * 100, "% topic proportion):\n\n")

for (t in 1:chosen_K) {
  strong <- dominant_topics %>% filter(dominant_topic == t, strong_exemplar)
  cat(rep("-", 60), "\n", sep = "")
  cat("Topic", t, ":", str_remove(topic_labels[t], "^Topic \\d+: "),
      " (", nrow(strong), " strong)\n", sep = "")

  if (nrow(strong) > 0) {
    for (i in 1:min(5, nrow(strong))) {
      row <- strong[i, ]
      title_str <- ifelse(is.na(row$Title), row$filename, row$Title)
      author_str <- ifelse(is.na(row$Author) | row$Author == "", "-", row$Author)
      pub_str <- ifelse(row$corpus == "Womans_Exponent", "WE", "RSM")
      cat(sprintf("  [%s%% | %s] %s | %s | %s\n",
                  row$proportion_pct, pub_str,
                  str_trunc(title_str, 50), author_str, row$year))
    }
  } else {
    cat("  (none above threshold)\n")
  }
  cat("\n")
}
```

### 10d. Representative Passages

```{r representative-passages}
cat("REPRESENTATIVE PASSAGES PER TOPIC\n")
cat(rep("=", 70), "\n\n", sep = "")

all_top_words <- labelTopics(stm_model_corpus, n = 15)

for (t in 1:chosen_K) {
  cat("TOPIC", t, ":", str_remove(topic_labels[t], "^Topic \\d+: "), "\n")
  cat(rep("-", 60), "\n", sep = "")

  top_docs <- topic_article_link %>% filter(topic_num == t) %>% head(3)
  topic_words <- tolower(all_top_words$frex[t, 1:15])

  for (j in 1:nrow(top_docs)) {
    fname <- top_docs$filename[j]
    title_str <- ifelse(is.na(top_docs$Title[j]), fname,
                        str_trunc(top_docs$Title[j], 60))

    # Search both input folders for the file
    match_file <- c(
      list.files(corpus_a_path, pattern = fixed(fname),
                 recursive = TRUE, full.names = TRUE),
      list.files(corpus_b_path, pattern = fixed(fname),
                 recursive = TRUE, full.names = TRUE)
    )
    if (length(match_file) == 0) next

    full_text <- read_file(match_file[1])
    # Strip header
    full_text <- str_remove(full_text, "^\\[.*?\\]\\s*\\n?")
    sentences <- str_split(full_text, "(?<=[.!?])\\s+")[[1]]
    sentences <- sentences[nchar(sentences) > 40 & nchar(sentences) < 500]
    if (length(sentences) == 0) next

    # Score sentences by FREX word overlap
    scores <- sapply(sentences, function(s) {
      words <- tolower(str_split(s, "\\s+")[[1]])
      sum(words %in% topic_words) / max(length(words), 1)
    })
    best <- str_squish(sentences[order(scores, decreasing = TRUE)[1]])

    pub_tag <- ifelse(grepl("input2", match_file[1]), "RSM", "WE")
    cat(sprintf("\n  [%s | %.1f%%] %s\n", pub_tag,
                top_docs$proportion[j] * 100, title_str))
    cat("  \"", str_trunc(best, 300), "\"\n", sep = "")
  }
  cat("\n\n")
}
```

---

## 11. Estimate Publication Effects

```{r set-coef-name}
# --------------------------------------------------------------------------
# FIX 5: Define corpus_coef_name HERE so every downstream chunk can see it
# --------------------------------------------------------------------------
# Determine coefficient name dynamically from factor levels
corpus_levels <- levels(meta$corpus)
cat("Corpus factor levels:", paste(corpus_levels, collapse = ", "), "\n")
cat("Reference group (alphabetically first):", corpus_levels[1], "\n\n")

# The non-reference level becomes the coefficient name
corpus_coef_name <- paste0("corpus", corpus_levels[2])
cat("Coefficient name:", corpus_coef_name, "\n\n")
```

```{r estimate-effects}
cat(rep("=", 70), "\n", sep = "")
cat("ESTIMATING PUBLICATION EFFECTS\n")
cat(rep("=", 70), "\n\n", sep = "")

prep_corpus <- estimateEffect(
  formula  = 1:chosen_K ~ corpus + s(year),
  stmobj   = stm_model_corpus,
  metadata = meta,
  uncertainty = "Global"
)

effects_file <- file.path(output_path, paste0("publication_effects_K", chosen_K, ".rds"))
saveRDS(prep_corpus, effects_file)
cat("✓ Effects saved to:", effects_file, "\n\n")
```

```{r diagnose-regression}
cat("Checking Topic 1 regression results:\n\n")
test_result <- summary(prep_corpus, topics = 1)
print(test_result)

cat("\nRow names in regression table:\n")
print(rownames(test_result$tables[[1]]))

cat("\nCorpus factor levels:\n")
print(levels(meta$corpus))
```

---

## 12. Identify Significant Differences

```{r view-differences}
cat(rep("=", 70), "\n", sep = "")
cat("TOPICS WITH SIGNIFICANT DIFFERENCES BETWEEN PUBLICATIONS\n")
cat(rep("=", 70), "\n\n", sep = "")

significant_topics <- tibble()

for (i in 1:chosen_K) {
  sum_result <- summary(prep_corpus, topics = i)

  if (corpus_coef_name %in% rownames(sum_result$tables[[1]])) {
    corpus_pvalue <- sum_result$tables[[1]][corpus_coef_name, "Pr(>|t|)"]
    corpus_coef   <- sum_result$tables[[1]][corpus_coef_name, "Estimate"]
    corpus_se     <- sum_result$tables[[1]][corpus_coef_name, "Std. Error"]

    if (corpus_pvalue < 0.05) {
      direction <- ifelse(corpus_coef > 0,
                          paste0("MORE in ", corpus_levels[2]),
                          paste0("MORE in ", corpus_levels[1]))

      cat(sprintf("%s\n", topic_labels[i]))
      cat(sprintf("  Difference: %.4f (SE = %.4f)\n", corpus_coef, corpus_se))
      cat(sprintf("  P-value: %.4f → %s\n\n", corpus_pvalue, direction))

      significant_topics <- bind_rows(significant_topics, tibble(
        Topic     = i,
        Label     = str_remove(topic_labels[i], "^Topic \\d+: "),
        Coefficient = corpus_coef,
        SE        = corpus_se,
        P_value   = corpus_pvalue,
        Direction = direction
      ))
    }
  }
}

if (nrow(significant_topics) == 0) {
  cat("No significant differences found at p < 0.05\n")
} else {
  cat("\nTotal significant differences:", nrow(significant_topics), "\n")
}
```

---

## 13. Build Comparison Table

```{r comparison-table}
corpus_effects <- map_dfr(1:chosen_K, function(i) {
  sum_result <- summary(prep_corpus, topics = i)

  if (corpus_coef_name %in% rownames(sum_result$tables[[1]])) {
    tibble(
      Topic      = i,
      Label      = str_remove(topic_labels[i], "^Topic \\d+: "),
      Difference = sum_result$tables[[1]][corpus_coef_name, "Estimate"],
      SE         = sum_result$tables[[1]][corpus_coef_name, "Std. Error"],
      P_value    = sum_result$tables[[1]][corpus_coef_name, "Pr(>|t|)"]
    )
  }
}) %>%
  mutate(
    Significant    = P_value < 0.05,
    Difference_Pct = round(Difference * 100, 2),
    Direction = case_when(
      !Significant ~ "No significant difference",
      Difference > 0 ~ "More in Woman's Exponent",
      TRUE ~ "More in Relief Society Magazine"
    )
  ) %>%
  arrange(desc(abs(Difference_Pct)))

# topic_props = doc_topics (created in Section 10 via make.dt)
topic_props <- doc_topics

cat("Comparison table built.\n")
print(corpus_effects)
```

---

## 14. Visualize Differences

```{r diverging-bar}
diverging_data <- corpus_effects %>%
  mutate(
    unique_label = paste0("T", Topic, ": ", Label),
    color_group  = case_when(
      !Significant ~ "No difference",
      Difference_Pct > 0 ~ "More in Woman's Exponent",
      TRUE ~ "More in Relief Society Magazine"
    )
  ) %>%
  arrange(Difference_Pct)

diverging_data$unique_label <- factor(
  diverging_data$unique_label,
  levels = unique(diverging_data$unique_label[order(diverging_data$Difference_Pct)])
)

ggplot(diverging_data, aes(x = Difference_Pct, y = unique_label, fill = color_group)) +
  geom_col() +
  geom_vline(xintercept = 0, linetype = "solid", color = "black", linewidth = 1) +
  scale_fill_manual(values = c(
    "More in Woman's Exponent"         = "#CD661D",
    "More in Relief Society Magazine"  = "#458B74",
    "No difference"                    = "#94a3b8"
  )) +
  labs(
    title    = "Topic Differences Between Publications",
    subtitle = "Positive = more in Woman's Exponent | Negative = more in Relief Society Magazine",
    x = "Difference (percentage points)",
    y = NULL,
    fill = "Direction"
  ) +
  theme_minimal(base_size = 11) +
  theme(
    legend.position  = "bottom",
    axis.text.y      = element_text(size = 8),
    panel.grid.major.y = element_blank()
  )
```

---

## 15. Plot Individual Significant Topic Comparisons

```{r plot-topic, fig.width=10, fig.height=6}
if (nrow(significant_topics) > 0) {

  cat("Creating comparison plots for significant topics...\n\n")

  # FIX 7: was max(3, ...) which would crash if fewer than 3 sig topics exist
  n_plots <- min(3, nrow(significant_topics))

  for (plot_num in 1:n_plots) {
    topic_to_plot <- significant_topics$Topic[plot_num]
    topic_col     <- paste0("Topic", topic_to_plot)

    plot_data <- topic_props %>%
      group_by(corpus) %>%
      summarize(
        mean_prop = mean(.data[[topic_col]]),
        se        = sd(.data[[topic_col]]) / sqrt(n()),
        ci_lower  = mean_prop - 1.96 * se,
        ci_upper  = mean_prop + 1.96 * se,
        .groups   = "drop"
      ) %>%
      mutate(
        publication = case_when(
          corpus == "Relief_Society_Magazine" ~ "Relief Society\nMagazine",
          corpus == "Womans_Exponent"         ~ "Woman's\nExponent",
          TRUE ~ as.character(corpus)
        ),
        publication = factor(publication,
                             levels = c("Relief Society\nMagazine", "Woman's\nExponent"))
      )

    p <- ggplot(plot_data, aes(x = publication, y = mean_prop)) +
      geom_point(size = 5, color = "#3b82f6") +
      geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),
                    width = 0.15, linewidth = 1.2, color = "#3b82f6") +
      geom_line(aes(group = 1), color = "#94a3b8", linewidth = 0.8, linetype = "dashed") +
      labs(
        title    = str_remove(topic_labels[topic_to_plot], "^Topic \\d+: "),
        subtitle = sprintf("Difference: %.2f%% (p = %.4f) — %s",
                           significant_topics$Coefficient[plot_num] * 100,
                           significant_topics$P_value[plot_num],
                           significant_topics$Direction[plot_num]),
        x = "Publication",
        y = "Expected Topic Proportion"
      ) +
      theme_minimal(base_size = 13) +
      theme(
        plot.title         = element_text(size = 15, face = "bold", hjust = 0.5),
        plot.subtitle      = element_text(size = 11, hjust = 0.5, color = "#64748b"),
        panel.grid.minor   = element_blank(),
        panel.grid.major.x = element_blank()
      ) +
      scale_y_continuous(labels = scales::percent_format(accuracy = 0.1),
                         limits = c(0, max(plot_data$ci_upper) * 1.1))

    print(p)
    cat("\n")
  }

} else {
  cat("No significant differences to plot.\n")
}
```

---

## 16. Faceted Comparison — Top 9 Most Different Topics

```{r faceted-comparison, fig.width=14, fig.height=10}
top_9_topics <- corpus_effects %>%
  arrange(desc(abs(Difference_Pct))) %>%
  head(9) %>%
  pull(Topic)

facet_data <- topic_props %>%
  select(corpus, all_of(paste0("Topic", top_9_topics))) %>%
  pivot_longer(-corpus, names_to = "topic", values_to = "proportion") %>%
  mutate(topic_num = as.numeric(str_remove(topic, "Topic"))) %>%
  group_by(corpus, topic_num) %>%
  summarize(
    mean     = mean(proportion),
    se       = sd(proportion) / sqrt(n()),
    ci_lower = mean - 1.96 * se,
    ci_upper = mean + 1.96 * se,
    .groups  = "drop"
  ) %>%
  mutate(
    topic_label = str_wrap(str_remove(topic_labels[topic_num], "^Topic \\d+: "), 25),
    publication = ifelse(corpus == "Relief_Society_Magazine",
                         "Relief Society\nMagazine", "Woman's\nExponent")
  )

ggplot(facet_data, aes(x = publication, y = mean, fill = publication)) +
  geom_col(alpha = 0.7) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.2) +
  facet_wrap(~topic_label, ncol = 3, scales = "free_y") +
  scale_fill_manual(values = c("Relief Society\nMagazine" = "#458B74",
                               "Woman's\nExponent"        = "#CD661D")) +
  labs(title = "Top 9 Topics: Comparison by Publication",
       x = NULL, y = "Mean Topic Proportion", fill = "Publication") +
  theme_minimal() +
  theme(axis.text.x    = element_blank(),
        legend.position = "bottom",
        strip.text      = element_text(size = 9, face = "bold")) +
  scale_y_continuous(labels = scales::percent)
```

---

## 17. Topic Prevalence Over Time

```{r topic-time-series, fig.width=12, fig.height=8}
topic_time <- topic_props %>%
  select(starts_with("Topic"), year, corpus) %>%
  group_by(year, corpus) %>%
  summarize(across(starts_with("Topic"), mean), .groups = "drop") %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "prevalence") %>%
  mutate(topic_num = as.numeric(str_remove(topic, "Topic")))

top_5_difference <- corpus_effects %>%
  arrange(desc(abs(Difference_Pct))) %>%
  head(5) %>%
  pull(Topic)

topic_time %>%
  filter(topic_num %in% top_5_difference) %>%
  mutate(topic_label = str_remove(topic_labels[topic_num], "^Topic \\d+: ")) %>%
  ggplot(aes(x = year, y = prevalence, color = topic_label, linetype = corpus)) +
  geom_line(linewidth = 1) +
  geom_point(size = 2) +
  facet_wrap(~topic_label, ncol = 2, scales = "free_y") +
  scale_color_brewer(palette = "Set2") +
  scale_linetype_manual(values = c("solid", "dashed")) +
  labs(title    = "Topic Prevalence Over Time",
       subtitle = "Top 5 topics with largest differences between publications",
       x = "Year", y = "Prevalence",
       color    = "Topic",
       linetype = "Publication") +
  theme_minimal() +
  theme(legend.position = "bottom") +
  scale_y_continuous(labels = scales::percent)
```


## Topic Continuity Over Time
```{r topic-continuity-time, fig.width=12, fig.height=8}
# Topics with the SMALLEST absolute difference between publications = most shared

top_5_similar <- corpus_effects %>%
  arrange(abs(Difference_Pct)) %>%
  head(6) %>%
  pull(Topic)

topic_time %>%
  filter(topic_num %in% top_5_similar) %>%
  mutate(
    topic_label = str_remove(topic_labels[topic_num], "^Topic \\d+: "),
    publication = ifelse(corpus == "Relief_Society_Magazine",
                         "Relief Society Magazine", "Woman's Exponent")
  ) %>%
  ggplot(aes(x = year, y = prevalence, color = publication, linetype = publication)) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 2.5, alpha = 0.7) +
  geom_smooth(method = "loess", se = FALSE, linewidth = 0.5, alpha = 0.4) +
  facet_wrap(~topic_label, ncol = 2, scales = "fixed") +
  scale_color_manual(values = c(
    "Woman's Exponent"        = "#CD661D",
    "Relief Society Magazine" = "#458B74"
  )) +
  scale_linetype_manual(values = c(
    "Woman's Exponent"        = "solid",
    "Relief Society Magazine" = "dashed"
  )) +
  labs(
    title    = "Topics of Greatest Continuity Between Publications",
    subtitle = "Lines tracking closely together = shared emphasis across time",
    x        = "Year",
    y        = "Mean Topic Proportion",
    color    = "Publication",
    linetype = "Publication"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    legend.position = "bottom",
    strip.text      = element_text(face = "bold", size = 10),
    panel.grid.minor = element_blank(),
    plot.title      = element_text(face = "bold", size = 15),
    plot.subtitle   = element_text(size = 11, color = "#64748b")
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1))
```

---

## 18. Topic Correlation Network

```{r topic-correlation-scatter, fig.width=10, fig.height=8}
topic_corr   <- topicCorr(stm_model_corpus)
corr_matrix  <- topic_corr$cor

corr_data <- as.data.frame(corr_matrix) %>%
  rownames_to_column("topic1") %>%
  pivot_longer(-topic1, names_to = "topic2", values_to = "correlation") %>%
  mutate(
    topic1_num = as.numeric(str_remove(topic1, "V")),
    topic2_num = as.numeric(str_remove(topic2, "V"))
  ) %>%
  filter(topic1_num < topic2_num, abs(correlation) > 0.02) %>%
  mutate(
    topic1_label = str_remove(topic_labels[topic1_num], "^Topic \\d+: "),
    topic2_label = str_remove(topic_labels[topic2_num], "^Topic \\d+: ")
  )

ggplot(corr_data, aes(x = topic1_num, y = topic2_num,
                      size = abs(correlation), color = correlation)) +
  geom_point(alpha = 0.8) +
  scale_color_gradient2(low = "#dc2626", mid = "#fbbf24", high = "#2563eb",
                        midpoint = 0, limits = c(-0.2, 0.2)) +
  scale_size_continuous(range = c(3, 15)) +
  labs(title    = "Topic Correlation Network",
       subtitle = "Weak correlations indicate well-separated topics (good!)",
       x = "Topic Number", y = "Topic Number",
       color = "Correlation", size = "Abs. Correlation") +
  theme_minimal(base_size = 13)
```

### Correlation Heatmap

```{r correlation-heatmap}
heatmap_data <- as.data.frame(corr_matrix) %>%
  rownames_to_column("topic1") %>%
  pivot_longer(-topic1, names_to = "topic2", values_to = "correlation") %>%
  mutate(
    topic1_num = as.numeric(str_remove(topic1, "V")),
    topic2_num = as.numeric(str_remove(topic2, "V"))
  )

ggplot(heatmap_data, aes(x = topic1_num, y = topic2_num, fill = correlation)) +
  geom_tile(color = "white", linewidth = 0.5) +
  scale_fill_gradient2(low = "#dc2626", mid = "white", high = "#2563eb",
                       midpoint = 0, limits = c(-0.15, 0.15),
                       breaks = seq(-0.15, 0.15, 0.05)) +
  labs(title    = "Topic Correlation Heatmap",
       subtitle = "Weak correlations are normal — indicates distinct topics",
       x = "Topic Number", y = "Topic Number", fill = "Correlation") +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        panel.grid  = element_blank()) +
  coord_fixed() +
  scale_x_continuous(breaks = seq(1, chosen_K, 1)) +
  scale_y_continuous(breaks = seq(1, chosen_K, 1))
```

### Side-by-Side Heatmaps by Publication

```{r heatmap-by-publication}
calc_pub_corr <- function(pub_name) {
  topic_props %>%
    filter(corpus == pub_name) %>%
    select(starts_with("Topic")) %>%
    as.matrix() %>%
    cor()
}

corr_rs <- calc_pub_corr("Relief_Society_Magazine")
corr_we <- calc_pub_corr("Womans_Exponent")

prepare_heatmap_data <- function(corr_matrix, pub_name) {
  as.data.frame(corr_matrix) %>%
    rownames_to_column("topic1") %>%
    pivot_longer(-topic1, names_to = "topic2", values_to = "correlation") %>%
    mutate(
      topic1_num  = as.numeric(str_remove(topic1, "Topic")),
      topic2_num  = as.numeric(str_remove(topic2, "Topic")),
      publication = pub_name
    )
}

bind_rows(
  prepare_heatmap_data(corr_rs, "Relief Society Magazine"),
  prepare_heatmap_data(corr_we, "Woman's Exponent")
) %>%
  ggplot(aes(x = topic1_num, y = topic2_num, fill = correlation)) +
  geom_tile(color = "white", linewidth = 0.3) +
  facet_wrap(~publication, ncol = 2) +
  scale_fill_gradient2(low = "#dc2626", mid = "white", high = "#2563eb",
                       midpoint = 0, limits = c(-0.3, 0.3)) +
  labs(title    = "Topic Correlation Comparison",
       subtitle = "How do topic relationships differ between publications?",
       x = "Topic Number", y = "Topic Number", fill = "Correlation") +
  theme_minimal() +
  theme(panel.grid = element_blank(),
        strip.text = element_text(size = 12, face = "bold")) +
  coord_fixed() +
  scale_x_continuous(breaks = seq(5, chosen_K, 5)) +
  scale_y_continuous(breaks = seq(5, chosen_K, 5))
```

---

## 19. Scatterplot: Topic Prevalence by Publication

```{r prevalence-scatter}
topic_means <- topic_props %>%
  group_by(corpus) %>%
  summarize(across(starts_with("Topic"), mean)) %>%
  pivot_longer(-corpus, names_to = "topic", values_to = "prevalence") %>%
  mutate(topic_num = as.numeric(str_remove(topic, "Topic"))) %>%
  pivot_wider(names_from = corpus, values_from = prevalence) %>%
  left_join(corpus_effects %>% select(Topic, P_value, Significant),
            by = c("topic_num" = "Topic")) %>%
  mutate(
    label = str_trunc(str_remove(topic_labels[topic_num], "^Topic \\d+: "), 30),
    distance_from_diagonal = abs(Womans_Exponent - Relief_Society_Magazine),
    show_label = Significant |
                 (!Significant & topic_num %in% head(order(distance_from_diagonal), 3))
  )

ggplot(topic_means, aes(x = Relief_Society_Magazine, y = Womans_Exponent)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed",
              color = "#94a3b8", linewidth = 1.5) +
  geom_point(aes(color = Significant,
                 size  = abs(Womans_Exponent - Relief_Society_Magazine)),
             alpha = 0.7) +
  geom_text_repel(
    data = topic_means %>% filter(show_label),
    aes(label = label, color = Significant),
    size = 3.5, max.overlaps = 20,
    box.padding = 0.5, point.padding = 0.3,
    segment.color = "#64748b", segment.linewidth = 0.3,
    show.legend = FALSE
  ) +
  scale_color_manual(values = c("FALSE" = "#474747", "FALSE" = "#474747"),
                     labels = c("No significant difference", "Significant difference")) +
  scale_size_continuous(range = c(3, 12), guide = "none") +
  labs(title    = "Topic Prevalence Comparison",
       subtitle = "Diagonal = equal prevalence; distance from line = magnitude of difference",
       x = "Relief Society Magazine (Mean Proportion)",
       y = "Woman's Exponent (Mean Proportion)",
       color = NULL) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "bottom",
        plot.title      = element_text(size = 16, face = "bold")) +
  scale_x_continuous(labels = scales::percent_format(accuracy = 0.1)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1))
```

---

## 20. Word Clouds

```{r wordcloud-single, fig.width=8, fig.height=6}
topic_to_show <- 17  # CHANGE THIS

topic_words_wc <- labelTopics(stm_model_corpus, topics = topic_to_show, n = 50)
word_freq <- data.frame(
  word = topic_words_wc$prob[1, ],
  freq = rank(desc(seq_along(topic_words_wc$prob[1, ])))
)

set.seed(123)
wordcloud(words = word_freq$word, freq = word_freq$freq,
          min.freq = 1, max.words = 50, random.order = FALSE,
          rot.per = 0.35, colors = brewer.pal(8, "Dark2"), scale = c(4, 0.5))
title(main = topic_labels[topic_to_show], cex.main = 1.5, col.main = "#1e3a8a")
```

```{r wordcloud-comparison, fig.width=14, fig.height=7}
# FIX 8: was using freq_rs for BOTH panels — left panel now correctly uses freq_we
topic_num_wc <- 4  # CHANGE THIS

topic_docs_wc <- topic_props
topic_col_wc  <- paste0("Topic", topic_num_wc)

get_corpus_words <- function(corpus_name) {
  processed_texts %>%
    filter(corpus == corpus_name) %>%
    left_join(topic_docs_wc %>% select(doc_id, !!sym(topic_col_wc)), by = "doc_id") %>%
    filter(!!sym(topic_col_wc) > quantile(!!sym(topic_col_wc), 0.75, na.rm = TRUE)) %>%
    pull(text_final) %>%
    paste(collapse = " ") %>%
    strsplit("\\s+") %>%
    `[[`(1) %>%
    table()
}

freq_we <- get_corpus_words("Womans_Exponent")
freq_rs <- get_corpus_words("Relief_Society_Magazine")

par(mfrow = c(1, 2))

set.seed(123)
wordcloud(names(freq_we), freq_we, max.words = 100,
          colors = brewer.pal(8, "BuGn")[3:8], scale = c(3, 0.5))
title(main = "Woman's Exponent", col.main = "#CD661D")

set.seed(123)
wordcloud(names(freq_rs), freq_rs, max.words = 100,
          colors = brewer.pal(8, "BuGn")[3:8], scale = c(3, 0.5))
title(main = "Relief Society Magazine", col.main = "#556B2F")

par(mfrow = c(1, 1))
```

### Whole-Corpus Word Cloud Comparison

```{r wordcloud-whole-corpus, fig.width=14, fig.height=7}
# ============================================================
# Side-by-side word clouds: ALL words per publication
# Shows the overall vocabulary fingerprint of each periodical
# ============================================================

freq_we_all <- processed_texts %>%
  filter(corpus == "Womans_Exponent") %>%
  pull(text_final) %>%
  paste(collapse = " ") %>%
  strsplit("\\s+") %>%
  `[[`(1) %>%
  table()

freq_rsm_all <- processed_texts %>%
  filter(corpus == "Relief_Society_Magazine") %>%
  pull(text_final) %>%
  paste(collapse = " ") %>%
  strsplit("\\s+") %>%
  `[[`(1) %>%
  table()

par(mfrow = c(1, 2))

set.seed(123)
wordcloud(names(freq_we_all), freq_we_all, max.words = 150,
          colors = brewer.pal(9, "Greys")[4:9], scale = c(4, 0.5))
title(main = "Woman's Exponent — Full Corpus", col.main = "#030303", cex.main = 1.3)

set.seed(123)
wordcloud(names(freq_rsm_all), freq_rsm_all, max.words = 150,
          colors = brewer.pal(9, "Greys")[4:9], scale = c(4, 0.5))
title(main = "Relief Society Magazine — Full Corpus", col.main = "#030303", cex.main = 1.3)

par(mfrow = c(1, 1))
```

### Distinctive Words: What Makes Each Publication Unique

```{r wordcloud-distinctive, fig.width=16, fig.height=9}
# ============================================================
# Words that are disproportionately MORE common in one pub
# vs the other — the vocabulary that distinguishes them
# ============================================================

# Build frequency tables with proportions
we_df <- tibble(word = names(freq_we_all), we_count = as.integer(freq_we_all)) %>%
  mutate(we_prop = we_count / sum(we_count))
rsm_df <- tibble(word = names(freq_rsm_all), rsm_count = as.integer(freq_rsm_all)) %>%
  mutate(rsm_prop = rsm_count / sum(rsm_count))

# Common OCR fragments and word-pieces to exclude
ocr_junk <- c("ters", "tion", "ence", "ment", "ness", "ings", "tive", "ance",
              "ered", "deliv", "presi", "inter", "encour", "terest", "testi",
              "bers", "soci", "coun", "howe", "dren", "chil", "pariel",
              "organiza", "ganized", "ference", "musser", "selion",
              "suf", "cts", "ref", "ber", "ter", "pre", "dis", "hus",
              "peo", "ety", "ous", "lar", "est", "con", "mony", "lief")

word_compare <- full_join(we_df, rsm_df, by = "word") %>%
  replace_na(list(we_count = 0, rsm_count = 0, we_prop = 0, rsm_prop = 0)) %>%
  filter(
    we_count + rsm_count >= 20,         # Only words with meaningful frequency
    nchar(word) >= 5,                   # Require 5+ chars to avoid most fragments
    !grepl("^[^a-z]+$", word),          # Drop pure symbols/numbers
    !word %in% ocr_junk,               # Drop known OCR fragments
    !grepl("^(pre|suf|dis|inter|un|re)[a-z]{0,2}$", word),  # Drop prefix-only fragments
    !grepl("^[a-z]{1,3}(tion|ment|ence|ness|ings|tive|ance|ered|ment)$", word),  # Drop suffix-only fragments
    # Require word to exist in BOTH corpora (at least a little) — truly distinctive
    # words are used MORE in one, not ONLY in one (which signals OCR artifact)
    we_count >= 3 & rsm_count >= 3
  ) %>%
  mutate(log_ratio = log2((we_prop + 0.00001) / (rsm_prop + 0.00001)))

# Words most distinctive to WE
we_distinctive <- word_compare %>%
  arrange(desc(log_ratio)) %>%
  head(80)

# Words most distinctive to RSM
rsm_distinctive <- word_compare %>%
  arrange(log_ratio) %>%
  head(80)

par(mfrow = c(1, 2), mar = c(1, 1, 3, 1))

set.seed(123)
wordcloud(we_distinctive$word, we_distinctive$log_ratio,
          max.words = 80, min.freq = 0, rot.per = 0.4,
          colors = brewer.pal(9, "Greys")[4:9], scale = c(3.5, 0.5))
title(main = "\nDistinctive to Woman's Exponent", col.main = "#030303", cex.main = 1.6, line = 0.7)

set.seed(123)
wordcloud(rsm_distinctive$word, abs(rsm_distinctive$log_ratio),
          max.words = 80, min.freq = 0, rot.per = 0.4,
          colors = brewer.pal(9, "Greys")[4:9], scale = c(3.0, 0.5))
title(main = "\nDistinctive to Relief Society Magazine", col.main = "#030303", cex.main = 1.6, line = 0.7)

par(mfrow = c(1, 1))
```

---

## 21. Topic Quality

```{r topic-quality-scatter, fig.width=10, fig.height=8}
# Compute coherence and exclusivity separately for reliability
sem_coh_vals <- semanticCoherence(stm_model_corpus, docs)
excl_vals    <- exclusivity(stm_model_corpus)

quality_df <- data.frame(
  topic     = 1:chosen_K,
  sem_coh   = sem_coh_vals,
  excl      = excl_vals
)
quality_df$label <- str_trunc(str_remove(topic_labels, "^Topic \\d+: "), 25)

# Join significance data
quality_df <- merge(quality_df,
                    corpus_effects[, c("Topic", "Significant", "Difference_Pct")],
                    by.x = "topic", by.y = "Topic", all.x = TRUE)

ggplot(quality_df, aes(x = sem_coh, y = excl)) +
  geom_point(aes(color = Significant, size = abs(Difference_Pct)), alpha = 0.7) +
  geom_text(aes(label = topic), size = 3, nudge_y = 0.3, check_overlap = TRUE) +
  scale_color_manual(values = c("FALSE" = "#94a3b8", "TRUE" = "#ef4444"),
                     labels = c("Not significant", "Significant difference")) +
  scale_size_continuous(range = c(3, 10), guide = "none") +
  labs(title    = "Topic Quality: Semantic Coherence vs Exclusivity",
       subtitle = "Upper right = high quality | Numbers = Topic IDs",
       x = "Semantic Coherence\n(higher = words co-occur more)",
       y = "Exclusivity\n(higher = words unique to topic)",
       color = NULL) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "bottom",
        plot.title      = element_text(face = "bold", size = 15))
```

---

# PART III: DEEP COMPARATIVE ANALYSIS

---

## 22. Topic Continuity & Handoff Between Publications

This section identifies which topics are **shared** (present in both publications), which are **signature** (strongly associated with one), and which represent an editorial **handoff** (declining in one, emerging in the other).

```{r topic-continuity, fig.width=12, fig.height=8}
cat(rep("=", 70), "\n", sep = "")
cat("TOPIC CONTINUITY ANALYSIS\n")
cat(rep("=", 70), "\n\n", sep = "")

# Mean topic proportion per publication
pub_means <- topic_props %>%
  group_by(corpus) %>%
  summarize(across(starts_with("Topic"), mean), .groups = "drop") %>%
  pivot_longer(-corpus, names_to = "topic", values_to = "prevalence") %>%
  mutate(topic_num = as.integer(str_remove(topic, "Topic"))) %>%
  pivot_wider(names_from = corpus, values_from = prevalence)

# Classify topics
pub_means <- pub_means %>%
  mutate(
    label = str_remove(topic_labels[topic_num], "^Topic \\d+: "),
    we_pct = Womans_Exponent * 100,
    rsm_pct = Relief_Society_Magazine * 100,
    ratio = we_pct / pmax(rsm_pct, 0.001),
    category = case_when(
      ratio > 2.0  ~ "WE Signature",
      ratio < 0.5  ~ "RSM Signature",
      ratio >= 0.8 & ratio <= 1.25 ~ "Shared (Balanced)",
      ratio > 1.25 ~ "Shared (WE-leaning)",
      TRUE ~ "Shared (RSM-leaning)"
    )
  )

cat("Topic Classification:\n\n")
for (cat_name in c("WE Signature", "Shared (Balanced)", "Shared (WE-leaning)",
                    "Shared (RSM-leaning)", "RSM Signature")) {
  topics_in_cat <- pub_means %>% filter(category == cat_name)
  if (nrow(topics_in_cat) > 0) {
    cat(cat_name, ":\n")
    for (i in 1:nrow(topics_in_cat)) {
      row <- topics_in_cat[i, ]
      cat(sprintf("  T%d: %-35s  WE: %5.1f%%  RSM: %5.1f%%\n",
                  row$topic_num, row$label, row$we_pct, row$rsm_pct))
    }
    cat("\n")
  }
}

# Visualize: Dumbbell plot
pub_means_long <- pub_means %>%
  select(topic_num, label, category, Womans_Exponent, Relief_Society_Magazine) %>%
  pivot_longer(c(Womans_Exponent, Relief_Society_Magazine),
               names_to = "pub", values_to = "prevalence") %>%
  mutate(
    publication = ifelse(pub == "Womans_Exponent", "Woman's Exponent", "Relief Society Magazine"),
    display_label = paste0("T", topic_num, ": ", str_trunc(label, 30))
  )

ggplot(pub_means_long, aes(x = prevalence, y = reorder(display_label, prevalence))) +
  geom_line(aes(group = display_label), color = "grey60", linewidth = 1.5) +
  geom_point(aes(color = publication), size = 4) +
  scale_color_manual(values = c("Woman's Exponent" = "#CD661D",
                                "Relief Society Magazine" = "#458B74")) +
  labs(title = "Topic Prevalence: Dumbbell Comparison",
       subtitle = "Distance between dots = magnitude of difference between publications",
       x = "Mean Topic Proportion", y = NULL, color = "Publication") +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom",
        panel.grid.major.y = element_blank()) +
  scale_x_continuous(labels = percent_format())
```

### Topic Fingerprint Radar

```{r topic-fingerprint, fig.width=10, fig.height=10}
# Radar/polar chart showing each publication's topic "fingerprint"
fingerprint_data <- pub_means %>%
  select(topic_num, label, we_pct, rsm_pct) %>%
  pivot_longer(c(we_pct, rsm_pct), names_to = "pub", values_to = "pct") %>%
  mutate(
    publication = ifelse(pub == "we_pct", "Woman's Exponent", "Relief Society Magazine"),
    topic_label = paste0("T", topic_num)
  )

ggplot(fingerprint_data, aes(x = topic_label, y = pct, fill = publication)) +
  geom_col(position = "dodge", alpha = 0.8) +
  coord_polar() +
  scale_fill_manual(values = c("Woman's Exponent" = "#CD661D",
                               "Relief Society Magazine" = "#458B74")) +
  labs(title = "Topic Fingerprint: Publication Profiles",
       subtitle = "Each spoke = one topic; length = prevalence",
       x = NULL, y = "Prevalence (%)", fill = "Publication") +
  theme_minimal(base_size = 10) +
  theme(legend.position = "bottom",
        axis.text.y = element_blank(),
        panel.grid.minor = element_blank())
```

---

## 23. Within-Topic Vocabulary Comparison

When both publications discuss the same topic, do they use different language? This reveals **how** each publication frames shared concerns.

```{r vocab-comparison, fig.width=16, fig.height=20}
cat(rep("=", 70), "\n", sep = "")
cat("WITHIN-TOPIC VOCABULARY COMPARISON\n")
cat(rep("=", 70), "\n\n", sep = "")

# OCR junk / nonsensical fragment blacklist
vocab_junk <- c(
  # Common OCR fragments (broken words, suffix/prefix remnants)
  "ing", "tion", "ment", "ness", "ings", "tive", "ance", "ence",
  "ered", "ters", "bers", "dren", "howe", "ould", "ight", "ther",
  "ated", "ting", "ally", "ible", "able", "ious", "eous", "ical",
  "onal", "ment", "ship", "ward", "wise", "like", "less", "ness",
  # Truncated word fragments
  "deliv", "presi", "inter", "encour", "terest", "testi",
  "soci", "coun", "chil", "pariel", "organiza", "ganized",
  "ference", "musser", "selion",
  # Structural / boilerplate remnants
  "column", "page", "pages", "number", "vol", "volume",
  "chapter", "section", "article", "editor", "editorial",
  "continued", "copyright", "printed", "published",
  "january", "february", "march", "april", "june",
  "july", "august", "september", "october", "november", "december",
  # Common function words that slip through stopword removal
  "also", "upon", "much", "many", "well", "even", "come",
  "came", "made", "make", "said", "just", "like", "shall",
  "would", "could", "should", "may", "might", "must",
  "yet", "still", "ever", "every", "very", "most",
  "one", "two", "three", "four", "five", "six",
  "first", "second", "third", "last", "next"
)

# Select top 6 most "shared" topics (closest to equal prevalence)
shared_topics <- pub_means %>%
  mutate(balance = abs(log2(ratio))) %>%
  arrange(balance) %>%
  head(6) %>%
  pull(topic_num)

cat("Most shared topics for vocabulary comparison:\n")
for (t in shared_topics) {
  cat(sprintf("  T%d: %s\n", t, str_remove(topic_labels[t], "^Topic \\d+: ")))
}
cat("\n")

# For each shared topic, find words that differ most between publications
get_topic_words_by_pub <- function(topic_num, pub_name) {
  topic_col <- paste0("Topic", topic_num)

  # Get top-quartile documents for this topic in this publication
  pub_docs <- topic_props %>%
    filter(corpus == pub_name)
  threshold <- quantile(pub_docs[[topic_col]], 0.75, na.rm = TRUE)

  doc_ids <- pub_docs %>%
    filter(.data[[topic_col]] >= threshold) %>%
    pull(doc_id)

  # Get word frequencies from these documents
  words <- processed_texts %>%
    filter(doc_id %in% doc_ids) %>%
    pull(text_final) %>%
    paste(collapse = " ") %>%
    str_split("\\s+") %>%
    `[[`(1)

  freq <- sort(table(words), decreasing = TRUE)
  tibble(word = names(freq), count = as.integer(freq)) %>%
    mutate(proportion = count / sum(count)) %>%
    filter(
      nchar(word) >= 4,                                    # Min 4 chars
      !word %in% vocab_junk,                               # Drop known junk
      !grepl("^[^a-z]+$", word),                           # Drop pure symbols/numbers
      !grepl("^[a-z]{1,3}(tion|ment|ence|ness|ings|tive|ance)$", word),  # Suffix-only
      !grepl("^(pre|suf|dis|un|re)[a-z]{0,2}$", word)     # Prefix-only fragments
    )
}

# Build comparison plots for shared topics
vocab_plots <- list()
for (idx in seq_along(shared_topics)) {
  t <- shared_topics[idx]

  words_we  <- get_topic_words_by_pub(t, "Womans_Exponent")
  words_rsm <- get_topic_words_by_pub(t, "Relief_Society_Magazine")

  # Join and compute log-ratio
  word_compare <- full_join(
    words_we %>% select(word, we_prop = proportion),
    words_rsm %>% select(word, rsm_prop = proportion),
    by = "word"
  ) %>%
    replace_na(list(we_prop = 0.0001, rsm_prop = 0.0001)) %>%
    mutate(
      log_ratio = log2(we_prop / rsm_prop),
      avg_prop = (we_prop + rsm_prop) / 2
    ) %>%
    filter(avg_prop > 0.001) %>%  # Only words with meaningful frequency
    arrange(desc(abs(log_ratio)))

  # Top 20 words each direction
  top_we  <- word_compare %>% filter(log_ratio > 0) %>% head(20)
  top_rsm <- word_compare %>% filter(log_ratio < 0) %>% head(20)
  plot_words <- bind_rows(top_we, top_rsm) %>%
    mutate(
      direction = ifelse(log_ratio > 0, "More in WE", "More in RSM"),
      word = reorder(word, log_ratio)
    )

  p <- ggplot(plot_words, aes(x = log_ratio, y = word, fill = direction)) +
    geom_col(alpha = 0.8) +
    geom_vline(xintercept = 0, linewidth = 0.8) +
    scale_fill_manual(values = c("More in WE" = "#CD661D", "More in RSM" = "#458B74")) +
    labs(title = paste0("T", t, ": ", str_trunc(str_remove(topic_labels[t], "^Topic \\d+: "), 35)),
         x = "Log2 Ratio (WE / RSM)", y = NULL, fill = NULL) +
    theme_minimal(base_size = 8) +
    theme(legend.position = "none", plot.title = element_text(size = 10, face = "bold"))

  vocab_plots[[idx]] <- p
}

# Combine plots
if (length(vocab_plots) >= 6) {
  (vocab_plots[[1]] | vocab_plots[[2]] | vocab_plots[[3]]) /
  (vocab_plots[[4]] | vocab_plots[[5]] | vocab_plots[[6]]) +
    plot_annotation(
      title = "Within-Topic Vocabulary Shifts",
      subtitle = "Top 20 words each publication emphasizes differently when discussing the SAME topic",
      theme = theme(plot.title = element_text(size = 16, face = "bold"))
    )
} else if (length(vocab_plots) >= 1) {
  wrap_plots(vocab_plots, ncol = 3) +
    plot_annotation(title = "Within-Topic Vocabulary Shifts")
}
```

---

## 24. Topic Diversity & Concentration

Is one publication more topically diverse or more narrowly focused? These measures reveal editorial strategy.

```{r topic-diversity, fig.width=12, fig.height=10}
cat(rep("=", 70), "\n", sep = "")
cat("TOPIC DIVERSITY ANALYSIS\n")
cat(rep("=", 70), "\n\n", sep = "")

# Shannon entropy per document (higher = more diverse)
doc_entropy <- topic_props %>%
  select(doc_id, corpus, starts_with("Topic")) %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "p") %>%
  filter(p > 0) %>%
  group_by(doc_id, corpus) %>%
  summarize(entropy = -sum(p * log2(p)), .groups = "drop")

# Gini concentration per document (higher = more concentrated on one topic)
doc_gini <- topic_props %>%
  select(doc_id, corpus, starts_with("Topic")) %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "p") %>%
  group_by(doc_id, corpus) %>%
  summarize(
    max_topic_prop = max(p),
    gini = 1 - sum(p^2),  # Inverse Herfindahl (0 = one topic dominates, 1 = even)
    .groups = "drop"
  )

# Publication-level summary
diversity_summary <- doc_entropy %>%
  left_join(doc_gini, by = c("doc_id", "corpus")) %>%
  group_by(corpus) %>%
  summarize(
    mean_entropy = mean(entropy),
    sd_entropy = sd(entropy),
    mean_gini = mean(gini),
    mean_max_prop = mean(max_topic_prop),
    pct_strong_exemplar = mean(max_topic_prop >= 0.4) * 100,
    .groups = "drop"
  ) %>%
  mutate(publication = ifelse(corpus == "Womans_Exponent",
                              "Woman's Exponent", "Relief Society Magazine"))

cat("Diversity Metrics:\n\n")
cat(sprintf("%-25s  Entropy  Gini   Max-Topic  Strong-Exemplar%%\n", "Publication"))
cat(rep("-", 75), "\n", sep = "")
for (i in 1:nrow(diversity_summary)) {
  r <- diversity_summary[i, ]
  cat(sprintf("%-25s  %.2f     %.3f  %.1f%%       %.1f%%\n",
              r$publication, r$mean_entropy, r$mean_gini,
              r$mean_max_prop * 100, r$pct_strong_exemplar))
}

# Entropy distribution plot
p1 <- doc_entropy %>%
  mutate(publication = ifelse(corpus == "Womans_Exponent",
                              "Woman's Exponent", "Relief Society Magazine")) %>%
  ggplot(aes(x = entropy, fill = publication)) +
  geom_density(alpha = 0.5, linewidth = 0.8) +
  scale_fill_manual(values = c("Woman's Exponent" = "#CD661D",
                               "Relief Society Magazine" = "#458B74")) +
  labs(title = "Topic Diversity per Document",
       subtitle = "Higher entropy = article discusses more topics evenly",
       x = "Shannon Entropy (bits)", y = "Density", fill = "Publication") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom")

# Dominant topic concentration plot
p2 <- doc_gini %>%
  mutate(publication = ifelse(corpus == "Womans_Exponent",
                              "Woman's Exponent", "Relief Society Magazine")) %>%
  ggplot(aes(x = max_topic_prop, fill = publication)) +
  geom_density(alpha = 0.5, linewidth = 0.8) +
  geom_vline(xintercept = 0.4, linetype = "dashed", color = "grey40") +
  ggplot2::annotate("text", x = 0.42, y = 0, label = "Exemplar\nthreshold", size = 3, hjust = 0) +
  scale_fill_manual(values = c("Woman's Exponent" = "#CD661D",
                               "Relief Society Magazine" = "#458B74")) +
  labs(title = "Topic Concentration per Document",
       subtitle = "Higher = article dominated by single topic; dashed line = 40% exemplar threshold",
       x = "Dominant Topic Proportion", y = "Density", fill = "Publication") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom") +
  scale_x_continuous(labels = percent_format())

p1 / p2
```

### Effective Number of Topics per Publication

```{r effective-topics, fig.width=10, fig.height=5}
# Publication-level topic distribution (how many topics does each pub actually "use"?)
pub_topic_dist <- topic_props %>%
  group_by(corpus) %>%
  summarize(across(starts_with("Topic"), mean), .groups = "drop") %>%
  pivot_longer(-corpus, names_to = "topic", values_to = "prevalence") %>%
  mutate(
    topic_num = as.integer(str_remove(topic, "Topic")),
    publication = ifelse(corpus == "Womans_Exponent",
                         "Woman's Exponent", "Relief Society Magazine"),
    label = str_trunc(str_remove(topic_labels[topic_num], "^Topic \\d+: "), 25)
  )

# Effective number of topics = exp(entropy of topic distribution)
pub_ent <- pub_topic_dist %>%
  filter(prevalence > 0) %>%
  group_by(publication) %>%
  summarize(
    eff_topics = exp(-sum(prevalence * log(prevalence))),
    .groups = "drop"
  )
cat("\nEffective number of topics:\n")
for (i in 1:nrow(pub_ent)) {
  cat(sprintf("  %s: %.1f (of %d)\n", pub_ent$publication[i], pub_ent$eff_topics[i], chosen_K))
}

# Stacked area showing topic weight per publication
ggplot(pub_topic_dist, aes(x = reorder(label, -prevalence), y = prevalence,
                            fill = publication)) +
  geom_col(position = "dodge", alpha = 0.8) +
  scale_fill_manual(values = c("Woman's Exponent" = "#CD661D",
                               "Relief Society Magazine" = "#458B74")) +
  labs(title = "Topic Weight Distribution by Publication",
       subtitle = paste0("Effective topics: WE = ", round(pub_ent$eff_topics[pub_ent$publication == "Woman's Exponent"], 1),
                         " | RSM = ", round(pub_ent$eff_topics[pub_ent$publication == "Relief Society Magazine"], 1)),
       x = NULL, y = "Mean Proportion", fill = "Publication") +
  theme_minimal(base_size = 10) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
        legend.position = "bottom") +
  scale_y_continuous(labels = percent_format())
```

---

## 25. Temporal Trajectory Analysis

How do topic prevalences evolve within each publication, and what happens at the transition point?

```{r temporal-trajectory, fig.width=14, fig.height=10}
cat(rep("=", 70), "\n", sep = "")
cat("TEMPORAL TRAJECTORY ANALYSIS\n")
cat(rep("=", 70), "\n\n", sep = "")

# Yearly topic prevalence per publication
yearly_topics <- topic_props %>%
  filter(!is.na(year)) %>%
  select(year, corpus, starts_with("Topic")) %>%
  group_by(year, corpus) %>%
  summarize(across(starts_with("Topic"), mean), .groups = "drop") %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "prevalence") %>%
  mutate(
    topic_num = as.integer(str_remove(topic, "Topic")),
    publication = ifelse(corpus == "Womans_Exponent",
                         "Woman's Exponent", "Relief Society Magazine"),
    label = str_remove(topic_labels[topic_num], "^Topic \\d+: ")
  )

# Pick top 6 most significant topics
top_sig_topics <- corpus_effects %>%
  arrange(P_value) %>%
  head(6) %>%
  pull(Topic)

yearly_topics %>%
  filter(topic_num %in% top_sig_topics) %>%
  ggplot(aes(x = year, y = prevalence, color = publication)) +
  geom_point(alpha = 0.6, size = 2) +
  geom_smooth(method = "loess", se = TRUE, alpha = 0.2, linewidth = 1.2) +
  facet_wrap(~str_wrap(label, 30), ncol = 3, scales = "free_y") +
  scale_color_manual(values = c("Woman's Exponent" = "#CD661D",
                                "Relief Society Magazine" = "#458B74")) +
  labs(title = "Topic Trajectories Over Time",
       subtitle = "Top 6 most significantly different topics with LOESS trends",
       x = "Year", y = "Mean Prevalence", color = "Publication") +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom",
        strip.text = element_text(face = "bold", size = 9)) +
  scale_y_continuous(labels = percent_format())
```

### Shared Topic Trajectories

```{r shared-trajectories, fig.width=14, fig.height=10}
# Topics with LEAST difference = most shared
shared_traj_topics <- corpus_effects %>%
  arrange(abs(Difference_Pct)) %>%
  head(6) %>%
  pull(Topic)

yearly_topics %>%
  filter(topic_num %in% shared_traj_topics) %>%
  ggplot(aes(x = year, y = prevalence, color = publication)) +
  geom_point(alpha = 0.6, size = 2) +
  geom_smooth(method = "loess", se = TRUE, alpha = 0.2, linewidth = 1.2) +
  facet_wrap(~str_wrap(label, 30), ncol = 3, scales = "free_y") +
  scale_color_manual(values = c("Woman's Exponent" = "#CD661D",
                                "Relief Society Magazine" = "#458B74")) +
  labs(title = "Shared Topic Trajectories",
       subtitle = "Topics with LEAST difference between publications — continuity in discourse",
       x = "Year", y = "Mean Prevalence", color = "Publication") +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom",
        strip.text = element_text(face = "bold", size = 9)) +
  scale_y_continuous(labels = percent_format())
```

### Topic Prevalence Heatmap Over Time

```{r topic-time-heatmap, fig.width=14, fig.height=8}
# Heatmap: years × topics, faceted by publication
yearly_topics %>%
  mutate(short_label = paste0("T", topic_num)) %>%
  ggplot(aes(x = year, y = short_label, fill = prevalence)) +
  geom_tile(color = "white", linewidth = 0.3) +
  facet_wrap(~publication, ncol = 2) +
  scale_fill_gradient(low = "white", high = "#2E4A1E",
                      labels = percent_format()) +
  labs(title = "Topic Prevalence Over Time: Full Landscape",
       subtitle = "Darker = higher prevalence in that year",
       x = "Year", y = "Topic", fill = "Prevalence") +
  theme_minimal(base_size = 10) +
  theme(strip.text = element_text(face = "bold", size = 12),
        panel.grid = element_blank()) +
  scale_y_discrete(limits = rev)
```

---

### Percentage Change in Topics Between Publications

How much does each topic's prevalence **shift** from the Exponent era to the Magazine era? This captures the editorial transition in quantitative terms.

```{r topic-pct-change, fig.width=12, fig.height=8}
cat(rep("=", 70), "\n", sep = "")
cat("PERCENTAGE CHANGE IN TOPICS: WE -> RSM\n")
cat(rep("=", 70), "\n\n", sep = "")

# Mean prevalence per topic per publication
era_means <- topic_props %>%
  group_by(corpus) %>%
  summarize(across(starts_with("Topic"), mean), .groups = "drop") %>%
  pivot_longer(-corpus, names_to = "topic", values_to = "prevalence") %>%
  mutate(topic_num = as.integer(str_remove(topic, "Topic"))) %>%
  pivot_wider(names_from = corpus, values_from = prevalence)

# Compute percentage change: (RSM - WE) / WE * 100
era_change <- era_means %>%
  mutate(
    label = str_remove(topic_labels[topic_num], "^Topic \\d+: "),
    we_pct = Womans_Exponent * 100,
    rsm_pct = Relief_Society_Magazine * 100,
    abs_change = rsm_pct - we_pct,
    pct_change = ifelse(Womans_Exponent > 0.001,
                        (Relief_Society_Magazine - Womans_Exponent) / Womans_Exponent * 100,
                        NA_real_),
    direction = case_when(
      abs_change > 0.5  ~ "Grew in Magazine",
      abs_change < -0.5 ~ "Declined in Magazine",
      TRUE ~ "Stable"
    )
  ) %>%
  arrange(desc(abs_change))

cat("Topic changes (WE era -> RSM era):\n\n")
cat(sprintf("%-35s  %6s  %6s  %8s  %8s\n",
            "Topic", "WE %", "RSM %", "Change", "% Change"))
cat(rep("-", 80), "\n", sep = "")
for (i in 1:nrow(era_change)) {
  r <- era_change[i, ]
  pct_str <- ifelse(is.na(r$pct_change), "N/A", sprintf("%+.0f%%", r$pct_change))
  cat(sprintf("%-35s  %5.1f%%  %5.1f%%  %+6.1fpp  %8s\n",
              str_trunc(r$label, 35), r$we_pct, r$rsm_pct, r$abs_change, pct_str))
}

# --- Absolute change bar chart (percentage points) ---
p_abs <- era_change %>%
  mutate(display = paste0("T", topic_num, ": ", str_trunc(label, 28)),
         display = reorder(display, abs_change)) %>%
  ggplot(aes(x = abs_change, y = display, fill = direction)) +
  geom_col(alpha = 0.85) +
  geom_vline(xintercept = 0, linewidth = 1) +
  scale_fill_manual(values = c("Grew in Magazine" = "#458B74",
                                "Declined in Magazine" = "#CD661D",
                                "Stable" = "#94a3b8")) +
  labs(title = "Topic Change: Woman's Exponent -> Relief Society Magazine",
       subtitle = "Absolute change in percentage points of topic prevalence",
       x = "Change (percentage points)", y = NULL, fill = NULL) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom", panel.grid.major.y = element_blank())

print(p_abs)
```

```{r topic-pct-change-relative, fig.width=12, fig.height=8}
# --- Relative (%) change bar chart ---
era_change_filtered <- era_change %>%
  filter(!is.na(pct_change), abs(pct_change) < 500) %>%  # Cap extreme ratios
  mutate(display = paste0("T", topic_num, ": ", str_trunc(label, 28)),
         display = reorder(display, pct_change))

if (nrow(era_change_filtered) > 0) {
  ggplot(era_change_filtered, aes(x = pct_change, y = display, fill = direction)) +
    geom_col(alpha = 0.85) +
    geom_vline(xintercept = 0, linewidth = 1) +
    scale_fill_manual(values = c("Grew in Magazine" = "#458B74",
                                  "Declined in Magazine" = "#CD661D",
                                  "Stable" = "#94a3b8")) +
    labs(title = "Relative Percentage Change in Topic Prevalence",
         subtitle = "How much did each topic grow or shrink relative to its Exponent-era baseline?",
         x = "Relative Change (%)", y = NULL, fill = NULL) +
    theme_minimal(base_size = 11) +
    theme(legend.position = "bottom", panel.grid.major.y = element_blank())
}
```

### Topic Change Over Time (Year-by-Year Gap)

```{r topic-gap-over-time, fig.width=14, fig.height=10}
# For years where BOTH publications have data, compute the prevalence gap
yearly_gap <- yearly_topics %>%
  select(year, corpus, topic_num, prevalence, label) %>%
  pivot_wider(names_from = corpus, values_from = prevalence) %>%
  filter(!is.na(Womans_Exponent), !is.na(Relief_Society_Magazine)) %>%
  mutate(gap = Relief_Society_Magazine - Womans_Exponent)

# If there's temporal overlap, show the gap over time
if (nrow(yearly_gap) > 0) {
  # Top 6 topics with largest variance in gap
  gap_var <- yearly_gap %>%
    group_by(topic_num, label) %>%
    summarize(gap_var = var(gap, na.rm = TRUE), .groups = "drop") %>%
    arrange(desc(gap_var)) %>%
    head(6)

  yearly_gap %>%
    filter(topic_num %in% gap_var$topic_num) %>%
    ggplot(aes(x = year, y = gap, fill = gap > 0)) +
    geom_col(alpha = 0.7, show.legend = FALSE) +
    geom_hline(yintercept = 0, linewidth = 0.8) +
    facet_wrap(~str_wrap(label, 25), ncol = 3, scales = "free_y") +
    scale_fill_manual(values = c("TRUE" = "#458B74", "FALSE" = "#CD661D")) +
    labs(title = "Year-by-Year Topic Prevalence Gap (RSM - WE)",
         subtitle = "Green = more prevalent in RSM that year | Orange = more prevalent in WE",
         x = "Year", y = "Prevalence Gap (RSM - WE)") +
    theme_minimal(base_size = 11) +
    theme(strip.text = element_text(face = "bold", size = 9)) +
    scale_y_continuous(labels = percent_format())
} else {
  cat("No overlapping years between publications — gap analysis requires temporal overlap.\n")
  cat("Showing era-to-era comparison instead (see absolute change chart above).\n")
}
```

---

## 26. Complementary Evolution Summary

```{r complementary-summary, fig.width=12, fig.height=8}
cat(rep("=", 70), "\n", sep = "")
cat("COMPLEMENTARY EVOLUTION SUMMARY\n")
cat(rep("=", 70), "\n\n", sep = "")

# Build a comprehensive topic classification
topic_class <- pub_means %>%
  left_join(corpus_effects %>% select(Topic, Significant, Difference_Pct, P_value),
            by = c("topic_num" = "Topic")) %>%
  mutate(
    evolution_type = case_when(
      !Significant ~ "Stable Core",
      category == "WE Signature" ~ "WE Distinctive",
      category == "RSM Signature" ~ "RSM Distinctive",
      TRUE ~ "Shifting Emphasis"
    ),
    evolution_type = factor(evolution_type,
                            levels = c("Stable Core", "Shifting Emphasis",
                                       "WE Distinctive", "RSM Distinctive"))
  )

cat("COMPLEMENTARY EVOLUTION CLASSIFICATION:\n\n")

cat("STABLE CORE — topics sustained across both publications:\n")
stable <- topic_class %>% filter(evolution_type == "Stable Core")
if (nrow(stable) > 0) {
  for (i in 1:nrow(stable)) {
    cat(sprintf("  T%d: %s (WE: %.1f%%, RSM: %.1f%%)\n",
                stable$topic_num[i], stable$label[i],
                stable$we_pct[i], stable$rsm_pct[i]))
  }
} else cat("  (none)\n")

cat("\nSHIFTING EMPHASIS — present in both but weighted differently:\n")
shifting <- topic_class %>% filter(evolution_type == "Shifting Emphasis")
if (nrow(shifting) > 0) {
  for (i in 1:nrow(shifting)) {
    cat(sprintf("  T%d: %s (WE: %.1f%%, RSM: %.1f%%, p=%.3f)\n",
                shifting$topic_num[i], shifting$label[i],
                shifting$we_pct[i], shifting$rsm_pct[i], shifting$P_value[i]))
  }
} else cat("  (none)\n")

cat("\nWE DISTINCTIVE — topics much more prevalent in the Exponent:\n")
we_dist <- topic_class %>% filter(evolution_type == "WE Distinctive")
if (nrow(we_dist) > 0) {
  for (i in 1:nrow(we_dist)) {
    cat(sprintf("  T%d: %s (WE: %.1f%% vs RSM: %.1f%%)\n",
                we_dist$topic_num[i], we_dist$label[i],
                we_dist$we_pct[i], we_dist$rsm_pct[i]))
  }
} else cat("  (none)\n")

cat("\nRSM DISTINCTIVE — topics much more prevalent in the Magazine:\n")
rsm_dist <- topic_class %>% filter(evolution_type == "RSM Distinctive")
if (nrow(rsm_dist) > 0) {
  for (i in 1:nrow(rsm_dist)) {
    cat(sprintf("  T%d: %s (RSM: %.1f%% vs WE: %.1f%%)\n",
                rsm_dist$topic_num[i], rsm_dist$label[i],
                rsm_dist$rsm_pct[i], rsm_dist$we_pct[i]))
  }
} else cat("  (none)\n")

# Visual summary
ggplot(topic_class, aes(x = we_pct, y = rsm_pct, color = evolution_type)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "grey70", linewidth = 1) +
  geom_point(size = 5, alpha = 0.8) +
  geom_text_repel(aes(label = paste0("T", topic_num, ": ", str_trunc(label, 25))),
                  size = 3, max.overlaps = 20, show.legend = FALSE) +
  scale_color_manual(values = c(
    "Stable Core" = "#6495ED",
    "Shifting Emphasis" = "#DAA520",
    "WE Distinctive" = "#CD661D",
    "RSM Distinctive" = "#458B74"
  )) +
  labs(title = "Complementary Evolution of Topics",
       subtitle = "Diagonal = equal prevalence | Distance from line = degree of difference",
       x = "Woman's Exponent (Mean %)", y = "Relief Society Magazine (Mean %)",
       color = "Evolution Type") +
  theme_minimal(base_size = 13) +
  theme(legend.position = "bottom",
        plot.title = element_text(face = "bold", size = 16)) +
  coord_fixed()
```

---

## 27. Export Results

```{r export-results}
cat("Exporting results to:", output_path, "\n\n")

# 1. Publication comparison table
write_csv(corpus_effects,
          file.path(output_path, paste0("publication_comparison_K", chosen_K, ".csv")))
cat("  publication_comparison.csv\n")

# 2. Significant differences
if (nrow(significant_topics) > 0) {
  write_csv(significant_topics,
            file.path(output_path, paste0("significant_differences_K", chosen_K, ".csv")))
  cat("  significant_differences.csv\n")
}

# 3. Topic summary with words
topic_props_mean <- colMeans(topic_props %>% select(starts_with("Topic")))
write_csv(tibble(
    topic_num = 1:chosen_K,
    label = str_remove(topic_labels, "^Topic \\d+: "),
    prevalence_pct = round(topic_props_mean * 100, 2),
    frex_words = apply(all_top_words$frex, 1, function(x) paste(x, collapse = ", ")),
    prob_words = apply(all_top_words$prob, 1, function(x) paste(x, collapse = ", "))
  ),
  file.path(output_path, paste0("topic_summary_K", chosen_K, ".csv")))
cat("  topic_summary.csv\n")

# 4. Full topic-article link
write_csv(topic_article_link %>% mutate(proportion_pct = round(proportion * 100, 2)),
          file.path(output_path, paste0("topic_article_full_link_K", chosen_K, ".csv")))
cat("  topic_article_full_link.csv\n")

# 5. Dominant topic per article
write_csv(dominant_topics,
          file.path(output_path, paste0("dominant_topic_per_article_K", chosen_K, ".csv")))
cat("  dominant_topic_per_article.csv\n")

# 6. Strong exemplars only
write_csv(dominant_topics %>% filter(strong_exemplar),
          file.path(output_path, paste0("strong_exemplars_K", chosen_K, ".csv")))
cat("  strong_exemplars.csv\n")

# 7. Top 25 exemplar articles per topic
write_csv(topic_article_link %>%
            group_by(topic_num, topic_label) %>%
            slice_max(proportion, n = 25) %>%
            ungroup() %>%
            mutate(proportion_pct = round(proportion * 100, 2)),
          file.path(output_path, paste0("topic_exemplar_articles_K", chosen_K, ".csv")))
cat("  topic_exemplar_articles.csv\n")

# 8. Topic classification (continuity analysis)
if (exists("topic_class")) {
  write_csv(topic_class %>% select(topic_num, label, category, evolution_type,
                                    we_pct, rsm_pct, Significant, Difference_Pct, P_value),
            file.path(output_path, paste0("topic_classification_K", chosen_K, ".csv")))
  cat("  topic_classification.csv\n")
}

cat("\nAll results exported.\n")
```

---

## 28. Summary Statistics

```{r summary-stats}
cat("\n", rep("=", 70), "\n", sep = "")
cat("COMPARISON SUMMARY\n")
cat(rep("=", 70), "\n\n", sep = "")

cat("Publications Compared:\n")
cat("  Woman's Exponent (", sum(meta$corpus == "Womans_Exponent"), " docs)\n", sep = "")
cat("  Relief Society Magazine (", sum(meta$corpus == "Relief_Society_Magazine"), " docs)\n\n", sep = "")

cat("Topic Analysis:\n")
cat("  Total topics:", chosen_K, "\n")
cat("  Significant differences:", sum(corpus_effects$Significant), "\n")
cat("    More in Woman's Exponent:", sum(corpus_effects$Direction == "More in Woman's Exponent"), "\n")
cat("    More in RS Magazine:", sum(corpus_effects$Direction == "More in Relief Society Magazine"), "\n")
cat("    No difference:", sum(corpus_effects$Direction == "No significant difference"), "\n\n")

cat("Largest differences:\n")
top_3 <- corpus_effects %>% head(3)
for (i in 1:nrow(top_3)) {
  cat(sprintf("  %s: %.2f%% (%s)\n", top_3$Label[i], top_3$Difference_Pct[i], top_3$Direction[i]))
}
```

---

## 29. Author-Topic Heatmap

```{r author-topic-heatmap, fig.width=12, fig.height=10}
cat(rep("=", 70), "\n", sep = "")
cat("AUTHOR-TOPIC ANALYSIS\n")
cat(rep("=", 70), "\n\n", sep = "")

# Build author-topic data from document-topic proportions
author_topic_data <- topic_props %>%
  filter(!is.na(Author), Author != "", nchar(Author) > 1) %>%
  mutate(Author = str_trim(Author))

if (nrow(author_topic_data) >= 10) {
  # Get top 25 most frequent authors
  top_authors <- author_topic_data %>%
    count(Author, sort = TRUE) %>%
    head(25) %>%
    pull(Author)

  # Calculate mean topic proportion per author
  author_matrix_data <- author_topic_data %>%
    filter(Author %in% top_authors) %>%
    select(Author, starts_with("Topic")) %>%
    group_by(Author) %>%
    summarize(across(starts_with("Topic"), mean), .groups = "drop")

  mat <- as.matrix(author_matrix_data %>% select(-Author))
  rownames(mat) <- author_matrix_data$Author
  colnames(mat) <- paste0("T", 1:chosen_K, ": ",
                           str_trunc(str_remove(topic_labels, "^Topic \\d+: "), 18))

  # Replace any NaN/Inf
  mat[!is.finite(mat)] <- 0

  pheatmap(mat,
    main = paste0("Author-Topic Affinity (Top ", length(top_authors), " Authors)"),
    color = colorRampPalette(c("white", "#D4E8D4", "#6E8B3D", "#2E4A1E"))(100),
    cluster_rows = TRUE, cluster_cols = FALSE,
    fontsize_row = 8, fontsize_col = 8, angle_col = 45, border_color = "grey90")
} else {
  cat("Skipping author-topic heatmap: not enough named authors in the combined corpus.\n")
  cat("Articles with author data:", nrow(author_topic_data), "\n")
}
```

---

## 30. Author-Topic by Publication

```{r author-topic-by-pub, fig.width=14, fig.height=8}
if (exists("author_topic_data") && nrow(author_topic_data) >= 10) {

  # Top 10 authors per publication
  top_by_pub <- author_topic_data %>%
    count(Author, corpus, sort = TRUE) %>%
    group_by(corpus) %>%
    slice_head(n = 10) %>%
    pull(Author) %>%
    unique()

  pub_author_data <- author_topic_data %>%
    filter(Author %in% top_by_pub) %>%
    select(Author, corpus, starts_with("Topic")) %>%
    pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "proportion") %>%
    mutate(topic_num = as.numeric(str_remove(topic, "Topic"))) %>%
    group_by(Author, corpus, topic_num) %>%
    summarize(mean_prop = mean(proportion), .groups = "drop") %>%
    mutate(
      topic_label = str_trunc(str_remove(topic_labels[topic_num], "^Topic \\d+: "), 20),
      publication = ifelse(corpus == "Relief_Society_Magazine",
                           "Relief Society Magazine", "Woman's Exponent")
    )

  # Top 3 topics per author
  top_topics_per_author <- pub_author_data %>%
    group_by(Author) %>%
    slice_max(mean_prop, n = 3) %>%
    ungroup()

  ggplot(top_topics_per_author,
         aes(x = reorder(Author, mean_prop), y = mean_prop,
             fill = topic_label)) +
    geom_col(position = "stack") +
    coord_flip() +
    facet_wrap(~publication, scales = "free_y") +
    scale_fill_brewer(palette = "Set3") +
    labs(title = "Top 3 Topics per Author (by Publication)",
         x = NULL, y = "Mean Topic Proportion", fill = "Topic") +
    theme_minimal(base_size = 11) +
    theme(legend.position = "bottom",
          strip.text = element_text(face = "bold", size = 12)) +
    scale_y_continuous(labels = percent_format())
}
```

---

## 31. Article Type Distribution

```{r article-type-dist, fig.width=12, fig.height=6}
type_data <- topic_props %>%
  filter(!is.na(Article_Type), Article_Type != "Unknown") %>%
  count(corpus, Article_Type, sort = TRUE) %>%
  mutate(publication = ifelse(corpus == "Relief_Society_Magazine",
                              "Relief Society Magazine", "Woman's Exponent"))

# Top 10 types per pub
top_types <- type_data %>%
  group_by(publication) %>%
  slice_max(n, n = 10) %>%
  pull(Article_Type) %>%
  unique()

type_data %>%
  filter(Article_Type %in% top_types) %>%
  ggplot(aes(x = reorder(Article_Type, n), y = n, fill = publication)) +
  geom_col(position = "dodge") +
  coord_flip() +
  scale_fill_manual(values = c("Woman's Exponent" = "#CD661D",
                               "Relief Society Magazine" = "#458B74")) +
  labs(title = "Article Type Distribution by Publication",
       x = NULL, y = "Count", fill = "Publication") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom")
```

---

## Session Info

```{r session-info}
sessionInfo()
```
