---
title: "STM Visualizations & Regression Analysis"
author: "Your Name"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: show
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 6)
```

# STM Visualizations & Regression Guide

This notebook demonstrates all major visualizations for STM topic modeling and explains how regression analysis helps you understand topic prevalence.

---

## Setup: Load Packages and Model

```{r load-packages}
library(stm)
library(tidyverse)
library(ggplot2)

# Set seed for reproducibility
set.seed(12345)

# Load your saved model (adjust filename as needed)
# stm_model <- readRDS("stm_model_K15.rds")
# stm_model_cov <- readRDS("stm_model_cov_K15.rds")  # If you have covariates
# docs <- readRDS("docs.rds")
# vocab <- readRDS("vocab.rds")
# meta <- readRDS("meta.rds")

# For this demo, we'll assume you have these objects loaded
```

**Note:** Make sure you've already run the main workflow and have:
- `stm_model` - your fitted STM model
- `stm_model_cov` - model with covariates (optional, for regression)
- `docs` - processed documents
- `vocab` - vocabulary
- `meta` - metadata

---

## Visualization 1: Topic Prevalence

**What it shows:** Which topics are most common across your corpus

```{r topic-prevalence}
# Create prevalence plot
plot(stm_model, 
     type = "summary", 
     n = 10,  # Show top 10 topics
     main = "Topic Prevalence - Top 10 Topics",
     xlim = c(0, 0.15))
```

### Interpretation:

- **X-axis:** Expected topic proportion (0 = 0%, 0.15 = 15%)
- **Y-axis:** Topics, labeled by their most probable words
- **Longer bars:** More prevalent topics

### What to look for:

- Is one topic dominating (>20%)? Might be too broad
- Are topics evenly distributed? Suggests diverse corpus
- Very small topics (<2%)? Might be noise or very specific themes

---

## Visualization 2: Topic Labels with Custom Names

After examining the top words, create meaningful labels:

```{r label-topics}
# View top words for each topic
labelTopics(stm_model, n = 7)

# Create your own topic labels (EDIT THESE based on your results)
topic_labels <- data.frame(
  topic_num = 1:15,
  label = c(
    "Economic Indicators",
    "Defense & Security", 
    "Climate Change",
    "Criminal Justice",
    "Healthcare Policy",
    "International Trade",
    "Elections & Voting",
    "Housing & Real Estate",
    "Education Reform",
    "Social Welfare",
    "Social Media",
    "Technology & AI",
    "Transportation",
    "Immigration",
    "Energy Policy"
  )
)

# Display labels with top words
print(topic_labels)
```

---

## Visualization 3: Topic Correlation Network

**What it shows:** Which topics frequently co-occur in the same documents

```{r topic-correlation, fig.width=10, fig.height=10}
# Calculate topic correlations
mod.out.corr <- topicCorr(stm_model)

# Plot correlation network
plot(mod.out.corr,
     main = "Topic Correlation Network")
```

### Interpretation:

- **Lines between topics:** These topics appear together in documents
- **No lines:** Topics are independent
- **Thick lines:** Stronger correlation
- **Clusters:** Groups of related topics

### What to look for:

- **Expected correlations:** Elections connected to Healthcare, Economy (policy issues)
- **Unexpected correlations:** Surprising relationships worth investigating
- **Isolated topics:** Topics that appear independently

---

## Visualization 4: Word Clouds for Individual Topics

**What it shows:** Most important words for a specific topic

```{r wordcloud-topic1, fig.width=8, fig.height=6}
# Create word cloud for Topic 1
cloud(stm_model, 
      topic = 1,
      scale = c(4, 0.5),
      max.words = 50,
      colors = brewer.pal(8, "Dark2"))

title(main = "Topic 1: Economic Indicators", 
      cex.main = 1.5)
```

```{r wordcloud-topic3, fig.width=8, fig.height=6}
# Create word cloud for Topic 3
cloud(stm_model, 
      topic = 3,
      scale = c(4, 0.5),
      max.words = 50,
      colors = brewer.pal(8, "Dark2"))

title(main = "Topic 3: Climate Change", 
      cex.main = 1.5)
```

### Create clouds for all topics:

```{r all-wordclouds, fig.width=8, fig.height=6, eval=FALSE}
# Loop through all topics (set eval=TRUE to run)
for (i in 1:15) {
  cloud(stm_model, 
        topic = i,
        scale = c(4, 0.5),
        max.words = 50,
        colors = brewer.pal(8, "Dark2"))
  
  title(main = paste("Topic", i, ":", topic_labels$label[i]), 
        cex.main = 1.5)
}
```

---

## Visualization 5: Topic Quality - Semantic Coherence vs Exclusivity

**What it shows:** Quality metrics for each topic

```{r topic-quality, fig.width=10, fig.height=8}
# Calculate and plot topic quality
topicQuality(stm_model, documents = docs)

# Add custom labels (optional)
text(x = topicQuality(stm_model, documents = docs)$semcoh,
     y = topicQuality(stm_model, documents = docs)$exclusivity,
     labels = 1:15,
     pos = 3, cex = 0.8)
```

### Interpretation:

- **X-axis:** Semantic Coherence (how often top words co-occur)
- **Y-axis:** Exclusivity (how unique words are to this topic)
- **Top-right quadrant:** Best topics (coherent AND exclusive)
- **Bottom-left quadrant:** Problematic topics

### What to do:

- **If many topics in bottom-left:** Try different K
- **Outliers:** Investigate those specific topics
- **Trade-off is normal:** Can't maximize both perfectly

---

## Visualization 6: Comparing Topics (Perspectives)

**What it shows:** How two topics differ in their vocabularies

```{r perspectives-plot, fig.width=12, fig.height=6}
# Compare two topics (e.g., Climate vs Elections)
plot(stm_model, 
     type = "perspectives", 
     topics = c(3, 7),  # Climate (T3) vs Elections (T7)
     main = "Comparing Topics: Climate Change vs Elections & Voting")
```

```{r perspectives-plot2, fig.width=12, fig.height=6}
# Compare another pair (e.g., Healthcare vs Technology)
plot(stm_model, 
     type = "perspectives", 
     topics = c(5, 12),  # Healthcare (T5) vs Technology (T12)
     main = "Comparing Topics: Healthcare Policy vs Technology & AI")
```

### Interpretation:

- **Left side:** Words more associated with first topic
- **Right side:** Words more associated with second topic
- **Large gaps:** Topics are very distinct (good!)
- **Words in middle:** Shared vocabulary

---

## Visualization 7: Topic Proportions in Example Documents

**What it shows:** How topics are distributed in specific documents

```{r document-topics}
# Get topic proportions for all documents
doc_topics <- make.dt(stm_model, meta = meta)

# View first few documents
head(doc_topics, 10)

# Visualize topic distribution for a single document
doc_num <- 1  # Change this to examine different documents

doc_topic_dist <- doc_topics %>%
  filter(docnum == doc_num) %>%
  select(starts_with("Topic")) %>%
  pivot_longer(everything(), names_to = "Topic", values_to = "Proportion") %>%
  mutate(Topic_Num = parse_number(Topic)) %>%
  left_join(topic_labels, by = c("Topic_Num" = "topic_num"))

ggplot(doc_topic_dist, aes(x = reorder(label, -Proportion), y = Proportion)) +
  geom_col(fill = "#667eea") +
  coord_flip() +
  labs(title = paste("Topic Distribution - Document", doc_num),
       x = "Topic",
       y = "Proportion") +
  theme_minimal() +
  theme(text = element_text(size = 12))
```

---

# REGRESSION ANALYSIS IN STM

## What is Regression in STM?

**Regression analysis** in STM helps you understand **what predicts topic prevalence**.

Instead of just knowing that "12.3% of the corpus is about Elections," regression lets you ask:

- Do **Elections topics** increase over time?
- Do certain **authors** write more about **Healthcare**?
- Are **Climate topics** more common in certain **sources**?

---

## When to Use Regression in STM

Use regression when you have **metadata** (covariates) and want to know:

✅ **Temporal trends:** How topics change over time  
✅ **Author differences:** Do different authors emphasize different topics?  
✅ **Source patterns:** Do topics vary by publication/source?  
✅ **Geographic patterns:** Do topics differ by location?  
✅ **Any categorical or continuous variable**

---

## Step 1: Fit STM Model with Covariates

**IMPORTANT:** You must fit a model WITH covariates to do regression

```{r fit-covariate-model, eval=FALSE}
# Example: Model with year and source as covariates
stm_model_cov <- stm(
  documents = docs,
  vocab = vocab,
  K = 15,
  prevalence = ~ year + source,  # YOUR COVARIATES HERE
  data = meta,
  max.em.its = 75,
  init.type = "Spectral",
  seed = 12345,
  verbose = TRUE
)

# Save the model
saveRDS(stm_model_cov, "stm_model_cov_K15.rds")
```

---

## Step 2: Estimate Effects

Use `estimateEffect()` to run the regression:

```{r estimate-effects, eval=FALSE}
# Estimate how covariates affect topic prevalence
# Formula: which topics ~ which covariates

prep <- estimateEffect(
  formula = 1:15 ~ year + source,  # All topics ~ year and source
  stmobj = stm_model_cov,
  metadata = meta,
  uncertainty = "Global"
)

# Save results
saveRDS(prep, "effect_estimates.rds")
```

### Breaking down the formula:

- `1:15` = Topics 1 through 15 (all topics)
- `~ year + source` = Predicted by year and source
- You can also do specific topics: `c(1, 3, 7) ~ year`

---

## Step 3: View Regression Tables

**THIS IS WHERE REGRESSION TABLES COME IN!**

```{r regression-table, eval=FALSE}
# View regression results for Topic 3 (Climate Change)
summary(prep, topics = 3)
```

### What the regression table shows:

```
Topic 3: Climate Change

            Estimate  Std.Error  t value  Pr(>|t|)    
(Intercept)  -0.0234   0.0045    -5.200   < 0.001  ***
year          0.0012   0.0003     4.000   < 0.001  ***
sourceNYT     0.0156   0.0067     2.328    0.020   *
sourceWSJ    -0.0089   0.0071    -1.254    0.210    
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
```

### How to read this table:

**Intercept (-0.0234):**
- Baseline topic proportion when all covariates = 0
- Not usually interesting

**year (0.0012):**
- **Positive coefficient** = Topic proportion INCREASES each year
- **0.0012** = Climate topic increases by 0.12 percentage points per year
- **p < 0.001** = Highly significant (marked ***)
- **Interpretation:** "Climate Change discussions have significantly increased over time"

**sourceNYT (0.0156):**
- **Positive coefficient** = NYT covers Climate more than baseline (reference category)
- **0.0156** = NYT has 1.56 percentage points MORE Climate coverage
- **p = 0.020** = Significant (marked *)
- **Interpretation:** "New York Times covers Climate Change more than other sources"

**sourceWSJ (-0.0089):**
- **Negative coefficient** = WSJ covers Climate less than baseline
- **p = 0.210** = NOT significant (no stars)
- **Interpretation:** "Wall Street Journal coverage of Climate is not significantly different"

---

## Step 4: Visualize Regression Results

### Continuous Covariates (like year):

```{r plot-continuous, eval=FALSE, fig.width=10, fig.height=6}
# Plot how topics change over time
plot(prep, 
     covariate = "year",
     topics = c(3, 7, 12),  # Climate, Elections, Technology
     model = stm_model_cov,
     method = "continuous",
     main = "Topic Trends Over Time",
     xlab = "Year",
     ylab = "Expected Topic Proportion")

# Add legend
legend("topleft", 
       legend = c("Topic 3: Climate", "Topic 7: Elections", "Topic 12: Technology"),
       col = 1:3, lty = 1, lwd = 2)
```

### Categorical Covariates (like source):

```{r plot-categorical, eval=FALSE, fig.width=10, fig.height=6}
# Plot how topics vary by source
plot(prep,
     covariate = "source",
     topics = c(3, 5, 7),  # Climate, Healthcare, Elections
     model = stm_model_cov,
     method = "pointestimate",
     main = "Topic Prevalence by Source",
     xlab = "Source",
     ylab = "Expected Topic Proportion")
```

---

## Complete Regression Workflow Example

```{r complete-regression-example, eval=FALSE}
# ============================================================================
# COMPLETE REGRESSION ANALYSIS WORKFLOW
# ============================================================================

# 1. FIT MODEL WITH COVARIATES
stm_model_cov <- stm(
  documents = docs,
  vocab = vocab,
  K = 15,
  prevalence = ~ year + author + source,  # Multiple covariates
  data = meta,
  max.em.its = 75,
  init.type = "Spectral",
  seed = 12345
)

# 2. ESTIMATE EFFECTS
prep <- estimateEffect(
  formula = 1:15 ~ year + author + source,
  stmobj = stm_model_cov,
  metadata = meta,
  uncertainty = "Global"
)

# 3. VIEW REGRESSION TABLES FOR EACH TOPIC
for (i in 1:15) {
  cat("\n\n========================================\n")
  cat("TOPIC", i, ":", topic_labels$label[i], "\n")
  cat("========================================\n")
  print(summary(prep, topics = i))
}

# 4. IDENTIFY SIGNIFICANT EFFECTS
# Which topics are significantly affected by year?
for (i in 1:15) {
  sum_result <- summary(prep, topics = i)
  year_pvalue <- sum_result$tables[[1]]["year", "Pr(>|t|)"]
  
  if (year_pvalue < 0.05) {
    year_coef <- sum_result$tables[[1]]["year", "Estimate"]
    direction <- ifelse(year_coef > 0, "INCREASING", "DECREASING")
    
    cat(sprintf("Topic %d (%s): %s over time (p = %.4f)\n", 
                i, topic_labels$label[i], direction, year_pvalue))
  }
}

# 5. VISUALIZE KEY FINDINGS
# Plot topics with significant time trends
significant_topics <- c(3, 7, 12)  # Based on your analysis

plot(prep,
     covariate = "year",
     topics = significant_topics,
     model = stm_model_cov,
     method = "continuous",
     main = "Topics with Significant Time Trends",
     xlab = "Year",
     ylab = "Expected Topic Proportion")
```

---

## Common Regression Questions & Answers

### Q1: "Do I always need to do regression?"

**No!** Regression is optional. Use it when:
- You have meaningful metadata (year, author, source, etc.)
- You want to test specific hypotheses
- You want to understand what predicts topics

Skip it if:
- You just want to explore topics
- You don't have good metadata
- Your goal is description, not prediction

---

### Q2: "What's the difference between the regular model and covariate model?"

**Regular STM model (`stm()` without covariates):**
- Finds topics and their prevalence
- Shows which topics exist and how common they are
- Can't test hypotheses about what predicts topics

**Covariate STM model (`stm()` with `prevalence = ~...`):**
- Finds topics AND models what affects their prevalence
- Tests hypotheses: "Does Climate increase over time?"
- Produces regression tables

---

### Q3: "What covariates should I include?"

Include covariates that might meaningfully predict topics:

**Good covariates:**
- **Time** (year, date) - for trends
- **Author/Source** - different perspectives
- **Location** - geographic patterns
- **Document type** - speeches vs articles
- **Political party** - partisan differences

**Bad covariates:**
- **Document ID** - too many categories
- **Document length** - not substantively meaningful
- **Random noise** - no theoretical reason

---

### Q4: "How do I interpret interaction effects?"

```{r interaction-example, eval=FALSE}
# Model with interaction
stm_model_int <- stm(
  documents = docs,
  vocab = vocab,
  K = 15,
  prevalence = ~ year * source,  # Interaction: year × source
  data = meta
)

prep_int <- estimateEffect(
  1:15 ~ year * source,
  stmobj = stm_model_int,
  metadata = meta
)

# Interpretation of year:sourceNYT coefficient:
# "The effect of year on topic prevalence DIFFERS between NYT and other sources"
# Example: Climate might increase over time in NYT but not in WSJ
```

---

## Regression Output Table Interpretation Guide

Here's how to read a complete regression table:

```
Topic: Climate Change

                    Estimate  Std.Error  t value  Pr(>|t|)    
(Intercept)         -0.0234    0.0045   -5.200   < 0.001  ***
year                 0.0012    0.0003    4.000   < 0.001  ***
sourceNYT            0.0156    0.0067    2.328    0.020   *
sourceWSJ           -0.0089    0.0071   -1.254    0.210    
authorSmith          0.0234    0.0089    2.629    0.009   **
authorJones         -0.0145    0.0092   -1.576    0.115    
```

| Column | Meaning |
|--------|---------|
| **Estimate** | Change in topic proportion for 1-unit increase in predictor |
| **Std.Error** | Uncertainty in the estimate |
| **t value** | Test statistic (Estimate/Std.Error) |
| **Pr(>\|t\|)** | P-value - probability of seeing this if no real effect |
| **Stars** | *** p<0.001, ** p<0.01, * p<0.05 |

**In plain English:**

"Climate Change topic increases by 0.12 percentage points each year (p<0.001). 
The New York Times covers Climate 1.56 percentage points more than other sources (p=0.02).
Author Smith writes about Climate 2.34 percentage points more than other authors (p=0.009)."

---

## Creating Publication-Ready Regression Tables

```{r publication-table, eval=FALSE}
# Extract regression results for multiple topics
library(broom)

# Function to extract tidy results
extract_effects <- function(prep_obj, topic_num) {
  summary(prep_obj, topics = topic_num)$tables[[1]] %>%
    as.data.frame() %>%
    rownames_to_column("Variable") %>%
    mutate(Topic = topic_num)
}

# Combine results for topics of interest
regression_results <- bind_rows(
  extract_effects(prep, 3),   # Climate
  extract_effects(prep, 7),   # Elections
  extract_effects(prep, 12)   # Technology
)

# Export to CSV
write_csv(regression_results, "regression_results.csv")

# Create formatted table
library(kableExtra)

regression_results %>%
  filter(Variable == "year") %>%  # Focus on time trends
  select(Topic, Estimate, `Pr(>|t|)`) %>%
  left_join(topic_labels, by = c("Topic" = "topic_num")) %>%
  select(label, Estimate, `Pr(>|t|)`) %>%
  kable(col.names = c("Topic", "Yearly Change", "P-value"),
        digits = 4,
        caption = "How Topics Change Over Time") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

---

## Summary: When and How to Use Regression

```{r summary-table, echo=FALSE}
summary_df <- data.frame(
  Question = c(
    "Do topics change over time?",
    "Do sources emphasize different topics?",
    "Do authors have topic specialties?",
    "Are topics seasonal?",
    "Do topics vary geographically?"
  ),
  Covariate = c("year or date", "source", "author", "month", "location"),
  Type = c("Continuous", "Categorical", "Categorical", "Categorical", "Categorical"),
  Example_Finding = c(
    "Climate increases 0.12% per year",
    "NYT covers healthcare 1.5% more",
    "Author Smith focuses on economics",
    "Education peaks in September",
    "Immigration higher in border states"
  )
)

knitr::kable(summary_df, 
             caption = "Common Research Questions and Regression Approaches")
```

---

## Key Takeaways

### Visualizations:
1. **Always start with Topic Prevalence** - understand what's in your corpus
2. **Check Topic Quality** - validate your model
3. **Use Word Clouds** - communicate findings visually
4. **Examine Correlations** - understand relationships

### Regression:
1. **Regression is OPTIONAL** - only use if you have metadata and research questions
2. **Fit with covariates** - `prevalence = ~ var1 + var2`
3. **Estimate effects** - `estimateEffect()`
4. **Interpret tables** - coefficients show change in topic proportion
5. **Visualize trends** - plots are clearer than tables

### Research Workflow:
**Exploratory:** Fit model → Visualize → Interpret topics  
**Hypothesis-Testing:** Fit covariate model → Regression → Test predictions

---

## Session Info

```{r session-info}
sessionInfo()
```
