---
title: "STM Topic Modeling - Complete Workflow"
author: "Your Name"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: show
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# STM Topic Modeling Workflow

This notebook walks through the complete workflow for topic modeling using the STM package in R, from raw text files to interpretable topics.

---

## 1. Setup: Install and Load Packages

```{r install-packages, eval=FALSE}
# Run this once to install packages (set eval=TRUE if needed)
install.packages("stm")
install.packages("tidyverse")
install.packages("tidytext")
install.packages("quanteda")
```

```{r load-packages}
# Load required libraries
library(stm)
library(tidyverse)
library(tidytext)
library(quanteda)

# Set seed for reproducibility
set.seed(12345)
```

---

## 2. Import Raw Text Files

```{r import-files}
library(tidyverse)
library(stm)

# Set seed for reproducibility
set.seed(12345)

# ============================================================================
# STEP 1: SET YOUR FOLDER PATH
# ============================================================================

# EDIT THIS PATH to point to your input folder
folder_path <- "C:/Users/birch/OneDrive - George Mason University - O365 Production/Dissertation/textanalysis/Topicmodel/input"

# ============================================================================
# STEP 2: LIST ALL FILES RECURSIVELY
# ============================================================================

# Get ALL files first
all_files <- list.files(
  path = folder_path,
  full.names = TRUE,
  recursive = TRUE
)

# Filter to only .txt files (case-insensitive)
file_paths <- all_files[grepl("\\.txt$", all_files, ignore.case = TRUE)]

cat("=" , rep("=", 60), "\n", sep = "")
cat("FILE IMPORT\n")
cat("=" , rep("=", 60), "\n\n", sep = "")

cat("Total .txt files found:", length(file_paths), "\n\n")

# Check if we found any files
if (length(file_paths) == 0) {
  cat("ERROR: No .txt files found!\n")
  cat("Total files of any type:", length(all_files), "\n")
  
  if (length(all_files) > 0) {
    cat("\nFile extensions found:\n")
    print(table(tools::file_ext(all_files)))
    cat("\nFirst 10 files:\n")
    print(basename(all_files)[1:10])
  }
  
  stop("No .txt files found. Please check your folder path.")
}

# Show sample of files found
cat("First 10 filenames found:\n")
print(basename(file_paths)[1:10])
```

---

## 3. Create Sample for Testing (Optional)

```{r create-sample}
# ============================================================================
# FOR TESTING: Use smaller sample
# ============================================================================

# OPTION 1: Use a sample for faster testing (RECOMMENDED for first run)
sample_size <- min(300, length(file_paths))  # Use 300 or all if fewer
cat("\nUsing", sample_size, "of", length(file_paths), "files for testing\n")
set.seed(123)
sampled_paths <- sample(file_paths, size = sample_size)

# OPTION 2: Use ALL files (comment out above, uncomment below)
# sampled_paths <- file_paths
# cat("\nUsing ALL", length(file_paths), "files\n")
```

---

## 4. Read Files and Extract Metadata

```{r read-files}
# ============================================================================
# READ ALL FILES INTO DATA FRAME
# ============================================================================

cat("\nReading files...\n")

raw_texts <- tibble(
  filepath = sampled_paths,
  filename = basename(sampled_paths),
  text = map_chr(sampled_paths, ~read_file(.x))
)

cat("Successfully read", nrow(raw_texts), "files\n")

# ============================================================================
# EXTRACT METADATA FROM FILENAMES AND PATHS
# ============================================================================

# Your filename format: April_Vol1_00_FRONT_MATTER.txt
raw_texts <- raw_texts %>%
  mutate(
    # Extract month from filename
    month = str_extract(filename, "^[A-Za-z]+"),
    
    # Extract volume (e.g., Vol1, Vol6)
    volume = str_extract(filename, "Vol\\d+"),
    
    # Extract section number (e.g., 00, 01, 02)
    section_num = str_extract(filename, "(?<=Vol\\d_)\\d{2}"),
    
    # Extract section name (everything after section number before .txt)
    section_name = str_remove(filename, "^[A-Za-z]+_Vol\\d+_\\d{2}_"),
    section_name = str_remove(section_name, "\\.txt$"),
    
    # Extract year from folder path
    year = as.numeric(str_extract(filepath, "\\d{4}")),
    
    # Create unique document ID
    doc_id = row_number(),
    
    # Calculate word count
    word_count = str_count(text, "\\S+")
  )

# ============================================================================
# DISPLAY RESULTS
# ============================================================================

cat("\n" , rep("=", 60), "\n", sep = "")
cat("DATA SUMMARY\n")
cat("=" , rep("=", 60), "\n\n", sep = "")

cat("Total documents loaded:", nrow(raw_texts), "\n")
cat("Volumes found:", paste(unique(na.omit(raw_texts$volume)), collapse = ", "), "\n")
cat("Months found:", paste(unique(na.omit(raw_texts$month)), collapse = ", "), "\n")
cat("Years found:", paste(unique(na.omit(raw_texts$year)), collapse = ", "), "\n")

cat("\nWord count statistics:\n")
cat("  Minimum:", min(raw_texts$word_count), "words\n")
cat("  Average:", round(mean(raw_texts$word_count)), "words\n")
cat("  Maximum:", max(raw_texts$word_count), "words\n")

cat("\nSample of loaded data:\n")
print(head(raw_texts %>% select(filename, month, volume, year, word_count), 10))

cat("\n" , rep("=", 60), "\n\n", sep = "")
```

---

## 5. Text Preprocessing

```{r preprocess-text}
# ============================================================================
# TEXT PREPROCESSING
# ============================================================================

cat("Preprocessing text...\n\n")

processed_texts <- raw_texts %>%
  mutate(
    # Convert to lowercase
    text_clean = str_to_lower(text),
    
    # Remove URLs
    text_clean = str_remove_all(text_clean, "http\\S+"),
    
    # Remove email addresses
    text_clean = str_remove_all(text_clean, "\\S+@\\S+"),
    
    # Remove extra whitespace
    text_clean = str_squish(text_clean)
  )

# Filter out very short documents (optional)
cat("Documents before filtering:", nrow(processed_texts), "\n")

processed_texts <- processed_texts %>%
  filter(word_count >= 50)  # Keep documents with at least 50 words

cat("Documents after filtering:", nrow(processed_texts), "\n")
cat("Removed:", nrow(raw_texts) - nrow(processed_texts), "short documents\n\n")

# Check distribution of word counts
cat("Word count distribution after filtering:\n")
print(summary(processed_texts$word_count))
```

---

## 6. Prepare Data for STM

```{r prepare-stm-data}
# ============================================================================
# DIAGNOSTIC: Check what's in your text files
# ============================================================================

cat("DIAGNOSTIC CHECK\n")
cat("=================\n\n")

# Check first document
cat("First document filename:", raw_texts$filename[1], "\n")
cat("First document length:", nchar(raw_texts$text[1]), "characters\n")
cat("First document word count:", raw_texts$word_count[1], "words\n\n")

cat("First 500 characters of first document:\n")
cat(substr(raw_texts$text[1], 1, 500), "\n\n")

# Check text after cleaning
cat("After basic cleaning:\n")
test_clean <- str_to_lower(raw_texts$text[1])
test_clean <- str_remove_all(test_clean, "http\\S+")
test_clean <- str_remove_all(test_clean, "\\S+@\\S+")
test_clean <- str_squish(test_clean)

cat("First 500 characters after cleaning:\n")
cat(substr(test_clean, 1, 500), "\n\n")

# Try manual tokenization to see what words are present
words <- str_split(test_clean, "\\s+")[[1]]
cat("Total words after basic cleaning:", length(words), "\n")
cat("First 50 words:\n")
cat(paste(words[1:50], collapse = ", "), "\n\n")

# Check stopwords removal
library(tm)
stopwords_en <- stopwords("english")
words_no_stop <- words[!words %in% stopwords_en]
cat("Words after stopword removal:", length(words_no_stop), "\n")
cat("First 30 words (no stopwords):\n")
cat(paste(words_no_stop[1:30], collapse = ", "), "\n")
```

---

## 7. Determine Optimal Number of Topics (K)

**This is where you set different numbers of topics to test!**

```{r search-k, cache=TRUE}
# ============================================================================
# SETTING DIFFERENT NUMBERS OF TOPICS (K)
# ============================================================================
# 
# K is the number of topics you want the model to find.
# There's no "correct" K - it depends on your data and goals.
#
# HOW TO SET K:
# 1. For initial exploration, test a range: c(5, 10, 15, 20, 25, 30)
# 2. For smaller corpora (<500 docs), try: c(5, 10, 15, 20)
# 3. For larger corpora (>1000 docs), try: c(10, 20, 30, 40, 50)
#
# The searchK() function tests multiple K values and helps you choose
# ============================================================================

# Define K values to test
# ADJUST THIS BASED ON YOUR DATA SIZE
K_values <- c(5, 10, 15, 20, 25)  # Testing 5 different K values

cat("=" , rep("=", 60), "\n", sep = "")
cat("SEARCHING FOR OPTIMAL K\n")
cat("=" , rep("=", 60), "\n\n", sep = "")

cat("Testing K values:", paste(K_values, collapse = ", "), "\n")
cat("This may take several minutes...\n\n")

# Search over different K values
K_search <- searchK(
  documents = docs,
  vocab = vocab,
  K = K_values,
  data = meta,
  init.type = "Spectral",
  verbose = TRUE
)

# Save results
saveRDS(K_search, "K_search_results.rds")
cat("\nSearch results saved to 'K_search_results.rds'\n")
```

### Visualize K Search Results

```{r plot-k-search, fig.width=10, fig.height=8}
# Plot diagnostic measures
plot(K_search)
```

**What to look for:**

- **Higher Semantic Coherence** = better (topics make more sense)
- **Higher Held-Out Likelihood** = better (model fits data well)
- **Lower Residuals** = better (model explains data well)
- **Exclusivity vs Coherence**: there's often a trade-off
  - High exclusivity = topics are distinct from each other
  - High coherence = words within topics are related

### Extract Search Results as Data Frame

```{r k-search-table}
# Create a summary table
k_results <- K_search$results %>%
  select(K, exclus, semcoh, heldout, residual)

knitr::kable(k_results, 
             digits = 3,
             col.names = c("K", "Exclusivity", "Semantic Coherence", 
                          "Held-Out Likelihood", "Residuals"),
             caption = "Model Diagnostics for Different K Values")
```

**How to choose K:**

- Look for the "elbow" where adding more topics doesn't help much
- Balance between coherence and exclusivity
- Consider interpretability - can you meaningfully label all topics?
- Try 2-3 promising K values and compare the actual topics

---

## 8. Fit the STM Model

```{r fit-model, cache=TRUE}
# ============================================================================
# CHOOSE YOUR K VALUE
# Based on the searchK results above, select the optimal K
# ============================================================================

# CHANGE THIS to your chosen K value
chosen_K <- 15

cat("=" , rep("=", 60), "\n", sep = "")
cat("FITTING STM MODEL\n")
cat("=" , rep("=", 60), "\n\n", sep = "")

cat("Fitting STM model with K =", chosen_K, "topics\n\n")

# Fit the model
stm_model <- stm(
  documents = docs,
  vocab = vocab,
  K = chosen_K,
  data = meta,
  max.em.its = 75,      # Maximum iterations
  init.type = "Spectral",
  seed = 12345,          # For reproducibility
  verbose = TRUE
)

# Save the model
saveRDS(stm_model, paste0("stm_model_K", chosen_K, ".rds"))
cat("\nModel saved to 'stm_model_K", chosen_K, ".rds'\n")
```

### Optional: Model with Covariates

```{r fit-model-covariates, eval=FALSE}
# If you have metadata like year, month, volume, etc., you can include it
# This shows how topics vary by your metadata variables

stm_model_cov <- stm(
  documents = docs,
  vocab = vocab,
  K = chosen_K,
  prevalence = ~ year + volume,  # ADJUST to match your metadata
  data = meta,
  max.em.its = 75,
  init.type = "Spectral",
  seed = 12345,
  verbose = TRUE
)

saveRDS(stm_model_cov, paste0("stm_model_cov_K", chosen_K, ".rds"))
```

---

## 9. Examine and Interpret Topics

```{r examine-topics}
# View top words for each topic
cat("=" , rep("=", 60), "\n", sep = "")
cat("TOP WORDS FOR EACH TOPIC\n")
cat("=" , rep("=", 60), "\n\n", sep = "")

labelTopics(stm_model, n = 10)
```

### Create Topic Labels

```{r create-labels}
# After viewing the top words, create meaningful labels
# EDIT THESE based on what you see in the top words

topic_labels <- c(
  "Topic 1: [Your Label]",
  "Topic 2: [Your Label]",
  "Topic 3: [Your Label]",
  "Topic 4: [Your Label]",
  "Topic 5: [Your Label]",
  "Topic 6: [Your Label]",
  "Topic 7: [Your Label]",
  "Topic 8: [Your Label]",
  "Topic 9: [Your Label]",
  "Topic 10: [Your Label]",
  "Topic 11: [Your Label]",
  "Topic 12: [Your Label]",
  "Topic 13: [Your Label]",
  "Topic 14: [Your Label]",
  "Topic 15: [Your Label]"
)

# Print labels with top words
cat("\n\nTOPIC LABELS WITH TOP WORDS:\n")
cat(rep("=", 60), "\n\n", sep = "")

for (i in 1:chosen_K) {
  cat(topic_labels[i], "\n")
  cat("  Top words:", paste(labelTopics(stm_model, topics = i, n = 7)$prob[1,], 
                          collapse = ", "), "\n\n")
}
```

### Find Example Documents

```{r find-examples}
# Find exemplar documents for Topic 1
# Change the topic number to explore different topics
topic_to_examine <- 1

cat("=" , rep("=", 60), "\n", sep = "")
cat("EXAMPLE DOCUMENTS FOR", topic_labels[topic_to_examine], "\n")
cat("=" , rep("=", 60), "\n\n", sep = "")

thoughts <- findThoughts(
  model = stm_model,
  texts = processed_texts$text_clean,
  topics = topic_to_examine,
  n = 3
)

for (i in 1:3) {
  cat("Example", i, ":\n")
  cat(substr(thoughts$docs[[1]][i], 1, 300), "...\n\n")
}
```

---

## 10. Visualize Results

### Topic Prevalence

```{r plot-prevalence, fig.width=10, fig.height=6}
# Which topics are most common?
plot(stm_model, 
     type = "summary", 
     n = 10,
     main = "Topic Prevalence - Top 10 Topics",
     xlim = c(0, 0.3))
```

### Topic Correlation Network

```{r plot-correlation, fig.width=10, fig.height=8}
# How do topics relate to each other?
mod.out.corr <- topicCorr(stm_model)
plot(mod.out.corr, 
     main = "Topic Correlation Network")
```

### Word Clouds for Specific Topics

```{r wordcloud, fig.width=8, fig.height=6}
# Create word cloud for a specific topic
cloud(stm_model, 
      topic = 1,  # Change this to view different topics
      scale = c(3, 0.5),
      main = topic_labels[1])
```

### Create Word Clouds for All Topics

```{r wordcloud-all, fig.width=8, fig.height=6, eval=FALSE}
# Set eval=TRUE to generate word clouds for all topics
for (i in 1:chosen_K) {
  cloud(stm_model, 
        topic = i,
        scale = c(3, 0.5),
        main = topic_labels[i])
}
```

### Topic Quality

```{r topic-quality, fig.width=8, fig.height=6}
# Evaluate semantic coherence vs exclusivity
topicQuality(stm_model, documents = docs)
```

### Compare Two Topics

```{r compare-topics, fig.width=8, fig.height=6}
# Compare words between two topics
plot(stm_model, 
     type = "perspectives", 
     topics = c(1, 5),  # Change these to compare different topics
     main = paste("Comparing", topic_labels[1], "vs", topic_labels[5]))
```

---

## 11. Analyze Topic Prevalence with Covariates (Optional)

This section only works if you fit a model with covariates above.

```{r analyze-covariates, eval=FALSE}
# Estimate effect of covariates on topic prevalence
prep <- estimateEffect(
  formula = 1:chosen_K ~ year + volume,  # ADJUST to match your covariates
  stmobj = stm_model_cov,
  metadata = meta,
  uncertainty = "Global"
)

# Plot effect of year on specific topics
plot(prep, 
     covariate = "year",
     topics = c(1, 5, 10),  # Choose topics to plot
     model = stm_model_cov,
     method = "continuous",
     main = "Topic Prevalence Over Time")

# Summary of effects for Topic 1
summary(prep, topics = 1)
```

---

## 12. Extract and Export Results

### Document-Topic Proportions

```{r export-doc-topics}
# Get topic proportions for each document
doc_topics <- make.dt(stm_model, meta = meta)

# View first few rows
head(doc_topics)

# Export to CSV
write_csv(doc_topics, paste0("document_topic_proportions_K", chosen_K, ".csv"))
cat("Exported to 'document_topic_proportions_K", chosen_K, ".csv'\n")
```

### Top Words per Topic

```{r export-top-words}
# Extract top 20 words per topic
top_words <- labelTopics(stm_model, n = 20)

# Create data frame
topic_words_df <- tibble(
  topic = 1:chosen_K,
  label = topic_labels,
  top_words = apply(top_words$prob, 1, function(x) paste(x, collapse = ", "))
)

# Export
write_csv(topic_words_df, paste0("topic_top_words_K", chosen_K, ".csv"))
cat("Exported to 'topic_top_words_K", chosen_K, ".csv'\n")

# Display
knitr::kable(topic_words_df, caption = "Top Words for Each Topic")
```

### Summary Statistics

```{r summary-stats}
# Create summary of your analysis
summary_stats <- tibble(
  metric = c("Number of documents", "Vocabulary size", "Number of topics", 
             "Model seed", "Lower threshold", "Upper threshold"),
  value = c(length(docs), length(vocab), chosen_K, 12345, 5, "95%")
)

knitr::kable(summary_stats, caption = "Analysis Summary")
```

---

## 13. Save Your Session

```{r save-session}
# Save all important objects
save(stm_model, docs, vocab, meta, K_search, raw_texts, processed_texts,
     file = paste0("stm_session_K", chosen_K, ".RData"))

cat("Session saved to 'stm_session_K", chosen_K, ".RData'\n")
cat("\nTo reload later: load('stm_session_K", chosen_K, ".RData')\n")
```

---

## Notes and Next Steps

### What you accomplished:
- ✅ Imported and preprocessed text files from multiple volumes/months
- ✅ Tested multiple K values to find optimal number of topics
- ✅ Fit an STM model
- ✅ Interpreted and labeled topics
- ✅ Created visualizations
- ✅ Exported results

### Next steps:
1. **Refine K**: Try different K values based on your searchK results
2. **Improve labels**: Read more example documents and refine topic names
3. **Add covariates**: Use year, volume, month to explore how topics vary
4. **Validate topics**: Share with domain experts to verify topics make sense
5. **Scale up**: Once satisfied with test results, run on full dataset

### Tips for choosing K:
- **Too few topics (K too small)**: Topics are very broad and mix different themes
- **Too many topics (K too large)**: Topics are very specific and might be redundant
- **Just right**: Topics are distinct, interpretable, and align with your research goals

### Common K ranges by corpus size:
- Small corpus (50-200 docs): K = 5-15
- Medium corpus (200-1000 docs): K = 10-25
- Large corpus (1000+ docs): K = 20-50

---

## Session Info

```{r session-info}
sessionInfo()
```
