---
title: "Topic-to-Article Linker - Woman's Exponent"
author: "Birch"
date: "`r Sys.Date()`"
output:
  html_notebook:
    toc: true
    toc_float: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Topic-to-Article Linker

This notebook runs STM topic modeling on whatever Woman's Exponent volumes are
placed in the input folder, then links each topic back to specific articles from
the inventory so you can identify concrete evidentiary examples for each topic
bucket. Just drop WEVol## folders into the input directory and run.

---

## 1. Load Packages

```{r load-packages}
library(stm)
library(tidyverse)
library(readxl)
library(stopwords)
library(igraph)
library(DT)
library(textstem)    # For lemmatization
library(pheatmap)    # For heatmaps
library(scales)      # For percent formatting
library(wordcloud)
library(ggridges)    # For ridgeline plots
library(patchwork)   # For plot composition (|, /)
library(ggrepel)     # For labeled scatter points

set.seed(12345)
cat("Packages loaded.\n")
```

---

## 2. Set Paths

```{r set-paths}
input_path <- "/home/rbirch/rbirch/Topicmodel/input"

output_path <- "/home/rbirch/rbirch/Topicmodel/output_linked"

inventory_path <- "/home/rbirch/rbirch/Topicmodel/WE_article_inventory_vols1-41.xlsx"

if (!dir.exists(output_path)) {
  dir.create(output_path, recursive = TRUE)
}

cat("Input:    ", input_path, "\n")
cat("Output:   ", output_path, "\n")
cat("Inventory:", inventory_path, "\n")
```

---

## 3. Load Article Inventory

```{r load-inventory}
inventory <- read_excel(inventory_path, sheet = "Article Inventory")

cat("Inventory loaded:", nrow(inventory), "articles\n")
cat("Columns:", paste(names(inventory), collapse = ", "), "\n\n")

# Detect which volumes are in the input folder
input_vol_dirs <- list.dirs(input_path, recursive = FALSE, full.names = FALSE)
input_vol_nums <- as.integer(str_extract(input_vol_dirs, "\\d+"))
input_vol_nums <- sort(input_vol_nums[!is.na(input_vol_nums)])

cat("Volumes detected in input:", paste(input_vol_nums, collapse = ", "), "\n")

# Filter inventory to only the volumes present in input
inventory_subset <- inventory %>%
  filter(Volume %in% input_vol_nums)

cat("Matching inventory articles:", nrow(inventory_subset), "\n")
```

---

## 4. Import Article Files

```{r import-files}
all_files <- list.files(path = input_path, full.names = TRUE, recursive = TRUE)
file_paths <- all_files[grepl("\\.txt$", all_files, ignore.case = TRUE)]

cat("Total .txt files found:", length(file_paths), "\n\n")

# Read all files
raw_texts <- tibble(
  filepath = file_paths,
  filename = basename(file_paths),
  text = map_chr(file_paths, ~read_file(.x))
)

cat("Read", nrow(raw_texts), "files.\n")
```

---

## 5. Extract Metadata & Join to Inventory

```{r extract-metadata}
# Extract metadata from file path structure
raw_texts <- raw_texts %>%
  mutate(
    # Parse volume from WEVol## directory
    volume_dir = str_extract(filepath, "WEVol\\d+"),
    volume_num = as.integer(str_extract(volume_dir, "\\d+")),
    # Parse from filename: WE_Vol32_1903_Issue1_002_TITLE.txt
    year = as.integer(str_extract(filename, "(?<=Vol\\d{1,2}_)\\d{4}")),
    issue = str_extract(filename, "(?<=Issue)\\d+"),
    article_number = as.integer(str_extract(filename, "(?<=Issue\\d{1,2}_)\\d{3}")),
    doc_id = row_number(),
    word_count = str_count(text, "\\S+")
  )

# Join to inventory by filename
raw_texts <- raw_texts %>%
  left_join(
    inventory_subset %>% select(Filename, Title, Author, Article_Type, Volume, Month),
    by = c("filename" = "Filename")
  )

match_count <- sum(!is.na(raw_texts$Title))
cat("Matched to inventory:", match_count, "of", nrow(raw_texts), "files\n")
cat("Unmatched:", sum(is.na(raw_texts$Title)), "\n\n")

# Show sample
raw_texts %>%
  filter(!is.na(Title)) %>%
  select(filename, Title, Author, Article_Type, Volume, year) %>%
  head(10) %>%
  print()
```

---

## 6. Text Cleaning

```{r clean-text}
standard_stopwords <- stopwords::stopwords("en", source = "snowball")

custom_stopwords <- c(
  "the", "of", "and", "in", "to", "a", "is", "that", "it", "for",
  "as", "on", "with", "be", "was", "by", "are", "from", "or", "an",
  "at", "this", "which", "have", "has", "had", "but", "not", "can",
  "will", "been", "were", "their", "they", "we", "our", "would",
  "there", "what", "so", "if", "who", "than", "may", "also",
  "mrs", "mr", "miss", "dr", "ms",
  "january", "february", "march", "april", "may", "june",
  "july", "august", "september", "october", "november", "december",
  "vol", "page", "number", "volume", "board", "officer", "general",
  "thee", "thou", "whom", "no", "num", "pp", "pg",
  "issue", "nth", "th", "st", "nd", "rd",
  "womansexponent", "exponent",
  # Masthead / publication boilerplate
  "editor", "publisher", "publishe", "published", "publish",
  "assistant", "monthly", "salt", "lake", "city", "utah",
  "term", "copy", "year", "month", "cts", "cent",
  "subscription", "subscribe", "postage", "mail", "deliver",
  "advertise", "advertiser", "advertisement", "advertising",
  
  # Table of contents vocabulary
  "content", "contents", "frontmatter", "front", "matter",
  # Common structural words in programs and listings
  "program", "report", "reports", "committee", "meeting",
  "secretary", "sec", "secy", "asst", "pres", "treas",
  "treasurer", "president", "vice"
)

years_as_words <- as.character(unique(na.omit(raw_texts$year)))

# OCR fragment / junk word blacklist — common broken words from digitized text
ocr_junk_stopwords <- c(
  # Suffix-only fragments
  "ing", "tion", "ment", "ness", "ings", "tive", "ance", "ence",
  "ered", "ters", "bers", "dren", "howe", "ould", "ight", "ther",
  "ated", "ting", "ally", "ible", "able", "ious", "eous", "ical",
  "onal", "ship", "ward", "wise", "less",
  # Truncated word fragments from OCR
  "deliv", "presi", "inter", "encour", "terest", "testi",
  "soci", "coun", "chil", "pariel", "organiza", "ganized",
  "ference", "musser", "selion",
  # Structural boilerplate remnants
  "column", "columns", "chapter", "section", "article",
  "continued", "copyright", "printed"
)

all_stopwords <- unique(c(standard_stopwords, custom_stopwords,
                          ocr_junk_stopwords, years_as_words))

# Regex patterns to catch OCR fragments not in the explicit list
is_ocr_fragment <- function(w) {
  grepl("^[a-z]{1,3}(tion|ment|ence|ness|ings|tive|ance)$", w) |
  grepl("^(pre|suf|dis|un|re)[a-z]{0,2}$", w) |
  grepl("^[^a-z]+$", w)
}

processed_texts <- raw_texts %>%
  mutate(
    text_clean = str_to_lower(text),
    text_clean = str_remove_all(text_clean, "http\\S+"),
    text_clean = str_remove_all(text_clean, "\\S+@\\S+"),
    text_clean = str_remove_all(text_clean, "\\bvol\\.?\\s*\\d+\\b"),
    text_clean = str_remove_all(text_clean, "\\bno\\.?\\s*\\d+\\b"),
    text_clean = str_remove_all(text_clean, "\\bp\\.?\\s*\\d+\\b"),
    text_clean = str_remove_all(text_clean, "\\b\\d+\\b"),
    text_clean = str_remove_all(text_clean, "[[:punct:]]"),
    text_clean = str_squish(text_clean),
    words = str_split(text_clean, "\\s+"),
    words_filtered = map(words, ~.x[!.x %in% all_stopwords]),
    words_filtered = map(words_filtered, ~.x[!grepl("^\\d+$", .x)]),
    words_filtered = map(words_filtered, ~.x[nchar(.x) >= 3 & !is_ocr_fragment(.x)]),
    # Lemmatize: women->woman, churches->church, etc.
    words_lemma = map(words_filtered, ~lemmatize_words(.x)),
    # Re-filter stopwords after lemmatization (some lemmas become stopwords)
    words_final = map(words_lemma, ~.x[!.x %in% all_stopwords & nchar(.x) >= 3 & !is_ocr_fragment(.x)]),
    text_final = map_chr(words_final, ~paste(.x, collapse = " ")),
    final_word_count = str_count(text_final, "\\S+")
  )

cat("Avg words before:", round(mean(raw_texts$word_count)), "\n")
cat("Avg words after:", round(mean(processed_texts$final_word_count)), "\n")

processed_texts <- processed_texts %>%
  filter(final_word_count >= 10)

cat("Documents after filtering:", nrow(processed_texts), "\n\n")

# --- Deduplicate near-identical documents ---
# Some articles were split into multiple sub-files with identical text.
# These duplicates give one piece of content outsized weight in the model.
cat("Deduplicating near-identical documents...\n")
n_before_dedup <- nrow(processed_texts)

processed_texts <- processed_texts %>%
  mutate(text_fingerprint = substr(text_final, 1, 200)) %>%
  group_by(text_fingerprint) %>%
  slice(1) %>%
  ungroup() %>%
  select(-text_fingerprint) %>%
  mutate(doc_id = row_number())

cat("  Removed", n_before_dedup - nrow(processed_texts), "near-duplicate documents\n")
cat("  Corpus after dedup:", nrow(processed_texts), "documents\n")
```

---

## 7. Prepare & Fit STM

```{r prepare-stm}
# Fill NA Article_Type so prevalence covariates don't create row mismatches
processed_texts <- processed_texts %>%
  mutate(Article_Type = ifelse(is.na(Article_Type), "Unknown", Article_Type))

processed <- textProcessor(
  documents = processed_texts$text_final,
  metadata = processed_texts %>%
    select(doc_id, filename, volume_num, year, issue, Title, Author, Article_Type),
  lowercase = FALSE,
  removestopwords = FALSE,
  removenumbers = TRUE,
  removepunctuation = FALSE,
  stem = FALSE,
  wordLengths = c(3, Inf),
  sparselevel = 1,
  language = "en",
  verbose = TRUE
)

out <- prepDocuments(
  documents = processed$documents,
  vocab = processed$vocab,
  meta = processed$meta,
  lower.thresh = 1,
  upper.thresh = Inf
)

docs <- out$documents
vocab <- out$vocab
meta <- out$meta

# Store the texts that actually made it into the model (for findThoughts later)
modeled_texts <- processed_texts$text_final[match(meta$doc_id, processed_texts$doc_id)]

cat("\nCorpus ready:", length(docs), "documents,", length(vocab), "vocab terms\n")
cat("  (dropped", nrow(processed_texts) - length(docs), "documents during preprocessing)\n")
```

```{r searchK, cache=TRUE}
# ============================================================
# DIAGNOSTIC: searchK - tests multiple K values
# Shows held-out likelihood, residuals, semantic coherence,
# and lower bound to help justify your choice of K.
# Set eval=FALSE after running once to skip on re-runs.
# ============================================================
cat("Running searchK diagnostic (this may take 10-30 minutes)...\n")

K_candidates <- c(5, 7, 10, 12, 15, 20)

searchK_results <- searchK(
  documents = docs,
  vocab = vocab,
  K = K_candidates,
  data = meta,
  prevalence = ~ s(year),
  init.type = "Spectral",
  seed = 12345,
  verbose = TRUE
)

plot(searchK_results)

# Save for reference
saveRDS(searchK_results, file.path(output_path, "searchK_results.rds"))
cat("searchK results saved. Use the plots to pick K.\n")
cat("Look for: high held-out likelihood, high semantic coherence,\n")
cat("low residuals, and a balance point on exclusivity vs coherence.\n")
```

```{r searchK-sweet-spot, eval=TRUE, fig.width=10, fig.height=6}
# ============================================================
# COHERENCE vs EXCLUSIVITY OVERLAY — Finding the Sweet Spot
# Both metrics on one plot with dual y-axes.
# The crossover/convergence region = optimal K.
# Set eval=FALSE after running once to skip on re-runs.
# ============================================================
if (exists("searchK_results")) {

  # Extract the metrics from searchK output
  sk_data <- data.frame(
    K       = unlist(searchK_results$results$K),
    semcoh  = unlist(searchK_results$results$semcoh),
    exclus  = unlist(searchK_results$results$exclus)
  )

  # Normalize both metrics to 0-1 scale for overlay comparison
  sk_norm <- sk_data %>%
    mutate(
      coherence_norm  = (semcoh - min(semcoh)) / (max(semcoh) - min(semcoh)),
      exclusivity_norm = (exclus - min(exclus)) / (max(exclus) - min(exclus))
    ) %>%
    select(K, coherence_norm, exclusivity_norm) %>%
    pivot_longer(c(coherence_norm, exclusivity_norm),
                 names_to = "metric", values_to = "value") %>%
    mutate(metric = ifelse(metric == "coherence_norm",
                           "Semantic Coherence", "Exclusivity"))

  # Find approximate sweet spot (where lines are closest)
  sweet_spot <- sk_data %>%
    mutate(
      coh_n = (semcoh - min(semcoh)) / (max(semcoh) - min(semcoh)),
      exc_n = (exclus - min(exclus)) / (max(exclus) - min(exclus)),
      gap   = abs(coh_n - exc_n)
    ) %>%
    slice_min(gap, n = 1)

  ggplot(sk_norm, aes(x = K, y = value, color = metric, linetype = metric)) +
    geom_line(linewidth = 1.3) +
    geom_point(size = 3) +
    # Mark the sweet spot
    geom_vline(xintercept = sweet_spot$K,
               linetype = "dotted", color = "grey30", linewidth = 0.8) +
    geom_label(data = sweet_spot,
               aes(x = K, y = 0.5, label = paste0("K=", K)),
               color = "grey30", size = 3.5, fill = "white",
               label.padding = unit(0.2, "lines"),
               inherit.aes = FALSE) +
    scale_color_manual(values = c("Semantic Coherence" = "#2563eb",
                                   "Exclusivity" = "#CD661D")) +
    scale_linetype_manual(values = c("solid", "dashed")) +
    scale_x_continuous(breaks = K_candidates) +
    labs(title = "Finding the Sweet Spot: Coherence vs Exclusivity",
         subtitle = "Woman's Exponent | Both metrics normalized 0-1 | Dotted line = most balanced tradeoff",
         x = "Number of Topics (K)",
         y = "Normalized Score (0-1)",
         color = "Metric", linetype = "Metric") +
    theme_minimal(base_size = 12) +
    theme(
      legend.position = "bottom",
      panel.grid.minor = element_blank(),
      plot.title = element_text(face = "bold", size = 16)
    )

  cat("\nSweet spot: K =", sweet_spot$K, "\n")
  cat("(where coherence and exclusivity tradeoff is most balanced)\n")
}
```

```{r set-k}
# ============================================================
# SET NUMBER OF TOPICS HERE
# After running searchK above, pick the K that balances
# coherence and exclusivity. Or just set it manually.
# ============================================================
chosen_K <- 12
cat("K =", chosen_K, "\n")
```

```{r fit-model, cache=TRUE}
# Using prevalence covariates: the model learns how topic prevalence
# varies by year and article type during fitting, not just post-hoc.
stm_model <- stm(
  documents = docs,
  vocab = vocab,
  K = chosen_K,
  prevalence = ~ s(year) + Article_Type,
  data = meta,
  max.em.its = 75,
  init.type = "Spectral",
  seed = 12345,
  verbose = TRUE
)

saveRDS(stm_model, file.path(output_path, paste0("stm_model_K", chosen_K, ".rds")))
cat("Model saved.\n")
```

---

## 8. Examine Topics

```{r examine-topics}
all_top_words <- labelTopics(stm_model, n = 15)

cat("Top words per topic:\n\n")
for (i in 1:chosen_K) {
  cat("Topic", i, "\n")
  cat("  FREX:", paste(all_top_words$frex[i, 1:10], collapse = ", "), "\n")
  cat("  PROB:", paste(all_top_words$prob[i, 1:10], collapse = ", "), "\n\n")
}
```

---

## 8b. Auto-Generate Topic Labels

Keyword rules try to assign descriptive labels based on FREX/PROB words.
Topics that don't match any rule get a label from their top 3 FREX words.
You can add rules or override labels in the next section.

```{r auto-labels}
cat(rep("=", 70), "\n", sep = "")
cat("AUTO-GENERATING LABELS\n")
cat(rep("=", 70), "\n\n", sep = "")

create_specific_label <- function(topic_num, frex_words, prob_words) {
  frex_text <- tolower(paste(frex_words, collapse = " "))
  prob_text <- tolower(paste(prob_words, collapse = " "))
  all_words <- paste(frex_text, prob_text)

  # ---- RELIGION & DOCTRINE ----
  if (grepl("kingdom.*gospel|baptism.*eternal|salvation|atonement", frex_text)) {
    label <- "Gospel Doctrine & Spiritual Kingdom"
  } else if (grepl("passover|paschal|feast|tabernacle", frex_text)) {
    label <- "Biblical Symbolism & Ancient Rituals"
  } else if (grepl("abraham.*sarai|biblical|moses|israel", frex_text)) {
    label <- "Biblical Narratives"
  } else if (grepl("prayer|faith.*hope|testimony|spirit.*holy", frex_text)) {
    label <- "Faith & Spiritual Life"
  } else if (grepl("lesson|scripture|doctrine|commandment", frex_text)) {
    label <- "Religious Lessons & Scripture Study"
  } else if (grepl("temple|ordinance|endowment|sealing", frex_text)) {
    label <- "Temple & Sacred Ordinances"
  } else if (grepl("missionary|mission.*field|convert|preach", frex_text)) {
    label <- "Missionary Work & Conversion"

  # ---- RELIEF SOCIETY & CHURCH ORG ----
  } else if (grepl("sisters.*presidency|organization.*grain|relief.*society.*leader", frex_text)) {
    label <- "Relief Society Leadership & Organization"
  } else if (grepl("stake.*ward|attendance.*conference|quarterly", frex_text)) {
    label <- "Stake & Ward Relief Society Reports"
  } else if (grepl("empey|mclelland|board.*member|general.*board", frex_text)) {
    label <- "Board Member Directory"
  } else if (grepl("conference|general.*conference|session|sustain", all_words)) {
    label <- "Church Conference Proceedings"

  # ---- WOMEN'S RIGHTS & POLITICS ----
  } else if (grepl("suffrage.*vote|legislature|franchise|ballot", frex_text)) {
    label <- "Women's Suffrage & Political Rights"
  } else if (grepl("council.*international|convention|delegate", frex_text)) {
    label <- "International Women's Councils"
  } else if (grepl("equal.*right|petition|protest|reform", frex_text)) {
    label <- "Women's Reform & Activism"

  # ---- DOMESTICITY & HOME ----
  } else if (grepl("recipe|tbsp|boiling|oven|flour|bake", frex_text)) {
    label <- "Recipes & Cooking Instructions"
  } else if (grepl("housework|housekeeping|budget|thrift", frex_text)) {
    label <- "Household Management & Budgeting"
  } else if (grepl("child|mother.*rear|parent|infant|nurture", frex_text)) {
    label <- "Motherhood & Child-Rearing"
  } else if (grepl("garden|plant.*seed|flower|cultivation", frex_text)) {
    label <- "Home Gardening & Agriculture"
  } else if (grepl("sew|pattern|dress|fabric|garment|fashion", frex_text)) {
    label <- "Sewing, Fashion & Handwork"

  # ---- EDUCATION & PROFESSIONALIZATION ----
  } else if (grepl("nurse.*hospital|nursing.*training|medical", frex_text)) {
    label <- "Nursing Training & Hospital Work"
  } else if (grepl("school|teacher|student|education|university|class", frex_text)) {
    label <- "Education & Schools"
  } else if (grepl("diet.*protein|nutrition|malnutrition|vitamin", frex_text)) {
    label <- "Nutrition & Dietary Science"
  } else if (grepl("radium.*curie|pasteur.*science|scientist|discovery", frex_text)) {
    label <- "Scientific Biography & Discovery"

  # ---- HISTORY & PIONEER ----
  } else if (grepl("emigration.*journey|wagon.*pioneer|handcart|plains", frex_text)) {
    label <- "Pioneer Emigration & Journey Stories"
  } else if (grepl("pioneer|settlement|early.*days|frontier", all_words)) {
    label <- "Pioneer Heritage & Settlement"

  # ---- LITERATURE & ARTS ----
  } else if (grepl("irving|tale|novel|literary|author", frex_text)) {
    label <- "Literature & Book Reviews"
  } else if (grepl("jerry|walter|jimmy|agnes|margaret", frex_text) && grepl("said|little|came", prob_text)) {
    label <- "Serialized Fiction & Stories"
  } else if (grepl("poem|verse|stanza|rhyme|lyric", all_words)) {
    label <- "Poetry & Verse"
  } else if (grepl("tableau.*song|music.*hymn|choir|sing", frex_text)) {
    label <- "Musical Programs & Performances"

  # ---- WAR & CURRENT EVENTS ----
  } else if (grepl("entente.*allies|war.*troops|soldier|military|battle", frex_text)) {
    label <- "War Commentary & News"
  } else if (grepl("europe|nation|government|political|congress", frex_text)) {
    label <- "National & International Affairs"

  # ---- COMMERCE & ADS ----
  } else if (grepl("merino.*cotton|bleached.*gauze|advertis|price|store", frex_text)) {
    label <- "Advertisements & Commerce"
  } else if (grepl("^\\d+.*\\d+.*\\d+", frex_text)) {
    label <- "Magazine Index & Page Numbers"

  # ---- HEALTH ----
  } else if (grepl("health|disease|sanit|hygiene|cure|sick", all_words)) {
    label <- "Health & Sanitation"

  # ---- OBITUARY & BIOGRAPHY ----
  } else if (grepl("death|funeral|deceased|mourn|tribute", frex_text)) {
    label <- "Obituaries & Tributes"
  } else if (grepl("life.*born|biography|memoir|career|accomplish", frex_text)) {
    label <- "Biographical Sketches"

  # ---- CORRESPONDENCE ----
  } else if (grepl("letter|editor|dear|correspond|write", frex_text)) {
    label <- "Correspondence & Letters"

  # ---- FALLBACK: use top 3 FREX words ----
  } else {
    keywords <- paste(tools::toTitleCase(frex_words[1:3]), collapse = " / ")
    label <- keywords
  }

  return(label)
}

topic_labels <- sapply(1:chosen_K, function(i) {
  frex_words <- all_top_words$frex[i, 1:10]
  prob_words <- all_top_words$prob[i, 1:10]
  create_specific_label(i, frex_words, prob_words)
})

cat("Auto-generated labels:\n")
cat(rep("=", 70), "\n\n", sep = "")

for (i in 1:chosen_K) {
  cat("Topic", i, ":", topic_labels[i], "\n")
  cat("  FREX:", paste(all_top_words$frex[i, 1:7], collapse = ", "), "\n")
  cat("  PROB:", paste(all_top_words$prob[i, 1:7], collapse = ", "), "\n\n")
}

# Export auto-labels for reference
frex_for_export <- apply(all_top_words$frex, 1, function(x) paste(x, collapse = ", "))
prob_for_export <- apply(all_top_words$prob, 1, function(x) paste(x, collapse = ", "))

label_export <- tibble(
  topic_num = 1:chosen_K,
  auto_label = topic_labels,
  frex_words = frex_for_export,
  prob_words = prob_for_export,
  manual_label = ""
)

labels_file <- file.path(output_path, paste0("topic_labels_K", chosen_K, ".csv"))
write_csv(label_export, labels_file)
cat("Labels saved to:", labels_file, "\n")
```

---

## 8c. Manual Label Overrides (Optional)

Review the auto-generated labels above. Override any that need better names.
Only uncomment and edit the lines you want to change.

```{r manual-overrides}
# ============================================================
# MANUAL OVERRIDES - uncomment and edit as needed
# ============================================================
topic_labels[1] <- "Poetry"
topic_labels[2] <- "Relief Society Conference Reports"
topic_labels[3] <- "Women's Rights"
topic_labels[4] <- "Relief Society Sponsored Education and Grain Storage"
topic_labels[5] <- "Community Celebration"
topic_labels[6] <- "International Women's Rights Organizations"
topic_labels[7] <- "Women's Traveling Reports"
topic_labels[8] <- "Memoriam and Obituaries"
topic_labels[9] <- "Tributes and Biographies of Women"
topic_labels[10] <- "Literature and Poetry"
topic_labels[11] <- "Motherhood and Women's Duties"
topic_labels[12] <- "Theology and Gospel Doctrine"

cat("FINAL TOPIC LABELS\n")
cat(rep("=", 70), "\n\n", sep = "")
for (i in 1:chosen_K) {
  cat("  Topic", i, ":", topic_labels[i], "\n")
}
```

---

## 8d. Find Examples for a Specific Topic

Change `topic_to_examine` to preview example articles for any topic
before finalizing labels.

```{r find-examples-custom}
# ============================================================
# CHANGE THIS to examine any topic
# ===========================================================
topic_to_examine <- 11

n_examples <- 10

cat(rep("=", 70), "\n", sep = "")
cat("TOPIC", topic_to_examine, ":", topic_labels[topic_to_examine], "\n")
cat(rep("=", 70), "\n", sep = "")
cat("FREX:", paste(all_top_words$frex[topic_to_examine, 1:10], collapse = ", "), "\n")
cat("PROB:", paste(all_top_words$prob[topic_to_examine, 1:10], collapse = ", "), "\n")
cat(rep("-", 70), "\n\n", sep = "")

# modeled_texts was stored after prepDocuments — guaranteed to match model docs
thoughts <- findThoughts(stm_model,
                         texts = modeled_texts,
                         topics = topic_to_examine,
                         n = n_examples)

thought_indices <- thoughts$index[[1]]

for (i in seq_along(thought_indices)) {
  idx <- thought_indices[i]
  row <- processed_texts[idx, ]

  cat(sprintf("Example %d of %d:\n", i, length(thought_indices)))
  cat(sprintf("  File:   %s\n", row$filename))
  cat(sprintf("  Title:  %s\n", ifelse(is.na(row$Title), "(unknown)", row$Title)))
  cat(sprintf("  Author: %s\n", ifelse(is.na(row$Author) | row$Author == "Unknown", "-", row$Author)))
  cat(sprintf("  Type:   %s\n", ifelse(is.na(row$Article_Type), "-", row$Article_Type)))
  cat(sprintf("  Vol %s, %s, Issue %s\n\n", row$volume_num, row$year, row$issue))
  cat(substr(thoughts$docs[[1]][i], 1, 400), "\n\n")
  cat(rep("-", 50), "\n\n", sep = "")
}
```

---

## 9. Link Topics to Articles

This is the key section: for each topic, find the articles with the highest
proportion of that topic. These are your evidentiary examples.

```{r link-topics-to-articles}
# Get document-topic proportions (make.dt merges meta columns automatically)
doc_topics <- make.dt(stm_model, meta = meta)

# Check what columns are available
cat("Columns in doc_topics:\n")
cat(paste(names(doc_topics), collapse = ", "), "\n\n")

# Build the full linked table
# make.dt() already includes all meta columns, so no join needed
topic_article_link <- doc_topics %>%
  pivot_longer(
    cols = starts_with("Topic"),
    names_to = "topic",
    values_to = "proportion"
  ) %>%
  mutate(
    topic_num = as.integer(str_remove(topic, "Topic")),
    topic_label = topic_labels[topic_num]
  ) %>%
  select(topic_num, topic_label, proportion,
         any_of(c("filename", "Title", "Author", "Article_Type",
                  "volume_num", "year", "issue"))) %>%
  arrange(topic_num, desc(proportion))

cat("Linked table:", nrow(topic_article_link), "rows\n")
cat("(", nrow(doc_topics), "documents x", chosen_K, "topics )\n")
```

---

## 9b. Dominant Topic Assignment

Each article is tagged with its single strongest topic, plus a confidence
flag based on whether the proportion exceeds a threshold.

```{r dominant-topic}
# ============================================================
# THRESHOLD: articles above this % are "strong" exemplars
# ============================================================
exemplar_threshold <- 0.40  # 40%

# Assign dominant topic to each document
# (doc_topics already has meta columns from make.dt)
dominant_topics <- doc_topics %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "proportion") %>%
  mutate(topic_num = as.integer(str_remove(topic, "Topic"))) %>%
  group_by(doc_id) %>%
  slice_max(proportion, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  mutate(
    topic_label = topic_labels[topic_num],
    strong_exemplar = proportion >= exemplar_threshold,
    proportion_pct = round(proportion * 100, 1)
  ) %>%
  select(doc_id, any_of(c("filename", "Title", "Author", "Article_Type",
         "volume_num", "year", "issue")),
         dominant_topic = topic_num, topic_label, proportion_pct, strong_exemplar) %>%
  arrange(dominant_topic, desc(proportion_pct))

cat("Dominant topic assigned to", nrow(dominant_topics), "documents\n")
cat("Strong exemplars (>", exemplar_threshold * 100, "%):", sum(dominant_topics$strong_exemplar), "\n\n")

# Summary of articles per topic
dominant_topics %>%
  group_by(dominant_topic, topic_label) %>%
  summarise(
    n_articles = n(),
    n_strong = sum(strong_exemplar),
    avg_proportion = round(mean(proportion_pct), 1),
    .groups = "drop"
  ) %>%
  print(n = chosen_K)
```

```{r strong-exemplars}
# Show strong exemplars per topic
cat("\nSTRONG EXEMPLARS (>", exemplar_threshold * 100, "% topic proportion):\n")

for (t in 1:chosen_K) {
  strong <- dominant_topics %>%
    filter(dominant_topic == t, strong_exemplar)

  cat("\n", rep("-", 60), "\n", sep = "")
  cat("Topic", t, ":", topic_labels[t], " (", nrow(strong), " strong exemplars)\n")

  if (nrow(strong) > 0) {
    for (i in 1:min(10, nrow(strong))) {
      row <- strong[i, ]
      cat(sprintf("  [%s%%] %s | %s | Vol %s %s\n",
                  row$proportion_pct,
                  ifelse(is.na(row$Title), row$filename, row$Title),
                  ifelse(is.na(row$Author) | row$Author == "Unknown", "-", row$Author),
                  row$volume_num, row$year))
    }
  } else {
    cat("  (none above threshold - try lowering exemplar_threshold)\n")
  }
}
```

---

## 10. Top Articles per Topic

For each topic bucket, here are the top 15 articles ranked by how strongly
they express that topic. Use these as evidentiary examples.

```{r top-articles-per-topic}
top_n_per_topic <- 15

for (t in 1:chosen_K) {
  cat("\n", rep("=", 70), "\n", sep = "")
  cat("TOPIC", t, ":", topic_labels[t], "\n")
  cat(rep("=", 70), "\n")
  cat("FREX:", paste(all_top_words$frex[t, 1:10], collapse = ", "), "\n\n")

  top_arts <- topic_article_link %>%
    filter(topic_num == t) %>%
    head(top_n_per_topic)

  for (i in 1:nrow(top_arts)) {
    row <- top_arts[i, ]
    cat(sprintf("  %2d. [%.1f%%] Vol %s, %s, Issue %s | %s | %s | %s\n",
                i,
                row$proportion * 100,
                row$volume_num,
                row$year,
                row$issue,
                ifelse(is.na(row$Title), row$filename, row$Title),
                ifelse(is.na(row$Author) | row$Author == "Unknown", "-", row$Author),
                ifelse(is.na(row$Article_Type), "-", row$Article_Type)))
  }
}
```

---

## 11. Interactive Article Browser

Use this searchable table to find articles by topic, type, author, etc.

```{r interactive-browser}
# Top 25 articles per topic for the interactive table
browse_data <- topic_article_link %>%
  group_by(topic_num) %>%
  slice_max(proportion, n = 25) %>%
  ungroup() %>%
  mutate(
    proportion_pct = round(proportion * 100, 1)
  ) %>%
  select(
    Topic = topic_num,
    Label = topic_label,
    `%` = proportion_pct,
    Title,
    Author,
    Type = Article_Type,
    Vol = volume_num,
    Year = year,
    Issue = issue,
    Filename = filename
  )

datatable(
  browse_data,
  filter = "top",
  options = list(pageLength = 20, scrollX = TRUE),
  caption = "Top 25 articles per topic - filter by topic, type, author, etc."
)
```

---

## 12. Topic Prevalence Summary

```{r topic-prevalence}
topic_props <- colMeans(doc_topics %>% select(starts_with("Topic")))

prevalence_df <- tibble(
  topic_num = 1:chosen_K,
  label = topic_labels,
  prevalence = topic_props,
  pct = round(topic_props * 100, 1)
) %>%
  arrange(desc(prevalence))

# Bar plot
par(mar = c(5, 18, 4, 2))
barplot(
  height = prevalence_df$prevalence,
  names.arg = prevalence_df$label,
  horiz = TRUE,
  las = 1,
  col = "#CD661D",
  border = "#8B4513",
  main = paste0("Topic Prevalence - Woman's Exponent (Vols ", min(input_vol_nums), "-", max(input_vol_nums), ")"),
  xlab = "Expected Topic Proportion",
  cex.names = 0.7,
  xlim = c(0, max(prevalence_df$prevalence) * 1.3)
)
text(
  x = prevalence_df$prevalence + 0.005,
  y = seq(0.7, by = 1.2, length.out = nrow(prevalence_df)),
  labels = paste0(prevalence_df$pct, "%"),
  cex = 0.7, col = "#8B4513", font = 2
)
par(mar = c(5, 4, 4, 2))

print(prevalence_df %>% select(topic_num, label, pct))
```

---

## 13. STM Summary Plot

```{r stm-summary, fig.width=10, fig.height=6}
plot(stm_model,
     type = "summary",
     n = min(10, chosen_K),
     main = paste("Topic Prevalence (K =", chosen_K, ")"),
     xlim = c(0, 0.3))
```

---

## 14. Lollipop Prevalence with Top Words

```{r lollipop-prevalence, fig.width=10, fig.height=6}
library(ggplot2)

top_words_display <- labelTopics(stm_model, n = 10)

labels_df <- tibble(
  topic = 1:chosen_K,
  name = topic_labels,
  words = sapply(1:chosen_K, function(i) paste(top_words_display$prob[i, 1:10], collapse = ", ")),
  full_label = paste0(name, ": ", words),
  prevalence = topic_props
)

ggplot(labels_df, aes(x = prevalence, y = reorder(full_label, prevalence))) +
  geom_segment(aes(x = 0, xend = prevalence, y = full_label, yend = full_label),
               linewidth = 1.2, color = "black") +
  geom_point(aes(x = prevalence, y = full_label), size = 0.5) +
  labs(
    title = paste("Topic Prevalence (K =", chosen_K, ")"),
    x = "Expected Topic Proportions",
    y = NULL
  ) +
  theme_minimal(base_size = 10) +
  theme(
    axis.text.y = element_text(size = 8, hjust = 1),
    plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
    panel.grid.major.y = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  scale_x_continuous(limits = c(0, 0.35), breaks = seq(0, 0.35, 0.05))
```

---

## 15. Topic Prevalence Over Time

```{r prevalence-over-time, fig.width=10, fig.height=6}
cat("Estimating time effects...\n")

prep_time <- estimateEffect(
  formula = 1:chosen_K ~ s(year),
  stmobj = stm_model,
  metadata = meta,
  uncertainty = "Global"
)

cat("Estimation complete.\n\n")

# Get top 6 most prevalent topics
top_6_topics <- order(topic_props, decreasing = TRUE)[1:min(6, chosen_K)]

par(mfrow = c(2, 3), mar = c(4, 4, 3, 1))
for (topic_num in top_6_topics) {
  plot(
    prep_time,
    covariate = "year",
    model = stm_model,
    topics = topic_num,
    method = "continuous",
    xlim = range(meta$year, na.rm = TRUE),
    main = str_wrap(topic_labels[topic_num], 30),
    xlab = "Year",
    ylab = "Topic Proportion",
    linecol = "#3b82f6",
    printlegend = TRUE,
    ci.level = 0.95,
    lwd = 2
  )
}
par(mfrow = c(1, 1))
```

---

## 16. Scatter Plot - Top 6 Topics Over Time

```{r scatter-top6, fig.width=10, fig.height=6}
topic_time_data <- make.dt(stm_model, meta = meta) %>%
  select(starts_with("Topic"), year) %>%
  filter(!is.na(year)) %>%
  group_by(year) %>%
  summarize(across(starts_with("Topic"), mean, na.rm = TRUE), .groups = "drop") %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "prevalence") %>%
  mutate(
    topic_num = as.numeric(str_remove(topic, "Topic")),
    topic_label = str_wrap(topic_labels[topic_num], 30)
  )

topic_time_top6 <- topic_time_data %>%
  filter(topic_num %in% top_6_topics)

ggplot(topic_time_top6, aes(x = year, y = prevalence)) +
  geom_line(color = "#E0EEEE", size = 1.5) +
  geom_point(color = "#E0EEEE", size = 3, alpha = 0.6) +
  geom_smooth(method = "loess", color = "#CD661D", linetype = "dashed",
              se = TRUE, alpha = 0.2) +
  facet_wrap(~topic_label, ncol = 3, scales = "free_y") +
  labs(
    title = "Topic Prevalence Over Time: Top 6 Most Prevalent Topics",
    subtitle = "Points = actual data | Dashed line = trend",
    x = "Year",
    y = "Mean Topic Proportion"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    strip.text = element_text(size = 10, face = "bold"),
    panel.grid.minor = element_blank(),
    plot.title = element_text(face = "bold", size = 14),
    plot.subtitle = element_text(size = 11, color = "grey40")
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1))
```

---

## 17. All Topics Over Time

```{r all-topics-time, fig.width=10, fig.height=8}
ggplot(topic_time_data, aes(x = year, y = prevalence)) +
  geom_line(color = "#CD661d", size = 0.8) +
  geom_point(color = "#CD661d", size = 1.5, alpha = 0.5) +
  facet_wrap(~topic_label, ncol = 4, scales = "free_y") +
  labs(
    title = paste0("Complete Topic Evolution Over Time (Woman's Exponent)"),
    subtitle = paste0("All ", chosen_K, " topics across years"),
    x = "Year",
    y = "Topic Proportion"
  ) +
  theme_minimal(base_size = 10) +
  theme(
    strip.text = element_text(size = 7, face = "bold"),
    panel.grid.minor = element_blank()
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1))
```

---

## 18. Single Topic Detail

```{r single-topic-detail, fig.width=10, fig.height=6}
# CHANGE THIS to examine any topic in detail
topic_to_examine <- 1

topic_detail <- topic_time_data %>%
  filter(topic_num == topic_to_examine)

ggplot(topic_detail, aes(x = year, y = prevalence)) +
  geom_line(color = "#3b82f6", size = 1.5) +
  geom_point(color = "#3b82f6", size = 4, alpha = 0.7) +
  geom_smooth(method = "loess", color = "#ef4444",
              fill = "#fecaca", alpha = 0.3, size = 1) +
  labs(
    title = topic_labels[topic_to_examine],
    subtitle = "Points = annual averages | Red band = smoothed trend with confidence interval",
    x = "Year",
    y = "Topic Proportion"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(size = 11, color = "#64748b"),
    panel.grid.minor = element_blank()
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1)) +
  scale_x_continuous(breaks = seq(min(topic_detail$year),
                                   max(topic_detail$year), by = 2))
```

---

## 19. Topic Correlation Network

```{r correlation-network, fig.width=10, fig.height=8}
mod.out.corr <- topicCorr(stm_model)
plot(mod.out.corr, main = "Topic Correlation Network")
```

---

## 20. Word Clouds

```{r wordcloud-topic1, fig.width=8, fig.height=6}
library(wordcloud)

cloud(stm_model,
      topic = 1,
      scale = c(3, 0.5),
      main = topic_labels[1])
```

```{r wordcloud-all, fig.width=8, fig.height=6, eval=FALSE}
# Set eval=TRUE to generate word clouds for all topics
for (i in 1:chosen_K) {
  cloud(stm_model,
        topic = i,
        scale = c(3, 0.5),
        main = topic_labels[i])
}
```

---

## 21. Topic Quality

```{r topic-quality, fig.width=8, fig.height=6}
topicQuality(stm_model, documents = docs)
```

---

## 22. Compare Two Topics

```{r compare-topics, fig.width=10, fig.height=6}
# Change the topic numbers to compare different topics
plot(stm_model,
     type = "perspectives",
     topics = c(1, 2),
     main = paste("Comparing", topic_labels[1], "vs", topic_labels[2]))
```

---

## 23. Trend Summary Statistics

```{r trend-summary}
topic_trends <- topic_time_data %>%
  group_by(topic_num, topic_label) %>%
  summarise(
    start_prev = first(prevalence),
    end_prev   = last(prevalence),
    change     = end_prev - start_prev,
    pct_change = round((change / start_prev) * 100, 1),
    trend      = case_when(
      change >  0.005 ~ "Increasing",
      change < -0.005 ~ "Decreasing",
      TRUE            ~ "Stable"
    ),
    .groups = "drop"
  ) %>%
  arrange(desc(abs(pct_change)))

cat("TOPIC CHANGE SUMMARY\n")
cat(rep("=", 50), "\n\n", sep = "")

for (i in 1:nrow(topic_trends)) {
  direction <- ifelse(topic_trends$pct_change[i] > 0, "increased", "decreased")
  cat(sprintf("Topic %d (%s): %s by %.1f%% over the study period\n",
              topic_trends$topic_num[i],
              topic_trends$topic_label[i],
              direction,
              abs(topic_trends$pct_change[i])))
}

cat("\n\nSUMMARY TABLE\n")
print(topic_trends %>% select(topic_num, topic_label, pct_change, trend))
```

---

## 24. Topic Prevalence Stats Table

```{r prevalence-stats}
prevalence_summary <- doc_topics %>%
  select(starts_with("Topic")) %>%
  summarise(across(everything(), mean, na.rm = TRUE)) %>%
  pivot_longer(everything(), names_to = "topic", values_to = "mean_proportion") %>%
  mutate(
    topic_num   = as.numeric(str_remove(topic, "Topic")),
    label       = topic_labels[topic_num],
    percentage  = round(mean_proportion * 100, 2),
    rank        = rank(-mean_proportion)
  ) %>%
  arrange(rank) %>%
  select(rank, label, percentage)

print(prevalence_summary)
```

---

## 25. Article Type Distribution per Topic

Which article types cluster into which topics?

```{r type-by-topic}
type_topic <- topic_article_link %>%
  filter(!is.na(Article_Type)) %>%
  group_by(topic_num, topic_label, Article_Type) %>%
  summarise(
    mean_proportion = mean(proportion),
    n_articles = n_distinct(filename),
    .groups = "drop"
  ) %>%
  arrange(topic_num, desc(mean_proportion))

# Show top 3 types per topic
type_topic %>%
  group_by(topic_num, topic_label) %>%
  slice_max(mean_proportion, n = 3) %>%
  print(n = chosen_K * 3)
```

---

## 26. Topic-Article Type Heatmap

```{r type-heatmap, fig.width=10, fig.height=7}
# Build a matrix of mean topic proportion by article type
heatmap_data <- topic_article_link %>%
  filter(!is.na(Article_Type), Article_Type != "Front Matter") %>%
  group_by(topic_num, Article_Type) %>%
  summarise(mean_prop = mean(proportion), .groups = "drop") %>%
  pivot_wider(names_from = Article_Type, values_from = mean_prop, values_fill = 0)

heatmap_matrix <- as.matrix(heatmap_data %>% select(-topic_num))
rownames(heatmap_matrix) <- paste0("T", heatmap_data$topic_num, ": ",
                                    str_trunc(topic_labels[heatmap_data$topic_num], 25))

pheatmap(
  heatmap_matrix,
  main = "Topic Affinity by Article Type",
  color = colorRampPalette(c("white", "#FDDBC7", "#CD661D", "#8B4513"))(50),
  cluster_rows = TRUE,
  cluster_cols = TRUE,
  display_numbers = TRUE,
  number_format = "%.2f",
  fontsize_number = 7,
  fontsize_row = 9,
  fontsize_col = 9,
  angle_col = 45
)
```

---

## 27. Stacked Area Chart - Topic Composition Over Time

```{r stacked-area, fig.width=12, fig.height=6}
stacked_data <- make.dt(stm_model, meta = meta) %>%
  select(starts_with("Topic"), year) %>%
  filter(!is.na(year)) %>%
  group_by(year) %>%
  summarize(across(starts_with("Topic"), mean, na.rm = TRUE), .groups = "drop") %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "prevalence") %>%
  mutate(
    topic_num = as.numeric(str_remove(topic, "Topic")),
    label = topic_labels[topic_num]
  )

ggplot(stacked_data, aes(x = year, y = prevalence, fill = reorder(label, -topic_num))) +
  geom_area(alpha = 0.8, color = "white", linewidth = 0.3) +
  labs(
    title = "Topic Composition Over Time",
    subtitle = "How the discourse mix shifts across years",
    x = "Year",
    y = "Topic Proportion",
    fill = "Topic"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    legend.position = "right",
    legend.text = element_text(size = 7),
    legend.key.size = unit(0.4, "cm")
  ) +
  scale_y_continuous(labels = percent_format()) +
  scale_fill_brewer(palette = "Set3", direction = -1)
```

---

## 28. Topic Co-occurrence Within Articles

Which topics tend to appear together in the same article? Articles that
are high in one topic may also be high in another, revealing thematic
connections.

```{r topic-cooccurrence, fig.width=9, fig.height=8}
# Correlation matrix of topic proportions across documents
topic_prop_matrix <- doc_topics %>%
  select(starts_with("Topic"))

topic_cor <- cor(topic_prop_matrix)
rownames(topic_cor) <- paste0("T", 1:chosen_K, ": ", str_trunc(topic_labels, 20))
colnames(topic_cor) <- paste0("T", 1:chosen_K)

pheatmap(
  topic_cor,
  main = "Topic Co-occurrence (Correlation Matrix)",
  color = colorRampPalette(c("#2166AC", "white", "#B2182B"))(50),
  display_numbers = TRUE,
  number_format = "%.2f",
  fontsize_number = 8,
  fontsize_row = 9,
  fontsize_col = 9,
  breaks = seq(-1, 1, length.out = 51)
)
```

---

## 29. Exclusivity vs Semantic Coherence

This plot helps evaluate topic quality. Topics in the upper-right are both
coherent (words make sense together) and exclusive (words are unique to
that topic). Labeled for easy identification.

```{r exclusivity-coherence, fig.width=9, fig.height=7}
topic_qual <- data.frame(
  topic = 1:chosen_K,
  label = topic_labels,
  coherence = semanticCoherence(stm_model, docs),
  exclusivity = exclusivity(stm_model)
)

ggplot(topic_qual, aes(x = coherence, y = exclusivity)) +
  geom_point(size = 4, color = "#CD661D") +
  geom_text(aes(label = paste0("T", topic)), vjust = -1, size = 3.5) +
  geom_text(aes(label = str_trunc(label, 25)), vjust = 2, size = 2.5,
            color = "grey40") +
  labs(
    title = "Topic Quality: Exclusivity vs Semantic Coherence",
    subtitle = "Upper-right = best topics (coherent + distinctive)",
    x = "Semantic Coherence",
    y = "Exclusivity"
  ) +
  theme_minimal(base_size = 12) +
  theme(
    plot.title = element_text(face = "bold", size = 14)
  )
```

---

## 30. Dominant Topic Distribution

How are articles distributed across topics? Are some topics dominating
the corpus?

```{r dominant-distribution, fig.width=10, fig.height=6}
dom_summary <- dominant_topics %>%
  count(dominant_topic, topic_label) %>%
  mutate(pct = n / sum(n) * 100)

ggplot(dom_summary, aes(x = reorder(topic_label, n), y = n, fill = pct)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, " (", round(pct, 1), "%)")),
            hjust = -0.1, size = 3) +
  coord_flip() +
  labs(
    title = "Articles per Dominant Topic",
    subtitle = "Each article assigned to its strongest topic",
    x = NULL, y = "Number of Articles"
  ) +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold")) +
  scale_fill_gradient(low = "#FDDBC7", high = "#8B4513") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.15)))
```

---

## 31. Topic-by-Volume Heatmap

Shows every topic's prevalence in every volume at a glance. Spot where
topics spike, fade, or first emerge.

```{r topic-volume-heatmap, fig.width=14, fig.height=7}
vol_topic_data <- make.dt(stm_model, meta = meta) %>%
  select(starts_with("Topic"), volume_num) %>%
  filter(!is.na(volume_num)) %>%
  group_by(volume_num) %>%
  summarize(across(starts_with("Topic"), mean, na.rm = TRUE), .groups = "drop")

vol_matrix <- as.matrix(vol_topic_data %>% select(-volume_num))
rownames(vol_matrix) <- paste0("Vol ", vol_topic_data$volume_num)
colnames(vol_matrix) <- paste0("T", 1:chosen_K, ": ", str_trunc(topic_labels, 20))

pheatmap(
  t(vol_matrix),
  main = "Topic Prevalence by Volume",
  color = colorRampPalette(c("white", "#FDDBC7", "#CD661D", "#8B4513"))(100),
  cluster_rows = TRUE,
  cluster_cols = FALSE,
  display_numbers = FALSE,
  fontsize_row = 8,
  fontsize_col = 9,
  angle_col = 45,
  border_color = "grey90"
)
```

---

## 32. Author-Topic Analysis

Which authors write most about which topics? Filters to authors with
multiple articles for meaningful patterns.

```{r author-topic, fig.width=12, fig.height=8}
# Find authors with enough articles to analyze
author_counts <- dominant_topics %>%
  filter(!is.na(Author), Author != "Unknown") %>%
  count(Author, sort = TRUE)

# Use top 20 most prolific authors
top_authors <- author_counts %>%
  head(20) %>%
  pull(Author)

author_topic_data <- topic_article_link %>%
  filter(Author %in% top_authors) %>%
  group_by(Author, topic_num) %>%
  summarise(mean_prop = mean(proportion), .groups = "drop") %>%
  pivot_wider(names_from = topic_num, values_from = mean_prop, values_fill = 0)

# Ensure all K topics are present as columns
for (k in 1:chosen_K) {
  if (!as.character(k) %in% names(author_topic_data)) {
    author_topic_data[[as.character(k)]] <- 0
  }
}
author_topic_data <- author_topic_data %>%
  select(Author, all_of(as.character(1:chosen_K)))

author_matrix <- as.matrix(author_topic_data %>% select(-Author))
rownames(author_matrix) <- author_topic_data$Author
colnames(author_matrix) <- paste0("T", 1:chosen_K, ": ", str_trunc(topic_labels, 18))

pheatmap(
  author_matrix,
  main = paste0("Author-Topic Affinity (Top ", length(top_authors), " Authors)"),
  color = colorRampPalette(c("white", "#FDDBC7", "#CD661D", "#8B4513"))(100),
  cluster_rows = TRUE,
  cluster_cols = TRUE,
  fontsize_row = 8,
  fontsize_col = 8,
  angle_col = 45,
  border_color = "grey90"
)
```

```{r author-topic-table}
# Table: each top author's dominant topic
author_dominant <- dominant_topics %>%
  filter(Author %in% top_authors) %>%
  count(Author, dominant_topic, topic_label, sort = TRUE) %>%
  group_by(Author) %>%
  slice_max(n, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  arrange(dominant_topic, desc(n))

cat("Most prolific authors and their primary topic:\n\n")
print(author_dominant, n = 20)
```

---

## 33. Topic Diversity per Volume

Are some volumes thematically narrow (dominated by 1-2 topics) or broad?
Shannon entropy measures diversity: higher = more diverse mix of topics.

```{r topic-diversity, fig.width=10, fig.height=6}
# Calculate Shannon entropy per volume
vol_diversity <- make.dt(stm_model, meta = meta) %>%
  select(starts_with("Topic"), volume_num, year) %>%
  filter(!is.na(volume_num)) %>%
  group_by(volume_num) %>%
  summarize(
    across(starts_with("Topic"), mean, na.rm = TRUE),
    year = first(year),
    n_articles = n(),
    .groups = "drop"
  ) %>%
  rowwise() %>%
  mutate(
    # Shannon entropy across topic proportions
    entropy = {
      props <- c_across(starts_with("Topic"))
      props <- props[props > 0]
      -sum(props * log(props))
    },
    # Normalized to 0-1 scale (max entropy = log(K))
    diversity = entropy / log(chosen_K)
  ) %>%
  ungroup()

ggplot(vol_diversity, aes(x = volume_num, y = diversity)) +
  geom_col(aes(fill = diversity), show.legend = FALSE) +
  geom_text(aes(label = round(diversity, 2)), vjust = -0.3, size = 2.5) +
  labs(
    title = "Topic Diversity per Volume",
    subtitle = "Higher = more thematically diverse (Shannon entropy, normalized)",
    x = "Volume",
    y = "Diversity (0 = one topic dominates, 1 = perfectly even)"
  ) +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold")) +
  scale_fill_gradient(low = "#FDDBC7", high = "#8B4513") +
  scale_y_continuous(limits = c(0, 1.1))
```

---

## 34. Ridgeline Plot - Topic Proportion Distributions

Shows the *spread* of topic proportions across all articles, not just
averages. Some topics may have tight distributions (consistent presence)
while others have long tails (a few articles are heavily about that topic).

```{r ridgeline, fig.width=10, fig.height=8}
library(ggridges)

ridge_data <- topic_article_link %>%
  mutate(topic_label_full = paste0("T", topic_num, ": ", topic_label))

ggplot(ridge_data, aes(x = proportion, y = reorder(topic_label_full, topic_num),
                        fill = after_stat(x))) +
  geom_density_ridges_gradient(scale = 2.5, rel_min_height = 0.01,
                                gradient_lwd = 0.3) +
  scale_fill_gradient(low = "#FDDBC7", high = "#8B4513", guide = "none") +
  labs(
    title = "Distribution of Topic Proportions Across Articles",
    subtitle = "Long right tails = some articles are strongly about that topic",
    x = "Topic Proportion",
    y = NULL
  ) +
  theme_minimal(base_size = 11) +
  theme(
    plot.title = element_text(face = "bold", size = 14),
    axis.text.y = element_text(size = 8)
  ) +
  scale_x_continuous(labels = percent_format(), limits = c(0, NA))
```

---

## 35. Topic Dendrogram

Hierarchical clustering showing which topics are most similar to each
other based on their word distributions.

```{r dendrogram, fig.width=10, fig.height=6}
# Get topic-word matrix (beta)
topic_word_matrix <- exp(stm_model$beta$logbeta[[1]])

# Distance between topics based on word distributions
topic_dist <- dist(topic_word_matrix, method = "euclidean")
topic_clust <- hclust(topic_dist, method = "ward.D2")

# Rename labels
topic_clust$labels <- paste0("T", 1:chosen_K, ": ", topic_labels)

par(mar = c(2, 4, 3, 12))
plot(as.dendrogram(topic_clust),
     horiz = TRUE,
     main = "Topic Similarity Dendrogram",
     xlab = "Distance",
     cex = 0.8)
par(mar = c(5, 4, 4, 2))
```

---

## 36. Within-Topic Vocabulary Comparison (Early vs Late Period)

When the same topic appears across both eras of the Exponent, does the
**language** shift? This reveals how the publication's framing of shared
concerns evolved over time.

```{r vocab-comparison-era, fig.width=16, fig.height=20}
cat(rep("=", 70), "\n", sep = "")
cat("WITHIN-TOPIC VOCABULARY COMPARISON (EARLY vs LATE)\n")
cat(rep("=", 70), "\n\n", sep = "")

# Split into early and late eras at median year
median_year <- median(meta$year, na.rm = TRUE)
doc_topics_era <- doc_topics %>%
  mutate(era = ifelse(year <= median_year, "Early", "Late"))

cat("Era split at year", median_year, "\n")
cat("  Early:", sum(doc_topics_era$era == "Early"), "documents\n")
cat("  Late: ", sum(doc_topics_era$era == "Late"), "documents\n\n")

# Function: get word frequencies for top-quartile docs of a topic in an era
# (includes OCR junk filtering as safety net even though stopwords catch most)
get_topic_words_by_era <- function(topic_num, era_name) {
  topic_col <- paste0("Topic", topic_num)
  era_docs <- doc_topics_era %>% filter(era == era_name)
  threshold <- quantile(era_docs[[topic_col]], 0.75, na.rm = TRUE)

  doc_ids <- era_docs %>%
    filter(.data[[topic_col]] >= threshold) %>%
    pull(doc_id)

  words <- processed_texts %>%
    filter(doc_id %in% doc_ids) %>%
    pull(text_final) %>%
    paste(collapse = " ") %>%
    str_split("\\s+") %>%
    `[[`(1)

  freq <- sort(table(words), decreasing = TRUE)
  tibble(word = names(freq), count = as.integer(freq)) %>%
    mutate(proportion = count / sum(count)) %>%
    filter(
      nchar(word) >= 4,
      !word %in% all_stopwords,
      !is_ocr_fragment(word)
    )
}

# Pick the 6 most prevalent topics for comparison
top_6_for_vocab <- order(topic_props, decreasing = TRUE)[1:min(6, chosen_K)]

cat("Comparing vocabulary for top", length(top_6_for_vocab), "topics:\n")
for (t in top_6_for_vocab) {
  cat(sprintf("  T%d: %s\n", t, topic_labels[t]))
}
cat("\n")

# Build log-ratio plots
vocab_plots <- list()
for (idx in seq_along(top_6_for_vocab)) {
  t <- top_6_for_vocab[idx]

  words_early <- get_topic_words_by_era(t, "Early")
  words_late  <- get_topic_words_by_era(t, "Late")

  word_compare <- full_join(
    words_early %>% select(word, early_prop = proportion),
    words_late  %>% select(word, late_prop = proportion),
    by = "word"
  ) %>%
    replace_na(list(early_prop = 0.0001, late_prop = 0.0001)) %>%
    mutate(
      log_ratio = log2(early_prop / late_prop),
      avg_prop = (early_prop + late_prop) / 2
    ) %>%
    filter(avg_prop > 0.001) %>%
    arrange(desc(abs(log_ratio)))

  # Top 20 words each direction
  top_early <- word_compare %>% filter(log_ratio > 0) %>% head(20)
  top_late  <- word_compare %>% filter(log_ratio < 0) %>% head(20)
  plot_words <- bind_rows(top_early, top_late) %>%
    mutate(
      direction = ifelse(log_ratio > 0,
                         paste0("More in Early (\u2264", median_year, ")"),
                         paste0("More in Late (>", median_year, ")")),
      word = reorder(word, log_ratio)
    )

  early_label <- paste0("More in Early (\u2264", median_year, ")")
  late_label  <- paste0("More in Late (>", median_year, ")")

  p <- ggplot(plot_words, aes(x = log_ratio, y = word, fill = direction)) +
    geom_col(alpha = 0.8) +
    geom_vline(xintercept = 0, linewidth = 0.8) +
    scale_fill_manual(values = setNames(c("#CD661D", "#8B4513"),
                                        c(early_label, late_label))) +
    labs(title = paste0("T", t, ": ", str_trunc(topic_labels[t], 35)),
         x = "Log2 Ratio (Early / Late)", y = NULL, fill = NULL) +
    theme_minimal(base_size = 8) +
    theme(legend.position = "none",
          plot.title = element_text(size = 10, face = "bold"))

  vocab_plots[[idx]] <- p
}

# Combine plots
if (length(vocab_plots) >= 6) {
  (vocab_plots[[1]] | vocab_plots[[2]] | vocab_plots[[3]]) /
  (vocab_plots[[4]] | vocab_plots[[5]] | vocab_plots[[6]]) +
    plot_annotation(
      title = "Within-Topic Vocabulary Shifts: Early vs Late Period",
      subtitle = paste0("Top 20 words each era emphasizes differently (split at ",
                        median_year, ")"),
      theme = theme(plot.title = element_text(size = 16, face = "bold"))
    )
} else if (length(vocab_plots) >= 1) {
  wrap_plots(vocab_plots, ncol = min(3, length(vocab_plots))) +
    plot_annotation(title = "Within-Topic Vocabulary Shifts: Early vs Late Period")
}
```

---

## 37. Topic Diversity & Concentration (Document-Level)

Section 33 measures diversity per *volume*. This section measures it per
*document*: is the typical article about one topic or several?

```{r doc-level-diversity, fig.width=12, fig.height=10}
cat(rep("=", 70), "\n", sep = "")
cat("DOCUMENT-LEVEL TOPIC DIVERSITY\n")
cat(rep("=", 70), "\n\n", sep = "")

# Shannon entropy per document (higher = more diverse)
doc_entropy <- doc_topics %>%
  select(doc_id, starts_with("Topic")) %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "p") %>%
  filter(p > 0) %>%
  group_by(doc_id) %>%
  summarize(entropy = -sum(p * log2(p)), .groups = "drop")

# Gini concentration per document
doc_gini <- doc_topics %>%
  select(doc_id, starts_with("Topic")) %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "p") %>%
  group_by(doc_id) %>%
  summarize(
    max_topic_prop = max(p),
    gini = 1 - sum(p^2),
    .groups = "drop"
  )

# Summary
diversity_summary <- doc_entropy %>%
  left_join(doc_gini, by = "doc_id") %>%
  summarize(
    mean_entropy = mean(entropy),
    sd_entropy = sd(entropy),
    mean_gini = mean(gini),
    mean_max_prop = mean(max_topic_prop),
    pct_strong_exemplar = mean(max_topic_prop >= 0.4) * 100
  )

cat("Diversity Metrics (Woman's Exponent):\n\n")
cat(sprintf("  Mean Shannon Entropy:     %.2f bits\n", diversity_summary$mean_entropy))
cat(sprintf("  SD Entropy:               %.2f\n", diversity_summary$sd_entropy))
cat(sprintf("  Mean Gini (inv-Herf):     %.3f\n", diversity_summary$mean_gini))
cat(sprintf("  Mean Dominant Topic %%:    %.1f%%\n", diversity_summary$mean_max_prop * 100))
cat(sprintf("  Strong Exemplars (>40%%):  %.1f%% of documents\n\n", diversity_summary$pct_strong_exemplar))

# Entropy distribution
p1 <- ggplot(doc_entropy, aes(x = entropy)) +
  geom_density(fill = "#CD661D", alpha = 0.5, linewidth = 0.8, color = "#8B4513") +
  labs(title = "Topic Diversity per Document",
       subtitle = "Higher entropy = article discusses more topics evenly",
       x = "Shannon Entropy (bits)", y = "Density") +
  theme_minimal(base_size = 12)

# Dominant topic concentration
p2 <- ggplot(doc_gini, aes(x = max_topic_prop)) +
  geom_density(fill = "#CD661D", alpha = 0.5, linewidth = 0.8, color = "#8B4513") +
  geom_vline(xintercept = 0.4, linetype = "dashed", color = "grey40") +
  ggplot2::annotate("text", x = 0.42, y = 0, label = "Exemplar\nthreshold", size = 3, hjust = 0) +
  labs(title = "Topic Concentration per Document",
       subtitle = "Higher = article dominated by single topic; dashed line = 40% exemplar threshold",
       x = "Dominant Topic Proportion", y = "Density") +
  theme_minimal(base_size = 12) +
  scale_x_continuous(labels = percent_format())

p1 / p2
```

### Effective Number of Topics

```{r effective-topics-we, fig.width=10, fig.height=5}
# Publication-level topic distribution
pub_topic_dist <- doc_topics %>%
  summarize(across(starts_with("Topic"), mean)) %>%
  pivot_longer(everything(), names_to = "topic", values_to = "prevalence") %>%
  mutate(
    topic_num = as.integer(str_remove(topic, "Topic")),
    label = str_trunc(topic_labels[topic_num], 25)
  )

# Effective number of topics = exp(entropy of topic distribution)
eff_topics <- pub_topic_dist %>%
  filter(prevalence > 0) %>%
  summarize(eff = exp(-sum(prevalence * log(prevalence)))) %>%
  pull(eff)

cat(sprintf("Effective number of topics: %.1f (of %d)\n\n", eff_topics, chosen_K))

ggplot(pub_topic_dist, aes(x = reorder(label, -prevalence), y = prevalence)) +
  geom_col(fill = "#CD661D", alpha = 0.8) +
  labs(title = "Topic Weight Distribution \u2014 Woman's Exponent",
       subtitle = paste0("Effective topics: ", round(eff_topics, 1), " of ", chosen_K),
       x = NULL, y = "Mean Proportion") +
  theme_minimal(base_size = 10) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8)) +
  scale_y_continuous(labels = percent_format())
```

---

## 38. Topic Prevalence Heatmap Over Time

```{r topic-heatmap-time, fig.width=12, fig.height=7}
# Yearly topic prevalence
yearly_topics_we <- doc_topics %>%
  filter(!is.na(year)) %>%
  select(year, starts_with("Topic")) %>%
  group_by(year) %>%
  summarize(across(starts_with("Topic"), mean), .groups = "drop") %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "prevalence") %>%
  mutate(
    topic_num = as.integer(str_remove(topic, "Topic")),
    short_label = paste0("T", topic_num, ": ", str_trunc(topic_labels[topic_num], 20))
  )

ggplot(yearly_topics_we, aes(x = year, y = short_label, fill = prevalence)) +
  geom_tile(color = "white", linewidth = 0.3) +
  scale_fill_gradient(low = "white", high = "#8B4513",
                      labels = percent_format()) +
  labs(title = "Topic Prevalence Over Time \u2014 Woman's Exponent",
       subtitle = "Darker = higher prevalence in that year",
       x = "Year", y = NULL, fill = "Prevalence") +
  theme_minimal(base_size = 11) +
  theme(panel.grid = element_blank(),
        plot.title = element_text(face = "bold", size = 14)) +
  scale_y_discrete(limits = rev) +
  scale_x_continuous(breaks = sort(unique(yearly_topics_we$year)))
```

---

## 39. Topic Percentage Change (Early vs Late Era)

How much does each topic's prevalence **shift** from the early period to the
late period?

```{r topic-era-change, fig.width=12, fig.height=8}
cat(rep("=", 70), "\n", sep = "")
cat("PERCENTAGE CHANGE IN TOPICS: EARLY vs LATE ERA\n")
cat(rep("=", 70), "\n\n", sep = "")

# Mean prevalence per topic per era
era_means <- doc_topics_era %>%
  group_by(era) %>%
  summarize(across(starts_with("Topic"), mean), .groups = "drop") %>%
  pivot_longer(-era, names_to = "topic", values_to = "prevalence") %>%
  mutate(topic_num = as.integer(str_remove(topic, "Topic"))) %>%
  pivot_wider(names_from = era, values_from = prevalence)

era_change <- era_means %>%
  mutate(
    label = topic_labels[topic_num],
    early_pct = Early * 100,
    late_pct = Late * 100,
    abs_change = late_pct - early_pct,
    pct_change = ifelse(Early > 0.001,
                        (Late - Early) / Early * 100,
                        NA_real_),
    direction = case_when(
      abs_change > 0.5  ~ "Grew in Late Period",
      abs_change < -0.5 ~ "Declined in Late Period",
      TRUE ~ "Stable"
    )
  ) %>%
  arrange(desc(abs_change))

cat(sprintf("Era split: Early (\u2264%d) vs Late (>%d)\n\n", median_year, median_year))
cat(sprintf("%-35s  %7s  %7s  %8s  %9s\n",
            "Topic", "Early%", "Late%", "Change", "% Change"))
cat(rep("-", 80), "\n", sep = "")
for (i in 1:nrow(era_change)) {
  r <- era_change[i, ]
  pct_str <- ifelse(is.na(r$pct_change), "N/A", sprintf("%+.0f%%", r$pct_change))
  cat(sprintf("%-35s  %5.1f%%  %5.1f%%  %+6.1fpp  %9s\n",
              str_trunc(r$label, 35), r$early_pct, r$late_pct, r$abs_change, pct_str))
}

# Absolute change bar chart
p_abs <- era_change %>%
  mutate(display = paste0("T", topic_num, ": ", str_trunc(label, 28)),
         display = reorder(display, abs_change)) %>%
  ggplot(aes(x = abs_change, y = display, fill = direction)) +
  geom_col(alpha = 0.85) +
  geom_vline(xintercept = 0, linewidth = 1) +
  scale_fill_manual(values = c("Grew in Late Period" = "#458B74",
                                "Declined in Late Period" = "#CD661D",
                                "Stable" = "#94a3b8")) +
  labs(title = paste0("Topic Change: Early (\u2264", median_year,
                      ") vs Late (>", median_year, ") Period"),
       subtitle = "Absolute change in percentage points of topic prevalence",
       x = "Change (percentage points)", y = NULL, fill = NULL) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom", panel.grid.major.y = element_blank())

print(p_abs)
```

```{r topic-era-change-relative, fig.width=12, fig.height=8}
# Relative (%) change bar chart
era_change_filtered <- era_change %>%
  filter(!is.na(pct_change), abs(pct_change) < 500) %>%
  mutate(display = paste0("T", topic_num, ": ", str_trunc(label, 28)),
         display = reorder(display, pct_change))

if (nrow(era_change_filtered) > 0) {
  ggplot(era_change_filtered, aes(x = pct_change, y = display, fill = direction)) +
    geom_col(alpha = 0.85) +
    geom_vline(xintercept = 0, linewidth = 1) +
    scale_fill_manual(values = c("Grew in Late Period" = "#458B74",
                                  "Declined in Late Period" = "#CD661D",
                                  "Stable" = "#94a3b8")) +
    labs(title = "Relative Percentage Change in Topic Prevalence",
         subtitle = paste0("How much did each topic grow or shrink relative to its early-period (\u2264",
                           median_year, ") baseline?"),
         x = "Relative Change (%)", y = NULL, fill = NULL) +
    theme_minimal(base_size = 11) +
    theme(legend.position = "bottom", panel.grid.major.y = element_blank())
}
```

---

## 40. Topic Evolution Summary

```{r evolution-summary, fig.width=10, fig.height=10}
cat(rep("=", 70), "\n", sep = "")
cat("TOPIC EVOLUTION SUMMARY\n")
cat(rep("=", 70), "\n\n", sep = "")

topic_evolution <- era_change %>%
  mutate(
    evolution_type = case_when(
      abs(abs_change) <= 0.5 ~ "Stable",
      abs_change > 0.5  ~ "Growing",
      abs_change < -0.5 ~ "Declining"
    ),
    evolution_type = factor(evolution_type,
                            levels = c("Stable", "Growing", "Declining"))
  )

cat("TOPIC EVOLUTION CLASSIFICATION:\n\n")
for (etype in c("Stable", "Growing", "Declining")) {
  cat(toupper(etype), ":\n")
  subset_ev <- topic_evolution %>% filter(evolution_type == etype)
  if (nrow(subset_ev) > 0) {
    for (i in 1:nrow(subset_ev)) {
      r <- subset_ev[i, ]
      cat(sprintf("  T%d: %s (Early: %.1f%%, Late: %.1f%%, %+.1fpp)\n",
                  r$topic_num, r$label, r$early_pct, r$late_pct, r$abs_change))
    }
  } else {
    cat("  (none)\n")
  }
  cat("\n")
}

# Scatter plot: early vs late prevalence
ggplot(topic_evolution, aes(x = early_pct, y = late_pct, color = evolution_type)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed",
              color = "grey70", linewidth = 1) +
  geom_point(size = 5, alpha = 0.8) +
  geom_text_repel(aes(label = paste0("T", topic_num, ": ", str_trunc(label, 25))),
                  size = 3, max.overlaps = 20, show.legend = FALSE) +
  scale_color_manual(values = c(
    "Stable" = "#6495ED",
    "Growing" = "#458B74",
    "Declining" = "#CD661D"
  )) +
  labs(title = "Topic Evolution: Early vs Late Period",
       subtitle = paste0("Diagonal = no change | Above = grew in late period (",
                         median_year + 1, "-", max(meta$year, na.rm = TRUE),
                         ") | Below = declined"),
       x = paste0("Early Period Mean % (\u2264", median_year, ")"),
       y = paste0("Late Period Mean % (>", median_year, ")"),
       color = "Evolution Type") +
  theme_minimal(base_size = 13) +
  theme(legend.position = "bottom",
        plot.title = element_text(face = "bold", size = 16)) +
  coord_fixed()
```

---

## 41. Representative Passages

Extracts the most representative sentences from top articles for each
topic -- ready to quote in your dissertation.

```{r representative-passages}
cat("REPRESENTATIVE PASSAGES PER TOPIC\n")
cat(rep("=", 70), "\n\n", sep = "")

# For each topic, get top 3 articles, extract best sentences
for (t in 1:chosen_K) {
  cat("TOPIC", t, ":", topic_labels[t], "\n")
  cat(rep("-", 60), "\n", sep = "")

  # Get top 3 articles for this topic
  top_docs <- topic_article_link %>%
    filter(topic_num == t) %>%
    head(3)

  # Get the topic's top words for sentence scoring
  topic_words <- tolower(all_top_words$frex[t, 1:15])

  for (j in 1:nrow(top_docs)) {
    fname <- top_docs$filename[j]
    title_str <- ifelse(is.na(top_docs$Title[j]), fname, top_docs$Title[j])

    # Find and read the file
    match_file <- list.files(input_path, pattern = fixed(fname),
                             recursive = TRUE, full.names = TRUE)
    if (length(match_file) == 0) next

    full_text <- read_file(match_file[1])

    # Split into sentences, score by topic word density
    sentences <- str_split(full_text, "(?<=[.!?])\\s+")[[1]]
    sentences <- sentences[nchar(sentences) > 40 & nchar(sentences) < 500]

    if (length(sentences) == 0) next

    scores <- sapply(sentences, function(s) {
      words <- tolower(str_split(s, "\\s+")[[1]])
      sum(words %in% topic_words) / max(length(words), 1)
    })

    best_idx <- order(scores, decreasing = TRUE)[1]
    best_sentence <- str_squish(sentences[best_idx])

    cat(sprintf("\n  [%s] (%.1f%% Topic %d)\n",
                title_str, top_docs$proportion[j] * 100, t))
    cat("  \"", str_trunc(best_sentence, 300), "\"\n", sep = "")
  }
  cat("\n\n")
}
```

---

## 42. Export Results

```{r export-results}
# 1. Full topic-article link (all documents x all topics)
full_export <- topic_article_link %>%
  mutate(proportion_pct = round(proportion * 100, 2))

write_csv(full_export,
          file.path(output_path, "topic_article_full_link.csv"))

# 2. Top articles per topic (best exemplars)
exemplars <- topic_article_link %>%
  group_by(topic_num, topic_label) %>%
  slice_max(proportion, n = 25) %>%
  ungroup() %>%
  mutate(proportion_pct = round(proportion * 100, 2))

write_csv(exemplars,
          file.path(output_path, "topic_exemplar_articles.csv"))

# 3. Topic summary with labels and words
topic_summary <- tibble(
  topic_num = 1:chosen_K,
  label = topic_labels,
  prevalence_pct = round(topic_props * 100, 2),
  frex_words = apply(all_top_words$frex, 1, function(x) paste(x, collapse = ", ")),
  prob_words = apply(all_top_words$prob, 1, function(x) paste(x, collapse = ", "))
)

write_csv(topic_summary,
          file.path(output_path, "topic_summary.csv"))

# 4. Dominant topic assignments (one row per article)
write_csv(dominant_topics,
          file.path(output_path, "dominant_topic_per_article.csv"))

# 5. Strong exemplars only
strong_only <- dominant_topics %>% filter(strong_exemplar)
write_csv(strong_only,
          file.path(output_path, "strong_exemplars.csv"))

cat("Exported to:", output_path, "\n")
cat("  - topic_article_full_link.csv (all doc-topic proportions)\n")
cat("  - topic_exemplar_articles.csv (top 25 articles per topic)\n")
cat("  - topic_summary.csv (labels + words)\n")
cat("  - dominant_topic_per_article.csv (each article tagged with its strongest topic)\n")
cat("  - strong_exemplars.csv (articles >", exemplar_threshold * 100, "% in their dominant topic)\n")
```

---

## 43. Read a Specific Article

Use this to quickly read the text of any article you've identified as an exemplar.

```{r read-article-function}
read_article <- function(fname, input_dir = input_path) {
  # Find the file
  match <- list.files(input_dir, pattern = fixed(fname), recursive = TRUE, full.names = TRUE)
  if (length(match) == 0) {
    cat("File not found:", fname, "\n")
    return(invisible(NULL))
  }
  txt <- read_file(match[1])
  # Print first 500 chars
  cat(rep("=", 70), "\n", sep = "")
  cat("File:", fname, "\n")
  cat(rep("=", 70), "\n\n", sep = "")
  cat(substr(txt, 1, 2000), "\n\n...")
  return(invisible(txt))
}

# Example: read the top article from Topic 1
top1 <- topic_article_link %>% filter(topic_num == 1) %>% head(1)
read_article(top1$filename)
```

---

## 44. Save Session

```{r save-session}
save(stm_model, docs, vocab, meta, raw_texts, processed_texts,
     all_stopwords, topic_labels, topic_article_link,
     dominant_topics, inventory_subset,
     file = file.path(output_path, paste0("topic_linker_session_K", chosen_K, ".RData")))

cat("Session saved. Reload with:\n")
cat('  load("', file.path(output_path, paste0("topic_linker_session_K", chosen_K, ".RData")), '")\n', sep = "")
```

---

## Quick Reference

After running this notebook, use the exported CSVs:

- **`topic_exemplar_articles.csv`** - Open this to see the top 25 articles for each topic. These are your best evidentiary examples.
- **`topic_article_full_link.csv`** - Full matrix if you need to find any article's topic distribution.
- **`topic_summary.csv`** - Quick reference for topic labels and key words.

To read a specific article in R:
```r
read_article("WE_Vol32_1903_Issue1_002_WOMANHOOD.txt")
```

```{r session-info}
sessionInfo()
```
