---
title: "STM Topic Modeling - Final Working Version"
author: "Your Name"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: show
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# STM Topic Modeling - Final Working Version

Stopwords properly removed + manual K selection

---

## 1. Load Packages

```{r load-packages}
library(stm)
library(tidyverse)
library(stopwords)
library(stm)
library(quanteda)

set.seed(12345)
cat("Packages loaded!\n")
```

---

## 2. Import Files

```{r import-files}
# EDIT THIS PATH
folder_path <- "C:/Users/birch/OneDrive - George Mason University - O365 Production/Dissertation/textanalysis/Topicmodel/input/"

all_files <- list.files(path = folder_path, full.names = TRUE, recursive = TRUE)
file_paths <- all_files[grepl("\\.txt$", all_files, ignore.case = TRUE)]

cat("Files found:", length(file_paths), "\n")
```

---

## 3. Sample and Read

```{r read-files}
sample_size <- min(300, length(file_paths))
set.seed(123)
sampled_paths <- sample(file_paths, size = sample_size)

raw_texts <- tibble(
  filepath = sampled_paths,
  filename = basename(sampled_paths),
  text = map_chr(sampled_paths, ~read_file(.x))
)

# Extract metadata
raw_texts <- raw_texts %>%
  mutate(
    month = str_extract(filename, "^[A-Za-z]+"),
    volume = str_extract(filename, "Vol\\d+"),
    year = as.numeric(str_extract(filepath, "\\d{4}")),
    doc_id = row_number()
  )

cat("Files read:", nrow(raw_texts), "\n")
```

---

## 4. Text Cleaning WITH Stopword Removal

```{r clean-with-stopwords}
cat("\n", rep("=", 70), "\n", sep = "")
cat("TEXT CLEANING WITH STOPWORD REMOVAL\n")
cat(rep("=", 70), "\n\n", sep = "")

# ============================================================================
# CREATE COMPREHENSIVE STOPWORD LIST
# ============================================================================

# Standard English stopwords
standard_stopwords <- stopwords::stopwords("en", source = "snowball")

# Add custom stopwords specific to your corpus
custom_stopwords <- c(
  # Common words
  "the", "of", "and", "in", "to", "a", "is", "that", "it", "for",
  "as", "on", "with", "be", "was", "by", "are", "from", "or", "an",
  "at", "this", "which", "have", "has", "had", "but", "not", "can",
  "will", "been", "were", "their", "they", "we", "our", "would",
  "there", "what", "so", "if", "who", "than", "may", "also",
  
  # Titles and honorifics (if you want to remove these)
  "mrs", "mr", "miss", "dr", "ms",
  
  # Month names (if you want to remove)
  "january", "february", "march", "april", "may", "june",
  "july", "august", "september", "october", "november", "december",
  
  # Add more domain-specific words here:
  "vol", "page", "number"
)

# Combine and remove duplicates
all_stopwords <- unique(c(standard_stopwords, custom_stopwords))

cat("Total stopwords to remove:", length(all_stopwords), "\n\n")

# ============================================================================
# APPLY CLEANING
# ============================================================================

processed_texts <- raw_texts %>%
  mutate(
    # Step 1: Basic cleaning
    text_clean = str_to_lower(text),
    text_clean = str_remove_all(text_clean, "http\\S+"),
    text_clean = str_remove_all(text_clean, "[[:punct:]]"),
    text_clean = str_squish(text_clean),
    
    # Step 2: Split into words
    words = str_split(text_clean, "\\s+"),
    
    # Step 3: Remove stopwords
    words_no_stop = map(words, ~.x[!.x %in% all_stopwords]),
    
    # Step 4: Remove short words (< 3 characters)
    words_final = map(words_no_stop, ~.x[nchar(.x) >= 3]),
    
    # Step 5: Rejoin
    text_final = map_chr(words_final, ~paste(.x, collapse = " ")),
    
    # Count final words
    final_word_count = str_count(text_final, "\\S+")
  )

cat("Cleaning results:\n")
cat("  Avg words before:", round(mean(str_count(raw_texts$text, "\\S+"))), "\n")
cat("  Avg words after:", round(mean(processed_texts$final_word_count)), "\n")

# Filter out very short documents
cat("\nFiltering short documents...\n")
cat("Before:", nrow(processed_texts), "documents\n")

processed_texts <- processed_texts %>%
  filter(final_word_count >= 20)

cat("After:", nrow(processed_texts), "documents\n\n")

# Show example
cat("EXAMPLE - First document transformation:\n")
cat(rep("-", 70), "\n", sep = "")
cat("BEFORE:\n", substr(raw_texts$text[1], 1, 300), "...\n\n")
cat("AFTER:\n", substr(processed_texts$text_final[1], 1, 300), "...\n")
cat(rep("-", 70), "\n\n", sep = "")
```

---

## 5. Prepare for STM

```{r prepare-stm}
cat("Filtering documents...\n")
cat("Before:", nrow(processed_texts), "documents\n")

# CHANGE THIS - make it more lenient
min_words <- 5  # CHANGED FROM 10 TO 5

processed_texts <- processed_texts %>%
  filter(final_word_count >= min_words)

cat("After (>= ", min_words, " words):", nrow(processed_texts), "documents\n")
cat("Removed:", nrow(raw_texts) - nrow(processed_texts), "documents\n\n")

if (nrow(processed_texts) == 0) {
  cat("\n❌ ALL DOCUMENTS REMOVED!\n\n")
  stop("No documents remaining")
}
```

---

## 6. Search for Optimal K (Optional)

You can use this to explore different K values, OR skip to Section 7 to set K manually.

```{r search-k-optional, eval=FALSE}
cat("Preparing for STM...\n\n")

processed <- textProcessor(
  documents = processed_texts$text_final,
  metadata = processed_texts %>% select(doc_id, month, volume, year, filename),
  lowercase = FALSE,
  removestopwords = FALSE,
  removenumbers = FALSE,
  removepunctuation = FALSE,
  stem = FALSE,
  wordLengths = c(2, Inf),  # CHANGED: Accept 2+ character words
  sparselevel = 1,
  language = "en",
  verbose = TRUE
)

cat("\n")
cat("After textProcessor:\n")
cat("  Documents:", length(processed$documents), "\n")
cat("  Vocab:", length(processed$vocab), "\n\n")

# ULTRA-LENIENT prepDocuments
out <- prepDocuments(
  documents = processed$documents,
  vocab = processed$vocab,
  meta = processed$meta,
  lower.thresh = 1,      # Keep words in 1+ documents
  upper.thresh = Inf     # No upper limit - keep everything!
)

docs <- out$documents
vocab <- out$vocab
meta <- out$meta

cat("\n", rep("=", 70), "\n", sep = "")
cat("FINAL CORPUS\n")
cat(rep("=", 70), "\n\n", sep = "")

cat("Documents:", length(docs), "\n")
cat("Vocabulary:", length(vocab), "\n")
cat("Metadata rows:", nrow(meta), "\n\n")

if (length(docs) == 0 || nrow(meta) == 0) {
  cat("❌ PROBLEM DETECTED!\n\n")
  cat("Debug info:\n")
  cat("  Input to prepDocuments:", length(processed$documents), "documents\n")
  cat("  Output from prepDocuments:", length(docs), "documents\n")
  
  stop("prepDocuments removed all documents!")
}

cat("Sample vocabulary:\n")
cat(paste(vocab[1:min(50, length(vocab))], collapse = ", "), "\n")

cat("\n", rep("=", 70), "\n\n", sep = "")

```

## 7. SET YOUR K VALUE MANUALLY

```{r set-k-manually}
# ============================================================================
# MANUALLY SET K HERE
# ============================================================================

# CHANGE THIS NUMBER to whatever K you want
chosen_K <- 20

# You can change this anytime and re-run from here

cat("You have chosen K =", chosen_K, "\n")
cat("This will create", chosen_K, "topics\n\n")
```
```{r}
# Check and fix metadata before fitting model
cat("Checking metadata...\n")

# Check year column
cat("Year column type:", class(meta$year), "\n")
cat("Year values:", paste(unique(meta$year), collapse = ", "), "\n")
cat("Any NAs in year?", any(is.na(meta$year)), "\n\n")

# Fix year if needed
meta <- meta %>%
  mutate(
    year = as.numeric(year),
    year = ifelse(is.na(year), median(year, na.rm = TRUE), year)  # Replace NAs with median
  )

# Check all columns
str(meta)
```

---

## 8. Fit STM Model with Your Chosen K

```{r fit-model, cache=TRUE}
cat(rep("=", 70), "\n", sep = "")
cat("FITTING STM MODEL WITH K =", chosen_K, "\n")
cat(rep("=", 70), "\n\n", sep = "")

stm_model <- stm(
  documents = docs,
  vocab = vocab,
  K = chosen_K,
  data = meta,
  max.em.its = 75,
  init.type = "Spectral",
  seed = 12345,
  verbose = TRUE
)

saveRDS(stm_model, paste0("stm_model_K", chosen_K, ".rds"))
cat("\nModel saved to 'stm_model_K", chosen_K, ".rds'\n")
```

---

## 9. Examine Topics

```{r examine-topics}
cat("\n", rep("=", 70), "\n", sep = "")
cat("TOP WORDS FOR EACH TOPIC\n")
cat(rep("=", 70), "\n\n", sep = "")

# Show top 15 words per topic
labelTopics(stm_model, n = 15)
```

---

## 10. Create Topic Labels

```{r create-labels}
# After examining the top words above, create meaningful labels
# EDIT THESE based on what you see

topic_labels <- c(
  "Topic 1: [Your Label]",
  "Topic 2: [Your Label]",
  "Topic 3: [Your Label]",
  "Topic 4: [Your Label]",
  "Topic 5: [Your Label]",
  "Topic 6: [Your Label]",
  "Topic 7: [Your Label]",
  "Topic 8: [Your Label]",
  "Topic 9: [Your Label]",
  "Topic 10: [Your Label]",
  "Topic 11: [Your Label]",
  "Topic 12: [Your Label]",
  "Topic 13: [Your Label]",
  "Topic 14: [Your Label]",
  "Topic 15: [Your Label]"
)[1:chosen_K]  # Only use as many as chosen_K

cat("\nTopics with top words:\n")
cat(rep("=", 70), "\n\n", sep = "")

for (i in 1:chosen_K) {
  cat(topic_labels[i], "\n")
  cat("  ", paste(labelTopics(stm_model, topics = i, n = 7)$prob[1,], 
                   collapse = ", "), "\n\n")
}
```

---

## 11. Find Example Documents

```{r find-examples}
topic_to_examine <- 1  # Change this to examine different topics

cat("Example documents for Topic", topic_to_examine, ":\n")
cat(rep("=", 70), "\n\n", sep = "")

thoughts <- findThoughts(
  model = stm_model,
  texts = processed_texts$text_final,
  topics = topic_to_examine,
  n = 3
)

for (i in 1:3) {
  cat("Example", i, ":\n")
  cat(substr(thoughts$docs[[1]][i], 1, 250), "...\n\n")
}
```

---

## 12. Visualizations

### Topic Prevalence

```{r plot-prevalence, fig.width=10, fig.height=6}
plot(stm_model, 
     type = "summary", 
     n = min(10, chosen_K),
     main = paste("Topic Prevalence (K =", chosen_K, ")"),
     xlim = c(0, 0.3))
```

### Topic Correlation Network

```{r plot-correlation, fig.width=10, fig.height=8}
mod.out.corr <- topicCorr(stm_model)
plot(mod.out.corr, main = "Topic Correlation Network")
```

### Word Cloud for Topic 1

```{r wordcloud, fig.width=8, fig.height=6}
cloud(stm_model, 
      topic = 1,
      scale = c(3, 0.5),
      main = "Word Cloud - Topic 1")
```

### Topic Quality

```{r topic-quality, fig.width=8, fig.height=6}
topicQuality(stm_model, documents = docs)
```

### Compare Two Topics

```{r compare-topics, fig.width=10, fig.height=6}
plot(stm_model, 
     type = "perspectives", 
     topics = c(1, 5),
     main = "Comparing Topics 1 and 5")
```

---

## 13. Export Results

```{r export-results}
# Document-topic proportions
doc_topics <- make.dt(stm_model, meta = meta)
write_csv(doc_topics, paste0("document_topics_K", chosen_K, ".csv"))

# Top words per topic
top_words <- labelTopics(stm_model, n = 20)
topic_words_df <- tibble(
  topic = 1:chosen_K,
  label = topic_labels,
  top_words = apply(top_words$prob, 1, function(x) paste(x, collapse = ", "))
)
write_csv(topic_words_df, paste0("topic_words_K", chosen_K, ".csv"))

cat("Results exported!\n")
cat("  - document_topics_K", chosen_K, ".csv\n")
cat("  - topic_words_K", chosen_K, ".csv\n")
```

---

## 14. Save Session

```{r save-session}
save(stm_model, docs, vocab, meta, 
     raw_texts, processed_texts, all_stopwords,
     file = paste0("stm_session_K", chosen_K, ".RData"))

cat("Session saved to 'stm_session_K", chosen_K, ".RData'\n")
```

---

## How to Use This Notebook:

### To Change K:
1. Go to **Section 7**
2. Change `chosen_K <- 15` to whatever you want (e.g., `chosen_K <- 20`)
3. Re-run from **Section 8** onwards

### To Add More Stopwords:
1. Go to **Section 4**
2. Add words to the `custom_stopwords` list:
   ```r
   custom_stopwords <- c(
     custom_stopwords,
     "your", "new", "words", "here"
   )
   ```
3. Re-run from **Section 4** onwards

### To Adjust Filtering:
In **Section 5**, change:
```r
lower.thresh = 5   # Change to 3 (more words) or 10 (fewer words)
upper.thresh = 0.95  # Change to 0.90 or 0.98
```

## Session Info

```{r session-info}
sessionInfo()
```
