
---
title: "Topic-to-Article Linker - Relief Society Magazine"
author: "Birch"
date: "`r Sys.Date()`"
output:
  html_notebook:
    toc: true
    toc_float: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Topic-to-Article Linker - Relief Society Magazine

This notebook runs STM topic modeling on whatever RSM volumes are placed in the
input folder, then links each topic back to specific articles from the inventory
so you can identify concrete evidentiary examples for each topic bucket.
Drop Vol##_#### folders into the input directory and run.

---

## 1. Load Packages

```{r load-packages}
install.packages(c("stm", "tidyverse", "readxl", "stopwords", "igraph", "DT",
                 "textstem", "pheatmap", "scales", "wordcloud", "ggridges", "patchwork",
                 "ggrepel"))
install.packages("tm")

```


```{r}
library(stm)
library(tidyverse)
library(readxl)
library(stopwords)
library(igraph)
library(DT)
library(textstem)    # For lemmatization
library(pheatmap)    # For heatmaps
library(scales)      # For percent formatting
library(wordcloud)
library(ggridges)    # For ridgeline plots
library(patchwork)   # For plot composition (|, /)
library(ggrepel)     # For labeled scatter points
library(tm)

set.seed(12345)
cat("Packages loaded.\n")
```

---

## 2. Set Paths

```{r set-paths}
cat(Sys.getenv("HOME"), "\n")

input_path <- "/home/rbirch/Topicmodel/input2"

output_path <- "/home/rbirch/Topicmodel/output_linked_RSM"

inventory_path <- "/home/rbirch/rbirch/Articleextractionrfiles/Administrationorganization/RSM_article_inventory_vols1-57.xlsx"

if (!dir.exists(output_path)) {
  dir.create(output_path, recursive = TRUE)
}

cat("Input:    ", input_path, "\n")
cat("Output:   ", output_path, "\n")
cat("Inventory:", inventory_path, "\n")
```

---
```{r}
# Check if anything exists at that path
file.exists("/home/birch/path/to/input2")
dir.exists("/home/birch/path/to/input2")

# Search from home for any .txt files
head(list.files(Sys.getenv("HOME"), pattern = "\\.txt$", recursive = TRUE), 20)
list.files("~/Topicmodel/input2", recursive = FALSE)

# Confirm the full path
list.dirs("~/Topicmodel/input2", recursive = FALSE, full.names = FALSE)

```


## 3. Load Article Inventory

```{r load-inventory}
# See what's actually in the folder
inventory <- read_excel(inventory_path, sheet = "Article Inventory")

cat("Inventory loaded:", nrow(inventory), "articles\n")
cat("Columns:", paste(names(inventory), collapse = ", "), "\n\n")

# Detect which volumes are in the input folder
input_vol_dirs <- list.dirs(input_path, recursive = FALSE, full.names = FALSE)
input_vol_nums <- as.integer(str_extract(input_vol_dirs, "^\\d+|(?<=Vol)\\d+"))
input_vol_nums <- sort(input_vol_nums[!is.na(input_vol_nums)])

cat("Volumes detected in input:", paste(input_vol_nums, collapse = ", "), "\n")

# Filter inventory to only the volumes present in input
inventory_subset <- inventory %>%
  filter(Volume %in% input_vol_nums)

cat("Matching inventory articles:", nrow(inventory_subset), "\n")
```

---

## 4. Import Article Files

```{r import-files}
all_files <- list.files(path = input_path, full.names = TRUE, recursive = TRUE)
file_paths <- all_files[grepl("\\.txt$", all_files, ignore.case = TRUE)]

# Exclude backup folders, QC reports, cleanup files
file_paths <- file_paths[!grepl("_backups|QC_Report|cleanup", file_paths)]

cat("Total .txt files found:", length(file_paths), "\n\n")

# Read all files and strip the metadata header line
raw_texts <- tibble(
  filepath = file_paths,
  filename = basename(file_paths),
  text = map_chr(file_paths, ~{
    raw <- read_file(.x)
    # Remove bracket header line if present
    str_remove(raw, "^\\[.*?\\]\\s*\\n?")
  })
)

cat("Read", nrow(raw_texts), "files.\n")
```

---

## 5. Extract Metadata & Join to Inventory

```{r extract-metadata}
# Extract metadata from directory structure: Vol{num}_{year}/{Month}/filename
raw_texts <- raw_texts %>%
  mutate(
    # Parse from directory path
    volume_folder = str_extract(filepath, "Vol\\d+_\\d{4}"),
    volume_num = as.integer(str_extract(volume_folder, "(?<=Vol)\\d+")),
    year = as.integer(str_extract(volume_folder, "\\d{4}$")),
    # Month from directory
    month = str_extract(filepath,
      "(?<=/)(January|February|March|April|May|June|July|August|September|October|November|December)(?=/)"),
    doc_id = row_number(),
    word_count = str_count(text, "\\S+")
  )

# Join to inventory by filename
raw_texts <- raw_texts %>%
  left_join(
    inventory_subset %>% select(Filename, Title, Author, Article_Type, Volume, Month, Issue),
    by = c("filename" = "Filename")
  )

match_count <- sum(!is.na(raw_texts$Title))
cat("Matched to inventory:", match_count, "of", nrow(raw_texts), "files\n")
cat("Unmatched:", sum(is.na(raw_texts$Title)), "\n\n")

raw_texts %>%
  filter(!is.na(Title)) %>%
  select(filename, Title, Author, Article_Type, Volume, year) %>%
  head(10) %>%
  print()
```

---

## 5b. Filter Out Non-Content Articles (Optional)

All article types are included by default. Uncomment lines to exclude any.

```{r filter-content}
cat("Article types before filtering:\n")
raw_texts %>%
  count(Article_Type, sort = TRUE) %>%
  print(n = 20)

cat("\n")

# ============================================================
# EXCLUDE THESE ARTICLE TYPES FROM MODELING
# Add types here ONLY if you want to remove them.
# All types are included by default.
# ============================================================
exclude_types <- c(
  "Board",         # Board member roster lists (pure name rosters, not content)
  "Contents"       # Tables of contents (title/page-number lists)
  # "Misc"         # KEPT IN — ads are part of the print culture record
)

exclude_patterns <- c(
  "BOARD",          # Catches board files not matched by Article_Type
  "CONTENTS"        # Catches contents files not matched by Article_Type
)

before_count <- nrow(raw_texts)

raw_texts <- raw_texts %>%
  filter(
    !(Article_Type %in% exclude_types) | is.na(Article_Type)
  ) %>%
  filter(
    !str_detect(filename, paste(c(exclude_patterns, "^$"), collapse = "|"))
  )

cat("Filtered:", before_count - nrow(raw_texts), "documents removed\n")
cat("Remaining:", nrow(raw_texts), "articles for modeling\n\n")

raw_texts <- raw_texts %>%
  mutate(doc_id = row_number())
```

---

## 6. Text Cleaning

```{r clean-text}
standard_stopwords <- stopwords::stopwords("en", source = "snowball")

custom_stopwords <- c(
  "the", "of", "and", "in", "to", "a", "is", "that", "it", "for",
  "as", "on", "with", "be", "was", "by", "are", "from", "or", "an",
  "at", "this", "which", "have", "has", "had", "but", "not", "can",
  "will", "been", "were", "their", "they", "we", "our", "would",
  "there", "what", "so", "if", "who", "than", "may", "also",
  "mrs", "mr", "miss", "dr", "ms",
  "january", "february", "march", "april", "may", "june",
  "july", "august", "september", "october", "november", "december",
  "vol", "page", "number", "volume", "board", "officer", "general",
  "thee", "thou", "whom", "no", "num", "pp", "pg",
  "issue", "nth", "th", "st", "nd", "rd",
  # RSM-specific boilerplate
  "relief", "society", "magazine", "bulletin",
  "latter", "day",
  # Masthead / publication boilerplate
  "editor", "publisher", "publishe", "published", "publish",
  "assistant", "monthly", "salt", "lake", "city", "utah",
  "term", "copy", "year", "month", "cts", "cent",
  "subscription", "subscribe", "postage", "mail", "deliver",
  "advertise", "advertiser", "advertisement", "advertising",
  "rate", "discount", "liberal", "regular", "space", "line",
  "nonpanel", "square", "extra",
  # Table of contents vocabulary
  "content", "contents", "frontmatter", "front", "matter",
  # Common structural words
  "program", "report", "reports", "committee", "meeting",
  "secretary", "sec", "secy", "asst", "pres", "treas",
  "treasurer", "president", "vice"
)

years_as_words <- as.character(unique(na.omit(raw_texts$year)))

# OCR fragment / junk word blacklist — common broken words from digitized text
ocr_junk_stopwords <- c(
  # Suffix-only fragments
  "ing", "tion", "ment", "ness", "ings", "tive", "ance", "ence",
  "ered", "ters", "bers", "dren", "howe", "ould", "ight", "ther",
  "ated", "ting", "ally", "ible", "able", "ious", "eous", "ical",
  "onal", "ship", "ward", "wise", "less",
  # Truncated word fragments from OCR
  "deliv", "presi", "inter", "encour", "terest", "testi",
  "soci", "coun", "chil", "pariel", "organiza", "ganized",
  "ference", "musser", "selion",
  # Structural boilerplate remnants
  "column", "columns", "chapter", "section", "article",
  "continued", "copyright", "printed"
)

all_stopwords <- unique(c(standard_stopwords, custom_stopwords,
                          ocr_junk_stopwords, years_as_words))

# Regex patterns to catch OCR fragments not in the explicit list
is_ocr_fragment <- function(w) {
  grepl("^[a-z]{1,3}(tion|ment|ence|ness|ings|tive|ance)$", w) |
  grepl("^(pre|suf|dis|un|re)[a-z]{0,2}$", w) |
  grepl("^[^a-z]+$", w)
}

processed_texts <- raw_texts %>%
  mutate(
    text_clean = str_to_lower(text),
    text_clean = str_remove_all(text_clean, "http\\S+"),
    text_clean = str_remove_all(text_clean, "\\S+@\\S+"),
    text_clean = str_remove_all(text_clean, "\\bvol\\.?\\s*\\d+\\b"),
    text_clean = str_remove_all(text_clean, "\\bno\\.?\\s*\\d+\\b"),
    text_clean = str_remove_all(text_clean, "\\bp\\.?\\s*\\d+\\b"),
    text_clean = str_remove_all(text_clean, "\\b\\d+\\b"),
    text_clean = str_remove_all(text_clean, "[[:punct:]]"),
    text_clean = str_squish(text_clean),
    words = str_split(text_clean, "\\s+"),
    words_filtered = map(words, ~.x[!.x %in% all_stopwords]),
    words_filtered = map(words_filtered, ~.x[!grepl("^\\d+$", .x)]),
    words_filtered = map(words_filtered, ~.x[nchar(.x) >= 3 & !is_ocr_fragment(.x)]),
    # Lemmatize
    words_lemma = map(words_filtered, ~lemmatize_words(.x)),
    # Re-filter after lemmatization
    words_final = map(words_lemma, ~.x[!.x %in% all_stopwords & nchar(.x) >= 3 & !is_ocr_fragment(.x)]),
    text_final = map_chr(words_final, ~paste(.x, collapse = " ")),
    final_word_count = str_count(text_final, "\\S+")
  )

cat("Avg words before:", round(mean(raw_texts$word_count)), "\n")
cat("Avg words after:", round(mean(processed_texts$final_word_count)), "\n")

processed_texts <- processed_texts %>%
  filter(final_word_count >= 10)

cat("Documents after filtering:", nrow(processed_texts), "\n\n")

# --- Deduplicate near-identical documents ---
# Some articles were split into multiple sub-files with identical text
# (e.g., Guide Lessons _b_a_a, _b_a_b, _b_b, _b_c). These duplicates
# give one piece of content outsized weight in the model.
cat("Deduplicating near-identical documents...\n")
n_before_dedup <- nrow(processed_texts)

processed_texts <- processed_texts %>%
  mutate(text_fingerprint = substr(text_final, 1, 200)) %>%
  group_by(text_fingerprint) %>%
  slice(1) %>%
  ungroup() %>%
  select(-text_fingerprint) %>%
  mutate(doc_id = row_number())

cat("  Removed", n_before_dedup - nrow(processed_texts), "near-duplicate documents\n")
cat("  Corpus after dedup:", nrow(processed_texts), "documents\n")
```

---

## 7. Prepare & Fit STM

```{r prepare-stm}
# Fill NAs in covariates so STM row counts stay consistent
# Use .data$ to avoid conflicts with R's built-in month() function
processed_texts <- processed_texts %>%
  mutate(
    Article_Type = ifelse(is.na(.data$Article_Type), "Unknown", .data$Article_Type),
    year = ifelse(is.na(.data$year), median(.data$year, na.rm = TRUE), .data$year)
  )

# month column may not exist if metadata extraction missed it
if ("month" %in% names(processed_texts)) {
  processed_texts <- processed_texts %>%
    mutate(month = ifelse(is.na(.data$month), "Unknown", .data$month))
} else {
  processed_texts$month <- "Unknown"
}

processed <- textProcessor(
  documents = processed_texts$text_final,
  metadata = processed_texts %>%
    select(doc_id, filename, volume_num, year, month, Title, Author, Article_Type),
  lowercase = FALSE,
  removestopwords = FALSE,
  removenumbers = TRUE,
  removepunctuation = FALSE,
  stem = FALSE,
  wordLengths = c(3, Inf),
  sparselevel = 1,
  language = "en",
  verbose = TRUE
)

out <- prepDocuments(
  documents = processed$documents,
  vocab = processed$vocab,
  meta = processed$meta,
  lower.thresh = 1,
  upper.thresh = Inf
)

docs <- out$documents
vocab <- out$vocab
meta <- out$meta

# Store the texts that actually made it into the model (for findThoughts later)
modeled_texts <- processed_texts$text_final[match(meta$doc_id, processed_texts$doc_id)]
cat("\nCorpus ready:", length(docs), "documents,", length(vocab), "vocab terms\n")
cat("  (dropped", nrow(processed_texts) - length(docs), "documents during preprocessing)\n")

# Ensure meta is exactly aligned with docs (no NAs in covariates)
meta$year <- as.numeric(meta$year)
meta$year[is.na(meta$year)] <- median(meta$year, na.rm = TRUE)
if (is.null(meta$month)) meta$month <- "Unknown"
meta$month[is.na(meta$month)] <- "Unknown"

cat("\nCorpus ready:", length(docs), "documents,", length(vocab), "vocab terms\n")
cat("Meta rows:", nrow(meta), "(should match docs)\n")
```

```{r searchK, cache=TRUE}
# ============================================================
# DIAGNOSTIC: searchK - tests multiple K values
# Shows held-out likelihood, residuals, semantic coherence,
# and lower bound to help justify your choice of K.
# Set eval=FALSE after running once to skip on re-runs.
# ============================================================
cat("Running searchK diagnostic...\n")

K_candidates <- c(5, 7, 10, 12, 15, 20)

searchK_results <- searchK(
  documents = docs,
  vocab = vocab,
  K = K_candidates,
  data = meta,
  prevalence = ~ s(year),
  init.type = "Spectral",
  seed = 12345,
  verbose = TRUE
)

plot(searchK_results)
saveRDS(searchK_results, file.path(output_path, "searchK_results.rds"))
cat("searchK results saved.\n")
```

```{r searchK-sweet-spot, eval=TRUE, fig.width=10, fig.height=6}
# ============================================================
# COHERENCE vs EXCLUSIVITY OVERLAY — Finding the Sweet Spot
# Both metrics on one plot with dual y-axes.
# The crossover/convergence region = optimal K.
# Set eval=FALSE after running once to skip on re-runs.
# ============================================================
if (exists("searchK_results")) {

  # Extract the metrics from searchK output
  sk_data <- data.frame(
    K       = unlist(searchK_results$results$K),
    semcoh  = unlist(searchK_results$results$semcoh),
    exclus  = unlist(searchK_results$results$exclus)
  )

  # Normalize both metrics to 0-1 scale for overlay comparison
  sk_norm <- sk_data %>%
    mutate(
      coherence_norm  = (semcoh - min(semcoh)) / (max(semcoh) - min(semcoh)),
      exclusivity_norm = (exclus - min(exclus)) / (max(exclus) - min(exclus))
    ) %>%
    select(K, coherence_norm, exclusivity_norm) %>%
    pivot_longer(c(coherence_norm, exclusivity_norm),
                 names_to = "metric", values_to = "value") %>%
    mutate(metric = ifelse(metric == "coherence_norm",
                           "Semantic Coherence", "Exclusivity"))

  # Find approximate sweet spot (where lines are closest)
  sweet_spot <- sk_data %>%
    mutate(
      coh_n = (semcoh - min(semcoh)) / (max(semcoh) - min(semcoh)),
      exc_n = (exclus - min(exclus)) / (max(exclus) - min(exclus)),
      gap   = abs(coh_n - exc_n)
    ) %>%
    slice_min(gap, n = 1)

  ggplot(sk_norm, aes(x = K, y = value, color = metric, linetype = metric)) +
    geom_line(linewidth = 1.3) +
    geom_point(size = 3) +
    # Mark the sweet spot
    geom_vline(xintercept = sweet_spot$K,
               linetype = "dotted", color = "grey30", linewidth = 0.8) +
    geom_label(data = sweet_spot,
               aes(x = K, y = 0.5, label = paste0("K=", K)),
               color = "grey30", size = 3.5, fill = "white",
               label.padding = unit(0.2, "lines"),
               inherit.aes = FALSE) +
    scale_color_manual(values = c("Semantic Coherence" = "#2563eb",
                                   "Exclusivity" = "#6E8B3D")) +
    scale_linetype_manual(values = c("solid", "dashed")) +
    scale_x_continuous(breaks = K_candidates) +
    labs(title = "Finding the Sweet Spot: Coherence vs Exclusivity",
         subtitle = "Relief Society Magazine | Both metrics normalized 0-1 | Dotted line = most balanced tradeoff",
         x = "Number of Topics (K)",
         y = "Normalized Score (0-1)",
         color = "Metric", linetype = "Metric") +
    theme_minimal(base_size = 12) +
    theme(
      legend.position = "bottom",
      panel.grid.minor = element_blank(),
      plot.title = element_text(face = "bold", size = 16)
    )

  cat("\nSweet spot: K =", sweet_spot$K, "\n")
  cat("(where coherence and exclusivity tradeoff is most balanced)\n")
}
```

```{r set-k}
# ============================================================
# SET NUMBER OF TOPICS HERE
# ============================================================
chosen_K <- 10
cat("K =", chosen_K, "\n")
```

```{r fit-model, cache=TRUE}
# Prevalence covariates: model learns how topic prevalence
# varies by year and article type during fitting.
stm_model <- stm(
  documents = docs,
  vocab = vocab,
  K = chosen_K,
  prevalence = ~ s(year) + Article_Type,
  data = meta,
  max.em.its = 75,
  init.type = "Spectral",
  seed = 12345,
  verbose = TRUE
)

saveRDS(stm_model, file.path(output_path, paste0("stm_model_K", chosen_K, ".rds")))
cat("Model saved.\n")
```

---

## 8. Examine Topics

```{r examine-topics}
all_top_words <- labelTopics(stm_model, n = 15)

cat("Top words per topic:\n\n")
for (i in 1:chosen_K) {
  cat("Topic", i, "\n")
  cat("  FREX:", paste(all_top_words$frex[i, 1:10], collapse = ", "), "\n")
  cat("  PROB:", paste(all_top_words$prob[i, 1:10], collapse = ", "), "\n\n")
}
```

---

## 8b. Auto-Generate Topic Labels

```{r auto-labels}
cat(rep("=", 70), "\n", sep = "")
cat("AUTO-GENERATING LABELS\n")
cat(rep("=", 70), "\n\n", sep = "")

create_specific_label <- function(topic_num, frex_words, prob_words) {
  frex_text <- tolower(paste(frex_words, collapse = " "))
  prob_text <- tolower(paste(prob_words, collapse = " "))
  all_words <- paste(frex_text, prob_text)

  # ---- RELIGION & DOCTRINE ----
  if (grepl("kingdom.*gospel|baptism.*eternal|salvation|atonement", frex_text)) {
    label <- "Gospel Doctrine & Spiritual Kingdom"
  } else if (grepl("passover|paschal|feast|tabernacle", frex_text)) {
    label <- "Biblical Symbolism & Ancient Rituals"
  } else if (grepl("abraham.*sarai|biblical|moses|israel", frex_text)) {
    label <- "Biblical Narratives"
  } else if (grepl("prayer|faith.*hope|testimony|spirit.*holy", frex_text)) {
    label <- "Faith & Spiritual Life"
  } else if (grepl("lesson|scripture|doctrine|commandment", frex_text)) {
    label <- "Religious Lessons & Scripture Study"
  } else if (grepl("temple|ordinance|endowment|sealing", frex_text)) {
    label <- "Temple & Sacred Ordinances"
  } else if (grepl("missionary|mission.*field|convert|preach", frex_text)) {
    label <- "Missionary Work & Conversion"

  # ---- RELIEF SOCIETY & CHURCH ORG ----
  } else if (grepl("sisters.*presidency|organization.*grain|relief.*leader", frex_text)) {
    label <- "Relief Society Leadership & Organization"
  } else if (grepl("stake.*ward|attendance.*conference|quarterly", frex_text)) {
    label <- "Stake & Ward Relief Society Reports"
  } else if (grepl("conference|general.*conference|session|sustain", all_words)) {
    label <- "Church Conference Proceedings"

  # ---- WOMEN'S RIGHTS & POLITICS ----
  } else if (grepl("suffrage.*vote|legislature|franchise|ballot", frex_text)) {
    label <- "Women's Suffrage & Political Rights"
  } else if (grepl("council.*international|convention|delegate", frex_text)) {
    label <- "International Women's Councils"
  } else if (grepl("equal.*right|petition|protest|reform", frex_text)) {
    label <- "Women's Reform & Activism"

  # ---- DOMESTICITY & HOME ----
  } else if (grepl("recipe|tbsp|boiling|oven|flour|bake", frex_text)) {
    label <- "Recipes & Cooking Instructions"
  } else if (grepl("housework|housekeeping|budget|thrift", frex_text)) {
    label <- "Household Management & Budgeting"
  } else if (grepl("child|mother.*rear|parent|infant|nurture", frex_text)) {
    label <- "Motherhood & Child-Rearing"
  } else if (grepl("garden|plant.*seed|flower|cultivation", frex_text)) {
    label <- "Home Gardening & Agriculture"
  } else if (grepl("sew|pattern|dress|fabric|garment|fashion", frex_text)) {
    label <- "Sewing, Fashion & Handwork"

  # ---- EDUCATION & PROFESSIONALIZATION ----
  } else if (grepl("nurse.*hospital|nursing.*training|medical", frex_text)) {
    label <- "Nursing Training & Hospital Work"
  } else if (grepl("school|teacher|student|education|university|class", frex_text)) {
    label <- "Education & Schools"
  } else if (grepl("diet.*protein|nutrition|malnutrition|vitamin", frex_text)) {
    label <- "Nutrition & Dietary Science"
  } else if (grepl("radium.*curie|pasteur.*science|scientist|discovery", frex_text)) {
    label <- "Scientific Biography & Discovery"

  # ---- HISTORY & PIONEER ----
  } else if (grepl("emigration.*journey|wagon.*pioneer|handcart|plains", frex_text)) {
    label <- "Pioneer Emigration & Journey Stories"
  } else if (grepl("pioneer|settlement|early.*days|frontier", all_words)) {
    label <- "Pioneer Heritage & Settlement"

  # ---- LITERATURE & ARTS ----
  } else if (grepl("irving|tale|novel|literary|author", frex_text)) {
    label <- "Literature & Book Reviews"
  } else if (grepl("jerry|walter|jimmy|agnes|margaret", frex_text) && grepl("said|little|came", prob_text)) {
    label <- "Serialized Fiction & Stories"
  } else if (grepl("poem|verse|stanza|rhyme|lyric", all_words)) {
    label <- "Poetry & Verse"
  } else if (grepl("tableau.*song|music.*hymn|choir|sing", frex_text)) {
    label <- "Musical Programs & Performances"

  # ---- WAR & CURRENT EVENTS ----
  } else if (grepl("entente.*allies|war.*troops|soldier|military|battle", frex_text)) {
    label <- "War Commentary & News"
  } else if (grepl("europe|nation|government|political|congress", frex_text)) {
    label <- "National & International Affairs"

  # ---- HEALTH ----
  } else if (grepl("health|disease|sanit|hygiene|cure|sick", all_words)) {
    label <- "Health & Sanitation"

  # ---- OBITUARY & BIOGRAPHY ----
  } else if (grepl("death|funeral|deceased|mourn|tribute", frex_text)) {
    label <- "Obituaries & Tributes"
  } else if (grepl("life.*born|biography|memoir|career|accomplish", frex_text)) {
    label <- "Biographical Sketches"

  # ---- GENEALOGY ----
  } else if (grepl("genealog|ancestor|pedigree|lineage|family.*history", frex_text)) {
    label <- "Genealogy & Family History"

  # ---- SOCIAL WELFARE ----
  } else if (grepl("welfare|charity|poor|needy|donate|service", frex_text)) {
    label <- "Social Welfare & Charitable Work"

  # ---- FALLBACK ----
  } else {
    keywords <- paste(tools::toTitleCase(frex_words[1:3]), collapse = " / ")
    label <- keywords
  }

  return(label)
}

topic_labels <- sapply(1:chosen_K, function(i) {
  frex_words <- all_top_words$frex[i, 1:10]
  prob_words <- all_top_words$prob[i, 1:10]
  create_specific_label(i, frex_words, prob_words)
})

cat("Auto-generated labels:\n\n")
for (i in 1:chosen_K) {
  cat("Topic", i, ":", topic_labels[i], "\n")
  cat("  FREX:", paste(all_top_words$frex[i, 1:7], collapse = ", "), "\n")
  cat("  PROB:", paste(all_top_words$prob[i, 1:7], collapse = ", "), "\n\n")
}

# Export auto-labels
label_export <- tibble(
  topic_num = 1:chosen_K,
  auto_label = topic_labels,
  frex_words = apply(all_top_words$frex, 1, function(x) paste(x, collapse = ", ")),
  prob_words = apply(all_top_words$prob, 1, function(x) paste(x, collapse = ", ")),
  manual_label = ""
)
write_csv(label_export, file.path(output_path, paste0("topic_labels_K", chosen_K, ".csv")))
```

---

## 8c. Manual Label Overrides (Optional)

```{r manual-overrides}
# ============================================================
# MANUAL OVERRIDES - uncomment and edit as needed
# ============================================================
#topic_labels[1] <- "Advertisements"
topic_labels[2] <- "Advertisements"
#topic_labels[3] <- "World News and World War I Reports"
#topic_labels[4] <- "Parenting Guidance and Moral Lessons"??
#topic_labels[5] <- "Advertisements"
topic_labels[7] <- "Recipes, Cooking Instructions, and Homecrafts"
topic_labels[9] <- "Home Gardening, Agriculture, Nature"
#topic_labels[10] <- "Faithbuilding Editorials"

cat("FINAL TOPIC LABELS\n")
cat(rep("=", 70), "\n\n", sep = "")
for (i in 1:chosen_K) {
  cat("  Topic", i, ":", topic_labels[i], "\n")
}
```

---

## 8d. Find Examples for a Specific Topic

```{r find-examples-custom}
# ============================================================
# CHANGE THIS to examine any topic
# ===========================================================
topic_to_examine <- 10
n_examples <- 10

cat(rep("=", 70), "\n", sep = "")
cat("TOPIC", topic_to_examine, ":", topic_labels[topic_to_examine], "\n")
cat(rep("=", 70), "\n", sep = "")
cat("FREX:", paste(all_top_words$frex[topic_to_examine, 1:10], collapse = ", "), "\n")
cat("PROB:", paste(all_top_words$prob[topic_to_examine, 1:10], collapse = ", "), "\n")
cat(rep("-", 70), "\n\n", sep = "")

# modeled_texts was stored after prepDocuments — guaranteed to match model docs
thoughts <- findThoughts(stm_model,
                         texts = modeled_texts,
                         topics = topic_to_examine,
                         n = n_examples)

thought_indices <- thoughts$index[[1]]

for (i in seq_along(thought_indices)) {
  idx <- thought_indices[i]
  row <- processed_texts[idx, ]

  cat(sprintf("Example %d of %d:\n", i, length(thought_indices)))
  cat(sprintf("  File:   %s\n", row$filename))
  cat(sprintf("  Title:  %s\n", ifelse(is.na(row$Title), "(unknown)", row$Title)))
  cat(sprintf("  Author: %s\n", ifelse(is.na(row$Author) | row$Author == "Unknown", "-", row$Author)))
  cat(sprintf("  Type:   %s\n", ifelse(is.na(row$Article_Type), "-", row$Article_Type)))
  cat(sprintf("  Vol %s, %s\n\n", row$volume_num, row$year))
  cat(substr(thoughts$docs[[1]][i], 1, 400), "\n\n")
  cat(rep("-", 50), "\n\n", sep = "")
}
```

---

## 9. Link Topics to Articles

```{r link-topics-to-articles}
doc_topics <- make.dt(stm_model, meta = meta)

cat("Columns in doc_topics:\n")
cat(paste(names(doc_topics), collapse = ", "), "\n\n")

topic_article_link <- doc_topics %>%
  pivot_longer(
    cols = starts_with("Topic"),
    names_to = "topic",
    values_to = "proportion"
  ) %>%
  mutate(
    topic_num = as.integer(str_remove(topic, "Topic")),
    topic_label = topic_labels[topic_num]
  ) %>%
  select(topic_num, topic_label, proportion,
         any_of(c("filename", "Title", "Author", "Article_Type",
                  "volume_num", "year", "month"))) %>%
  arrange(topic_num, desc(proportion))

cat("Linked table:", nrow(topic_article_link), "rows\n")
```

---

## 9b. Dominant Topic Assignment

```{r dominant-topic}
exemplar_threshold <- 0.40

dominant_topics <- doc_topics %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "proportion") %>%
  mutate(topic_num = as.integer(str_remove(topic, "Topic"))) %>%
  group_by(doc_id) %>%
  slice_max(proportion, n = 1, with_ties = FALSE) %>%
  ungroup() %>%
  mutate(
    topic_label = topic_labels[topic_num],
    strong_exemplar = proportion >= exemplar_threshold,
    proportion_pct = round(proportion * 100, 1)
  ) %>%
  select(doc_id, any_of(c("filename", "Title", "Author", "Article_Type",
         "volume_num", "year", "month")),
         dominant_topic = topic_num, topic_label, proportion_pct, strong_exemplar) %>%
  arrange(dominant_topic, desc(proportion_pct))

cat("Dominant topic assigned to", nrow(dominant_topics), "documents\n")
cat("Strong exemplars (>", exemplar_threshold * 100, "%):", sum(dominant_topics$strong_exemplar), "\n\n")

dominant_topics %>%
  group_by(dominant_topic, topic_label) %>%
  summarise(n_articles = n(), n_strong = sum(strong_exemplar),
            avg_proportion = round(mean(proportion_pct), 1), .groups = "drop") %>%
  print(n = chosen_K)
```

```{r strong-exemplars}
cat("\nSTRONG EXEMPLARS (>", exemplar_threshold * 100, "%):\n")

for (t in 1:chosen_K) {
  strong <- dominant_topics %>% filter(dominant_topic == t, strong_exemplar)
  cat("\n", rep("-", 60), "\n", sep = "")
  cat("Topic", t, ":", topic_labels[t], " (", nrow(strong), " strong)\n")
  if (nrow(strong) > 0) {
    for (i in 1:min(10, nrow(strong))) {
      row <- strong[i, ]
      cat(sprintf("  [%s%%] %s | %s | Vol %s %s\n",
                  row$proportion_pct,
                  ifelse(is.na(row$Title), row$filename, row$Title),
                  ifelse(is.na(row$Author) | row$Author == "Unknown", "-", row$Author),
                  row$volume_num, row$year))
    }
  } else {
    cat("  (none above threshold)\n")
  }
}
```

---

## 10. Top Articles per Topic

```{r top-articles-per-topic}
top_n_per_topic <- 15

for (t in 1:chosen_K) {
  cat("\n", rep("=", 70), "\n", sep = "")
  cat("TOPIC", t, ":", topic_labels[t], "\n")
  cat(rep("=", 70), "\n")
  cat("FREX:", paste(all_top_words$frex[t, 1:10], collapse = ", "), "\n\n")

  top_arts <- topic_article_link %>% filter(topic_num == t) %>% head(top_n_per_topic)

  for (i in 1:nrow(top_arts)) {
    row <- top_arts[i, ]
    cat(sprintf("  %2d. [%.1f%%] Vol %s, %s | %s | %s | %s\n",
                i, row$proportion * 100, row$volume_num, row$year,
                ifelse(is.na(row$Title), row$filename, row$Title),
                ifelse(is.na(row$Author) | row$Author == "Unknown", "-", row$Author),
                ifelse(is.na(row$Article_Type), "-", row$Article_Type)))
  }
}
```

---

## 11. Interactive Article Browser

```{r interactive-browser}
browse_data <- topic_article_link %>%
  group_by(topic_num) %>%
  slice_max(proportion, n = 25) %>%
  ungroup() %>%
  mutate(proportion_pct = round(proportion * 100, 1)) %>%
  select(Topic = topic_num, Label = topic_label, `%` = proportion_pct,
         any_of(c("Title", "Author", "Article_Type", "volume_num",
                  "year", "month", "filename")))

datatable(browse_data, filter = "top",
          options = list(pageLength = 20, scrollX = TRUE),
          caption = "Top 25 articles per topic")
```

---

## 12. Topic Prevalence Summary

```{r topic-prevalence}
topic_props_mean <- colMeans(doc_topics %>% select(starts_with("Topic")))

prevalence_df <- tibble(
  topic_num = 1:chosen_K, label = topic_labels,
  prevalence = topic_props_mean, pct = round(topic_props_mean * 100, 1)
) %>% arrange(desc(prevalence))

par(mar = c(5, 18, 4, 2))
barplot(height = prevalence_df$prevalence, names.arg = prevalence_df$label,
  horiz = TRUE, las = 1, col = "#C1CDC1", border = "#556B2F",
  main = paste0("Topic Prevalence - RSM (Vols ", min(input_vol_nums), "-", max(input_vol_nums), ")"),
  xlab = "Expected Topic Proportion", cex.names = 0.7,
  xlim = c(0, max(prevalence_df$prevalence) * 1.3))
text(x = prevalence_df$prevalence + 0.005,
     y = seq(0.7, by = 1.2, length.out = nrow(prevalence_df)),
     labels = paste0(prevalence_df$pct, "%"), cex = 0.7, col = "#556B2F", font = 2)
par(mar = c(5, 4, 4, 2))
```

---

## 13. STM Summary Plot

```{r stm-summary, fig.width=10, fig.height=6}
plot(stm_model, type = "summary", n = min(10, chosen_K),
     main = paste("Topic Prevalence (K =", chosen_K, ")"), xlim = c(0, 0.3))
```

---

## 14. Lollipop Prevalence with Top Words

```{r lollipop-prevalence, fig.width=10, fig.height=6}
labels_df <- tibble(
  topic = 1:chosen_K, name = topic_labels,
  words = sapply(1:chosen_K, function(i) paste(all_top_words$prob[i, 1:10], collapse = ", ")),
  full_label = paste0(name, ": ", words), prevalence = topic_props_mean)

ggplot(labels_df, aes(x = prevalence, y = reorder(full_label, prevalence))) +
  geom_segment(aes(x = 0, xend = prevalence, y = full_label, yend = full_label),
               linewidth = 1.2, color = "black") +
  geom_point(size = 0.5) +
  labs(title = paste("Topic Prevalence (K =", chosen_K, ")"),
       x = "Expected Topic Proportions", y = NULL) +
  theme_minimal(base_size = 10) +
  theme(axis.text.y = element_text(size = 8, hjust = 1),
        plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
        panel.grid.major.y = element_blank(), panel.grid.minor = element_blank()) +
  scale_x_continuous(limits = c(0, 0.35), breaks = seq(0, 0.35, 0.05))
```

---

## 15. Topic Prevalence Over Time

```{r prevalence-over-time, fig.width=10, fig.height=6}
cat("Docs:", length(docs), "| Meta rows:", nrow(meta), "\n")
cat("NA years:", sum(is.na(meta$year)), "| NA Article_Type:", sum(is.na(meta$Article_Type)), "\n")

# Use the same covariates as the model fit, or just year
prep_time <- estimateEffect(1:chosen_K ~ s(year) + Article_Type,
                            stmobj = stm_model,
                            metadata = meta,
                            uncertainty = "Global")

top_6_topics <- order(topic_props_mean, decreasing = TRUE)[1:min(6, chosen_K)]

par(mfrow = c(2, 3), mar = c(4, 4, 3, 1))
for (tn in top_6_topics) {
  plot(prep_time, covariate = "year", model = stm_model, topics = tn,
       method = "continuous", xlim = range(meta$year, na.rm = TRUE),
       main = str_wrap(topic_labels[tn], 30), xlab = "Year",
       ylab = "Topic Proportion", linecol = "#53868B",
       printlegend = TRUE, ci.level = 0.95, lwd = 2)
}
par(mfrow = c(1, 1))
```

---

## 16. Scatter Plot - Top 6 Topics Over Time

```{r scatter-top6, fig.width=10, fig.height=6}
topic_time_data <- doc_topics %>%
  select(starts_with("Topic"), year) %>%
  filter(!is.na(year)) %>%
  group_by(year) %>%
  summarize(across(starts_with("Topic"), mean, na.rm = TRUE), .groups = "drop") %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "prevalence") %>%
  mutate(topic_num = as.numeric(str_remove(topic, "Topic")),
         topic_label = str_wrap(topic_labels[topic_num], 30))

ggplot(topic_time_data %>% filter(topic_num %in% top_6_topics),
       aes(x = year, y = prevalence)) +
  geom_line(color = "#8B1A1A", size = 1.5) +
  geom_point(color = "#CD2626", size = 3, alpha = 0.7) +
  geom_smooth(method = "loess", color = "#8B0000", linetype = "dashed",
              se = TRUE, fill = "#FFB6C1", alpha = 0.3) +
  facet_wrap(~topic_label, ncol = 3, scales = "free_y") +
  labs(title = "Top 6 Topics Over Time - Relief Society Magazine",
       x = "Year", y = "Mean Topic Proportion") +
  theme_minimal(base_size = 12) +
  theme(strip.text = element_text(size = 10, face = "bold"),
        panel.grid.minor = element_blank(),
        plot.title = element_text(face = "bold", size = 14)) +
  scale_y_continuous(labels = percent_format(accuracy = 0.1))
```

---

## 17. All Topics Over Time

```{r all-topics-time, fig.width=10, fig.height=8}
ggplot(topic_time_data, aes(x = year, y = prevalence)) +
  geom_line(color = "#53868B", size = 0.8) +
  geom_point(color = "#53868B", size = 1.5, alpha = 0.5) +
  facet_wrap(~topic_label, ncol = 4, scales = "free_y") +
  labs(title = "Complete Topic Evolution - Relief Society Magazine",
       x = "Year", y = "Topic Proportion") +
  theme_minimal(base_size = 10) +
  theme(strip.text = element_text(size = 7, face = "bold"),
        panel.grid.minor = element_blank()) +
  scale_y_continuous(labels = percent_format(accuracy = 0.1))
```

---

## 18. Single Topic Detail

```{r single-topic-detail, fig.width=10, fig.height=6}
topic_to_examine <- 1
topic_detail <- topic_time_data %>% filter(topic_num == topic_to_examine)

ggplot(topic_detail, aes(x = year, y = prevalence)) +
  geom_line(color = "#53868B", size = 1.5) +
  geom_point(color = "#53868B", size = 4, alpha = 0.7) +
  geom_smooth(method = "loess", color = "#CD2626", fill = "#FFB6C1", alpha = 0.3, size = 1) +
  labs(title = topic_labels[topic_to_examine],
       subtitle = "Points = annual averages | Red band = smoothed trend",
       x = "Year", y = "Topic Proportion") +
  theme_minimal(base_size = 14) +
  theme(plot.title = element_text(face = "bold", size = 16),
        panel.grid.minor = element_blank()) +
  scale_y_continuous(labels = percent_format(accuracy = 0.1))
```

---

## 19. Topic Correlation Network

```{r correlation-network, fig.width=10, fig.height=8}
mod.out.corr <- topicCorr(stm_model)
plot(mod.out.corr, main = "Topic Correlation Network - RSM",
     vertex.color = "#C1CDC1", vertex.label.color = "#556B2F")
```

---

## 20. Word Clouds

```{r wordcloud-topic1, fig.width=8, fig.height=6}
rs_colors <- c("#6E8B3D", "#A2CD5A", "#BCEE68", "#556B2F")
cloud(stm_model, topic = 1, scale = c(3, 0.5), colors = rs_colors,
      main = topic_labels[1])
```

```{r wordcloud-all, fig.width=8, fig.height=6, eval=FALSE}
for (i in 1:chosen_K) {
  cloud(stm_model, topic = i, scale = c(3, 0.5), colors = rs_colors,
        main = topic_labels[i])
}
```

---

## 21. Topic Quality

```{r topic-quality, fig.width=8, fig.height=6}
topicQuality(stm_model, documents = docs)
```

---

## 22. Compare Two Topics

```{r compare-topics, fig.width=10, fig.height=6}
plot(stm_model, type = "perspectives", topics = c(1, 2),
     main = paste("Comparing", topic_labels[1], "vs", topic_labels[2]))
```

---

## 23. Trend Summary Statistics

```{r trend-summary}
topic_trends <- topic_time_data %>%
  group_by(topic_num, topic_label) %>%
  summarise(start_prev = first(prevalence), end_prev = last(prevalence),
            change = end_prev - start_prev,
            pct_change = round((change / start_prev) * 100, 1),
            trend = case_when(change > 0.005 ~ "Increasing",
                              change < -0.005 ~ "Decreasing", TRUE ~ "Stable"),
            .groups = "drop") %>%
  arrange(desc(abs(pct_change)))

cat("TOPIC CHANGE SUMMARY\n", rep("=", 50), "\n\n", sep = "")
for (i in 1:nrow(topic_trends)) {
  cat(sprintf("Topic %d (%s): %s by %.1f%%\n",
              topic_trends$topic_num[i], topic_trends$topic_label[i],
              ifelse(topic_trends$pct_change[i] > 0, "increased", "decreased"),
              abs(topic_trends$pct_change[i])))
}
```

---

## 24. Topic Prevalence Stats Table

```{r prevalence-stats}
doc_topics %>%
  select(starts_with("Topic")) %>%
  summarise(across(everything(), mean, na.rm = TRUE)) %>%
  pivot_longer(everything(), names_to = "topic", values_to = "mean_proportion") %>%
  mutate(topic_num = as.numeric(str_remove(topic, "Topic")),
         label = topic_labels[topic_num],
         percentage = round(mean_proportion * 100, 2),
         rank = rank(-mean_proportion)) %>%
  arrange(rank) %>%
  select(rank, label, percentage) %>%
  print()
```

---

## 25. Article Type Distribution per Topic

```{r type-by-topic}
type_topic <- topic_article_link %>%
  filter(!is.na(Article_Type)) %>%
  group_by(topic_num, topic_label, Article_Type) %>%
  summarise(mean_proportion = mean(proportion), n_articles = n_distinct(filename),
            .groups = "drop") %>%
  arrange(topic_num, desc(mean_proportion))

type_topic %>%
  group_by(topic_num, topic_label) %>%
  slice_max(mean_proportion, n = 3) %>%
  print(n = chosen_K * 3)
```

---

## 26. Topic-Article Type Heatmap

```{r type-heatmap, fig.width=10, fig.height=7}
heatmap_data <- topic_article_link %>%
  filter(!is.na(Article_Type)) %>%
  group_by(topic_num, Article_Type) %>%
  summarise(mean_prop = mean(proportion), .groups = "drop") %>%
  pivot_wider(names_from = Article_Type, values_from = mean_prop, values_fill = 0)

heatmap_matrix <- as.matrix(heatmap_data %>% select(-topic_num))
rownames(heatmap_matrix) <- paste0("T", heatmap_data$topic_num, ": ",
                                    str_trunc(topic_labels[heatmap_data$topic_num], 25))

pheatmap(heatmap_matrix, main = "Topic Affinity by Article Type - RSM",
  color = colorRampPalette(c("white", "#C1CDC1", "#6E8B3D", "#556B2F"))(50),
  cluster_rows = TRUE, cluster_cols = TRUE, display_numbers = TRUE,
  number_format = "%.2f", fontsize_number = 7, fontsize_row = 9,
  fontsize_col = 9, angle_col = 45)
```

---
```{r}
library(RColorBrewer)
display.brewer.all()
```

## 27. Stacked Area Chart - Topic Composition Over Time

```{r stacked-area, fig.width=12, fig.height=6}
stacked_data <- topic_time_data %>%
  mutate(label = topic_labels[topic_num])

ggplot(stacked_data, aes(x = year, y = prevalence, fill = reorder(label, -topic_num))) +
  geom_area(alpha = 0.8, color = "white", linewidth = 0.3) +
  labs(title = "Topic Composition Over Time - RSM",
       x = "Year", y = "Topic Proportion", fill = "Topic") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold", size = 14),
        legend.text = element_text(size = 7), legend.key.size = unit(0.4, "cm")) +
  scale_y_continuous(labels = percent_format()) +
  scale_fill_brewer(palette = "Set2", direction = -1)
```

---

## 28. Topic Co-occurrence Within Articles

```{r topic-cooccurrence, fig.width=9, fig.height=8}
topic_cor <- cor(doc_topics %>% select(starts_with("Topic")))
rownames(topic_cor) <- paste0("T", 1:chosen_K, ": ", str_trunc(topic_labels, 20))
colnames(topic_cor) <- paste0("T", 1:chosen_K)

pheatmap(topic_cor, main = "Topic Co-occurrence - RSM",
  color = colorRampPalette(c("#2166AC", "white", "#B2182B"))(50),
  display_numbers = TRUE, number_format = "%.2f", fontsize_number = 8,
  breaks = seq(-1, 1, length.out = 51))
```

---

## 29. Exclusivity vs Semantic Coherence

```{r exclusivity-coherence, fig.width=9, fig.height=7}
topic_qual <- data.frame(
  topic = 1:chosen_K, label = topic_labels,
  coherence = semanticCoherence(stm_model, docs),
  exclusivity = exclusivity(stm_model))

ggplot(topic_qual, aes(x = coherence, y = exclusivity)) +
  geom_point(size = 4, color = "#6E8B3D") +
  geom_text(aes(label = paste0("T", topic)), vjust = -1, size = 3.5) +
  geom_text(aes(label = str_trunc(label, 25)), vjust = 2, size = 2.5, color = "grey40") +
  labs(title = "Topic Quality: Exclusivity vs Semantic Coherence",
       x = "Semantic Coherence", y = "Exclusivity") +
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(face = "bold", size = 14))
```

---

## 30. Dominant Topic Distribution

```{r dominant-distribution, fig.width=10, fig.height=6}
dom_summary <- dominant_topics %>% count(dominant_topic, topic_label) %>%
  mutate(pct = n / sum(n) * 100)

ggplot(dom_summary, aes(x = reorder(topic_label, n), y = n, fill = pct)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = paste0(n, " (", round(pct, 1), "%)")), hjust = -0.1, size = 3) +
  coord_flip() +
  labs(title = "Articles per Dominant Topic - RSM", x = NULL, y = "Number of Articles") +
  theme_minimal(base_size = 11) +
  scale_fill_gradient(low = "#C1CDC1", high = "#556B2F") +
  scale_y_continuous(expand = expansion(mult = c(0, 0.15)))
```

---

## 31. Topic-by-Volume Heatmap

```{r topic-volume-heatmap, fig.width=14, fig.height=7}
vol_topic_data <- doc_topics %>%
  select(starts_with("Topic"), volume_num) %>%
  filter(!is.na(volume_num)) %>%
  group_by(volume_num) %>%
  summarize(across(starts_with("Topic"), mean, na.rm = TRUE), .groups = "drop")

vol_matrix <- as.matrix(vol_topic_data %>% select(-volume_num))
rownames(vol_matrix) <- paste0("Vol ", vol_topic_data$volume_num)
colnames(vol_matrix) <- paste0("T", 1:chosen_K, ": ", str_trunc(topic_labels, 20))

pheatmap(t(vol_matrix), main = "Topic Prevalence by Volume - RSM",
  color = colorRampPalette(c("white", "#C1CDC1", "#6E8B3D", "#556B2F"))(100),
  cluster_rows = TRUE, cluster_cols = FALSE, display_numbers = FALSE,
  fontsize_row = 8, fontsize_col = 9, angle_col = 45, border_color = "grey90")
```

---

## 32. Author-Topic Analysis

```{r author-topic, fig.width=12, fig.height=8}
author_counts <- dominant_topics %>%
  filter(!is.na(Author), Author != "Unknown", nchar(Author) > 1) %>%
  count(Author, sort = TRUE)

cat("Authors with named articles:", nrow(author_counts), "\n")

if (nrow(author_counts) >= 2) {
  top_authors <- author_counts %>% head(min(20, nrow(author_counts))) %>% pull(Author)
  cat("Top authors:", paste(head(top_authors, 5), collapse = ", "), "\n\n")

  author_topic_data <- topic_article_link %>%
    filter(Author %in% top_authors) %>%
    group_by(Author, topic_num) %>%
    summarise(mean_prop = mean(proportion), .groups = "drop") %>%
    pivot_wider(names_from = topic_num, values_from = mean_prop, values_fill = 0)

  for (k in 1:chosen_K) {
    if (!as.character(k) %in% names(author_topic_data)) {
      author_topic_data[[as.character(k)]] <- 0
    }
  }
  author_topic_data <- author_topic_data %>%
    select(Author, all_of(as.character(1:chosen_K)))

  author_matrix <- as.matrix(author_topic_data %>% select(-Author))
  author_matrix[is.na(author_matrix) | is.nan(author_matrix) | is.infinite(author_matrix)] <- 0
  rownames(author_matrix) <- author_topic_data$Author
  colnames(author_matrix) <- paste0("T", 1:chosen_K, ": ", str_trunc(topic_labels, 18))

  pheatmap(author_matrix,
    main = paste0("Author-Topic Affinity (Top ", length(top_authors), " Authors) - RSM"),
    color = colorRampPalette(c("white", "#C1CDC1", "#6E8B3D", "#556B2F"))(100),
    cluster_rows = FALSE, cluster_cols = FALSE,
    fontsize_row = 8, fontsize_col = 8, angle_col = 45, border_color = "grey90")
} else {
  cat("\nSkipping author-topic heatmap: the RSM inventory has no author data for Vols 1-10.\n")
  cat("Authors ARE present in the filenames (e.g., 'Lula_Greene_Richards') but were not\n")
  cat("parsed into the inventory. To enable this visualization, update the RSM inventory\n")
  cat("to populate the Author column for early volumes.\n")
}
```

---

## 33. Topic Diversity per Volume

```{r topic-diversity, fig.width=10, fig.height=6}
vol_diversity <- doc_topics %>%
  select(starts_with("Topic"), volume_num, year) %>%
  filter(!is.na(volume_num)) %>%
  group_by(volume_num) %>%
  summarize(across(starts_with("Topic"), mean, na.rm = TRUE),
            year = first(year), n_articles = n(), .groups = "drop") %>%
  rowwise() %>%
  mutate(entropy = { props <- c_across(starts_with("Topic")); props <- props[props > 0]
    -sum(props * log(props)) },
    diversity = entropy / log(chosen_K)) %>%
  ungroup()

ggplot(vol_diversity, aes(x = volume_num, y = diversity)) +
  geom_col(aes(fill = diversity), show.legend = FALSE) +
  geom_text(aes(label = round(diversity, 2)), vjust = -0.3, size = 2.5) +
  labs(title = "Topic Diversity per Volume - RSM",
       subtitle = "Higher = more thematically diverse (Shannon entropy)",
       x = "Volume", y = "Diversity (0-1)") +
  theme_minimal(base_size = 11) +
  scale_fill_gradient(low = "#C1CDC1", high = "#556B2F") +
  scale_y_continuous(limits = c(0, 1.1))
```

---

## 34. Ridgeline Plot

```{r ridgeline, fig.width=10, fig.height=8}
ridge_data <- topic_article_link %>%
  mutate(topic_label_full = paste0("T", topic_num, ": ", topic_label))

ggplot(ridge_data, aes(x = proportion, y = reorder(topic_label_full, topic_num),
                        fill = after_stat(x))) +
  geom_density_ridges_gradient(scale = 2.5, rel_min_height = 0.01, gradient_lwd = 0.3) +
  scale_fill_gradient(low = "#C1CDC1", high = "#556B2F", guide = "none") +
  labs(title = "Distribution of Topic Proportions - RSM",
       x = "Topic Proportion", y = NULL) +
  theme_minimal(base_size = 11) +
  theme(plot.title = element_text(face = "bold", size = 14)) +
  scale_x_continuous(labels = percent_format(), limits = c(0, NA))
```

---

## 35. Topic Dendrogram

```{r dendrogram, fig.width=10, fig.height=6}
topic_word_matrix <- exp(stm_model$beta$logbeta[[1]])
topic_dist <- dist(topic_word_matrix, method = "euclidean")
topic_clust <- hclust(topic_dist, method = "ward.D2")
topic_clust$labels <- paste0("T", 1:chosen_K, ": ", topic_labels)

par(mar = c(2, 4, 3, 12))
plot(as.dendrogram(topic_clust), horiz = TRUE,
     main = "Topic Similarity Dendrogram - RSM", xlab = "Distance", cex = 0.8)
par(mar = c(5, 4, 4, 2))
```

---

## 36. Within-Topic Vocabulary Comparison (Early vs Late Period)

When the same topic appears across both eras of the Magazine, does the
**language** shift? This reveals how the publication's framing of shared
concerns evolved over time.

```{r vocab-comparison-era, fig.width=16, fig.height=20}
cat(rep("=", 70), "\n", sep = "")
cat("WITHIN-TOPIC VOCABULARY COMPARISON (EARLY vs LATE)\n")
cat(rep("=", 70), "\n\n", sep = "")

# Split into early and late eras at median year
median_year <- median(meta$year, na.rm = TRUE)
doc_topics_era <- doc_topics %>%
  mutate(era = ifelse(year <= median_year, "Early", "Late"))

cat("Era split at year", median_year, "\n")
cat("  Early:", sum(doc_topics_era$era == "Early"), "documents\n")
cat("  Late: ", sum(doc_topics_era$era == "Late"), "documents\n\n")

# Function: get word frequencies for top-quartile docs of a topic in an era
# (includes OCR junk filtering as safety net even though stopwords catch most)
get_topic_words_by_era <- function(topic_num, era_name) {
  topic_col <- paste0("Topic", topic_num)
  era_docs <- doc_topics_era %>% filter(era == era_name)
  threshold <- quantile(era_docs[[topic_col]], 0.75, na.rm = TRUE)

  doc_ids <- era_docs %>%
    filter(.data[[topic_col]] >= threshold) %>%
    pull(doc_id)

  words <- processed_texts %>%
    filter(doc_id %in% doc_ids) %>%
    pull(text_final) %>%
    paste(collapse = " ") %>%
    str_split("\\s+") %>%
    `[[`(1)

  freq <- sort(table(words), decreasing = TRUE)
  tibble(word = names(freq), count = as.integer(freq)) %>%
    mutate(proportion = count / sum(count)) %>%
    filter(
      nchar(word) >= 4,
      !word %in% all_stopwords,
      !is_ocr_fragment(word)
    )
}

# Pick the 6 most prevalent topics for comparison
top_6_for_vocab <- order(topic_props_mean, decreasing = TRUE)[1:min(6, chosen_K)]

cat("Comparing vocabulary for top", length(top_6_for_vocab), "topics:\n")
for (t in top_6_for_vocab) {
  cat(sprintf("  T%d: %s\n", t, topic_labels[t]))
}
cat("\n")

# Build log-ratio plots
vocab_plots <- list()
for (idx in seq_along(top_6_for_vocab)) {
  t <- top_6_for_vocab[idx]

  words_early <- get_topic_words_by_era(t, "Early")
  words_late  <- get_topic_words_by_era(t, "Late")

  word_compare <- full_join(
    words_early %>% select(word, early_prop = proportion),
    words_late  %>% select(word, late_prop = proportion),
    by = "word"
  ) %>%
    replace_na(list(early_prop = 0.0001, late_prop = 0.0001)) %>%
    mutate(
      log_ratio = log2(early_prop / late_prop),
      avg_prop = (early_prop + late_prop) / 2
    ) %>%
    filter(avg_prop > 0.001) %>%
    arrange(desc(abs(log_ratio)))

  # Top 20 words each direction
  top_early <- word_compare %>% filter(log_ratio > 0) %>% head(20)
  top_late  <- word_compare %>% filter(log_ratio < 0) %>% head(20)
  plot_words <- bind_rows(top_early, top_late) %>%
    mutate(
      direction = ifelse(log_ratio > 0,
                         paste0("More in Early (\u2264", median_year, ")"),
                         paste0("More in Late (>", median_year, ")")),
      word = reorder(word, log_ratio)
    )

  early_label <- paste0("More in Early (\u2264", median_year, ")")
  late_label  <- paste0("More in Late (>", median_year, ")")

  p <- ggplot(plot_words, aes(x = log_ratio, y = word, fill = direction)) +
    geom_col(alpha = 0.8) +
    geom_vline(xintercept = 0, linewidth = 0.8) +
    scale_fill_manual(values = setNames(c("#6E8B3D", "#556B2F"),
                                        c(early_label, late_label))) +
    labs(title = paste0("T", t, ": ", str_trunc(topic_labels[t], 35)),
         x = "Log2 Ratio (Early / Late)", y = NULL, fill = NULL) +
    theme_minimal(base_size = 8) +
    theme(legend.position = "none",
          plot.title = element_text(size = 10, face = "bold"))

  vocab_plots[[idx]] <- p
}

# Combine plots
if (length(vocab_plots) >= 6) {
  (vocab_plots[[1]] | vocab_plots[[2]] | vocab_plots[[3]]) /
  (vocab_plots[[4]] | vocab_plots[[5]] | vocab_plots[[6]]) +
    plot_annotation(
      title = "Within-Topic Vocabulary Shifts: Early vs Late Period",
      subtitle = paste0("Top 20 words each era emphasizes differently (split at ",
                        median_year, ")"),
      theme = theme(plot.title = element_text(size = 16, face = "bold"))
    )
} else if (length(vocab_plots) >= 1) {
  wrap_plots(vocab_plots, ncol = min(3, length(vocab_plots))) +
    plot_annotation(title = "Within-Topic Vocabulary Shifts: Early vs Late Period")
}
```

---

## 37. Topic Diversity & Concentration (Document-Level)

Section 33 measures diversity per *volume*. This section measures it per
*document*: is the typical article about one topic or several?

```{r doc-level-diversity, fig.width=12, fig.height=10}
cat(rep("=", 70), "\n", sep = "")
cat("DOCUMENT-LEVEL TOPIC DIVERSITY\n")
cat(rep("=", 70), "\n\n", sep = "")

# Shannon entropy per document (higher = more diverse)
doc_entropy <- doc_topics %>%
  select(doc_id, starts_with("Topic")) %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "p") %>%
  filter(p > 0) %>%
  group_by(doc_id) %>%
  summarize(entropy = -sum(p * log2(p)), .groups = "drop")

# Gini concentration per document
doc_gini <- doc_topics %>%
  select(doc_id, starts_with("Topic")) %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "p") %>%
  group_by(doc_id) %>%
  summarize(
    max_topic_prop = max(p),
    gini = 1 - sum(p^2),
    .groups = "drop"
  )

# Summary
diversity_summary <- doc_entropy %>%
  left_join(doc_gini, by = "doc_id") %>%
  summarize(
    mean_entropy = mean(entropy),
    sd_entropy = sd(entropy),
    mean_gini = mean(gini),
    mean_max_prop = mean(max_topic_prop),
    pct_strong_exemplar = mean(max_topic_prop >= 0.4) * 100
  )

cat("Diversity Metrics (Relief Society Magazine):\n\n")
cat(sprintf("  Mean Shannon Entropy:     %.2f bits\n", diversity_summary$mean_entropy))
cat(sprintf("  SD Entropy:               %.2f\n", diversity_summary$sd_entropy))
cat(sprintf("  Mean Gini (inv-Herf):     %.3f\n", diversity_summary$mean_gini))
cat(sprintf("  Mean Dominant Topic %%:    %.1f%%\n", diversity_summary$mean_max_prop * 100))
cat(sprintf("  Strong Exemplars (>40%%):  %.1f%% of documents\n\n", diversity_summary$pct_strong_exemplar))

# Entropy distribution
p1 <- ggplot(doc_entropy, aes(x = entropy)) +
  geom_density(fill = "#6E8B3D", alpha = 0.5, linewidth = 0.8, color = "#556B2F") +
  labs(title = "Topic Diversity per Document",
       subtitle = "Higher entropy = article discusses more topics evenly",
       x = "Shannon Entropy (bits)", y = "Density") +
  theme_minimal(base_size = 12)

# Dominant topic concentration
p2 <- ggplot(doc_gini, aes(x = max_topic_prop)) +
  geom_density(fill = "#6E8B3D", alpha = 0.5, linewidth = 0.8, color = "#556B2F") +
  geom_vline(xintercept = 0.4, linetype = "dashed", color = "grey40") +
  ggplot2::annotate("text", x = 0.42, y = 0, label = "Exemplar\nthreshold", size = 3, hjust = 0) +
  labs(title = "Topic Concentration per Document",
       subtitle = "Higher = article dominated by single topic; dashed line = 40% exemplar threshold",
       x = "Dominant Topic Proportion", y = "Density") +
  theme_minimal(base_size = 12) +
  scale_x_continuous(labels = percent_format())

p1 / p2
```

### Effective Number of Topics

```{r effective-topics-rsm, fig.width=10, fig.height=5}
# Publication-level topic distribution
pub_topic_dist <- doc_topics %>%
  summarize(across(starts_with("Topic"), mean)) %>%
  pivot_longer(everything(), names_to = "topic", values_to = "prevalence") %>%
  mutate(
    topic_num = as.integer(str_remove(topic, "Topic")),
    label = str_trunc(topic_labels[topic_num], 25)
  )

# Effective number of topics = exp(entropy of topic distribution)
eff_topics <- pub_topic_dist %>%
  filter(prevalence > 0) %>%
  summarize(eff = exp(-sum(prevalence * log(prevalence)))) %>%
  pull(eff)

cat(sprintf("Effective number of topics: %.1f (of %d)\n\n", eff_topics, chosen_K))

ggplot(pub_topic_dist, aes(x = reorder(label, -prevalence), y = prevalence)) +
  geom_col(fill = "#6E8B3D", alpha = 0.8) +
  labs(title = "Topic Weight Distribution \u2014 Relief Society Magazine",
       subtitle = paste0("Effective topics: ", round(eff_topics, 1), " of ", chosen_K),
       x = NULL, y = "Mean Proportion") +
  theme_minimal(base_size = 10) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8)) +
  scale_y_continuous(labels = percent_format())
```

---

## 38. Topic Prevalence Heatmap Over Time

```{r topic-heatmap-time, fig.width=12, fig.height=7}
# Yearly topic prevalence
yearly_topics_rsm <- doc_topics %>%
  filter(!is.na(year)) %>%
  select(year, starts_with("Topic")) %>%
  group_by(year) %>%
  summarize(across(starts_with("Topic"), mean), .groups = "drop") %>%
  pivot_longer(starts_with("Topic"), names_to = "topic", values_to = "prevalence") %>%
  mutate(
    topic_num = as.integer(str_remove(topic, "Topic")),
    short_label = paste0("T", topic_num, ": ", str_trunc(topic_labels[topic_num], 20))
  )

ggplot(yearly_topics_rsm, aes(x = year, y = short_label, fill = prevalence)) +
  geom_tile(color = "white", linewidth = 0.3) +
  scale_fill_gradient(low = "white", high = "#556B2F",
                      labels = percent_format()) +
  labs(title = "Topic Prevalence Over Time \u2014 Relief Society Magazine",
       subtitle = "Darker = higher prevalence in that year",
       x = "Year", y = NULL, fill = "Prevalence") +
  theme_minimal(base_size = 11) +
  theme(panel.grid = element_blank(),
        plot.title = element_text(face = "bold", size = 14)) +
  scale_y_discrete(limits = rev) +
  scale_x_continuous(breaks = sort(unique(yearly_topics_rsm$year)))
```

---

## 39. Topic Percentage Change (Early vs Late Era)

How much does each topic's prevalence **shift** from the early period to the
late period?

```{r topic-era-change, fig.width=12, fig.height=8}
cat(rep("=", 70), "\n", sep = "")
cat("PERCENTAGE CHANGE IN TOPICS: EARLY vs LATE ERA\n")
cat(rep("=", 70), "\n\n", sep = "")

# Mean prevalence per topic per era
era_means <- doc_topics_era %>%
  group_by(era) %>%
  summarize(across(starts_with("Topic"), mean), .groups = "drop") %>%
  pivot_longer(-era, names_to = "topic", values_to = "prevalence") %>%
  mutate(topic_num = as.integer(str_remove(topic, "Topic"))) %>%
  pivot_wider(names_from = era, values_from = prevalence)

era_change <- era_means %>%
  mutate(
    label = topic_labels[topic_num],
    early_pct = Early * 100,
    late_pct = Late * 100,
    abs_change = late_pct - early_pct,
    pct_change = ifelse(Early > 0.001,
                        (Late - Early) / Early * 100,
                        NA_real_),
    direction = case_when(
      abs_change > 0.5  ~ "Grew in Late Period",
      abs_change < -0.5 ~ "Declined in Late Period",
      TRUE ~ "Stable"
    )
  ) %>%
  arrange(desc(abs_change))

cat(sprintf("Era split: Early (\u2264%d) vs Late (>%d)\n\n", median_year, median_year))
cat(sprintf("%-35s  %7s  %7s  %8s  %9s\n",
            "Topic", "Early%", "Late%", "Change", "% Change"))
cat(rep("-", 80), "\n", sep = "")
for (i in 1:nrow(era_change)) {
  r <- era_change[i, ]
  pct_str <- ifelse(is.na(r$pct_change), "N/A", sprintf("%+.0f%%", r$pct_change))
  cat(sprintf("%-35s  %5.1f%%  %5.1f%%  %+6.1fpp  %9s\n",
              str_trunc(r$label, 35), r$early_pct, r$late_pct, r$abs_change, pct_str))
}

# Absolute change bar chart
p_abs <- era_change %>%
  mutate(display = paste0("T", topic_num, ": ", str_trunc(label, 28)),
         display = reorder(display, abs_change)) %>%
  ggplot(aes(x = abs_change, y = display, fill = direction)) +
  geom_col(alpha = 0.85) +
  geom_vline(xintercept = 0, linewidth = 1) +
  scale_fill_manual(values = c("Grew in Late Period" = "#6E8B3D",
                                "Declined in Late Period" = "#CD661D",
                                "Stable" = "#94a3b8")) +
  labs(title = paste0("Topic Change: Early (\u2264", median_year,
                      ") vs Late (>", median_year, ") Period"),
       subtitle = "Absolute change in percentage points of topic prevalence",
       x = "Change (percentage points)", y = NULL, fill = NULL) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom", panel.grid.major.y = element_blank())

print(p_abs)
```

```{r topic-era-change-relative, fig.width=12, fig.height=8}
# Relative (%) change bar chart
era_change_filtered <- era_change %>%
  filter(!is.na(pct_change), abs(pct_change) < 500) %>%
  mutate(display = paste0("T", topic_num, ": ", str_trunc(label, 28)),
         display = reorder(display, pct_change))

if (nrow(era_change_filtered) > 0) {
  ggplot(era_change_filtered, aes(x = pct_change, y = display, fill = direction)) +
    geom_col(alpha = 0.85) +
    geom_vline(xintercept = 0, linewidth = 1) +
    scale_fill_manual(values = c("Grew in Late Period" = "#6E8B3D",
                                  "Declined in Late Period" = "#CD661D",
                                  "Stable" = "#94a3b8")) +
    labs(title = "Relative Percentage Change in Topic Prevalence",
         subtitle = paste0("How much did each topic grow or shrink relative to its early-period (\u2264",
                           median_year, ") baseline?"),
         x = "Relative Change (%)", y = NULL, fill = NULL) +
    theme_minimal(base_size = 11) +
    theme(legend.position = "bottom", panel.grid.major.y = element_blank())
}
```

---

## 40. Topic Evolution Summary

```{r evolution-summary, fig.width=10, fig.height=10}
cat(rep("=", 70), "\n", sep = "")
cat("TOPIC EVOLUTION SUMMARY\n")
cat(rep("=", 70), "\n\n", sep = "")

topic_evolution <- era_change %>%
  mutate(
    evolution_type = case_when(
      abs(abs_change) <= 0.5 ~ "Stable",
      abs_change > 0.5  ~ "Growing",
      abs_change < -0.5 ~ "Declining"
    ),
    evolution_type = factor(evolution_type,
                            levels = c("Stable", "Growing", "Declining"))
  )

cat("TOPIC EVOLUTION CLASSIFICATION:\n\n")
for (etype in c("Stable", "Growing", "Declining")) {
  cat(toupper(etype), ":\n")
  subset_ev <- topic_evolution %>% filter(evolution_type == etype)
  if (nrow(subset_ev) > 0) {
    for (i in 1:nrow(subset_ev)) {
      r <- subset_ev[i, ]
      cat(sprintf("  T%d: %s (Early: %.1f%%, Late: %.1f%%, %+.1fpp)\n",
                  r$topic_num, r$label, r$early_pct, r$late_pct, r$abs_change))
    }
  } else {
    cat("  (none)\n")
  }
  cat("\n")
}

# Scatter plot: early vs late prevalence
ggplot(topic_evolution, aes(x = early_pct, y = late_pct, color = evolution_type)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed",
              color = "grey70", linewidth = 1) +
  geom_point(size = 5, alpha = 0.8) +
  geom_text_repel(aes(label = paste0("T", topic_num, ": ", str_trunc(label, 25))),
                  size = 3, max.overlaps = 20, show.legend = FALSE) +
  scale_color_manual(values = c(
    "Stable" = "#6495ED",
    "Growing" = "#6E8B3D",
    "Declining" = "#CD661D"
  )) +
  labs(title = "Topic Evolution: Early vs Late Period",
       subtitle = paste0("Diagonal = no change | Above = grew in late period (",
                         median_year + 1, "-", max(meta$year, na.rm = TRUE),
                         ") | Below = declined"),
       x = paste0("Early Period Mean % (\u2264", median_year, ")"),
       y = paste0("Late Period Mean % (>", median_year, ")"),
       color = "Evolution Type") +
  theme_minimal(base_size = 13) +
  theme(legend.position = "bottom",
        plot.title = element_text(face = "bold", size = 16)) +
  coord_fixed()
```

---

## 41. Representative Passages

```{r representative-passages}
cat("REPRESENTATIVE PASSAGES PER TOPIC\n")
cat(rep("=", 70), "\n\n", sep = "")

for (t in 1:chosen_K) {
  cat("TOPIC", t, ":", topic_labels[t], "\n")
  cat(rep("-", 60), "\n", sep = "")

  top_docs <- topic_article_link %>% filter(topic_num == t) %>% head(3)
  topic_words <- tolower(all_top_words$frex[t, 1:15])

  for (j in 1:nrow(top_docs)) {
    fname <- top_docs$filename[j]
    title_str <- ifelse(is.na(top_docs$Title[j]), fname, top_docs$Title[j])
    match_file <- list.files(input_path, pattern = fixed(fname),
                             recursive = TRUE, full.names = TRUE)
    if (length(match_file) == 0) next
    full_text <- read_file(match_file[1])
    sentences <- str_split(full_text, "(?<=[.!?])\\s+")[[1]]
    sentences <- sentences[nchar(sentences) > 40 & nchar(sentences) < 500]
    if (length(sentences) == 0) next
    scores <- sapply(sentences, function(s) {
      words <- tolower(str_split(s, "\\s+")[[1]])
      sum(words %in% topic_words) / max(length(words), 1)
    })
    best_sentence <- str_squish(sentences[order(scores, decreasing = TRUE)[1]])
    cat(sprintf("\n  [%s] (%.1f%% Topic %d)\n", title_str,
                top_docs$proportion[j] * 100, t))
    cat("  \"", str_trunc(best_sentence, 300), "\"\n", sep = "")
  }
  cat("\n\n")
}
```

---

## 42. Export Results

```{r export-results}
# 1. Full topic-article link
write_csv(topic_article_link %>% mutate(proportion_pct = round(proportion * 100, 2)),
          file.path(output_path, "topic_article_full_link.csv"))

# 2. Top exemplars
write_csv(topic_article_link %>% group_by(topic_num, topic_label) %>%
  slice_max(proportion, n = 25) %>% ungroup() %>%
  mutate(proportion_pct = round(proportion * 100, 2)),
  file.path(output_path, "topic_exemplar_articles.csv"))

# 3. Topic summary
write_csv(tibble(topic_num = 1:chosen_K, label = topic_labels,
  prevalence_pct = round(topic_props_mean * 100, 2),
  frex_words = apply(all_top_words$frex, 1, function(x) paste(x, collapse = ", ")),
  prob_words = apply(all_top_words$prob, 1, function(x) paste(x, collapse = ", "))),
  file.path(output_path, "topic_summary.csv"))

# 4. Dominant topic per article
write_csv(dominant_topics, file.path(output_path, "dominant_topic_per_article.csv"))

# 5. Strong exemplars
write_csv(dominant_topics %>% filter(strong_exemplar),
          file.path(output_path, "strong_exemplars.csv"))

cat("Exported to:", output_path, "\n")
cat("  - topic_article_full_link.csv\n  - topic_exemplar_articles.csv\n")
cat("  - topic_summary.csv\n  - dominant_topic_per_article.csv\n  - strong_exemplars.csv\n")
```

---

## 43. Read a Specific Article

```{r read-article-function}
read_article <- function(fname, input_dir = input_path) {
  match <- list.files(input_dir, pattern = fixed(fname), recursive = TRUE, full.names = TRUE)
  if (length(match) == 0) { cat("File not found:", fname, "\n"); return(invisible(NULL)) }
  txt <- read_file(match[1])
  cat(rep("=", 70), "\n", sep = ""); cat("File:", fname, "\n")
  cat(rep("=", 70), "\n\n", sep = ""); cat(substr(txt, 1, 2000), "\n\n...")
  return(invisible(txt))
}

top1 <- topic_article_link %>% filter(topic_num == 1) %>% head(1)
read_article(top1$filename)
```

---

## 44. Save Session

```{r save-session}
save(stm_model, docs, vocab, meta, raw_texts, processed_texts,
     all_stopwords, topic_labels, topic_article_link,
     dominant_topics, inventory_subset,
     file = file.path(output_path, paste0("topic_linker_session_K", chosen_K, ".RData")))

cat("Session saved. Reload with:\n")
cat('  load("', file.path(output_path, paste0("topic_linker_session_K", chosen_K, ".RData")), '")\n', sep = "")
```

---

```{r session-info}
sessionInfo()
```
