---
title: "Relief Society Magazine — Universal Article Extractor v2"
date: "`r Sys.Date()`"
output:
  html_notebook:
    toc: true
    toc_float: true
    theme: flatly
    code_folding: hide
---

```{r setup, message=FALSE, warning=FALSE}
for (pkg in c("stringr","readr","knitr","kableExtra")) {
  if (!requireNamespace(pkg, quietly=TRUE)) install.packages(pkg)
}
library(stringr); library(readr); library(knitr); library(kableExtra)

# ============================================================
# CONFIGURATION — update these paths to match your machine
# ============================================================
INPUT_DIRS <- c(
  "C:/Users/birch/OneDrive - George Mason University - O365 Production/Dissertation/textanalysis/Articleextractionrfiles/input/Vol27split",
  "C:/Users/birch/OneDrive - George Mason University - O365 Production/Dissertation/textanalysis/Articleextractionrfiles/input/Vol28split",
  "C:/Users/birch/OneDrive - George Mason University - O365 Production/Dissertation/textanalysis/Articleextractionrfiles/input/Vol29split"
)
OUTPUT_DIR <- "C:/Users/birch/OneDrive - George Mason University - O365 Production/Dissertation/textanalysis/Articleextractionrfiles/output"

if (!dir.exists(OUTPUT_DIR)) dir.create(OUTPUT_DIR, recursive=TRUE)
```

```{r helpers}
# ============================================================
# HELPERS
# ============================================================

read_file_safe <- function(path) {
  # Try UTF-8 first; if that fails, fall back to windows-1252.
  # After reading, validate the string by running nchar(); if that
  # throws an "invalid multibyte string" error the file contains
  # non-UTF-8 bytes that slipped through, so re-read as latin1.
  txt <- tryCatch(
    read_file(path, locale=locale(encoding="UTF-8")),
    error=function(e) read_file(path, locale=locale(encoding="windows-1252"))
  )
  ok <- tryCatch({ nchar(txt); TRUE }, error=function(e) FALSE)
  if (!ok) {
    txt <- read_file(path, locale=locale(encoding="latin1"))
    cat("  NOTE: Re-read as latin1 (non-UTF-8 bytes detected)\n")
  }
  txt
}

safe_filename <- function(title, max_chars = 50L) {
  clean <- str_replace_all(title, "[<>:\"/\\\\|?*,;()\\[\\]\r\n\u2014\u2013'\u2018\u2019\u201c\u201d`]", "")
  clean <- str_replace_all(clean, "\\s+", "_")
  clean <- str_replace_all(clean, "_+", "_")
  clean <- str_trim(str_replace_all(clean, "^_+|_+$", ""))
  if (nchar(clean) == 0) clean <- "untitled"
  if (nchar(clean) > max_chars) clean <- str_sub(clean, 1, max_chars)
  clean <- str_replace(clean, "_+$", "")  # remove trailing underscore after truncation
  clean
}

# Build a short filename from a CONTENTS title:  title snippet + author last name.
# E.g. "Parents What of Youth in a War-Torn World Mark K. Allen"
#   -> "Parents_What_of_Youth_Allen"
short_title_filename <- function(title) {
  clean <- str_replace_all(title,
    "[<>:\"/\\\\|?*,;()\\[\\]\r\n\u2014\u2013'\u2018\u2019\u201c\u201d`]", "")
  clean <- str_trim(clean)
  if (nchar(clean) == 0) return("untitled")

  words <- str_split(clean, "\\s+")[[1]]
  words <- words[nchar(words) > 0]
  if (length(words) == 0) return("untitled")

  # Try to detect author name block at end of title (2-4 Name-like words).
  # Name-like: starts with uppercase or is a connector (de, van, etc.)
  author_last <- ""
  title_words <- words

  if (length(words) > 3) {
    for (n_auth in c(4L, 3L, 2L)) {
      if (n_auth >= length(words)) next
      cand <- tail(words, n_auth)
      is_name <- sapply(cand, function(w)
        str_detect(w, "^[A-Z]") ||
        w %in% c("de","van","von","del","la","le","da","di"))
      if (all(is_name)) {
        author_last <- tail(cand, 1)     # last name
        title_words <- head(words, length(words) - n_auth)
        break
      }
    }
  }

  # Title snippet: first words up to ~25 chars
  snippet_parts <- character(0)
  n_chars <- 0L
  for (w in title_words) {
    if (n_chars + nchar(w) + 1L > 25L && length(snippet_parts) >= 1) break
    snippet_parts <- c(snippet_parts, w)
    n_chars <- n_chars + nchar(w) + 1L
  }
  snippet <- paste(snippet_parts, collapse = "_")

  # Combine title snippet + author last name
  result <- if (nchar(author_last) > 0 && nchar(snippet) > 0) {
    paste0(snippet, "_", author_last)
  } else if (nchar(snippet) > 0) {
    snippet
  } else {
    paste(head(words, min(3, length(words))), collapse = "_")
  }

  # Sanitize underscores
  result <- str_replace_all(result, "\\s+", "_")
  result <- str_replace_all(result, "_+", "_")
  result <- str_replace(result, "^_+|_+$", "")

  # Final cap at 50 chars
  if (nchar(result) > 50) result <- str_sub(result, 1, 50)
  result <- str_replace(result, "_+$", "")
  if (nchar(result) == 0) result <- "untitled"
  result
}

get_significant_words <- function(title) {
  stops <- c("the","a","an","of","in","on","at","to","for","and","or","but","by",
             "its","is","are","was","were","be","been","our","her","his","my","we",
             "it","as","with","from","that","this","not","no","out","new","all",
             "how","what","who","when","where","why","can","may","will","shall",
             "has","had","have","does","did","do","about","into","upon")
  # Split on whitespace, em/en-dashes, and hyphens (including single)
  # Also split on apostrophe-hyphen combos like "Teachers'-Seeking"
  words <- str_split(title, "[\\s\u2014\u2013]+|\\s*-+\\s*|'-")[[1]]
  words <- words[nchar(words) > 2]
  words <- words[!tolower(words) %in% stops]
  words <- str_replace(words, "[?.!,;:'\"]+$", "")
  words[nchar(words) > 0]
}

# Snap a found title position backward to the nearest paragraph break.
# Many article titles appear in the MIDDLE of a line (e.g., "By Author\nTitle\nText...")
# or after running headers.  Walking back to the nearest blank line gives the
# clean article start that includes any pre-title header / byline text.
# Looks back up to max_back chars; returns original pos if no break found.
snap_to_para_start <- function(text, pos, min_pos, max_back=600L) {
  if (pos <= min_pos) return(pos)
  lo  <- max(min_pos, pos - max_back)
  pre <- str_sub(text, lo, pos - 1L)

  # Helper: find nearby sentence end within 150 chars (for run-together OCR text)
  find_nearby_sent_end <- function() {
    lo_t <- max(min_pos, pos - 150L)
    pre_t <- str_sub(text, lo_t, pos - 1L)
    se <- str_locate_all(pre_t, "[.!?][)'\",]?\\s+")[[1]]
    if (nrow(se) > 0L) {
      snap_s <- lo_t + se[nrow(se), 2]
      if (snap_s <= pos) return(snap_s)
    }
    NA_integer_
  }

  # First choice: find the LAST double-newline (paragraph break) in the lookback window
  breaks <- str_locate_all(pre, "(\r?\n){2,}")[[1]]
  if (nrow(breaks) > 0L) {
    snap <- lo + breaks[nrow(breaks), 2]
    if (snap < pos) {
      if ((pos - snap) <= 200L) return(snap)
      # Far paragraph break (>200 chars); prefer a nearby sentence end if available
      sent_snap <- find_nearby_sent_end()
      if (!is.na(sent_snap)) return(sent_snap)
      return(snap)  # fallback to far paragraph break
    }
  }

  # Second choice: single newline (common in OCR where blank lines are missing)
  single_nl <- str_locate_all(pre, "\n")[[1]]
  if (nrow(single_nl) > 0L) {
    snap <- lo + single_nl[nrow(single_nl), 2]
    if (snap < pos) {
      if ((pos - snap) <= 200L) return(snap)
      # Far newline (>200 chars); prefer a nearby sentence end if available
      sent_snap <- find_nearby_sent_end()
      if (!is.na(sent_snap)) return(sent_snap)
      return(snap)  # fallback to far newline
    }
  }

  # Third choice: running header end.
  # For run-together OCR text where articles share the same line,
  # separated only by running headers like "598 RELIEF SOCIETY MAGAZINE—SEPTEMBER 1942".
  # Snap to just AFTER the last running header in the lookback window,
  # so the article text starts right after the header (which clean_headers strips).
  # Use an extended lookback (+100 chars) to catch the header's leading page number.
  lo_h  <- max(min_pos, pos - max_back - 100L)
  pre_h <- str_sub(text, lo_h, pos - 1L)
  rh_pats_snap <- c(
    "\\d{1,3}\\s+(?:Vol\\.?\\s*\\d+[^\\n]{0,30})?(?:THE\\s+)?RELIEF\\s+SOCIETY\\s+MAGAZINE(?:[^A-Za-z\\n]{0,5}(?:JANUARY|FEBRUARY|MARCH|APRIL|MAY|JUNE|JULY|AUGUST|SEPTEMBER|OCTOBER|NOVEMBER|DECEMBER)[,\\s]*\\d{4})?",
    "(?:THE\\s+)?RELIEF\\s+SOCIETY\\s+MAGAZINE[^A-Za-z\\n]{0,5}(?:JANUARY|FEBRUARY|MARCH|APRIL|MAY|JUNE|JULY|AUGUST|SEPTEMBER|OCTOBER|NOVEMBER|DECEMBER)[,\\s]*\\d{4}"
  )
  for (rp in rh_pats_snap) {
    hdrs <- str_locate_all(pre_h, regex(rp, ignore_case=FALSE))[[1]]
    if (nrow(hdrs) > 0L) {
      snap_h <- lo_h + hdrs[nrow(hdrs), 2]
      if (snap_h <= pos && (pos - snap_h) <= 300L) return(snap_h)
    }
  }

  # Fourth choice: end of previous sentence within the last 150 chars only.
  # Handles run-together OCR text where articles flow on the same line.
  sent_snap <- find_nearby_sent_end()
  if (!is.na(sent_snap)) return(sent_snap)

  # No good snap point found — return raw match position
  pos
}

classify_article <- function(title) {
  t <- tolower(title)
  if (str_detect(t, "^editorial|editorial[\\s\u2014\u2013-]")) return("Editorial")
  if (str_detect(t, "guide lesson"))                           return("Guide_Lessons")
  if (str_detect(t, "notes (from|to) the field"))             return("Notes_from_Field")
  if (str_detect(t, "home economics"))                        return("Home_Economics")
  if (str_detect(t, "home science"))                          return("Home_Science")
  if (str_detect(t, "current (topic|event)"))                 return("Current_Topics")
  if (str_detect(t, "home entertain"))                        return("Home_Entertainments")
  if (str_detect(t, "frontispiece"))                          return("Frontispiece")
  if (str_detect(t, "book notice"))                           return("Book_Notices")
  if (str_detect(t, "theological studies"))                   return("Lesson_Department")
  if (str_detect(t, "eliza roxey snow|poetry contest"))       return("Poetry_Contest")
  "Article"
}

get_metadata <- function(filename) {
  list(
    volume = str_extract(filename, "(?i)(?<=Vol)\\d+"),
    number = str_extract(filename, "(?i)(?<=No)\\d+"),
    month  = str_extract(filename, paste0(
      "(?i)(January|February|March|April|May|June|July|",
      "August|September|October|November|December)")),
    year   = str_extract(filename, "\\d{4}")
  )
}
```

```{r find-sections}
# ============================================================
# FIND SECTIONS
# Correctly locates:
#   contents_start / contents_text — the TOC listing
#   body_start — character position where article bodies begin
#                (AFTER the publication-info block, never before it)
#   board_start / board_end — the general board roster
#   body_end — last character of article content
#
# The key insight: the publication-info block
# ("Entered as second-class matter ... Phone Wasatch NNNN")
# marks the true boundary between the front matter/CONTENTS
# and the article body. body_start = position after this block
# plus the following VOL marker line.
# This prevents the CONTENTS listing from being searched for
# article titles, which caused fragments and wrong boundaries.
# ============================================================
find_sections <- function(text) {
  s   <- list()
  len <- nchar(text)

  # ---- CONTENTS keyword ----
  # Use str_locate_all to find ALL occurrences of "CONTENTS".
  # Pick the occurrence that has the MOST article-like lines (lines ending with
  # 2-3 digit page numbers) in the first 500 chars. This correctly selects the
  # actual article listing over header/section label uses of "CONTENTS".
  # If "CONTENTS" (plural) doesn't score well (< 3 article-like lines), also
  # try "CONTENT" (singular) — OCR sometimes drops the trailing S (e.g. Vol28 Jul).
  cp_all <- str_locate_all(text, regex("\\bCONTENTS\\b", ignore_case=TRUE))[[1]]
  best_start  <- if (nrow(cp_all) > 0) cp_all[1,1] else NA_integer_
  best_count  <- 0L
  if (nrow(cp_all) > 0) {
    for (ci in seq_len(nrow(cp_all))) {
      region <- str_sub(text, cp_all[ci,1], min(cp_all[ci,1] + 500L, len))
      rlines <- str_split(region, "\n")[[1]]
      art_count <- sum(str_detect(rlines, "\\d{2,3}\\s*$"))
      if (art_count > best_count) {
        best_count <- art_count
        best_start <- cp_all[ci,1]
      }
    }
  }
  # If CONTENTS (plural) didn't score well (< 3 article-like lines), also
  # try "CONTENT" (singular) — OCR sometimes drops the trailing S (e.g. Vol28 Jul).
  if (best_count < 3L) {
    cp_sing <- str_locate_all(text, regex("\\bCONTENT\\b", ignore_case=TRUE))[[1]]
    if (nrow(cp_sing) > 0) {
      for (ci in seq_len(nrow(cp_sing))) {
        region <- str_sub(text, cp_sing[ci,1], min(cp_sing[ci,1] + 500L, len))
        rlines <- str_split(region, "\n")[[1]]
        art_count <- sum(str_detect(rlines, "\\d{2,3}\\s*$"))
        if (art_count > best_count) {
          best_count <- art_count
          best_start <- cp_sing[ci,1]
        }
      }
    }
  }
  if (!is.na(best_start)) {
    s$contents_start <- best_start
  } else {
    # Fallback: some issues omit the "CONTENTS" heading entirely.
    # Strategy 1: dot-leader TOC after Vol masthead (e.g. Vol24 May)
    # Strategy 2: category-header TOC — "SPECIAL FEATURES" / "Special
    #   Features" directly after Vol masthead, followed by lines ending
    #   in 2-3 digit page numbers (e.g. Vol29 Jul)
    # Support both Roman (Vol. XXIX) and Arabic (Vol. 29) volume numbers.
    vol_line_m <- str_locate(text,
      regex("Vol\\.?\\s+(?:X{0,4}[IVX]+|\\d{1,3})\\s+[A-Z]+,?\\s+\\d{4}\\s+No\\.\\s*\\d{1,2}",
            ignore_case=TRUE))
    if (!is.na(vol_line_m[1,1])) {
      after_vol <- str_sub(text, vol_line_m[1,2] + 1L,
                           min(vol_line_m[1,2] + 800L, len))
      dot_entries <- str_count(after_vol, "\\.{3,}.*?\\d{2,3}")
      if (dot_entries >= 3) {
        s$contents_start <- vol_line_m[1,2] + 1L
        cat("  NOTE: No CONTENTS heading found; using dot-leader TOC after Vol masthead\n")
      } else {
        # Check for category-header TOC: "SPECIAL FEATURES" etc. + page numbers
        cat_hdr_m <- str_locate(after_vol,
          regex("(?:SPECIAL\\s+FEATURES|GENERAL\\s+FEATURES|POETRY|FICTION|LESSONS)",
                ignore_case=TRUE))
        if (!is.na(cat_hdr_m[1,1])) {
          # Verify: count lines ending with 2-3 digit page numbers
          toc_region <- str_sub(after_vol, cat_hdr_m[1,1], nchar(after_vol))
          pg_lines <- str_count(toc_region, "\\d{2,3}\\s*(\n|$)")
          if (pg_lines >= 3) {
            s$contents_start <- vol_line_m[1,2] + cat_hdr_m[1,1]
            cat("  NOTE: No CONTENTS heading found; using category-header TOC after Vol masthead\n")
          } else {
            s$contents_start <- NA_integer_
          }
        } else {
          s$contents_start <- NA_integer_
        }
      }
    } else {
      s$contents_start <- NA_integer_
    }
  }

  # ---- Publication-info block ----
  # "Entered as second-class matter ... Phone Wasatch NNNN"
  # There may be two of these (one before CONTENTS in front ads, one at end of CONTENTS).
  # We want the LAST one that occurs before or near the end of the CONTENTS section.
  pub_pattern <- regex(
    "Entered as second[- ]class matter[\\s\\S]{0,400}(?:(?:Tele)?phone\\s+Wasatch\\s+\\d+|Wasatch\\s+\\d+)",
    ignore_case=TRUE, dotall=TRUE)
  all_pub <- str_locate_all(text, pub_pattern)[[1]]

  # Find the pub block that is associated with the CONTENTS section
  # (closest one AT OR AFTER CONTENTS start, never before it)
  s$pub_end <- NA_integer_
  if (nrow(all_pub) > 0 && !is.na(s$contents_start)) {
    # Only accept pub blocks whose START is at or after (contents_start - 200)
    after <- all_pub[all_pub[,1] >= s$contents_start - 200, , drop=FALSE]
    if (nrow(after) > 0) {
      s$pub_end <- after[1, 2]
    }
    # Do NOT fall back to the last match overall: it may be in back-ads
    # far from CONTENTS, which corrupts pub_end and body_start.
  }

  # Safety: pub_end must be at or after contents_start.
  # If it landed before (e.g. front-ad block just before CONTENTS), reset to NA
  # so the fallback loop below can find the correct marker after CONTENTS.
  if (!is.na(s$pub_end) && !is.na(s$contents_start) &&
      s$pub_end < s$contents_start) {
    s$pub_end <- NA_integer_
  }

  # Fallback pub-end markers — always filtered to >= contents_start AND within 6000 chars
  # The 6000-char window prevents back-ads occurrences from being picked up.
  if (is.na(s$pub_end)) {
    for (pat in c("(?:Tele)?phone\\s+Wasatch\\s+\\d+", "\\$1\\.00\\s+a\\s+[Yy]ear",
                  "Organ\\s+of\\s+the\\s+Relief\\s+Society")) {
      m <- str_locate_all(text, regex(pat, ignore_case=TRUE))[[1]]
      if (nrow(m) > 0 && !is.na(s$contents_start)) {
        after <- m[m[,1] >= s$contents_start &
                   m[,1] <  s$contents_start + 6000L, , drop=FALSE]
        if (nrow(after) > 0) { s$pub_end <- after[1,2]; break }
      }
    }
  }

  # ---- CONTENTS text ----
  # From CONTENTS keyword to pub_end.
  # Clamp to max 5000 chars to prevent runaway if pub_end detection fails.
  s$contents_text <- NULL
  if (!is.na(s$contents_start)) {
    # Hard cap: CONTENTS section should never be more than 5000 chars
    hard_cap <- min(s$contents_start + 5000L, len)
    end_of_contents <- if (!is.na(s$pub_end) && s$pub_end < hard_cap) s$pub_end else hard_cap

    # Additional safety: if we can find "Organ of the Relief Society" before hard_cap, use that.
    # BUT only if the resulting CONTENTS text would be > 200 chars. Otherwise the "Organ" text
    # is part of the masthead right before/after the CONTENTS keyword, not the subscription block.
    organ_m <- str_locate(
      str_sub(text, s$contents_start, hard_cap),
      regex("Organ\\s+of\\s+the\\s+Relief\\s+Society", ignore_case=TRUE))
    if (!is.na(organ_m[1,1])) {
      organ_abs <- s$contents_start + organ_m[1,1] - 1L
      if (organ_abs < end_of_contents && (organ_abs - s$contents_start) > 200L)
        end_of_contents <- organ_abs
    }

    s$contents_end  <- end_of_contents
    s$contents_text <- str_sub(text, s$contents_start, s$contents_end)

    # If the extracted CONTENTS text is too small (< 200 chars) and there are more CONTENTS
    # occurrences, try the LAST occurrence — the actual listing often follows a header CONTENTS.
    if (nchar(s$contents_text) < 200 && nrow(cp_all) >= 2) {
      for (ci in 2:nrow(cp_all)) {
        alt_start   <- cp_all[ci, 1]
        alt_hard    <- min(alt_start + 5000L, len)
        alt_end     <- if (!is.na(s$pub_end) && s$pub_end > alt_start && s$pub_end < alt_hard)
                         s$pub_end else alt_hard
        # Check for Organ truncation
        alt_organ_m <- str_locate(
          str_sub(text, alt_start, alt_hard),
          regex("Organ\\s+of\\s+the\\s+Relief\\s+Society", ignore_case=TRUE))
        if (!is.na(alt_organ_m[1,1])) {
          alt_organ_abs <- alt_start + alt_organ_m[1,1] - 1L
          if (alt_organ_abs < alt_end && (alt_organ_abs - alt_start) > 200L)
            alt_end <- alt_organ_abs
        }
        alt_text <- str_sub(text, alt_start, alt_end)
        if (nchar(alt_text) > nchar(s$contents_text)) {
          s$contents_start <- alt_start
          s$contents_end   <- alt_end
          s$contents_text  <- alt_text
        }
      }
    }
  } else {
    s$contents_end <- NA_integer_
  }

  # ---- BODY START ----
  # Find the VOL. N MONTH, YEAR No. N masthead line that separates the
  # front-matter (subscription info, pub block) from the first article.
  # body_start = character AFTER the end of that VOL line.
  #
  # Problem solved here: some split files have their CONTENTS section starting
  # late (e.g. at char 2425), so contents_end can be as late as char 7425.
  # If we only search AFTER contents_end, we miss the VOL marker that sits
  # between the CONTENTS text and the first article (e.g. at char 3595).
  # Fix: search the entire first 12,000 chars of the file for ALL occurrences
  # of the VOL pattern, then pick the LAST one that is followed by article text
  # (not by another pub/masthead block).  This reliably finds the final 
  # "VOL. XVI MARCH, 1929 No. 3" line that immediately precedes the first article,
  # even when the same line appears twice (once in the CONTENTS block, once after).
  s$body_start <- NA_integer_

  # Primary VOL pattern: requires "No. N" at the end (standard masthead format)
  # e.g. "VOL. XVI MARCH, 1929 No. 3"
  vol_pat <- regex(
    "VOL\\.?\\s*(?:[IVXL]+|\\d+)\\.?[^\\n]{0,25}(?:JANUARY|FEBRUARY|MARCH|APRIL|MAY|JUNE|JULY|AUGUST|SEPTEMBER|OCTOBER|NOVEMBER|DECEMBER)[^\\n]{0,30}No\\.?\\s*\\d+",
    ignore_case=TRUE)

  # Fallback VOL pattern: handles OCR-corrupted "No." (e.g. "= a" instead of "No. 9")
  # This is looser — just VOL + Roman/Arabic + Month + Year — to find the masthead line
  # even when the issue number is garbled.
  vol_pat_loose <- regex(
    "VOL\\.?\\s*(?:[IVXL]+|\\d+)\\.?[^\\n]{0,25}(?:JANUARY|FEBRUARY|MARCH|APRIL|MAY|JUNE|JULY|AUGUST|SEPTEMBER|OCTOBER|NOVEMBER|DECEMBER)[^\\n]{0,15}(?:19|18)\\d\\d",
    ignore_case=TRUE)

  # Search across the first 30,000 chars (covers all known split-file layouts,
  # including issues where CONTENTS starts late or the VOL marker is far from file start)
  wide_chunk   <- str_sub(text, 1L, min(30000L, len))
  vol_m_strict <- str_locate_all(wide_chunk, vol_pat)[[1]]
  vol_m_loose  <- str_locate_all(wide_chunk, vol_pat_loose)[[1]]
  # Run BOTH patterns and combine.  An early garbled-OCR masthead (e.g. "= a" instead of
  # "No. 9") is caught by the loose pattern even when the strict pattern also matches a
  # later, clean copy of the same line.  Combining and sorting by position then picking
  # the FIRST match after CONTENTS correctly sets body_start to just after the masthead.
  all_vol_m <- rbind(vol_m_strict, vol_m_loose)
  if (nrow(all_vol_m) > 0) {
    all_vol_m <- all_vol_m[!duplicated(all_vol_m[, 1L]), , drop=FALSE]
    all_vol_m <- all_vol_m[order(all_vol_m[, 1L]), , drop=FALSE]
  }

  s$vol_marker_found <- FALSE   # TRUE when body_start set from a reliable VOL marker

  if (nrow(all_vol_m) > 0) {
    # Use the FIRST occurrence AFTER the CONTENTS section start.
    # Rationale: the masthead VOL line appears in the front matter, immediately after
    # the CONTENTS + publication block. In some issues (Sep16, Sep17) the masthead
    # is followed by article content WITH NO NEWLINE — all in one giant text blob.
    # Later in that blob, running-header copies of the VOL line appear (e.g. at pg edges).
    # Using the LAST occurrence would pick a running header mid-article, setting body_start
    # too late and skipping 3–4 early articles. Using the FIRST occurrence after CONTENTS
    # reliably picks the masthead, placing body_start right at the article content start.
    contents_start_for_vol <- if (!is.na(s$contents_start)) s$contents_start else 0L
    # Filter to matches after CONTENTS start; fall back to all matches if none qualify
    after_contents <- all_vol_m[all_vol_m[,1] > contents_start_for_vol, , drop=FALSE]
    target_row  <- if (nrow(after_contents) > 0) 1L else 1L  # first qualifying
    target_m    <- if (nrow(after_contents) > 0) after_contents else all_vol_m
    vol_end_rel <- target_m[target_row, 2]
    # Advance past the rest of that line, but cap at 300 chars.
    # Rationale: in some OCR files the VOL masthead line runs directly into article
    # content with no newline for thousands of characters (e.g. Sep16, Sep17).
    # If we naively seek the next \n we skip over all those articles.
    # Capping at 300 chars ensures body_start lands just after the masthead marker,
    # right at the beginning of article content.
    tail_chunk  <- str_sub(wide_chunk, vol_end_rel + 1L, vol_end_rel + 300L)
    line_end_m  <- str_locate(tail_chunk, "\n")
    extra       <- if (!is.na(line_end_m[1,1])) line_end_m[1,1] else 0L
    s$body_start       <- vol_end_rel + extra
    s$vol_marker_found <- TRUE
  }

  # Fallback: if no VOL marker found anywhere, start right after the CONTENTS block
  if (is.na(s$body_start) || s$body_start < 1L) {
    s$body_start <- if (!is.na(s$contents_end)) s$contents_end + 1L
                    else if (!is.na(s$pub_end))  s$pub_end + 1L
                    else 1L
  }

  # Guard: if body_start landed inside or before the CONTENTS/subscription block
  # (happens when the VOL marker appears BEFORE the CONTENTS section, e.g. Sep 1942),
  # advance past the subscription block to avoid including boilerplate in articles.
  if (!is.na(s$contents_end) && s$body_start <= s$contents_end) {
    # Search for "MAGAZINE CIRCULATION" marker after contents_end
    post_end  <- min(len, s$contents_end + 2000L)
    post_text <- str_sub(text, s$contents_end + 1L, post_end)
    mag_circ  <- str_locate(post_text,
                   regex("MAGAZINE\\s+CIRCULATION\\s*[\\d,]+", ignore_case=TRUE))
    if (!is.na(mag_circ[1,1])) {
      circ_end_abs <- s$contents_end + mag_circ[1,2]
      tail <- str_sub(text, circ_end_abs + 1L, circ_end_abs + 50L)
      nl   <- str_locate(tail, "\n")
      s$body_start <- circ_end_abs + if (!is.na(nl[1,1])) nl[1,1] else 1L
    } else {
      s$body_start <- s$contents_end + 1L
    }
  }

  # ---- BOARD section ----
  # PRIMARY: Find "Motto" which uniquely identifies the actual board roster.
  # It appears exactly once per issue, immediately before the member names.
  # This avoids matching the credit line "PUBLISHED MONTHLY BY THE GENERAL
  # BOARD OF RELIEF SOCIETY" which is NOT the board roster.
  s$board_start <- NA_integer_
  s$board_end   <- NA_integer_
  motto_m <- str_locate(text, regex("Motto", ignore_case=FALSE))
  if (!is.na(motto_m[1,1])) {
    # Snap backward to find the start of the board block:
    # Look back up to 500 chars for "THE RELIEF SOCIETY" or "THE CHURCH"
    motto_pos <- motto_m[1,1]
    lookback  <- str_sub(text, max(1L, motto_pos - 500L), motto_pos - 1L)
    # Find "THE RELIEF SOCIETY" or "THE CHURCH" in the lookback
    church_m <- str_locate_all(lookback,
      regex("THE\\s+(?:RELIEF\\s+SOCIETY|CHURCH)\\s+OF", ignore_case=TRUE))[[1]]
    if (nrow(church_m) > 0) {
      # Use the LAST match (closest to Motto)
      s$board_start <- max(1L, motto_pos - 500L) + church_m[nrow(church_m), 1] - 1L
    } else {
      s$board_start <- motto_pos
    }
    # Find the end of the board block: look forward for Editor/Manager/end markers
    # Use multiline=TRUE so $ matches end-of-line (not end-of-string),
    # preventing the board from swallowing editorial text that follows.
    bc <- str_sub(text, s$board_start, min(s$board_start + 3000L, len))
    for (ep in c("Acting\\s+Business\\s+Manager[^\\n]{0,80}",
                 "Assistant\\s+Manager[^\\n]{0,80}",
                 "Business\\s+Manager[^\\n]{0,80}",
                 "Manager[^\\n]{0,40}",
                 "Amy\\s+Brown\\s+Lyman[^\\n]{0,80}",
                 "Room\\s+\\d+[^\\n]{0,50}(?:Bishop|Building|Utah)",
                 "Bishop'?s?\\s+Buil", "Music\\s+Director",
                 "\\$1\\.00\\s+a\\s+Year")) {
      em <- str_locate_all(bc, regex(ep, ignore_case=TRUE, multiline=TRUE))[[1]]
      if (nrow(em) > 0) { s$board_end <- s$board_start + em[nrow(em),2]; break }
    }
    if (is.na(s$board_end)) s$board_end <- min(s$board_start + 2000L, len)
  } else {
    # Fallback: try original patterns (for issues without "Motto")
    # Only search in the front matter (before body_start) to avoid matching
    # biographical article text like "the General Board, Mrs. Lyman..."
    front_limit <- if (!is.na(s$body_start)) s$body_start else min(len, 10000L)
    front_text  <- str_sub(text, 1L, front_limit)
    board_pats <- c(
      "PRESIDENCY\\s+AND\\s+GENERAL\\s+BOARD(?:\\s+OF(?:\\s+THE)?)?\\s+RELIEF",
      "RELIEF\\s+SOCIETY\\s+GENERAL\\s+BOARD\\s+[A-Z]",
      "THE\\s+GENERAL\\s+BOARD[,.]?\\s+(?:MRS\\.|Mrs\\.)"
    )
    for (bp in board_pats) {
      m <- str_locate(front_text, regex(bp, ignore_case=TRUE))
      if (!is.na(m[1,1])) { s$board_start <- m[1,1]; break }
    }
    if (!is.na(s$board_start)) {
      bc <- str_sub(text, s$board_start, min(s$board_start + 3000L, len))
      for (ep in c("Acting\\s+Business\\s+Manager[^\\n]{0,80}",
                   "Business\\s+Manager[^\\n]{0,80}",
                   "Room\\s+\\d+[^\\n]{0,50}(?:Bishop|Building|Utah)",
                   "Bishop'?s?\\s+Buil", "Music\\s+Director",
                   "\\$1\\.00\\s+a\\s+Year")) {
        em <- str_locate_all(bc, regex(ep, ignore_case=TRUE, multiline=TRUE))[[1]]
        if (nrow(em) > 0) { s$board_end <- s$board_start + em[nrow(em),2]; break }
      }
      if (is.na(s$board_end)) s$board_end <- min(s$board_start + 2000L, len)
    }
  }

  # ---- BODY END (start of back ads) ----
  # Search last 30% for back-ad markers
  ads_from   <- as.integer(len * 0.70)
  ads_chunk  <- str_sub(text, ads_from, len)
  s$body_end <- len
  for (ap in c("ADVERTISERS'?\\s+(?:DIRECTORY|INDEX)",
                "INDEX\\s+TO\\s+ADVERTISERS",
                "PATRONIZE\\s+OUR\\s+ADVERTISERS")) {
    m <- str_locate(ads_chunk, regex(ap, ignore_case=TRUE))
    if (!is.na(m[1,1])) { s$body_end <- ads_from + m[1,1] - 1L; break }
  }

  return(s)
}
```

```{r parse-contents}
# ============================================================
# CONTENTS PARSER
# Handles both line-by-line and single-line collapsed CONTENTS.
# Strips dot leaders, page numbers, trailing author attributions.
# Returns data.frame(title, page, category)
# ============================================================
parse_contents_section <- function(contents_text) {
  empty <- data.frame(title=character(), page=integer(), category=character(),
                      stringsAsFactors=FALSE)
  if (is.null(contents_text) || nchar(str_trim(contents_text)) == 0) return(empty)

  ct <- str_replace_all(contents_text, "\r\n|\r", "\n")
  ct <- str_replace_all(ct, regex("Here is the corrected OCR.*?:\\s*",
                                   ignore_case=TRUE), "")
  ct <- str_replace_all(ct, "\\*\\*Page\\*\\*", "")

  # --- Batch page numbers detection ---
  # Some OCR issues place ALL page numbers on a single line at the end of CONTENTS,
  # separated from title lines. Detect this pattern and pair numbers with titles.
  ct_lines_raw <- str_split(ct, "\n")[[1]]
  ct_lines_raw <- ct_lines_raw[nchar(str_trim(ct_lines_raw)) > 0]

  # Look for a line that is entirely space-separated page numbers (5+ numbers)
  batch_pg_idx <- which(str_detect(ct_lines_raw, "^\\s*\\d{1,4}(\\s+\\d{1,4}){4,}\\s*$"))
  if (length(batch_pg_idx) > 0) {
    batch_line <- str_trim(ct_lines_raw[batch_pg_idx[1]])
    page_nums <- as.integer(str_extract_all(batch_line, "\\d+")[[1]])

    # Collect title lines (non-skip, non-batch, non-pure-number lines)
    skip_pat <- regex(
      "^(CONTENTS?|ADVERTISERS?|Page\\s*$|\\*\\*|(THE\\s+)?RELIEF\\s+SOCIETY|Vol\\.?\\s*[IVXL0-9]|Organ\\s+of\\s+the|PUBLISHED|Jesus Christ)",
      ignore_case=TRUE)
    title_lines <- ct_lines_raw[!str_detect(ct_lines_raw, skip_pat) &
                                !str_detect(ct_lines_raw, "^\\s*\\d{1,4}(\\s+\\d{1,4}){4,}\\s*$") &
                                seq_along(ct_lines_raw) < batch_pg_idx[1]]
    title_lines <- title_lines[nchar(str_trim(title_lines)) >= 2]

    # Pair them up if counts are compatible
    if (length(title_lines) > 0 && length(page_nums) >= length(title_lines)) {
      # Re-create lines with page numbers appended
      paired_lines <- character(length(title_lines))
      for (j in seq_along(title_lines)) {
        paired_lines[j] <- paste(str_trim(title_lines[j]), page_nums[j])
      }
      ct <- paste(paired_lines, collapse="\n")
    }
  }

  # Normalise OCR "?" that appears as a dash replacement.
  # Common in Vol29 (1942) where em-dashes are OCR'd as "?".
  # Replace when "?" is between word chars, or after apostrophe/close-paren/quote
  # (e.g., "Teachers'?Seeking", "Contest)?Title").
  ct <- str_replace_all(ct, "(?<=[\\w'\")])\\?(?=\\w)", "\u2014")

  # Normalise double-hyphens ("--") to em-dash.
  # Common in December 1942 where OCR produces "--" instead of em-dash.
  ct <- str_replace_all(ct, "--+", "\u2014")

  # Always apply inline expansion to split embedded "NNN Title" within long lines.
  # This covers single-line CONTENTS and partially-collapsed formats.
  ct_exp <- str_replace_all(ct, "\\.{2,}", " ")
  ct_exp <- str_replace_all(ct_exp, "[ \\t]{2,}", " ")
  # Split on "page_number SPACE Capital" -- matches single-letter words too (A, I)
  ct_exp <- str_replace_all(ct_exp, "(\\d{1,4})\\s{1,3}([A-Z\"])", "\\1\n\\2")
  lines  <- str_split(ct_exp, "\n")[[1]]
  lines  <- lines[nchar(str_trim(lines)) > 0]

  arts <- parse_linebased(lines)

  if (nrow(arts) > 0) {
    arts <- arts[!duplicated(arts$title), ]

    # Interpolate page numbers for entries with page=0 that aren't Frontispieces.
    # Use position-based interpolation from surrounding entries with known pages.
    for (j in seq_len(nrow(arts))) {
      if (arts$page[j] == 0L &&
          !str_detect(arts$title[j], regex("frontispiece", ignore_case=TRUE))) {
        # Find nearest previous and next entries with known pages
        prev_pg <- NA_integer_; next_pg <- NA_integer_
        if (j > 1) {
          prev_idx <- which(arts$page[1:(j-1)] > 0)
          if (length(prev_idx) > 0) prev_pg <- arts$page[max(prev_idx)]
        }
        if (j < nrow(arts)) {
          next_idx <- which(arts$page[(j+1):nrow(arts)] > 0)
          if (length(next_idx) > 0) next_pg <- arts$page[j + min(next_idx)]
        }
        # Assign interpolated page
        if (!is.na(prev_pg) && !is.na(next_pg)) {
          arts$page[j] <- as.integer(round((prev_pg + next_pg) / 2))
        } else if (!is.na(prev_pg)) {
          arts$page[j] <- prev_pg + 1L
        } else if (!is.na(next_pg)) {
          arts$page[j] <- max(1L, next_pg - 1L)
        }
      }
    }

    arts <- arts[order(arts$page), ]

    # Strip CONTENTS category prefixes from titles.
    # Vol26+ CONTENTS uses "Special Features Title...", "Poetry Title...",
    # "General Features Title...", "Fiction Title..." as section labels.
    # These prefixes don't appear in the body text and block title matching.
    cat_prefixes <- c("Special Features", "General Features",
                      "Poetry", "Fiction", "Lessons")
    for (j in seq_len(nrow(arts))) {
      for (pfx in cat_prefixes) {
        pfx_pat <- regex(paste0("^", pfx, "\\s+"), ignore_case = TRUE)
        if (str_detect(arts$title[j], pfx_pat)) {
          stripped <- str_trim(str_replace(arts$title[j], pfx_pat, ""))
          if (nchar(stripped) >= 3) {
            arts$title[j] <- stripped
          }
          break
        }
      }
    }

    # Strip physical-location prefixes from CONTENTS titles.
    # e.g. "Back of contents — The Songster" → "The Songster"
    #      "Inside front cover — Poem" → "Poem"
    # These describe WHERE the piece is printed, not its title,
    # and block find_in_window from matching the actual text.
    loc_pat <- regex(
      "^(?:Back\\s+of\\s+(?:contents|frontispiece|flyleaf|cover)|Inside\\s+(?:front|back)\\s+cover)\\s*[\u2014\u2013—-]+\\s*",
      ignore_case=TRUE)
    for (j in seq_len(nrow(arts))) {
      if (str_detect(arts$title[j], loc_pat)) {
        stripped <- str_trim(str_replace(arts$title[j], loc_pat, ""))
        if (nchar(stripped) >= 3) arts$title[j] <- stripped
      }
    }

    arts$category <- sapply(arts$title, classify_article)
  }
  arts
}

parse_linebased <- function(lines) {
  arts    <- data.frame(title=character(), page=integer(), stringsAsFactors=FALSE)
  pending <- ""
  just_saved_page <- FALSE   # TRUE after saving a title+page entry
  skip    <- regex(
    "^(CONTENTS?:?|ADVERTISERS?|Page\\s*$|\\*\\*|(THE\\s+)?RELIEF\\s+SOCIETY\\s+(OF|MAGAZINE|GENERAL)|Vol\\.?\\s*[IVXL0-9]|Organ\\s+of\\s+the|PUBLISHED\\s+MONTHLY|Jesus\\s+Christ|Bishop'?s\\s+Building|Editorial\\s+and\\s+Business|Telephone\\s+Wasatch|Subscription\\s+Price|Entered\\s+as\\s+second|Stamps\\s+should|Acceptance\\s+for\\s+mailing|No\\.?\\s*$|SPECIAL\\s+FEATURES\\s*$|GENERAL\\s+FEATURES\\s*$|POETRY\\s*$|FICTION\\s*$|LESSONS\\s*$)",
    ignore_case=TRUE)

  # Detect standalone author attribution lines (e.g. "Christie Lund Coles").
  # These appear in multi-line CONTENTS formats where author is on a separate line
  # after the title+page line.  Matches 2-5 words, each starting with uppercase
  # or being an initial (A., B.C.), optional honorifics (President, Dr., etc.),
  # no trailing colon (which would indicate a section header like "Editorials:").
  is_author_line <- function(s) {
    if (nchar(s) > 55 || str_detect(s, ":\\s*$")) return(FALSE)
    words <- str_split(str_trim(s), "\\s+")[[1]]
    if (length(words) < 2 || length(words) > 5) return(FALSE)
    # Each word must start with uppercase or be an initial like "A." "B.C."
    # Allow small preposition/connector words (de, van, von, Jr., Sr., II, III)
    ok <- sapply(words, function(w) {
      str_detect(w, "^[A-Z]") ||
      w %in% c("de", "van", "von", "del", "la", "le", "da", "di")
    })
    # At least 2 words must start with uppercase
    n_upper <- sum(str_detect(words, "^[A-Z]"))
    all(ok) && n_upper >= 2
  }

  # Strip "By Firstname [Middle] Lastname..." suffix from a CONTENTS title string.
  # Only removes explicit "By Author" attribution — bare trailing names (without "By")
  # are left in place. The S10 author-proximity strategy handles those cases:
  # it extracts the last word of the title as a candidate author last name and
  # searches for "By LastName" proximity in the body text.
  strip_author <- function(t) {
    t <- str_trim(str_replace(t,
      regex("\\s+[Bb]y\\s+[A-Z][a-zA-Z.,'\u2014\u2013 -]{2,}$"), ""))
    str_trim(t)
  }

  for (ln in lines) {
    ln <- str_trim(ln)
    ln <- str_trim(str_replace(ln, "^\\*+\\s*", ""))   # strip leading * OCR artifacts
    if (nchar(ln) < 2 || str_detect(ln, skip)) next

    clean <- str_trim(str_replace_all(ln, "\\s{2,}", " "))

    # Special case: line contains "Frontispiece" in the MIDDLE followed by a page number
    # e.g. "Portrait of Mrs. X Frontispiece Emily Sophia Richards 521"
    # -> two entries: (Portrait... Frontispiece, pg=0) and (Emily Sophia Richards, pg=521)
    front_mid <- str_match(clean,
      "^(.+?)\\s+[Ff]rontispiece\\s+(.+?)\\s+(\\d{1,4})\\s*$")
    if (!is.na(front_mid[1,1])) {
      bef <- str_trim(strip_author(front_mid[1,2]))
      aft <- str_trim(strip_author(front_mid[1,3]))
      pg_val <- suppressWarnings(as.integer(front_mid[1,4]))
      if (nchar(bef) >= 2)
        arts <- rbind(arts, data.frame(title=paste(bef,"Frontispiece"),
                                       page=0L, stringsAsFactors=FALSE))
      if (nchar(aft) >= 2 && !is.na(pg_val) && pg_val >= 1)
        arts <- rbind(arts, data.frame(title=aft, page=pg_val,
                                       stringsAsFactors=FALSE))
      pending <- ""
      next
    }

    # Strip trailing punctuation that OCR may attach to page numbers (e.g. "645," or "58]")
    clean <- str_replace(clean, "(\\d{1,4})[,;.\\]\\)]+\\s*$", "\\1")

    # Handle page ranges like "887-890" → keep first page number only
    clean <- str_replace(clean, "(\\d{1,4})-\\d{1,4}\\s*$", "\\1")

    pg_m <- str_match(clean, "\\s+(\\d{1,4})\\s*$")

    if (is.na(pg_m[1,1])) {
      # Multi-line CONTENTS format: after a title+page entry, the next line
      # is often the author's name (e.g. "Christie Lund Coles").
      # Skip these author attribution lines to prevent wrong title merges.
      if (just_saved_page && is_author_line(clean)) {
        just_saved_page <- FALSE
        next
      }
      just_saved_page <- FALSE

      if (str_detect(clean, regex("Frontispiece", ignore_case=TRUE))) {
        full <- if (nchar(pending) > 0 && nchar(pending) < 60) paste(pending, clean) else clean
        full <- strip_author(full)
        arts <- rbind(arts, data.frame(title=str_trim(full), page=0L,
                                       stringsAsFactors=FALSE))
        pending <- ""
      } else if (nchar(clean) > 1 && !str_detect(clean, "^\\d+$")) {
        is_continuation <- nchar(pending) > 0 && nchar(pending) < 80 &&
          (str_detect(clean, "^[a-z]") ||
           str_detect(clean, "^(By |by )") ||
           str_detect(clean, "^(of |and |the |for |in |on |to |at |or |with )") ||
           (nchar(clean) < 50 && str_detect(clean, "^[A-Z][a-z]") &&
            !str_detect(clean, "\\d{2,3}\\s*$")))
        if (nchar(pending) == 0) {
          pending <- clean
        } else if (is_continuation) {
          pending <- paste(pending, clean)
        } else {
          # About to replace pending — emit previous pending as a no-page entry
          # if it looks like a real title (>= 5 chars, has letters, not pure author)
          old_pending <- strip_author(pending)
          if (nchar(old_pending) >= 5 && str_detect(old_pending, "[A-Za-z]{3,}") &&
              !str_detect(old_pending, skip)) {
            arts <- rbind(arts, data.frame(title=str_trim(old_pending), page=0L,
                                           stringsAsFactors=FALSE))
          }
          pending <- clean
        }
      }
      next
    }

    pg <- suppressWarnings(as.integer(pg_m[1,2]))
    if (is.na(pg) || pg < 1 || pg > 2000) next

    title <- str_trim(str_replace(clean, "\\s+\\d{1,4}\\s*$", ""))
    title <- strip_author(title)
    title <- str_trim(str_replace_all(title, "\\s{2,}", " "))
    if (nchar(title) < 2 || str_detect(title, "^\\d+$")) { pending <- ""; next }

    if (nchar(pending) > 0 && nchar(pending) < 120)
      title <- paste(pending, title)
    pending <- ""
    just_saved_page <- TRUE
    arts <- rbind(arts, data.frame(title=str_trim(title), page=pg,
                                   stringsAsFactors=FALSE))
  }
  # Emit any remaining pending as a no-page entry
  if (nchar(pending) > 0) {
    old_pending <- strip_author(pending)
    if (nchar(old_pending) >= 5 && str_detect(old_pending, "[A-Za-z]{3,}") &&
        !str_detect(old_pending, skip)) {
      arts <- rbind(arts, data.frame(title=str_trim(old_pending), page=0L,
                                     stringsAsFactors=FALSE))
    }
  }
  arts
}
```

```{r page-index}
# ============================================================
# PAGE INDEX
# Maps page numbers to character positions within body text.
# Used only to narrow search windows; not required for correctness.
# ============================================================
build_page_index <- function(body_text, body_offset) {
  pages <- data.frame(page=integer(), position=integer(), stringsAsFactors=FALSE)

  # Pattern 1: Standard even-page headers — "72 RELIEF SOCIETY MAGAZINE" or
  #            "72 THE RELIEF SOCIETY MAGAZINE"
  even_m <- str_locate_all(body_text,
    regex("(\\d{1,3})\\s+(?:THE\\s+)?RELIEF\\s+SOCIETY\\s+MAGAZINE\\.?",
          ignore_case=FALSE))[[1]]
  if (nrow(even_m) > 0) {
    for (i in seq_len(nrow(even_m))) {
      chunk <- str_sub(body_text, even_m[i,1], even_m[i,2])
      pg    <- suppressWarnings(as.integer(str_extract(chunk, "^\\d+")))
      if (!is.na(pg) && pg >= 1 && pg <= 999)
        pages <- rbind(pages, data.frame(page=pg,
          position=even_m[i,1] + body_offset - 1L, stringsAsFactors=FALSE))
    }
  }

  # Pattern 2: Vol26+ even-page headers — "124 - FEBRUARY, RELIEF SOCIETY MAGAZINE"
  even_m2 <- str_locate_all(body_text,
    regex("(\\d{1,3})\\s*[-\u2013\u2014]\\s*[A-Z]+,?\\s+RELIEF\\s+SOCIETY\\s+MAGAZINE",
          ignore_case=FALSE))[[1]]
  if (nrow(even_m2) > 0) {
    for (i in seq_len(nrow(even_m2))) {
      chunk <- str_sub(body_text, even_m2[i,1], even_m2[i,2])
      pg    <- suppressWarnings(as.integer(str_extract(chunk, "^\\d+")))
      if (!is.na(pg) && pg >= 1 && pg <= 999)
        pages <- rbind(pages, data.frame(page=pg,
          position=even_m2[i,1] + body_offset - 1L, stringsAsFactors=FALSE))
    }
  }

  # Pattern 3: Vol26+ odd-page headers — "RELIEF SOCIETY MAGAZINE, FEBRUARY - 125"
  odd_m <- str_locate_all(body_text,
    regex("RELIEF\\s+SOCIETY\\s+MAGAZINE,?\\s+[A-Z]+\\s*[-\u2013\u2014]\\s*(\\d{1,3})",
          ignore_case=FALSE))[[1]]
  if (nrow(odd_m) > 0) {
    for (i in seq_len(nrow(odd_m))) {
      chunk <- str_sub(body_text, odd_m[i,1], odd_m[i,2])
      pg    <- suppressWarnings(as.integer(str_extract(chunk, "\\d+$")))
      if (!is.na(pg) && pg >= 1 && pg <= 999)
        pages <- rbind(pages, data.frame(page=pg,
          position=odd_m[i,1] + body_offset - 1L, stringsAsFactors=FALSE))
    }
  }

  if (nrow(pages) > 2) {
    keep <- rep(TRUE, nrow(pages))
    for (i in 2:(nrow(pages)-1)) {
      if (pages$page[i] < pages$page[i-1] - 5 ||
          pages$page[i] > pages$page[i+1] + 5) keep[i] <- FALSE
    }
    pages <- pages[keep, ]
  }
  pages[!duplicated(pages$page), ]
}

page_to_pos <- function(pi, pg, lo, hi) {
  if (nrow(pi)==0) return(lo)
  ex <- pi[pi$page==pg, ]
  if (nrow(ex)>0) return(ex$position[1])
  bef <- pi[pi$page < pg, ]
  aft <- pi[pi$page > pg, ]
  CPP <- 2400L
  if (nrow(bef)>0 && nrow(aft)>0) {
    b <- bef[nrow(bef),]; a <- aft[1,]
    frac <- (pg - b$page) / (a$page - b$page)
    return(as.integer(b$position + frac*(a$position - b$position)))
  }
  if (nrow(bef)>0) return(as.integer(bef$position[nrow(bef)] + (pg - bef$page[nrow(bef)]) * CPP))
  if (nrow(aft)>0) return(max(lo, as.integer(aft$position[1]  - (aft$page[1]  - pg) * CPP)))
  lo
}
```

```{r title-finder}
# ============================================================
# TITLE FINDER
# Searches for a title string within a character window.
# Tries six strategies in order, from exact to fuzzy.
# Returns the absolute character position in the full text,
# or NA if not found.
#
# IMPORTANT: callers always pass window = [body_start, body_end]
# so the CONTENTS listing is never searched.
# ============================================================
find_in_window <- function(text, title, w_start, w_end, allow_s10 = TRUE,
                           require_para_start = FALSE) {
  if (w_start >= w_end || nchar(str_trim(title)) == 0) return(NA_integer_)
  chunk <- str_sub(text, w_start, w_end)

  # Normalise em-dashes, en-dashes, double-hyphens, and OCR "?" to plain hyphen
  title <- str_replace_all(title, "\u2014|\u2013|---?", "-")
  title <- str_replace_all(title, "(?<=[\\w'\")])\\?(?=\\w)", "-")   # OCR "?" as dash
  # Drop Frontispiece suffix (handled separately)
  title <- str_trim(str_replace(title,
    regex("\\s+Frontispiece\\s*$", ignore_case=TRUE), ""))

  try_pat <- function(pat) {
    m <- tryCatch(str_locate(chunk, regex(pat, ignore_case=TRUE)),
                  error=function(e) matrix(NA_integer_,1,2))
    if (!is.na(m[1,1])) return(w_start + m[1,1] - 1L)
    NA_integer_
  }

  # Variant of try_pat that requires the match to be at a paragraph/line start.
  # Used for Strategy 11 proximity matches when no page_index is available,
  # to prevent matching title/author words inside the body of a previous article.
  try_pat_para <- function(pat) {
    pos <- try_pat(pat)
    if (is.na(pos)) return(NA_integer_)
    # Check that the character immediately before the match is a newline or start-of-body
    if (pos <= w_start) return(pos)   # at start of window = OK
    preceding <- str_sub(text, max(1L, pos - 2L), pos - 1L)
    if (str_detect(preceding, "\n")) return(pos)
    NA_integer_   # match is inside a line, not at paragraph start → reject
  }

  esc <- function(s) str_replace_all(s, "([.?*+^$\\[\\]\\\\(){}|])", "\\\\\\1")

  # 1. Exact match
  pos <- try_pat(esc(title)); if (!is.na(pos)) return(pos)

  # 2. Whitespace flexible
  pos <- try_pat(str_replace_all(esc(title), "\\s+", "\\\\s+"))
  if (!is.na(pos)) return(pos)

  # 3. Dash flexible (plain - or em/en dash)
  df  <- str_replace_all(esc(title), "[-\u2014\u2013]", "[-\u2014\u2013]+")
  df  <- str_replace_all(df, "\\s+", "\\\\s+")
  pos <- try_pat(df); if (!is.na(pos)) return(pos)

  # 4. Drop intra-word hyphens
  nh <- str_replace_all(title, "(?<=[a-zA-Z])-(?=[a-zA-Z])", "")
  if (nh != title) {
    pos <- try_pat(str_replace_all(esc(nh), "\\s+", "\\\\s+"))
    if (!is.na(pos)) return(pos)
  }

  # 5. EDITORIAL special case
  # Body format: "EDITORIAL\nThe Bright New Year"  (two separate lines)
  # CONTENTS produces: "EditorialThe Bright New Year" (merged, dash stripped)
  # Strategy: if title starts with "Editorial", search for EDITORIAL + subtitle words
  if (str_detect(title, regex("^Editorial", ignore_case=TRUE))) {
    subtitle <- str_trim(str_replace(title, regex("^Editorial[-: ]*", ignore_case=TRUE), ""))
    sub_words <- str_split(subtitle, "\\s+")[[1]]
    sub_words <- sub_words[nchar(sub_words) > 2]
    if (length(sub_words) >= 1) {
      # Search for EDITORIAL followed by the first significant word within ~200 chars
      ed_pat <- paste0("EDITORIAL[\\s\\S]{0,200}\\b",
                       esc(sub_words[1]), "\\b")
      pos <- try_pat(ed_pat)
      if (!is.na(pos)) return(pos)
    }
    # Fallback: just find EDITORIAL itself (there's usually only one per issue)
    pos <- try_pat("EDITORIAL\\b")
    if (!is.na(pos)) return(pos)
  }

  # 6. PORTRAIT special case
  # Portrait pages are image-only; body may contain only the person's name as a caption.
  # Search for the name AFTER stripping "Portrait of" / "Mrs." / "Miss" / "Dr."
  if (str_detect(title, regex("^(?:Portrait|Frontispiece Portrait)", ignore_case=TRUE))) {
    name <- str_replace(title, regex("^(?:Frontispiece\\s+)?Portrait\\s+of\\s+", ignore_case=TRUE), "")
    name <- str_replace(name, regex("^(?:Mrs?|Miss|Dr)\\.?\\s+", ignore_case=TRUE), "")
    name <- str_trim(name)
    if (nchar(name) >= 4) {
      pos <- try_pat(str_replace_all(esc(name), "\\s+", "\\\\s+"))
      if (!is.na(pos)) return(pos)
      # Try just the last name
      last <- str_extract(name, "[A-Z][a-z]+$")
      if (!is.na(last) && nchar(last) >= 4) {
        pos <- try_pat(paste0("\\b", esc(last), "\\b"))
        if (!is.na(pos)) return(pos)
      }
    }
  }

  # 7. Title contains em-dash subtitle: search only part BEFORE the dash
  # e.g. "Nature in the Raw-Snake River" -> search "Nature in the Raw"
  if (str_detect(title, "-")) {
    before_dash <- str_trim(str_split(title, "-")[[1]][1])
    # Strip trailing apostrophe/quote (e.g. "Visiting Teachers'" -> "Visiting Teachers")
    before_dash <- str_replace(before_dash, "['\"]+$", "")
    if (nchar(before_dash) >= 4 && before_dash != title) {
      pos <- try_pat(str_replace_all(esc(before_dash), "\\s+", "\\\\s+"))
      if (!is.na(pos)) return(pos)
    }
  }

  # 8. Strip leading/trailing honorifics (Pres., Dr., Mrs., Mr.)
  cleaned <- str_trim(str_replace(title,
    regex("^(?:Pres\\.|Dr\\.|Mrs?\\.|Prof\\.)\\s+"), ""))
  if (cleaned != title && nchar(cleaned) >= 4) {
    pos <- try_pat(str_replace_all(esc(cleaned), "\\s+", "\\\\s+"))
    if (!is.na(pos)) return(pos)
  }

  # 9. Significant-word proximity (most permissive, run last)
  sigs <- get_significant_words(title)
  if (length(sigs) >= 2) {
    for (n in c(min(length(sigs),4), min(length(sigs),3), 2)) {
      if (n > length(sigs)) next
      pat <- paste(
        sapply(sigs[seq_len(n)], function(w) paste0("\\b", esc(w), "\\b")),
        collapse=".{0,80}")
      pos <- try_pat(pat)
      if (!is.na(pos)) {
        # Check for a nearby line-start match (within 3000 chars forward).
        # Article titles usually start on their own line; a mid-line match
        # may be a false positive inside body text (e.g. a name list).
        # Only prefer the line-start match if it's close — running headers
        # further away are false positives themselves.
        pos_ls <- try_pat(paste0("(?<=\\n)[ \\t]*", pat))
        if (!is.na(pos_ls) && pos_ls > pos && (pos_ls - pos) <= 3000L)
          return(pos_ls)
        return(pos)
      }
    }
  }

  # 9b. Plural/singular normalization
  # OCR CONTENTS entries sometimes differ in number from the body heading:
  # e.g. CONTENTS has "Thoroughbreds" but body heading reads "Thoroughbred".
  # Try dropping a trailing 's' from each significant word that ends in 's'.
  if (length(sigs) >= 1) {
    sigs_norm <- sapply(sigs, function(w)
      if (str_detect(w, "s$") && nchar(w) > 4) str_sub(w, 1, nchar(w)-1L) else w)
    if (!identical(sigs, sigs_norm)) {
      for (n in c(min(length(sigs_norm),4), min(length(sigs_norm),3), 2)) {
        if (n > length(sigs_norm)) next
        pat <- paste(
          sapply(sigs_norm[seq_len(n)], function(w) paste0("\\b", esc(w), "\\b")),
          collapse=".{0,80}")
        pos <- try_pat(pat)
        if (!is.na(pos)) {
          pos_ls <- try_pat(paste0("(?<=\\n)[ \\t]*", pat))
          if (!is.na(pos_ls) && pos_ls > pos && (pos_ls - pos) <= 3000L)
            return(pos_ls)
          return(pos)
        }
      }
    }
  }

  # 10. Author-name search
  # Normally only runs when allow_s10=TRUE (narrow/wide windows), because on full-body
  # fallback it risks false-positive matches far from the article's true position.
  # EXCEPTION: allow S10 on full-body when the title contains an embedded author name
  # (trailing capitalized words that look like a personal name suffix).
  # e.g. "Love's Recompense Grace Jacobson" — body has "Love's Recompense By Mrs. Grace Jacobson"
  # S1-S9 all fail because the title form ≠ body form. S10 finds it by author-name proximity.
  # The plausibility guard in the caller (|pos - pg_est| ≤ tolerance) prevents far-off matches.
  author_m_check <- str_match(title,
    "^(.{3,40}?)\\s+([A-Z][a-zA-Z.]+(?:\\s+[A-Z][a-zA-Z.]*){1,3})$")
  has_embedded_author <- !is.na(author_m_check[1,1])
  if (!allow_s10 && !has_embedded_author) return(NA_integer_)
  #
  # Many CONTENTS entries embed the author after the title:
  #   "One Sunrise Elsie E. Barrett"  -> title "One Sunrise" + author "Elsie E. Barrett"
  #   "A Tribute Annie Wells Cannon"  -> title "A Tribute"   + author "Annie Wells Cannon"
  # In the article body, the author appears on a byline: "By Elsie E. Barrett"
  # This strategy extracts a candidate author from the trailing capitalized-name
  # suffix of the title and searches for it (with and without "By").
  #
  # Guard: Portrait titles already have strategy 6 (name extraction after "Portrait of").
  # Running strategy 10 on them confuses the portrait subject for an author byline,
  # causing false matches when the person's name appears elsewhere in the body.
  if (str_detect(title, regex("^Portrait", ignore_case = TRUE))) return(NA_integer_)
  #
  # Candidate author: 2-3 trailing words that are ALL Title-Case or UPPER (names),
  # preceded by a single-word or short title part.
  author_m <- str_match(title,
    "^(.{3,40}?)\\s+([A-Z][a-zA-Z.]+(?:\\s+[A-Z][a-zA-Z.]*){1,3})$")
  # Greedy fallback: if the lazy split puts a title word in the author group
  # (title_part has no significant words >= 5 chars), try greedy split
  # to prefer a longer title_part and shorter author.
  # e.g. "Song for Morning Katherine Fernelius":
  #   lazy:   title="Song for", author="Morning Katherine Fernelius" — BAD
  #   greedy: title="Song for Morning", author="Katherine Fernelius" — GOOD
  if (!is.na(author_m[1,1])) {
    tp_check <- get_significant_words(str_trim(author_m[1,2]))
    if (!any(nchar(tp_check) >= 5)) {
      author_m2 <- str_match(title,
        "^(.{3,40})\\s+([A-Z][a-zA-Z.]+(?:\\s+[A-Z][a-zA-Z.]*){1,3})$")
      if (!is.na(author_m2[1,1])) author_m <- author_m2
    }
  }
  if (!is.na(author_m[1,1])) {
    title_part <- str_trim(author_m[1,2])   # e.g. "One Sunrise"
    author_str <- str_trim(author_m[1,3])   # e.g. "Elsie E. Barrett"
    last_name  <- str_extract(author_str, "[A-Za-z]+$")   # e.g. "Barrett"

    # Safety guard: author_str must look like a real personal name.
    # Require the LAST word (surname) to be >= 4 chars (rules out "Men", "Cox", "Wu").
    # 4-char surnames like Lund, Lind, Done, Reed, Page are common in these texts.
    is_valid_author <- !is.na(last_name) && nchar(last_name) >= 4

    # Guard for 10a/10b: only search by author name when title_part has at least
    # one significant word >= 5 chars. (Lowered from 6 to catch titles like
    # "A Song for New Years" where "Years"=5, "Winter Grass" where "Grass"=5.)
    tp_sigs      <- get_significant_words(title_part)
    tp_long_sigs <- tp_sigs[nchar(tp_sigs) >= 5]
    author_search_safe <- length(tp_long_sigs) >= 1

    if (is_valid_author) {
      # 10a. "By <full author>" in body (e.g. "By Elsie E. Barrett")
      # After matching, verify that at least one of the first two name-words
      # in author_str appears near the match.  This prevents false positives
      # from a different person with the same surname (e.g. matching
      # "By Elsie C. Carroll" when seeking "By Velma B. Carroll") while
      # tolerating wrong splits where a title word lands in author_str
      # (e.g. author_str = "Still Elsie E. Barrett" — "Still" is really
      # part of the title, but "Elsie" IS near the match → accept).
      if (author_search_safe) {
        pos <- try_pat(paste0("[Bb]y\\s+[A-Z][a-zA-Z.]+(?:\\s+[A-Z.]+){0,2}\\s+",
                              esc(last_name), "\\b"))
        if (!is.na(pos)) {
          author_names <- str_extract_all(author_str, "[A-Za-z]{3,}")[[1]]
          author_names <- head(author_names[author_names != last_name], 2)
          if (length(author_names) >= 1) {
            near <- str_sub(text, max(1L, pos - 5L), min(nchar(text), pos + 120L))
            name_found <- any(sapply(author_names, function(nm)
              str_detect(near, regex(paste0("\\b", esc(nm), "\\b"),
                                     ignore_case = TRUE))))
            if (name_found) return(pos)
            # No author name confirmed — fall through to S10b
          } else {
            return(pos)   # no name words to verify; accept
          }
        }
      }

      # 10b. Full author string (handles "Elsie E. Barrett" or "Annie Wells Cannon")
      if (author_search_safe) {
        pos <- try_pat(str_replace_all(esc(author_str), "\\s+", "\\\\s+"))
        if (!is.na(pos)) return(pos)
      }

      # 10c. Just the title part — only when title_part has >= 2 sig words >= 5 chars each,
      # or one sig word >= 8 chars.  Short/common title parts match too many places.
      tp_long5 <- tp_sigs[nchar(tp_sigs) >= 5]
      tp_long8 <- tp_sigs[nchar(tp_sigs) >= 8]
      title_search_safe <- length(tp_long5) >= 2 || length(tp_long8) >= 1
      if (title_search_safe && title_part != title) {
        pos <- try_pat(str_replace_all(esc(title_part), "\\s+", "\\\\s+"))
        if (!is.na(pos)) return(pos)
      }

      # 10d. Title sig word + last-name proximity (first sig word only, forward)
      if (author_search_safe && length(tp_sigs) >= 1) {
        pos <- try_pat(paste0("\\b", esc(tp_sigs[1]), "\\b.{0,200}\\b",
                              esc(last_name), "\\b"))
        if (!is.na(pos)) return(pos)
      }

      # 11. Combined title+author proximity — ALL sig words tried in both directions.
      # This is the "title separated from author by minimal words" strategy.
      # The article heading and byline may appear on adjacent lines:
      #   TITLE WORDS                     ← article heading line
      #   By Author Name                  ← byline line (already caught by 10a)
      # OR they may appear separately in running text.
      # Strategy 11 tries every sig word paired with the last name, forward AND reverse,
      # with a generous gap allowance. Requires sig word >= 4 chars to reduce noise.
      # Reverse direction (last_name before sig_word) catches cases where author
      # attribution appears above the title (e.g. photo captions or section headers).
      # When require_para_start=TRUE (no page_index files), the match must begin at
      # a line/paragraph start to prevent false matches inside article body text.
      tp_fn <- if (require_para_start) try_pat_para else try_pat
      for (sw in tp_sigs[nchar(tp_sigs) >= 4]) {
        # Forward: title word appears first, then author last name
        pos <- tp_fn(paste0("\\b", esc(sw), "\\b.{0,400}\\b", esc(last_name), "\\b"))
        if (!is.na(pos)) return(pos)
        # Reverse: author last name appears first, then title word (within ~2 lines)
        pos <- tp_fn(paste0("\\b", esc(last_name), "\\b.{0,120}\\b", esc(sw), "\\b"))
        if (!is.na(pos)) return(pos)
      }
    }
  }

  # 12. OCR character-class substitution
  # Replace common OCR-confused characters with character classes in the regex.
  # Handles: l/I/1 confusion, O/0, rn/m, U/V confusion, etc.
  ocr_title <- title
  ocr_title <- str_replace_all(ocr_title, "l", "[lI1]")
  ocr_title <- str_replace_all(ocr_title, "I", "[lI1]")
  ocr_title <- str_replace_all(ocr_title, "O", "[O0]")
  ocr_title <- str_replace_all(ocr_title, "rn", "(?:rn|m)")
  ocr_sigs <- get_significant_words(title)
  ocr_sigs <- ocr_sigs[nchar(ocr_sigs) >= 4]
  if (length(ocr_sigs) >= 2) {
    ocr_pats <- sapply(ocr_sigs[seq_len(min(3, length(ocr_sigs)))], function(w) {
      w <- str_replace_all(w, "l", "[lI1]")
      w <- str_replace_all(w, "I", "[lI1]")
      w <- str_replace_all(w, "O", "[O0]")
      paste0("\\b", w, "\\b")
    })
    pat <- paste(ocr_pats, collapse=".{0,120}")
    pos <- try_pat(pat)
    if (!is.na(pos)) return(pos)
  }

  # 13. Known recurring title matching
  # Many issues contain recurring sections with predictable titles.
  # When the CONTENTS OCR is garbled, try matching the known body heading.
  known_titles <- c(
    "Happenings", "HAPPENINGS",
    "Notes from the Field", "NOTES FROM THE FIELD",
    "Notes to the Field", "NOTES TO THE FIELD",
    "Lesson Department", "LESSON DEPARTMENT",
    "Magazine Drive", "MAGAZINE DRIVE",
    "Guide Lessons", "GUIDE LESSONS",
    "Book Notices", "BOOK NOTICES",
    "Editorials?", "EDITORIALS?"
  )
  t_lower <- tolower(title)
  for (kt in known_titles) {
    # Check if the garbled title shares >=3 consecutive chars with a known title
    kt_lower <- tolower(kt)
    # Try direct regex match first
    if (str_detect(t_lower, fixed(kt_lower))) {
      pos <- try_pat(paste0("\\b", esc(kt), "\\b"))
      if (!is.na(pos)) return(pos)
    }
    # Check for partial overlap (at least 4 consecutive matching chars)
    for (start in seq_len(max(1, nchar(kt_lower) - 3))) {
      substr_kt <- str_sub(kt_lower, start, start + 3)
      if (str_detect(t_lower, fixed(substr_kt))) {
        pos <- try_pat(paste0("\\b", esc(kt), "\\b"))
        if (!is.na(pos)) return(pos)
        break
      }
    }
  }

  # 14. First significant words only — when the full title fails, try just
  # the first 2 significant words. Only runs when both words are >= 5 chars
  # to avoid false matches from short common words. The gap between words
  # is limited to 40 chars to match heading proximity (not body text).
  if (length(sigs) >= 2) {
    first2 <- sigs[seq_len(min(2, length(sigs)))]
    if (all(nchar(first2) >= 5)) {
      pat <- paste(sapply(first2, function(w) paste0("\\b", esc(w), "\\b")),
                   collapse=".{0,40}")
      pos <- try_pat(pat)
      if (!is.na(pos)) return(pos)
    }
  }

  NA_integer_
}
# Page-guided search: narrow -> wide -> full body with plausibility guard
# Strategy 10 (author-name search) runs in all windows but full-body results
# are validated against the page estimate to prevent false positives.
find_article_start <- function(text, title, pg, page_index, body_start, body_end) {
  CPP <- 2400L

  # Full-body search if page index too small (no page estimate to validate against)
  if (nrow(page_index) < 3)
    return(find_in_window(text, title, body_start, body_end, allow_s10=TRUE))

  pg_est <- page_to_pos(page_index, pg, body_start, body_end)

  # Narrow (±2 pages) — S10 allowed, bounded window
  s1 <- max(body_start, page_to_pos(page_index, max(1L,pg-2L), body_start, body_end) - CPP)
  e1 <- min(body_end,   page_to_pos(page_index, pg+3L,         body_start, body_end) + CPP)
  pos <- find_in_window(text, title, s1, e1, allow_s10=TRUE)
  if (!is.na(pos)) return(pos)

  # Wide (±5 pages) — S10 allowed, bounded window
  s2 <- max(body_start, page_to_pos(page_index, max(1L,pg-5L), body_start, body_end) - CPP*2L)
  e2 <- min(body_end,   page_to_pos(page_index, pg+6L,         body_start, body_end) + CPP*2L)
  pos <- find_in_window(text, title, s2, e2, allow_s10=TRUE)
  if (!is.na(pos)) return(pos)

  # Full-body — S10 allowed but result validated against page estimate
  pos_fb <- find_in_window(text, title, body_start, body_end, allow_s10=TRUE)
  if (!is.na(pos_fb) && (is.na(pg_est) || abs(pos_fb - pg_est) <= 25000L))
    return(pos_fb)
  NA_integer_
}
```

```{r header-cleaner}
# ============================================================
# RUNNING HEADER CLEANER
# Removes OCR-embedded running headers from extracted article text.
# ============================================================
clean_headers <- function(txt) {
  # "N RELIEF SOCIETY MAGAZINE" even-page headers
  txt <- str_replace_all(txt,
    regex("\\d{1,3}\\s+(?:THE\\s+)?RELIEF\\s+SOCIETY\\s+MAGAZINE\\.?"), " ")
  # "RELIEF SOCIETY MAGAZINE N" reversed
  txt <- str_replace_all(txt,
    regex("(?:THE\\s+)?RELIEF\\s+SOCIETY\\s+MAGAZINE\\.?\\s+\\d{1,3}"), " ")
  # "RELIEF SOCIETY MAGAZINE—MONTH, YEAR" running header (em-dash + month + year)
  txt <- str_replace_all(txt,
    regex("(?:THE\\s+)?RELIEF\\s+SOCIETY\\s+MAGAZINE[\u2014\u2013—-]+\\s*[A-Z]+,?\\s+\\d{4}",
          ignore_case=TRUE), " ")
  # "THE Relief Society Magazine Vol. N No. N" mixed-case body header
  txt <- str_replace_all(txt,
    regex("THE\\s+Relief\\s+Society\\s+Magazine\\s+VOL\\.?\\s+[IVXL0-9]+[^\\n]{0,40}No\\.?\\s+\\d+",
          ignore_case=FALSE), " ")
  # "RELIEF SOCIETY CONFERENCE NNN" running head (conference issue)
  txt <- str_replace_all(txt,
    regex("RELIEF\\s+SOCIETY\\s+CONFERENCE\\s+\\d{1,4}"), " ")
  # Board roster block — full block from "THE RELIEF SOCIETY OF THE CHURCH"
  # or "Motto" through to Editor/Manager lines
  txt <- str_replace_all(txt,
    regex("(?:THE\\s+(?:RELIEF\\s+SOCIETY|CHURCH)\\s+OF[\\s\\S]{0,2000}?(?:Assistant\\s+Manager|Manager|Amy\\s+Brown\\s+Lyman)[^\\n]*)",
          dotall=TRUE, ignore_case=TRUE), " ")
  # Also strip shorter board fragments that may remain
  txt <- str_replace_all(txt,
    regex("Motto[^\\n]{0,40}Charity[\\s\\S]{0,2000}?(?:Assistant\\s+Manager|Manager|Amy\\s+Brown\\s+Lyman)[^\\n]*",
          dotall=TRUE, ignore_case=TRUE), " ")
  txt <- str_replace_all(txt,
    regex("(?:PRESIDENCY\\s+AND\\s+)?GENERAL\\s+BOARD[^\\n]{0,200}(?:Salt Lake City|Bishop.*?Building|Room\\s+\\d+|Music Director)",
          dotall=TRUE, ignore_case=TRUE), " ")
  # Collapse extra whitespace but preserve paragraph breaks
  txt <- str_replace_all(txt, "[ \\t]{3,}", "  ")
  str_trim(txt)
}
```

```{r process-issue}
# ============================================================
# PROCESS ISSUE
# Core function: reads one split-issue .txt file and extracts
# one text file per article.
#
# ARTICLE BOUNDARY LOGIC:
# 1. Parse CONTENTS -> list of (title, page)
# 2. Search for each title in body_start..body_end ONLY
#    (CONTENTS listing is explicitly excluded from search)
# 3. Sort found positions; each article runs from its start
#    to the next article's start (or body_end for the last)
# 4. ALL text from body_start to body_end is accounted for:
#    - Gaps between articles -> Misc_gap files
#    - Text before first article -> Misc_front
#    - Text after last article -> Misc_back
#    No text is ever discarded.
# 5. Articles not found in OCR text -> placeholder file
#    stating text is absent from source.
# ============================================================
process_issue <- function(filepath, output_dir) {
  filename <- basename(filepath)
  meta     <- get_metadata(filename)
  if (is.na(meta$month))  meta$month  <- "Unknown"
  if (is.na(meta$volume)) meta$volume <- "XX"
  if (is.na(meta$year))   meta$year   <- "????"
  if (is.na(meta$number)) meta$number <- "0"

  text <- read_file_safe(filepath)
  len  <- nchar(text)

  # ----------------------------------------------------------
  # Pre-process: Insert paragraph breaks at running header positions.
  # Some OCR files have massive run-together lines where multiple
  # articles flow on a single line.  Running headers like
  # "598 RELIEF SOCIETY MAGAZINE—SEPTEMBER 1942" mark page boundaries
  # but have no surrounding newlines.  Inserting \n\n at these positions
  # restores paragraph breaks so snap_to_para_start can find article
  # boundaries.
  #
  # SELECTIVE: Only process individual lines that have 3+ running headers.
  # Lines with fewer headers are single-article paragraphs that just
  # happen to span a page break — inserting breaks there disrupts
  # find_in_window position matching.
  # ----------------------------------------------------------
  rh_break <- paste0(
    "(?:\\d{1,3}\\s+(?:Vol\\.?\\s*\\d+[^\\n]{0,30})?)?",
    "(?:THE\\s+)?RELIEF\\s+SOCIETY\\s+MAGAZINE",
    "(?:[^A-Za-z\\n]{0,5}",
      "(?:JANUARY|FEBRUARY|MARCH|APRIL|MAY|JUNE|JULY|AUGUST|",
      "SEPTEMBER|OCTOBER|NOVEMBER|DECEMBER)[,\\s]*\\d{4})?"
  )
  rh_break_re <- regex(rh_break, ignore_case=FALSE)
  lines_vec <- str_split(text, "\n")[[1]]
  rh_ct <- 0L
  for (li in seq_along(lines_vec)) {
    if (nchar(lines_vec[li]) > 2000L && str_count(lines_vec[li], rh_break_re) >= 3L) {
      ct_before <- str_count(lines_vec[li], rh_break_re)
      # Insert \n\n around each header occurrence in this line
      lines_vec[li] <- str_replace_all(lines_vec[li],
        regex(paste0("(", rh_break, ")"), ignore_case=FALSE),
        "\n\n\\1\n\n")
      rh_ct <- rh_ct + ct_before
    }
  }
  if (rh_ct > 0L) {
    text <- paste(lines_vec, collapse="\n")
    len  <- nchar(text)
    cat("  >> Inserted", rh_ct, "header breaks in lines with 3+ running headers.\n")
  }

  cat("\n", rep("=",70), "\n", sep="")
  cat("FILE:", filename, "\n")
  cat("SIZE:", format(len, big.mark=","), "chars\n")

  # Output folder: output/Vol16_1929/March/
  out_folder <- file.path(output_dir,
                          paste0("Vol", meta$volume, "_", meta$year),
                          meta$month)
  if (dir.exists(out_folder)) unlink(out_folder, recursive=TRUE)
  dir.create(out_folder, showWarnings=FALSE, recursive=TRUE)

  prefix <- paste0(meta$month, "_Vol", meta$volume, "_No", meta$number)

  # ----------------------------------------------------------
  # Step 1: Locate sections
  # ----------------------------------------------------------
  s <- find_sections(text)
  body_start <- s$body_start
  body_end   <- s$body_end

  # Safety: ensure body_start does not overlap with contents region.
  # EXCEPTION: if body_start was set from a reliable VOL marker (e.g. "VOL. XVI MARCH, 1929 No. 3"),
  # trust it ONLY when it's well after the contents_start (at least 200 chars after).
  # If the VOL marker is AT or BEFORE the contents_start, it's part of the front-matter
  # masthead (e.g. "VOL. XXIII SEPTEMBER, 1936 No. 9" appearing right before "CONTENTS"),
  # not the body boundary. In that case, use contents_end + 1 instead.
  if (!is.na(s$contents_end) && !is.na(body_start) && body_start <= s$contents_end) {
    vol_is_front_matter <- isTRUE(s$vol_marker_found) &&
      !is.na(s$contents_start) &&
      body_start < (s$contents_start + 200L)

    if (isTRUE(s$vol_marker_found) && !vol_is_front_matter) {
      cat("  NOTE: body_start from VOL marker (", body_start,
          ") is before contents_end (", s$contents_end,
          ") — trusting VOL marker (well after CONTENTS start)\n", sep="")
      # Keep body_start as-is; the VOL marker is authoritative.
    } else {
      if (vol_is_front_matter) {
        cat("  NOTE: VOL marker (", body_start, ") is in front matter (at/before CONTENTS start ",
            s$contents_start, ") — advancing past contents_end\n", sep="")
      } else {
        cat("  WARNING: body_start inside CONTENTS region — advancing past contents_end\n")
      }
      body_start <- s$contents_end + 1L
      s$body_start <- body_start
    }
  }

  cat(sprintf("  CONTENTS: %s to %s\n",
              ifelse(is.na(s$contents_start),"?",s$contents_start),
              ifelse(is.na(s$contents_end),  "?",s$contents_end)))
  cat(sprintf("  body_start: %s  body_end: %s\n",
              format(body_start, big.mark=","),
              format(body_end,   big.mark=",")))

  # ----------------------------------------------------------
  # Step 2: Save CONTENTS and BOARD files, plus a _00_Misc.txt
  # containing ALL text from the beginning of the file up to
  # body_start (volume header, issue number, CONTENTS listing,
  # Board roster, etc.).  Every byte before the body is captured.
  # ----------------------------------------------------------
  pre_body_text <- str_trim(str_sub(text, 1L, body_start - 1L))
  if (nchar(pre_body_text) > 0) {
    # Trim any article text that leaked into the pre-body region.
    # Many issues print the first article (often a poem) on the inside front cover,
    # right after the last advertisement.  The reliable cut point is the LAST
    # "Mention Relief Society Magazine" ad footer — article text follows that.
    # Since the first article is already extracted correctly as a body article,
    # trimming here avoids a duplicate in _00_Misc.txt with no data loss.
    last_ad <- str_locate_all(pre_body_text,
      regex("Mention Relief Society Magazine", ignore_case=TRUE))[[1]]
    if (nrow(last_ad) > 0) {
      cut_pos <- last_ad[nrow(last_ad), "end"]
      pre_body_trimmed <- str_trim(str_sub(pre_body_text, 1L, cut_pos))
    } else {
      pre_body_trimmed <- pre_body_text
    }
    write_file(pre_body_trimmed,
               file.path(out_folder, paste0(prefix, "_00_Misc.txt")))
    trimmed_chars <- nchar(pre_body_text) - nchar(pre_body_trimmed)
    if (trimmed_chars > 10) {
      cat(sprintf("  Pre-body (00_Misc): %s chars (trimmed %s chars of article text already captured in body)\n",
                  format(nchar(pre_body_trimmed), big.mark=","),
                  format(trimmed_chars, big.mark=",")))
    } else {
      cat(sprintf("  Pre-body (00_Misc): %s chars\n",
                  format(nchar(pre_body_trimmed), big.mark=",")))
    }
  }

  if (!is.null(s$contents_text))
    write_file(str_trim(s$contents_text),
               file.path(out_folder, paste0(prefix, "_00_CONTENTS.txt")))

  board_text <- ""
  if (!is.na(s$board_start)) {
    board_text <- str_trim(str_sub(text, s$board_start, s$board_end))
    write_file(board_text,
               file.path(out_folder, paste0(prefix, "_00_BOARD.txt")))
    cat(sprintf("  Board: %d chars\n", nchar(board_text)))
  }

  # ----------------------------------------------------------
  # Step 3: Parse CONTENTS
  # ----------------------------------------------------------
  arts <- if (!is.null(s$contents_text))
    parse_contents_section(s$contents_text) else
    data.frame(title=character(), page=integer(), category=character(),
               stringsAsFactors=FALSE)

  # ----------------------------------------------------------
  # Step 3b: Fix outlier page numbers (OCR digit truncation)
  # ----------------------------------------------------------
  # OCR sometimes garbles the last digit of a page number, e.g. "58]" parses
  # as page 58 instead of 581.  Detect ISOLATED pages — those with < 2
  # neighbours within ±100 pages — and try appending a digit (0-9) to bring
  # them into the cluster.  This avoids false-fixing legitimate low pages
  # like pg 1-4 in January where all pages cluster together near 1-54.
  if (nrow(arts) >= 5) {
    valid_pgs <- arts$page[arts$page > 0]
    if (length(valid_pgs) >= 5) {
      pg_med <- median(valid_pgs)
      for (i in which(arts$page > 0)) {
        neighbors <- sum(abs(valid_pgs - arts$page[i]) <= 100) - 1L
        if (neighbors < 2L) {
          # Isolated page — try appending a digit
          candidates_pg <- arts$page[i] * 10L + 0:9
          dists <- abs(candidates_pg - pg_med)
          best  <- candidates_pg[which.min(dists)]
          fixed_neighbors <- sum(abs(valid_pgs - best) <= 100)
          if (fixed_neighbors >= 3L) {
            cat(sprintf("  PAGE FIX: '%s' pg %d -> %d (outlier corrected)\n",
                        str_sub(arts$title[i], 1, 40), arts$page[i], best))
            arts$page[i] <- best
          }
        }
      }
      # Re-sort by page to restore correct ordering after fixes
      arts <- arts[order(arts$page), ]

      # Step 3c: Remove entries with impossible page numbers.
      # OCR noise from "20 Bishop's Building" address creates stray page
      # numbers (2, 3, 20) that form a mini-cluster.  Detect a large gap
      # (>100 pages) in the sorted page sequence: if a small group of
      # entries (<=5) sits below the gap while the main cluster sits above,
      # remove the small group.  Safe for Jan issues because they have no
      # such gap (all pages are in the 1-60 range together).
      valid_pgs  <- sort(arts$page[arts$page > 0])
      if (length(valid_pgs) >= 5) {
        gaps <- diff(valid_pgs)
        big_gap_idx <- which(gaps > 100)
        if (length(big_gap_idx) > 0) {
          # Use the largest gap
          largest <- big_gap_idx[which.max(gaps[big_gap_idx])]
          below_n <- largest           # entries below the gap
          above_n <- length(valid_pgs) - largest
          if (below_n < above_n && below_n <= 5) {
            cutoff <- valid_pgs[largest]
            keep <- rep(TRUE, nrow(arts))
            for (i in seq_len(nrow(arts))) {
              if (arts$page[i] > 0 && arts$page[i] <= cutoff) {
                cat(sprintf("  JUNK REMOVED: '%s' pg %d (below gap; main cluster starts pg %d)\n",
                            str_sub(arts$title[i], 1, 50), arts$page[i],
                            valid_pgs[largest + 1L]))
                keep[i] <- FALSE
              }
            }
            arts <- arts[keep, ]
          }
        }
      }
    }
  }

  cat(sprintf("  Articles in CONTENTS: %d\n", nrow(arts)))

  if (nrow(arts) == 0) {
    # Save full body as one Misc file — no text is lost
    write_file(str_sub(text, body_start, body_end),
               file.path(out_folder, paste0(prefix, "_Misc_fullbody.txt")))
    cat("  No CONTENTS parsed. Full body saved as Misc.\n")
    return(data.frame(file=filename, n_contents=0L, n_saved=0L,
                      n_missed=0L, total_chars=len, stringsAsFactors=FALSE))
  }

  # ----------------------------------------------------------
  # Step 4: Build page index (within body only, positions absolute)
  # ----------------------------------------------------------
  body_text  <- str_sub(text, body_start, body_end)
  page_index <- build_page_index(body_text, body_start)
  cat(sprintf("  Page index: %d markers (from running headers)\n", nrow(page_index)))

  # Step 4b: Synthetic page index when running headers are absent
  # Many Vol24/Vol25 issues have no running headers with page numbers (OCR
  # stripped them), yet CONTENTS still lists articles with valid page numbers.
  # We can interpolate page positions linearly across the body text.
  # This enables Step 6 fallback strategies (author-near-page, caps-heading,
  # byline-pattern) that are otherwise skipped when page_index < 3.
  if (nrow(page_index) < 3 && nrow(arts) >= 3) {
    valid_pgs <- arts$page[arts$page > 0]
    if (length(valid_pgs) >= 3) {
      pg_min <- min(valid_pgs)
      pg_max <- max(valid_pgs)
      pg_range <- pg_max - pg_min
      if (pg_range > 0) {
        body_len <- body_end - body_start + 1L
        # Create synthetic markers at every unique CONTENTS page
        synth_pgs <- sort(unique(valid_pgs))
        synth_pos <- body_start +
          as.integer((synth_pgs - pg_min) / pg_range * (body_len - 1L))
        synth_df  <- data.frame(page = synth_pgs, position = synth_pos,
                                stringsAsFactors = FALSE)
        # Merge with any existing markers (existing take precedence)
        if (nrow(page_index) > 0) {
          synth_df <- synth_df[!synth_df$page %in% page_index$page, ]
        }
        page_index <- rbind(page_index, synth_df)
        page_index <- page_index[order(page_index$page), ]
        cat(sprintf("  Synthetic page index: %d total markers (interpolated from CONTENTS pages %d-%d)\n",
                    nrow(page_index), pg_min, pg_max))
      }
    }
  }

  # ----------------------------------------------------------
  # Step 5: TWO-PASS HYBRID SEARCH
  #
  # PASS A — Independent search (no sequential advancement):
  #   Each article searches its own page-windowed region of the full body,
  #   independently of every other article. search_from is NOT advanced.
  #   This means Strategy 10/11 false positives cannot cascade: if article [i]
  #   gets a wrong position, it cannot push article [i+1]'s search forward.
  #
  # PASS B — Order validation:
  #   The CONTENTS table defines the true article order. After all candidates
  #   are found, enforce monotonicity: if candidate[i] <= candidate[i-1]
  #   (i.e., this article appears to start before or at the same place as the
  #   previous one), the candidate is a false match and is discarded.
  #   The article then falls through to the page-estimate fallback in Step 6.
  # ----------------------------------------------------------
  candidates <- rep(NA_integer_, nrow(arts))   # raw finds from Pass A
  positions  <- rep(NA_integer_, nrow(arts))   # validated positions from Pass B
  CPP <- 2400L

  # ---- Pass A: independent per-article search ----
  for (i in seq_len(nrow(arts))) {
    title <- arts$title[i]
    pg    <- arts$page[i]
    cat_i <- arts$category[i]

    # Frontispiece / page-0 articles: always near start of body
    if (cat_i == "Frontispiece" || pg <= 0L) {
      ft <- str_trim(str_replace(title, regex("\\s+Frontispiece\\s*$",
                                              ignore_case=TRUE), ""))
      win_end <- min(body_end, body_start + 6000L)
      pos <- if (nchar(ft) >= 3)
        find_in_window(text, ft, body_start, win_end)
      else NA_integer_
      if (is.na(pos))
        pos <- find_in_window(text, title, body_start, win_end)
      if (!is.na(pos) &&
          !(cat_i == "Frontispiece" && (pos - body_start) > 2000L)) {
        # Distance guard: frontispiece captions live near body_start.
        # A match >2000 chars away is a false positive in article body.
        candidates[i] <- max(snap_to_para_start(text, pos, body_start, max_back=300L), body_start)
      } else if (cat_i == "Frontispiece") {
        # Image-only frontispiece OR distant false positive: leave as NA.
        # Step 11 will search pre-body regions; otherwise logged as NIS.
        # Do NOT fall back to body_start — that merges with the first
        # real article and absorbs its content.
      } else {
        candidates[i] <- body_start   # page-0 non-frontispiece fallback
      }
      next
    }

    # Normal articles: narrow → wide → full-body, each bounded by page estimate.
    # IMPORTANT: search always starts from body_start (not search_from),
    # so articles can be found even if a previous article's position was wrong.
    if (nrow(page_index) >= 3) {
      pg_est <- page_to_pos(page_index, pg, body_start, body_end)
      # Only use narrow/wide windows when page index has enough markers (>= 6)
      # for reliable position estimates. With fewer markers, interpolation is too
      # coarse and the window may center on the wrong occurrence of a title
      # (e.g. in lesson previews instead of the actual article).
      pos <- NA_integer_
      if (nrow(page_index) >= 6) {
        # Narrow window: pg ± 3–4 pages
        s1 <- max(body_start,
                  page_to_pos(page_index, max(1L, pg-3L), body_start, body_end) - CPP)
        e1 <- min(body_end,
                  page_to_pos(page_index, pg+4L, body_start, body_end) + CPP)
        pos <- find_in_window(text, title, s1, e1, allow_s10=TRUE)
        # Wide window: pg ± 6–7 pages
        if (is.na(pos)) {
          s2 <- max(body_start,
                    page_to_pos(page_index, max(1L, pg-6L), body_start, body_end) - CPP*2L)
          e2 <- min(body_end,
                    page_to_pos(page_index, pg+7L, body_start, body_end) + CPP*2L)
          pos <- find_in_window(text, title, s2, e2, allow_s10=TRUE)
        }
      }
      # Full-body fallback: plausibility-checked against pg_est.
      # Conference proceedings articles (Work and Business Meeting, General Session,
      # etc.) often appear as subsection headings EARLIER in the body than their
      # page number suggests — use a wider tolerance (50,000 chars) for those.
      # SPECIAL CASE: When pg_est was clamped to body_end (because ALL page markers
      # extrapolate beyond body_end), the pg_est is unreliable — it simply reflects
      # the end of the file, not a real position estimate. For conference session
      # headings in this situation the gap can exceed 100k chars (e.g. Jun16 where
      # "Work and Business Meeting" is at @25816 but pg_est = body_end = 149966).
      # In that case, skip the plausibility check entirely and use the full-body find.
      if (is.na(pos)) {
        pos_fb <- find_in_window(text, title, body_start, body_end, allow_s10=FALSE)
        if (!is.na(pos_fb)) {
          # pg_est is unreliable when:
          #   (a) clamped to body_end  — page number extrapolates beyond the file, OR
          #   (b) extrapolated below body_start — inverted/disordered page markers
          # In either case the estimate is meaningless, so skip the plausibility check.
          # pg_est is unreliable when it falls outside the body:
          #   >= body_end : extrapolation put the estimate past the end of the file
          #                 (covers both clamped-to-body_end AND unclamped overshoots,
          #                  e.g. pg352 in a conference issue where the last page marker
          #                  is pg338 → estimate = 169,222 >> body_end = 149,966)
          #   < body_start: negative/backward extrapolation from inverted page markers
          pg_est_is_clamped  <- !is.na(pg_est) && (pg_est >= body_end)
          pg_est_is_negative <- !is.na(pg_est) && (pg_est < body_start)
          pg_est_unreliable  <- pg_est_is_clamped || pg_est_is_negative
          plausible <- is.na(pg_est) ||
                       pg_est_unreliable  ||
                       abs(pos_fb - pg_est) <= 25000L
          pos <- if (plausible) pos_fb else NA_integer_
        }
      }
      # S10 full-body fallback: uses author-proximity strategies (allow_s10=TRUE).
      if (is.na(pos)) {
        pos_fb2 <- find_in_window(text, title, body_start, body_end, allow_s10=TRUE)
        if (!is.na(pos_fb2)) {
          pg_est_is_clamped2  <- !is.na(pg_est) && (pg_est >= body_end)
          pg_est_is_negative2 <- !is.na(pg_est) && (pg_est < body_start)
          pg_est_unreliable2  <- pg_est_is_clamped2 || pg_est_is_negative2
          plausible2 <- is.na(pg_est) ||
                        pg_est_unreliable2 ||
                        abs(pos_fb2 - pg_est) <= 25000L
          pos <- if (plausible2) pos_fb2 else NA_integer_
        }
      }
    } else {
      # No page index: search full body with S10/S11.
      pos <- find_in_window(text, title, body_start, body_end, allow_s10=TRUE)
    }

    if (!is.na(pos)) {
      candidates[i] <- max(snap_to_para_start(text, pos, body_start), body_start)
    }
  }

  # ---- Pass B: Enforce monotonic ordering ----
  # Articles are already in page order from parse_contents_section().
  # Enforce that positions increase monotonically: each article's position
  # must be >= the previous article's accepted position.  This ensures the
  # script processes the file from beginning to end without splicing.
  #
  # If a candidate position is BEFORE the previous article's position,
  # the match is likely a false hit (e.g. a repeated word earlier in the
  # file).  Re-search the title ONLY in the valid forward region.
  min_allowed_pos <- body_start
  for (i in seq_len(nrow(arts))) {
    if (!is.na(candidates[i])) {
      if (candidates[i] >= min_allowed_pos) {
        # Candidate is in valid forward position — accept it
        positions[i] <- candidates[i]
        # "Notes from/to the Field" are catch-all sections whose positions
        # can be unreliable (e.g., matching a generic header ahead of where
        # the section actually begins).  Don't let them advance
        # min_allowed_pos — this prevents cascading displacement of
        # subsequent articles (editorial, lessons) that may appear earlier
        # in the body text despite having higher page numbers.
        is_notes <- str_detect(arts$title[i],
                               regex("^Notes\\s+(from|to)\\s+the\\s+Field",
                                     ignore_case=TRUE))
        if (!is_notes) {
          min_allowed_pos <- candidates[i] + 1L
        }
      } else {
        # Candidate is BEFORE previous article — re-search forward only
        pos2 <- find_in_window(text, arts$title[i], min_allowed_pos, body_end,
                               allow_s10=TRUE)
        if (!is.na(pos2)) {
          fwd_jump   <- pos2 - candidates[i]
          near_start <- candidates[i] <= (body_start + 5000L)
          # Guard against cascade: reject reorders with large jumps, or
          # reorders that land far from the expected page position.
          # This prevents cascading displacement where one bad reorder
          # pushes min_allowed_pos far forward, forcing all subsequent
          # articles to cluster at the end of the file.
          reject_reorder <- FALSE
          if ((near_start && fwd_jump > 50000L) || fwd_jump > 40000L) {
            reject_reorder <- TRUE
            cat(sprintf("    [%02d] rejected reorder: @%d -> @%d (jump %d too large)\n",
                        i, candidates[i], pos2, fwd_jump))
          } else if (fwd_jump > 15000L && nrow(page_index) >= 6 &&
                     arts$page[i] > 0) {
            # For moderate jumps (15K-40K), also check page-estimate distance.
            # If the reorder lands far from the page estimate, it's likely
            # a cascade artifact rather than a correct placement.
            pg_est_reorder <- page_to_pos(page_index, arts$page[i],
                                          body_start, body_end)
            if (!is.na(pg_est_reorder) &&
                abs(pos2 - pg_est_reorder) > 35000L) {
              reject_reorder <- TRUE
              cat(sprintf("    [%02d] rejected reorder: @%d -> @%d (page est @%d, dist %d too far)\n",
                          i, candidates[i], pos2, pg_est_reorder,
                          abs(pos2 - pg_est_reorder)))
            }
          }
          if (reject_reorder) {
            # Leave positions[i] = NA for Step 6 / Step 11 fallback
          } else {
            positions[i] <- max(snap_to_para_start(text, pos2, min_allowed_pos), min_allowed_pos)
            min_allowed_pos <- positions[i] + 1L
            cat(sprintf("    [%02d] reordered: was @%d, now @%d (forward-only)\n",
                        i, candidates[i], positions[i]))
          }
        }
        # If not found forward, leave as NA for Step 6 fallback
      }
    }
  }

  # ---- Report found positions ----
  for (i in seq_len(nrow(arts))) {
    pg <- arts$page[i]
    cat(sprintf("    [%02d] pg%3s %-48s -> %s\n", i,
                ifelse(is.numeric(pg), as.character(as.integer(pg)), pg),
                str_sub(arts$title[i],1,48),
                if (!is.na(positions[i])) paste0("@", positions[i]) else "MISS"))
  }

  # ----------------------------------------------------------
  # Step 6: Page-position fallback for remaining misses
  # Enhanced: also try to find a "By [Author]" pattern near the
  # estimated page position, or an ALL-CAPS heading, when the
  # garbled CONTENTS title itself can't be matched.
  # All positions are constrained to be:
  #   >= min_allowed_pos (previous article's position + 1)
  #   <  max_allowed_pos (next article's already-accepted position)
  # This maintains monotonic ordering from beginning to end of file.
  # ----------------------------------------------------------
  min_allowed_pos <- body_start
  for (i in seq_len(nrow(arts))) {
    if (!is.na(positions[i])) {
      min_allowed_pos <- positions[i] + 1L
      next
    }
    if (arts$page[i] <= 0L || nrow(page_index) < 3) next
    # Find the next already-accepted position (max constraint)
    max_allowed_pos <- body_end
    for (j in (i+1L):min(nrow(arts), i+20L)) {
      if (j > nrow(arts)) break
      if (!is.na(positions[j])) { max_allowed_pos <- positions[j] - 1L; break }
    }
    est <- page_to_pos(page_index, arts$page[i], body_start, body_end)
    # Clamp estimate to be within [min_allowed_pos, max_allowed_pos]
    est <- max(est, min_allowed_pos)
    est <- min(est, max_allowed_pos)
    if (est >= body_start && est <= max_allowed_pos) {
      # Search backward from est, but never before min_allowed_pos
      back_start <- max(min_allowed_pos, est - 2000L)
      search_end <- min(max_allowed_pos, est + 500L)
      pos_try <- find_in_window(text, arts$title[i], back_start, search_end,
                                allow_s10=TRUE)
      if (!is.na(pos_try) && pos_try >= min_allowed_pos && pos_try <= max_allowed_pos) {
        positions[i] <- max(snap_to_para_start(text, pos_try, min_allowed_pos), min_allowed_pos)
      } else {
        # Try extracting author last name from title and searching for "By [Name]"
        author_m_fb <- str_match(arts$title[i],
          "^.{2,40}?\\s+([A-Z][a-zA-Z.]+(?:\\s+[A-Z][a-zA-Z.]*){1,3})$")
        if (!is.na(author_m_fb[1,1])) {
          fb_author <- str_trim(author_m_fb[1,2])
          fb_last   <- str_extract(fb_author, "[A-Za-z]+$")
          if (!is.na(fb_last) && nchar(fb_last) >= 4) {
            fb_chunk <- str_sub(text, back_start, search_end)
            fb_pat   <- paste0("[Bb]y\\s+[A-Z][a-zA-Z.]+(?:\\s+[A-Z.]+){0,2}\\s+",
                               str_replace_all(fb_last, "([.?*+^$\\[\\]\\\\(){}|])", "\\\\\\1"),
                               "\\b")
            fb_m <- tryCatch(str_locate(fb_chunk, regex(fb_pat, ignore_case=FALSE)),
                             error=function(e) matrix(NA_integer_,1,2))
            if (!is.na(fb_m[1,1])) {
              fb_pos <- back_start + fb_m[1,1] - 1L
              if (fb_pos >= min_allowed_pos && fb_pos <= max_allowed_pos) {
                positions[i] <- max(snap_to_para_start(text, fb_pos, min_allowed_pos, max_back=300L),
                                    min_allowed_pos)
                cat(sprintf("    [%02d] pg%3d %-48s -> @%d [author-near-page]\n",
                            i, arts$page[i], str_sub(arts$title[i],1,48), positions[i]))
              }
            }
          }
        }
        if (!is.na(positions[i])) {
          min_allowed_pos <- positions[i] + 1L; next
        }
        # Text pattern inference
        fb_chunk2 <- str_sub(text, back_start, search_end)

        # Look for ALL-CAPS headings
        caps_pat <- "(?<=\\n)\\s*([A-Z][A-Z ]{5,60})\\s*(?=\\n)"
        caps_m   <- str_locate_all(fb_chunk2, regex(caps_pat))[[1]]
        if (nrow(caps_m) > 0) {
          for (ci in seq_len(nrow(caps_m))) {
            caps_text <- str_sub(fb_chunk2, caps_m[ci,1], caps_m[ci,2])
            if (!str_detect(caps_text, regex("RELIEF SOCIETY|MAGAZINE|ADVERTISERS",
                                             ignore_case=FALSE))) {
              fb_pos <- back_start + caps_m[ci,1] - 1L
              if (fb_pos >= min_allowed_pos && fb_pos <= max_allowed_pos) {
                positions[i] <- max(snap_to_para_start(text, fb_pos, min_allowed_pos, max_back=300L),
                                    min_allowed_pos)
                cat(sprintf("    [%02d] pg%3d %-48s -> @%d [caps-heading]\n",
                            i, arts$page[i], str_sub(arts$title[i],1,48), positions[i]))
                break
              }
            }
          }
          if (!is.na(positions[i])) {
            min_allowed_pos <- positions[i] + 1L; next
          }
        }

        # Look for "By [Name]" byline pattern
        byline_pat <- "(?<=\\n)\\s*[Bb]y\\s+[A-Z][a-zA-Z.]+(?:\\s+[A-Z][a-zA-Z.]+){1,3}\\s*(?=\\n)"
        byline_m   <- str_locate_all(fb_chunk2, regex(byline_pat))[[1]]
        if (nrow(byline_m) > 0) {
          fb_pos <- back_start + byline_m[1,1] - 1L
          if (fb_pos >= min_allowed_pos && fb_pos <= max_allowed_pos) {
            positions[i] <- max(snap_to_para_start(text, fb_pos, min_allowed_pos, max_back=300L),
                                min_allowed_pos)
            cat(sprintf("    [%02d] pg%3d %-48s -> @%d [byline-pattern]\n",
                        i, arts$page[i], str_sub(arts$title[i],1,48), positions[i]))
          }
        }
        if (!is.na(positions[i])) {
          min_allowed_pos <- positions[i] + 1L; next
        }

        # Final fallback: snap to paragraph break, constrained to valid range
        positions[i] <- min(
          max(snap_to_para_start(text, est, min_allowed_pos, max_back=1000L),
              min_allowed_pos),
          max_allowed_pos)
      }
      # Update min_allowed_pos after any assignment.
      # Use proportional advancement: advance by at least half the expected
      # page gap to the next article.  This prevents consecutive page-est
      # articles from clustering at sequential +1 offsets, which produces
      # tiny/empty files for articles on adjacent pages.
      if (!is.na(positions[i])) {
        next_pg <- NA_integer_
        for (j in (i + 1L):min(nrow(arts), i + 10L)) {
          if (j > nrow(arts)) break
          if (arts$page[j] > 0) { next_pg <- arts$page[j]; break }
        }
        if (!is.na(next_pg) && arts$page[i] > 0 && next_pg >= arts$page[i]) {
          pg_diff <- max(1L, next_pg - arts$page[i])
          min_gap <- as.integer(CPP * pg_diff / 3L)
          min_allowed_pos <- positions[i] + max(1L, min_gap)
        } else {
          min_allowed_pos <- positions[i] + 1L
        }
      }
      cat(sprintf("    [%02d] pg%3d %-48s -> @%d [page-est]\n",
                  i, arts$page[i], str_sub(arts$title[i],1,48), positions[i]))
    }
  }

  # ----------------------------------------------------------
  # Step 7: Assign boundaries
  # Each article: start_pos to (next_start - 1), last to body_end.
  # Missed articles (not found in OCR) get placeholder files.
  # ----------------------------------------------------------

  # Build a sorted table of found articles
  found_idx <- which(!is.na(positions))
  miss_idx  <- which(is.na(positions))

  saved_count <- 0L

  if (length(found_idx) == 0) {
    # Nothing found — save entire body as one Misc file
    write_file(str_sub(text, body_start, body_end),
               file.path(out_folder, paste0(prefix, "_Misc_fullbody.txt")))
    cat("  No article positions found. Full body saved.\n")
    return(data.frame(file=filename, n_contents=nrow(arts), n_saved=0L,
                      n_missed=nrow(arts), total_chars=len, stringsAsFactors=FALSE))
  }

  art_tbl <- data.frame(
    orig_i   = found_idx,
    position = positions[found_idx],
    stringsAsFactors=FALSE)
  # Positions are already in monotonic page order from Pass B enforcement.
  # Do NOT re-sort by position — this preserves the CONTENTS ordering
  # and prevents articles from being spliced out of order.

  # ----------------------------------------------------------
  # Step 7b: Group near-adjacent articles for merging.
  #
  # Articles listed separately in the CONTENTS sometimes correspond to
  # continuous text in the OCR (e.g. Morning + Afternoon sessions,
  # or three short companion pieces with no gap between them).
  # When consecutive articles are within MERGE_THRESH characters of
  # each other — including the exact-same-position case (both resolve
  # to body_start or to the same section heading) — they are merged
  # into ONE output file.  The file is labelled with the title of the
  # first article in the group; all subsequent titles are appended
  # after a " + " separator so the combined content is traceable.
  #
  # This replaces the old "+1 offset" disambiguation which created
  # 1-character stub files for all but the last article at a shared
  # position.
  # ----------------------------------------------------------
  MERGE_THRESH <- 10L

  groups    <- list()
  cur_grp   <- c(1L)
  for (k in seq_len(nrow(art_tbl))) {
    if (k == 1L) {
      cur_grp <- c(k)
    } else if (art_tbl$position[k] - art_tbl$position[k - 1L] <= MERGE_THRESH) {
      cur_grp <- c(cur_grp, k)
    } else {
      groups[[length(groups) + 1L]] <- cur_grp
      cur_grp <- c(k)
    }
  }
  groups[[length(groups) + 1L]] <- cur_grp
  n_groups <- length(groups)

  # Compute start / end position and list of orig_i for every merged group
  grp_start <- integer(n_groups)
  grp_end   <- integer(n_groups)
  grp_orig  <- vector("list", n_groups)
  for (g in seq_len(n_groups)) {
    rows          <- groups[[g]]
    grp_start[g]  <- art_tbl$position[rows[1L]]
    grp_end[g]    <- if (g < n_groups)
                       art_tbl$position[groups[[g + 1L]][1L]] - 1L
                     else
                       body_end
    grp_orig[[g]] <- art_tbl$orig_i[rows]
  }

  # ----------------------------------------------------------
  # Step 7c: Absorb tiny article groups into the next group.
  #
  # When position estimation places multiple CONTENTS entries on
  # adjacent pages (e.g. pages 149, 150, 151), the text can get
  # fragmented into tiny slivers — some just 20-30 characters.
  # These fragments are not usable standalone articles.
  #
  # Fix: if a group's text span is below TINY_THRESH characters,
  # absorb it into the NEXT group (extend the next group backward
  # to include the tiny group's text).  Iterate until no tiny
  # non-last groups remain.
  # ----------------------------------------------------------
  TINY_THRESH <- 250L

  repeat {
    tiny_found <- FALSE
    for (g in seq_len(length(grp_start) - 1L)) {
      span <- grp_end[g] - grp_start[g] + 1L
      if (span < TINY_THRESH) {
        cat(sprintf("    Tiny group [%s] (%d chars) absorbed into next group\n",
                    paste(grp_orig[[g]], collapse=","), span))
        # Extend the next group backward to include this group's text
        grp_start[g + 1L] <- grp_start[g]
        grp_orig[[g + 1L]] <- c(grp_orig[[g]], grp_orig[[g + 1L]])
        # Remove this group
        grp_start <- grp_start[-(g)]
        grp_end   <- grp_end[-(g)]
        grp_orig  <- grp_orig[-(g)]
        tiny_found <- TRUE
        break   # restart scan since indices shifted
      }
    }
    if (!tiny_found) break
  }
  n_groups <- length(grp_start)

  # ----------------------------------------------------------
  # Step 8: FRONT MATTER
  # Everything from body_start up to the first group's start.
  #
  # When few page markers exist, the first found article may be
  # positioned far into the file (via [page-est]) while the real
  # article text starts at body_start.  A large front_matter gap
  # (>5000 chars) almost certainly contains article content that
  # was mismatched to later positions.  In that case, extend the
  # first article group backward to body_start so the text stays
  # with the article files instead of being spliced into Misc.
  # Small gaps (<= 5000 chars) are genuine front matter (masthead,
  # frontispiece caption, etc.) and are saved as Misc as before.
  # ----------------------------------------------------------
  if (grp_start[1L] > body_start) {
    front <- clean_headers(str_sub(text, body_start, grp_start[1L] - 1L))
    if (nchar(board_text) > 50) front <- str_replace(front, fixed(board_text), "")
    front <- str_trim(front)
    if (nchar(front) > 5000L) {
      # Large gap — likely contains article text.  Extend the first
      # article group to start at body_start so nothing is spliced off.
      grp_start[1L] <- body_start
      cat(sprintf("  NOTE: Large front gap (%s chars) — prepended to first article group\n",
                  format(nchar(front), big.mark=",")))
    } else if (nchar(front) > 0) {
      write_file(front,
                 file.path(out_folder, paste0(prefix, "_Misc_front_matter.txt")))
      cat(sprintf("  Misc: front_matter saved (%s chars)\n",
                  format(nchar(front), big.mark=",")))
    }
  }

  # ----------------------------------------------------------
  # Step 9: SAVE EACH (MERGED) ARTICLE GROUP and GAPS between them
  # ----------------------------------------------------------
  for (g in seq_len(n_groups)) {
    orig_is  <- grp_orig[[g]]
    a_start  <- grp_start[g]
    a_end    <- grp_end[g]

    art_raw  <- str_sub(text, a_start, a_end)
    art_text <- clean_headers(art_raw)
    if (nchar(board_text) > 50)
      art_text <- str_replace(art_text, fixed(board_text), "")
    art_text <- str_trim(art_text)

    # --- Strip leading continuation/conclusion markers ---
    # When position estimation draws the article boundary slightly before
    # the actual title, the tail of the PREVIOUS article leaks in.
    # This tail typically ends with "(Continued on page NNN)".
    # Example: "Their untiring efforts and (Continued on page 221) PAGE 161
    #           The Promise Of The Gospel..."
    # Strip EVERYTHING up to and including the continuation marker if it
    # appears within the first 500 characters of the article text.
    if (nchar(art_text) > 100L) {
      leading_chunk <- str_sub(art_text, 1L, min(500L, nchar(art_text)))
      cont_lead_m <- str_locate(leading_chunk,
                      regex("\\(?(?:Continued|Concluded)\\s+(?:on|from)\\s+page\\s+\\d+\\)?",
                            ignore_case = TRUE))
      if (!is.na(cont_lead_m[1,1])) {
        stripped_lead <- str_trim(str_sub(art_text, 1L, cont_lead_m[1,2]))
        art_text <- str_trim(str_sub(art_text, cont_lead_m[1,2] + 1L, nchar(art_text)))
        if (nchar(stripped_lead) > 5L) {
          cat(sprintf("    Leading continuation stripped from [%02d]: '%s' (%d chars)\n",
                      g, str_sub(stripped_lead, 1, 60), nchar(stripped_lead)))
        }
      }
    }

    # --- Truncate at "(Continued/Concluded from page NNN)" from OTHER articles ---
    # In the physical magazine, articles are sometimes interrupted and
    # continued on a later page.  The continuation text is then placed
    # after an unrelated article in the OCR stream.  When we extract an
    # article's block of text, the continuation from the OTHER article
    # gets spliced onto the end.
    #
    # Detection: search for "(Continued from page NNN)" or
    # "(Concluded from page NNN)" AFTER the first 500 characters.
    # Articles that ARE themselves continuations will have the marker
    # very near the start (within ~200 chars) and are left alone.
    if (nchar(art_text) > 600L) {
      cont_from_m <- str_locate_all(art_text,
                       regex("\\(?(?:Continued|Concluded) from page \\d+\\)?",
                             ignore_case = FALSE))[[1]]
      if (nrow(cont_from_m) > 0) {
        # Find the first occurrence after position 500
        late_hits <- which(cont_from_m[, 1] > 500L)
        if (length(late_hits) > 0) {
          hit_start <- cont_from_m[late_hits[1], 1]
          # Search backward up to 500 chars for a paragraph break or line break
          lookback_start <- max(1L, hit_start - 500L)
          lookback_text  <- str_sub(art_text, lookback_start, hit_start - 1L)

          # Prefer paragraph break (double newline) for a clean cut
          para_breaks <- str_locate_all(lookback_text, "\n\\s*\n")[[1]]
          if (nrow(para_breaks) > 0) {
            # Character before the first \n of the paragraph break
            cut_pos <- lookback_start + para_breaks[nrow(para_breaks), 1] - 2L
          } else {
            # Fall back to single newline
            newlines <- str_locate_all(lookback_text, "\n")[[1]]
            if (nrow(newlines) > 0) {
              cut_pos <- lookback_start + newlines[nrow(newlines), 1] - 2L
            } else {
              cut_pos <- hit_start - 1L
            }
          }

          if (cut_pos > 100L && cut_pos < nchar(art_text) - 50L) {
            stripped_cont <- str_trim(str_sub(art_text, cut_pos + 1L, nchar(art_text)))
            art_text      <- str_trim(str_sub(art_text, 1L, cut_pos))
            if (nchar(stripped_cont) > 5L) {
              cont_fn <- file.path(out_folder,
                                   paste0(prefix, "_Misc_cont_", sprintf("%02d", g), ".txt"))
              write_file(stripped_cont, cont_fn)
              cat(sprintf("    Continuation from other article stripped from [%02d]: %s chars -> Misc_cont_%02d\n",
                          g, format(nchar(stripped_cont), big.mark = ","), g))
            }
          }
        }
      }
    }

    # --- Truncate at "(Continued/Concluded on page NNN)" ---
    # When the article text ends with "(Continued on page 221)" followed
    # by content from the NEXT article (which starts immediately after
    # in the OCR stream), cut AFTER the marker — keep the marker as
    # part of this article, discard everything after it.
    if (nchar(art_text) > 600L) {
      cont_on_m <- str_locate_all(art_text,
                     regex("\\(?(?:Continued|Concluded)\\s+on\\s+page\\s+\\d+\\)?",
                           ignore_case = FALSE))[[1]]
      if (nrow(cont_on_m) > 0) {
        late_on <- which(cont_on_m[, 1] > 500L)
        if (length(late_on) > 0) {
          cut_after <- cont_on_m[late_on[1], 2]
          remaining <- nchar(art_text) - cut_after
          if (remaining > 100L) {
            stripped_on <- str_trim(str_sub(art_text, cut_after + 1L, nchar(art_text)))
            art_text    <- str_trim(str_sub(art_text, 1L, cut_after))
            if (nchar(stripped_on) > 5L) {
              cont_fn <- file.path(out_folder,
                                   paste0(prefix, "_Misc_cont_", sprintf("%02d", g), ".txt"))
              # Append if file already exists from "from page" truncation
              if (file.exists(cont_fn)) {
                existing <- read_file(cont_fn)
                write_file(paste0(existing, "\n\n", stripped_on), cont_fn)
              } else {
                write_file(stripped_on, cont_fn)
              }
              cat(sprintf("    Trailing '(Continued on page)' stripped from [%02d]: %s chars\n",
                          g, format(nchar(stripped_on), big.mark = ",")))
            }
          }
        }
      }
    }

    # --- Strip trailing ads from the LAST article group ---
    # The last group extends to body_end (== file end for Vol24-26), so
    # back-cover ads (Beneficial Life, Deseret News Press, etc.) are
    # swallowed into the last article's text.  Find the EARLIEST ad
    # marker across a broad list, then cut at the preceding paragraph
    # break to cleanly separate article from ads.
    if (g == n_groups) {
      ad_markers <- c(
        # Specific ad copy / taglines (appear early in ad section)
        "Invest\\s+Your\\s+Time\\s+in\\s+Business\\s+Education",
        "Bind\\s+Your\\s+Relief\\s+Society\\s+Magazine",
        "Preserve\\s+in\\s+bound\\s+volumes",
        "FOUR\\s+WAYS\\s+BETTER",
        "L\\.?\\s*D\\.?\\s*S\\.?\\s+TRAINING\\s+PAYS",
        "Planning\\s+Your\\s+Future.*will\\s+explain",
        # Advertiser names with addresses (clearly ads, not article mentions)
        "DESERET\\s+BOOK\\s+COMPANY\\s+\\d+\\s+East",
        "DESERET\\s+NEWS\\s+PRESS\\s+\\d+\\s+Richards",
        "L\\.?\\s*D\\.?\\s*S\\.?\\s+BUSINESS\\s+COLLEGE\\s+\\d+\\s+North",
        "KNIGHT.?S?\\s+SPRING\\s+CANYON\\s+COAL",
        "BLUE\\s+BLAZE\\s+COAL",
        "ARDEN\\s+DAIRY",
        "BENNETT\\s+GLASS\\s+&?\\s*PAINT",
        "FAIRBANKS.MORSE",
        "MOUNTAIN\\s+FUEL\\s+SUPPLY",
        "UTAH\\s+POWER\\s+&\\s+LIGHT",
        "SALT\\s+LAKE\\s+GLASS\\s+&\\s+PAINT",
        "SUGAR\\s+HOUSE\\s+LUMBER",
        "CRYSTAL\\s+PALACE\\s+MARKET",
        "PEERLESS\\s+LAUNDRY",
        "INTERMOUNTAIN\\s+BEET\\s+SUGAR",
        "LOCAL\\s+BEET\\s+SUGAR\\s+FOR",
        "Z\\.?\\s*C\\.?\\s*M\\.?\\s*I\\.?\\s+Clothing\\s+Factory",
        "Personalized\\s+Christmas\\s+Cards",
        "DESERET\\s+MORTUARY",
        # Ad footers and boilerplate
        "When\\s+Buying\\s+Mention\\s+Relief\\s+Society",
        "Mention\\s+Relief\\s+Society\\s+Magazine",
        "THE\\s+RELIEF\\s+SOCIETY\\s+MAGAZINE\\s+MORE\\s+THAN\\s+\\d",
        # Insurance (usually last)
        "BENEFICIAL\\s+LIFE\\s+INSURANCE",
        "BENEFICIAL\\s+LIFE\\s+(?:BLDG|BUILDING)",
        "HOME\\s+OFFICE[^\\n]*SALT\\s+LAKE\\s+CITY"
      )
      art_len <- nchar(art_text)
      # Search the last 50% to catch early ads
      search_from <- as.integer(art_len * 0.50)
      tail_text   <- str_sub(art_text, search_from, art_len)

      # Find the EARLIEST ad marker across ALL patterns
      earliest_pos <- NA_integer_
      for (amp in ad_markers) {
        am <- str_locate(tail_text, regex(amp, ignore_case = TRUE))
        if (!is.na(am[1, 1])) {
          abs_pos <- search_from + am[1, 1] - 1L
          if (is.na(earliest_pos) || abs_pos < earliest_pos)
            earliest_pos <- abs_pos
        }
      }

      if (!is.na(earliest_pos) && earliest_pos > 100L) {
        # Search backward from the ad marker to find a paragraph break
        # (double-newline) or start-of-line, for a clean cut.
        lookback <- str_sub(art_text,
                            max(1L, earliest_pos - 500L), earliest_pos)
        para_break <- str_locate_all(lookback, "\n\\s*\n")[[1]]
        if (nrow(para_break) > 0) {
          # Cut at the LAST paragraph break before the ad marker
          ad_cut <- max(1L, earliest_pos - 500L) + para_break[nrow(para_break), 2]
        } else {
          # No paragraph break found — cut right before the marker
          ad_cut <- earliest_pos - 1L
        }

        if (ad_cut > 100L) {
          stripped_ads <- str_trim(str_sub(art_text, ad_cut + 1L, art_len))
          art_text     <- str_trim(str_sub(art_text, 1L, ad_cut))
          if (nchar(stripped_ads) > 5L) {
            back_fn <- file.path(out_folder,
                                 paste0(prefix, "_Misc_back_matter.txt"))
            write_file(stripped_ads, back_fn)
            cat(sprintf("  Trailing ads stripped from last article: %s chars -> back_matter\n",
                        format(nchar(stripped_ads), big.mark = ",")))
          }
        }
      }
    }

    # Combined title: first article's title (+ subsequent if merged)
    primary_i     <- orig_is[1L]
    combined_title <- paste(arts$title[orig_is], collapse = " + ")
    display_title  <- str_sub(combined_title, 1, 60)

    saved_count <- saved_count + length(orig_is)   # count articles covered, not files
    fn <- file.path(out_folder,
      paste0(prefix, "_", sprintf("%02d", g), "_",
             arts$category[primary_i], "_",
             short_title_filename(arts$title[primary_i]), ".txt"))
    write_file(art_text, fn)

    if (length(orig_is) > 1L) {
      cat(sprintf("    Saved [%02d] %-60s %s chars  [MERGED %d articles]\n",
                  g, display_title, format(nchar(art_text), big.mark=","),
                  length(orig_is)))
    } else {
      cat(sprintf("    Saved [%02d] %-48s %s chars\n",
                  g, str_sub(arts$title[primary_i], 1, 48),
                  format(nchar(art_text), big.mark=",")))
    }

    # Gap to next group — save even small gaps so NO text is ever lost
    if (g < n_groups) {
      g_start <- grp_end[g] + 1L
      g_end   <- grp_start[g + 1L] - 1L
      if (g_end >= g_start) {
        gap <- str_trim(clean_headers(str_sub(text, g_start, g_end)))
        if (nchar(board_text) > 50) gap <- str_replace(gap, fixed(board_text), "")
        gap <- str_trim(gap)
        if (nchar(gap) > 5L) {
          gfn <- file.path(out_folder,
            paste0(prefix, "_Misc_gap_", sprintf("%02d", g), "_",
                   sprintf("%02d", g + 1L), ".txt"))
          write_file(gap, gfn)
          cat(sprintf("    Misc gap [%02d]->[%02d]: %s chars\n",
                      g, g + 1L, format(nchar(gap), big.mark=",")))
        }
      }
    }
  }

  # ----------------------------------------------------------
  # Step 10: BACK MATTER
  # Everything from the last group's end to body_end.
  # ----------------------------------------------------------
  last_end <- grp_end[n_groups]
  if (last_end < body_end) {
    back <- str_trim(clean_headers(str_sub(text, last_end + 1L, body_end)))
    if (nchar(back) > 5L) {
      write_file(back,
                 file.path(out_folder, paste0(prefix, "_Misc_back_matter.txt")))
      cat(sprintf("  Misc: back_matter saved (%s chars)\n",
                  format(nchar(back), big.mark=",")))
    }
  }

  # ----------------------------------------------------------
  # Step 11: Pre-body search for MISS articles, then placeholders
  # Some CONTENTS entries refer to text in the pre-body region.
  # If found, extract them as separate article files (not just Misc).
  # ----------------------------------------------------------
  true_miss_idx <- integer(0)
  prebody_article_num <- 0L
  if (length(miss_idx) > 0) {
    for (mi in miss_idx) {
      # Search pre-body regions EXCLUDING the CONTENTS listing.
      # Region 1: before CONTENTS (e.g. cover page text, early poems)
      # Region 2: between CONTENTS end and body start (e.g. frontispiece, ads)
      # This prevents CONTENTS entries from being extracted as bogus articles.
      pb_pos <- NA_integer_
      ct_s <- if (!is.na(s$contents_start)) s$contents_start else 1L
      ct_e <- if (!is.na(s$contents_end))   s$contents_end   else 0L
      if (ct_s > 1L) {
        pb_pos <- find_in_window(text, arts$title[mi], 1L, ct_s - 1L,
                                 allow_s10=TRUE)
      }
      if (is.na(pb_pos) && ct_e + 1L < body_start) {
        pb_pos <- find_in_window(text, arts$title[mi], ct_e + 1L,
                                 body_start - 1L, allow_s10=TRUE)
      }
      if (!is.na(pb_pos)) {
        # Found in pre-body — extract as separate article file
        # Find extent: from title position to next double-newline or body_start
        pb_region <- str_sub(text, pb_pos, body_start - 1L)
        # Find first double-newline after initial content (skip first 20 chars)
        end_break <- str_locate(str_sub(pb_region, 20L, nchar(pb_region)),
                                "\n\\s*\n")
        if (!is.na(end_break[1,1])) {
          # Check if there's meaningful text after the break; if < 200 chars
          # of remaining content, take it all (it's likely part of the article)
          remaining <- nchar(pb_region) - (20L + end_break[1,2])
          if (remaining > 200L) {
            pb_text <- str_trim(str_sub(pb_region, 1L, 20L + end_break[1,2]))
          } else {
            pb_text <- str_trim(pb_region)
          }
        } else {
          pb_text <- str_trim(pb_region)
        }
        # Only save if the text is substantial (not just a masthead line)
        if (nchar(pb_text) > 30L && !str_detect(arts$title[mi],
            regex("PUBLISHED\\s+MONTHLY|Bishop.s\\s+Building", ignore_case=TRUE))) {
          prebody_article_num <- prebody_article_num + 1L
          pb_fn <- file.path(out_folder,
            paste0(prefix, "_00pb", sprintf("%d", prebody_article_num), "_",
                   arts$category[mi], "_",
                   short_title_filename(arts$title[mi]), ".txt"))
          write_file(pb_text, pb_fn)
          saved_count <- saved_count + 1L
          cat(sprintf("    Saved pre-body article: '%s' (%s chars)\n",
                      str_sub(arts$title[mi],1,50),
                      format(nchar(pb_text), big.mark=",")))
        } else {
          # Masthead or tiny text — already in Misc, just count
          saved_count <- saved_count + 1L
          cat(sprintf("    Captured in _00_Misc: '%s' (pre-body @%d)\n",
                      str_sub(arts$title[mi],1,50), pb_pos))
        }
      } else {
        true_miss_idx <- c(true_miss_idx, mi)
      }
    }
  }

  if (length(true_miss_idx) > 0) {
    for (mi in true_miss_idx) {
      # Log to console only — no placeholder files.  The text for these
      # articles is genuinely absent from the OCR body (Frontispiece pages,
      # poems/pieces on un-scanned pages, or garbled OCR titles).
      cat(sprintf("    NOT IN SOURCE: '%s' (pg %s)\n",
                  str_sub(arts$title[mi],1,50), arts$page[mi]))
    }
  }

  # ----------------------------------------------------------
  # Step 11b: Extract pre-body articles misplaced at body_start.
  # When page-est clusters multiple articles at/near body_start,
  # their actual text is often in the post-CONTENTS pre-body region
  # (poems, cover notes, frontispiece text).  Search there and
  # extract as separate _00pb files.
  # ----------------------------------------------------------
  bodystart_idx <- which(!is.na(positions) &
                         positions >= body_start &
                         positions <= body_start + 50L)
  if (length(bodystart_idx) >= 2L) {
    ct_e <- if (!is.na(s$contents_end)) s$contents_end else 0L
    if (ct_e + 1L < body_start - 100L) {
      pb_found <- data.frame(idx=integer(0), pos=integer(0),
                             stringsAsFactors=FALSE)
      for (bi in bodystart_idx) {
        pb_pos <- find_in_window(text, arts$title[bi], ct_e + 1L,
                                 body_start - 1L, allow_s10=TRUE)
        if (!is.na(pb_pos)) {
          pb_found <- rbind(pb_found, data.frame(idx=bi, pos=pb_pos))
        }
      }
      if (nrow(pb_found) > 0L) {
        pb_found <- pb_found[order(pb_found$pos), ]
        # Deduplicate: if two matches are within 100 chars, keep earliest
        if (nrow(pb_found) > 1L) {
          keep <- rep(TRUE, nrow(pb_found))
          for (k in 2:nrow(pb_found)) {
            if (pb_found$pos[k] - pb_found$pos[k-1] < 100L) keep[k] <- FALSE
          }
          pb_found <- pb_found[keep, , drop=FALSE]
        }
        for (k in seq_len(nrow(pb_found))) {
          start_pos <- pb_found$pos[k]
          end_pos   <- if (k < nrow(pb_found)) pb_found$pos[k+1] - 1L
                       else body_start - 1L
          pb_text <- str_trim(str_sub(text, start_pos, end_pos))
          # Strip trailing Vol./No. masthead line
          pb_text <- str_replace(pb_text,
            regex("\\s*Vol\\.?\\s*\\d+\\s+[A-Z]+,?\\s+\\d{4}\\s+No\\.?\\s*\\d+\\s*$",
                  ignore_case=TRUE), "")
          pb_text <- str_trim(pb_text)
          ai <- pb_found$idx[k]
          if (nchar(pb_text) > 50L &&
              !str_detect(pb_text, regex("^\\s*PUBLISHED\\s+MONTHLY",
                                        ignore_case=TRUE))) {
            prebody_article_num <- prebody_article_num + 1L
            pb_fn <- file.path(out_folder,
              paste0(prefix, "_00pb", sprintf("%d", prebody_article_num), "_",
                     arts$category[ai], "_",
                     short_title_filename(arts$title[ai]), ".txt"))
            write_file(pb_text, pb_fn)
            saved_count <- saved_count + 1L
            cat(sprintf("    Saved pre-body [body_start] article: '%s' (%s chars)\n",
                        str_sub(arts$title[ai],1,50),
                        format(nchar(pb_text), big.mark=",")))
          }
        }
      }
    }
  }

  # ----------------------------------------------------------
  # Step 12: Scan Misc_cont files for embedded CONTENTS articles.
  # When Fix 14/17b strips continuation text from an article group,
  # sometimes a following article's body gets swept into the
  # Misc_cont file.  Find these by searching for the first
  # distinctive word of each CONTENTS title after a paragraph break.
  # ----------------------------------------------------------
  misc_cont_files <- sort(list.files(out_folder,
                           pattern="_Misc_cont_\\d+\\.txt$",
                           full.names=TRUE))
  if (length(misc_cont_files) > 0L) {
    common_words <- c("the", "this", "that", "with", "from", "their",
                      "about", "what", "which", "they", "them",
                      "chapter", "part", "page", "society", "article",
                      "relief", "magazine", "notes", "field", "editorial",
                      "general", "lesson", "work")
    for (mcf in misc_cont_files) {
      mc_text <- read_file(mcf)
      if (nchar(mc_text) < 200L) next
      best_match <- NULL
      for (i in seq_len(nrow(arts))) {
        tw <- str_split(arts$title[i], "\\s+")[[1]]
        tw <- tw[nchar(tw) > 3L]
        tw <- tw[!tolower(tw) %in% common_words]
        if (length(tw) == 0L) next
        search_word <- tw[1]
        # Look for the distinctive word after a paragraph break (\n\n)
        # and at least 50 chars into the file (skip continuation header)
        m_all <- str_locate_all(mc_text,
                   regex(paste0("\\n\\s*\\n[^\\n]*?\\b", search_word, "\\b"),
                         ignore_case = TRUE))[[1]]
        if (nrow(m_all) > 0L) {
          for (r in seq_len(nrow(m_all))) {
            if (m_all[r,1] > 50L) {
              if (is.null(best_match) || m_all[r,1] < best_match$pos) {
                best_match <- list(idx=i, pos=m_all[r,1], word=search_word)
              }
              break
            }
          }
        }
      }
      if (!is.null(best_match)) {
        # Advance past the \n\n whitespace to the actual article line start
        split_pos <- best_match$pos
        while (split_pos <= nchar(mc_text) &&
               str_sub(mc_text, split_pos, split_pos) %in% c("\n", "\r", " ", "\t")) {
          split_pos <- split_pos + 1L
        }
        pre_text <- str_trim(str_sub(mc_text, 1L, split_pos - 1L))
        art_text_mc <- str_trim(str_sub(mc_text, split_pos, nchar(mc_text)))
        if (nchar(art_text_mc) > 50L) {
          ai <- best_match$idx
          prebody_article_num <- prebody_article_num + 1L
          art_fn <- file.path(out_folder,
            paste0(prefix, "_00pb", sprintf("%d", prebody_article_num), "_",
                   arts$category[ai], "_",
                   short_title_filename(arts$title[ai]), ".txt"))
          write_file(art_text_mc, art_fn)
          saved_count <- saved_count + 1L
          # Rewrite Misc_cont with only the continuation part
          if (nchar(pre_text) > 5L) {
            write_file(pre_text, mcf)
          } else {
            file.remove(mcf)
          }
          cat(sprintf("    Extracted from Misc_cont: '%s' (%s chars) [matched '%s']\n",
                      str_sub(arts$title[ai],1,50),
                      format(nchar(art_text_mc), big.mark=","),
                      best_match$word))
        }
      }
    }
  }

  n_missed <- length(true_miss_idx)
  cat(sprintf("\n  RESULT: %d saved, %d NOT IN SOURCE, %d total in CONTENTS\n",
              saved_count, n_missed, nrow(arts)))

  data.frame(file=filename, n_contents=nrow(arts), n_saved=saved_count,
             n_missed=n_missed, total_chars=len, stringsAsFactors=FALSE)
}
```

```{r run, message=FALSE}
# ============================================================
# MAIN LOOP
# ============================================================
cat("Relief Society Magazine — Universal Article Extractor\n")
cat(rep("=",70), "\n\n", sep="")

all_results <- list()

for (input_dir in INPUT_DIRS) {
  if (!dir.exists(input_dir)) {
    cat("WARNING: not found:", input_dir, "\n"); next
  }
  files <- sort(list.files(input_dir, pattern="\\.txt$",
                           full.names=TRUE, recursive=FALSE))
  cat("\n", rep("#",70), "\n", sep="")
  cat("FOLDER:", basename(input_dir), " — ", length(files), "file(s)\n")
  cat(rep("#",70), "\n", sep="")

  for (f in files) {
    res <- tryCatch(
      process_issue(f, OUTPUT_DIR),
      error=function(e) {
        cat("ERROR:", basename(f), "—", conditionMessage(e), "\n")
        data.frame(file=basename(f), n_contents=0L, n_saved=0L,
                   n_missed=0L, total_chars=0L, stringsAsFactors=FALSE)
      })
    all_results[[length(all_results)+1]] <- res
  }
}

results_df <- if (length(all_results)>0) do.call(rbind, all_results) else NULL
```

## Summary {.tabset}

### Results Table

```{r summary}
if (!is.null(results_df) && nrow(results_df)>0) {
  cat(sprintf("Files processed:       %d\n",   nrow(results_df)))
  cat(sprintf("Articles in CONTENTS:  %d\n",   sum(results_df$n_contents)))
  cat(sprintf("Articles saved:        %d\n",   sum(results_df$n_saved)))
  cat(sprintf("Not in source (OCR):   %d\n",   sum(results_df$n_missed)))
  cat(sprintf("Hit rate:              %.1f%%\n",
              sum(results_df$n_saved) / max(1, sum(results_df$n_contents)) * 100))
  cat("Output folder:", OUTPUT_DIR, "\n\n")

  kable(results_df,
        col.names=c("File","In CONTENTS","Saved","Not in Source","Total Chars"),
        format.args=list(big.mark=",")) %>%
    kable_styling(bootstrap_options=c("striped","hover","condensed"),
                  full_width=FALSE) %>%
    column_spec(4, color=ifelse(results_df$n_missed > 0, "red", "darkgreen"))
}
```

### Notes on "Not In Source" Files

When an article listed in the CONTENTS cannot be found anywhere in the body text, the script saves a `_NOT_IN_SOURCE_` placeholder file. This happens when the original print pages were not included in the digitisation/OCR — the text simply is not in the source file. These are **not extraction errors**; they reflect genuine gaps in the OCR source material.

Gaps between articles are saved as `_Misc_gap_` files so that no text is ever discarded. The entire range from `body_start` to `body_end` is always fully covered.
